### 2020-02-28 paper/paper.tex
Add JHEP-style article

\documentclass[a4paper,11pt]{article}
\pdfoutput=1

\usepackage{jheppub}
\usepackage[T1]{fontenc}

\title{Including EW and mixed QCD-EW corrections into PDF fits}

\author[a,b]{S. Carrazza,}
\author[b]{E. Nocera,}
\author[a]{C. Schwan}
\author[a,b]{and M. Zaro}

\affiliation[a]{Tif Lab, Dipartimento di Fisica, Universit\`a di Milano and INFN, Sezione di Milano, 20133 Milano, Italy}
\affiliation[b]{Nikhef Theory Group, Science Park 105, 1098 XG Amsterdam, The Netherlands}

\emailAdd{stefano.carraza@mi.infn.it}
\emailAdd{e.nocera@nikhef.nl}
\emailAdd{christopher.schwan@mi.infn.it}
\emailAdd{marco.zaro@mi.infn.it}

\abstract{}

\begin{document}

\maketitle
\flushbottom

\section{Introduction}
\label{sec:introduction}

\cite{Carli:2010rw}
\cite{Bertone:2014zva}

\appendix

\acknowledgments

C.S. is supported by the European Research Council under the European Unions Horizon 2020 research and innovation Programme (grant agreement no. 740006).

\bibliographystyle{JHEP}
\bibliography{paper}

\end{document}

### 2020-02-28 applgridphoton/include/pineappl.h
Rename `file` to `grid`

@@ -47,7 +47,7 @@ typedef enum
 pineappl_grid_format;
 
 ///
-int pineappl_file_open(
+int pineappl_grid_new(
     int n_bins,
     double const* bin_limits,
     pineappl_lumi* lumi,
@@ -66,11 +66,11 @@ int pineappl_file_open(
 );
 
 ///
-void pineappl_file_close(int file_id);
+void pineappl_grid_delete(int grid_id);
 
 ///
-void pineappl_file_fill(
-    int file_id,
+void pineappl_grid_fill(
+    int grid_id,
     double x1,
     double x2,
     double q2,
@@ -80,10 +80,10 @@ void pineappl_file_fill(
 );
 
 ///
-void pineappl_file_scale(int file_id, double factor);
+void pineappl_grid_scale(int grid_id, double factor);
 
 ///
-void pineappl_file_write(int file_id, char const* filename);
+void pineappl_grid_write(int grid_id, char const* filename);
 
 // TODO: remove the `const&`
 
@@ -94,8 +94,8 @@ typedef void (*pineappl_func_xfx)(double const& x1, double const& q2, double* pd
 typedef double (*pineappl_func_alphas)(double const& q2);
 
 ///
-void pineappl_file_convolute(
-    int file_id,
+void pineappl_grid_convolute(
+    int grid_id,
     pineappl_func_xfx pdf1,
     pineappl_func_xfx pdf2,
     pineappl_func_alphas alphas,

### 2020-02-28 applgridphoton/src/pineappl.cpp

@@ -55,7 +55,7 @@ void pineappl_lumi_add(pineappl_lumi* lumi, unsigned combinations, int* pdg_id_p
     lumi->combinations.emplace_back(std::vector<int>(pdg_id_pairs, pdg_id_pairs + 2 * combinations));
 }
 
-int pineappl_file_open(
+int pineappl_grid_new(
     int n_bins,
     double const* bin_limits,
     pineappl_lumi* lumi,
@@ -120,13 +120,13 @@ int pineappl_file_open(
     return index;
 }
 
-void pineappl_file_close(int /*file_id*/)
+void pineappl_grid_delete(int /*grid_id*/)
 {
     // TODO: deallocate memory
 }
 
-void pineappl_file_fill(
-    int file_id,
+void pineappl_grid_fill(
+    int grid_id,
     double x1,
     double x2,
     double q2,
@@ -134,21 +134,21 @@ void pineappl_file_fill(
     double const* weight,
     unsigned grid_index
 ) {
-    appl_grids().at(file_id).fill_grid(x1, x2, q2, observable, weight, grid_index);
+    appl_grids().at(grid_id).fill_grid(x1, x2, q2, observable, weight, grid_index);
 }
 
-void pineappl_file_scale(int file_id, double factor)
+void pineappl_grid_scale(int grid_id, double factor)
 {
-    appl_grids().at(file_id) *= factor;
+    appl_grids().at(grid_id) *= factor;
 }
 
-void pineappl_file_write(int file_id, char const* filename)
+void pineappl_grid_write(int grid_id, char const* filename)
 {
-    appl_grids().at(file_id).Write(filename);
+    appl_grids().at(grid_id).Write(filename);
 }
 
-void pineappl_file_convolute(
-    int file_id,
+void pineappl_grid_convolute(
+    int grid_id,
     pineappl_func_xfx pdf1,
     pineappl_func_xfx pdf2,
     pineappl_func_alphas alphas,
@@ -161,7 +161,7 @@ void pineappl_file_convolute(
     // TODO: selecting and deselecting grids is not completely possible with APPLgrid
     assert( grid_mask == nullptr );
 
-    auto const result = appl_grids().at(file_id).vconvolute(pdf1, pdf2, alphas, 99, scale_ren,
+    auto const result = appl_grids().at(grid_id).vconvolute(pdf1, pdf2, alphas, 99, scale_ren,
         scale_fac, scale_energy);
 
     std::copy(result.begin(), result.end(), bins);

### 2020-02-28 applgridphoton/tests/basic.cpp

@@ -40,7 +40,7 @@ TEST_CASE("", "")
     std::array<double, 2> bin_limits = { 0.0, 1.0 };
 
     // create a new file
-    int file_id = pineappl_file_open(
+    int grid_id = pineappl_grid_new(
         bin_limits.size() - 1,
         bin_limits.data(),
         lumi,
@@ -62,16 +62,16 @@ TEST_CASE("", "")
     pineappl_lumi_delete(lumi);
 
     // this is the first time that we call the function, thus the index must be zero
-    CHECK( file_id == 0 );
+    CHECK( grid_id == 0 );
 
     std::array<double, 1> const weights = { 1.0 };
 
-    pineappl_file_fill(file_id, 0.25, 0.25, 10000.0, 0.25, weights.data(), 0);
+    pineappl_grid_fill(grid_id, 0.25, 0.25, 10000.0, 0.25, weights.data(), 0);
 
     double result;
 
-    pineappl_file_convolute(
-        file_id,
+    pineappl_grid_convolute(
+        grid_id,
         simple_pdf,
         simple_pdf,
         alphas,

### 2020-02-28 applgridphoton/include/pineappl.h
Use pointers instead of indices for grid functions

@@ -47,7 +47,10 @@ typedef enum
 pineappl_grid_format;
 
 ///
-int pineappl_grid_new(
+struct pineappl_grid;
+
+///
+pineappl_grid* pineappl_grid_new(
     int n_bins,
     double const* bin_limits,
     pineappl_lumi* lumi,
@@ -66,11 +69,11 @@ int pineappl_grid_new(
 );
 
 ///
-void pineappl_grid_delete(int grid_id);
+void pineappl_grid_delete(pineappl_grid* grid);
 
 ///
 void pineappl_grid_fill(
-    int grid_id,
+    pineappl_grid* grid,
     double x1,
     double x2,
     double q2,
@@ -80,10 +83,10 @@ void pineappl_grid_fill(
 );
 
 ///
-void pineappl_grid_scale(int grid_id, double factor);
+void pineappl_grid_scale(pineappl_grid* grid, double factor);
 
 ///
-void pineappl_grid_write(int grid_id, char const* filename);
+void pineappl_grid_write(pineappl_grid* grid, char const* filename);
 
 // TODO: remove the `const&`
 
@@ -95,7 +98,7 @@ typedef double (*pineappl_func_alphas)(double const& q2);
 
 ///
 void pineappl_grid_convolute(
-    int grid_id,
+    pineappl_grid* grid,
     pineappl_func_xfx pdf1,
     pineappl_func_xfx pdf2,
     pineappl_func_alphas alphas,

### 2020-02-28 applgridphoton/src/pineappl.cpp
Use pointers instead of indices for grid functions

@@ -7,18 +7,8 @@
 #include <array>
 #include <cassert>
 #include <string>
+#include <utility>
 #include <vector>
-
-namespace
-{
-
-std::vector<appl::grid>& appl_grids()
-{
-    static std::vector<appl::grid> appl_grids_;
-    return appl_grids_;
-}
-
-}
 
 struct pineappl_lumi
 {
@@ -55,7 +45,17 @@ void pineappl_lumi_add(pineappl_lumi* lumi, unsigned combinations, int* pdg_id_p
     lumi->combinations.emplace_back(std::vector<int>(pdg_id_pairs, pdg_id_pairs + 2 * combinations));
 }
 
-int pineappl_grid_new(
+struct pineappl_grid
+{
+    pineappl_grid(appl::grid&& grid)
+        : grid(std::move(grid))
+    {
+    }
+
+    appl::grid grid;
+};
+
+pineappl_grid* pineappl_grid_new(
     int n_bins,
     double const* bin_limits,
     pineappl_lumi* lumi,
@@ -72,8 +72,6 @@ int pineappl_grid_new(
     unsigned x_order,
     char const* map
 ) {
-    int const index = appl_grids().size();
-
     // STEP 1: prepare the vector containing the grid parameters for all grids
 
     // TODO: other format are currently not implemented
@@ -93,7 +91,7 @@ int pineappl_grid_new(
 
     // STEP 2: prepare the PDF combinations
 
-    std::string const pdf_name = "pineappl_appl_grid_pdf_bridge_" + std::to_string(index);
+    std::string const pdf_name = "pineappl_appl_grid_pdf_bridge_0"; // TODO: add unique identifier
     std::vector<int> lumi_vector;
     lumi_vector.push_back(lumi->combinations.size());
 
@@ -114,19 +112,17 @@ int pineappl_grid_new(
 
     // STEP 3: create the appl grids
 
-    appl_grids().emplace_back(n_bins, bin_limits, nq2, q2_min, q2_max, q2_order, nx, x_min, x_max,
-        x_order, pdf_name, order_ids, map);
-
-    return index;
+    return new pineappl_grid(appl::grid(n_bins, bin_limits, nq2, q2_min, q2_max, q2_order, nx,
+        x_min, x_max, x_order, pdf_name, order_ids, map));
 }
 
-void pineappl_grid_delete(int /*grid_id*/)
+void pineappl_grid_delete(pineappl_grid* grid)
 {
-    // TODO: deallocate memory
[…]

### 2020-02-28 applgridphoton/tests/basic.cpp

@@ -40,7 +40,7 @@ TEST_CASE("", "")
     std::array<double, 2> bin_limits = { 0.0, 1.0 };
 
     // create a new file
-    int grid_id = pineappl_grid_new(
+    auto* grid = pineappl_grid_new(
         bin_limits.size() - 1,
         bin_limits.data(),
         lumi,
@@ -61,17 +61,14 @@ TEST_CASE("", "")
     // delete luminosity function
     pineappl_lumi_delete(lumi);
 
-    // this is the first time that we call the function, thus the index must be zero
-    CHECK( grid_id == 0 );
-
     std::array<double, 1> const weights = { 1.0 };
 
-    pineappl_grid_fill(grid_id, 0.25, 0.25, 10000.0, 0.25, weights.data(), 0);
+    pineappl_grid_fill(grid, 0.25, 0.25, 10000.0, 0.25, weights.data(), 0);
 
     double result;
 
     pineappl_grid_convolute(
-        grid_id,
+        grid,
         simple_pdf,
         simple_pdf,
         alphas,
@@ -83,4 +80,6 @@ TEST_CASE("", "")
     );
 
     CHECK( result == 1.0 );
+
+    pineappl_grid_delete(grid);
 }

### 2020-03-20 paper/paper.tex
adding notes

@@
 
-\emailAdd{stefano.carraza@mi.infn.it}
+\emailAdd{stefano.carrazza@mi.infn.it}
 \emailAdd{e.nocera@nikhef.nl}
@@
 
+ERN
+
+The impact of EW corrections to LHC data.\\
+How to do that consistently, include systematically EW corrections, blabla.\\
+Outline a possible strategy to deal with EW correction in LHC observables (FSR, PHOTOS, dressed/born, ...).\\
+Pinappl kills amcfast and mcgrid, replace applgrid and fastnlo.\\
+
+\section{Technical}
+
+CS, MZ
+
+Describe pineappl, representation of grids, accuracy and performance.\\
+We may provide converters from applgrid.\\
+How to integrate in MC codes, how this works in aMCblast (setup, MG5 version, urls).\\
+Appendix: how to create and fill grids, + simple code.\\
+
+\section{Results}
+
+SC
+
+For datasets in 3.1qed (+DY2), compute pure NLO QCD (born) vs NLO QCD + NLO EW (dressed) FKtables and:\\
+- compute data/prediction plots\\
+- compute chi2\\
+
+\section{Double counting}
+
+Count von Count, ALL
+
+Explain the problem to experimentalists.\\
+
+\section{Outlook}
+
+ALL
+
 \cite{Carli:2010rw}

### 2020-03-20 paper/technical-aspects.tex
Add praise for PineAPPL

\subsection{PineAPPL}
\label{sec:pineappl}

In this paper we introduce a new program called \textsc{PineAPPL}, which solves the same problem as \textsc{APPLgrid}~\cite{} and \textsc{fastNLO}~\cite{}, but also supports EW corrections, which are the main interest here.
In particular, the following features distinguish it from the two aforementioned programs:
\begin{itemize}
\item support for arbitrary fixed-order calculations in $\alpha$ and $\alpha_\mathrm{s}$ with
\item support for scale variations in multiples of the central renormalization and factorization scale,
\item support for all-order predictions from resummation and photon-/parton-showers,
\item a simple \textsc{C}-interface, with a wrapper for \textsc{Fortran}
\item and support for it implemented in \textsc{mg5\_aMC@NLO},
\item converters to convert \textsc{APPLgrids} and \textsc{fastNLO} tables.
\end{itemize}

\subsection{Grid representation}
\label{sec:grid-representation}

\subsection{Accuracy and performance}
\label{sec:accuracy-and-performance}

CS, MZ

How to integrate in MC codes, how this works in aMCblast (setup, MG5 version, urls).\\
Appendix: how to create and fill grids, + simple code.

### 2020-03-23 paper/technical-aspects.tex
some edits in paper

@@
 
+\subsubsection{Cross sections in a multi-coupling expansion}
+The structure of the cross-section weights needed by \textsc{PineAPPL} follows the scheme outlined in 
+Refs.~\cite{Frederix:2011ss, Bertone:2014zva}, embedded in a mixed-coupling expansion, see Ref.~\cite{Frederix:2018nkq} and Refs.CITE for
+specific examples. Starting 
+from the latter, an observable $\Sigma(\alphas, \alpha)$ is written as
+\begin{equation}
+    \Sigma(\alphas, \alpha) = \alpha^c \alphas^{c_S} \sum_{a_S, a} \alphas^{a_S} \alpha^a \Sigma_{a_S, a}\,.
+\end{equation}
+$c$ and $c_S$ are process-dependent; the contributions $\Sigma_{a_S, a}$ are in general non-zero for $a_S, a \ge 0$ and $a_S + a > q$, where also $q$ is a process-dependent quantity. For example,
+for (stable) top-pair production, $c=c_S=0$ and $q=2$; for Drell-Yan production, $c=2$, $c_S=0$, and $q=0$. Terms 
+with  $a_S + a = q + k$ correspond to different N$^k$LO contributions to $\Sigma$, usually
+labeled as N$^k$LO$_i$, $i =1,2, \ldots$, with $i=1$ assigned to the term with the largest power of $\alphas$. Given the hierarchy of the couplings,
+one expects that 
+\begin{equation}
+ \textrm{N}^k\textrm{LO}_1 \gg \textrm{N}^k\textrm{LO}_2 \gg\ldots \, ,
+\end{equation}
+however such a relation is not always respected, and sometimes blatantly violated~CITE.
+
+Given the perturbative order (LO, NLO, \ldots), different weights $\cal W$, with different kinematics expressed by the set $\cal P$, enter the various 
+terms $\Sigma_{a_S, a}$. One can write 
+\begin{equation}
+    \Sigma_{a_S, a}= \sum_{l\in \mathcal P} f_1(x_1^{(l)},\mu_F^{(l)}) \,f_2(x_2^{(l)},\mu_F^{(l)}) \mathcal W^{(l)}_{a_S, a} 
+    d \textrm{PS}\,,
+\end{equation}
+where we have introduced the parton distributions $f_{1,2}$ and the phase-space measure $d$PS.
+\begin{itemize}
+    \item At LO, $\mathcal P = \{B\}$, $B$ being the Born kinematics, and the weight structure is trivial,
+    \begin{equation}
+        \mathcal W^{(l)}_{a_S, a} = {\mathcal W^{(l),0}_{a_S, a}}\,.
+    \end{equation}
+    \item At NLO, $\mathcal P = \{E, S, C, SC\}$ with, $E$ being the event (or resolved) kinematics, and $S$, $C$, $SC$ being
+        respectively the soft, collinear, and soft-collinear kinematics. The weight structure includes three terms at NLO:
+    \begin{equation}
+        \mathcal W^{(l)}_{a_S, a} = {{\mathcal W}^{(l),0}_{a_S, a}} + 
+                                {\mathcal W^{(l),R}_{a_S, a}} \log\left(\frac{{\mu_R^{(l)}}^2}{Q^2}\right) + 
+                                {\mathcal W^{(l),F}_{a_S, a}} \log\left(\frac{{\mu_F^{(l)}}^2}{Q^2}\right) 
+    \end{equation}
+    where, besides the renormalisation and factorisation scales $\mu_{R,F}$, we have introduced the Ellis-Sexton scale $Q$
+\end{itemize}
+
 \subsection{Grid representation}

### 2020-03-23 applgriddiff/include/applgriddiff.hpp

@@ -1,18 +1,0 @@
-#ifndef APPLGRIDDIFF_HPP
-#define APPLGRIDDIFF_HPP
-
-#include <TDirectory.h>
-#include <TH1.h>
-#include <TObject.h>
-#include <TVectorT.h>
-
-bool diff_directory(TDirectory& dir1, TDirectory& dir2);
-
-bool diff_histogram(TH1 const& obj1, TH1 const& obj2);
-
-template <typename T>
-bool diff_vector_t(TVectorT<T> const& obj1, TVectorT<T> const& obj2);
-
-bool dispatch_and_diff(TObject& obj1, TObject& obj2);
-
-#endif

### 2020-03-23 applgridphoton/appl_grid/SparseMatrix3d.h

@@ -1,120 +1,0 @@
-// emacs: this is -*- c++ -*-
-//
-//   SparseMatrix3d.h        
-//
-//                   
-// 
-//   Copyright (C) 2007 M.Sutton (sutt@hep.ucl.ac.uk)    
-//
-//   $Id: SparseMatrix3d.h, v1.0   Wed Nov 14 14:23:49 GMT 2007 sutt
-
-
-#ifndef __SPARSEMATRIX3D_H
-#define __SPARSEMATRIX3D_H
-
-#include <iostream>
-
-#include "axis.h"
-#include "tsparse3d.h"
-
-class SparseMatrix3d : public tsparse3d<double> {
-
-public:
-
-  // constructors and destructor
-
-  SparseMatrix3d( int Nx, double lx, double ux, 
-		  int Ny, double ly, double uy, 
-		  int Nz, double lz, double uz);
-
-  SparseMatrix3d(const SparseMatrix3d& s); 
-
-  ~SparseMatrix3d() { empty_fast(); } 
-
-  // axis accessors
-  const axis<double>& xaxis() const { return m_xaxis; } 
-  const axis<double>& yaxis() const { return m_yaxis; } 
-  const axis<double>& zaxis() const { return m_zaxis; } 
-
-
-  // trim to sparse structure 
-  void trim() { empty_fast(); tsparse3d<double>::trim(); }
-    
-  // access using the fast (dangerous) methods
-  double& fill_fast(int i, int j, int k);
-  double  fill_fast(int i, int j, int k) const;
-
-  void fill(double x, double y, double z, double w);
-  
-  /// check if the axes are all the same
-  bool compare_axes(const SparseMatrix3d& s) const { 
-
-#if 0
-
-    std::cout << "SparseMatrix: " 
-	      << "\tx " << m_xaxis 
-	      << "\ty " << m_yaxis 
-	      << "\tz " << m_zaxis << std::endl; 
-
-    std::cout << "SparseMatrix: " 
-	      << "\tx " << s.m_xaxis 
-	      << "\ty " << s.m_yaxis 
-	      << "\tz " << s.m_zaxis << std::endl; 
-
-    std::cout << "SparseMatrix: " 
-	      << "\tx " << ( m_xaxis == s.m_xaxis ) 
-	      << "\ty " << ( m_yaxis == s.m_yaxis )
[…]

### 2020-03-23 applgridphoton/appl_grid/appl_grid.h

@@ -1,279 +1,0 @@
-// emacs: this is -*- c++ -*-
-
-//  appl_grid.h       
-
-//  grid class header - all the functions needed to create and 
-//  fill the grid from an NLO calculation program
-//  
-//  Copyright (C) 2007 Mark Sutton (sutt@hep.ucl.ac.uk)    
-
-// $Id: appl_grid.h, v1.00 2007/10/16 17:01:39 sutt
-
-// Fixme: this needs to be tidied up. eg there are too many different, 
-//        and too many version of, accessors for x/y, Q2/tau etc there 
-//        should be only  one set, for x and Q2 *or* y and tau, but 
-//        not both. In fact they should be for x and Q2, since y and tau 
-//        should be purely an internal grid issue of no concern for the 
-//        user.
-
-#ifndef __APPL_PHOTON
-#define __APPL_PHOTON
-#endif
-
-#ifndef __APPL_GRID_H
-#define __APPL_GRID_H
-
-#include "histo1d.hpp"
-
-#include <exception>
-#include <iosfwd>
-#include <string>
-#include <vector>
-
-namespace appl { 
-
-
-/// forward declarations - full definitions included 
-/// from appl_grid.cxx 
-class igrid;
-class appl_pdf;
-
-class order_id
-{
-public:
-    order_id(int alphs, int alpha, int lmuf2, int lmur2)
-        : alphs_{alphs}
-        , alpha_{alpha}
-        , lmuf2_{lmuf2}
-        , lmur2_{lmur2}
-    {
-    }
-
-    int alphs() const
-    {
-        return alphs_;
-    }
-
-    int alpha() const
-    {
-        return alpha_;
-    }
-
-    int lmuf2() const
-    {
-        return lmuf2_;
-    }
-
-    int lmur2() const
-    {
-        return lmur2_;
-    }
-
-private:
-    int alphs_;
-    int alpha_;
-    int lmuf2_;
-    int lmur2_;
-};
-
-inline bool operator==(order_id const& a, order_id const& b)
-{
-    return (a.alphs() == b.alphs()) && (a.alpha() == b.alpha()) && (a.lmuf2() == b.lmuf2())
-        && (a.lmur2() == b.lmur2());
-}
-
-/// externally visible grid class
-class grid {
-
-public:
-
-  // grid error exception
-  class exception : public std::exception { 
-  public:
-    exception(const std::string& s);
-    exception(std::ostream&);
[…]

### 2020-03-23 applgridphoton/appl_grid/appl_igrid.h

@@ -1,336 +1,0 @@
-// emacs: this is -*- c++ -*-
-//
-//   appl_igrid.h        
-//
-//  grid class header - all the functions needed to create and 
-//  fill the grid from an NLO calculation program, based on the 
-//  class from D.Clements and T.Carli.
-//
-//  See contribution from T.Carli et al from the HERA-LHC 
-//  workshop - working group 3 
-//  
-//  Copyright (C) 2007 Mark Sutton (sutt@hep.ucl.ac.uk)    
-//
-//   $Id: appl_igrid.h, v2.00  Fri Nov  2 05:31:03 GMT 2007 sutt $
-
-// Fixme: this needs to be tidied up. eg there are too many different, 
-//        and too many version of, accessors for x/y, Q2/tau etc there 
-//        should be only  one set, for x and Q2 *or* y and tau, but 
-//        not both. In fact maybe they should be for x and Q2, since y 
-//        and tau should perhaps be purely an internal grid issue of no 
-//        concern for the user.
-
-
-#ifndef __APPL_IGRID_H
-#define __APPL_IGRID_H
-
-#include <map>
-#include <string>
-#include <vector>
-
-#include "appl_grid/appl_pdf.h"
-#include "appl_grid/SparseMatrix3d.h"
-
-template <typename T>
-class Cache;
-
-using NodeCache = Cache<std::pair<double,double>>;
-
-namespace appl {
-
-class igrid {
-
-private:
-
-  // grid error exception
-  class exception { 
-  public:
-    exception(const std::string& s);
-    exception(std::ostream&);
-  };
-
-  typedef double (igrid::*transform_t)(double) const;
-
-  // structure to store the x<->y transform pairs for 
-  struct transform_vec {
-    transform_vec() : mfx(0), mfy(0) { } 
-    transform_vec( transform_t __fx, transform_t __fy) : mfx(__fx), mfy(__fy) { } 
-    transform_t mfx;
-    transform_t mfy;
-  };
-  
-
-public:
-
-  igrid(int NQ2,   double Q2min=10000.0, double Q2max=25000000.0,  int Q2order=5,  
-	int Nx=50, double xmin=1e-5,     double xmax=0.9,          int xorder=5, 
-	std::string transform="f", int Nproc=6, bool disflag=false);
-
-  igrid(const igrid& g);
-
-  igrid(igrid&& g) = delete;
-  igrid() = delete;
-
[…]

### 2020-03-23 applgridphoton/appl_grid/axis.h

@@ -1,117 +1,0 @@
-
-// emacs: this is -*- c++ -*-
-//
-//   axis.h        
-//
-//                   
-// 
-//   Copyright (C) 2007 M.Sutton (sutt@hep.ucl.ac.uk)    
-//
-//   $Id: axis.h, v   Wed Nov 14 02:13:30 GMT 2007 sutt
-
-
-#ifndef __AXIS_H
-#define __AXIS_H
-
-#include <iostream>
-#include <iomanip>
-#include <vector>
-#include <cmath>
-
-
-
-template<class T> 
-class axis {
-
-public:
-
-  axis() : m_N(0), m_min(0), m_max(0) { }
-
-  axis(int N, T mn, T mx) : m_N(N), m_min(mn), m_max(mx) { 
-    if ( m_N>1 )   m_delta  = (m_max-m_min)/(m_N-1);
-    else           m_delta  = 0;
-    if ( m_delta ) m_idelta = 1/m_delta;
-    else           m_idelta = 0;
-    for ( int i=0 ; i<m_N ; i++ ) {
-      double x2 = 0;
-      if ( m_N>1 ) x2 = ((m_N-1-i)*m_min + i*m_max)/(m_N-1);
-      else         x2 = m_min;
-      m_v.push_back(x2);    
-    }
-  }
-  
-  ~axis() {  }
-  
-  int N()      const { return m_N; } 
-  T   min()    const { return m_min; }
-  T   max()    const { return m_max; }
-  T   delta()  const { return m_delta; }
-  T   idelta() const { return m_idelta; }
-
-  axis(const axis& ax) 
-    : m_N(ax.m_N), m_min(ax.m_min), m_max(ax.m_max), 
-      m_delta(ax.m_delta), m_idelta(ax.m_idelta) { 
-    for ( int i=0 ; i<m_N ; i++ ) m_v.push_back(ax.m_v[i]);    
-  } 
-
-
-  axis& operator=(const axis& ax) { 
-    m_N   = ax.m_N;
-    m_min = ax.m_min;
-    m_max = ax.m_max;
-    
-    m_delta  = ax.m_delta;
-    m_idelta = ax.m_idelta;
-    
-    m_v = ax.m_v;
-
-    return *this;
-  }
-  
-  const std::vector<T>& v() const { return m_v; }  
-  
-  T&       operator()(int i)       { return m_v[i]; }
-  const T& operator()(int i) const { return m_v[i]; }
-  
[…]

### 2020-03-23 applgridphoton/appl_grid/combination.h

@@ -1,118 +1,0 @@
-// emacs: this is -*- c++ -*-
-//
-//   @file    combination.h        
-//
-//                   
-//  
-//   Copyright (C) 2013 M.Sutton (sutt@cern.ch)    
-//
-//   $Id: combination.h, v0.0   Thu  4 Jul 2013 23:20:40 CEST sutt $
-
-
-#ifndef  COMBINATION_H
-#define  COMBINATION_H
-
-#include <iostream>
-
-
-#include <iostream>
-#include <sstream>
-#include <fstream>
-#include <string>
-
-#include <vector>
-#include <utility>
-
-
-
-class combination { 
-
-public:
-
-  typedef std::pair<int,int> cpair;
-
-public:
-
-  /// constructors and destructor
-  combination(const std::vector<int>& v);
-
-  combination(const std::string& line);
-
-  virtual ~combination() {}
-
-  /// evaluate the actual combination
-
-  double evaluate( const double* xfA, const double* xfB,
-		   const std::vector<double>& ckmsum=std::vector<double>(), 
-		   const std::vector<std::vector<double> >& ckm2=std::vector<std::vector<double> >()  ) const;  
-
-  /// number of pairs
-  unsigned size() const { return m_pairs.size(); }  
-
-  /// do any of these remaining need to be public?
-
-  /// index
-  int    index()     const { return m_index; }
-
-  /// accessors to the pairs themselves
-  cpair  pair(int i) const { return m_pairs[i]; }
-
-  const std::vector<cpair>& pairs() const { return m_pairs; }
-
-  cpair&       operator[](int i)       { return m_pairs[i]; } 
-  const cpair& operator[](int i) const { return m_pairs[i]; } 
-
-private:
-
-  /// actually construct combination from the pair list
-  void construct(const std::vector<int>& v);
-
-  /// remap from the pdg to lhapdf code
-  int remap(int i) 
-  {
-    if (i == 21) return 0;
-    else if (i == 22) return 7;
-    else return i;		   
-  } 
-
-private:
-
-  int                m_index;
-  unsigned           m_size;
-  
-  std::vector<cpair> m_pairs;
-
-  static int         gindex;
-  
-};
-
-
-
-
-inline std::ostream& operator<<( std::ostream& s, const combination& _c ) { 
[…]

### 2020-03-23 applgridphoton/appl_grid/tsparse1d.h

@@ -1,192 +1,0 @@
-// emacs: this is -*- c++ -*-
-//
-//   tsparse1d.h        
-//
-//   very basic 2d sparse matrix class, needs to be improved, 
-//   and extended to 3d                   
-// 
-//   Copyright (C) 2007 M.Sutton (sutt@hep.ucl.ac.uk)    
-//
-//   $Id: tsparse1d.h, v1.0   Fri Nov  9 00:17:31 CET 2007 sutt
-
-
-#ifndef __TSPARSE1D_H
-#define __TSPARSE1D_H
-
-#include <iostream>
-
-#include <iomanip>
-
-#include <sstream>
-
-#include <string>
-
-#include "appl_grid/tsparse_base.h"
-
-
-template<class T> 
-class tsparse1d : public tsparse_base {
-
-public: 
-
-  tsparse1d(int nx) : tsparse_base(nx), m_v(NULL) {
-    m_v = new T[m_Nx];
-    for ( int i=0 ; i<Nx() ; i++ ) m_v[i]=0;
-  }
-  
-  tsparse1d(int nx, int lx, int _size=1) 
-    : tsparse_base(nx, lx, _size), m_v(NULL) {
-    if ( _size ) m_v = new T[_size];
-    for ( int i=0 ; i<_size ; i++ ) m_v[i]=0;
-  }
-  
-  ~tsparse1d() { if ( m_v ) delete[] m_v; }
- 
- 
-  T* trim() { 
-    
-    int xmin = m_lx;  int xmax = m_ux;
-    
-    for ( ; xmin<xmax+1 && m_v[xmin-m_lx]==0 ; xmin++ ) { } 
-    for ( ; xmin<xmax   && m_v[xmax-m_lx]==0 ; xmax-- ) { } 
-
-    // don't need to change anything 
-    if ( xmin==m_lx && xmax==m_ux )  return m_v;    
-
-    // it is empty now so delete everything
-    if ( xmax<xmin ) {     
-      m_lx = xmin;
-      m_ux = xmax;      
-      delete[] m_v; 
-      return m_v = NULL; 
-    }
-
-    // create a new, smaller list
-    T* newv = new T[xmax-xmin+1];
-    T* newp = newv;
-    T* mvp  = m_v+xmin-m_lx;
-    for ( int j=xmin ; j<=xmax ; j++ ) (*newp++) = (*mvp++);
-
-    m_lx = xmin; 
-    m_ux = xmax;      
-    
[…]

### 2020-03-23 applgridphoton/src/Cache.h

@@ -1,151 +1,0 @@
-// emacs: this is -*- c++ -*-
-//
-//   @file    Cache.h        
-//            evaluate a pdf function and store values in a cache.
-//            if this x, Q2 node has been requested before then 
-//            retrieve the values and return them if not, generate 
-//            and then add to the cache and then retiurn them
-//
-//            the new LHAPDF (version 6) may implement something 
-//            like this internally, but a retieval from the cache 
-//            is still around 20-40 times faster than LHAPDF 6                   
-//  
-//   Copyright (C) 2013 M.Sutton (sutt@cern.ch)    
-//
-//   $Id: Cache.h, v0.0   Sat 19 Oct 2013 14:12:42 CEST sutt $
-
-
-#pragma  once
-
-#include <iostream>
-#include <map>
-#include <utility>
-
-/// Pass an LHAPDF (version 5) function pointer into the cache, 
-/// then call using the evaluate() method instead of the calling 
-/// the pdf directly. 
-
-template<typename T>
-class Cache : public std::map<T, std::vector<double> > {
- 
-private: 
-
-  /// actual type def of the map for convenience
-  typedef std::map<T,std::vector<double> > _map;
-
-  /// function pointer type
-  typedef void (*pdffunction)(const double& , const double&, double* );
-
-  /// for fast copy 
-  struct partons { double p[14]; };
-
-public:
-
-  /// give it the pdf function to use
-  Cache( pdffunction pdf=0, unsigned mx=20000 ) : _pdf(pdf), _max(mx), _ncalls(0), _ncached(0), _reset(0), _disabled(false), _printstats(false) { } 
-
-  virtual ~Cache() { } 
-
-  
-  /// evaluate the pdf function
-  /// if this node has been requested before, retrieve values 
-  /// from the cache, if not, generate and then add to cache
-  /// for next time 
-  void evaluate( const double& x, const double& Q, double*  xf ) {
-    
-    if ( _pdf==0 ) { 
-      /// should really throw an exception here
-      std::cerr << "whoops, pdf cache has no pdf!!" << std::endl; 
-      return; 
-    }
-
-    _ncalls++;
-
-    /// if we don't want to use the cache for some reason (it can get quite large)     
-    if ( _disabled ) return _pdf( x, Q, xf );
-
-    //    _reset++;
-
[…]

### 2020-03-23 applgridphoton/src/appl_timer.h

@@ -1,55 +1,0 @@
-/**************************************************************************
- **
- **   File:         appl_timer.h  
- **
- **   Description:  small timer wrapper  
- **                   
- **                   
- ** 
- **   Author:       M.Sutton  
- **
- **   Created:      Fri Jun 29 18:59:09 BST 2001
- **   Modified:     
- **                   
- **                   
- **
- **************************************************************************/ 
-
-
-#ifndef __APPL_TIMER
-#define __APPL_TIMER
-
-#include <time.h>
-#include <sys/time.h>
-
-#define APPL_TIMER_START  0
-#define APPL_TIMER_STOP   1
-#define APPL_TIMER_SINCE -1
-
-#ifdef __cplusplus
-// namespace appl { 
-extern "C" {
-#endif
-
-
-double appl_timer(int   );
-void   appl_timer_initkey(void);
-struct timeval appl_timer_start(void);
-double         appl_timer_stop(struct timeval );
-
-#ifdef __cplusplus
-}
-// };
-#endif
-
-#endif /* __APPL_TIMER */
-
-
-
-
-
-
-
-
-
-

### 2020-03-23 applgridphoton/src/applcheck.cpp

@@ -1,155 +1,0 @@
-#include <algorithm>
-#include <array>
-#include <cstddef>
-#include <iostream>
-#include <memory>
-#include <vector>
-
-#include <LHAPDF/LHAPDF.h>
-#include <appl_grid/appl_grid.h>
-
-std::unique_ptr<LHAPDF::PDF> pdf;
-
-enum flavour_map_index : std::size_t
-{
-    anti_top,      // -6: anti-top
-    anti_bottom,   // -5: anti-bottom
-    anti_charm,    // -4: anti-charm
-    anti_strange,  // -3: anti-strange
-    anti_up,       // -2: anti-up
-    anti_down,     // -1: anti-down
-    gluon,         // 21: gluon
-    down,          //  1: down
-    up,            //  2: up
-    strange,       //  3: strange
-    charm,         //  4: charm
-    bottom,        //  5: bottom
-    top,           //  6: top
-    photon,        // 22: photon
-};
-
-std::array<bool, 14> flavour_map = {
-    true,  // -6: anti-top
-    true,  // -5: anti-bottom
-    true,  // -4: anti-charm
-    true,  // -3: anti-strange
-    true,  // -2: anti-up
-    true,  // -1: anti-down
-    true,  // 21: gluon
-    true,  //  1: down
-    true,  //  2: up
-    true,  //  3: strange
-    true,  //  4: charm
-    true,  //  5: bottom
-    true,  //  6: top
-    true,  // 22: photon
-};
-
-constexpr int index_to_pdg_id(std::size_t index)
-{
-    return (index == gluon) ? 21 : ((index == photon) ? 22 : (static_cast <int> (index) - 6));
-}
-
-extern "C" void evolvepdf(double const& x, double const& q, double* xfx)
-{
-    for (std::size_t i = 0; i != flavour_map.size(); ++i)
-    {
-        if (flavour_map.at(i))
-        {
-            xfx[i] = pdf->xfxQ(index_to_pdg_id(i), x, q);
-        }
-        else
-        {
-            xfx[i] = 0.0;
-        }
-    }
-}
-
-extern "C" double alphaspdf(double const& q)
-{
-    return pdf->alphasQ(q);
-}
-
-int main(int argc, char* argv[])
-{
-    // set LHAPDF low verbosity
-    LHAPDF::setVerbosity(0);
-
-    if (argc != 3)
-    {
[…]

### 2020-03-23 applgridphoton/src/histo1d.cpp

@@ -1,48 +1,0 @@
-#include "appl_grid/histo1d.hpp"
-
-#include <TH1D.h>
-
-namespace appl
-{
-
-histo1d::histo1d(void* pointer)
-    : pointer_{pointer}
-{
-}
-
-int histo1d::Fill(double x, double w)
-{
-    return static_cast <TH1D*> (pointer_)->Fill(x, w);
-}
-
-void histo1d::Scale(double c)
-{
-    static_cast <TH1D*> (pointer_)->Scale(c);
-}
-
-double histo1d::GetBinContent(int bin) const
-{
-    return static_cast <TH1D*> (pointer_)->GetBinContent(bin);
-}
-
-void histo1d::SetBinContent(int bin, double content)
-{
-    static_cast <TH1D*> (pointer_)->SetBinContent(bin, content);
-}
-
-int histo1d::GetNbinsX() const
-{
-    return static_cast <TH1D*> (pointer_)->GetNbinsX();
-}
-
-double histo1d::GetBinWidth(int bin) const
-{
-    return static_cast <TH1D*> (pointer_)->GetBinWidth(bin);
-}
-
-void* histo1d::pointer() const
-{
-    return pointer_;
-}
-
-}

### 2020-03-23 applgridphoton/src/merge_bins.cpp

@@ -1,30 +1,0 @@
-#include <appl_grid/appl_grid.h>
-
-#include <fstream>
-#include <iostream>
-#include <string>
-#include <utility>
-#include <vector>
-
-int main(int argc, char* argv[])
-{
-    if (argc < 3)
-    {
-        std::cerr << "Usage: merge_bins outgrid grid1 [grid2 ...]\n";
-
-        return 1;
-    }
-
-    std::vector<std::string> args(&argv[2], &argv[argc]);
-
-    std::vector<appl::grid> grids;
-    grids.reserve(args.size());
-
-    for (auto const& arg : args)
-    {
-        grids.emplace_back(arg);
-    }
-
-    appl::grid result(std::move(grids));
-    result.Write(argv[1]);
-}

### 2020-03-23 applgridphoton/src/sparse_matrix3d_root_interface.cpp

@@ -1,85 +1,0 @@
-#include "sparse_matrix3d_root_interface.hpp"
-
-#include "appl_grid/tsparse2d.h"
-#include "appl_grid/tsparse1d.h"
-
-#include <TH1D.h>
-
-SparseMatrix3d* sparse_matrix3d_from_th3d(TH3D const& histogram)
-{
-    // TODO: are the following casts neccessary?
-    TH1D* hx = (TH1D*)(&histogram)->Project3D("x");
-    TH1D* hy = (TH1D*)(&histogram)->Project3D("y");
-    TH1D* hz = (TH1D*)(&histogram)->Project3D("z");
-
-    auto* matrix = new SparseMatrix3d(
-        hx->GetNbinsX(), hx->GetBinCenter(1), hx->GetBinCenter(hx->GetNbinsX()),
-        hy->GetNbinsX(), hy->GetBinCenter(1), hy->GetBinCenter(hy->GetNbinsX()),
-        hz->GetNbinsX(), hz->GetBinCenter(1), hz->GetBinCenter(hz->GetNbinsX())
-    );
-
-    delete hx;
-    delete hy;
-    delete hz;
-
-    for (int i = 0; i < matrix->xaxis().N(); ++i)
-    {
-        for (int j = 0; j < matrix->yaxis().N(); ++j)
-        {
-            for (int k = 0; k < matrix->zaxis().N(); ++k)
-            {
-                (*matrix)(i,j,k) = histogram.GetBinContent(i + 1, j + 1, k + 1);
-            }
-        }
-    }
-
-    return matrix;
-}
-
-TH3D* sparse_matrix3d_to_th3d(SparseMatrix3d const& matrix, std::string const& s)
-{
-    double const delx = matrix.xaxis().delta();
-    double const dely = matrix.yaxis().delta();
-    double const delz = matrix.zaxis().delta();
-
-    TH3D* h = new TH3D(
-        s.c_str(),
-        s.c_str(),
-        matrix.xaxis().N(),
-        matrix.xaxis().min()-0.5*delx,
-        matrix.xaxis().max()+0.5*delx,
-        matrix.yaxis().N(),
-        matrix.yaxis().min()-0.5*dely,
-        matrix.yaxis().max()+0.5*dely,
-        matrix.zaxis().N(),
-        matrix.zaxis().min()-0.5*delz,
-        matrix.zaxis().max()+0.5*delz
-    );
-
-    for (int i = matrix.lo(); i <= matrix.hi(); ++i)
-    {
[…]

### 2020-03-23 applgridphoton/src/sparse_matrix3d_root_interface.hpp

@@ -1,12 +1,0 @@
-#ifndef SPARSE_MATRIX_3D_ROOT_INTERFACE_HPP
-#define SPARSE_MATRIX_3D_ROOT_INTERFACE_HPP
-
-#include "appl_grid/SparseMatrix3d.h"
-
-#include <TH3D.h>
-
-SparseMatrix3d* sparse_matrix3d_from_th3d(TH3D const& histogram);
-
-TH3D* sparse_matrix3d_to_th3d(SparseMatrix3d const& matrix, std::string const& s);
-
-#endif

### 2020-03-23 nnpdf31_proc/ATLASTOPDIFF8TEVTRAPNORM/analysis.f

@@ -1,67 +1,0 @@
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-      subroutine analysis_begin(nwgt,weights_info)
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-
-      implicit none
-      integer nwgt
-      character*(*) weights_info(*)
-
-      call HwU_inithist(nwgt,weights_info)
-      call HwU_book(1,'t rap ', 4,0.0d0,1.6d0)
-      call HwU_book(2,'t rap ', 1,1.6d0,2.5d0)
-      return
-      end
-
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-      subroutine analysis_end(dummy)
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-
-      implicit none
-      double precision dummy
-      call HwU_write_file
-      return                
-      end
-
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-      subroutine analysis_fill(p,istatus,ipdg,wgts,ibody)
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-
-      implicit none
-      include 'nexternal.inc'
-      integer istatus(nexternal)
-      integer iPDG(nexternal)
-      integer ibody
-      integer i
-      double precision p(0:4,nexternal)
-      double precision wgts(*)
-      double precision yt, getrapidity
-      external getrapidity
- 
-      yt  = getrapidity(p(0,3), p(3,3))
-
-      call HwU_fill(1,yt,wgts)
-      call HwU_fill(2,yt,wgts)
-
- 999  return      
-      end
-
-ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-
-      function getrapidity(en,pl)
-      implicit none
-      real*8 getrapidity,en,pl,tiny,xplus,xminus,y
-      parameter (tiny=1.d-8)
-      xplus=en+pl
-      xminus=en-pl
-      if(xplus.gt.tiny.and.xminus.gt.tiny)then
-         if( (xplus/xminus).gt.tiny.and.(xminus/xplus).gt.tiny)then
-            y=0.5d0*log( xplus/xminus  )
-         else
-            y=sign(1.d0,pl)*1.d8
-         endif
-      else 
[…]

### 2020-03-23 nnpdf31_proc/ATLASZHIGHMASS49FB/analysis.f

@@ -1,95 +1,0 @@
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-      subroutine analysis_begin(nwgt,weights_info)
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-
-      implicit none
-      integer nwgt
-      character*(*) weights_info(*)
-
-      call HwU_inithist(nwgt,weights_info)
-      call HwU_book(1,'lmlp inv m', 1,  116d0,  130d0)
-      call HwU_book(2,'lmlp inv m', 6,  130d0,  250d0)
-      call HwU_book(3,'lmlp inv m', 1,  250d0,  300d0)
-      call HwU_book(4,'lmlp inv m', 2,  300d0,  500d0)
-      call HwU_book(5,'lmlp inv m', 1,  500d0,  700d0)
-      call HwU_book(6,'lmlp inv m', 1,  700d0, 1000d0)
-      call HwU_book(7,'lmlp inv m', 1, 1000d0, 1500d0)
-      return
-      end
-
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-      subroutine analysis_end(dummy)
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-
-      implicit none
-      double precision dummy
-      call HwU_write_file
-      return                
-      end
-
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-      subroutine analysis_fill(p,istatus,ipdg,wgts,ibody)
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-
-      implicit none
-      include 'nexternal.inc'
-      include 'cuts.inc'
-      integer istatus(nexternal)
-      integer iPDG(nexternal)
-      integer ibody  
-      integer i
-      integer j
-      double precision p(0:4,nexternal)
-      double precision wgts(*)
-      double precision ppl(0:3), pplb(0:3), ppv(0:3), xmll, getinvm
-      external getinvm
-
-      double precision p_reco(0:4,nexternal)
-      integer iPDG_reco(nexternal)
-
-
-
-      call recombine_momenta(rphreco, etaphreco, lepphreco, quarkphreco,
[…]

### 2020-03-23 nnpdf31_proc/CMSTOPDIFF8TEVTTRAPNORM/analysis.f

@@ -1,73 +1,0 @@
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-      subroutine analysis_begin(nwgt,weights_info)
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-
-      implicit none
-      integer nwgt
-      character*(*) weights_info(*)
-
-      call HwU_inithist(nwgt,weights_info)
-      call HwU_book(1,'t-tx pair rap ', 3,0.0d0,0.9d0)
-      call HwU_book(2,'t-tx pair rap ', 1,0.9d0,1.3d0)
-      call HwU_book(3,'t-tx pair rap ', 1,1.3d0,2.5d0)
-      return
-      end
-
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-      subroutine analysis_end(dummy)
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-
-      implicit none
-      double precision dummy
-      call HwU_write_file
-      return                
-      end
-
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-      subroutine analysis_fill(p,istatus,ipdg,wgts,ibody)
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-
-      implicit none
-      include 'nexternal.inc'
-      integer istatus(nexternal)
-      integer iPDG(nexternal)
-      integer ibody  
-      integer i
-      double precision p(0:4,nexternal)
-      double precision wgts(*)
-      double precision pttx(0:3), yttx, getrapidity
-      external getrapidity
-
-      do i=0,3
-        pttx(i)=p(i,3)+p(i,4)
-      enddo
-
-      yttx= getrapidity(pttx(0), pttx(3))
-
-      call HwU_fill(1,yttx,wgts)
-      call HwU_fill(2,yttx,wgts)
-      call HwU_fill(3,yttx,wgts)
-
- 999  return      
-      end
-
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-
-      function getrapidity(en,pl)
-      implicit none
-      real*8 getrapidity,en,pl,tiny,xplus,xminus,y
-      parameter (tiny=1.d-8)
-      xplus=en+pl
-      xminus=en-pl
[…]

### 2020-03-23 nnpdf31_proc/CMSTTBARTOT8TEV/analysis.f

@@ -1,40 +1,0 @@
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-      subroutine analysis_begin(nwgt,weights_info)
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-
-      implicit none
-      integer nwgt
-      character*(*) weights_info(*)
-
-      call HwU_inithist(nwgt,weights_info)
-      call HwU_book(1,'total rate      ', 1,0.5d0,1.5d0)
-      return
-      end
-
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-      subroutine analysis_end(dummy)
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-
-      implicit none
-      double precision dummy
-      call HwU_write_file
-      return                
-      end
-
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-      subroutine analysis_fill(p,istatus,ipdg,wgts,ibody)
-cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-
-      implicit none
-      include 'nexternal.inc'
-      integer istatus(nexternal)
-      integer iPDG(nexternal)
-      double precision p(0:4,nexternal)
-      double precision wgts(*)
-      integer ibody
-      double precision var
-
-      var=1d0
-      call HwU_fill(1,var,wgts)
-      return
-      end

### 2020-03-23 run.sh

@@ -1,132 +1,0 @@
-#!/bin/bash
-
-# exit script at the first sign of an error
-set -o errexit
-
-# the following exits if undeclared variables are used
-set -o nounset
-
-# exit if some program in a pipeline fails
-set -o pipefail
-
-# check arguments of the script
-if (( $# != 1 )); then
-    echo "Usage: ./run.sh [dataset]" >&2
-    echo "  The following datasets are available:" >&2
-
-    for i in $(ls -d nnpdf31_proc/*); do
-        echo "  - ${i##*/}" >&2
-    done
-
-    exit 1
-fi
-
-# name of the dataset
-dataset="$1"
-
-mg5amc=$(which mg5_aMC 2> /dev/null || true)
-
-if [[ ! -x ${mg5amc} ]]; then
-    echo "The binary \`mg5_aMC\` wasn't found. Please adjust your PATH variable" >&2
-    exit 1
-fi
-
-applcheck=$(which applcheck 2> /dev/null || true)
-
-if [[ ! -x ${applcheck} ]]; then
-    echo "The binary \`applcheck\` wasn't found. Please adjust your PATH variable" >&2
-    exit 1
-fi
-
-merge_bins=$(which merge_bins 2> /dev/null || true)
-
-if [[ ! -x ${merge_bins} ]]; then
-    echo "The binary \`merge_bins\` wasn't found. Please adjust your PATH variable" >&2
-    exit 1
-fi
-
-# name of the directory where the output is written to
-output="${dataset}"-$(date +%Y%m%d%H%M%S)
-
-if [[ -d $output ]]; then
-    # since we add a date postfix to the name this shouldn't happen
-    echo "Error: output directory already exists" >&2
-    exit 1
-fi
-
-# create and change into output directory
-mkdir "${output}"
-cd "${output}"
-
-# copy the output file to the directory and replace the variables
-output_file=output.txt
-cp ../nnpdf31_proc/"${dataset}"/output.txt "${output_file}"
-sed -i "s/@OUTPUT@/${dataset}/g" "${output_file}"
-
-# create output folder
-python2 "${mg5amc}" "${output_file}" |& tee output.log
-
-# copy patches if there are any
-for i in $(find ../nnpdf31_proc/"${dataset}" -name '*.patch'); do
-    patch -p1 -d "${dataset}" < $i
-done
-
-# enforce proper analysis
[…]

### 2020-03-23 applgriddiff/include/applgriddiff.hpp
Revert "some edits in paper"
This reverts commit 1325752a4a49f15ce2acfeceb8090e1c2eec6b8b.

@@ -1,0 +1,18 @@
+#ifndef APPLGRIDDIFF_HPP
+#define APPLGRIDDIFF_HPP
+
+#include <TDirectory.h>
+#include <TH1.h>
+#include <TObject.h>
+#include <TVectorT.h>
+
+bool diff_directory(TDirectory& dir1, TDirectory& dir2);
+
+bool diff_histogram(TH1 const& obj1, TH1 const& obj2);
+
+template <typename T>
+bool diff_vector_t(TVectorT<T> const& obj1, TVectorT<T> const& obj2);
+
+bool dispatch_and_diff(TObject& obj1, TObject& obj2);
+
+#endif

### 2020-03-23 applgriddiff/src/diffs.cpp

@@ -1,0 +1,282 @@
+#include "applgriddiff.hpp"
+
+#include <algorithm>
+#include <cstddef>
+#include <iostream>
+#include <string>
+#include <vector>
+
+#include <TH3.h>
+#include <TKey.h>
+
+bool diff_directory(TDirectory& dir1, TDirectory& dir2)
+{
+    auto dir1_keys = dir1.GetListOfKeys();
+    auto dir2_keys = dir2.GetListOfKeys();
+
+    std::vector<std::string> dir1_names;
+    std::vector<std::string> dir2_names;
+
+    for (auto const& key : *dir1_keys)
+    {
+        dir1_names.emplace_back(key->GetName());
+    }
+
+    for (auto const& key : *dir2_keys)
+    {
+        dir2_names.emplace_back(key->GetName());
+    }
+
+    if (dir1_names.size() != dir2_names.size())
+    {
+        std::cout << ">>> files have different structures\n";
+        return true;
+    }
+
+    std::sort(dir1_names.begin(), dir1_names.end());
+    std::sort(dir2_names.begin(), dir2_names.end());
+
+    if (!std::equal(dir1_names.begin(), dir1_names.end(), dir2_names.begin()))
+    {
+        std::cout << ">>> files have different structures\n";
+        return true;
+    }
+
+    bool diff = false;
+
+    for (auto const& name : dir1_names)
+    {
+        auto* cls1 = dir1.FindKey(name.c_str())->GetClassName();
+        auto* cls2 = dir1.FindKey(name.c_str())->GetClassName();
+
+        if ((cls1 != std::string("TFileString")) && (cls2 != std::string("TFileString")))
+        {
+            auto* obj1 = dir1.Get(name.c_str());
+            auto* obj2 = dir2.Get(name.c_str());
+
+            if ((obj1 == nullptr) && (obj2 == nullptr))
+            {
+                std::cout << "???\n";
+                continue;
+            }
+
+            diff &= dispatch_and_diff(*obj1, *obj2);
+        }
+        else
+        {
+            std::cout << ">>> ignoring unknown TFileString objects\n";
+        }
+    }
+
+    return diff;
+}
+
+bool diff_histogram(TH1 const& obj1, TH1 const& obj2)
+{
+    if (obj1.GetNbinsX() != obj2.GetNbinsX())
+    {
+        std::cout << ">>> files have different structures\n";
+
+        return true;
+    }
+    else if (obj1.GetNbinsY() != obj2.GetNbinsY())
+    {
[…]

### 2020-03-23 applgridphoton/appl_grid/SparseMatrix3d.h

@@ -1,0 +1,120 @@
+// emacs: this is -*- c++ -*-
+//
+//   SparseMatrix3d.h        
+//
+//                   
+// 
+//   Copyright (C) 2007 M.Sutton (sutt@hep.ucl.ac.uk)    
+//
+//   $Id: SparseMatrix3d.h, v1.0   Wed Nov 14 14:23:49 GMT 2007 sutt
+
+
+#ifndef __SPARSEMATRIX3D_H
+#define __SPARSEMATRIX3D_H
+
+#include <iostream>
+
+#include "axis.h"
+#include "tsparse3d.h"
+
+class SparseMatrix3d : public tsparse3d<double> {
+
+public:
+
+  // constructors and destructor
+
+  SparseMatrix3d( int Nx, double lx, double ux, 
+		  int Ny, double ly, double uy, 
+		  int Nz, double lz, double uz);
+
+  SparseMatrix3d(const SparseMatrix3d& s); 
+
+  ~SparseMatrix3d() { empty_fast(); } 
+
+  // axis accessors
+  const axis<double>& xaxis() const { return m_xaxis; } 
+  const axis<double>& yaxis() const { return m_yaxis; } 
+  const axis<double>& zaxis() const { return m_zaxis; } 
+
+
+  // trim to sparse structure 
+  void trim() { empty_fast(); tsparse3d<double>::trim(); }
+    
+  // access using the fast (dangerous) methods
+  double& fill_fast(int i, int j, int k);
+  double  fill_fast(int i, int j, int k) const;
+
+  void fill(double x, double y, double z, double w);
+  
+  /// check if the axes are all the same
+  bool compare_axes(const SparseMatrix3d& s) const { 
+
+#if 0
+
+    std::cout << "SparseMatrix: " 
+	      << "\tx " << m_xaxis 
+	      << "\ty " << m_yaxis 
+	      << "\tz " << m_zaxis << std::endl; 
+
+    std::cout << "SparseMatrix: " 
+	      << "\tx " << s.m_xaxis 
+	      << "\ty " << s.m_yaxis 
+	      << "\tz " << s.m_zaxis << std::endl; 
+
+    std::cout << "SparseMatrix: " 
+	      << "\tx " << ( m_xaxis == s.m_xaxis ) 
+	      << "\ty " << ( m_yaxis == s.m_yaxis )
[…]

### 2020-03-23 applgridphoton/appl_grid/appl_grid.h

@@ -1,0 +1,279 @@
+// emacs: this is -*- c++ -*-
+
+//  appl_grid.h       
+
+//  grid class header - all the functions needed to create and 
+//  fill the grid from an NLO calculation program
+//  
+//  Copyright (C) 2007 Mark Sutton (sutt@hep.ucl.ac.uk)    
+
+// $Id: appl_grid.h, v1.00 2007/10/16 17:01:39 sutt
+
+// Fixme: this needs to be tidied up. eg there are too many different, 
+//        and too many version of, accessors for x/y, Q2/tau etc there 
+//        should be only  one set, for x and Q2 *or* y and tau, but 
+//        not both. In fact they should be for x and Q2, since y and tau 
+//        should be purely an internal grid issue of no concern for the 
+//        user.
+
+#ifndef __APPL_PHOTON
+#define __APPL_PHOTON
+#endif
+
+#ifndef __APPL_GRID_H
+#define __APPL_GRID_H
+
+#include "histo1d.hpp"
+
+#include <exception>
+#include <iosfwd>
+#include <string>
+#include <vector>
+
+namespace appl { 
+
+
+/// forward declarations - full definitions included 
+/// from appl_grid.cxx 
+class igrid;
+class appl_pdf;
+
+class order_id
+{
+public:
+    order_id(int alphs, int alpha, int lmuf2, int lmur2)
+        : alphs_{alphs}
+        , alpha_{alpha}
+        , lmuf2_{lmuf2}
+        , lmur2_{lmur2}
+    {
+    }
+
+    int alphs() const
+    {
+        return alphs_;
+    }
+
+    int alpha() const
+    {
+        return alpha_;
+    }
+
+    int lmuf2() const
+    {
+        return lmuf2_;
+    }
+
+    int lmur2() const
+    {
+        return lmur2_;
+    }
+
+private:
+    int alphs_;
+    int alpha_;
+    int lmuf2_;
+    int lmur2_;
+};
+
+inline bool operator==(order_id const& a, order_id const& b)
+{
+    return (a.alphs() == b.alphs()) && (a.alpha() == b.alpha()) && (a.lmuf2() == b.lmuf2())
+        && (a.lmur2() == b.lmur2());
+}
+
+/// externally visible grid class
+class grid {
+
+public:
+
+  // grid error exception
+  class exception : public std::exception { 
+  public:
+    exception(const std::string& s);
+    exception(std::ostream&);
[…]

### 2020-03-23 applgridphoton/appl_grid/appl_igrid.h

@@ -1,0 +1,336 @@
+// emacs: this is -*- c++ -*-
+//
+//   appl_igrid.h        
+//
+//  grid class header - all the functions needed to create and 
+//  fill the grid from an NLO calculation program, based on the 
+//  class from D.Clements and T.Carli.
+//
+//  See contribution from T.Carli et al from the HERA-LHC 
+//  workshop - working group 3 
+//  
+//  Copyright (C) 2007 Mark Sutton (sutt@hep.ucl.ac.uk)    
+//
+//   $Id: appl_igrid.h, v2.00  Fri Nov  2 05:31:03 GMT 2007 sutt $
+
+// Fixme: this needs to be tidied up. eg there are too many different, 
+//        and too many version of, accessors for x/y, Q2/tau etc there 
+//        should be only  one set, for x and Q2 *or* y and tau, but 
+//        not both. In fact maybe they should be for x and Q2, since y 
+//        and tau should perhaps be purely an internal grid issue of no 
+//        concern for the user.
+
+
+#ifndef __APPL_IGRID_H
+#define __APPL_IGRID_H
+
+#include <map>
+#include <string>
+#include <vector>
+
+#include "appl_grid/appl_pdf.h"
+#include "appl_grid/SparseMatrix3d.h"
+
+template <typename T>
+class Cache;
+
+using NodeCache = Cache<std::pair<double,double>>;
+
+namespace appl {
+
+class igrid {
+
+private:
+
+  // grid error exception
+  class exception { 
+  public:
+    exception(const std::string& s);
+    exception(std::ostream&);
+  };
+
+  typedef double (igrid::*transform_t)(double) const;
+
+  // structure to store the x<->y transform pairs for 
+  struct transform_vec {
+    transform_vec() : mfx(0), mfy(0) { } 
+    transform_vec( transform_t __fx, transform_t __fy) : mfx(__fx), mfy(__fy) { } 
+    transform_t mfx;
+    transform_t mfy;
+  };
+  
+
+public:
+
+  igrid(int NQ2,   double Q2min=10000.0, double Q2max=25000000.0,  int Q2order=5,  
+	int Nx=50, double xmin=1e-5,     double xmax=0.9,          int xorder=5, 
+	std::string transform="f", int Nproc=6, bool disflag=false);
+
+  igrid(const igrid& g);
+
+  igrid(igrid&& g) = delete;
+  igrid() = delete;
+
[…]

### 2020-03-23 applgridphoton/appl_grid/appl_pdf.h

@@ -1,0 +1,189 @@
+// emacs: this is -*- c++ -*-
+//
+//   appl_pdf.h        
+//
+//   pdf transform functions header                  
+// 
+//   Copyright (C) 2007 M.Sutton (sutt@hep.ucl.ac.uk)    
+//
+//   $Id: appl_pdf.h, v   Fri Dec 21 22:19:50 GMT 2007 sutt $
+
+
+#ifndef __APPL_PDF_H
+#define __APPL_PDF_H
+
+#include <iostream>
+#include <fstream>
+#include <sstream>
+
+#include <exception>
+#include <vector> 
+#include <map> 
+#include <string> 
+
+#include <exception> 
+
+
+namespace appl { 
+
+
+class appl_pdf;
+
+typedef std::map<const std::string, appl_pdf*> pdfmap;
+
+
+// this is a *maybe* nice class, a base class for pdf 
+// functions
+//
+// it has a virtual evaluate() method to be definied in 
+// the derived class, and a static std::map of all the names
+// of instances of the derived classes
+//
+// when a new instance of the class is created, it 
+// automatically adds it's name to the std::map, so the user 
+// doesn't need to worry about consistency, and removes 
+// itself when the derived instance is deleted
+
+class appl_pdf { 
+
+public:
+
+  // pdf error exception
+  class exception : public std::exception { 
+  public: 
+    exception(const std::string& s="");
+    exception(std::ostream&);
+    const char* what() const noexcept;
+  };
+  
+public:
+
+  /// constructor and destructor
+  appl_pdf(const std::string& name);
+
+  virtual ~appl_pdf();
+
+  /// retrieve an instance from the std::map 
+  static appl_pdf* getpdf(const std::string& s, bool printout=true);
+  
+  /// initialise the factory  
+  static bool create_map(); 
+
+  virtual void evaluate(const double* fA, const double* fB, double* H) = 0; 
+
+  virtual int decideSubProcess( const int , const int  ) const;
+
+  std::string   name() const { return m_name;  }
+
+  int     Nproc() const { return m_Nproc; } 
+  int     size()  const { return m_Nproc; } 
+
+
+
+  std::string  rename(const std::string& name) { 
+    /// remove my entry from the std::map, and add me again with my new name
+    if ( __pdfmap.find(m_name)!=__pdfmap.end() ) { 
+      __pdfmap.erase(__pdfmap.find(m_name));
+    }
+    else { 
[…]

### 2020-03-23 applgridphoton/appl_grid/axis.h

@@ -1,0 +1,117 @@
+
+// emacs: this is -*- c++ -*-
+//
+//   axis.h        
+//
+//                   
+// 
+//   Copyright (C) 2007 M.Sutton (sutt@hep.ucl.ac.uk)    
+//
+//   $Id: axis.h, v   Wed Nov 14 02:13:30 GMT 2007 sutt
+
+
+#ifndef __AXIS_H
+#define __AXIS_H
+
+#include <iostream>
+#include <iomanip>
+#include <vector>
+#include <cmath>
+
+
+
+template<class T> 
+class axis {
+
+public:
+
+  axis() : m_N(0), m_min(0), m_max(0) { }
+
+  axis(int N, T mn, T mx) : m_N(N), m_min(mn), m_max(mx) { 
+    if ( m_N>1 )   m_delta  = (m_max-m_min)/(m_N-1);
+    else           m_delta  = 0;
+    if ( m_delta ) m_idelta = 1/m_delta;
+    else           m_idelta = 0;
+    for ( int i=0 ; i<m_N ; i++ ) {
+      double x2 = 0;
+      if ( m_N>1 ) x2 = ((m_N-1-i)*m_min + i*m_max)/(m_N-1);
+      else         x2 = m_min;
+      m_v.push_back(x2);    
+    }
+  }
+  
+  ~axis() {  }
+  
+  int N()      const { return m_N; } 
+  T   min()    const { return m_min; }
+  T   max()    const { return m_max; }
+  T   delta()  const { return m_delta; }
+  T   idelta() const { return m_idelta; }
+
+  axis(const axis& ax) 
+    : m_N(ax.m_N), m_min(ax.m_min), m_max(ax.m_max), 
+      m_delta(ax.m_delta), m_idelta(ax.m_idelta) { 
+    for ( int i=0 ; i<m_N ; i++ ) m_v.push_back(ax.m_v[i]);    
+  } 
+
+
+  axis& operator=(const axis& ax) { 
+    m_N   = ax.m_N;
+    m_min = ax.m_min;
+    m_max = ax.m_max;
+    
+    m_delta  = ax.m_delta;
+    m_idelta = ax.m_idelta;
+    
+    m_v = ax.m_v;
+
+    return *this;
+  }
+  
+  const std::vector<T>& v() const { return m_v; }  
+  
+  T&       operator()(int i)       { return m_v[i]; }
+  const T& operator()(int i) const { return m_v[i]; }
+  
[…]

### 2020-03-23 applgridphoton/appl_grid/histo1d.hpp

@@ -1,0 +1,29 @@
+#ifndef APPL_GRID_HISTO1D_HPP
+#define APPL_GRID_HISTO1D_HPP
+
+//#include <cstddef>
+
+namespace appl
+{
+
+class histo1d
+{
+public:
+    histo1d(void* pointer);
+
+    int Fill(double x, double w);
+    void Scale(double c);
+    double GetBinContent(int bin) const;
+    void SetBinContent(int bin, double content);
+    int GetNbinsX() const;
+    double GetBinWidth(int bin) const;
+
+    void* pointer() const;
+
+private:
+    void* pointer_;
+};
+
+}
+
+#endif

### 2020-03-23 applgridphoton/appl_grid/lumi_pdf.h

@@ -1,0 +1,108 @@
+// emacs: this is -*- c++ -*-
+//
+//   @file    lumi_pdf.h        
+//
+//            a lumi pdf type - to read in the combinations
+//            for the subprocesses from a file
+//
+//            the file format is as from madgraph nproc rows ...
+//
+//              index  npairs   p1 p2   p3 p4   p5 p6 ...  
+//              index  npairs   ...
+//              ...
+//
+//            where  npairs is the number of parton-parton pairs
+//            in this subprocess
+//
+//  
+//   Copyright (C) 2013 M.Sutton (sutt@cern.ch)    
+//
+//   $Id: lumi_pdf.h, v0.0   Mon 28 Jan 2013 15:41:10 GMT sutt $
+
+
+#ifndef  LUMI_PDF_H
+#define  LUMI_PDF_H
+
+#include <iostream>
+
+#include "appl_grid/appl_pdf.h" 
+#include "appl_grid/combination.h"
+
+
+class lumi_pdf : public appl::appl_pdf {
+
+public:
+
+  lumi_pdf(const std::string& s="", const std::vector<int>& combinations=std::vector<int>() );   // , int Wcharge=0 );
+
+  lumi_pdf(const std::string& s, const std::vector<combination>& combinations, int ckmcharge=0 );             // , int Wcharge=0 );
+
+  virtual ~lumi_pdf() {   } 
+
+  void evaluate(const double* _fA, const double* _fB, double* H);
+
+  /// additional user defined functions to actually initialise 
+  /// based on the input file
+
+  /// how many combinations of subprocesses are there ?
+  unsigned size() const { return m_combinations.size(); }
+ 
+  //  void initialise(const std::string& filename);
+
+  //  bool initialised() const { return m_initialised; }
+
+  const combination& operator[](int i) const { return m_combinations.at(i); }  
+
+  int  decideSubProcess(const int iflav1, const int iflav2) const ;
+
+  std::vector<int> serialise() const;
+
+  void write(const std::string& filename) const;
+ 
+  void write(std::ostream& s=std::cout) const; 
+
+  //  std::string summary(std::ostream& s=std::cout) const; 
+  std::string summary() const; 
+  
+private:
+
+  /// add a combination
+  void add(const combination& c) {  m_combinations.push_back(c); }
+
+  void create_lookup();
+
+private:
+
[…]

### 2020-03-23 applgridphoton/appl_grid/tsparse1d.h

@@ -1,0 +1,192 @@
+// emacs: this is -*- c++ -*-
+//
+//   tsparse1d.h        
+//
+//   very basic 2d sparse matrix class, needs to be improved, 
+//   and extended to 3d                   
+// 
+//   Copyright (C) 2007 M.Sutton (sutt@hep.ucl.ac.uk)    
+//
+//   $Id: tsparse1d.h, v1.0   Fri Nov  9 00:17:31 CET 2007 sutt
+
+
+#ifndef __TSPARSE1D_H
+#define __TSPARSE1D_H
+
+#include <iostream>
+
+#include <iomanip>
+
+#include <sstream>
+
+#include <string>
+
+#include "appl_grid/tsparse_base.h"
+
+
+template<class T> 
+class tsparse1d : public tsparse_base {
+
+public: 
+
+  tsparse1d(int nx) : tsparse_base(nx), m_v(NULL) {
+    m_v = new T[m_Nx];
+    for ( int i=0 ; i<Nx() ; i++ ) m_v[i]=0;
+  }
+  
+  tsparse1d(int nx, int lx, int _size=1) 
+    : tsparse_base(nx, lx, _size), m_v(NULL) {
+    if ( _size ) m_v = new T[_size];
+    for ( int i=0 ; i<_size ; i++ ) m_v[i]=0;
+  }
+  
+  ~tsparse1d() { if ( m_v ) delete[] m_v; }
+ 
+ 
+  T* trim() { 
+    
+    int xmin = m_lx;  int xmax = m_ux;
+    
+    for ( ; xmin<xmax+1 && m_v[xmin-m_lx]==0 ; xmin++ ) { } 
+    for ( ; xmin<xmax   && m_v[xmax-m_lx]==0 ; xmax-- ) { } 
+
+    // don't need to change anything 
+    if ( xmin==m_lx && xmax==m_ux )  return m_v;    
+
+    // it is empty now so delete everything
+    if ( xmax<xmin ) {     
+      m_lx = xmin;
+      m_ux = xmax;      
+      delete[] m_v; 
+      return m_v = NULL; 
+    }
+
+    // create a new, smaller list
+    T* newv = new T[xmax-xmin+1];
+    T* newp = newv;
+    T* mvp  = m_v+xmin-m_lx;
+    for ( int j=xmin ; j<=xmax ; j++ ) (*newp++) = (*mvp++);
+
+    m_lx = xmin; 
+    m_ux = xmax;      
+    
[…]

### 2020-03-23 applgridphoton/appl_grid/tsparse2d.h

@@ -1,0 +1,348 @@
+// emacs: this is -*- c++ -*-
+//
+//   tsparse2d.h        
+//
+//   very basic 2d sparse matrix class, needs to be improved, 
+//   and extended to 3d.
+//
+//   NB: be VERY CAREFUL about the use of the (i,j) index operator, 
+//       since it checks to see whether the given element exists,
+//       and if not, it creates it, so even viewing it such as...
+//
+//          tsparse2d<...> d(10,10); std::cout << a(2,3) << std::endl;                    
+//
+//       will create the element if it doesn't exist *unless* you 
+//       are looking at a const tsparse2d<...>
+// 
+//   Copyright (C) 2007 M.Sutton (sutt@hep.ucl.ac.uk)    
+//
+//   $Id: tsparse2d.h, v1.0   Fri Nov  9 00:17:31 CET 2007 sutt
+
+
+#ifndef __TSPARSE2D_H
+#define __TSPARSE2D_H
+
+#include <iostream>
+
+#include <iomanip>
+
+#include <cmath>
+
+
+
+#include "tsparse1d.h"
+
+
+template<class T> 
+class tsparse2d : public tsparse_base {
+
+#if 0
+public:
+
+  class exception { 
+  public:
+    exception(const std::string& s) { cerr << s << std::endl; }; 
+    exception(ostream&) { cerr << s << std::endl; };
+  };
+#endif
+
+public:
+
+  tsparse2d(int nx, int ny) : tsparse_base(nx), m_Ny(ny), m_v(NULL) {  
+    m_v = new tsparse1d<T>*[m_Nx];
+    for ( int i=0 ; i<Nx() ; i++ ) m_v[i] = new tsparse1d<T>(m_Ny);
+  }
+
+  tsparse2d(int nx, int ny, int lx, int ly, int _size=1, int _sizey=1) : tsparse_base(nx, lx, _size), m_Ny(ny), m_v(NULL) {  
+    if ( _size ) m_v = new tsparse1d<T>*[_size];
+    for ( int i=0 ; i<_size ; i++ ) m_v[i] = new tsparse1d<T>(m_Ny,ly, _sizey);
+  }
+
+
+  
+  ~tsparse2d() { 
+    if ( m_v ) { 
[…]

### 2020-03-23 applgridphoton/appl_grid/tsparse3d.h

@@ -1,0 +1,109 @@
+// emacs: this is -*- c++ -*-
+//
+//   tsparse3d.h        
+//
+//   very basic 3d sparse matrix class, needs to be improved, 
+//   and extended to 3d                   
+// 
+//   Copyright (C) 2007 M.Sutton (sutt@hep.ucl.ac.uk)    
+//
+//   $Id: tsparse3d.h, v   Fri Nov  9 00:17:31 CET 2007 sutt
+
+
+#ifndef __TSPARSE3D_H
+#define __TSPARSE3D_H
+
+#include <iostream>
+
+#include "tsparse2d.h"
+
+
+template<class T> 
+class tsparse3d : public tsparse_base {
+
+public:
+
+  tsparse3d(int nx, int ny, int nz);
+
+  tsparse3d(const tsparse3d& t);
+
+  ~tsparse3d();
+
+  // accessors
+  int Ny() const { return m_Ny; } 
+  int Nz() const { return m_Nz; } 
+
+
+
+  void trim();
+
+  void untrim();
+
+  bool trimmed() const { return m_trimmed; }
+
+  bool trimmed(int i, int j, int k) const;
+
+  T operator()(int i, int j, int k) const;
+
+  const tsparse2d<T>* operator[](int i) const;
+
+  T& operator()(int i, int j, int k);
+
+  int size() const;
+
+  void print() const;
+
+  int ymin();
+
+  int ymax();
+
+  int zmin();
+
+  int zmax();
+
+
+  // algebraic operators
+
+  tsparse3d& operator=(const tsparse3d& t);
+
+  tsparse3d& operator*=(const double& d);
+
+  tsparse3d& operator+=(const tsparse3d& t) {
+    m_trimmed = false;
+    if ( Nx()!=t.Nx() || Ny()!=t.Ny() || Nz()!=t.Nz() ) throw out_of_range("bin mismatch");
+    for ( int i=0 ; i<Nx() ; i++ ) {
+      for ( int j=0 ; j<Ny() ; j++ ) {
+	for ( int k=0 ; k<Nz() ; k++ ) (*this)(i,j,k) += t(i,j,k);
+      }
+    }
+    return *this;
+  }
+
+private:
+
+  void grow(int i);
+
+protected:
+  
+  int m_Ny;
+  int m_Nz;
+  
+  tsparse2d<T>**  m_v;
+  
+  //  T** m_fastindex;
+  
[…]

### 2020-03-23 applgridphoton/appl_grid/tsparse_base.h

@@ -1,0 +1,91 @@
+// emacs: this is -*- c++ -*-
+//
+//   tsparse_base.h        
+//
+//   base class for common range checking and utilities for generic 
+//   sparse matrix classes
+//                   
+// 
+//   Copyright (C) 2007 M.Sutton (sutt@hep.ucl.ac.uk)    
+//
+//   $Id: tsparse_base.h, v0.0   Thu Nov 22 01:28:27 GMT 2007 sutt
+
+
+#ifndef __TSPARSE_BASE_H
+#define __TSPARSE_BASE_H
+
+#include <iostream>
+
+
+#include <cmath>
+
+
+class tsparse_base {
+
+public: 
+
+  // range exception
+  class out_of_range { 
+  public: 
+    out_of_range(const std::string& s="out of range");
+  };
+
+public:
+  
+  // constructors etc
+
+  tsparse_base()       : m_Nx(0),  m_lx(1),  m_ux(0)    { }
+  tsparse_base(const int& nx) : m_Nx(nx), m_lx(0),  m_ux(nx-1) { } 
+  tsparse_base(const int& nx, const int& lx, const int& _size=1)  
+    : m_Nx(nx), m_lx(lx), m_ux(lx+_size-1) { } 
+
+  virtual ~tsparse_base() { } 
+
+
+  // access functions
+
+  int Nx() const { return m_Nx; } 
+  int lo() const { return m_lx; }
+  int hi() const { return m_ux; }
+
+  virtual int size() const { return m_ux-m_lx+1; } //  + 3*sizeof(int); } 
+
+  bool trimmed(int i) const { return ( i<m_lx || i>m_ux ? false : true );  } 
+
+  // make sure index is not out of range
+  void range_check(int i) const { if ( i<0 || i>m_Nx-1 ) { 
+      std::cerr << "index i=" << i << std::endl;
+      throw out_of_range(); 
+    }    
+  } 
+
+  bool operator==(int i) const { return size()==i; } 
+
+  int xmin() { return m_lx; } 
+  int xmax() { return m_ux; } 
+
+  // shouldn't really be in here, it's just for printing 
+  static double mant(double x) { 
+    return  x/std::pow(10.,int(std::log10(std::fabs(x))+128)-128);
+  }
+
+protected:
+
+  int m_Nx; // number of elements
+  int m_lx; // indices of lowest and highest occupied 
[…]

### 2020-03-23 applgridphoton/src/Cache.h

@@ -1,0 +1,151 @@
+// emacs: this is -*- c++ -*-
+//
+//   @file    Cache.h        
+//            evaluate a pdf function and store values in a cache.
+//            if this x, Q2 node has been requested before then 
+//            retrieve the values and return them if not, generate 
+//            and then add to the cache and then retiurn them
+//
+//            the new LHAPDF (version 6) may implement something 
+//            like this internally, but a retieval from the cache 
+//            is still around 20-40 times faster than LHAPDF 6                   
+//  
+//   Copyright (C) 2013 M.Sutton (sutt@cern.ch)    
+//
+//   $Id: Cache.h, v0.0   Sat 19 Oct 2013 14:12:42 CEST sutt $
+
+
+#pragma  once
+
+#include <iostream>
+#include <map>
+#include <utility>
+
+/// Pass an LHAPDF (version 5) function pointer into the cache, 
+/// then call using the evaluate() method instead of the calling 
+/// the pdf directly. 
+
+template<typename T>
+class Cache : public std::map<T, std::vector<double> > {
+ 
+private: 
+
+  /// actual type def of the map for convenience
+  typedef std::map<T,std::vector<double> > _map;
+
+  /// function pointer type
+  typedef void (*pdffunction)(const double& , const double&, double* );
+
+  /// for fast copy 
+  struct partons { double p[14]; };
+
+public:
+
+  /// give it the pdf function to use
+  Cache( pdffunction pdf=0, unsigned mx=20000 ) : _pdf(pdf), _max(mx), _ncalls(0), _ncached(0), _reset(0), _disabled(false), _printstats(false) { } 
+
+  virtual ~Cache() { } 
+
+  
+  /// evaluate the pdf function
+  /// if this node has been requested before, retrieve values 
+  /// from the cache, if not, generate and then add to cache
+  /// for next time 
+  void evaluate( const double& x, const double& Q, double*  xf ) {
+    
+    if ( _pdf==0 ) { 
+      /// should really throw an exception here
+      std::cerr << "whoops, pdf cache has no pdf!!" << std::endl; 
+      return; 
+    }
+
+    _ncalls++;
+
+    /// if we don't want to use the cache for some reason (it can get quite large)     
+    if ( _disabled ) return _pdf( x, Q, xf );
+
+    //    _reset++;
+
[…]

### 2020-03-23 applgridphoton/src/Directory.h

@@ -1,0 +1,70 @@
+// emacs: this is -*- c++ -*-
+/**************************************************************************
+ **
+ **   File:         appl_grid/Directory.h  
+ **
+ **   Description:  class to keep a directory for each object 
+ **                 in a root sort of way, but needed to keep 
+ **                 the root objects out of the actual code.   
+ ** 
+ **   Author:       M.Sutton  
+ **
+ **   Created:      Wed May  4 17:54:25 BST 2005
+ **   Modified:     
+ **                   
+ **                   
+ **
+ **************************************************************************/ 
+
+
+#ifndef __DIRECTORY_H
+#define __DIRECTORY_H
+
+#include "TDirectory.h"
+
+// #include "utils.h"
+
+class Directory {
+
+ public:
+
+  Directory() : mDir(NULL), mPop(NULL) { } 
+  Directory(std::string n) : mDir(NULL) { 
+    mPop = gDirectory;
+    //    depunctuate(n);
+    mDir = gDirectory->mkdir(n.c_str());
+  } 
+
+  void push() { 
+    mPop = gDirectory;
+    if (mDir) mDir->cd();
+  } 
+
+  void pop() { if (mPop) mPop->cd(); }
+
+  void Write() { 
+    push();
+    mDir->Write();
+    pop();
+  } 
+
+ private:
+  
+  TDirectory* mDir;
+  TDirectory* mPop;
+
+};
+
+
+
+#endif  /* __DIRECTORY_H */
+
+
+
+
+
+
+
+
+
+

### 2020-03-23 applgridphoton/src/appl_timer.h

@@ -1,0 +1,55 @@
+/**************************************************************************
+ **
+ **   File:         appl_timer.h  
+ **
+ **   Description:  small timer wrapper  
+ **                   
+ **                   
+ ** 
+ **   Author:       M.Sutton  
+ **
+ **   Created:      Fri Jun 29 18:59:09 BST 2001
+ **   Modified:     
+ **                   
+ **                   
+ **
+ **************************************************************************/ 
+
+
+#ifndef __APPL_TIMER
+#define __APPL_TIMER
+
+#include <time.h>
+#include <sys/time.h>
+
+#define APPL_TIMER_START  0
+#define APPL_TIMER_STOP   1
+#define APPL_TIMER_SINCE -1
+
+#ifdef __cplusplus
+// namespace appl { 
+extern "C" {
+#endif
+
+
+double appl_timer(int   );
+void   appl_timer_initkey(void);
+struct timeval appl_timer_start(void);
+double         appl_timer_stop(struct timeval );
+
+#ifdef __cplusplus
+}
+// };
+#endif
+
+#endif /* __APPL_TIMER */
+
+
+
+
+
+
+
+
+
+

### 2020-03-23 applgridphoton/src/applcheck.cpp

@@ -1,0 +1,155 @@
+#include <algorithm>
+#include <array>
+#include <cstddef>
+#include <iostream>
+#include <memory>
+#include <vector>
+
+#include <LHAPDF/LHAPDF.h>
+#include <appl_grid/appl_grid.h>
+
+std::unique_ptr<LHAPDF::PDF> pdf;
+
+enum flavour_map_index : std::size_t
+{
+    anti_top,      // -6: anti-top
+    anti_bottom,   // -5: anti-bottom
+    anti_charm,    // -4: anti-charm
+    anti_strange,  // -3: anti-strange
+    anti_up,       // -2: anti-up
+    anti_down,     // -1: anti-down
+    gluon,         // 21: gluon
+    down,          //  1: down
+    up,            //  2: up
+    strange,       //  3: strange
+    charm,         //  4: charm
+    bottom,        //  5: bottom
+    top,           //  6: top
+    photon,        // 22: photon
+};
+
+std::array<bool, 14> flavour_map = {
+    true,  // -6: anti-top
+    true,  // -5: anti-bottom
+    true,  // -4: anti-charm
+    true,  // -3: anti-strange
+    true,  // -2: anti-up
+    true,  // -1: anti-down
+    true,  // 21: gluon
+    true,  //  1: down
+    true,  //  2: up
+    true,  //  3: strange
+    true,  //  4: charm
+    true,  //  5: bottom
+    true,  //  6: top
+    true,  // 22: photon
+};
+
+constexpr int index_to_pdg_id(std::size_t index)
+{
+    return (index == gluon) ? 21 : ((index == photon) ? 22 : (static_cast <int> (index) - 6));
+}
+
+extern "C" void evolvepdf(double const& x, double const& q, double* xfx)
+{
+    for (std::size_t i = 0; i != flavour_map.size(); ++i)
+    {
+        if (flavour_map.at(i))
+        {
+            xfx[i] = pdf->xfxQ(index_to_pdg_id(i), x, q);
+        }
+        else
+        {
+            xfx[i] = 0.0;
+        }
+    }
+}
+
+extern "C" double alphaspdf(double const& q)
+{
+    return pdf->alphasQ(q);
+}
+
+int main(int argc, char* argv[])
+{
+    // set LHAPDF low verbosity
+    LHAPDF::setVerbosity(0);
+
+    if (argc != 3)
+    {
[…]

### 2020-03-23 applgridphoton/src/merge_bins.cpp

@@ -1,0 +1,30 @@
+#include <appl_grid/appl_grid.h>
+
+#include <fstream>
+#include <iostream>
+#include <string>
+#include <utility>
+#include <vector>
+
+int main(int argc, char* argv[])
+{
+    if (argc < 3)
+    {
+        std::cerr << "Usage: merge_bins outgrid grid1 [grid2 ...]\n";
+
+        return 1;
+    }
+
+    std::vector<std::string> args(&argv[2], &argv[argc]);
+
+    std::vector<appl::grid> grids;
+    grids.reserve(args.size());
+
+    for (auto const& arg : args)
+    {
+        grids.emplace_back(arg);
+    }
+
+    appl::grid result(std::move(grids));
+    result.Write(argv[1]);
+}

### 2020-03-23 applgridphoton/src/pdf_info.cpp

@@ -1,0 +1,60 @@
+#include <appl_grid/appl_grid.h>
+#include <appl_grid/appl_igrid.h>
+#include <appl_grid/appl_pdf.h>
+#include <appl_grid/lumi_pdf.h>
+
+#include <fstream>
+#include <iostream>
+#include <sstream>
+#include <string>
+#include <utility>
+#include <vector>
+
+int main(int argc, char* argv[])
+{
+    if (argc != 2)
+    {
+        std::cerr << "Usage: pdf_info grid\n";
+
+        return 1;
+    }
+
+    appl::grid const grid(argv[1]);
+
+    std::vector<std::string> strings;
+
+    for (std::size_t i = 0; i != grid.order_ids().size(); ++i)
+    {
+        auto const& pdf = *dynamic_cast <lumi_pdf const*> (grid.genpdf(i));
+
+        for (std::size_t k = 0; k != pdf.size(); ++k)
+        {
+            for (int j = 0; j != grid.Nobs_internal(); ++j)
+            {
+                auto const& sparse_grid = *grid.weightgrid(i, j)->weightgrid(k);
+
+                if (sparse_grid.size() != 0)
+                {
+                    if (strings.size() <= k)
+                    {
+                        strings.resize(k + 1);
+                    }
+
+                    std::ostringstream out;
+
+                    out << "O(as^" << grid.order_ids().at(i).alphs() << " a^"
+                        << grid.order_ids().at(i).alpha() << ") iobs=" << j << " pdf=" << k
+                        << " non-zero combination (size=" << sparse_grid.size() << ") = " << pdf[k]
+                        << '\n';
+
+                    strings.at(k).append(out.str());
+                }
+            }
+        }
+    }
+
+    for (auto const& string : strings)
+    {
+        std::cout << string;
+    }
+}

### 2020-03-23 applgridphoton/src/sparse_matrix3d_root_interface.cpp

@@ -1,0 +1,85 @@
+#include "sparse_matrix3d_root_interface.hpp"
+
+#include "appl_grid/tsparse2d.h"
+#include "appl_grid/tsparse1d.h"
+
+#include <TH1D.h>
+
+SparseMatrix3d* sparse_matrix3d_from_th3d(TH3D const& histogram)
+{
+    // TODO: are the following casts neccessary?
+    TH1D* hx = (TH1D*)(&histogram)->Project3D("x");
+    TH1D* hy = (TH1D*)(&histogram)->Project3D("y");
+    TH1D* hz = (TH1D*)(&histogram)->Project3D("z");
+
+    auto* matrix = new SparseMatrix3d(
+        hx->GetNbinsX(), hx->GetBinCenter(1), hx->GetBinCenter(hx->GetNbinsX()),
+        hy->GetNbinsX(), hy->GetBinCenter(1), hy->GetBinCenter(hy->GetNbinsX()),
+        hz->GetNbinsX(), hz->GetBinCenter(1), hz->GetBinCenter(hz->GetNbinsX())
+    );
+
+    delete hx;
+    delete hy;
+    delete hz;
+
+    for (int i = 0; i < matrix->xaxis().N(); ++i)
+    {
+        for (int j = 0; j < matrix->yaxis().N(); ++j)
+        {
+            for (int k = 0; k < matrix->zaxis().N(); ++k)
+            {
+                (*matrix)(i,j,k) = histogram.GetBinContent(i + 1, j + 1, k + 1);
+            }
+        }
+    }
+
+    return matrix;
+}
+
+TH3D* sparse_matrix3d_to_th3d(SparseMatrix3d const& matrix, std::string const& s)
+{
+    double const delx = matrix.xaxis().delta();
+    double const dely = matrix.yaxis().delta();
+    double const delz = matrix.zaxis().delta();
+
+    TH3D* h = new TH3D(
+        s.c_str(),
+        s.c_str(),
+        matrix.xaxis().N(),
+        matrix.xaxis().min()-0.5*delx,
+        matrix.xaxis().max()+0.5*delx,
+        matrix.yaxis().N(),
+        matrix.yaxis().min()-0.5*dely,
+        matrix.yaxis().max()+0.5*dely,
+        matrix.zaxis().N(),
+        matrix.zaxis().min()-0.5*delz,
+        matrix.zaxis().max()+0.5*delz
+    );
+
+    for (int i = matrix.lo(); i <= matrix.hi(); ++i)
+    {
[…]

### 2020-03-23 applgridphoton/src/sparse_matrix3d_root_interface.hpp

@@ -1,0 +1,12 @@
+#ifndef SPARSE_MATRIX_3D_ROOT_INTERFACE_HPP
+#define SPARSE_MATRIX_3D_ROOT_INTERFACE_HPP
+
+#include "appl_grid/SparseMatrix3d.h"
+
+#include <TH3D.h>
+
+SparseMatrix3d* sparse_matrix3d_from_th3d(TH3D const& histogram);
+
+TH3D* sparse_matrix3d_to_th3d(SparseMatrix3d const& matrix, std::string const& s);
+
+#endif

### 2020-03-23 nnpdf31_proc/ATLASTOPDIFF8TEVTRAPNORM/analysis.f

@@ -1,0 +1,67 @@
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_begin(nwgt,weights_info)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      integer nwgt
+      character*(*) weights_info(*)
+
+      call HwU_inithist(nwgt,weights_info)
+      call HwU_book(1,'t rap ', 4,0.0d0,1.6d0)
+      call HwU_book(2,'t rap ', 1,1.6d0,2.5d0)
+      return
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_end(dummy)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      double precision dummy
+      call HwU_write_file
+      return                
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_fill(p,istatus,ipdg,wgts,ibody)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      include 'nexternal.inc'
+      integer istatus(nexternal)
+      integer iPDG(nexternal)
+      integer ibody
+      integer i
+      double precision p(0:4,nexternal)
+      double precision wgts(*)
+      double precision yt, getrapidity
+      external getrapidity
+ 
+      yt  = getrapidity(p(0,3), p(3,3))
+
+      call HwU_fill(1,yt,wgts)
+      call HwU_fill(2,yt,wgts)
+
+ 999  return      
+      end
+
+ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      function getrapidity(en,pl)
+      implicit none
+      real*8 getrapidity,en,pl,tiny,xplus,xminus,y
+      parameter (tiny=1.d-8)
+      xplus=en+pl
+      xminus=en-pl
+      if(xplus.gt.tiny.and.xminus.gt.tiny)then
+         if( (xplus/xminus).gt.tiny.and.(xminus/xplus).gt.tiny)then
+            y=0.5d0*log( xplus/xminus  )
+         else
+            y=sign(1.d0,pl)*1.d8
+         endif
+      else 
[…]

### 2020-03-23 nnpdf31_proc/ATLASTTBARTOT7TEV/analysis.f

@@ -1,0 +1,40 @@
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_begin(nwgt,weights_info)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      integer nwgt
+      character*(*) weights_info(*)
+
+      call HwU_inithist(nwgt,weights_info)
+      call HwU_book(1,'total rate      ', 1,0.5d0,1.5d0)
+      return
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_end(dummy)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      double precision dummy
+      call HwU_write_file
+      return                
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_fill(p,istatus,ipdg,wgts,ibody)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      include 'nexternal.inc'
+      integer istatus(nexternal)
+      integer iPDG(nexternal)
+      double precision p(0:4,nexternal)
+      double precision wgts(*)
+      integer ibody
+      double precision var
+
+      var=1d0
+      call HwU_fill(1,var,wgts)
+      return
+      end

### 2020-03-23 nnpdf31_proc/ATLASZHIGHMASS49FB/analysis.f

@@ -1,0 +1,95 @@
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_begin(nwgt,weights_info)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      integer nwgt
+      character*(*) weights_info(*)
+
+      call HwU_inithist(nwgt,weights_info)
+      call HwU_book(1,'lmlp inv m', 1,  116d0,  130d0)
+      call HwU_book(2,'lmlp inv m', 6,  130d0,  250d0)
+      call HwU_book(3,'lmlp inv m', 1,  250d0,  300d0)
+      call HwU_book(4,'lmlp inv m', 2,  300d0,  500d0)
+      call HwU_book(5,'lmlp inv m', 1,  500d0,  700d0)
+      call HwU_book(6,'lmlp inv m', 1,  700d0, 1000d0)
+      call HwU_book(7,'lmlp inv m', 1, 1000d0, 1500d0)
+      return
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_end(dummy)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      double precision dummy
+      call HwU_write_file
+      return                
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_fill(p,istatus,ipdg,wgts,ibody)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      include 'nexternal.inc'
+      include 'cuts.inc'
+      integer istatus(nexternal)
+      integer iPDG(nexternal)
+      integer ibody  
+      integer i
+      integer j
+      double precision p(0:4,nexternal)
+      double precision wgts(*)
+      double precision ppl(0:3), pplb(0:3), ppv(0:3), xmll, getinvm
+      external getinvm
+
+      double precision p_reco(0:4,nexternal)
+      integer iPDG_reco(nexternal)
+
+
+
+      call recombine_momenta(rphreco, etaphreco, lepphreco, quarkphreco,
[…]

### 2020-03-23 nnpdf31_proc/CMSTOPDIFF8TEVTTRAPNORM/analysis.f

@@ -1,0 +1,73 @@
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_begin(nwgt,weights_info)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      integer nwgt
+      character*(*) weights_info(*)
+
+      call HwU_inithist(nwgt,weights_info)
+      call HwU_book(1,'t-tx pair rap ', 3,0.0d0,0.9d0)
+      call HwU_book(2,'t-tx pair rap ', 1,0.9d0,1.3d0)
+      call HwU_book(3,'t-tx pair rap ', 1,1.3d0,2.5d0)
+      return
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_end(dummy)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      double precision dummy
+      call HwU_write_file
+      return                
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_fill(p,istatus,ipdg,wgts,ibody)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      include 'nexternal.inc'
+      integer istatus(nexternal)
+      integer iPDG(nexternal)
+      integer ibody  
+      integer i
+      double precision p(0:4,nexternal)
+      double precision wgts(*)
+      double precision pttx(0:3), yttx, getrapidity
+      external getrapidity
+
+      do i=0,3
+        pttx(i)=p(i,3)+p(i,4)
+      enddo
+
+      yttx= getrapidity(pttx(0), pttx(3))
+
+      call HwU_fill(1,yttx,wgts)
+      call HwU_fill(2,yttx,wgts)
+      call HwU_fill(3,yttx,wgts)
+
+ 999  return      
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      function getrapidity(en,pl)
+      implicit none
+      real*8 getrapidity,en,pl,tiny,xplus,xminus,y
+      parameter (tiny=1.d-8)
+      xplus=en+pl
+      xminus=en-pl
[…]

### 2020-03-23 run.sh

@@ -1,0 +1,132 @@
+#!/bin/bash
+
+# exit script at the first sign of an error
+set -o errexit
+
+# the following exits if undeclared variables are used
+set -o nounset
+
+# exit if some program in a pipeline fails
+set -o pipefail
+
+# check arguments of the script
+if (( $# != 1 )); then
+    echo "Usage: ./run.sh [dataset]" >&2
+    echo "  The following datasets are available:" >&2
+
+    for i in $(ls -d nnpdf31_proc/*); do
+        echo "  - ${i##*/}" >&2
+    done
+
+    exit 1
+fi
+
+# name of the dataset
+dataset="$1"
+
+mg5amc=$(which mg5_aMC 2> /dev/null || true)
+
+if [[ ! -x ${mg5amc} ]]; then
+    echo "The binary \`mg5_aMC\` wasn't found. Please adjust your PATH variable" >&2
+    exit 1
+fi
+
+applcheck=$(which applcheck 2> /dev/null || true)
+
+if [[ ! -x ${applcheck} ]]; then
+    echo "The binary \`applcheck\` wasn't found. Please adjust your PATH variable" >&2
+    exit 1
+fi
+
+merge_bins=$(which merge_bins 2> /dev/null || true)
+
+if [[ ! -x ${merge_bins} ]]; then
+    echo "The binary \`merge_bins\` wasn't found. Please adjust your PATH variable" >&2
+    exit 1
+fi
+
+# name of the directory where the output is written to
+output="${dataset}"-$(date +%Y%m%d%H%M%S)
+
+if [[ -d $output ]]; then
+    # since we add a date postfix to the name this shouldn't happen
+    echo "Error: output directory already exists" >&2
+    exit 1
+fi
+
+# create and change into output directory
+mkdir "${output}"
+cd "${output}"
+
+# copy the output file to the directory and replace the variables
+output_file=output.txt
+cp ../nnpdf31_proc/"${dataset}"/output.txt "${output_file}"
+sed -i "s/@OUTPUT@/${dataset}/g" "${output_file}"
+
+# create output folder
+python2 "${mg5amc}" "${output_file}" |& tee output.log
+
+# copy patches if there are any
+for i in $(find ../nnpdf31_proc/"${dataset}" -name '*.patch'); do
+    patch -p1 -d "${dataset}" < $i
+done
+
+# enforce proper analysis
[…]

### 2020-03-23 paper/technical-aspects.tex
Add Marco's changes

@@
 \end{equation}
-$c$ and $c_S$ are process-dependent; the contributions $\Sigma_{a_S, a}$ are in general non-zero for $a_S, a \ge 0$ and $a_S + a > q$, where also $q$ is a process-dependent quantity. For example,
+$c$ and $c_S$ are process-dependent; the contributions $\Sigma_{a_S, a}$ are in general non-zero for $a_S, a \ge 0$ and $a_S + a > q$, where also $q$ is a process-dependent
+uantity. For example,
 for (stable) top-pair production, $c=c_S=0$ and $q=2$; for Drell-Yan production, $c=2$, $c_S=0$, and $q=0$. Terms

### 2020-03-23 paper/paper.tex
some edits in paper
Revert "some edits in paper"
This reverts commit 1325752a4a49f15ce2acfeceb8090e1c2eec6b8b.
Add Marco's changes
Add more text to the PineAPPL section

@@
 \usepackage[T1]{fontenc}
+
+\newcommand{\alphas}{\alpha_{S}}
 
@@
 
-\section{Technical}
+\section{Binning phase-space weights with \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
+\label{sec:pineappl}
 
-CS, MZ
-
-Describe pineappl, representation of grids, accuracy and performance.\\
-We may provide converters from applgrid.\\
-How to integrate in MC codes, how this works in aMCblast (setup, MG5 version, urls).\\
-Appendix: how to create and fill grids, + simple code.\\
+\input{pineappl}
 
 \section{Results}
+\label{sec:results}
 
@@
 
+\section{More details about \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
+\label{app:pineappl-interface}
+
+\input{pineappl-appendix}
+
 \bibliographystyle{JHEP}

### 2020-03-23 paper/pineappl.tex
Add more text to the PineAPPL section

--- 2020-03-23 paper/technical-aspects.tex
@@
-\subsection{PineAPPL}
-\label{sec:pineappl}
-
-In this paper we introduce a new program called \textsc{PineAPPL}, which solves the same problem as \textsc{APPLgrid}~\cite{} and \textsc{fastNLO}~\cite{}, but also supports EW corrections, which are the main interest here.
-In particular, the following features distinguish it from the two aforementioned programs:
+In this paper we introduce a new library called \textsc{PineAPPL}, which is similar to \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}.
+Like to those two libraries, also \textsc{PineAPPL} bins phase-space weights in a PDF-independent manner, but it understands EW corrections, which are the main interest in this paper.
+The following features distinguish it:
 \begin{itemize}
-\item support for arbitrary fixed-order calculations in $\alpha$ and $\alpha_\mathrm{s}$ with
-\item support for scale variations in multiples of the central renormalization and factorization scale,
-\item support for all-order predictions from resummation and photon-/parton-showers,
-\item a simple \textsc{C}-interface, with a wrapper for \textsc{Fortran}
-\item and support for it implemented in \textsc{mg5\_aMC@NLO},
-\item converters to convert \textsc{APPLgrids} and \textsc{fastNLO} tables.
+\item Support for arbitrary fixed-order calculations in powers of $\alpha$, $\alpha_\mathrm{s}$ or combinations thereof, e.g.\ in mixed QCD-EW corrections.
+Furthermore variations of the renormalization and factorization scale are supported, if needed.
+For each needed combination of the couplings and logarithms of renormalization and factorization scale a separate subgrid is created (see Sec.~\ref{sec:grid-representation} for more details);
+\item Support for all-order predictions coming from a resummation calculation or a photon-/parton-shower, which are important for some observables (see Sec.~\ref{sec:results}),
+\item A simple \textsc{C}-interface, with a wrapper for \textsc{Fortran} and \textsc{Python} (see App.~\ref{app:pineappl-interface} for examples and documentation), which is needed for Monte Carlos and programs to read and write \textsc{PineAPPL} grids.
+\textsc{PineAPPL} itself is written in Rust.
 \end{itemize}
+For \textsc{mg5\_aMC@NLO}~\cite{Alwall:2014hca,Frederix:2018nkq} the interfacing code is already implemented in the most recent version, which replaces the \textsc{aMCfast}~\cite{Bertone:2014zva} interface.
+The interfacing code for other Monte Carlo generators should be easy to write, see App.~\ref{app:pineappl-interface} for a small example program.
+Finally, \textsc{PineAPPL} provides programs to convert \textsc{APPLgrids} and \textsc{fastNLO} tables to \textsc{PineAPPL} grids.
 
@@
 
-\subsection{Grid representation}
+\subsection{Grid representation and accuracy}
 \label{sec:grid-representation}

### 2020-03-25 paper/sec-pineappl.tex
Fix some spelling mistakes and change structure
- reference multi-coupling expansion in outline of the PineAPPL section
- Drell-Yan needs an 'en dash' instead of a hyphen
- spelling: `labeled` -> `labelled`

--- 2020-03-23 paper/pineappl.tex
@@
+\section{Binning phase-space weights with \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
+\label{sec:pineappl}
+
 In this paper we introduce a new library called \textsc{PineAPPL}, which is similar to \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}.
@@
 \item Support for arbitrary fixed-order calculations in powers of $\alpha$, $\alpha_\mathrm{s}$ or combinations thereof, e.g.\ in mixed QCD-EW corrections.
-Furthermore variations of the renormalization and factorization scale are supported, if needed.
-For each needed combination of the couplings and logarithms of renormalization and factorization scale a separate subgrid is created (see Sec.~\ref{sec:grid-representation} for more details);
+Furthermore, variations of the renormalization and factorization scale are supported, if needed.
+For each needed combination of the couplings and logarithms of renormalization and factorization scale a separate subgrid is created (see the following Sec.~\ref{sec:multi-coupling-expansion} and Sec.~\ref{sec:grid-representation} for more details);
 \item Support for all-order predictions coming from a resummation calculation or a photon-/parton-shower, which are important for some observables (see Sec.~\ref{sec:results}),
@@
 
-\subsubsection{Cross sections in a multi-coupling expansion}
+\subsection{Cross sections in a multi-coupling expansion}
+\label{sec:multi-coupling-expansion}
+
 The structure of the cross-section weights needed by \textsc{PineAPPL} follows the scheme outlined in
-Refs.~\cite{Frederix:2011ss, Bertone:2014zva}, embedded in a mixed-coupling expansion, see Ref.~\cite{Frederix:2018nkq} and Refs.CITE for
+Refs.~\cite{Frederix:2011ss, Bertone:2014zva}, embedded in a mixed-coupling expansion, see Ref.~\cite{Frederix:2018nkq} and Refs.TODO for
 specific examples. Starting
@@
 $c$ and $c_S$ are process-dependent; the contributions $\Sigma_{a_S, a}$ are in general non-zero for $a_S, a \ge 0$ and $a_S + a > q$, where also $q$ is a process-dependent
-uantity. For example,
-for (stable) top-pair production, $c=c_S=0$ and $q=2$; for Drell-Yan production, $c=2$, $c_S=0$, and $q=0$. Terms
+quantity. For example,
+for (stable) top-pair production, $c=c_S=0$ and $q=2$; for Drell--Yan production, $c=2$, $c_S=0$, and $q=0$. Terms
 with  $a_S + a = q + k$ correspond to different N$^k$LO contributions to $\Sigma$, usually
-labeled as N$^k$LO$_i$, $i =1,2, \ldots$, with $i=1$ assigned to the term with the largest power of $\alphas$. Given the hierarchy of the couplings,
+labelled as N$^k$LO$_i$, $i =1,2, \ldots$, with $i=1$ assigned to the term with the largest power of $\alphas$. Given the hierarchy of the couplings,
 one expects that
@@
 \end{equation}
-however such a relation is not always respected, and sometimes blatantly violated~CITE.
+however such a relation is not always respected, and sometimes blatantly violated~TODO.
 
@@
 \end{equation}
-where we have introduced the parton distributions $f_{1,2}$ and the phase-space measure $d$PS.
+where we have introduced the parton distributions $f_{1,2}$ and the phase-space measure $d$PS. The structure of the weights $ \mathcal W^{(l)}_{a_S, a}$ is 
+identical to the case when only correction of QCD origin are treated. In particular:
 \begin{itemize}

### 2020-03-25 paper/paper.tex
adding analysis and some placeholders

@@
 
-SC
+In Table~\ref{table:chi2} we show the $\chi^2$ values for datasets..., using the NNPDF3.1 NLO luxQED set.
 
-For datasets in 3.1qed (+DY2), compute pure NLO QCD (born) vs NLO QCD + NLO EW (dressed) FKtables and:\\
-- compute data/prediction plots\\
-- compute chi2\\
+In Figure~\ref{fig:datacomparison} we present the data prediction comparison for the equivalent setup presented in Table~\ref{table:chi2}.
+
+\begin{table}
+    \centering
+    \begin{tabular}{l|c|cc}
+        \multicolumn{1}{l}{} &  & \multicolumn{2}{c}{$\chi^{2}/n_{{\rm data}}$}\tabularnewline
+        \hline
+        Dataset & $n_{{\rm data}}$ & QCD & QCD+EW\tabularnewline
+        \hline
+        ATLAS HM DY 7 TeV & 13 & 1.151 & 1.036\tabularnewline
+        \hline
+        ATLAS $\sigma_{tt}^{{\rm tot}}$ & 3 & 2.549 & 3.271\tabularnewline
+        \hline
+        CMS $\sigma_{tt}^{{\rm tot}}$ & 3 & 0.986 & 1.654\tabularnewline
+        \hline
+    \end{tabular}
+    \caption{$\chi^2$ values for NNPDF3.1 NLO luxQED.}
+    \label{table:chi2}
+\end{table}
+
+\begin{figure}
+    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs0_plot_fancy_dataspecs_0}
+    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs0_datanorm_plot_fancy_dataspecs_0}
+    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs1_plot_fancy_dataspecs_0}
+    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs1_datanorm_plot_fancy_dataspecs_0}
+    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs2_plot_fancy_dataspecs_0}
+    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs2_datanorm_plot_fancy_dataspecs_0}
+    \caption{Data prediction comparison plots.}
+    \label{fig:datacomparison}
+\end{figure}
 
@@
 
-C.S. is supported by the European Research Council under the European Unions Horizon 2020 research and innovation Programme (grant agreement no. 740006).
+S.C. and C.S. are supported by the European Research Council under the European Unions Horizon 2020 research and innovation Programme (grant agreement no. 740006).
 

### 2020-03-25 paper/analysis/run.sh

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+# generate plots using vp2
+validphys analysis.yaml

### 2020-03-27 paper/paper.tex
start drafting chapter on double counting

--- 2020-03-23 paper/paper.tex
@@
 
-\section{Binning phase-space weights with \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
-\label{sec:pineappl}
+\section{Technical aspects}
+\label{sec:technical-aspects}
 
-\input{pineappl}
+\input{technical-aspects}
 
 \section{Results}
-\label{sec:results}
 
@@
 \section{Double counting}
-
 Count von Count, ALL
 
-Explain the problem to experimentalists.\\
+Explain the problem to experimentalists (the bee and the flower).\\
+
+As it has been mentioned in the introduction, the ability to consistently include electro-weak correction in
+PDF fits is not enough to make a fully-fledged fit possible in a consistent manner. Indeed, experimental data should
+be provided in  a format that allows PDF collaborations to employ them in such fits in a theoretically sound manner. In this
+section, we will try to provide some guidelines, by highlighting some sources of inconsistency commonly occurring in experimental 
+analyses. These will either lead to accounting multiple times for EW effects (so-called double counting), or to not accounting at
+all for such effects.\footnote{By no means we intend to blame on our beloved experimental colleagues for what they write or do. However,
+    we think that by highlighting errors and making everybody more cautious about them is the only way to avoid repeating such
+    errors in the future.}
+
+A common source of inconsistency is the subtraction of backgrounds processes which must not be considered as such. The typical example
+is neutral-current Drell-Yan, where the signal process is an opposite-sign lepton pair, which starts
+at $\mathcal O(\alpha^2)$. Because this process is usually thought
+as a quark-initiated, $s$-channel mechanism ($q\bar q \to \gamma^*/Z \to \ell^+ \ell^-$), in many analyses the photon-induced component,
+$\gamma \gamma \to \ell^+ \ell^-$ in the $t$ channel, is considered as a different process, and it 
+subtracted (see e.g. Refs.~\cite{}). However, such a distinction cannot be physically
+justified beyond LO. Indeed, at $\mathcal O(\alpha^3)$, the reaction $q \gamma \to \ell^+ \ell^- q$ becomes possible, which
+includes both kind of topologies. {\bf MZ add Feynman diags} The problem here derives from the fact 
+that identifing a process based only on its 
+initial-state partons is plain wrong in quantum mechanics. While this fact is well established in QCD --nobody would ever 
+consider to ``subtract'' the gluon-initiated contribution to top-pair production in top analyses-- seemingly it is not so
+when EW corrections are considered.
+
+A second example is related to removing EW effects from data. These can be either the full EW corrections (Refs??) 
+or just a part, for example deconvolving multiple-photon radiation from light particles in the final state. This applies mostly
+to processes such as neutral- or charge-current Drell-Yan, specially when electrons are considered. The problem lie in the fact that
+ electrons, and to a lesser extent muons, tend to radiate photons, and such photons are typically not accounted
+for in hard matrix-elements. Thus, leptons that are measured in the detector are less energetic, and this fact is compensated for
+by undoing the photon shower before publishing data, which are referred to e.g. as \emph{Born-level electrons}~\cite{}. There are 
+at least two 
+problems related with this. The first, a quite obvious one, is that when EW corrections
+are included at fixed order, the first photon emission is included exactly at the matrix-element level. The second, which
+applies for electrons, is that they are never measured as bare particles, because of the finite resolution 
+of the electromagnetic calorimeter. Since collinear photonic emission cannot be resolved, at least data 
+involving electrons should also be published
+in terms of dressed particles, after applying some recombination scheme. This has the further advantage of being 
+inclusive on the effect of further collinear emissions. For what concerns muons, while in principle
+the concept of bare muons is a physical one, it should be kept in mind that modern, general-purpose codes employed to
+compute EW corrections treat leptons as massless. This fact encourages to explore the possibility of employing dressed
+muons, on the same footing as their electron counterpart.
 
@@
 
-\section{More details about \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
-\label{app:pineappl-interface}
-
-\input{pineappl-appendix}
-
 \bibliographystyle{JHEP}

### 2020-03-27 nnpdf31_proc/CMSDY2D11/analysis.f
Try to accumulate 2D distributions in CMSDY2D11

@@ -7,12 +7,12 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
       character*(*) weights_info(*)
 
       call HwU_inithist(nwgt,weights_info)
-      call HwU_book(1,'lmlp inv m', 1,  20d0,   30d0)
-      call HwU_book(2,'lmlp inv m', 1,  30d0,   45d0)
-      call HwU_book(3,'lmlp inv m', 1,  45d0,   60d0)
-      call HwU_book(4,'lmlp inv m', 1,  60d0,  120d0)
-      call HwU_book(5,'lmlp inv m', 1, 120d0,  200d0)
-      call HwU_book(6,'lmlp inv m', 1, 200d0, 1500d0)
+      call HwU_book(1,'lmlp inv m yrap', 24, 0d0,   10d0*2.4)
+c      call HwU_book(2,'lmlp inv m yrap', 24, 0d0,   15d0*2.4)
+c      call HwU_book(3,'lmlp inv m yrap', 24, 0d0,   15d0*2.4)
+c      call HwU_book(4,'lmlp inv m yrap', 24, 0d0,   60d0*2.4)
+c      call HwU_book(5,'lmlp inv m yrap', 24, 0d0,   80d0*2.4)
+c      call HwU_book(6,'lmlp inv m yrap', 12, 0d0, 1300d0*2.4)
 
       return
       end
@@ -42,7 +42,9 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
       double precision p(0:4,nexternal)
       double precision wgts(*)
       double precision ppl(0:3), pplb(0:3), ppv(0:3), xmll, getinvm
+      double precision xyll, gety
       external getinvm
+      external gety
 
       double precision p_reco(0:4,nexternal)
       integer iPDG_reco(nexternal)
@@ -61,13 +63,21 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
       enddo
 
       xmll=getinvm(ppv(0),ppv(1),ppv(2),ppv(3))
+      xyll=gety(ppv(0),ppv(1),ppv(2),ppv(3))
 
-      call HwU_fill(1,xmll,wgts)
-      call HwU_fill(2,xmll,wgts)
-      call HwU_fill(3,xmll,wgts)
-      call HwU_fill(4,xmll,wgts)
-      call HwU_fill(5,xmll,wgts)
[…]

### 2020-03-27 nnpdf31_proc/CMSDY2D11/analysis.f
Add more fixes for the CMSDY2D11 dataset

@@ -7,12 +7,12 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
       character*(*) weights_info(*)
 
       call HwU_inithist(nwgt,weights_info)
-      call HwU_book(1,'lmlp inv m yrap', 24, 0d0,   10d0*2.4)
-c      call HwU_book(2,'lmlp inv m yrap', 24, 0d0,   15d0*2.4)
-c      call HwU_book(3,'lmlp inv m yrap', 24, 0d0,   15d0*2.4)
-c      call HwU_book(4,'lmlp inv m yrap', 24, 0d0,   60d0*2.4)
-c      call HwU_book(5,'lmlp inv m yrap', 24, 0d0,   80d0*2.4)
-c      call HwU_book(6,'lmlp inv m yrap', 12, 0d0, 1300d0*2.4)
+      call HwU_book(1,'lmlp m yrap', 24,  20d0*2.4,   30d0*2.4)
+      call HwU_book(2,'lmlp m yrap', 24,  30d0*2.4,   45d0*2.4)
+      call HwU_book(3,'lmlp m yrap', 24,  45d0*2.4,   60d0*2.4)
+      call HwU_book(4,'lmlp m yrap', 24,  60d0*2.4,  120d0*2.4)
+      call HwU_book(5,'lmlp m yrap', 24, 120d0*2.4,  200d0*2.4)
+      call HwU_book(6,'lmlp m yrap', 12, 200d0*2.4, 1500d0*2.4)
 
       return
       end
@@ -45,6 +45,8 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
       double precision xyll, gety
       external getinvm
       external gety
+      integer bin
+      double precision minmll, maxmll
 
       double precision p_reco(0:4,nexternal)
       integer iPDG_reco(nexternal)
@@ -65,19 +67,36 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
       xmll=getinvm(ppv(0),ppv(1),ppv(2),ppv(3))
       xyll=gety(ppv(0),ppv(1),ppv(2),ppv(3))
 
+      bin = -1
+
       if (xmll.ge.20d0.and.xmll.lt.30d0) then
-        call HwU_fill(1,xyll*10d0,wgts)
-c      elseif (xmll.ge.30d0.and.xmll.lt.45d0) then
-c        call HwU_fill(2,xmll,wgts)
[…]

### 2020-03-30 paper/paper.tex
Cleanup

--- 2020-03-23 paper/paper.tex
@@
 
-\section{Introduction}
-\label{sec:introduction}
-
-ERN
-
-The impact of EW corrections to LHC data.\\
-How to do that consistently, include systematically EW corrections, blabla.\\
-Outline a possible strategy to deal with EW correction in LHC observables (FSR, PHOTOS, dressed/born, ...).\\
-Pinappl kills amcfast and mcgrid, replace applgrid and fastnlo.\\
-
-\section{Binning phase-space weights with \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
-\label{sec:pineappl}
-
-\input{pineappl}
-
-\section{Results}
-\label{sec:results}
-
-SC
-
-For datasets in 3.1qed (+DY2), compute pure NLO QCD (born) vs NLO QCD + NLO EW (dressed) FKtables and:\\
-- compute data/prediction plots\\
-- compute chi2\\
-
-\section{Double counting}
-
-Count von Count, ALL
-
-Explain the problem to experimentalists.\\
-
-\section{Outlook}
-
-ALL
-
-\cite{Carli:2010rw}
-\cite{Bertone:2014zva}
+\input{sec-introduction}
+\input{sec-pineappl}
+\input{sec-results}
+\input{sec-doublecounting}
+\input{sec-conclusion}
 
@@
 
-C.S. is supported by the European Research Council under the European Unions Horizon 2020 research and innovation Programme (grant agreement no. 740006).
+C.S. is supported by the European Research Council under the European Unions 
+Horizon 2020 research and innovation Programme (grant agreement no. 740006).
 

### 2020-03-30 paper/sec-conclusion.tex
Cleanup

\section{Outlook}

ALL

\cite{Carli:2010rw}
\cite{Bertone:2014zva}

### 2020-03-30 paper/sec-doublecounting.tex
Cleanup

\section{Double counting}
Count von Count, ALL

Explain the problem to experimentalists (the bee and the flower).\\

As it has been mentioned in the introduction, the ability to consistently include electro-weak correction in
PDF fits is not enough to make a fully-fledged fit possible in a consistent manner. Indeed, experimental data should
be provided in  a format that allows PDF collaborations to employ them in such fits in a theoretically sound manner. In this
section, we will try to provide some guidelines, by highlighting some sources of inconsistency commonly occurring in experimental 
analyses. These will either lead to accounting multiple times for EW effects (so-called double counting), or to not accounting at
all for such effects.\footnote{By no means we intend to blame on our beloved experimental colleagues for what they write or do. However,
    we think that by highlighting errors and making everybody more cautious about them is the only way to avoid repeating such
    errors in the future.}

A common source of inconsistency is the subtraction of backgrounds processes which must not be considered as such. The typical example
is neutral-current Drell-Yan, where the signal process is an opposite-sign lepton pair, which starts
at $\mathcal O(\alpha^2)$. Because this process is usually thought
as a quark-initiated, $s$-channel mechanism ($q\bar q \to \gamma^*/Z \to \ell^+ \ell^-$), in many analyses the photon-induced component,
$\gamma \gamma \to \ell^+ \ell^-$ in the $t$ channel, is considered as a different process, and it 
subtracted (see e.g. Refs.~\cite{}). However, such a distinction cannot be physically
justified beyond LO. Indeed, at $\mathcal O(\alpha^3)$, the reaction $q \gamma \to \ell^+ \ell^- q$ becomes possible, which
includes both kind of topologies. {\bf MZ add Feynman diags} The problem here derives from the fact 
that identifing a process based only on its 
initial-state partons is plain wrong in quantum mechanics. While this fact is well established in QCD --nobody would ever 
consider to ``subtract'' the gluon-initiated contribution to top-pair production in top analyses-- seemingly it is not so
when EW corrections are considered.

A second example is related to removing EW effects from data. These can be either the full EW corrections (Refs??) 
or just a part, for example deconvolving multiple-photon radiation from light particles in the final state. This applies mostly
to processes such as neutral- or charge-current Drell-Yan, specially when electrons are considered. The problem lie in the fact that
 electrons, and to a lesser extent muons, tend to radiate photons, and such photons are typically not accounted
for in hard matrix-elements. Thus, leptons that are measured in the detector are less energetic, and this fact is compensated for
by undoing the photon shower before publishing data, which are referred to e.g. as \emph{Born-level electrons}~\cite{}. There are 
at least two 
problems related with this. The first, a quite obvious one, is that when EW corrections
are included at fixed order, the first photon emission is included exactly at the matrix-element level. The second, which
applies for electrons, is that they are never measured as bare particles, because of the finite resolution 
of the electromagnetic calorimeter. Since collinear photonic emission cannot be resolved, at least data 
involving electrons should also be published
in terms of dressed particles, after applying some recombination scheme. This has the further advantage of being 
inclusive on the effect of further collinear emissions. For what concerns muons, while in principle
the concept of bare muons is a physical one, it should be kept in mind that modern, general-purpose codes employed to
compute EW corrections treat leptons as massless. This fact encourages to explore the possibility of employing dressed
muons, on the same footing as their electron counterpart.

### 2020-03-30 paper/sec-introduction.tex
Cleanup

\section{Introduction}
\label{sec:introduction}

The Large Hadron Collider (LHC)

ERN

The impact of EW corrections to LHC data.\\
How to do that consistently, include systematically EW corrections, blabla.\\
Outline a possible strategy to deal with EW correction in LHC observables (FSR, PHOTOS, dressed/born, ...).\\
Pinappl kills amcfast and mcgrid, replace applgrid and fastnlo.\\

### 2020-03-30 paper/sec-results.tex
Cleanup

\section{Results}
\label{sec:results}

SC

For datasets in 3.1qed (+DY2), compute pure NLO QCD (born) vs NLO QCD + NLO EW (dressed) FKtables and:\\
- compute data/prediction plots\\
- compute chi2\\

### 2020-03-31 paper/sec-introduction.tex
Intro WIP

@@
 
-The Large Hadron Collider (LHC)
+With the recent completion of Run II, the Large Hadron Collider (LHC) has 
+accumulated data from an integrated luminosity of approximately 
+150~fb$^{-1}$~\cite{Mangano:2020icy}. This represents only a small fraction of 
+the anticipated 3000 fb$^{-1}$ that will eventually be recorded in the 
+forthcoming twenty years of LHC operation. Nevertheless the statistical 
+uncertainty of the data has already shrunk to unprecedentedly small values,
+typically 1\% or less, a fact that will allow for precision tests of the 
+Standard Model (SM) and for indirect searches of New Physics only if 
+theoretical predictions become comparatively precise. This entails the 
+computation of additional higher-order contributions to the fixed-order 
+coupling-constant perturbative expansion, on the one hand, and an increasingly 
+sophisticated determination of the Parton Distribution Functions (PDFs) of the 
+proton~\cite{Gao:2017yyd}, on the other hand.
 
-ERN
+In the first respect, because Quantum Chromodynamics (QCD) dominates the 
+interactions occurring within colliding protons at the LHC, much effort 
+has been devoted to the computation of higher-order QCD corrections: 
+fully-differential next-to-leading order (NLO) results, possibly matched to the
+parton shower, are currently automated in various general-purpose
+Monte Carlo generators~\cite{Gleisberg:2008ta,Alwall:2014hca,Bellm:2015jjp}, 
+while an increasing number of next-to-next-to-leading order (NNLO) predictions 
+are becoming available for processes with various degrees of inclusiveness
+(see {\it e.g.}~\cite{Amoroso:2020lgh} and references therein). The computation
+of higher-order corrections in the Electroweak (EW) theory has 
+witnessed a comparatively less comprehensive progress. Nevertheless frameworks 
+were developed in which the QCD and EW couplings are simultaneously treated as 
+small parameters in the perturbative expansion, and the computation of 
+theoretical predictions, accurate to NLO (including mixed-coupling QCD+EW 
+terms), is automated~\cite{Biedermann:2017yoi,Frederix:2018nkq}.
 
-The impact of EW corrections to LHC data.\\
+In the second respect, contemporary PDF
+sets~\cite{Harland-Lang:2014zoa,Ball:2017nwa,Hou:2019efy}
+incorporate a significant amount of LHC data, which is analysed with NNLO QCD 
+theory by default. No EW corrections are included in the theoretical 
+description of the experimental observables to which PDFs are optimised,
+except for QED effects if a photon PDF is 
+determined~\cite{Schmidt:2015zda,Bertone:2017bme,Harland-Lang:2019pla}. 
+The resulting relative PDF uncertainy --- 
+which accounts only for the uncertainty of the data and of the 
+methodology inherent to each PDF determination --- can be as low as 1\% at the 
+EW scale~\cite{Ball:2017nwa}. Theoretical uncertainties, possibly of comparable 
+size ({\it e.g.} from missing higher-order terms in the perturbative expansion),
+can also be included in a PDF determination and represented into PDF 
+uncertainties~\cite{AbdulKhalek:2019bux,AbdulKhalek:2019ihb}.
+This leads to a noticeable improvement of PDF accuracy, in that the overall 
+statistical quality of the fit increases, at the price of a modest 
+deterioration of PDF precision, in that PDF uncertainties are slightly inflated.
+
+The two respects are intertwined: PDFs provide a way of obtaining a prediction
+for a given process in terms of other processes, therefore the accuracy and 
+precision with which PDFs are able to make predictions crucially depend on 
+the accuracy of the perturbative computation used in the PDF determination
+(matched to the precision of the data). Electroweak (including mixed QCD+EW) 
+effects should therefore naturally be included in a PDF determination. The 
+reason is twofold. First, one expects NNLO QCD and NLO EW corrections to be of 
+comparable size because, at the EW scale, the QCD and EW coupling constants 
+become similar, $\alpha_s^2\sim \alpha$. If NNLO QCD corrections are included 
+by default in PDF determinations, NLO EW and NLO EW+QCD corrections should be 
+taken into account on the same footing. Second, the virtual exchange of soft or 
+collinear weak bosons leads to Sudakov 
+logarithms~\cite{Denner:2000jv,Denner:2001gw},
+which can make the coefficients of the EW series grow faster than 
+their QCD counterparts. Such a behaviour becomes relevant in
+phase-space regions associated with large mass scales (roughly of the order
+of the TeV), where several LHC data sets ({\it e.g.} $Z$ boson transverse 
+momentum distributions) enter both the determination of PDFs and the search
+for New Physics.
+
+The systematic inclusion of EW corrections in a PDF determination entails
+the solution of two separate problems. efficiency (produce lookup tables)
+and consistency (avoid double counting).
+This paper addresses the first problem. How? By developing Pinanppl
+
 How to do that consistently, include systematically EW corrections, blabla.\\

### 2020-04-01 paper/sec-introduction.tex
Intro WIP

@@
 The systematic inclusion of EW corrections in a PDF determination entails
-the solution of two separate problems. efficiency (produce lookup tables)
-and consistency (avoid double counting).
-This paper addresses the first problem. How? By developing Pinanppl
+the solution of two separate problems. First, a problem of efficiency:
+fast interpolation grids should be constructed, whereby partonic matrix 
+elements, accurate to NLO QCD+EW, are precomputed in such a way that the 
+numerical convolution with generic input PDFs can be efficiently approximated
+by means of interpolation techniques. Such grids are a fundamental ingredient
+in any PDF fit, where the evaluation of the hadronic cross section needs to 
+be performed a large number of times. While two default formats exist for
+these grids, {\sc APPLgrid}~\cite{Carli:2010rw} and 
+{\sc fastNLO}~\cite{Kluge:2006xs}, none of them allows for the inlusion of EW
+corrections nor for the interface to a Monte Carlo generator accurate to 
+NLO QED+EW. Second, a problem of consistency: the way in which EW effects may
+(or may not) be folded into the data varies across different experimental 
+analyses, a fact that challenges their consistent theoretical interpretation. 
+Examples are the subtraction of background processes which should not be 
+considered as such ({\it e.g.} the $t$-channel photon-induced component in 
+neutral-current Drell-Yan, which are not different processes beyond LO) or of 
+just a part of the EW effects ({\it e.g.} multiple-photon radiation from light 
+particles in the final state of neutral- or charged-current Drell-Yan, 
+especially with electrons). Be that as it may if EW effects are systematically
+included in theoretical predictions, they should not be in the data,
+otherwise they will be double counted.
+
+In this paper we address the first of these two problems.
+How? By developing {\sc PineAPPL}
+
+the second problem, the solution of which, however, remains beyond the scope of 
+the current work.
 
@@
 Pinappl kills amcfast and mcgrid, replace applgrid and fastnlo.\\
+
+The paper is organised as follows.

### 2020-04-01 paper/sec-introduction.tex
Intro - first draft

@@
 parton shower, are currently automated in various general-purpose
-Monte Carlo generators~\cite{Gleisberg:2008ta,Alwall:2014hca,Bellm:2015jjp}, 
+Monte Carlo generators~\cite{Gleisberg:2008ta,Alwall:2014hca,Bellm:2015jjp}
+(see also ref.~\cite{Buckley:2011ms} for a review),
 while an increasing number of next-to-next-to-leading order (NNLO) predictions 
@@
 particles in the final state of neutral- or charged-current Drell-Yan, 
-especially with electrons). Be that as it may if EW effects are systematically
-included in theoretical predictions, they should not be in the data,
+especially with electrons). Be that as it may, if EW effects are systematically
+included in theoretical predictions, they should not be included in the data,
 otherwise they will be double counted.
 
-In this paper we address the first of these two problems.
-How? By developing {\sc PineAPPL}
+In this paper we address the first of these two problems. Specifically, 
+we develop {\sc PineAPPL}, a new library that provides a direct interface 
+from parton-level Monte Carlo event generators accurate up to NLO QCD+EW to
+fast interpolation grids. The library supports variations of the factorisation
+and renormalisations scales, resummation, and matching with a photon- and/or
+parton-shower. The library is included by default in 
+{\sc MadGraph5\_aMC@NLO} ({\sc mg5\_aMC@NLO} henceforth) within which it has 
+been designed and tested. However, it is suitable for use as a plugin in any 
+Monte Carlo generator that supports NLO QCD+EW computations, such as 
+{\sc SHERPA}~\cite{Biedermann:2017yoi}. In this respect, {\sc PineAPPL}
+supersedes the {\sc aMCfast} interface~\cite{Bertone:2014zva} and complements
+the {\sc MCgrid} interface~\cite{DelDebbio:2013kxa,Bothmann:2015dba}.
 
-the second problem, the solution of which, however, remains beyond the scope of 
-the current work.
+The paper is organised as follows. In Sect.~\ref{sec:pineappl} we introduce
+{\sc PineAPPL}, we describe its features, we illustrate its operation, and we
+assess its performance. In Sect.~\ref{sec:results}, by means of 
+{\sc mg5\_AMC@NLO} and {\sc PineAPPL}, we compute fast interpolation grids for 
+a representative set of data that is typically included in a fit of PDFs.
+In Sect.~\ref{sec:double-counting} we use these results to formulate more 
+comprehensively the second problem sketched above, the solution of which, 
+however, remains beyond the scope of the current work. We provide an outlook in
+Sect~\ref{sec:conclusion}.
 
-How to do that consistently, include systematically EW corrections, blabla.\\
-Outline a possible strategy to deal with EW correction in LHC observables (FSR, PHOTOS, dressed/born, ...).\\
-Pinappl kills amcfast and mcgrid, replace applgrid and fastnlo.\\
-
-The paper is organised as follows.
+%Outline a possible strategy to deal with EW correction in LHC observables 
+%(FSR, PHOTOS, dressed/born, ...).

### 2020-04-01 paper/sec-introduction.tex
Fixed missing cross ref

@@
 a representative set of data that is typically included in a fit of PDFs.
-In Sect.~\ref{sec:double-counting} we use these results to formulate more 
+In Sect.~\ref{sec:doublecounting} we use these results to formulate more 
 comprehensively the second problem sketched above, the solution of which, 

### 2020-04-01 paper/sec-introduction.tex
Intro - revised

@@
 Monte Carlo generators~\cite{Gleisberg:2008ta,Alwall:2014hca,Bellm:2015jjp}
-(see also ref.~\cite{Buckley:2011ms} for a review),
+(see also~\cite{Buckley:2011ms} for a review),
 while an increasing number of next-to-next-to-leading order (NNLO) predictions 
@@
 (see {\it e.g.}~\cite{Amoroso:2020lgh} and references therein). The computation
-of higher-order corrections in the Electroweak (EW) theory has 
+of higher-order corrections in the Electroweak (EW) and mixed QCD+EW theory has 
 witnessed a comparatively less comprehensive progress. Nevertheless frameworks 
@@
 small parameters in the perturbative expansion, and the computation of 
-theoretical predictions, accurate to NLO (including mixed-coupling QCD+EW 
-terms), is automated~\cite{Biedermann:2017yoi,Frederix:2018nkq}.
+theoretical predictions, accurate to NLO in both (including mixed-coupling 
+QCD+EW terms), is automated~\cite{Biedermann:2017yoi,Frederix:2018nkq}.
 
@@
 incorporate a significant amount of LHC data, which is analysed with NNLO QCD 
-theory by default. No EW corrections are included in the theoretical 
-description of the experimental observables to which PDFs are optimised,
-except for QED effects if a photon PDF is 
+theory by default. No EW corrections are systematically included in the 
+theoretical description of the experimental observables to which PDFs are 
+optimised, except for QED effects if a photon PDF is 
 determined~\cite{Schmidt:2015zda,Bertone:2017bme,Harland-Lang:2019pla}. 
-The resulting relative PDF uncertainy --- 
-which accounts only for the uncertainty of the data and of the 
-methodology inherent to each PDF determination --- can be as low as 1\% at the 
-EW scale~\cite{Ball:2017nwa}. Theoretical uncertainties, possibly of comparable 
-size ({\it e.g.} from missing higher-order terms in the perturbative expansion),
-can also be included in a PDF determination and represented into PDF 
-uncertainties~\cite{AbdulKhalek:2019bux,AbdulKhalek:2019ihb}.
-This leads to a noticeable improvement of PDF accuracy, in that the overall 
-statistical quality of the fit increases, at the price of a modest 
-deterioration of PDF precision, in that PDF uncertainties are slightly inflated.
+The resulting relative PDF uncertainy --- which accounts only for the 
+uncertainty of the data and of residual methodology inefficiencies inherent to 
+each PDF determination --- can be as low as 1\% at the EW 
+scale~\cite{Ball:2017nwa}. Theoretical uncertainties, possibly of comparable 
+size ({\it e.g.} from missing higher-order terms in the QCD perturbative 
+expansion), have started to be included in a PDF determination and represented 
+into PDF uncertainties only very 
+recently~\cite{AbdulKhalek:2019bux,AbdulKhalek:2019ihb}. This has led to a 
+noticeable improvement of PDF accuracy, in terms of an overall
+better statistical quality of the fit, at the price of a modest deterioration 
+of PDF precision, in terms of a slight inflation of PDF uncertainties.
 
@@
 reason is twofold. First, one expects NNLO QCD and NLO EW corrections to be of 
-comparable size because, at the EW scale, the QCD and EW coupling constants 
-become similar, $\alpha_s^2\sim \alpha$. If NNLO QCD corrections are included 
+comparable size because, at the EW scale, the QCD and EW running couplings 
+become similar, $\alpha_S^2\sim \alpha$. If NNLO QCD corrections are included 
 by default in PDF determinations, NLO EW and NLO EW+QCD corrections should be 
@@
 these grids, {\sc APPLgrid}~\cite{Carli:2010rw} and 
-{\sc fastNLO}~\cite{Kluge:2006xs}, none of them allows for the inlusion of EW
-corrections nor for the interface to a Monte Carlo generator accurate to 
+{\sc fastNLO}~\cite{Kluge:2006xs}, none of them supports the inclusion of EW
+corrections nor the interface to a Monte Carlo generator accurate to 
 NLO QED+EW. Second, a problem of consistency: the way in which EW effects may
@@
 considered as such ({\it e.g.} the $t$-channel photon-induced component in 
-neutral-current Drell-Yan, which are not different processes beyond LO) or of 
-just a part of the EW effects ({\it e.g.} multiple-photon radiation from light 
-particles in the final state of neutral- or charged-current Drell-Yan, 
-especially with electrons). Be that as it may, if EW effects are systematically
-included in theoretical predictions, they should not be included in the data,
-otherwise they will be double counted.
+neutral-current Drell-Yan, which is not a separate processes beyond the leading
+order) or of just a part of the EW effects ({\it e.g.} multiple-photon 
+radiation from light particles in the final state of neutral- or charged-current
+Drell-Yan, especially with electrons). Be that as it may, if EW effects are 
+systematically included in theoretical predictions, they should not be included 
+in the data, otherwise they will be double counted.
 
@@
 comprehensively the second problem sketched above, the solution of which, 
-however, remains beyond the scope of the current work. We provide an outlook in
-Sect~\ref{sec:conclusion}.
+however, remains beyond the scope of the current work. We provide our
+conclusions and an outlook in Sect.~\ref{sec:conclusion}.
 

### 2020-04-06 paper/paper.tex
Small tweak
adding plots using pgf

--- 2020-03-25 paper/paper.tex
@@
 \usepackage[T1]{fontenc}
+\usepackage{pgf}
 
@@
     \centering
-    \begin{tabular}{l|c|cc}
-        \multicolumn{1}{l}{} &  & \multicolumn{2}{c}{$\chi^{2}/n_{{\rm data}}$}\tabularnewline
+    \begin{tabular}{l|c|c}
         \hline
-        Dataset & $n_{{\rm data}}$ & QCD & QCD+EW\tabularnewline
+        Dataset & $n_{{\rm data}}$ & $\chi^{2}/n_{{\rm data}}$ \tabularnewline
         \hline
-        ATLAS HM DY 7 TeV & 13 & 1.151 & 1.036\tabularnewline
+        ATLAS HM DY 7 TeV & 13 & 1.39 \tabularnewline
         \hline
-        ATLAS $\sigma_{tt}^{{\rm tot}}$ & 3 & 2.549 & 3.271\tabularnewline
-        \hline
-        CMS $\sigma_{tt}^{{\rm tot}}$ & 3 & 0.986 & 1.654\tabularnewline
+        CMS $\sigma_{tt}^{{\rm tot}}$ & 3 & 1.78\tabularnewline
         \hline
@@
 \begin{figure}
-    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs0_plot_fancy_dataspecs_0}
-    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs0_datanorm_plot_fancy_dataspecs_0}
-    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs1_plot_fancy_dataspecs_0}
-    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs1_datanorm_plot_fancy_dataspecs_0}
-    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs2_plot_fancy_dataspecs_0}
-    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs2_datanorm_plot_fancy_dataspecs_0}
+    \resizebox{0.5\textwidth}{!}{\input{plots/ATLASZHIGHMASS49FB.pgf}}
+    \resizebox{0.5\textwidth}{!}{\input{plots/CMSTTBARTOT.pgf}}
     \caption{Data prediction comparison plots.}

### 2020-04-06 paper/app-pineappl.tex
Rewrite PineAPPL section

\section{More technical details about \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}

\subsection{Installation}
\label{app:installation}

\subsection{Drell--Yan \texorpdfstring{$n$}{n}-tuple storage size}
\label{app:drell-yan-storage}

\subsection{Example program}
\label{app:example-program}

### 2020-04-06 paper/sec-pineappl.tex
Cleanup
Rewrite PineAPPL section

--- 2020-03-23 paper/pineappl.tex
@@
-In this paper we introduce a new library called \textsc{PineAPPL}, which is similar to \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}.
-Like to those two libraries, also \textsc{PineAPPL} bins phase-space weights in a PDF-independent manner, but it understands EW corrections, which are the main interest in this paper.
+\section{PDF-independent binning of phase-space weights with \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
+\label{sec:pineappl}
+
+In this paper we introduce a new library called \textsc{PineAPPL}, which bins phase-space weights independently from the chosen PDF set.
+The files produced in this way, generally called grids, can be used to quickly evaluate several observables and also to assess the impact of different PDF sets and their PDF uncertainties.
+Finally they are the main theoretical input to a PDF determination.
+In that sense \textsc{PineAPPL} is similar to \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}, but it also understands EW, which are the main interest in this paper.
 The following features distinguish it:
@@
 \item Support for arbitrary fixed-order calculations in powers of $\alpha$, $\alpha_\mathrm{s}$ or combinations thereof, e.g.\ in mixed QCD-EW corrections.
-Furthermore variations of the renormalization and factorization scale are supported, if needed.
-For each needed combination of the couplings and logarithms of renormalization and factorization scale a separate subgrid is created (see Sec.~\ref{sec:grid-representation} for more details);
-\item Support for all-order predictions coming from a resummation calculation or a photon-/parton-shower, which are important for some observables (see Sec.~\ref{sec:results}),
-\item A simple \textsc{C}-interface, with a wrapper for \textsc{Fortran} and \textsc{Python} (see App.~\ref{app:pineappl-interface} for examples and documentation), which is needed for Monte Carlos and programs to read and write \textsc{PineAPPL} grids.
-\textsc{PineAPPL} itself is written in Rust.
+Furthermore, variations of the renormalisation and factorisation scale are supported, if needed.
+For each needed combination of the couplings and logarithms of renormalisation and factorisation scale a separate subgrid is created (see section~\ref{sec:multi-coupling-expansion} for more details);
+\item Support for all-order predictions coming from a resummation calculation or a photon-/parton-shower, which are important for some observables (see section~\ref{sec:results}),
+\item A simple \textsc{C}-interface, with a wrapper for \textsc{Fortran} and \textsc{Python} (see appendix~\ref{app:example-program} for examples and documentation), which is needed for Monte Carlos and programs to read and write \textsc{PineAPPL} grids.
+\textsc{PineAPPL} itself is written in Rust (see appendix~\ref{app:installation} for installation instructions).
 \end{itemize}
 For \textsc{mg5\_aMC@NLO}~\cite{Alwall:2014hca,Frederix:2018nkq} the interfacing code is already implemented in the most recent version, which replaces the \textsc{aMCfast}~\cite{Bertone:2014zva} interface.
-The interfacing code for other Monte Carlo generators should be easy to write, see App.~\ref{app:pineappl-interface} for a small example program.
+The interfacing code for other Monte Carlo generators should be easy to write, see appendix~\ref{app:example-program} for a small example program.
 Finally, \textsc{PineAPPL} provides programs to convert \textsc{APPLgrids} and \textsc{fastNLO} tables to \textsc{PineAPPL} grids.
 
-\subsubsection{Cross sections in a multi-coupling expansion}
-The structure of the cross-section weights needed by \textsc{PineAPPL} follows the scheme outlined in
-Refs.~\cite{Frederix:2011ss, Bertone:2014zva}, embedded in a mixed-coupling expansion, see Ref.~\cite{Frederix:2018nkq} and Refs.CITE for
-specific examples. Starting
-from the latter, an observable $\Sigma(\alphas, \alpha)$ is written as
+\subsection{Cross sections in a multi-coupling expansion}
+\label{sec:multi-coupling-expansion}
+
+Fixed-order partonic cross sections supported by \textsc{PineAPPL} are expansions in powers of the strong coupling $\alpha_\mathrm{s}$, the electromagnetic coupling $\alpha$, and, if scale variations are desired, also in the logarithms of $\xi_\mathrm{R} = \mu_\mathrm{R}^2 / Q^2$ and $\xi_\mathrm{F} = \mu_\mathrm{F}^2 / Q^2$,
 \begin{equation}
-    \Sigma(\alphas, \alpha) = \alpha^c \alphas^{c_S} \sum_{a_S, a} \alphas^{a_S} \alpha^a \Sigma_{a_S, a}\,.
+\sigma_{ab} (x_1, x_2, Q^2; \xi_\mathrm{R}, \xi_\mathrm{F}) = \sum_{k,l,m,n} \alpha_\mathrm{s}^k \left( \xi_\mathrm{R} Q^2 \right) \log^m ( \xi_\mathrm{R} ) \log^n ( \xi_\mathrm{F} ) w_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2 \right) \text{,}
+\label{eq:expansion}
 \end{equation}
-$c$ and $c_S$ are process-dependent; the contributions $\Sigma_{a_S, a}$ are in general non-zero for $a_S, a \ge 0$ and $a_S + a > q$, where also $q$ is a process-dependent
-uantity. For example,
-for (stable) top-pair production, $c=c_S=0$ and $q=2$; for Drell-Yan production, $c=2$, $c_S=0$, and $q=0$. Terms
-with  $a_S + a = q + k$ correspond to different N$^k$LO contributions to $\Sigma$, usually
-labeled as N$^k$LO$_i$, $i =1,2, \ldots$, with $i=1$ assigned to the term with the largest power of $\alphas$. Given the hierarchy of the couplings,
-one expects that
+with the phase-space weights $w$ defined as
 \begin{equation}
- \textrm{N}^k\textrm{LO}_1 \gg \textrm{N}^k\textrm{LO}_2 \gg\ldots \, ,
+w_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2 \right) = \alpha^l \sigma_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2 \right) \text{.}
+\label{eq:phase-space-weight}
 \end{equation}
-however such a relation is not always respected, and sometimes blatantly violated~CITE.
+The left-hand side of eq.~\eqref{eq:expansion} shows the partonic cross section for a process $a + b \to X$, where the parton $a$ has momentum fraction $x_1$ and $b$ has momentum fraction $x_2$.
+The central value of the renormalisation and factorisation scale, $Q^2$, is treated as an independent variable; the parameters $\xi_\mathrm{R}$ and $\xi_\mathrm{F}$ allow varying the scales around the central value.
 
-Given the perturbative order (LO, NLO, \ldots), different weights $\cal W$, with different kinematics expressed by the set $\cal P$, enter the various
-terms $\Sigma_{a_S, a}$. One can write
+Eq.~\eqref{eq:phase-space-weight} contains the phase-space weights that we assume are calculated numerically, e.g.\ with a Monte Carlo generator, and then passed to \textsc{PineAPPL}, which will store this information either approximately or exactly, depending on the chosen format (see section~\ref{sec:grid-representation}).
+In particular, this phase-space weight is the product of
+\begin{itemize}
+\item the electroweak coupling $\alpha$, which we assume does not depend on either $x_1$, $x_2$, or $Q^2$ --- this is the case for the most prominent choices of $\alpha$, namely $\alpha (0)$, $\alpha (M_\mathrm{Z})$, and $\alpha_{G_\mu}$, but is not the case when $\alpha (\mu)$ is a (dynamic) scale-dependent coupling --- and
+\item the rest of the partonic cross section, denoted using a multi index $(k,l,m,n)$, where each index is the exponent of either a coupling or a logarithm.
+\end{itemize}
+Having stored eq.~\eqref{eq:phase-space-weight}, this allows \textsc{PineAPPL} to quickly calculate
 \begin{equation}
-    \Sigma_{a_S, a}= \sum_{l\in \mathcal P} f_1(x_1^{(l)},\mu_F^{(l)}) \,f_2(x_2^{(l)},\mu_F^{(l)}) \mathcal W^{(l)}_{a_S, a}
-    d \textrm{PS}\,,
+\sigma (\xi_\mathrm{R}, \xi_\mathrm{R}) = \sum_{a,b} \int_0^1 \mathrm{d} x_1 \int_0^1 \mathrm{d} x_2 \int_0^1 \mathrm{d} y \, f_a (x_1, \xi_\mathrm{F} Q^2) f_b (x_2, \xi_\mathrm{F} Q^2) \sigma_{ab} (x_1, x_2, Q^2) \text{.}
+\label{eq:pineappl-convolution}
 \end{equation}
-where we have introduced the parton distributions $f_{1,2}$ and the phase-space measure $d$PS.
-\begin{itemize}
-    \item At LO, $\mathcal P = \{B\}$, $B$ being the Born kinematics, and the weight structure is trivial,
+where $Q^2 = Q^2_\mathrm{min} + (Q^2_\mathrm{max} - Q^2_\mathrm{min}) y$, to obtain the hadronic cross sections for arbitrarily many PDF sets and scale variations.
+
+\subsubsection{Example}
+\label{sec:pineappl-example}
+
+To give an example of eq.~\eqref{eq:expansion}, the following shows Drell--Yan lepton-pair production up to terms at NLO:
 \begin{equation}
-        \mathcal W^{(l)}_{a_S, a} = {\mathcal W^{(l),0}_{a_S, a}}\,.
+\begin{split}
+\sigma_{ab} (\xi_\mathrm{R}, \xi_\mathrm{F})
+    &= \left[ \alpha^2 \sigma_{ab}^{(0,2,0,0)} \right] \\
+    &+ \alpha_\mathrm{s} \left( \xi_\mathrm{R} Q^2 \right) \left[ \alpha^2 \sigma_{ab}^{(1,2,0,0)} \right] + \alpha_\mathrm{s} \left( \xi_\mathrm{R} Q^2 \right) \log (\xi_\mathrm{F}) \left[ \alpha^2 \sigma_{ab}^{(1,2,0,1)} (Q^2) \right] \\
+    &+ \left[ \alpha^3 \sigma_{ab}^{(0,3,0,0)} \right] + \log (\xi_\mathrm{F}) \left[ \alpha^3 \sigma_{ab}^{(0,3,0,1)} (Q^2) \right] \text{.}
+\end{split}
 \end{equation}
-    \item At NLO, $\mathcal P = \{E, S, C, SC\}$ with, $E$ being the event (or resolved) kinematics, and $S$, $C$, $SC$ being
-        respectively the soft, collinear, and soft-collinear kinematics. The weight structure includes three terms at NLO:
-    \begin{equation}
-        \mathcal W^{(l)}_{a_S, a} = {{\mathcal W}^{(l),0}_{a_S, a}} +
-                                {\mathcal W^{(l),R}_{a_S, a}} \log\left(\frac{{\mu_R^{(l)}}^2}{Q^2}\right) +
-                                {\mathcal W^{(l),F}_{a_S, a}} \log\left(\frac{{\mu_F^{(l)}}^2}{Q^2}\right)
-    \end{equation}
-    where, besides the renormalisation and factorisation scales $\mu_{R,F}$, we have introduced the Ellis-Sexton scale $Q$
-\end{itemize}
+The first term with index $(0,2,0,0)$ is the LO term, the next line shows the NLO QCD correction, and the final line the NLO EW correction.
+Note that the dependence on the renormalisation scale is only indirectly through $\alpha_\mathrm{s}$, because the LO does not have any gluons in the initial or final state.
+Terms proportional to $\log (\xi_\mathrm{R})$ vanish, because they require an explicit dependence on the renormalisation scale, which only enters through counterterms with more than two gluons.
+
+\subsubsection{General characteristics}
+
+In general, we define as leading order all terms for which the sum of the coupling exponents in eq.~\eqref{eq:expansion} is smallest, i.e.\ $k + l = p$, where $p = \min (k+l)$.
+This number is process dependent and usually determined by the number of external particles.
+For many processes there is only one LO, but when a process has multiple quark lines, colourless (photons, \dots) and coloured particles (gluons, \ldots) can be exchanged between them, which allows for more than one leading order.
+To each leading order a higher-order correction with an additional power of $\alpha_\mathrm{s}$ and $\alpha$ can be calculated, which in general leads to at least two next-to-leading order corrections.
+Sometimes there are higher orders that cannot directly be understood as a correction to a leading order, e.g.\ $\mathrm{p} \mathrm{p} \to \ell \bar{\ell} + \mathrm{jet} + X$, which has one leading order, $\mathcal{O} (\alpha_\mathrm{s} \alpha^2)$, but three next-to-leading orders, one of which is $\mathcal{O} (\alpha^4)$~TODO.
+
+Due to typical size of the couplings $\alpha_\mathrm{s}^2 \sim \alpha$, it is naively expected that within the same order, i.e.\ for fixed $k + l$, terms with larger powers $\alpha_\mathrm{s}^k$ dominate over those with smaller powers; however, in practise this naive expectation is not always true due to dynamic effects.
+Some prominent examples are vector-boson scattering processes and TODO.
 
@@
 
-\subsection{Accuracy and performance}
-\label{sec:accuracy-and-performance}
+So far we did not explain how the phase space-weights, eq.~\ref{eq:phase-space-weight}, are represented.
+An obvious choice are $n$-tuples, which for each observable and for each combination $(a, b, k, l, m, n)$ saves a list of $N$ 4-tuples,
+\begin{equation}
+\left\{ x_1^i, x_2^i, Q^2_i, \frac{\mathrm{d}}{\mathrm{d} \phi_i} w^{(k,l,m,n)}_{ab} (x_1^i, x_2^i, Q^2_i) \right\}_{i=1}^N \text{.}
+\end{equation}
+The last element in the tuple is not an integrated cross section as in eq.~\eqref{eq:phase-space-weight}, but rather fully differential in the phase space $\phi$, evaluated at a specific phase-space point $\phi_i$.
+This is due to the fact that Monte Carlo integrators do not perform the phase space integrals and the convolution with the PDFs separately, but together at the same time.
 
-CS, MZ
+In case of $n$-tuples, the reconstruction of the integrated cross section, eq.~\eqref{eq:pineappl-convolution}, is very straightforward, for example for the central scale choice,
+\begin{equation}
+w_{ab}^{(k,l,m,n)} = \sum_{i=1}^N f_a (x_1^i, Q^2_i) f_b (x_2^i, Q^2) \alpha_\mathrm{s} (Q^2) \frac{\mathrm{d}}{\mathrm{d} \phi_i} w^{(k,l,m,n)}_{ab} (x_1^i, x_2^i, Q^2_i) \text{,} \label{eq:n-tuple-integration}
+\end{equation}
+given a proper normalization of the integral measures; this equation is the same approximation that a Monte Carlo integrator evaluates.
+For the full hadronic cross section it is only required to sum eq.~\eqref{eq:n-tuple-integration} over all open indices.
 
-How to integrate in MC codes, how this works in aMCblast (setup, MG5 version, urls).\\
-Appendix: how to create and fill grids, + simple code.
+This method has the clear advantage of being able to reproduce exactly the numerical value of the generator.
+However, the price to pay for is in large storage requirements.
+In the case of the NLO Drell--Yan (section~\ref{sec:pineappl-example}) the $n$-tuples need roughly \SI{7030}{\giga\byte} of storage (see appendix~\ref{app:drell-yan-storage} for an explanation of this number).
+
+A different choice is to build an interpolation grid, which basically partitions the space
+\begin{equation}
+H = [x_\mathrm{min},x_\mathrm{max}]^2 \times [Q^2_\mathrm{min}, Q^2_\mathrm{max}] \ni (x_1, x_2, Q^2)
+\end{equation}
+along each axis into a small numbers of bins, which allows one to approximately recover the result of the cross section.

### 2020-04-06 paper/sec-introduction.tex
Fix small mistakes in the introduction
- ran a spell checker over the introduction
- use siunitx for units
- Drell-Yan -> Drell--Yan (en dash instead of a hyphen)
- changes dictated by the JHEP author's manual:
  - 'section' instead of 'Sec.' or 'Sect.'
  - 'ref.' instead of 'Ref.'
  - no italicised latin abbreviations

@@
 accumulated data from an integrated luminosity of approximately 
-150~fb$^{-1}$~\cite{Mangano:2020icy}. This represents only a small fraction of 
-the anticipated 3000 fb$^{-1}$ that will eventually be recorded in the 
+\SI{150}{\per\femto\barn}~\cite{Mangano:2020icy}. This represents only a small fraction of
+the anticipated \SI{3000}{\per\femto\barn} that will eventually be recorded in the
 forthcoming twenty years of LHC operation. Nevertheless the statistical 
-uncertainty of the data has already shrunk to unprecedentedly small values,
-typically 1\% or less, a fact that will allow for precision tests of the 
+uncertainty of the data has already shrunk to unprecedented small values,
+typically \SI{1}{\percent} or less, a fact that will allow for precision tests of the
 Standard Model (SM) and for indirect searches of New Physics only if 
@@
 Monte Carlo generators~\cite{Gleisberg:2008ta,Alwall:2014hca,Bellm:2015jjp}
-(see also~\cite{Buckley:2011ms} for a review),
+(see also ref.~\cite{Buckley:2011ms} for a review),
 while an increasing number of next-to-next-to-leading order (NNLO) predictions 
 are becoming available for processes with various degrees of inclusiveness
-(see {\it e.g.}~\cite{Amoroso:2020lgh} and references therein). The computation
-of higher-order corrections in the Electroweak (EW) and mixed QCD+EW theory has 
+(see e.g.\ ref.~\cite{Amoroso:2020lgh} and references therein). The computation
+of higher-order corrections in the electroweak (EW) and mixed QCD+EW theory has
 witnessed a comparatively less comprehensive progress. Nevertheless frameworks 
@@
 determined~\cite{Schmidt:2015zda,Bertone:2017bme,Harland-Lang:2019pla}. 
-The resulting relative PDF uncertainy --- which accounts only for the 
+The resulting relative PDF uncertainty --- which accounts only for the
 uncertainty of the data and of residual methodology inefficiencies inherent to 
@@
 scale~\cite{Ball:2017nwa}. Theoretical uncertainties, possibly of comparable 
-size ({\it e.g.} from missing higher-order terms in the QCD perturbative 
+size (e.g.\ from missing higher-order terms in the QCD perturbative
 expansion), have started to be included in a PDF determination and represented 
@@
 Examples are the subtraction of background processes which should not be 
-considered as such ({\it e.g.} the $t$-channel photon-induced component in 
-neutral-current Drell-Yan, which is not a separate processes beyond the leading
-order) or of just a part of the EW effects ({\it e.g.} multiple-photon 
+considered as such (e.g.\ the $t$-channel photon-induced component in
+neutral-current Drell--Yan, which is not a separate processes beyond the leading
+order) or of just a part of the EW effects (e.g.\ multiple-photon
 radiation from light particles in the final state of neutral- or charged-current
-Drell-Yan, especially with electrons). Be that as it may, if EW effects are 
+Drell--Yan, especially with electrons). Be that as it may, if EW effects are
 systematically included in theoretical predictions, they should not be included 
@@
 fast interpolation grids. The library supports variations of the factorisation
-and renormalisations scales, resummation, and matching with a photon- and/or
+and renormalisation scales, resummation, and matching with a photon- and/or
 parton-shower. The library is included by default in 
@@
 
-The paper is organised as follows. In Sect.~\ref{sec:pineappl} we introduce
+The paper is organised as follows. In section~\ref{sec:pineappl} we introduce
 {\sc PineAPPL}, we describe its features, we illustrate its operation, and we
-assess its performance. In Sect.~\ref{sec:results}, by means of 
+assess its performance. In section~\ref{sec:results}, by means of
 {\sc mg5\_AMC@NLO} and {\sc PineAPPL}, we compute fast interpolation grids for 
 a representative set of data that is typically included in a fit of PDFs.
-In Sect.~\ref{sec:doublecounting} we use these results to formulate more 
+In section~\ref{sec:doublecounting} we use these results to formulate more
 comprehensively the second problem sketched above, the solution of which, 
 however, remains beyond the scope of the current work. We provide our
-conclusions and an outlook in Sect.~\ref{sec:conclusion}.
+conclusions and an outlook in section~\ref{sec:conclusion}.
 

### 2020-04-07 paper/sec-pineappl.tex
comments in multi-copling expansion

@@
 \label{sec:multi-coupling-expansion}
+{\bf MZ comments:}
+\begin{itemize}
+    \item I would prefer to keep the notation similar to the aMCfast paper, or at least to start with that, and then generalise it
+    \item drop eq 2.2, start already by 2.1 with a symmetric treatment of $\alpha$ and $\alpha_s$ (plus, the symbol $\sigma$ is overloaded there)
+    \item $Q$ is the Ellis-Sexton scale, a (unphysical) scale introduced to have all logs in the form $\log(\mu_R/F / Q)$, and hence to separate
+        the dependence of $\mu_R$ and $\mu_F$
+    \item the business of the different kinematics (born, resolved, counterterms, etc) is not mentioned at all
+    \item eq 2.1 assumes $\sigma_{ab}$ integrated over phase-space?
+\end{itemize}
+{\bf end MZ comments:}
 

### 2020-04-07 run.sh
Print one more digit of the per cent error

@@ -132,10 +132,10 @@ sed -e '1,/all bins:/d' \
 # compare the results from the APPLgrid and from mg5_aMC
 paste -d ' ' results.applgrid results.mg5_aMC | \
     awk 'function abs(x) { return x < 0.0 ? -x : x; }
-         BEGIN { print "-----------------------------------------------------------"
+         BEGIN { print "------------------------------------------------------------"
                  print "   APPLgrid       mg5_aMC   mg5_aMC unc.  sigmas  per cent"
-                 print "-----------------------------------------------------------" }
-         { printf "% e % e %e %7.2f %7.2f%%\n", $1, $2, $3, $3 != 0.0 ? abs($1-$2)/$3 : 0.0,
+                 print "------------------------------------------------------------" }
+         { printf "% e % e %e %7.2f %7.3f%%\n", $1, $2, $3, $3 != 0.0 ? abs($1-$2)/$3 : 0.0,
                                                 $2 != 0.0 ? abs($1-$2)/$2*100 : 0.0 }' | \
     tee results.log
 

### 2020-04-07 paper/sec-results.tex
Updated processes in Sect.3

@@
 - compute chi2\\
+
+ERN 7 Apr: there is consensus on the fact that we should present results for the
+following data sets:
+\begin{itemize}
+\item ATLAS high mass DY distributions, 7 TeV~\cite{Aad:2013iua} (CS);
+\item CMS 2D DY distributions, 7 TeV~\cite{Chatrchyan:2013tia} (CS);
+\item ATLAS top pair differential distributions ($m_{t\bar{t}}$ and $p_T^t$), 
+8 TeV~\cite{Aad:2015mbv} (ERN);
+\item CMS $Z$ $pT$ distributions, 13 TeV~\cite{Sirunyan:2019bzr} (ERN).
+\end{itemize}
+
+We agree not to display any LHCb measurement, given that they won't add
+further value to our discussion.
+Note added: we might also want to have a look at the ATLAS 2D and 3D DY 
+distributions, 8 TeV~\cite{Aad:2016zzw,Aaboud:2017ffb}, if time allows 
+us to do so.

### 2020-04-20 paper/sec-introduction.tex
Use the alphas macro

@@
 comparable size because, at the EW scale, the QCD and EW running couplings 
-become similar, $\alpha_S^2\sim \alpha$. If NNLO QCD corrections are included 
+become similar, $\alphas^2\sim \alpha$. If NNLO QCD corrections are included
 by default in PDF determinations, NLO EW and NLO EW+QCD corrections should be 

### 2020-04-20 paper/sec-pineappl.tex
Use the alphas macro

@@
 \begin{itemize}
-\item Support for arbitrary fixed-order calculations in powers of $\alpha$, $\alpha_\mathrm{s}$ or combinations thereof, e.g.\ in mixed QCD-EW corrections.
+\item Support for arbitrary fixed-order calculations in powers of $\alpha$, $\alphas$ or combinations thereof, e.g.\ in mixed QCD-EW corrections.
 Furthermore, variations of the renormalisation and factorisation scale are supported, if needed.
@@
     \item I would prefer to keep the notation similar to the aMCfast paper, or at least to start with that, and then generalise it
-    \item drop eq 2.2, start already by 2.1 with a symmetric treatment of $\alpha$ and $\alpha_s$ (plus, the symbol $\sigma$ is overloaded there)
+    \item drop eq 2.2, start already by 2.1 with a symmetric treatment of $\alpha$ and $\alphas$ (plus, the symbol $\sigma$ is overloaded there)
     \item $Q$ is the Ellis-Sexton scale, a (unphysical) scale introduced to have all logs in the form $\log(\mu_R/F / Q)$, and hence to separate
@@
 
-Fixed-order partonic cross sections supported by \textsc{PineAPPL} are expansions in powers of the strong coupling $\alpha_\mathrm{s}$, the electromagnetic coupling $\alpha$, and, if scale variations are desired, also in the logarithms of $\xi_\mathrm{R} = \mu_\mathrm{R}^2 / Q^2$ and $\xi_\mathrm{F} = \mu_\mathrm{F}^2 / Q^2$,
+Fixed-order partonic cross sections supported by \textsc{PineAPPL} are expansions in powers of the strong coupling $\alphas$, the electromagnetic coupling $\alpha$, and, if scale variations are desired, also in the logarithms of $\xi_\mathrm{R} = \mu_\mathrm{R}^2 / Q^2$ and $\xi_\mathrm{F} = \mu_\mathrm{F}^2 / Q^2$,
 \begin{equation}
-\sigma_{ab} (x_1, x_2, Q^2; \xi_\mathrm{R}, \xi_\mathrm{F}) = \sum_{k,l,m,n} \alpha_\mathrm{s}^k \left( \xi_\mathrm{R} Q^2 \right) \log^m ( \xi_\mathrm{R} ) \log^n ( \xi_\mathrm{F} ) w_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2 \right) \text{,}
+\sigma_{ab} (x_1, x_2, Q^2; \xi_\mathrm{R}, \xi_\mathrm{F}) = \sum_{k,l,m,n} \alphas^k \left( \xi_\mathrm{R} Q^2 \right) \log^m ( \xi_\mathrm{R} ) \log^n ( \xi_\mathrm{F} ) w_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2 \right) \text{,}
 \label{eq:expansion}
@@
     &= \left[ \alpha^2 \sigma_{ab}^{(0,2,0,0)} \right] \\
-    &+ \alpha_\mathrm{s} \left( \xi_\mathrm{R} Q^2 \right) \left[ \alpha^2 \sigma_{ab}^{(1,2,0,0)} \right] + \alpha_\mathrm{s} \left( \xi_\mathrm{R} Q^2 \right) \log (\xi_\mathrm{F}) \left[ \alpha^2 \sigma_{ab}^{(1,2,0,1)} (Q^2) \right] \\
+    &+ \alphas \left( \xi_\mathrm{R} Q^2 \right) \left[ \alpha^2 \sigma_{ab}^{(1,2,0,0)} \right] + \alphas \left( \xi_\mathrm{R} Q^2 \right) \log (\xi_\mathrm{F}) \left[ \alpha^2 \sigma_{ab}^{(1,2,0,1)} (Q^2) \right] \\
     &+ \left[ \alpha^3 \sigma_{ab}^{(0,3,0,0)} \right] + \log (\xi_\mathrm{F}) \left[ \alpha^3 \sigma_{ab}^{(0,3,0,1)} (Q^2) \right] \text{.}
@@
 The first term with index $(0,2,0,0)$ is the LO term, the next line shows the NLO QCD correction, and the final line the NLO EW correction.
-Note that the dependence on the renormalisation scale is only indirectly through $\alpha_\mathrm{s}$, because the LO does not have any gluons in the initial or final state.
+Note that the dependence on the renormalisation scale is only indirectly through $\alphas$, because the LO does not have any gluons in the initial or final state.
 Terms proportional to $\log (\xi_\mathrm{R})$ vanish, because they require an explicit dependence on the renormalisation scale, which only enters through counterterms with more than two gluons.
@@
 For many processes there is only one LO, but when a process has multiple quark lines, colourless (photons, \dots) and coloured particles (gluons, \ldots) can be exchanged between them, which allows for more than one leading order.
-To each leading order a higher-order correction with an additional power of $\alpha_\mathrm{s}$ and $\alpha$ can be calculated, which in general leads to at least two next-to-leading order corrections.
-Sometimes there are higher orders that cannot directly be understood as a correction to a leading order, e.g.\ $\mathrm{p} \mathrm{p} \to \ell \bar{\ell} + \mathrm{jet} + X$, which has one leading order, $\mathcal{O} (\alpha_\mathrm{s} \alpha^2)$, but three next-to-leading orders, one of which is $\mathcal{O} (\alpha^4)$~TODO.
+To each leading order a higher-order correction with an additional power of $\alphas$ and $\alpha$ can be calculated, which in general leads to at least two next-to-leading order corrections.
+Sometimes there are higher orders that cannot directly be understood as a correction to a leading order, e.g.\ $\mathrm{p} \mathrm{p} \to \ell \bar{\ell} + \mathrm{jet} + X$, which has one leading order, $\mathcal{O} (\alphas \alpha^2)$, but three next-to-leading orders, one of which is $\mathcal{O} (\alpha^4)$~TODO.
 
-Due to typical size of the couplings $\alpha_\mathrm{s}^2 \sim \alpha$, it is naively expected that within the same order, i.e.\ for fixed $k + l$, terms with larger powers $\alpha_\mathrm{s}^k$ dominate over those with smaller powers; however, in practise this naive expectation is not always true due to dynamic effects.
+Due to typical size of the couplings $\alphas^2 \sim \alpha$, it is naively expected that within the same order, i.e.\ for fixed $k + l$, terms with larger powers $\alphas^k$ dominate over those with smaller powers; however, in practise this naive expectation is not always true due to dynamic effects.
 Some prominent examples are vector-boson scattering processes and TODO.
@@
 \begin{equation}
-w_{ab}^{(k,l,m,n)} = \sum_{i=1}^N f_a (x_1^i, Q^2_i) f_b (x_2^i, Q^2) \alpha_\mathrm{s} (Q^2) \frac{\mathrm{d}}{\mathrm{d} \phi_i} w^{(k,l,m,n)}_{ab} (x_1^i, x_2^i, Q^2_i) \text{,} \label{eq:n-tuple-integration}
+w_{ab}^{(k,l,m,n)} = \sum_{i=1}^N f_a (x_1^i, Q^2_i) f_b (x_2^i, Q^2) \alphas (Q^2) \frac{\mathrm{d}}{\mathrm{d} \phi_i} w^{(k,l,m,n)}_{ab} (x_1^i, x_2^i, Q^2_i) \text{,} \label{eq:n-tuple-integration}
 \end{equation}

### 2020-04-20 paper/sec-doublecounting.tex
Intro - first draft
Add some small changes
- Drell-Yan -> Drell--Yan

@@
 \section{Double counting}
-Count von Count, ALL
-
-Explain the problem to experimentalists (the bee and the flower).\\
+\label{sec:doublecounting}
 
@@
 A common source of inconsistency is the subtraction of backgrounds processes which must not be considered as such. The typical example
-is neutral-current Drell-Yan, where the signal process is an opposite-sign lepton pair, which starts
+is neutral-current Drell--Yan, where the signal process is an opposite-sign lepton pair, which starts
 at $\mathcal O(\alpha^2)$. Because this process is usually thought
@@
 or just a part, for example deconvolving multiple-photon radiation from light particles in the final state. This applies mostly
-to processes such as neutral- or charge-current Drell-Yan, specially when electrons are considered. The problem lie in the fact that
+to processes such as neutral- or charge-current Drell--Yan, specially when electrons are considered. The problem lie in the fact that
  electrons, and to a lesser extent muons, tend to radiate photons, and such photons are typically not accounted

### 2020-04-27 paper/sec-pineappl.tex
Add some small changes
- Drell-Yan -> Drell--Yan
Clarify parts of the PineAPPL section
- implemented some of Marco's suggestions
- added more text

@@
 \textsc{PineAPPL} itself is written in Rust (see appendix~\ref{app:installation} for installation instructions).
+\item Superior efficiency for datasets with more then 100 observables.
 \end{itemize}
@@
     \item I would prefer to keep the notation similar to the aMCfast paper, or at least to start with that, and then generalise it
-    \item drop eq 2.2, start already by 2.1 with a symmetric treatment of $\alpha$ and $\alphas$ (plus, the symbol $\sigma$ is overloaded there)
-    \item $Q$ is the Ellis-Sexton scale, a (unphysical) scale introduced to have all logs in the form $\log(\mu_R/F / Q)$, and hence to separate
-        the dependence of $\mu_R$ and $\mu_F$
     \item the business of the different kinematics (born, resolved, counterterms, etc) is not mentioned at all
-    \item eq 2.1 assumes $\sigma_{ab}$ integrated over phase-space?
 \end{itemize}
@@
 
-Fixed-order partonic cross sections supported by \textsc{PineAPPL} are expansions in powers of the strong coupling $\alphas$, the electromagnetic coupling $\alpha$, and, if scale variations are desired, also in the logarithms of $\xi_\mathrm{R} = \mu_\mathrm{R}^2 / Q^2$ and $\xi_\mathrm{F} = \mu_\mathrm{F}^2 / Q^2$,
+Fixed-order partonic cross sections $a + b \to X$ supported by \textsc{PineAPPL} are expansions in powers of the strong coupling $\alphas$, the electromagnetic coupling $\alpha$, and the logarithms of $\xi_\mathrm{R} = \mu_\mathrm{R}^2 / Q^2$ and $\xi_\mathrm{F} = \mu_\mathrm{F}^2 / Q^2$,
 \begin{equation}
-\sigma_{ab} (x_1, x_2, Q^2; \xi_\mathrm{R}, \xi_\mathrm{F}) = \sum_{k,l,m,n} \alphas^k \left( \xi_\mathrm{R} Q^2 \right) \log^m ( \xi_\mathrm{R} ) \log^n ( \xi_\mathrm{F} ) w_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2 \right) \text{,}
+\sigma_{ab} (x_1, x_2, \phi) = \sum_{k,l,m,n} \alphas^k \left( \xi_\mathrm{R} Q^2 \right) \alpha^l \log^m ( \xi_\mathrm{R} ) \log^n ( \xi_\mathrm{F} ) w_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2, \phi \right) \text{.}
 \label{eq:expansion}
 \end{equation}
-with the phase-space weights $w$ defined as
+Above $Q^2$ denotes the Ellis--Sexton scale, which, if chosen dynamically, depends on the phase space $\phi$, $Q^2 = Q^2 (\phi)$.
+If this is the case, then we assume the fractions $\xi_\mathrm{R}$ and $\xi_\mathrm{F}$ to be constants of phase space, however.
+For the central scale choice, $\xi_\mathrm{R} = \xi_\mathrm{F} = 1$, the terms $m > 0$ and $n > 0$ are clearly not needed; they are only required if scale variations are desired.
+For example, a seven-point scale variation sets the fractions to following values,
 \begin{equation}
-w_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2 \right) = \alpha^l \sigma_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2 \right) \text{.}
-\label{eq:phase-space-weight}
+(\xi_\mathrm{R}, \xi_\mathrm{F}) \in \left\{ \bigl( 1, 1 \bigr), \bigl( \tfrac{1}{2}, \tfrac{1}{2} \bigr), \bigl( 2, 2 \bigr), \bigl( \tfrac{1}{2}, 1 \bigr), \bigl( 1, \tfrac{1}{2} \bigr), \bigl( 2, 1 \bigr), \bigl( 1, 2 \bigr) \right\} \text{,}
 \end{equation}
-The left-hand side of eq.~\eqref{eq:expansion} shows the partonic cross section for a process $a + b \to X$, where the parton $a$ has momentum fraction $x_1$ and $b$ has momentum fraction $x_2$.
-The central value of the renormalisation and factorisation scale, $Q^2$, is treated as an independent variable; the parameters $\xi_\mathrm{R}$ and $\xi_\mathrm{F}$ allow varying the scales around the central value.
+and estimates the perturbative QCD uncertainty---no EW uncertainty is covered by this method---as the envelope of the cross section evaluated with the previous values.
 
-Eq.~\eqref{eq:phase-space-weight} contains the phase-space weights that we assume are calculated numerically, e.g.\ with a Monte Carlo generator, and then passed to \textsc{PineAPPL}, which will store this information either approximately or exactly, depending on the chosen format (see section~\ref{sec:grid-representation}).
-In particular, this phase-space weight is the product of
-\begin{itemize}
-\item the electroweak coupling $\alpha$, which we assume does not depend on either $x_1$, $x_2$, or $Q^2$ --- this is the case for the most prominent choices of $\alpha$, namely $\alpha (0)$, $\alpha (M_\mathrm{Z})$, and $\alpha_{G_\mu}$, but is not the case when $\alpha (\mu)$ is a (dynamic) scale-dependent coupling --- and
-\item the rest of the partonic cross section, denoted using a multi index $(k,l,m,n)$, where each index is the exponent of either a coupling or a logarithm.
-\end{itemize}
-Having stored eq.~\eqref{eq:phase-space-weight}, this allows \textsc{PineAPPL} to quickly calculate
+As is clear from eq.~\eqref{eq:expansion}, the EW coupling $\alpha$ is assumed not to be a dynamically varying coupling, but instead a constant over phase space.
+This, however, includes the most common choices of the coupling, which are (not necessarily in this order), $\alpha (0)$, $\alpha (M_\mathrm{Z})$, and $\alpha_{G_\mu}$.
+
+The task that \textsc{PineAPPL} solves is to (approximately) reconstruct the function
 \begin{equation}
-\sigma (\xi_\mathrm{R}, \xi_\mathrm{R}) = \sum_{a,b} \int_0^1 \mathrm{d} x_1 \int_0^1 \mathrm{d} x_2 \int_0^1 \mathrm{d} y \, f_a (x_1, \xi_\mathrm{F} Q^2) f_b (x_2, \xi_\mathrm{F} Q^2) \sigma_{ab} (x_1, x_2, Q^2) \text{.}
+w_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2, \phi \right)
+\end{equation}
+from a set of $N$ function evaluations for specific phase-space points and momentum fractions
+\begin{equation}
+\left\{ \phi_i, x_1^{(i)}, x_2^{(i)}, Q^2_i \right\}_{i=1}^N \text{,}
+\end{equation}
+given by the Monte Carlo integrator.
+Using eq.~\eqref{eq:expansion} and
+\begin{equation}
+\sigma (\xi_\mathrm{R}, \xi_\mathrm{R}) = \sum_{a,b} \int_0^1 \mathrm{d} x_1 \int_0^1 \mathrm{d} x_2 \int \mathrm{d} \phi \, f_a (x_1, \xi_\mathrm{F} Q^2) f_b (x_2, \xi_\mathrm{F} Q^2) \sigma_{ab} (x_1, x_2, \phi) \text{,}
 \label{eq:pineappl-convolution}
 \end{equation}
-where $Q^2 = Q^2_\mathrm{min} + (Q^2_\mathrm{max} - Q^2_\mathrm{min}) y$, to obtain the hadronic cross sections for arbitrarily many PDF sets and scale variations.
+\textsc{PineAPPL} can calculate hadronic cross sections for arbitrarily many PDF sets and scale variations quickly.
 
-\subsubsection{Example}
+\subsubsection{Example: Drell--Yan lepton-pair production}
 \label{sec:pineappl-example}
 
-To give an example of eq.~\eqref{eq:expansion}, the following shows Drell--Yan lepton-pair production up to terms at NLO:
+To give an example of eq.~\eqref{eq:expansion}, the following shows Drell--Yan lepton-pair production up to terms at NLO (with arguments $x_1$, $x_2$, and $\phi$ suppressed for the phase-space weights):
 \begin{equation}
 \begin{split}
-\sigma_{ab} (\xi_\mathrm{R}, \xi_\mathrm{F})
-    &= \left[ \alpha^2 \sigma_{ab}^{(0,2,0,0)} \right] \\
-    &+ \alphas \left( \xi_\mathrm{R} Q^2 \right) \left[ \alpha^2 \sigma_{ab}^{(1,2,0,0)} \right] + \alphas \left( \xi_\mathrm{R} Q^2 \right) \log (\xi_\mathrm{F}) \left[ \alpha^2 \sigma_{ab}^{(1,2,0,1)} (Q^2) \right] \\
-    &+ \left[ \alpha^3 \sigma_{ab}^{(0,3,0,0)} \right] + \log (\xi_\mathrm{F}) \left[ \alpha^3 \sigma_{ab}^{(0,3,0,1)} (Q^2) \right] \text{.}
+\sigma_{ab}
+    &= \alpha^2 w_{ab}^{(0,2,0,0)} \\
+    &+ \alphas \left( \xi_\mathrm{R} Q^2 \right) \alpha^2 w_{ab}^{(1,2,0,0)} + \alphas \left( \xi_\mathrm{R} Q^2 \right) \log (\xi_\mathrm{F}) \alpha^2 w_{ab}^{(1,2,0,1)} (Q^2) \\
+    &+ \alpha^3 w_{ab}^{(0,3,0,0)} + \log (\xi_\mathrm{F}) \alpha^3 w_{ab}^{(0,3,0,1)} (Q^2) \text{.}
 \end{split}
 \end{equation}
-The first term with index $(0,2,0,0)$ is the LO term, the next line shows the NLO QCD correction, and the final line the NLO EW correction.
-Note that the dependence on the renormalisation scale is only indirectly through $\alphas$, because the LO does not have any gluons in the initial or final state.
-Terms proportional to $\log (\xi_\mathrm{R})$ vanish, because they require an explicit dependence on the renormalisation scale, which only enters through counterterms with more than two gluons.
+The first term with index $(0,2,0,0)$ is the LO term, the following line shows the NLO QCD correction, and the final line the NLO EW correction.
+Note that for all terms the dependence on the renormalisation scale is only indirectly through $\alphas$, because 1) higher-order terms in $\alpha$ never generate a renormalisation scale dependence (in the $\alpha$ schemes that are valid according to section~\ref{sec:multi-coupling-expansion}) and 2) higher-order QCD corrections only introduce an explicit renormalisation scale dependence in counterterms with vertices with more than two gluons.
+These terms, however, are not present in this process at NLO.
+Both NLOs, however, have a contribution from a collinear counterterm that depends on the factorisation scale.
+
+% TODO: add graphical representation of the multi-coupling expansion
+
+\subsubsection{Example: top-pair production}
+
+TODO
 
@@
 For many processes there is only one LO, but when a process has multiple quark lines, colourless (photons, \dots) and coloured particles (gluons, \ldots) can be exchanged between them, which allows for more than one leading order.
-To each leading order a higher-order correction with an additional power of $\alphas$ and $\alpha$ can be calculated, which in general leads to at least two next-to-leading order corrections.
+To each leading order a higher-order correction with an additional power of $\alphas$ or $\alpha$ can be calculated, which in general leads to at least two next-to-leading order corrections.
 Sometimes there are higher orders that cannot directly be understood as a correction to a leading order, e.g.\ $\mathrm{p} \mathrm{p} \to \ell \bar{\ell} + \mathrm{jet} + X$, which has one leading order, $\mathcal{O} (\alphas \alpha^2)$, but three next-to-leading orders, one of which is $\mathcal{O} (\alpha^4)$~TODO.
@@
 
-So far we did not explain how the phase space-weights, eq.~\ref{eq:phase-space-weight}, are represented.
-An obvious choice are $n$-tuples, which for each observable and for each combination $(a, b, k, l, m, n)$ saves a list of $N$ 4-tuples,
+In this subsection we explain the details of how the phase-space weights $w_{ab}$ in eq.~\ref{eq:expansion} are represented.
+
+\subsubsection{4-tuples}
+
+One very simple representation are 4-tuples, which for each phase-space point and combination $(a, b, k, l, m, n)$ saves a list of the parton fractions $x_1$ and $x_2$, the scale $Q^2$, and the phase-space weight $w$; this is sufficient for a total cross section.
+If, however, a differential cross section shall be reconstructed, we first need to generalise eq.~\eqref{eq:expansion}:
 \begin{equation}
-\left\{ x_1^i, x_2^i, Q^2_i, \frac{\mathrm{d}}{\mathrm{d} \phi_i} w^{(k,l,m,n)}_{ab} (x_1^i, x_2^i, Q^2_i) \right\}_{i=1}^N \text{.}
+\frac{\mathrm{d} \sigma_{ab}}{\mathrm{d} \mathcal{O}} (x_1, x_2, \phi, \mathcal{O}) = \sum_{k,l,m,n} \alphas^k \left( \xi_\mathrm{R} Q^2 \right) \alpha^l \log^m ( \xi_\mathrm{R} ) \log^n ( \xi_\mathrm{F} ) \frac{\mathrm{d} w_{ab}^{(k,l,m,n)}}{\mathrm{d} \mathcal{O}} \left( x_1, x_2, Q^2, \phi \right) \\
 \end{equation}
-The last element in the tuple is not an integrated cross section as in eq.~\eqref{eq:phase-space-weight}, but rather fully differential in the phase space $\phi$, evaluated at a specific phase-space point $\phi_i$.
-This is due to the fact that Monte Carlo integrators do not perform the phase space integrals and the convolution with the PDFs separately, but together at the same time.
+where, because of a finite number of phase-space points given by the Monte Carlo integrator, we numerically approximates the derivative as
+\begin{equation}
+\begin{split}
+\frac{\mathrm{d} w_{ab}^{(k,l,m,n)}}{\mathrm{d} \mathcal{O}} \left( x_1, x_2, Q^2, \phi \right) &\approx \sum_{o=1}^M \frac{\Theta (\mathcal{O}_o^\mathrm{min} \le \mathcal{O} < \mathcal{O}_o^\mathrm{max})}{\mathcal{O}_o^\mathrm{max} - \mathcal{O}_o^\mathrm{min}} w_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2, \phi \right) \\
+&= \sum_{o=1}^M w_{ab}^{(k,l,m,n,o)} \left( x_1, x_2, Q^2, \phi, \mathcal{O} \right) \text{,}
+\end{split}
+\end{equation}
+using $M$ discrete bins with boundaries $\{ \mathcal{O}_o^\mathrm{min}, \mathcal{O}_o^\mathrm{max} \}_{o=1}^M$.
 
-In case of $n$-tuples, the reconstruction of the integrated cross section, eq.~\eqref{eq:pineappl-convolution}, is very straightforward, for example for the central scale choice,
+This means that for each bin $o$ of the observable $\mathcal{O}$ and therefore for each combination $(a,b,k,l,m,n,o)$ we save the following 4-tuples:
 \begin{equation}
-w_{ab}^{(k,l,m,n)} = \sum_{i=1}^N f_a (x_1^i, Q^2_i) f_b (x_2^i, Q^2) \alphas (Q^2) \frac{\mathrm{d}}{\mathrm{d} \phi_i} w^{(k,l,m,n)}_{ab} (x_1^i, x_2^i, Q^2_i) \text{,} \label{eq:n-tuple-integration}
+\left\{ x_1^i, x_2^i, Q^2_i, w^{(k,l,m,n,o)}_{ab} (x_1^i, x_2^i, Q^2_i, \phi_i, \mathcal{O}_i) \right\}_{i=1}^N \text{,} \label{eq:four-tuples}
 \end{equation}
-given a proper normalization of the integral measures; this equation is the same approximation that a Monte Carlo integrator evaluates.
-For the full hadronic cross section it is only required to sum eq.~\eqref{eq:n-tuple-integration} over all open indices.
+The reconstruction of the differential cross section for bin $o$ is then straightforwardly done by multiplying the phase-space weights $w$ with PDFs evaluated with the correct arguments given in the 4-tuple and summing over all indices $a$, $b$, $k$, $l$, $m$, $n$, and $i$.
 
-This method has the clear advantage of being able to reproduce exactly the numerical value of the generator.
-However, the price to pay for is in large storage requirements.
-In the case of the NLO Drell--Yan (section~\ref{sec:pineappl-example}) the $n$-tuples need roughly \SI{7030}{\giga\byte} of storage (see appendix~\ref{app:drell-yan-storage} for an explanation of this number).
+Using 4-tuples has the clear advantage of being very easy to implement and therefore also easy to test.
+Furthermore, they reproduce the exact numerical value that is also calculated by the Monte Carlo integrator.
+However, the price one has to pay is the size of the 4-tuples, which scales linearly with the number of phase-space weights $N$.
+Because the uncertainties of Monte Carlo integrators shrink as $1/\sqrt{N}$, this typically means \numrange{e7}{e9} phase-space points.
+In the case of the NLO Drell--Yan (section~\ref{sec:pineappl-example}) the 4-tuples need roughly TODO~\si{\giga\byte} of storage (see appendix~\ref{app:drell-yan-storage} for an explanation of this number).
+With increasing size also the speed of the convolution degrades, because it basically becomes bound by the speed with which the 4-tuples can be read from disk.
 
-A different choice is to build an interpolation grid, which basically partitions the space
+\subsubsection{Interpolation grids}
+
+A different choice partition the $(x_1, x_2, Q^2)$ space,
 \begin{equation}
@@
 \end{equation}
-along each axis into a small numbers of bins, which allows one to approximately recover the result of the cross section.
+along each axis into a small numbers of bins and to insert the phase-space weights $w$ into the corresponding discrete bin.
+This method is straightforward, but given a finite number of bins this usually yields a bad approximation for the cross section.
+This can be remedied by increasing the number of bins, which would also increase the space requirements of the grid.
+There are, however, more refined methods, which keep the number of bins constant, while improving the quality of the approximation: Interpolation grids.
+
+TODO

### 2020-04-27 paper/sec-doublecounting.tex
Fix small Latex mistakes

@@
 $\gamma \gamma \to \ell^+ \ell^-$ in the $t$ channel, is considered as a different process, and it 
-subtracted (see e.g. Refs.~\cite{}). However, such a distinction cannot be physically
-justified beyond LO. Indeed, at $\mathcal O(\alpha^3)$, the reaction $q \gamma \to \ell^+ \ell^- q$ becomes possible, which
+subtracted (see e.g.\ refs.~\cite{}). However, such a distinction cannot be physically
+justified beyond LO\@. Indeed, at $\mathcal O(\alpha^3)$, the reaction $q \gamma \to \ell^+ \ell^- q$ becomes possible, which
 includes both kind of topologies. {\bf MZ add Feynman diags} The problem here derives from the fact 
 that identifing a process based only on its 
-initial-state partons is plain wrong in quantum mechanics. While this fact is well established in QCD --nobody would ever 
-consider to ``subtract'' the gluon-initiated contribution to top-pair production in top analyses-- seemingly it is not so
+initial-state partons is plain wrong in quantum mechanics. While this fact is well established in QCD---nobody would ever
+consider to \enquote{subtract} the gluon-initiated contribution to top-pair production in top analyses---seemingly it is not so
 when EW corrections are considered.
@@
 for in hard matrix-elements. Thus, leptons that are measured in the detector are less energetic, and this fact is compensated for
-by undoing the photon shower before publishing data, which are referred to e.g. as \emph{Born-level electrons}~\cite{}. There are 
+by undoing the photon shower before publishing data, which are referred to e.g.\ as \emph{Born-level electrons}~\cite{}. There are
 at least two 

### 2020-04-27 paper/sec-introduction.tex
Fix small Latex mistakes

@@
 determined~\cite{Schmidt:2015zda,Bertone:2017bme,Harland-Lang:2019pla}. 
-The resulting relative PDF uncertainty --- which accounts only for the
+The resulting relative PDF uncertainty---which accounts only for the
 uncertainty of the data and of residual methodology inefficiencies inherent to 
-each PDF determination --- can be as low as 1\% at the EW 
+each PDF determination---can be as low as 1\% at the EW
 scale~\cite{Ball:2017nwa}. Theoretical uncertainties, possibly of comparable 
@@
 phase-space regions associated with large mass scales (roughly of the order
-of the TeV), where several LHC data sets ({\it e.g.} $Z$ boson transverse 
+of the \si{\tera\electronvolt}), where several LHC data sets (e.g.\ $Z$ boson transverse
 momentum distributions) enter both the determination of PDFs and the search
@@
 be performed a large number of times. While two default formats exist for
-these grids, {\sc APPLgrid}~\cite{Carli:2010rw} and 
-{\sc fastNLO}~\cite{Kluge:2006xs}, none of them supports the inclusion of EW
+these grids, \textsc{APPLgrid}~\cite{Carli:2010rw} and
+\textsc{fastNLO}~\cite{Kluge:2006xs}, none of them supports the inclusion of EW
 corrections nor the interface to a Monte Carlo generator accurate to 
-NLO QED+EW. Second, a problem of consistency: the way in which EW effects may
+NLO QED+EW\@. Second, a problem of consistency: the way in which EW effects may
 (or may not) be folded into the data varies across different experimental 
@@
 In this paper we address the first of these two problems. Specifically, 
-we develop {\sc PineAPPL}, a new library that provides a direct interface 
+we develop \textsc{PineAPPL}, a new library that provides a direct interface
 from parton-level Monte Carlo event generators accurate up to NLO QCD+EW to
@@
 parton-shower. The library is included by default in 
-{\sc MadGraph5\_aMC@NLO} ({\sc mg5\_aMC@NLO} henceforth) within which it has 
+\textsc{MadGraph5\_aMC@NLO} (\textsc{mg5\_aMC@NLO} henceforth) within which it has
 been designed and tested. However, it is suitable for use as a plugin in any 
 Monte Carlo generator that supports NLO QCD+EW computations, such as 
-{\sc SHERPA}~\cite{Biedermann:2017yoi}. In this respect, {\sc PineAPPL}
-supersedes the {\sc aMCfast} interface~\cite{Bertone:2014zva} and complements
-the {\sc MCgrid} interface~\cite{DelDebbio:2013kxa,Bothmann:2015dba}.
+\textsc{SHERPA}~\cite{Biedermann:2017yoi}. In this respect, \textsc{PineAPPL}
+supersedes the \textsc{aMCfast} interface~\cite{Bertone:2014zva} and complements
+the \textsc{MCgrid} interface~\cite{DelDebbio:2013kxa,Bothmann:2015dba}.
 
 The paper is organised as follows. In section~\ref{sec:pineappl} we introduce
-{\sc PineAPPL}, we describe its features, we illustrate its operation, and we
+\textsc{PineAPPL}, we describe its features, we illustrate its operation, and we
 assess its performance. In section~\ref{sec:results}, by means of
-{\sc mg5\_AMC@NLO} and {\sc PineAPPL}, we compute fast interpolation grids for 
+\textsc{mg5\_AMC@NLO} and \textsc{PineAPPL}, we compute fast interpolation grids for
 a representative set of data that is typically included in a fit of PDFs.

### 2020-04-27 paper/sec-doublecounting.tex
Fix two spelling mistakes

@@
 includes both kind of topologies. {\bf MZ add Feynman diags} The problem here derives from the fact 
-that identifing a process based only on its 
+that identifying a process based only on its
 initial-state partons is plain wrong in quantum mechanics. While this fact is well established in QCD---nobody would ever

### 2020-04-27 paper/sec-introduction.tex
Fix two spelling mistakes

@@
 corrections nor the interface to a Monte Carlo generator accurate to 
-NLO QED+EW\@. Second, a problem of consistency: the way in which EW effects may
+NLO QCD+EW\@. Second, a problem of consistency: the way in which EW effects may
 (or may not) be folded into the data varies across different experimental 

### 2020-06-09 paper/sec-doublecounting.tex
Add CS's notes for the double-counting section

@@
 muons, on the same footing as their electron counterpart.
+
+\clearpage
+\noindent
+\textbf{Notes from CS}:
+\begin{itemize}
+\item overall we should also point out the positive (rewrite the last part of this section a bit): for leptonic observables there always seems to be a pre-/post-FSR dataset with born/dressed leptons
+\begin{itemize}
+\item is this really the case?
+\item is this also the case for non-leptonic observables? Specifically: Do ATLAS/CMS subtract photon radiation for observables of jet, top, or any other reconstructed objects (for instance: Z pT)?
+\end{itemize}
+\item double-photon initiated processes:
+\begin{itemize}
+\item how do they subtract it exactly (one analysis uses a concrete PDF set and subtracts the theory prediction; point out first how they do it, then that this is not a good idea, even if it would make sense: mixing theory predictions with measurements)
+\item explain why they do it and point that this is not good
+\end{itemize}
+\item stress subtraction of \emph{irreducible} backgrounds
+\end{itemize}

### 2020-06-12 paper/sec-doublecounting.tex
additions in dobule counting section

@@
 
-A common source of inconsistency is the subtraction of backgrounds processes which must not be considered as such. The typical example
+A common source of inconsistency is the subtraction of (irreducible) background processes which must not be considered as such. The typical example
 is neutral-current Drell--Yan, where the signal process is an opposite-sign lepton pair, which starts
@@
 $\gamma \gamma \to \ell^+ \ell^-$ in the $t$ channel, is considered as a different process, and it 
-subtracted (see e.g.\ refs.~\cite{}). However, such a distinction cannot be physically
+subtracted, possibly evaluated with different parton densities and/or including (unphysical) higher-order 
+corrections. For example, in Ref.~\cite{Aaboud:2017ffb}, one reads:
+\begin{quote}
+The photon-induced process, $\gamma\gamma \to \ell \ell$, is simulated at LO using Pythia 8 
+and the MRST2004qed PDF set~\cite{Martin:2004dh}. The expected yield for this process also accounts for 
+NLO QED/EW corrections from references~\cite{Bardin:2012jk,Bondarenko:2013nu}, which decrease the yield by approximately 30\%.
+\end{quote}
+Such a distinction cannot be physically
 justified beyond LO\@. Indeed, at $\mathcal O(\alpha^3)$, the reaction $q \gamma \to \ell^+ \ell^- q$ becomes possible, which
-includes both kind of topologies. {\bf MZ add Feynman diags} The problem here derives from the fact 
+includes both kind of topologies. {\bf MZ add Feynman diags}
+
+{\bf It looks like CMS does things in a pretty consistent manner~\cite{Sirunyan:2018owv, CMS:2014jea}. Shall we mention? We should
+not make ATLAS appear as the bad guys, and CMS as the good ones.} The problem here derives from the fact 
 that identifying a process based only on its

### 2020-06-12 paper/sec-doublecounting.tex
added few refs

@@
 subtracted, possibly evaluated with different parton densities and/or including (unphysical) higher-order 
-corrections. For example, in Ref.~\cite{Aaboud:2017ffb}, one reads:
+corrections. For example, in Refs.~\cite{Aaboud:2017ffb,Aad:2016zzw}, one reads:
 \begin{quote}
@@
 \end{quote}
-Such a distinction cannot be physically
+A similar statement appears also in an older analysis~\cite{Aad:2013iua}. Such a distinction cannot be physically
 justified beyond LO\@. Indeed, at $\mathcal O(\alpha^3)$, the reaction $q \gamma \to \ell^+ \ell^- q$ becomes possible, which

### 2020-06-22 paper/sec-pineappl.tex
Fix small Latex mistakes
Improve section 2

@@
 In this paper we introduce a new library called \textsc{PineAPPL}, which bins phase-space weights independently from the chosen PDF set.
-The files produced in this way, generally called grids, can be used to quickly evaluate several observables and also to assess the impact of different PDF sets and their PDF uncertainties.
-Finally they are the main theoretical input to a PDF determination.
-In that sense \textsc{PineAPPL} is similar to \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}, but it also understands EW, which are the main interest in this paper.
-The following features distinguish it:
+The resulting files, generally called grids, can be used to quickly convolute the observables with multiple PDF sets.
+This has at least two applications:
 \begin{itemize}
-\item Support for arbitrary fixed-order calculations in powers of $\alpha$, $\alphas$ or combinations thereof, e.g.\ in mixed QCD-EW corrections.
+\item the study of the dependence of observables on PDF sets; e.g.\ to determine how the central predictions of observables change when changing the PDF set, the PDF uncertainties for different PDF set, etc.\ and
+\item the determination of PDF sets themselves; the grids together with the corresponding experimental data are the main inputs for a PDF fit.
+\end{itemize}
+This puts \textsc{PineAPPL} in the same category than \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}.
+What sets \textsc{PineAPPL} apart from the other libraries is its support for electroweak (EW) predictions/corrections, which are the main interest in this paper.
+More specifically, the following features are supported:
+\begin{itemize}
+\item Support for arbitrary fixed-order calculations in powers of $\alpha$, $\alphas$ or combinations thereof, in particular also mixed QCD-EW corrections.
 Furthermore, variations of the renormalisation and factorisation scale are supported, if needed.
 For each needed combination of the couplings and logarithms of renormalisation and factorisation scale a separate subgrid is created (see section~\ref{sec:multi-coupling-expansion} for more details);
-\item Support for all-order predictions coming from a resummation calculation or a photon-/parton-shower, which are important for some observables (see section~\ref{sec:results}),
-\item A simple \textsc{C}-interface, with a wrapper for \textsc{Fortran} and \textsc{Python} (see appendix~\ref{app:example-program} for examples and documentation), which is needed for Monte Carlos and programs to read and write \textsc{PineAPPL} grids.
+%\item Support for all-order predictions coming from a resummation calculation or a photon-/parton-shower, which are important for some observables (see section~\ref{sec:results}),
+\item A simple \textsc{C}-interface (see appendix~\ref{app:example-program} for examples and documentation), which is needed for Monte Carlos and programs to read and write \textsc{PineAPPL} grids.
 \textsc{PineAPPL} itself is written in Rust (see appendix~\ref{app:installation} for installation instructions).
-\item Superior efficiency for datasets with more then 100 observables.
+\item Another interface is the command-line program \texttt{pineappl}, which allows users of the generated grids to perform convolutions of the grid with PDF sets.
+Additionally, it can print further information on how the corresponding luminosity function is constructed, which perturbative orders are stored, the relative size of each correction, the relative size of each partonic channel, etc.
+%\item Possibility to import \textsc{APPLgrids} and \textsc{fastNLO} tables.
+\item Superior efficiency and moderate memory requirements for differential distributions with more then 100 bins.
 \end{itemize}
-For \textsc{mg5\_aMC@NLO}~\cite{Alwall:2014hca,Frederix:2018nkq} the interfacing code is already implemented in the most recent version, which replaces the \textsc{aMCfast}~\cite{Bertone:2014zva} interface.
+For \textsc{mg5\_aMC@NLO}~\cite{Alwall:2014hca,Frederix:2018nkq} the interfacing code is already implemented in a separate version, which is intended to replace the \textsc{aMCfast}~\cite{Bertone:2014zva} interface.
 The interfacing code for other Monte Carlo generators should be easy to write, see appendix~\ref{app:example-program} for a small example program.
-Finally, \textsc{PineAPPL} provides programs to convert \textsc{APPLgrids} and \textsc{fastNLO} tables to \textsc{PineAPPL} grids.
 
@@
 For the central scale choice, $\xi_\mathrm{R} = \xi_\mathrm{F} = 1$, the terms $m > 0$ and $n > 0$ are clearly not needed; they are only required if scale variations are desired.
-For example, a seven-point scale variation sets the fractions to following values,
+For example, a seven-point scale variation sets the fractions to the following values,
 \begin{equation}
@@
 Note that for all terms the dependence on the renormalisation scale is only indirectly through $\alphas$, because 1) higher-order terms in $\alpha$ never generate a renormalisation scale dependence (in the $\alpha$ schemes that are valid according to section~\ref{sec:multi-coupling-expansion}) and 2) higher-order QCD corrections only introduce an explicit renormalisation scale dependence in counterterms with vertices with more than two gluons.
-These terms, however, are not present in this process at NLO.
+These terms, however, are not present in this process at NLO\@.
 Both NLOs, however, have a contribution from a collinear counterterm that depends on the factorisation scale.
@@
 
-Due to typical size of the couplings $\alphas^2 \sim \alpha$, it is naively expected that within the same order, i.e.\ for fixed $k + l$, terms with larger powers $\alphas^k$ dominate over those with smaller powers; however, in practise this naive expectation is not always true due to dynamic effects.
+Due to the typical sizes of the couplings $\alphas^2 \sim \alpha$, it is naively expected that within the same order, i.e.\ for fixed $k + l$, terms with larger powers $\alphas^k$ dominate over those with smaller powers; however, in practise this naive expectation is not always true due to dynamic effects.
 Some prominent examples are vector-boson scattering processes and TODO.
@@
 
-A different choice partition the $(x_1, x_2, Q^2)$ space,
+A different choice partitions the $(x_1, x_2, Q^2)$ space,
 \begin{equation}

### 2020-06-23 paper/sec-pineappl.tex
Add more content to section 2

@@
 \item Support for arbitrary fixed-order calculations in powers of $\alpha$, $\alphas$ or combinations thereof, in particular also mixed QCD-EW corrections.
-Furthermore, variations of the renormalisation and factorisation scale are supported, if needed.
+Electroweak corrections require the inclusion of photon-initiated contributions, which are supported.
+In fact \textsc{PineAPPL} supports arbitrary initial-state combinations, for example leptonic initial states, for which PDFs have recently calculated~\cite{}.
+\item Variations of the renormalisation and factorisation scale are supported, if needed.
 For each needed combination of the couplings and logarithms of renormalisation and factorisation scale a separate subgrid is created (see section~\ref{sec:multi-coupling-expansion} for more details);
@@
 Fixed-order partonic cross sections $a + b \to X$ supported by \textsc{PineAPPL} are expansions in powers of the strong coupling $\alphas$, the electromagnetic coupling $\alpha$, and the logarithms of $\xi_\mathrm{R} = \mu_\mathrm{R}^2 / Q^2$ and $\xi_\mathrm{F} = \mu_\mathrm{F}^2 / Q^2$,
+\begin{multline}
+\frac{\mathrm{d} \sigma_{ab}}{\mathrm{d} \mathcal{O}} (x_1, x_2, \mathcal{O}, \xi_\mathrm{R}, \xi_\mathrm{F}) \\
+= \sum_{k,l,m,n} \alphas^k \left( \xi_\mathrm{R} Q^2 \right) \alpha^l \log^m ( \xi_\mathrm{R} ) \log^n ( \xi_\mathrm{F} ) W_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2, \mathcal{O} \right) \text{.}
+\label{eq:expansion}
+\end{multline}
+The above cross section is differential w.r.t.\ the observable $\mathcal{O}$, which, in general, is a function of phase space and subject to the usual conditions (soft- and collinear safety, \ldots).
+In experiments, but also for many calculations where the phase-space integration is performed using a Monte Carlo integrator, finite statistics does not allow us to reconstruct the exact dependence of the cross section on the observable $\mathcal{O}$.
+Instead, it it sufficient to approximate the derivative using a piecewise-constant function,
 \begin{equation}
-\sigma_{ab} (x_1, x_2, \phi) = \sum_{k,l,m,n} \alphas^k \left( \xi_\mathrm{R} Q^2 \right) \alpha^l \log^m ( \xi_\mathrm{R} ) \log^n ( \xi_\mathrm{F} ) w_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2, \phi \right) \text{.}
-\label{eq:expansion}
+W_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2, \mathcal{O} \right) \approx \sum_{o=1}^M \frac{\Theta (\mathcal{O}_o^\mathrm{min} \le \mathcal{O} < \mathcal{O}_o^\mathrm{max})}{\mathcal{O}_o^\mathrm{max} - \mathcal{O}_o^\mathrm{min}} w_{ab}^{(k,l,m,n,o)} \left( x_1, x_2, Q^2 \right) \text{,}
 \end{equation}
-Above $Q^2$ denotes the Ellis--Sexton scale, which, if chosen dynamically, depends on the phase space $\phi$, $Q^2 = Q^2 (\phi)$.
-If this is the case, then we assume the fractions $\xi_\mathrm{R}$ and $\xi_\mathrm{F}$ to be constants of phase space, however.
-For the central scale choice, $\xi_\mathrm{R} = \xi_\mathrm{F} = 1$, the terms $m > 0$ and $n > 0$ are clearly not needed; they are only required if scale variations are desired.
-For example, a seven-point scale variation sets the fractions to the following values,
+which uses $M$ bins with limits $\{ \mathcal{O}_o^\mathrm{min}, \mathcal{O}_o^\mathrm{max} \}_{o=1}^M$ to partition a finite range of the observable,
 \begin{equation}
-(\xi_\mathrm{R}, \xi_\mathrm{F}) \in \left\{ \bigl( 1, 1 \bigr), \bigl( \tfrac{1}{2}, \tfrac{1}{2} \bigr), \bigl( 2, 2 \bigr), \bigl( \tfrac{1}{2}, 1 \bigr), \bigl( 1, \tfrac{1}{2} \bigr), \bigl( 2, 1 \bigr), \bigl( 1, 2 \bigr) \right\} \text{,}
+\mathcal{O}_0^\mathrm{min} < \mathcal{O}_0^\mathrm{max} = \mathcal{O}_1^\mathrm{min} < \ldots < \mathcal{O}_{M-1}^\mathrm{max} = \mathcal{O}_M^\mathrm{min} < \mathcal{O}_M^\mathrm{max} \text{.}
 \end{equation}
-and estimates the perturbative QCD uncertainty---no EW uncertainty is covered by this method---as the envelope of the cross section evaluated with the previous values.
+
+If chosen dynamically the Ellis--Sexton scale $Q^2$ depends on the phase space as well, but we assume the fractions $\xi_\mathrm{R}$ and $\xi_\mathrm{F}$ to be constants of phase space in any case.
+This allows variations around the central scale choice $\xi_\mathrm{R} = \xi_\mathrm{F} = 1$, but not changing the scale arbitrarily.
+The terms with powers $m > 0$ and $n > 0$ vanish for the central scale choice and are only required for variations of the factorisation and renormalisation scales.
+To estimate the perturbative QCD uncertainty---no EW uncertainty is covered by this method---one typically uses a 7-point scale variation, which evaluates the cross section using the following values,
+\begin{equation}
+(\xi_\mathrm{R}, \xi_\mathrm{F}) \in \left\{ \bigl( 1, 1 \bigr), \bigl( \tfrac{1}{2}, \tfrac{1}{2} \bigr), \bigl( 2, 2 \bigr), \bigl( \tfrac{1}{2}, 1 \bigr), \bigl( 1, \tfrac{1}{2} \bigr), \bigl( 2, 1 \bigr), \bigl( 1, 2 \bigr) \right\} \text{.}
+\end{equation}
+The (asymmetric) uncertainties are the given as the minimum and maximum value (the envelope), measured from the central value $(1, 1)$.
 
@@
 
-The task that \textsc{PineAPPL} solves is to (approximately) reconstruct the function
+The task that \textsc{PineAPPL} solves can now be described: Approximately reconstruct the functions
 \begin{equation}
-w_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2, \phi \right)
+w_{ab}^{(k,l,m,n,o)} \left( x_1, x_2, Q^2 \right)
 \end{equation}
-from a set of $N$ function evaluations for specific phase-space points and momentum fractions
+from a set of $N$ function evaluations for specific momentum fractions, scales, and values of the observable:
 \begin{equation}
-\left\{ \phi_i, x_1^{(i)}, x_2^{(i)}, Q^2_i \right\}_{i=1}^N \text{,}
+\left\{ x_1^{(i)}, x_2^{(i)}, Q^2_i, \mathcal{O}_i \right\}_{i=1}^N \text{,}
 \end{equation}
@@
 Using eq.~\eqref{eq:expansion} and
-\begin{equation}
-\sigma (\xi_\mathrm{R}, \xi_\mathrm{R}) = \sum_{a,b} \int_0^1 \mathrm{d} x_1 \int_0^1 \mathrm{d} x_2 \int \mathrm{d} \phi \, f_a (x_1, \xi_\mathrm{F} Q^2) f_b (x_2, \xi_\mathrm{F} Q^2) \sigma_{ab} (x_1, x_2, \phi) \text{,}
+\begin{multline}
+\frac{\mathrm{d} \sigma}{\mathrm{d} \mathcal{O}} (\mathcal{O}, \xi_\mathrm{R}, \xi_\mathrm{R}) \\
+= \sum_{a,b} \int_0^1 \mathrm{d} x_1 \int_0^1 \mathrm{d} x_2 \int_{Q^2_\mathrm{min}}^{Q^2_\mathrm{max}} \mathrm{d} Q^2 \, f_a (x_1, \xi_\mathrm{F} Q^2) f_b (x_2, \xi_\mathrm{F} Q^2) \sigma_{ab} (x_1, x_2, Q^2, \xi_\mathrm{R}, \xi_\mathrm{R}) \text{,}
 \label{eq:pineappl-convolution}
-\end{equation}
-\textsc{PineAPPL} can calculate hadronic cross sections for arbitrarily many PDF sets and scale variations quickly.
+\end{multline}
+\textsc{PineAPPL} can quickly calculate hadronic cross sections for arbitrarily many PDF sets and perform scale variations.
 
-\subsubsection{Example: Drell--Yan lepton-pair production}
+\subsubsection{Example: Drell--Yan lepton-pair production at the LHC}
 \label{sec:pineappl-example}
 
-To give an example of eq.~\eqref{eq:expansion}, the following shows Drell--Yan lepton-pair production up to terms at NLO (with arguments $x_1$, $x_2$, and $\phi$ suppressed for the phase-space weights):
+To give an example of eq.~\eqref{eq:expansion}, the following shows Drell--Yan lepton-pair production up to terms at NLO (with some arguments suppressed for the phase-space weights):
 \begin{equation}
@@
 \sigma_{ab}
-    &= \alpha^2 w_{ab}^{(0,2,0,0)} \\
-    &+ \alphas \left( \xi_\mathrm{R} Q^2 \right) \alpha^2 w_{ab}^{(1,2,0,0)} + \alphas \left( \xi_\mathrm{R} Q^2 \right) \log (\xi_\mathrm{F}) \alpha^2 w_{ab}^{(1,2,0,1)} (Q^2) \\
-    &+ \alpha^3 w_{ab}^{(0,3,0,0)} + \log (\xi_\mathrm{F}) \alpha^3 w_{ab}^{(0,3,0,1)} (Q^2) \text{.}
+    &= \alpha^2 W_{ab}^{(0,2,0,0)} \\
+    &+ \alphas \left( \xi_\mathrm{R} Q^2 \right) \alpha^2 W_{ab}^{(1,2,0,0)} (Q^2) + \alphas \left( \xi_\mathrm{R} Q^2 \right) \log (\xi_\mathrm{F}) \alpha^2 W_{ab}^{(1,2,0,1)} (Q^2) \\
+    &+ \alpha^3 W_{ab}^{(0,3,0,0)} (Q^2) + \log (\xi_\mathrm{F}) \alpha^3 W_{ab}^{(0,3,0,1)} (Q^2) \text{.}
 \end{split}
@@
 The first term with index $(0,2,0,0)$ is the LO term, the following line shows the NLO QCD correction, and the final line the NLO EW correction.
-Note that for all terms the dependence on the renormalisation scale is only indirectly through $\alphas$, because 1) higher-order terms in $\alpha$ never generate a renormalisation scale dependence (in the $\alpha$ schemes that are valid according to section~\ref{sec:multi-coupling-expansion}) and 2) higher-order QCD corrections only introduce an explicit renormalisation scale dependence in counterterms with vertices with more than two gluons.
-These terms, however, are not present in this process at NLO\@.
-Both NLOs, however, have a contribution from a collinear counterterm that depends on the factorisation scale.
+Note that all terms depend on the renormalisation scale only indirectly through $\alphas$, because 1) higher-order terms in $\alpha$ never generate a renormalisation scale dependence (in the $\alpha$ schemes that are valid according to section~\ref{sec:multi-coupling-expansion}) and 2) higher-order QCD corrections only introduce an explicit renormalisation scale dependence in counterterms with vertices with more than two gluons.
+At NLO these terms are not present in this process so that terms proportional to $\log (\xi_\mathrm{R})$ vanish.
+Both NLOs, however, have contributions from a collinear counterterm that depend on the factorisation scale.
+
+At NLO this process has 63 different initial states, of which there is one photon--photon initial state and 31 initial states with at least one (anti-)quark.
+The remaining 31 given by the transposition of the partons from the first 31 initial states.
 
@@
 
-\subsubsection{Example: top-pair production}
-
-TODO
+%\subsubsection{Example: top-pair production}
+%
+%\begin{equation}
+%\begin{split}
+%\sigma_{ab}
+%&= \alpha^2                                                                   W_{ab}^{(0,2,0,0)}
+% + \alphas   \left( \xi_\mathrm{R} Q^2 \right) \alpha                         W_{ab}^{(1,1,0,0)}
+% + \alphas^2 \left( \xi_\mathrm{R} Q^2 \right)                                W_{ab}^{(2,0,0,0)} \\
+%&+ \alphas^3 \left( \xi_\mathrm{R} Q^2 \right)                                W_{ab}^{(3,0,0,0)} \\
+%&+ \alphas^3 \left( \xi_\mathrm{R} Q^2 \right)          \log (\xi_\mathrm{F}) W_{ab}^{(3,0,0,1)} (Q^2)
+% + \alphas^3 \left( \xi_\mathrm{R} Q^2 \right)          \log (\xi_\mathrm{R}) W_{ab}^{(3,0,1,0)} (Q^2) \\
+%&+ \alphas^2 \left( \xi_\mathrm{R} Q^2 \right) \alpha                         W_{ab}^{(2,1,0,0)} \\
+%&+ \alphas^2 \left( \xi_\mathrm{R} Q^2 \right) \alpha   \log (\xi_\mathrm{F}) W_{ab}^{(2,1,0,1)} (Q^2)
+% + \alphas^2 \left( \xi_\mathrm{R} Q^2 \right) \alpha   \log (\xi_\mathrm{R}) W_{ab}^{(2,1,1,0)} (Q^2) \\
+%&+ \alphas   \left( \xi_\mathrm{R} Q^2 \right) \alpha^2                       W_{ab}^{(1,2,0,0)} \\
+%&+ \alphas   \left( \xi_\mathrm{R} Q^2 \right) \alpha^2 \log (\xi_\mathrm{F}) W_{ab}^{(1,2,0,1)} (Q^2)
+% + \alphas   \left( \xi_\mathrm{R} Q^2 \right) \alpha^2 \log (\xi_\mathrm{R}) W_{ab}^{(1,2,1,0)} (Q^2) \\
+%&+           \left( \xi_\mathrm{R} Q^2 \right) \alpha^3                       W_{ab}^{(0,3,0,0)} \\
+%&+           \left( \xi_\mathrm{R} Q^2 \right) \alpha^3 \log (\xi_\mathrm{F}) W_{ab}^{(0,3,0,1)} (Q^2)
+% +           \left( \xi_\mathrm{R} Q^2 \right) \alpha^3 \log (\xi_\mathrm{R}) W_{ab}^{(0,3,1,0)} (Q^2)
+%\end{split}
+%\end{equation}
 
@@
 To each leading order a higher-order correction with an additional power of $\alphas$ or $\alpha$ can be calculated, which in general leads to at least two next-to-leading order corrections.
-Sometimes there are higher orders that cannot directly be understood as a correction to a leading order, e.g.\ $\mathrm{p} \mathrm{p} \to \ell \bar{\ell} + \mathrm{jet} + X$, which has one leading order, $\mathcal{O} (\alphas \alpha^2)$, but three next-to-leading orders, one of which is $\mathcal{O} (\alpha^4)$~TODO.
+%Sometimes there are higher orders that cannot directly be understood as a correction to a leading order, e.g.\ $\mathrm{p} \mathrm{p} \to \ell \bar{\ell} + \mathrm{jet} + X$, which has one leading order, $\mathcal{O} (\alphas \alpha^2)$, but three next-to-leading orders, one of which is $\mathcal{O} (\alpha^4)$~TODO.
 
 Due to the typical sizes of the couplings $\alphas^2 \sim \alpha$, it is naively expected that within the same order, i.e.\ for fixed $k + l$, terms with larger powers $\alphas^k$ dominate over those with smaller powers; however, in practise this naive expectation is not always true due to dynamic effects.
-Some prominent examples are vector-boson scattering processes and TODO.
+Some prominent examples are vector-boson scattering processes~\cite{Biedermann:2017bss,Denner:2019tmn} and top-pair production with another top-pair or a W boson~\cite{Frederix:2017wme}.
 
@@
 
-In this subsection we explain the details of how the phase-space weights $w_{ab}$ in eq.~\ref{eq:expansion} are represented.
+In this subsection we explain the details of how the phase-space weights $w_{ab}$ in eq.~\eqref{eq:expansion} are represented.
 
@@
 
-One very simple representation are 4-tuples, which for each phase-space point and combination $(a, b, k, l, m, n)$ saves a list of the parton fractions $x_1$ and $x_2$, the scale $Q^2$, and the phase-space weight $w$; this is sufficient for a total cross section.
-If, however, a differential cross section shall be reconstructed, we first need to generalise eq.~\eqref{eq:expansion}:
+A straightforward representation are 4-tuples, which for each phase-space point saves a list of the momentum fractions $x_1$ and $x_2$, the scale $Q^2$, and the phase-space weight $w$; this is sufficient to reconstruct a total cross section.
+
+For each combination $(a,b,k,l,m,n,o)$ we save the following 4-tuples:
 \begin{equation}
-\frac{\mathrm{d} \sigma_{ab}}{\mathrm{d} \mathcal{O}} (x_1, x_2, \phi, \mathcal{O}) = \sum_{k,l,m,n} \alphas^k \left( \xi_\mathrm{R} Q^2 \right) \alpha^l \log^m ( \xi_\mathrm{R} ) \log^n ( \xi_\mathrm{F} ) \frac{\mathrm{d} w_{ab}^{(k,l,m,n)}}{\mathrm{d} \mathcal{O}} \left( x_1, x_2, Q^2, \phi \right) \\
+\left\{ x_1^i, x_2^i, Q^2_i, w^{(k,l,m,n,o)}_{ab} (x_1^i, x_2^i, Q^2_i, \mathcal{O}_i) \right\}_{i=1}^N \text{,} \label{eq:four-tuples}
 \end{equation}
-where, because of a finite number of phase-space points given by the Monte Carlo integrator, we numerically approximates the derivative as
-\begin{equation}
-\begin{split}
-\frac{\mathrm{d} w_{ab}^{(k,l,m,n)}}{\mathrm{d} \mathcal{O}} \left( x_1, x_2, Q^2, \phi \right) &\approx \sum_{o=1}^M \frac{\Theta (\mathcal{O}_o^\mathrm{min} \le \mathcal{O} < \mathcal{O}_o^\mathrm{max})}{\mathcal{O}_o^\mathrm{max} - \mathcal{O}_o^\mathrm{min}} w_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2, \phi \right) \\
-&= \sum_{o=1}^M w_{ab}^{(k,l,m,n,o)} \left( x_1, x_2, Q^2, \phi, \mathcal{O} \right) \text{,}
-\end{split}
-\end{equation}
-using $M$ discrete bins with boundaries $\{ \mathcal{O}_o^\mathrm{min}, \mathcal{O}_o^\mathrm{max} \}_{o=1}^M$.
+The reconstruction of the differential cross section is then done by simply multiplying the phase-space weights $w$ with PDFs evaluated with the correct arguments given in the 4-tuple and summing over all indices $a$, $b$, $k$, $l$, $m$, $n$, $o$, and $i$.
 
-This means that for each bin $o$ of the observable $\mathcal{O}$ and therefore for each combination $(a,b,k,l,m,n,o)$ we save the following 4-tuples:
-\begin{equation}
-\left\{ x_1^i, x_2^i, Q^2_i, w^{(k,l,m,n,o)}_{ab} (x_1^i, x_2^i, Q^2_i, \phi_i, \mathcal{O}_i) \right\}_{i=1}^N \text{,} \label{eq:four-tuples}
-\end{equation}
-The reconstruction of the differential cross section for bin $o$ is then straightforwardly done by multiplying the phase-space weights $w$ with PDFs evaluated with the correct arguments given in the 4-tuple and summing over all indices $a$, $b$, $k$, $l$, $m$, $n$, and $i$.
-
-Using 4-tuples has the clear advantage of being very easy to implement and therefore also easy to test.
+Using 4-tuples has the clear advantage of being very easy to implement and test.
 Furthermore, they reproduce the exact numerical value that is also calculated by the Monte Carlo integrator.
 However, the price one has to pay is the size of the 4-tuples, which scales linearly with the number of phase-space weights $N$.
-Because the uncertainties of Monte Carlo integrators shrink as $1/\sqrt{N}$, this typically means \numrange{e7}{e9} phase-space points.
+Because the uncertainties of Monte Carlo integrators shrink only as $1/\sqrt{N}$, however, this typically means \numrange{e6}{e9} phase-space points are necessary for a good convergence.
 In the case of the NLO Drell--Yan (section~\ref{sec:pineappl-example}) the 4-tuples need roughly TODO~\si{\giga\byte} of storage (see appendix~\ref{app:drell-yan-storage} for an explanation of this number).
@@
 This method is straightforward, but given a finite number of bins this usually yields a bad approximation for the cross section.
-This can be remedied by increasing the number of bins, which would also increase the space requirements of the grid.
-There are, however, more refined methods, which keep the number of bins constant, while improving the quality of the approximation: Interpolation grids.
+Increasing the number of bins improves the accuracy, but it also increases the space requirements of the grid.
+Interpolation methods offers more precision, while keeping the number of bins constants.
 
-TODO
+We use the same Lagrange-interpolation grid presented in Ref.~\cite{Carli:2010rw} with the parameters published in Ref.~\cite{Bertone:2014zva}, which give decent precision (see section~\ref{sec:results}).
+The method presented in previous references first maps $(x_1, x_2, Q^2) \mapsto (y_1, y_2, \tau)$, with the maps defined as
+\begin{equation}
+y(x) = 5 (1-x) - \log x \text{,} \qquad \tau (Q^2) = \log \log \frac{Q^2}{(\SI{0.25}{\giga\electronvolt})^2} \text{,}
+\end{equation}
+and then feeds the variables $(y_1, y_2, \tau)$ into the 3-dimensional Lagrange-interpolation grid with 50 bins in each $y$ direction and 30 bins in $\tau$ direction.
+The interpolation order is 3 for each variable, and only the subspace $[\num{2e7},1] \times [\num{2e-7},1] \times [100,\num{e6}] \subset H$\footnote{In Ref.~\cite{Bertone:2014zva} the upper limit for $Q$ is given as \SI{3162}{\giga\electronvolt} (which corresponds to $Q^2 \approx \SI{e7}{\giga\electronvolt}$), but in the code we found the value given above.} is mapped.
+For the convolution of a grid with a PDF set also the inverse functions are needed, which are
+\begin{equation}
+x(y) = \frac{1}{5} \operatorname{W}_0 (5 \exp (5-x)) \text{,} \qquad Q^2 (\tau) = (\SI{0.25}{\giga\electronvolt})^2 \exp (\exp (\tau)) \text{,}
+\end{equation}
+where $\operatorname{W}_0 (x)$ is (the principle branch of) the Lambert W function or product logarithm, which satisfies the relation $\operatorname{W} (x) \exp (\operatorname{W} (x)) = x$.
+
+\subsubsection{Combination of differently weighed phase-spaces points}
+
+To improve the convergence of phase-space integrations Monte Carlo integrators usually use importance sampling, typically using one or both of VEGAS~\cite{} and multi-channel MC~\cite{}.
+Both algorithms are adaptive and perform a number of iterations, each iteration trying to improve the convergence by changing the distribution from which phase-space points are sampled.
+This raises the question if the differently sampled phase-space points are compatible with each other in the grid generation, and, if the answer is no, how this can be remedied.

### 2020-06-23 nnpdf31_proc/CMS_Z_13TEV/analysis.f
New analyses

@@ -1,0 +1,110 @@
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_begin(nwgt,weights_info)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      integer nwgt
+      character*(*) weights_info(*)
+
+      call set_error_estimation(1)
+      call HwU_inithist(nwgt,weights_info)
+      call HwU_book( 1,'Z pT', 14,   0.5d0,  13.5d0)
+      call HwU_book( 2,'Z pT',  1,  13.5d0,  15.0d0)
+      call HwU_book( 3,'Z pT',  4,  15.0d0,  21.0d0)
+      call HwU_book( 4,'Z pT',  1,  21.0d0,  23.5d0)
+      call HwU_book( 5,'Z pT',  1,  23.5d0,  26.5d0)
+      call HwU_book( 6,'Z pT',  1,  26.5d0,  30.0d0)
+      call HwU_book( 7,'Z pT',  1,  30.0d0,  34.5d0)
+      call HwU_book( 8,'Z pT',  1,  34.5d0,  40.0d0)
+      call HwU_book( 9,'Z pT',  1,  40.0d0,  47.5d0)
+      call HwU_book(10,'Z pT',  1,  47.5d0,  58.5d0)
+      call HwU_book(11,'Z pT',  1,  58.5d0,  75.0d0)
+      call HwU_book(12,'Z pT',  1,  75.0d0, 102.5d0)
+      call HwU_book(13,'Z pT',  1, 102.5d0, 140.0d0)
+      call HwU_book(14,'Z pT',  1, 140.0d0, 175.0d0)
+      call HwU_book(15,'Z pT',  2, 175.0d0, 235.0d0)
+      call HwU_book(16,'Z pT',  1, 235.0d0, 275.0d0)
+      call HwU_book(17,'Z pT',  1, 275.0d0, 350.0d0)
+      call HwU_book(18,'Z pT',  1, 350.0d0, 450.0d0)
+      call HwU_book(19,'Z pT',  1, 450.0d0, 650.0d0)
+      call HwU_book(20,'Z pT',  1, 650.0d0,1150.0d0)
+      
+      return
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_end(dummy)
[…]

### 2020-06-23 nnpdf31_proc/ATLAS_TTB_DIFF_8TEV_LJ_TPTNORM/analysis.f
New data sets

@@ -1,0 +1,57 @@
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_begin(nwgt,weights_info)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      integer nwgt
+      character*(*) weights_info(*)
+
+      call set_error_estimation(1)
+      call HwU_inithist(nwgt,weights_info)
+      call HwU_book(1,'t pT ', 1,0.0d0,60.0d0)
+      call HwU_book(2,'t pT ', 1,60.0d0,100.0d0)
+      call HwU_book(3,'t pT ', 2,100.0d0,200.0d0)
+      call HwU_book(4,'t pT ', 2,200.0d0,320.0d0)
+      call HwU_book(5,'t pT ', 1,320.0d0,400.0d0)
+      call HwU_book(6,'t pT ', 1,400.0d0,500.0d0)
+
+      return
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_end(dummy)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      double precision dummy
+      call HwU_write_file
+      return                
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_fill(p,istatus,ipdg,wgts,ibody)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      include 'nexternal.inc'
+      integer istatus(nexternal)
+      integer iPDG(nexternal)
+      integer ibody
+      integer i
+      double precision p(0:4,nexternal)
+      double precision wgts(*)
+      double precision pt_t
+ 
+      pt_t   = dsqrt(p(1,3)**2 + p(2,3)**2)
+
+      call HwU_fill(1,pt_t,wgts)
+      call HwU_fill(2,pt_t,wgts)
+      call HwU_fill(3,pt_t,wgts)
+      call HwU_fill(4,pt_t,wgts)
+      call HwU_fill(5,pt_t,wgts)
+      call HwU_fill(6,pt_t,wgts)
+
+ 999  return      
+      end
+
+ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc

### 2020-06-23 nnpdf31_proc/ATLAS_TTB_DIFF_8TEV_LJ_TTMNORM/analysis.f

@@ -1,0 +1,63 @@
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_begin(nwgt,weights_info)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      integer nwgt
+      character*(*) weights_info(*)
+
+      call set_error_estimation(1)
+      call HwU_inithist(nwgt,weights_info)
+      call HwU_book(1,'tt m ', 1,345d0,400.0d0)
+      call HwU_book(2,'tt m ', 1,400.0d0,470.0d0)
+      call HwU_book(3,'tt m ', 1,470.0d0,550.0d0)
+      call HwU_book(4,'tt m ', 1,550.0d0,650.0d0)
+      call HwU_book(5,'tt m ', 1,650.0d0,800.0d0)
+      call HwU_book(6,'tt m ', 1,800.0d0,1100.0d0)
+      call HwU_book(7,'tt m ', 1,1100.0d0,1600.0d0)
+
+      return
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_end(dummy)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      double precision dummy
+      call HwU_write_file
+      return                
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_fill(p,istatus,ipdg,wgts,ibody)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      include 'nexternal.inc'
+      integer istatus(nexternal)
+      integer iPDG(nexternal)
+      integer ibody
+      integer i
+      double precision p(0:4,nexternal)
+      double precision wgts(*)
+      double precision pttx(0:3), mtt
+
+      do i=0,3
+         pttx(i)=p(i,3)+p(i,4)
+      enddo
+      
+      mtt    = dsqrt(dot(pttx, pttx))
+      
+      call HwU_fill(1,mtt,wgts)
+      call HwU_fill(2,mtt,wgts)
+      call HwU_fill(3,mtt,wgts)
+      call HwU_fill(4,mtt,wgts)
[…]

### 2020-06-23 nnpdf31_proc/ATLAS_TTB_DIFF_8TEV_LJ_TTRAPNORM/analysis.f

@@ -1,0 +1,74 @@
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_begin(nwgt,weights_info)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      integer nwgt
+      character*(*) weights_info(*)
+
+      call set_error_estimation(1)
+      call HwU_inithist(nwgt,weights_info)
+      call HwU_book(1,'tt rap ', 3,0.0d0,0.9d0)
+      call HwU_book(2,'tt rap ', 1,0.9d0,1.3d0)
+      call HwU_book(3,'tt rap ', 1,1.3d0,2.5d0)
+      return
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_end(dummy)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      double precision dummy
+      call HwU_write_file
+      return                
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_fill(p,istatus,ipdg,wgts,ibody)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      include 'nexternal.inc'
+      integer istatus(nexternal)
+      integer iPDG(nexternal)
+      integer ibody
+      integer i
+      double precision p(0:4,nexternal)
+      double precision wgts(*)
+      double precision pttx(0:3), yttx, getrapidity
+      external getrapidity
+
+      do i=0,3
+        pttx(i)=p(i,3)+p(i,4)
+      enddo
+      
+      yttx  = getrapidity(pttx(0,3), pttx(3,3))
+
+      call HwU_fill(1,yttx,wgts)
+      call HwU_fill(2,yttx,wgts)
+      call HwU_fill(3,yttx,wgts)
+
+ 999  return      
+      end
+
+ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      function getrapidity(en,pl)
+      implicit none
+      real*8 getrapidity,en,pl,tiny,xplus,xminus,y
+      parameter (tiny=1.d-8)
+      xplus=en+pl
+      xminus=en-pl
[…]

### 2020-06-25 paper/sec-results.tex
Add Christpher's comments about plots

@@
 us to do so.
+
+CS 25 Jun: We've agreed to show basically two types of plots: 1) technical plots showing the good agreement between the MC compared to the results from the grids, and 2) phenomenological results showing larger EW corrections, for example.
+In the aMCfast paper both is shown in single plot, but since we have more to show, I suggest the following: for the technical plots we show a 2x2 matrix of plots, each showing the difference of the grid result compared to the MC result, in the following fashion:
+\begin{itemize}
+\item NLO QCD with low statistics,
+\item NLO QCD+EW with low statistics,
+\item NLO QCD with high statistics, and finally
+\item NLO QCD+EW with high statistics,
+\end{itemize}
+each showing a few scale variations.
+These plots then clearly show that no matter what corrections you choose, no matter the statistics, and no matter the scale variation, the agreement is always excellent.
+In any case I would like to avoid showing a plot with absolute numbers and low statistics, which looks a bit ridiculous in my opinion (look at figure 1, left side, top plot of the aMCfast paper).
+
+Finally we can show another series of plots, which in my opinion should be very similar to the usual pheno paper plots: absolute numbers with a scale variation band, maybe a few corrections shown in the same plot and then in the bottom relative corrections.

### 2020-07-01 paper/app-pineappl.tex
Add appendix about PineAPPL to the paper

@@
 \section{More technical details about \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
+
+%\subsection{Efficiency of the grid representation}
+%\label{app:pineappl-representation-efficiency}
+%
+%Using a similar notation introduced in eq.~\eqref{eq:expansion}, we single out a specific NLO correction:
+%\begin{equation}
+%\begin{split}
+%\alphas^k \bigl( \mu_\mathrm{R}^2 \bigr) \alpha^l \Bigl[ \log \bigl( \mu_\mathrm{R}^2 \bigr) &W_{ab}^{(k,l,1,0)} (x_1, x_2) \\
+%+ \log \bigl( \mu_\mathrm{F}^2 \bigr) &W_{ab}^{(k,l,0,1)} (x_1, x_2) \\
+%&W_{ab}^{(k,l,0,0)} (x_1, x_2) \Bigr] \text{.}
+%\end{split}
+%\end{equation}
+%If we assume the case of a dynamic scale choice, i.e.\ $\mu_\mathrm{R}^2 \equiv \mu_\mathrm{R}^2 \bigl( x_1, x_2 \bigr)$ and $\mu_\mathrm{F}^2 \equiv \mu_\mathrm{F}^2 \bigl( x_1, x_2 \bigr)$,
 
@@
 
+\textsc{PineAPPL} currently consists of three parts: 1) the library itself, which is a dependency for the other parts, 2) the helper program \texttt{pineappl}, which allows to read \textsc{PineAPPL} grids from the command line and make predictions with it, and finally 3) the C interface, which is intended to be used in Monte Carlo integrators to generate the grids.
+
+\lstset{
+  basicstyle=\ttfamily,
+  showstringspaces=false,
+  commentstyle=\color{red},
+  keywordstyle=\color{blue}
+}
+
+All parts are written in Rust and therefore need a Rust compiler and other tools.
+On computers with a \texttt{bash} shell the installation is as simple as
+\begin{lstlisting}[language=bash]
+curl --proto '=https' --tlsv1.2 -sSf https://sh.rustup.rs | sh
+\end{lstlisting}
+which downloads the compiler \texttt{rustc}, the package manager \texttt{cargo}, and a few other helpful tools.
+When the installation has completed make sure to read and follow the instructions printed before.
+See also \url{https://www.rust-lang.org/tools/install} for more details and for installation instructions for other systems.
+
+The command-line program \texttt{pineappl} is compiled and installed using
+\begin{lstlisting}[language=bash]
+cargo install pineappl_cli
+\end{lstlisting}
+This program also needs \texttt{LHAPDF} installed.
+For usage instructions simply type \texttt{pineappl} in your shell and read the help message.
+
+For the C interface you need to first install \texttt{cargo-c}, download the \textsc{PineAPPL} repository, and compile and finally install into it into a directory \texttt{\$prefix} as follows:
+\begin{lstlisting}[language=bash]
+cargo install cargo-c
+git clone https://github.com/N3PDF/pineappl/
+cd pineappl_capi/
+cargo cinstall --release --prefix=${prefix}
+\end{lstlisting}
+The last line will install the C header \texttt{pineappl\_capi.h}, the library, and a pkg-config\footnote{A standard way on Linux to express how dependencies are compiled/linked against, see \url{https://www.freedesktop.org/wiki/Software/pkg-config/}} file (\texttt{pineappl\_capi.pc}).
+Make sure that the environment variables \texttt{PATH}, \texttt{LD\_LIBRARY\_PATH}, and \texttt{PKG\_CONFIG\_PATH} are properly set.
+The latter is needed for \texttt{pkg-config -{}-cflags -{}-libs pineappl\_capi} to work, which prints the necessary compiler/linker flags.
+See App.~\ref{app:example-program} for an example.
+
+Updated installation instructions are kept in the file \texttt{README.md} in \textsc{PineAPPL}'s repository at \url{https://github.com/N3PDF/pineappl/}.
+
 \subsection{Drell--Yan \texorpdfstring{$n$}{n}-tuple storage size}
@@
 
-\subsection{Example program}
+TODO
+
+\subsection{Example Monte Carlo program}
 \label{app:example-program}
+
+\definecolor{mygreen}{rgb}{0,0.6,0}
+\definecolor{mygray}{rgb}{0.5,0.5,0.5}
+\definecolor{mymauve}{rgb}{0.58,0,0.82}
+
+\lstset{
+  belowcaptionskip=1\baselineskip,
+  breaklines=true,
+  frame=L,
+  numbers=left,
+  xleftmargin=\parindent,
+  showstringspaces=false,
+  basicstyle=\footnotesize\ttfamily,
+  keywordstyle=\bfseries\color{green!40!black},
+  commentstyle=\itshape\color{purple!40!black},
+  identifierstyle=\color{blue},
+  stringstyle=\color{orange},
+}
+
+The following listing shows how to setup \textsc{PineAPPL} using its C interface in a simple Monte Carlo integrator for calculating the double-photon contribution to Drell--Yan lepton-pair production at the LHC.
+All \textsc{PineAPPL} functions have the prefix \texttt{pineappl\_}.
+The full example can be found at TODO.
+\begin{lstlisting}[language=C++,mathescape=true]
+// create a new luminosity function for the $\gamma\gamma$ initial state
+auto* lumi = pineappl_lumi_new();
+int32_t pdg_ids[] = { 22, 22 };
+double ckm_factors[] = { 1.0 };
+pineappl_lumi_add(lumi, 2, pdg_ids, ckm_factors);
+
+// only LO $\alpha_\mathrm{s}^0 \alpha^2 \log^0(\xi_\mathrm{R}) \log^0(\xi_\mathrm{F})$
+uint32_t orders[] = { 0, 2, 0, 0 };
+
+// we bin in rapidity from 0 to 2.4 in steps of 0.1
+double bins[] = {
+    0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0, 1.1, 1.2,
+    1.3, 1.4, 1.5, 1.6, 1.7, 1.8, 1.9, 2.0, 2.1, 2.2, 2.3, 2.4
+};
+
+// create the PineAPPL grid with default interpolation and binning parameters
+auto* keyval = pineappl_keyval_new();
+auto* grid = pineappl_grid_new(lumi, 1, orders, 24, bins, keyval);
+
+// now we no longer need `keyval` and `lumi`
+pineappl_keyval_delete(keyval);
+pineappl_lumi_delete(lumi);
+
+// fill the grid with phase-space points
+fill_grid(grid, 10000000);
+
+// perform a convolution of the grid with PDFs
+auto* pdf = LHAPDF::mkPDF("NNPDF31_nlo_as_0118_luxqed", 0);
+auto xfx = [](int32_t id, double x, double q2, void* pdf) {
+    return static_cast <LHAPDF::PDF*> (pdf)->xfxQ2(id, x, q2);
+};
+auto alphas = [](double q2, void* pdf) {
+    return static_cast <LHAPDF::PDF*> (pdf)->alphasQ2(q2);
+};
+
+std::vector<double> dxsec(24);
+pineappl_grid_convolute(grid, xfx, xfx, alphas, pdf, nullptr,
+    nullptr, 1.0, 1.0, dxsec.data());
+
+// print the results
+for (std::size_t i = 0; i != 24; ++i) {
+    std::printf("%.1f %.1f %.3e\n", bins[i], bins[i + 1], dxsec[i]);
+}
+
+// write the grid to disk
+pineappl_grid_write(grid, "DY-LO-AA.pineappl");
+
+// destroy the object
+pineappl_grid_delete(grid);
+\end{lstlisting}
+
+\subsection{Demonstration of \texorpdfstring{\texttt{pineappl}}{pineappl}}
+\label{app:pineappl-demo}
+
+TODO
+
+\subsection{Sample runcard for \texorpdfstring{\textsc{mg5\_aMC@NLO}}{mg5\_aMC@NLO}}
+\label{app:sample-runcard}
+
+TODO

### 2020-07-01 paper/sec-pineappl.tex
Rewrite parts of section 2

@@
-\section{PDF-independent binning of phase-space weights with \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
+\section{PDF-independent storage of phase-space weights with \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
 \label{sec:pineappl}
 
-In this paper we introduce a new library called \textsc{PineAPPL}, which bins phase-space weights independently from the chosen PDF set.
-The resulting files, generally called grids, can be used to quickly convolute the observables with multiple PDF sets.
-This has at least two applications:
+In this paper we present a new library called \textsc{PineAPPL}, which stores phase-space weights of a Monte Carlo (MC) integration independently from the chosen PDFs.
+This separates the task of producing predictions for observables into two steps: 1) the generation of the \emph{grids}, which is how the generated files are called, and 2) the convolution of those grids with a set of PDFs.
+The advantage of this method is that the time-consuming first step has to be done only once and therefore allows for very quick convolutions of a grids with multiple PDF sets.
+
+The convolution is typically done in a few seconds or less, which offers at least two applications:
+\begin{enumerate}
+\item the study of PDF-dependence of observables; e.g.\ PDF set comparisons, PDF uncertainties for different PDF set, $\alphas$ variations, etc., and
+\item the determination of PDF sets themselves; the grids together with the corresponding experimental data constitute two important ingredients for a PDF fit.
+\end{enumerate}
+This puts \textsc{PineAPPL} in the same category as \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}.
+However, it supports electroweak (EW) predictions/corrections, which are the main interest in this paper.
+In particular, the following features are supported:
 \begin{itemize}
-\item the study of the dependence of observables on PDF sets; e.g.\ to determine how the central predictions of observables change when changing the PDF set, the PDF uncertainties for different PDF set, etc.\ and
-\item the determination of PDF sets themselves; the grids together with the corresponding experimental data are the main inputs for a PDF fit.
+\item Support for arbitrary fixed-order calculations in powers of $\alpha$, $\alphas$ or combinations thereof, in particular also mixed QCD--EW corrections.
+\item EW corrections require the inclusion of photon-initiated contributions, which are supported as well.
+In fact, \textsc{PineAPPL} allows arbitrary initial-state combinations, e.g.\ leptonic initial states, for which PDFs have been calculated recently~\cite{Buonocore:2020nai}.
+\item Variations of the renormalisation and factorisation scale around the central scale choice are supported, which are needed to estimate the QCD scale uncertainty.
+%\item Support for all-order predictions coming from a resummation calculation or a photon-/parton-shower, which are important for some observables (see section~\ref{sec:results}),
 \end{itemize}
-This puts \textsc{PineAPPL} in the same category than \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}.
-What sets \textsc{PineAPPL} apart from the other libraries is its support for electroweak (EW) predictions/corrections, which are the main interest in this paper.
-More specifically, the following features are supported:
+On a more technical level, we further point out the following differences of \textsc{PineAPPL}:
 \begin{itemize}
-\item Support for arbitrary fixed-order calculations in powers of $\alpha$, $\alphas$ or combinations thereof, in particular also mixed QCD-EW corrections.
-Electroweak corrections require the inclusion of photon-initiated contributions, which are supported.
-In fact \textsc{PineAPPL} supports arbitrary initial-state combinations, for example leptonic initial states, for which PDFs have recently calculated~\cite{}.
-\item Variations of the renormalisation and factorisation scale are supported, if needed.
-For each needed combination of the couplings and logarithms of renormalisation and factorisation scale a separate subgrid is created (see section~\ref{sec:multi-coupling-expansion} for more details);
-%\item Support for all-order predictions coming from a resummation calculation or a photon-/parton-shower, which are important for some observables (see section~\ref{sec:results}),
-\item A simple \textsc{C}-interface (see appendix~\ref{app:example-program} for examples and documentation), which is needed for Monte Carlos and programs to read and write \textsc{PineAPPL} grids.
-\textsc{PineAPPL} itself is written in Rust (see appendix~\ref{app:installation} for installation instructions).
-\item Another interface is the command-line program \texttt{pineappl}, which allows users of the generated grids to perform convolutions of the grid with PDF sets.
-Additionally, it can print further information on how the corresponding luminosity function is constructed, which perturbative orders are stored, the relative size of each correction, the relative size of each partonic channel, etc.
+\item Earlier experiments with APPLgrid (only QCD corrections) showed that it uses a substantial amount memory (close to \SI{80}{\giga\byte}), if a grid for a differential distributions with more than 10 bins was generated.
+The memory usage is substantially reduced (roughly \SI{1}{\giga\byte}) after \enquote{optimisation} of the grids, i.e.\ an optimisation of the grid representation in memory.
+However, this means that this two-step procedure of 1) producing an unoptimised grid and 2) filling an optimised grid effectively limits the bins to a small number.
+\textsc{PineAPPL} avoids this by using a more space-efficient representation from the start.
+\item \textsc{PineAPPL} offers an easy-to-use interface written in the C programming language, to allow MC integrators to read and write \textsc{PineAPPL} grids.
+C was chosen because it plays well with Fortran and C++, in which most MC integrators are written.
+The interface consists of roughly 30 functions of which basically only a handful are needed.
+See appendix~\ref{app:example-program} for an example.
+%\textsc{PineAPPL} itself is written in Rust (see appendix~\ref{app:installation} for installation instructions).
+\item The program \texttt{pineappl}, which performs convolutions on the command line (see appendix~\ref{app:pineappl-demo}), without requiring the user to write a new program.
+In addition to convolutions, it can also print how the luminosity function is constructed, which perturbative orders are stored, their size, the size of each partonic channel, etc., separately for each bin.
 %\item Possibility to import \textsc{APPLgrids} and \textsc{fastNLO} tables.
-\item Superior efficiency and moderate memory requirements for differential distributions with more then 100 bins.
 \end{itemize}
-For \textsc{mg5\_aMC@NLO}~\cite{Alwall:2014hca,Frederix:2018nkq} the interfacing code is already implemented in a separate version, which is intended to replace the \textsc{aMCfast}~\cite{Bertone:2014zva} interface.
-The interfacing code for other Monte Carlo generators should be easy to write, see appendix~\ref{app:example-program} for a small example program.
+For \textsc{mg5\_aMC@NLO}~\cite{Alwall:2014hca,Frederix:2018nkq} the interfacing code is already implemented\footnote{It can be downloaded from \url{https://code.launchpad.net/~amcblast/+junk/3.0.2}}, which is intended to replace the \textsc{aMCfast}~\cite{Bertone:2014zva} interface.
+Its usage is very similar to that of \textsc{mg5\_aMC 2}+\textsc{aMCfast}+\textsc{APPLgrid}.
+However, using \textsc{PineAPPL} is much faster especially for small runs, because the grids do not need to be optimised and are merged faster.
+See appendix~\ref{app:sample-runcard} for an example of a runcard.
+
+Interfacing code for other MC generators should be easy to write, see appendix~\ref{app:example-program} for a small example program.
 
@@
 \label{sec:multi-coupling-expansion}
-{\bf MZ comments:}
-\begin{itemize}
-    \item I would prefer to keep the notation similar to the aMCfast paper, or at least to start with that, and then generalise it
-    \item the business of the different kinematics (born, resolved, counterterms, etc) is not mentioned at all
-\end{itemize}
-{\bf end MZ comments:}
 
@@
 \end{multline}
-The above cross section is differential w.r.t.\ the observable $\mathcal{O}$, which, in general, is a function of phase space and subject to the usual conditions (soft- and collinear safety, \ldots).
-In experiments, but also for many calculations where the phase-space integration is performed using a Monte Carlo integrator, finite statistics does not allow us to reconstruct the exact dependence of the cross section on the observable $\mathcal{O}$.
+The cross section shown above is differential w.r.t.\ the observable $\mathcal{O}$, which, in general, is a function of phase space and subject to the usual conditions (soft- and collinear safety, etc.).
+
+In experiments, but also for many calculations where the phase-space integration is performed using MC techniques, finite statistics does not allow us to reconstruct the exact dependence of the cross section on the observable $\mathcal{O}$.
 Instead, it it sufficient to approximate the derivative using a piecewise-constant function,
@@
 \mathcal{O}_0^\mathrm{min} < \mathcal{O}_0^\mathrm{max} = \mathcal{O}_1^\mathrm{min} < \ldots < \mathcal{O}_{M-1}^\mathrm{max} = \mathcal{O}_M^\mathrm{min} < \mathcal{O}_M^\mathrm{max} \text{.}
+\label{eq:bins-of-diff-xsection}
 \end{equation}
 
-If chosen dynamically the Ellis--Sexton scale $Q^2$ depends on the phase space as well, but we assume the fractions $\xi_\mathrm{R}$ and $\xi_\mathrm{F}$ to be constants of phase space in any case.
+% TODO: add table with aMCfast notation
+
+%\begin{table}
+%\begin{tabular}{ll}
+%\toprule
+%Old notation & new notation \\
+%\midrule
+%\bottomrule
+%\end{tabular}
+%\caption{Translation table for the notation of ref.~\cite{Bertone:2014zva} to the one used in eq.~\eqref{eq:expansion}.}
+%\label{tab:amcfast-notation}
+%\end{table}
+
+If chosen dynamically the Ellis--Sexton scale $Q^2$ depends on the phase space, but we assume the fractions $\xi_\mathrm{R}$ and $\xi_\mathrm{F}$ to be constants of phase space in any case.
 This allows variations around the central scale choice $\xi_\mathrm{R} = \xi_\mathrm{F} = 1$, but not changing the scale arbitrarily.
@@
 \end{equation}
-The (asymmetric) uncertainties are the given as the minimum and maximum value (the envelope), measured from the central value $(1, 1)$.
+The (asymmetric) uncertainties are then given as the minimum and maximum value (the envelope), measured from the central value $(1, 1)$.
 
@@
 \end{equation}
-given by the Monte Carlo integrator.
+given by the MC integrator.
 Using eq.~\eqref{eq:expansion} and
@@
 \end{multline}
-\textsc{PineAPPL} can quickly calculate hadronic cross sections for arbitrarily many PDF sets and perform scale variations.
+\textsc{PineAPPL} can then quickly calculate hadronic cross sections for arbitrarily many PDF sets and perform scale variations.
+
+\subsubsection{General characteristics}
+
+In general, we define leading order (LO) as the set of all possible initial states $a b$ which lead to the same final state $X$, for which the sum of the coupling exponents in eq.~\eqref{eq:expansion} is smallest, i.e.\ $k + l = p$, where $p = \min (k+l)$.
+This number is process dependent and usually determined by the number of external particles.
+For many processes there is only one LO, but when a process has multiple quark lines, colourless (photons, \dots) and coloured particles (gluons, \ldots) can be exchanged between them, making it possible to have more than one LO.
+An important example at the LHC is di-jet production, which has three different LOs: $\mathcal{O} (\alpha^2)$, $\mathcal{O} (\alphas \alpha)$, and $\mathcal{O} (\alpha^2)$.
+Each LO receives a higher-order correction with an additional power of $\alphas$ or $\alpha$, which in general leads to at least two next-to-leading order (NLO) corrections.
+The correction with the largest power in $\alphas$ can be unambiguously called \enquote{the} QCD correction, and the one with the largest power in $\alpha$ \enquote{the} EW correction.
+All remaining corrections are of mixed type, meaning that they, in general, cannot be attributed to either one of strong or electroweak origin.
+%Sometimes there are higher orders that cannot directly be understood as a correction to a LO, e.g.\ $\mathrm{p} \mathrm{p} \to \ell \bar{\ell} + \mathrm{jet} + X$, which has one LO, $\mathcal{O} (\alphas \alpha^2)$, but three NLOs, one of which is $\mathcal{O} (\alpha^4)$~TODO.
+
+Due to the typical sizes of the couplings $\alphas^2 \sim \alpha$, it is naively expected that within the same order, i.e.\ for fixed $k + l$, terms with larger powers $\alphas^k$ dominate over those with smaller powers.
+In practice, however, this naive expectation is not always true due to dynamic effects.
+Some examples are vector-boson scattering processes~\cite{Biedermann:2017bss,Denner:2019tmn}, top-pair production with a W boson and four-top production~\cite{Frederix:2017wme}, and Higgs production with a bottom-pair~\cite{Pagani:2020rsg}.
 
@@
     &= \alpha^2 W_{ab}^{(0,2,0,0)} \\
-    &+ \alphas \left( \xi_\mathrm{R} Q^2 \right) \alpha^2 W_{ab}^{(1,2,0,0)} (Q^2) + \alphas \left( \xi_\mathrm{R} Q^2 \right) \log (\xi_\mathrm{F}) \alpha^2 W_{ab}^{(1,2,0,1)} (Q^2) \\
-    &+ \alpha^3 W_{ab}^{(0,3,0,0)} (Q^2) + \log (\xi_\mathrm{F}) \alpha^3 W_{ab}^{(0,3,0,1)} (Q^2) \text{.}
+    &+ \alphas \left( \xi_\mathrm{R} Q^2 \right) \alpha^2 W_{ab}^{(1,2,0,0)} (Q^2) + \alphas \left( \xi_\mathrm{R} Q^2 \right) \log (\xi_\mathrm{F}) \alpha^2 W_{ab}^{(1,2,0,1)} \\
+    &+ \alpha^3 W_{ab}^{(0,3,0,0)} (Q^2) + \log (\xi_\mathrm{F}) \alpha^3 W_{ab}^{(0,3,0,1)} \text{.}
 \end{split}
@@
 Note that all terms depend on the renormalisation scale only indirectly through $\alphas$, because 1) higher-order terms in $\alpha$ never generate a renormalisation scale dependence (in the $\alpha$ schemes that are valid according to section~\ref{sec:multi-coupling-expansion}) and 2) higher-order QCD corrections only introduce an explicit renormalisation scale dependence in counterterms with vertices with more than two gluons.
-At NLO these terms are not present in this process so that terms proportional to $\log (\xi_\mathrm{R})$ vanish.
-Both NLOs, however, have contributions from a collinear counterterm that depend on the factorisation scale.
+At NLO these terms are not present for this process so that terms proportional to $\log (\xi_\mathrm{R})$ vanish.
+Both NLOs, however, have contributions from a collinear counterterm that depends on the factorisation scale.
 
-At NLO this process has 63 different initial states, of which there is one photon--photon initial state and 31 initial states with at least one (anti-)quark.
-The remaining 31 given by the transposition of the partons from the first 31 initial states.
+Since this process has a single LO, mixed QCD--EW corrections first appear at next-to-next-to-leading order (NNLO), which includes the QCD correction at $\mathcal{O} (\alphas^2 \alpha^2)$, the EW correction $\mathcal{O} (\alpha^4)$, and a single mixed correction at $\mathcal{O} (\alphas \alpha^3)$.
+
+Note that all initial states have to be taken into account that lead to the same final state.
+This includes the photon-photon initial state, which appears already at LO.
+The particles in the corresponding Feynman diagrams are all colourless, so that it does not receive a QCD correction.
+However, it does receive EW corrections, which also introduce quark--photon contributions, in analogy of QCD corrections introducing quark--gluon contributions.
+%At NLO this process has 63 different initial states, of which there is one photon--photon initial state and 31 initial states with at least one (anti-)quark.
+%The remaining 31 are given by the transposition of the partons from the first 31 initial states.
 
@@
 
-\subsubsection{General characteristics}
-
-In general, we define as leading order all terms for which the sum of the coupling exponents in eq.~\eqref{eq:expansion} is smallest, i.e.\ $k + l = p$, where $p = \min (k+l)$.
-This number is process dependent and usually determined by the number of external particles.
-For many processes there is only one LO, but when a process has multiple quark lines, colourless (photons, \dots) and coloured particles (gluons, \ldots) can be exchanged between them, which allows for more than one leading order.
-To each leading order a higher-order correction with an additional power of $\alphas$ or $\alpha$ can be calculated, which in general leads to at least two next-to-leading order corrections.
-%Sometimes there are higher orders that cannot directly be understood as a correction to a leading order, e.g.\ $\mathrm{p} \mathrm{p} \to \ell \bar{\ell} + \mathrm{jet} + X$, which has one leading order, $\mathcal{O} (\alphas \alpha^2)$, but three next-to-leading orders, one of which is $\mathcal{O} (\alpha^4)$~TODO.
-
-Due to the typical sizes of the couplings $\alphas^2 \sim \alpha$, it is naively expected that within the same order, i.e.\ for fixed $k + l$, terms with larger powers $\alphas^k$ dominate over those with smaller powers; however, in practise this naive expectation is not always true due to dynamic effects.
-Some prominent examples are vector-boson scattering processes~\cite{Biedermann:2017bss,Denner:2019tmn} and top-pair production with another top-pair or a W boson~\cite{Frederix:2017wme}.
-
 \subsection{Grid representation and accuracy}
@@
 
-In this subsection we explain the details of how the phase-space weights $w_{ab}$ in eq.~\eqref{eq:expansion} are represented.
+In this subsection we explain the details of how the phase-space weights $w_{ab}$ in eq.~\eqref{eq:bins-of-diff-xsection} are represented.
 
@@
 Using 4-tuples has the clear advantage of being very easy to implement and test.
-Furthermore, they reproduce the exact numerical value that is also calculated by the Monte Carlo integrator.
+Furthermore, they reproduce the exact numerical value that is also calculated by the MC integrator.
 However, the price one has to pay is the size of the 4-tuples, which scales linearly with the number of phase-space weights $N$.
-Because the uncertainties of Monte Carlo integrators shrink only as $1/\sqrt{N}$, however, this typically means \numrange{e6}{e9} phase-space points are necessary for a good convergence.
+Because the uncertainties of MC integrators shrink only as $1/\sqrt{N}$ this typically means \numrange{e6}{e9} phase-space points are necessary for a good convergence.
 In the case of the NLO Drell--Yan (section~\ref{sec:pineappl-example}) the 4-tuples need roughly TODO~\si{\giga\byte} of storage (see appendix~\ref{app:drell-yan-storage} for an explanation of this number).
@@
 Increasing the number of bins improves the accuracy, but it also increases the space requirements of the grid.
-Interpolation methods offers more precision, while keeping the number of bins constants.
+Interpolation methods offer more precision, while keeping the number of bins constants.
 
 We use the same Lagrange-interpolation grid presented in Ref.~\cite{Carli:2010rw} with the parameters published in Ref.~\cite{Bertone:2014zva}, which give decent precision (see section~\ref{sec:results}).
-The method presented in previous references first maps $(x_1, x_2, Q^2) \mapsto (y_1, y_2, \tau)$, with the maps defined as
+The method presented in the previous references first maps $(x_1, x_2, Q^2) \mapsto (y_1, y_2, \tau)$, with the maps defined as
 \begin{equation}
@@
 and then feeds the variables $(y_1, y_2, \tau)$ into the 3-dimensional Lagrange-interpolation grid with 50 bins in each $y$ direction and 30 bins in $\tau$ direction.
-The interpolation order is 3 for each variable, and only the subspace $[\num{2e7},1] \times [\num{2e-7},1] \times [100,\num{e6}] \subset H$\footnote{In Ref.~\cite{Bertone:2014zva} the upper limit for $Q$ is given as \SI{3162}{\giga\electronvolt} (which corresponds to $Q^2 \approx \SI{e7}{\giga\electronvolt}$), but in the code we found the value given above.} is mapped.
+The interpolation order is 3 for each variable, and only the subspace $[\num{2e7},1] \times [\num{2e-7},1] \times [100,\num{e6}] \subset H$\footnote{In Ref.~\cite{Bertone:2014zva} the upper limit for $Q$ is given as \SI{3162}{\giga\electronvolt} (which corresponds to $Q_\mathrm{max}^2 \approx \SI{e7}{\giga\electronvolt}$), but in the code we found the value $Q_\mathrm{max}^2 = \SI{e6}{\giga\electronvolt\squared}$.} is mapped.
 For the convolution of a grid with a PDF set also the inverse functions are needed, which are
@@
 
-To improve the convergence of phase-space integrations Monte Carlo integrators usually use importance sampling, typically using one or both of VEGAS~\cite{} and multi-channel MC~\cite{}.
+To improve the convergence of phase-space integrations MC integrators usually use importance sampling, typically using one or both of VEGAS~\cite{} and multi-channel MC~\cite{}.
 Both algorithms are adaptive and perform a number of iterations, each iteration trying to improve the convergence by changing the distribution from which phase-space points are sampled.

### 2020-07-01 paper/sec-pineappl.tex
some changes in sec-pineappl

@@
 
-In this paper we present a new library called \textsc{PineAPPL}, which stores phase-space weights of a Monte Carlo (MC) integration independently from the chosen PDFs.
+In this paper we present a new library called \textsc{PineAPPL}, which stores phase-space weights of a Monte Carlo (MC) integration independently from the chosen PDFs,
+including higher-order corrections.
 This separates the task of producing predictions for observables into two steps: 1) the generation of the \emph{grids}, which is how the generated files are called, and 2) the convolution of those grids with a set of PDFs.
-The advantage of this method is that the time-consuming first step has to be done only once and therefore allows for very quick convolutions of a grids with multiple PDF sets.
+The advantage of this method is that the time-consuming step 1) has to be done only once and it allows for very quick convolutions of a given grids with multiple PDF sets.
 
@@
 \end{enumerate}
-This puts \textsc{PineAPPL} in the same category as \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}.
-However, it supports electroweak (EW) predictions/corrections, which are the main interest in this paper.
+This puts \textsc{PineAPPL} in the same category as \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}. With
+respect to the capabilities of these computer codes, \textsc{PineAPPL} makes it possible for the first time to include also higher-order corrections due to electroweak (EW)
+(and in general mixed QCD-EW) effects. Documenting this extension, and how to interface \textsc{PineAPPL} with a general-purpose matrix-element generator, is the main interest of this paper.
+
 In particular, the following features are supported:
 \begin{itemize}
-\item Support for arbitrary fixed-order calculations in powers of $\alpha$, $\alphas$ or combinations thereof, in particular also mixed QCD--EW corrections.
-\item EW corrections require the inclusion of photon-initiated contributions, which are supported as well.
-In fact, \textsc{PineAPPL} allows arbitrary initial-state combinations, e.g.\ leptonic initial states, for which PDFs have been calculated recently~\cite{Buonocore:2020nai}.
-\item Variations of the renormalisation and factorisation scale around the central scale choice are supported, which are needed to estimate the QCD scale uncertainty.
+\item The inclusion of pertrubative corrections (at fixed-order, i.e. without parton-shower matching) with any given set of powers of $\alpha$, $\alphas$, in particular 
+    including mixed QCD--EW corrections.
+\item The support for non-coloured initial-state partons, such as photon-initiated contributions.
+In fact, \textsc{PineAPPL} allows arbitrary initial-state combinations, e.g.\ leptonic initial states~\cite{Bertone:2015lqa,Buonocore:2020nai}.
+\item The estimate of theory uncertainty via variations of the renormalisation and factorisation scale (the electroweak coupling is assumed to be scale independent, 
+    consistently with the most commonly used renormalisation schemes).
 %\item Support for all-order predictions coming from a resummation calculation or a photon-/parton-shower, which are important for some observables (see section~\ref{sec:results}),
 \end{itemize}
-On a more technical level, we further point out the following differences of \textsc{PineAPPL}:
+On a more technical level, we further point out the following differences and improvements in \textsc{PineAPPL}:
 \begin{itemize}
-\item Earlier experiments with APPLgrid (only QCD corrections) showed that it uses a substantial amount memory (close to \SI{80}{\giga\byte}), if a grid for a differential distributions with more than 10 bins was generated.
+    \item \textsc{APPLgrid} typically required a substantial amount of memory (close to \SI{80}{\giga\byte}), if a grid for a 
+        differential distributions with more than 10 bins was generated.
 The memory usage is substantially reduced (roughly \SI{1}{\giga\byte}) after \enquote{optimisation} of the grids, i.e.\ an optimisation of the grid representation in memory.
-However, this means that this two-step procedure of 1) producing an unoptimised grid and 2) filling an optimised grid effectively limits the bins to a small number.
+However, this required a two-step procedure: first, to produce an unoptimised grid in order to identify those parts where
+the cross section is either zero or extremely suppressed; second, after those parts are removed, to fill
+an optimised grid with a a small number of bins.
 \textsc{PineAPPL} avoids this by using a more space-efficient representation from the start.
 \item \textsc{PineAPPL} offers an easy-to-use interface written in the C programming language, to allow MC integrators to read and write \textsc{PineAPPL} grids.
-C was chosen because it plays well with Fortran and C++, in which most MC integrators are written.
-The interface consists of roughly 30 functions of which basically only a handful are needed.
+C was chosen because it can be easily interfaced with both Fortran and C++, in which most MC integrators are written.
+The interface consists of roughly 30 functions, among which only a handful are needed in practice.
 See appendix~\ref{app:example-program} for an example.
 %\textsc{PineAPPL} itself is written in Rust (see appendix~\ref{app:installation} for installation instructions).
-\item The program \texttt{pineappl}, which performs convolutions on the command line (see appendix~\ref{app:pineappl-demo}), without requiring the user to write a new program.
+\item The shell command \texttt{pineappl}, which performs convolutions on the c
+    ommand line (see appendix~\ref{app:pineappl-demo}), without requiring the user to write a new program.
 In addition to convolutions, it can also print how the luminosity function is constructed, which perturbative orders are stored, their size, the size of each partonic channel, etc., separately for each bin.
@@
 \end{itemize}
-For \textsc{mg5\_aMC@NLO}~\cite{Alwall:2014hca,Frederix:2018nkq} the interfacing code is already implemented\footnote{It can be downloaded from \url{https://code.launchpad.net/~amcblast/+junk/3.0.2}}, which is intended to replace the \textsc{aMCfast}~\cite{Bertone:2014zva} interface.
-Its usage is very similar to that of \textsc{mg5\_aMC 2}+\textsc{aMCfast}+\textsc{APPLgrid}.
-However, using \textsc{PineAPPL} is much faster especially for small runs, because the grids do not need to be optimised and are merged faster.
+
+We have interfaced \textsc{PineAPPL} with the new version (v3+) of
+\textsc{mg5\_aMC@NLO}~\cite{Alwall:2014hca,Frederix:2018nkq}\footnote{It can be downloaded 
+    from \url{https://code.launchpad.net/~amcblast/+junk/3.0.2}, and will soon be merged in the official code release}, where it will replace the \textsc{aMCfast}~\cite{Bertone:2014zva} interface.
+Its usage is very similar to that of \textsc{mg5\_aMC v2}+\textsc{aMCfast}+\textsc{APPLgrid}.
+In practice, using \textsc{PineAPPL} leads to substantially faster run times, in particular for simple processes, because the grids do not need to be optimised 
+and their combination is faster.
 See appendix~\ref{app:sample-runcard} for an example of a runcard.
 
-Interfacing code for other MC generators should be easy to write, see appendix~\ref{app:example-program} for a small example program.
+Building an interface for other MC generators poses no difficulties, see appendix~\ref{app:example-program} for a small example program.
 

### 2020-07-07 paper/sec-pineappl.tex
Add comment about different phase spaces
Add a few fixes to section 2

@@
 given by the MC integrator.
+Note that in the above equation we do not differentiate w.r.t.\ which phase-space integration (Born, real, subtraction term, etc.) the weight came from, because e.g.\ for a certain NLO all weights are filled into a single grid with fixed $k$ and $l$ and $m=n=0$.
+
 Using eq.~\eqref{eq:expansion} and
@@
 
-Since this process has a single LO, mixed QCD--EW corrections first appear at next-to-next-to-leading order (NNLO), which includes the QCD correction at $\mathcal{O} (\alphas^2 \alpha^2)$, the EW correction $\mathcal{O} (\alpha^4)$, and a single mixed correction at $\mathcal{O} (\alphas \alpha^3)$.
+Since this process has a single LO, mixed QCD--EW corrections first appear at next-to-next-to-leading order (NNLO), which include the QCD correction at $\mathcal{O} (\alphas^2 \alpha^2)$, the EW correction $\mathcal{O} (\alpha^4)$, and a single mixed correction at $\mathcal{O} (\alphas \alpha^3)$.
 
 Note that all initial states have to be taken into account that lead to the same final state.
-This includes the photon-photon initial state, which appears already at LO.
-The particles in the corresponding Feynman diagrams are all colourless, so that it does not receive a QCD correction.
-However, it does receive EW corrections, which also introduce quark--photon contributions, in analogy of QCD corrections introducing quark--gluon contributions.
+This includes the photon--photon initial state, which appears already at LO.
+In the corresponding Feynman diagrams all particles are colourless, so that this subprocess only receives EW and mixed QCD--EW corrections, but never (pure) QCD corrections.
+The EW corrections also introduce quark--photon contributions, in analogy of QCD corrections introducing quark--gluon contributions.
+
 %At NLO this process has 63 different initial states, of which there is one photon--photon initial state and 31 initial states with at least one (anti-)quark.
@@
 
-For each combination $(a,b,k,l,m,n,o)$ we save the following 4-tuples:
+For each combination $(a,b,k,l,m,n,o)$ we save the following 4-tuples,
 \begin{equation}
-\left\{ x_1^i, x_2^i, Q^2_i, w^{(k,l,m,n,o)}_{ab} (x_1^i, x_2^i, Q^2_i, \mathcal{O}_i) \right\}_{i=1}^N \text{,} \label{eq:four-tuples}
+\left\{ x_1^i, x_2^i, Q^2_i, w^{(k,l,m,n,o)}_{ab} (x_1^i, x_2^i, Q^2_i, \mathcal{O}_i) \right\}_{i=1}^N \text{.} \label{eq:four-tuples}
 \end{equation}

### 2020-07-07 paper/sec-pineappl.tex
Add corrections to Marco's corrections

@@
 
-In this paper we present a new library called \textsc{PineAPPL}, which stores phase-space weights of a Monte Carlo (MC) integration independently from the chosen PDFs,
-including higher-order corrections.
+In this paper we present a new library called \textsc{PineAPPL}, which stores phase-space weights of a Monte Carlo (MC) integration of a fixed-order calculation independently from the chosen PDFs.
 This separates the task of producing predictions for observables into two steps: 1) the generation of the \emph{grids}, which is how the generated files are called, and 2) the convolution of those grids with a set of PDFs.
-The advantage of this method is that the time-consuming step 1) has to be done only once and it allows for very quick convolutions of a given grids with multiple PDF sets.
+The advantage of this method is that the time-consuming step 1) has to be done only once and, therefore, allows for very quick convolutions of a given grid with multiple PDF sets.
 
@@
 \end{enumerate}
-This puts \textsc{PineAPPL} in the same category as \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}. With
-respect to the capabilities of these computer codes, \textsc{PineAPPL} makes it possible for the first time to include also higher-order corrections due to electroweak (EW)
-(and in general mixed QCD-EW) effects. Documenting this extension, and how to interface \textsc{PineAPPL} with a general-purpose matrix-element generator, is the main interest of this paper.
+This puts \textsc{PineAPPL} in the same category as \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}.
+With respect to the capabilities of these computer codes, \textsc{PineAPPL} makes it possible for the first time to include also higher-order corrections due to electroweak (EW), and in general mixed QCD--EW, effects.
+Documenting this extension, and how to interface \textsc{PineAPPL} with a general-purpose matrix-element generator, is the main interest of this paper.
 
@@
 \begin{itemize}
-\item The inclusion of pertrubative corrections (at fixed-order, i.e. without parton-shower matching) with any given set of powers of $\alpha$, $\alphas$, in particular 
-    including mixed QCD--EW corrections.
+\item The inclusion of perturbative corrections (fixed-order, i.e.\ without parton-shower matching) with any given set of powers of $\alpha$, $\alphas$, in particular including mixed QCD--EW corrections.
 \item The support for non-coloured initial-state partons, such as photon-initiated contributions.
 In fact, \textsc{PineAPPL} allows arbitrary initial-state combinations, e.g.\ leptonic initial states~\cite{Bertone:2015lqa,Buonocore:2020nai}.
-\item The estimate of theory uncertainty via variations of the renormalisation and factorisation scale (the electroweak coupling is assumed to be scale independent, 
-    consistently with the most commonly used renormalisation schemes).
+\item The estimate of theory uncertainty via variations of the renormalisation and factorisation scale (the electroweak coupling is assumed to be scale-independent, consistently with the commonest renormalisation schemes).
 %\item Support for all-order predictions coming from a resummation calculation or a photon-/parton-shower, which are important for some observables (see section~\ref{sec:results}),
@@
 \begin{itemize}
-    \item \textsc{APPLgrid} typically required a substantial amount of memory (close to \SI{80}{\giga\byte}), if a grid for a 
-        differential distributions with more than 10 bins was generated.
+\item \textsc{APPLgrid} typically required a substantial amount of memory (close to \SI{120}{\giga\byte} for Drell--Yan), if a grid for a differential distributions with more than 10 bins was generated.
 The memory usage is substantially reduced (roughly \SI{1}{\giga\byte}) after \enquote{optimisation} of the grids, i.e.\ an optimisation of the grid representation in memory.
-However, this required a two-step procedure: first, to produce an unoptimised grid in order to identify those parts where
-the cross section is either zero or extremely suppressed; second, after those parts are removed, to fill
-an optimised grid with a a small number of bins.
+However, this required a two-step procedure: first, to produce an unoptimised grid in order to identify those parts where the cross section is either zero or extremely suppressed; second, after those parts are removed, to fill an optimised grid with a small number of bins.
 \textsc{PineAPPL} avoids this by using a more space-efficient representation from the start.
@@
 %\textsc{PineAPPL} itself is written in Rust (see appendix~\ref{app:installation} for installation instructions).
-\item The shell command \texttt{pineappl}, which performs convolutions on the c
-    ommand line (see appendix~\ref{app:pineappl-demo}), without requiring the user to write a new program.
+\item The shell command \texttt{pineappl}, which performs convolutions on the command line (see appendix~\ref{app:pineappl-demo}), without requiring the user to write a new program.
 In addition to convolutions, it can also print how the luminosity function is constructed, which perturbative orders are stored, their size, the size of each partonic channel, etc., separately for each bin.
@@
 
-We have interfaced \textsc{PineAPPL} with the new version (v3+) of
-\textsc{mg5\_aMC@NLO}~\cite{Alwall:2014hca,Frederix:2018nkq}\footnote{It can be downloaded 
-    from \url{https://code.launchpad.net/~amcblast/+junk/3.0.2}, and will soon be merged in the official code release}, where it will replace the \textsc{aMCfast}~\cite{Bertone:2014zva} interface.
+We have interfaced \textsc{PineAPPL} with the new version (v3+) of \textsc{mg5\_aMC@NLO}~\cite{Alwall:2014hca,Frederix:2018nkq}\footnote{It can be downloaded from \url{https://code.launchpad.net/~amcblast/+junk/3.0.2}, and will soon be merged in the official code release.}, where it will replace the \textsc{aMCfast}~\cite{Bertone:2014zva} interface.
 Its usage is very similar to that of \textsc{mg5\_aMC v2}+\textsc{aMCfast}+\textsc{APPLgrid}.

### 2020-07-07 nnpdf31_proc/ATLAS_TTB_DIFF_8TEV_LJ_TTMNORM/analysis.f
Various mistakes in the analysis files corrected

@@ -42,6 +42,7 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
       double precision p(0:4,nexternal)
       double precision wgts(*)
       double precision pttx(0:3), mtt
+      double precision dot
 
       do i=0,3
          pttx(i)=p(i,3)+p(i,4)

### 2020-07-07 nnpdf31_proc/ATLAS_TTB_DIFF_8TEV_LJ_TTRAPNORM/analysis.f

@@ -43,7 +43,7 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
         pttx(i)=p(i,3)+p(i,4)
       enddo
       
-      yttx  = getrapidity(pttx(0,3), pttx(3,3))
+      yttx  = getrapidity(pttx(0), pttx(3))
 
       call HwU_fill(1,yttx,wgts)
       call HwU_fill(2,yttx,wgts)

### 2020-07-07 paper/sec-doublecounting.tex
added feynman diags

@@
 justified beyond LO\@. Indeed, at $\mathcal O(\alpha^3)$, the reaction $q \gamma \to \ell^+ \ell^- q$ becomes possible, which
-includes both kind of topologies. {\bf MZ add Feynman diags}
+includes both kind of topologies, see Fig.~\ref{fig:dy-pi}. 
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.6\textwidth, trim=0.cm 11cm 0.cm 2cm, clip=True]{figures/dy-pi.pdf}\\
+    \caption{\label{fig:dy-pi}
+    Photon-induced (left) and quark-induced (right) contributions to the Drell-Yan process. In black, the LO process is shown.
+    In red, the initial-state splitting leading to the real-emission $q \gamma \to \ell^+ \ell^- q$ is highlighted. Such a 
+    real emission enters in the NLO EW corrections.}
+\end{figure}
 

### 2020-07-13 paper/sec-pineappl.tex
Expand Lagrange-interpolation grid section

@@
 
+Following ref.~\cite{Carli:2010rw} (see eq.~(17) therein), we divide the weights before filling them into the grid by the function
+\begin{equation}
+\omega (x_1, x_2) = \left( \frac{\sqrt{x_1}}{1 - 0.99 x_1} \right)^3 \left( \frac{\sqrt{x_2}}{1 - 0.99 x_2} \right)^3 \text{.}
+\end{equation}
+This flattens the interpolated function in the region $x \to 1$, where the PDFs are small and tend towards zero, and enhances the function in the small-$x$ region.
+The effect of this step is an improvement of the accuracy that depends on the initial states and the process, but it can be as large as a factor of \numrange{10}{100} (one or two more correct digits), see section~TODO.
+Before performing a convolution this step is inverted by simply multiplying the interpolated grid values with $\omega (x_1, x_2)$.
+
+The final step is filling the weights into the grid, which maps the variables $(y_1, y_2, \tau)$ onto the 3-dimensional Lagrange-interpolation grid with $N_y = 50$ points in each $y$ direction and $N_\tau = 30$ points in $\tau$ direction.
+The interpolation orders $s_y$ and $s_\tau$ are 3 for each dimension, and only the subspace $[\num{2e-7},1] \times [\num{2e-7},1] \times [\num{e2},\num{e6}] \subset H$\footnote{In ref.~\cite{Bertone:2014zva} the upper limit for $Q$ is given as \SI{3162}{\giga\electronvolt} (which corresponds to $Q_\mathrm{max}^2 \approx \SI{e7}{\giga\electronvolt}$), but in the code we found the value $Q_\mathrm{max}^2 = \SI{e6}{\giga\electronvolt\squared}$.} is mapped.
+
+\begin{figure}
+\centering
+\parbox{0.6\textwidth}{\includegraphics{figures/grid-insertion}}
+\begin{tabular}{ll}
+\toprule
+$u_1$/$u_2$ & $x_1$/$x_2$ \\
+\midrule
+0 & \num{1.00e0} \\
+1 & \num{6.36e-1} \\
+2 & \num{3.20e-1} \\
+3 & \num{9.96e-2} \\
+4 & \num{1.57e-2} \\
+5 & \num{1.74e-3} \\
+6 & \num{1.81e-4} \\
+7 & \num{1.87e-5} \\
+8 & \num{1.93e-6} \\
+9 & \num{2.00e-7} \\
+\bottomrule
+\end{tabular}
+\caption{Example for a 2-dimensional $10 \times 10$ grid, which is being filled at the location marked with the small black square, at $(5.8,4.8)$.
+Each side of the grey square starting at $k_i = 4$ and $k_j = 3$ has a length of $N_y + 1 = 4$.
+This square marks the grid values that are being updated using eq.~\eqref{eq:interpolation}.
+The table on the right-hand side marks gives the parton-momentum fractions for each grid point.
+Note that around $u=3$ the values are linearly distributed, then logarithmically.}
+\label{fig:grid}
+\end{figure}
+
+To illustrate the filling step we give an example in figure~\ref{fig:grid}, where, for simplicity, we assume we have chosen a static scale, so that we do not need to interpolate $\tau$ direction, and where we also limited the number of grid points to $N_y = 10$.
+To each grid point a numerical value $a_{i,j}$ is associated, and the set of all numerical values $\{ a_{i,j} \}$ for all grid indices $(i,j) \in [0,N_y) \times [0,N_y)$ constitute \enquote{the grid}.
+Inserting a specific weight $W = w (x_1, x_2) / \omega(x_1, x_2)$ into the grid is shown in figure~\ref{fig:grid} as a small black square, inside the larger grey one.
+We have defined the grid points at specific positions, but the points given by the MC will land somewhere between them\footnote{The technical term for this interpolation problem is sometimes called \emph{subtabulation}.}.
+The interpolation order $s_y$ then defines a square with length $s_y + 1$ around its centre $(u_1(y_1(x_1)),u_2(y_2(x_2)))$, given by the MC.
+All grid points with indices $(i,j)$ covered by the grey square are then updated according to the following formula:
+\begin{equation}
+a_{i,j} = a_{i,j} + I_i(u(y(x_1))) I_j(u(y(x_2))) W(x_1,x_2) / \omega(x_1,x_2)
+\label{eq:interpolation}
+\end{equation}
+with the Lagrange basis functions
+\begin{equation}
+I_i (u) = \prod_{\substack{k=k_i \\ k \neq i}}^{k_i + s_y} \frac{u-k}{i-k}
+\end{equation}
+where the product runs over all indices of the grid points covered by the grey square in figure~\ref{fig:grid}, starting the smallest index in the square, $k_i$ and $k_j$.
+We also remapped
+\begin{equation}
+u(y) = \frac{y-y_\text{min}}{\Delta y} \text{,} \quad
+\end{equation}
+using $y_\text{min} = y(x_\text{max})$ and $y_\text{max} = y(x_\text{min})$ and the grid spacing $\Delta y = (y_\text{max} - y_\text{min})/(N_y-1)$, so that the integer part of $u(y)$ gives the grid index, e.g.\ $u(y_\text{min}) = 0$ and $u(y_\text{max}) = N_y - 1$.
+
+\begin{figure}
+\centering
+TODO
+\caption{TODO}
+\label{fig:example-grid}
+\end{figure}
+
+Finally, figure~\ref{fig:example-grid} shows an example of a convoluted grid, but differential in $x_1$ and $x_2$.
+
 \subsubsection{Combination of differently weighed phase-spaces points}

### 2020-07-13 paper/figures/compile.sh

@@ -1,0 +1,3 @@
+#!/bin/bash
+
+latexmk -pdf grid-insertion

### 2020-07-15 paper/plotscript/pineappl_plot.py
adding plot script and figures

@@ -1,0 +1,164 @@
+#!/usr/env/bin python
+"""
+Plotting script for pineappl grid analysis.
+"""
+import os
+import argparse
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import matplotlib.patches as mpatches
+
+
+parser = argparse.ArgumentParser()
+parser.add_argument('--qcd', default=None, type=str, required=True)
+parser.add_argument('--qcdew', default=None, type=str, required=True)
+parser.add_argument('--nbins', default=None, nargs="+", required=True)
+parser.add_argument('--bins', default=None, nargs="+", required=True)
+parser.add_argument('--xscale', default='linear', type=str)
+parser.add_argument('--yscale', default='linear', type=str)
+parser.add_argument('--title', default='Use --title option', type=str)
+parser.add_argument('--ylabel', default='Use --ylabel option', type=str)
+parser.add_argument('--xlabel', default='Use --xlabel option', type=str)
+parser.add_argument('--ylim', nargs="+", default=None, type=str)
+parser.add_argument('--xlim', nargs="+", default=None, type=str)
+parser.add_argument('--legend', default='best', type=str)
+parser.add_argument('--legend-lower', default='best', type=str)
+parser.add_argument('--multiply', default=1, type=float)
+parser.add_argument('--output', default='pineappl_accuracy.pdf', type=str)
+args = parser.parse_args()
+
+
+def load_results_log(logfolder, bins, nbins):
+    """Load data from results.log.
+
+    Args:
+        logfolder (str): path to pineappl output.
+
+    Returns:
+        Pandas dataframe containing the results.log data.
+    """
+    with open(f'{logfolder}/results.log', 'r') as f:
+        minbin = int(nbins[0])
+        maxbin = int(nbins[1])
+        data_from_file = f.readlines()[3+minbin:3+maxbin+1]
+        data = np.zeros(shape=(maxbin-minbin+2, 7))
+
+        bindex = minbin
+        for w, line in enumerate(data_from_file):
+            index = 0
+            for j in line.split(' '):
+                if j == '':
+                    continue
+                data[w, index] = np.float64(j)
+                index += 1
[…]

### 2020-07-15 paper/plotscript/run_plots.sh

@@ -1,0 +1,101 @@
+#!/bin/bash
+
+# ATLAS Z HIGH Mass
+python pineappl_plot.py \
+    --qcd ATLASZHIGHMASS49FB-20200625102151 \
+    --qcdew ATLASZHIGHMASS49FB-20200623223328 \
+    --nbins 0 12 \
+    --bins 116 130 150 170 190 210 230 250 300 400 500 700 1000 1500 \
+    --title "ATLAS high-mass Drell-Yan at $\sqrt{s}=7$ TeV" \
+    --output "pineappl_ATLASZHIGHMASS49FB.pdf" \
+    --ylabel "$ \mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}} $ [pb]" \
+    --xlabel "$ M_{\ell \bar{\ell}}$ [GeV]" \
+    --yscale "log" \
+    --xscale "log" \
+    --legend "upper right" \
+    --legend-lower "upper left" \
+    --xlim 100 1800
+
+# CMS bin1
+python pineappl_plot.py \
+    --qcd CMSDY2D11-20200625180039 \
+    --qcdew CMSDY2D11-20200626080745  \
+    --nbins 0 23 \
+    --bins 0.0 0.1 0.2 0.3 0.4 0.5 0.6 0.7 0.8 0.9 1.0 1.1 1.2 1.3 1.4 1.5 1.6 1.7 1.8 1.9 2.0 2.1 2.2 2.3 2.4 \
+    --title "CMS 2D Drell-Yan 2011, $ 20 < M_{\ell \bar{\ell}} < 30 $ GeV" \
+    --output "pineappl_CMSDY2D11_bin1.pdf" \
+    --ylabel "$ \mathrm{d} \sigma / \mathrm{d} y_{\ell \bar{\ell}} $ [pb]" \
+    --xlabel " $ y_{\ell \bar{\ell}} $ " \
+    --legend "lower left" \
+    --legend-lower "upper left" \
+    --multiply 10
+
+# CMS bin2
+python pineappl_plot.py \
+    --qcd CMSDY2D11-20200625180039 \
+    --qcdew CMSDY2D11-20200626080745  \
+    --nbins 24 47 \
[…]

### 2020-07-15 paper/sec-results.tex
including plots in draft

@@
 
-SC
+\begin{figure}
+    \centering
+    \includegraphics[width=0.33\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB}
+    \caption{PineAPPL comparison for ATLAS high-mass Drell-Yan.}
+    \label{fig:atlaszhighmass49fb}
+\end{figure}
 
-For datasets in 3.1qed (+DY2), compute pure NLO QCD (born) vs NLO QCD + NLO EW (dressed) FKtables and:\\
-- compute data/prediction plots\\
-- compute chi2\\
+\begin{figure}
+    \centering
+    \includegraphics[width=0.33\textwidth]{figures/pineappl_CMSDY2D11_bin1}\includegraphics[width=0.33\textwidth]{figures/pineappl_CMSDY2D11_bin2}\includegraphics[width=0.33\textwidth]{figures/pineappl_CMSDY2D11_bin3}
+    \includegraphics[width=0.33\textwidth]{figures/pineappl_CMSDY2D11_bin4}\includegraphics[width=0.33\textwidth]{figures/pineappl_CMSDY2D11_bin5}\includegraphics[width=0.33\textwidth]{figures/pineappl_CMSDY2D11_bin6}
+    \caption{PineAPPL comparison for CMS 2D Drell-Yan.}
+    \label{fig:cmsdy2d11}
+\end{figure}
 

### 2020-07-15 paper/sec-results.tex
updating permille label, increasing figure sizes

--- 2020-06-25 paper/sec-results.tex
@@
 
-SC
+\begin{figure}
+    \centering
+    \includegraphics[width=0.4\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB}
+    \caption{PineAPPL comparison for ATLAS high-mass Drell-Yan.}
+    \label{fig:atlaszhighmass49fb}
+\end{figure}
 
-For datasets in 3.1qed (+DY2), compute pure NLO QCD (born) vs NLO QCD + NLO EW (dressed) FKtables and:\\
-- compute data/prediction plots\\
-- compute chi2\\
+\begin{figure}
+    \centering
+    \includegraphics[width=0.4\textwidth]{figures/pineappl_CMSDY2D11_bin1}\includegraphics[width=0.4\textwidth]{figures/pineappl_CMSDY2D11_bin2}
+    \includegraphics[width=0.4\textwidth]{figures/pineappl_CMSDY2D11_bin3}\includegraphics[width=0.4\textwidth]{figures/pineappl_CMSDY2D11_bin4}
+    \includegraphics[width=0.4\textwidth]{figures/pineappl_CMSDY2D11_bin5}\includegraphics[width=0.4\textwidth]{figures/pineappl_CMSDY2D11_bin6}
+    \caption{PineAPPL comparison for CMS 2D Drell-Yan.}
+    \label{fig:cmsdy2d11}
+\end{figure}
 

### 2020-07-15 paper/plotscript/pineappl_plot.py

@@ -121,7 +121,7 @@ def plot_pineappl(qcd_data, qcdew_data):
                         (qcd_data['pineappl']/qcd_data['mg5_amc'] - 1)*1000,
                         step='post', color=colors[1],
                         label='NLO QCD')
-    axs[2].set_ylabel('PineAPPL / MC [‰]')
+    axs[2].set_ylabel('PineAPPL / MC - 1 [‰]')
     axs[2].legend(loc=args.legend_lower, frameon=False)
 
     for i in range(2):

### 2020-07-15 paper/plotscript/pineappl_plot.py
indenting plot script

@@ -60,7 +60,7 @@ def load_results_log(logfolder, bins, nbins):
         data[:, 0:3] *= args.multiply
         columns = ['pineappl', 'mg5_amc', 'mg5_amc_unc', 'sigmas',
                    'permille', 'bin']
-        df = pd.DataFrame(data[:,:-1], columns=columns)
+        df = pd.DataFrame(data[:, :-1], columns=columns)
     return df
 
 
@@ -92,16 +92,20 @@ def plot_pineappl(qcd_data, qcdew_data):
 
     # physics plot ratio
     axs[1].fill_between(qcd_data['bin'],
-                        (qcd_data['mg5_amc']-qcd_data['mg5_amc_unc'])/qcdew_data['mg5_amc'],
-                        (qcd_data['mg5_amc']+qcd_data['mg5_amc_unc'])/qcdew_data['mg5_amc'],
+                        (qcd_data['mg5_amc']-qcd_data['mg5_amc_unc']) /
+                        qcdew_data['mg5_amc'],
+                        (qcd_data['mg5_amc']+qcd_data['mg5_amc_unc']) /
+                        qcdew_data['mg5_amc'],
                         step='post', color=colors[0], alpha=alpha)
     axs[1].fill_between(qcd_data['bin'],
                         qcd_data['pineappl']/qcdew_data['mg5_amc'],
                         qcd_data['pineappl']/qcdew_data['mg5_amc'],
                         step='post', color=colors[0])
     axs[1].fill_between(qcdew_data['bin'],
-                        (qcdew_data['mg5_amc']-qcdew_data['mg5_amc_unc'])/qcdew_data['mg5_amc'],
-                        (qcdew_data['mg5_amc']+qcdew_data['mg5_amc_unc'])/qcdew_data['mg5_amc'],
+                        (qcdew_data['mg5_amc']-qcdew_data['mg5_amc_unc']
+                         )/qcdew_data['mg5_amc'],
+                        (qcdew_data['mg5_amc']+qcdew_data['mg5_amc_unc']
+                         )/qcdew_data['mg5_amc'],
                         step='post', color=colors[1], alpha=alpha)
     axs[1].fill_between(qcdew_data['bin'],
                         qcdew_data['pineappl']/qcdew_data['mg5_amc'],
@@ -111,8 +115,10 @@ def plot_pineappl(qcd_data, qcdew_data):
 
     # ratio pineappl/mg5 qcd
     axs[2].fill_between(qcdew_data['bin'],
[…]

### 2020-07-15 paper/plotscript/pineappl_plot.py
updating atlas normalization and removing script (moving to pineapplgrids repo)

@@ -1,170 +1,0 @@
-#!/usr/env/bin python
-"""
-Plotting script for pineappl grid analysis.
-"""
-import os
-import argparse
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-import matplotlib.patches as mpatches
-
-
-parser = argparse.ArgumentParser()
-parser.add_argument('--qcd', default=None, type=str, required=True)
-parser.add_argument('--qcdew', default=None, type=str, required=True)
-parser.add_argument('--nbins', default=None, nargs="+", required=True)
-parser.add_argument('--bins', default=None, nargs="+", required=True)
-parser.add_argument('--xscale', default='linear', type=str)
-parser.add_argument('--yscale', default='linear', type=str)
-parser.add_argument('--title', default='Use --title option', type=str)
-parser.add_argument('--ylabel', default='Use --ylabel option', type=str)
-parser.add_argument('--xlabel', default='Use --xlabel option', type=str)
-parser.add_argument('--ylim', nargs="+", default=None, type=str)
-parser.add_argument('--xlim', nargs="+", default=None, type=str)
-parser.add_argument('--legend', default='best', type=str)
-parser.add_argument('--legend-lower', default='best', type=str)
-parser.add_argument('--multiply', default=1, type=float)
-parser.add_argument('--output', default='pineappl_accuracy.pdf', type=str)
-args = parser.parse_args()
-
-
-def load_results_log(logfolder, bins, nbins):
-    """Load data from results.log.
-
-    Args:
-        logfolder (str): path to pineappl output.
-
-    Returns:
-        Pandas dataframe containing the results.log data.
-    """
-    with open(f'{logfolder}/results.log', 'r') as f:
-        minbin = int(nbins[0])
-        maxbin = int(nbins[1])
-        data_from_file = f.readlines()[3+minbin:3+maxbin+1]
-        data = np.zeros(shape=(maxbin-minbin+2, 7))
-
-        bindex = minbin
-        for w, line in enumerate(data_from_file):
-            index = 0
-            for j in line.split(' '):
-                if j == '':
-                    continue
-                data[w, index] = np.float64(j)
-                index += 1
-            data[w, index] = np.float64(bins[w])
[…]

### 2020-07-15 paper/plotscript/run_plots.sh

@@ -1,101 +1,0 @@
-#!/bin/bash
-
-# ATLAS Z HIGH Mass
-python pineappl_plot.py \
-    --qcd ATLASZHIGHMASS49FB-20200625102151 \
-    --qcdew ATLASZHIGHMASS49FB-20200623223328 \
-    --nbins 0 12 \
-    --bins 116 130 150 170 190 210 230 250 300 400 500 700 1000 1500 \
-    --title "ATLAS high-mass Drell-Yan at $\sqrt{s}=7$ TeV" \
-    --output "pineappl_ATLASZHIGHMASS49FB.pdf" \
-    --ylabel "$ \mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}} $ [pb]" \
-    --xlabel "$ M_{\ell \bar{\ell}}$ [GeV]" \
-    --yscale "log" \
-    --xscale "log" \
-    --legend "upper right" \
-    --legend-lower "upper left" \
-    --xlim 100 1800
-
-# CMS bin1
-python pineappl_plot.py \
-    --qcd CMSDY2D11-20200625180039 \
-    --qcdew CMSDY2D11-20200626080745  \
-    --nbins 0 23 \
-    --bins 0.0 0.1 0.2 0.3 0.4 0.5 0.6 0.7 0.8 0.9 1.0 1.1 1.2 1.3 1.4 1.5 1.6 1.7 1.8 1.9 2.0 2.1 2.2 2.3 2.4 \
-    --title "CMS 2D Drell-Yan 2011, $ 20 < M_{\ell \bar{\ell}} < 30 $ GeV" \
-    --output "pineappl_CMSDY2D11_bin1.pdf" \
-    --ylabel "$ \mathrm{d} \sigma / \mathrm{d} y_{\ell \bar{\ell}} $ [pb]" \
-    --xlabel " $ y_{\ell \bar{\ell}} $ " \
-    --legend "lower left" \
-    --legend-lower "upper left" \
-    --multiply 10
-
-# CMS bin2
-python pineappl_plot.py \
-    --qcd CMSDY2D11-20200625180039 \
-    --qcdew CMSDY2D11-20200626080745  \
-    --nbins 24 47 \
[…]

### 2020-07-19 nnpdf31_proc/ATLAS_TTB_DIFF_8TEV_LJ_TTRAPNORM/analysis.f
Dynamical scale for top pair production proceses

@@ -8,9 +8,9 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
 
       call set_error_estimation(1)
       call HwU_inithist(nwgt,weights_info)
-      call HwU_book(1,'tt rap ', 3,0.0d0,0.9d0)
-      call HwU_book(2,'tt rap ', 1,0.9d0,1.3d0)
-      call HwU_book(3,'tt rap ', 1,1.3d0,2.5d0)
+      call HwU_book(1,'t-tx pair rap ', 3,0.0d0,0.9d0)
+      call HwU_book(2,'t-tx pair rap ', 1,0.9d0,1.3d0)
+      call HwU_book(3,'t-tx pair rap ', 1,1.3d0,2.5d0)
       return
       end
 
@@ -32,7 +32,7 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
       include 'nexternal.inc'
       integer istatus(nexternal)
       integer iPDG(nexternal)
-      integer ibody
+      integer ibody  
       integer i
       double precision p(0:4,nexternal)
       double precision wgts(*)
@@ -42,8 +42,8 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
       do i=0,3
         pttx(i)=p(i,3)+p(i,4)
       enddo
-      
-      yttx  = getrapidity(pttx(0), pttx(3))
+
+      yttx= getrapidity(pttx(0), pttx(3))
 
       call HwU_fill(1,yttx,wgts)
       call HwU_fill(2,yttx,wgts)
@@ -52,7 +52,7 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
  999  return      
       end
 
-ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
 
       function getrapidity(en,pl)
       implicit none

### 2020-07-19 paper/paper.tex
Rewrite PineAPPL section
Use the alphas macro
Fix small Latex mistakes
Use a proper font
Add appendix about PineAPPL to the paper
Rewrite parts of section 2
Add a few fixes to section 2
Expand Lagrange-interpolation grid section
Add first draft of the results section

--- 2020-03-30 paper/paper.tex
@@
 
+\usepackage[UKenglish]{babel}
+\usepackage{booktabs}
+\usepackage{csquotes}
 \usepackage{jheppub}
 \usepackage[T1]{fontenc}
+\usepackage{listings}
+\usepackage{lmodern}
+\usepackage[binary-units=true,detect-weight=true]{siunitx}
+\usepackage{xcolor}
 
-\newcommand{\alphas}{\alpha_{S}}
+\newcommand{\alphas}{\alpha_\mathrm{s}}
 
@@
 
-\author[a,b]{S. Carrazza,}
+\author[a]{S. Carrazza,}
 \author[b]{E. Nocera,}
@@
 
-\affiliation[a]{Tif Lab, Dipartimento di Fisica, Universit\`a di Milano and INFN, Sezione di Milano, 20133 Milano, Italy}
-\affiliation[b]{Nikhef Theory Group, Science Park 105, 1098 XG Amsterdam, The Netherlands}
+\affiliation[a]{Tif Lab, Dipartimento di Fisica, 
+Universit\`a di Milano and INFN, Sezione di Milano, 20133 Milano, Italy}
+\affiliation[b]{Nikhef Theory Group, Science Park 105, 1098 XG Amsterdam, 
+The Netherlands}
 
@@
 
-C.S. is supported by the European Research Council under the European Unions 
-Horizon 2020 research and innovation Programme (grant agreement no. 740006).
+C.S.\ is supported by the European Research Council under the European Unions
+Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
 
-\section{More details about \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
-\label{app:pineappl-interface}
-
-\input{pineappl-appendix}
+\input{app-pineappl}
 

### 2020-07-19 paper/sec-results.tex
increasing figure size
Add first draft of the results section

--- 2020-06-25 paper/sec-results.tex
@@
 
-SC
+In this section we present a comparison of NLO QCD and NLO QCD+EW predictions for three different processes: DY lepton-pair production, top-pair production, and finally Z-boson (lepton-pair) production with non-zero transverse momentum at the LHC.
 
-For datasets in 3.1qed (+DY2), compute pure NLO QCD (born) vs NLO QCD + NLO EW (dressed) FKtables and:\\
-- compute data/prediction plots\\
-- compute chi2\\
+Our first aim is a technical one, namely to show the validity of the results reconstructed with the \textsc{PineAPPL} grids introduced in section~\ref{sec:pineappl} and to give a measure of accuracy that can be achieved with them.
+The second aim is to quantify the size of the EW corrections for the setups defined by the experimental collaborations for the processes given below.
 
-ERN 7 Apr: there is consensus on the fact that we should present results for the
-following data sets:
+The following processes are either already part of PDF determinations (7 and \SI{8}{\tera\electronvolt}) in refs.~\cite{} or will likely be part of next-generation PDF fits (\SI{13}{\tera\electronvolt}).
+We discuss,
 \begin{itemize}
-\item ATLAS high mass DY distributions, 7 TeV~\cite{Aad:2013iua} (CS);
-\item CMS 2D DY distributions, 7 TeV~\cite{Chatrchyan:2013tia} (CS);
-\item ATLAS top pair differential distributions ($m_{t\bar{t}}$ and $p_T^t$), 
-8 TeV~\cite{Aad:2015mbv} (ERN);
-\item CMS $Z$ $pT$ distributions, 13 TeV~\cite{Sirunyan:2019bzr} (ERN).
+\item in section~\ref{sec:atlas-high-mass-dy}, ATLAS high-mass DY lepton-pair production at \SI{7}{\tera\electronvolt} \cite{Aad:2013iua}, measuring $\mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}}$ for the lepton-pair invariant mass $M_{\ell \bar{\ell}} > \SI{116}{\giga\electronvolt}$,
+\item in section~\ref{sec:cms-dy}, CMS DY lepton-pair production at \SI{7}{\tera\electronvolt} \cite{Chatrchyan:2013tia}, measuring $\mathrm{d} \sigma / \mathrm{d} y_{\ell \bar{\ell}}$ for six slices in the range $\SI{20}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{1500}{\giga\electronvolt}$,
+\item in section~\ref{sec:atlas-top-pair-production}, ATLAS top-pair production at \SI{8}{\tera\electronvolt} \cite{Aad:2015mbv}, measuring
+\begin{itemize}
+\item the transverse momentum of the reconstructed top, $\mathrm{d} \sigma / \mathrm{d} p_\mathrm{T}^\mathrm{t}$,
+\item its rapidity, $\mathrm{d} \sigma / \mathrm{d} y_\mathrm{t}$,
+\item the invariant mass of the reconstructed top pair, $\mathrm{d} \sigma / \mathrm{d} M_{\mathrm{t} \bar{\mathrm{t}}}$, and
+\item its rapidity, $\mathrm{d} \sigma / \mathrm{d} M_{\mathrm{t} \bar{\mathrm{t}}}$,
+\end{itemize}
+\item in section~\ref{sec:cms-transverse-momentum}, CMS transverse momentum of the Z boson at \SI{13}{\tera\electronvolt} \cite{Sirunyan:2019bzr}, measuring $\mathrm{d} \sigma / \mathrm{d} p_\mathrm{Z}$ for $p_\mathrm{Z} > \SI{20}{\giga\electronvolt}$.
+\end{itemize}
+We used the MC \texttt{mg5\_aMC@NLO}~\cite{} and the PDF set \texttt{NNPDF31\_as\_0118\_luxqed}~\cite{} to generate the predictions.
+The chosen PDF set contains a photon PDF calculated from the LUXQED method~\cite{}.
+For each process---except top-pair production, which has stable tops in the final state---we use a complex-mass scheme~\cite{} as described in ref.~\cite{}.
+The values of the most important parameters are
+\begin{equation}
+\begin{aligned}
+M_\mathrm{W} &= \SI{80}{\giga\electronvolt} \text{,} \quad &
+M_\mathrm{Z} &= \SI{90}{\giga\electronvolt} \text{,} \quad &
+m_\mathrm{t} &= \SI{170}{\giga\electronvolt} \text{,} \\
+\Gamma_\mathrm{W} &= \SI{2}{\giga\electronvolt} \text{,} &
+\Gamma_\mathrm{Z} &= \SI{2}{\giga\electronvolt} \text{,} &
+G_\mu &= \text{.}
+\end{aligned}
+\end{equation}
+
+\noindent
+TODO for each of the following subsections:
+\begin{itemize}
+\item size of the photon-initiated contributions,
+\item largest partonic channel,
+\item most important $x$ region,
+\item PDF uncertainty,
 \end{itemize}
 
-We agree not to display any LHCb measurement, given that they won't add
-further value to our discussion.
-Note added: we might also want to have a look at the ATLAS 2D and 3D DY 
-distributions, 8 TeV~\cite{Aad:2016zzw,Aaboud:2017ffb}, if time allows 
-us to do so.
+\subsection{ATLAS high-mass DY lepton-pair production at \SI{7}{\tera\electronvolt}}
+\label{sec:atlas-high-mass-dy}
 
-CS 25 Jun: We've agreed to show basically two types of plots: 1) technical plots showing the good agreement between the MC compared to the results from the grids, and 2) phenomenological results showing larger EW corrections, for example.
-In the aMCfast paper both is shown in single plot, but since we have more to show, I suggest the following: for the technical plots we show a 2x2 matrix of plots, each showing the difference of the grid result compared to the MC result, in the following fashion:
-\begin{itemize}
-\item NLO QCD with low statistics,
-\item NLO QCD+EW with low statistics,
-\item NLO QCD with high statistics, and finally
-\item NLO QCD+EW with high statistics,
-\end{itemize}
-each showing a few scale variations.
-These plots then clearly show that no matter what corrections you choose, no matter the statistics, and no matter the scale variation, the agreement is always excellent.
-In any case I would like to avoid showing a plot with absolute numbers and low statistics, which looks a bit ridiculous in my opinion (look at figure 1, left side, top plot of the aMCfast paper).
+\begin{equation}
+\begin{gathered}
+p_\mathrm{T}^\ell > \SI{25}{\giga\electronvolt} \text{,} \quad |\eta_\ell| < 2.5 \text{,} \\
+\SI{116}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{1500}{\giga\electronvolt} \text{,}
+\end{gathered}
+\end{equation}
 
-Finally we can show another series of plots, which in my opinion should be very similar to the usual pheno paper plots: absolute numbers with a scale variation band, maybe a few corrections shown in the same plot and then in the bottom relative corrections.
+\subsection{CMS DY lepton-pair production at \SI{7}{\tera\electronvolt}}
+\label{sec:cms-dy}
+
+\begin{equation}
+\begin{gathered}
+p_\mathrm{T}^{\ell_1} > \SI{14}{\giga\electronvolt} \text{,} \quad p_\mathrm{T}^{\ell_2} > \SI{9}{\giga\electronvolt} \text{,} \quad |\eta_\ell| < 2.4 \text{,} \\
+|\eta_{\ell \bar{\ell}}| < 2.4 \text{,} \quad \SI{20}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{1500}{\giga\electronvolt} \text{,}
+\end{gathered}
+\end{equation}
+
+\subsection{ATLAS top-pair production at \SI{8}{\tera\electronvolt}}
+\label{sec:atlas-top-pair-production}
+
+\subsection{CMS transverse momentum of the Z boson at \SI{13}{\tera\electronvolt}}
+\label{sec:cms-transverse-momentum}
+
+\begin{equation}
+\begin{gathered}
+p_\mathrm{T}^\ell > \SI{25}{\giga\electronvolt} \text{,} \quad |\eta_\ell| < 2.4 \text{,} \quad M_\mathrm{Z} - \SI{15}{\giga\electronvolt} < M_{\ell \bar{\ell}} < M_\mathrm{Z} + \SI{20}{\giga\electronvolt} \text{,} \\
+|\eta_{\ell \bar{\ell}}| < 2.4 \text{,} \quad \SI{20}{\giga\electronvolt} < p_\mathrm{T}^{\ell \bar{\ell}} < \SI{1500}{\giga\electronvolt} \text{,}
+\end{gathered}
+\end{equation}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB}
+    \caption{PineAPPL comparison for ATLAS high-mass Drell--Yan at $\sqrt{s}=7$ TeV.}
+    \label{fig:atlaszhighmass49fb}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin1}%
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin2}
+    \caption{PineAPPL comparison for CMS 2D Drell--Yan.}
+    \label{fig:cmsdy2d11_bins12}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin3}%
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin4}
+    \caption{PineAPPL comparison for CMS 2D Drell--Yan.}
+    \label{fig:cmsdy2d11_bins34}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin5}%
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin6}
+    \caption{PineAPPL comparison for CMS 2D Drell--Yan.}
+    \label{fig:cmsdy2d11_bins56}
+\end{figure}
+
+%ERN 7 Apr: there is consensus on the fact that we should present results for the
+%following data sets:
+%\begin{itemize}
+%\item ATLAS high mass DY distributions, 7 TeV~\cite{Aad:2013iua} (CS);
+%\item CMS 2D DY distributions, 7 TeV~\cite{Chatrchyan:2013tia} (CS);
+%\item ATLAS top pair differential distributions ($m_{t\bar{t}}$ and $p_T^t$),
+%8 TeV~\cite{Aad:2015mbv} (ERN);
+%\item CMS $Z$ $pT$ distributions, 13 TeV~\cite{Sirunyan:2019bzr} (ERN).
+%\end{itemize}
+%
+%We agree not to display any LHCb measurement, given that they won't add
+%further value to our discussion.
+%Note added: we might also want to have a look at the ATLAS 2D and 3D DY
+%distributions, 8 TeV~\cite{Aad:2016zzw,Aaboud:2017ffb}, if time allows
+%us to do so.
+%
+%CS 25 Jun: We've agreed to show basically two types of plots: 1) technical plots showing the good agreement between the MC compared to the results from the grids, and 2) phenomenological results showing larger EW corrections, for example.
+%In the aMCfast paper both is shown in single plot, but since we have more to show, I suggest the following: for the technical plots we show a 2x2 matrix of plots, each showing the difference of the grid result compared to the MC result, in the following fashion:
+%\begin{itemize}
+%\item NLO QCD with low statistics,
+%\item NLO QCD+EW with low statistics,
+%\item NLO QCD with high statistics, and finally
+%\item NLO QCD+EW with high statistics,
+%\end{itemize}
+%each showing a few scale variations.
+%These plots then clearly show that no matter what corrections you choose, no matter the statistics, and no matter the scale variation, the agreement is always excellent.
+%In any case I would like to avoid showing a plot with absolute numbers and low statistics, which looks a bit ridiculous in my opinion (look at figure 1, left side, top plot of the aMCfast paper).
+%
+%Finally we can show another series of plots, which in my opinion should be very similar to the usual pheno paper plots: absolute numbers with a scale variation band, maybe a few corrections shown in the same plot and then in the bottom relative corrections.

### 2020-07-20 run.sh
Calculate scale variations

@@ -143,9 +143,7 @@ EOF
     "${applcheck}" "${pdfstring}" "${dataset}".root > applcheck.log
 
     # extract the numerical results from mg5_aMC
-    sed -e '/^  [+-]/!d' \
-        -e 's/^  [+-][0-9].[0-9]\+e[+-][0-9]\+   [+-][0-9].[0-9]\+e[+-][0-9]\+   [+]*\([0-9].[0-9]\+e[+-][0-9]\+\)   [+]*\([0-9].[0-9]\+e[+-][0-9]\+\)$/\1 \2/' \
-        "${dataset}"/Events/run_01*/MADatNLO.HwU > results.mg5_aMC
+    sed '/^  [+-]/!d' "${dataset}"/Events/run_01*/MADatNLO.HwU > results.mg5_aMC
 
     # extract the numerical results from the APPLgrid
     sed -e '1,/all bins:/d' \
@@ -167,8 +165,8 @@ EOF
          BEGIN { print "---------------------------------------------------------------"
                  print "   " program "       mg5_aMC   mg5_aMC unc.   sigmas   per mille"
                  print "---------------------------------------------------------------" }
-         { printf "% e % e %e %8.3f %10.4f\n", $1, $2, $3, $3 != 0.0 ? abs($1-$2)/$3 : 0.0,
-                                               $2 != 0.0 ? abs($1-$2)/$2*1000 : 0.0 }' | \
+         { printf "% e % e %e %8.3f %10.4f\n", $1, $4, $5, $5 != 0.0 ? abs($1-$4)/$5 : 0.0,
+                                               $4 != 0.0 ? abs($1-$4)/$4*1000 : 0.0 }' | \
         tee results.log
 
     rm results.mg5_aMC results.grid

### 2020-07-20 paper/sec-pineappl.tex
Fix wrongly defined xiR and xiF

@@
 
-Fixed-order partonic cross sections $a + b \to X$ supported by \textsc{PineAPPL} are expansions in powers of the strong coupling $\alphas$, the electromagnetic coupling $\alpha$, and the logarithms of $\xi_\mathrm{R} = \mu_\mathrm{R}^2 / Q^2$ and $\xi_\mathrm{F} = \mu_\mathrm{F}^2 / Q^2$,
+Fixed-order partonic cross sections $a + b \to X$ supported by \textsc{PineAPPL} are expansions in powers of the strong coupling $\alphas$, the electromagnetic coupling $\alpha$, and the logarithms of $\xi_\mathrm{R} = \mu_\mathrm{R} / Q$ and $\xi_\mathrm{F} = \mu_\mathrm{F} / Q$,
 \begin{multline}
 \frac{\mathrm{d} \sigma_{ab}}{\mathrm{d} \mathcal{O}} (x_1, x_2, \mathcal{O}, \xi_\mathrm{R}, \xi_\mathrm{F}) \\
-= \sum_{k,l,m,n} \alphas^k \left( \xi_\mathrm{R} Q^2 \right) \alpha^l \log^m ( \xi_\mathrm{R} ) \log^n ( \xi_\mathrm{F} ) W_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2, \mathcal{O} \right) \text{.}
+= \sum_{k,l,m,n} \alphas^k \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^l \log^m ( \xi_\mathrm{R}^2 ) \log^n ( \xi_\mathrm{F}^2 ) W_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2, \mathcal{O} \right) \text{.}
 \label{eq:expansion}
@@
 \frac{\mathrm{d} \sigma}{\mathrm{d} \mathcal{O}} (\mathcal{O}, \xi_\mathrm{R}, \xi_\mathrm{R}) \\
-= \sum_{a,b} \int_0^1 \mathrm{d} x_1 \int_0^1 \mathrm{d} x_2 \int_{Q^2_\mathrm{min}}^{Q^2_\mathrm{max}} \mathrm{d} Q^2 \, f_a (x_1, \xi_\mathrm{F} Q^2) f_b (x_2, \xi_\mathrm{F} Q^2) \sigma_{ab} (x_1, x_2, Q^2, \xi_\mathrm{R}, \xi_\mathrm{R}) \text{,}
+= \sum_{a,b} \int_0^1 \mathrm{d} x_1 \int_0^1 \mathrm{d} x_2 \int_{Q^2_\mathrm{min}}^{Q^2_\mathrm{max}} \mathrm{d} Q^2 \, f_a (x_1, \xi_\mathrm{F}^2 Q^2) f_b (x_2, \xi_\mathrm{F}^2 Q^2) \sigma_{ab} (x_1, x_2, Q^2, \xi_\mathrm{R}, \xi_\mathrm{R}) \text{,}
 \label{eq:pineappl-convolution}
@@
     &= \alpha^2 W_{ab}^{(0,2,0,0)} \\
-    &+ \alphas \left( \xi_\mathrm{R} Q^2 \right) \alpha^2 W_{ab}^{(1,2,0,0)} (Q^2) + \alphas \left( \xi_\mathrm{R} Q^2 \right) \log (\xi_\mathrm{F}) \alpha^2 W_{ab}^{(1,2,0,1)} \\
-    &+ \alpha^3 W_{ab}^{(0,3,0,0)} (Q^2) + \log (\xi_\mathrm{F}) \alpha^3 W_{ab}^{(0,3,0,1)} \text{.}
+    &+ \alphas \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^2 W_{ab}^{(1,2,0,0)} (Q^2) + \alphas \left( \xi_\mathrm{R}^2 Q^2 \right) \log (\xi_\mathrm{F}^2) \alpha^2 W_{ab}^{(1,2,0,1)} \\
+    &+ \alpha^3 W_{ab}^{(0,3,0,0)} (Q^2) + \log (\xi_\mathrm{F}^2) \alpha^3 W_{ab}^{(0,3,0,1)} \text{.}
 \end{split}
@@
 Note that all terms depend on the renormalisation scale only indirectly through $\alphas$, because 1) higher-order terms in $\alpha$ never generate a renormalisation scale dependence (in the $\alpha$ schemes that are valid according to section~\ref{sec:multi-coupling-expansion}) and 2) higher-order QCD corrections only introduce an explicit renormalisation scale dependence in counterterms with vertices with more than two gluons.
-At NLO these terms are not present for this process so that terms proportional to $\log (\xi_\mathrm{R})$ vanish.
+At NLO these terms are not present for this process so that terms proportional to $\log (\xi_\mathrm{R}^2)$ vanish.
 Both NLOs, however, have contributions from a collinear counterterm that depends on the factorisation scale.
@@
 %&= \alpha^2                                                                       W_{ab}^{(0,2,0,0)}
-% + \alphas   \left( \xi_\mathrm{R} Q^2 \right) \alpha                         W_{ab}^{(1,1,0,0)}
-% + \alphas^2 \left( \xi_\mathrm{R} Q^2 \right)                                W_{ab}^{(2,0,0,0)} \\
-%&+ \alphas^3 \left( \xi_\mathrm{R} Q^2 \right)                                W_{ab}^{(3,0,0,0)} \\
-%&+ \alphas^3 \left( \xi_\mathrm{R} Q^2 \right)          \log (\xi_\mathrm{F}) W_{ab}^{(3,0,0,1)} (Q^2)
-% + \alphas^3 \left( \xi_\mathrm{R} Q^2 \right)          \log (\xi_\mathrm{R}) W_{ab}^{(3,0,1,0)} (Q^2) \\
-%&+ \alphas^2 \left( \xi_\mathrm{R} Q^2 \right) \alpha                         W_{ab}^{(2,1,0,0)} \\
-%&+ \alphas^2 \left( \xi_\mathrm{R} Q^2 \right) \alpha   \log (\xi_\mathrm{F}) W_{ab}^{(2,1,0,1)} (Q^2)
-% + \alphas^2 \left( \xi_\mathrm{R} Q^2 \right) \alpha   \log (\xi_\mathrm{R}) W_{ab}^{(2,1,1,0)} (Q^2) \\
-%&+ \alphas   \left( \xi_\mathrm{R} Q^2 \right) \alpha^2                       W_{ab}^{(1,2,0,0)} \\
-%&+ \alphas   \left( \xi_\mathrm{R} Q^2 \right) \alpha^2 \log (\xi_\mathrm{F}) W_{ab}^{(1,2,0,1)} (Q^2)
-% + \alphas   \left( \xi_\mathrm{R} Q^2 \right) \alpha^2 \log (\xi_\mathrm{R}) W_{ab}^{(1,2,1,0)} (Q^2) \\
-%&+           \left( \xi_\mathrm{R} Q^2 \right) \alpha^3                       W_{ab}^{(0,3,0,0)} \\
-%&+           \left( \xi_\mathrm{R} Q^2 \right) \alpha^3 \log (\xi_\mathrm{F}) W_{ab}^{(0,3,0,1)} (Q^2)
-% +           \left( \xi_\mathrm{R} Q^2 \right) \alpha^3 \log (\xi_\mathrm{R}) W_{ab}^{(0,3,1,0)} (Q^2)
+% + \alphas   \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha                           W_{ab}^{(1,1,0,0)}
+% + \alphas^2 \left( \xi_\mathrm{R}^2 Q^2 \right)                                  W_{ab}^{(2,0,0,0)} \\
+%&+ \alphas^3 \left( \xi_\mathrm{R}^2 Q^2 \right)                                  W_{ab}^{(3,0,0,0)} \\
+%&+ \alphas^3 \left( \xi_\mathrm{R}^2 Q^2 \right)          \log (\xi_\mathrm{F}^2) W_{ab}^{(3,0,0,1)} (Q^2)
+% + \alphas^3 \left( \xi_\mathrm{R}^2 Q^2 \right)          \log (\xi_\mathrm{R}^2) W_{ab}^{(3,0,1,0)} (Q^2) \\
+%&+ \alphas^2 \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha                           W_{ab}^{(2,1,0,0)} \\
+%&+ \alphas^2 \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha   \log (\xi_\mathrm{F}^2) W_{ab}^{(2,1,0,1)} (Q^2)
+% + \alphas^2 \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha   \log (\xi_\mathrm{R}^2) W_{ab}^{(2,1,1,0)} (Q^2) \\
+%&+ \alphas   \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^2                         W_{ab}^{(1,2,0,0)} \\
+%&+ \alphas   \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^2 \log (\xi_\mathrm{F}^2) W_{ab}^{(1,2,0,1)} (Q^2)
+% + \alphas   \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^2 \log (\xi_\mathrm{R}^2) W_{ab}^{(1,2,1,0)} (Q^2) \\
+%&+           \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^3                         W_{ab}^{(0,3,0,0)} \\
+%&+           \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^3 \log (\xi_\mathrm{F}^2) W_{ab}^{(0,3,0,1)} (Q^2)
+% +           \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^3 \log (\xi_\mathrm{R}^2) W_{ab}^{(0,3,1,0)} (Q^2)
 %\end{split}

### 2020-07-20 paper/sec-pineappl.tex
added small discussion about kinematics of contributions

@@
 The (asymmetric) uncertainties are then given as the minimum and maximum value (the envelope), measured from the central value $(1, 1)$.
-
 As is clear from eq.~\eqref{eq:expansion}, the EW coupling $\alpha$ is assumed not to be a dynamically varying coupling, but instead a constant over phase space.
 This, however, includes the most common choices of the coupling, which are (not necessarily in this order), $\alpha (0)$, $\alpha (M_\mathrm{Z})$, and $\alpha_{G_\mu}$.
-
 The task that \textsc{PineAPPL} solves can now be described: Approximately reconstruct the functions
@@
 given by the MC integrator.
-Note that in the above equation we do not differentiate w.r.t.\ which phase-space integration (Born, real, subtraction term, etc.) the weight came from, because e.g.\ for a certain NLO all weights are filled into a single grid with fixed $k$ and $l$ and $m=n=0$.
-
 Using eq.~\eqref{eq:expansion} and
@@
 \end{multline}
-\textsc{PineAPPL} can then quickly calculate hadronic cross sections for arbitrarily many PDF sets and perform scale variations.
+\textsc{PineAPPL} can then quickly calculate hadronic cross sections for arbitrarily many PDF sets and perform scale variations.\\
+
+Note that in this section we have omitted the dependence of the weights, observable and scales on the specific kinematics for 
+which they are compured. Indeed, beyond LO,
+different kinematic contributions have to be considered (in Ref.~\cite{Bertone:2014zva}, they are labeled by the index $\alpha$, see
+Eq. 12 therein). Their consistent treatment must be ensured by the interface between
+\textsc{PineAPPL} and the specific cross-section compuation at hand\footnote{
+    For example, while in the FKS subtraction scheme~\cite{Frixione:1995ms,Frixione:1997np} employed in \textsc{mg5\_aMC@NLO}
+    maximally one kind of kinematics for each counterterm (soft, collinear and soft-collinear) is needed, this 
+    is not the general case, for example in the Catani-Seymour one~\cite{Catani:1996jh}}.
+However, \textsc{PineAPPL} remains completely blind to this fact, as all weights are filled into a given grid
+identified only by the indices $k, l, m, n$.
 

### 2020-07-20 paper/sec-pineappl.tex
Add a few corrections to the last commit

--- 2020-07-20 paper/sec-pineappl.tex
@@
 \textsc{PineAPPL} can then quickly calculate hadronic cross sections for arbitrarily many PDF sets and perform scale variations.
+
+Note that in this section we have omitted the dependence of the weights, observable and scales on the specific kinematics for
+which they are computed. Indeed, beyond LO,
+different kinematic contributions have to be considered (in ref.~\cite{Bertone:2014zva} they are labelled with an index $\alpha$, see
+eq.\ 12 therein). Their consistent treatment must be ensured by the interface between
+\textsc{PineAPPL} and the specific cross-section computation at hand\footnote{
+    In the FKS subtraction scheme~\cite{Frixione:1995ms,Frixione:1997np} employed in \textsc{mg5\_aMC@NLO}
+    maximally one kind of kinematics for each counterterm (soft, collinear, and soft-collinear) is needed, but this
+    is not the general case, for example in the Catani--Seymour subtraction~\cite{Catani:1996jh} different dipoles may have different phase spaces and therefore different scales.}.
+However, \textsc{PineAPPL} remains completely blind to this fact, as all weights are filled into a given grid
+identified only by the indices $k, l, m, n$.
 

### 2020-07-20 paper/app-pineappl.tex
Revise appendix

@@
 
+\subsubsection*{Installation of Rust}
+
 \lstset{
-  basicstyle=\ttfamily,
+  basicstyle=\ttfamily\small,
   showstringspaces=false,
@@
 
+\subsubsection*{Installation of the command-line program \texorpdfstring{\texttt{pineappl}}{pineappl}}
+
 The command-line program \texttt{pineappl} is compiled and installed using
@@
 \end{lstlisting}
-This program also needs \texttt{LHAPDF} installed.
+This program also needs \texttt{LHAPDF} \cite{Buckley:2014ana} installed.
 For usage instructions simply type \texttt{pineappl} in your shell and read the help message.
 
-For the C interface you need to first install \texttt{cargo-c}, download the \textsc{PineAPPL} repository, and compile and finally install into it into a directory \texttt{\$prefix} as follows:
+\subsubsection*{Installation of the C-language interface (optional)}
+
+For the C interface you need to first install \texttt{cargo-c},
 \begin{lstlisting}[language=bash]
 cargo install cargo-c
+\end{lstlisting}
+and then download the \textsc{PineAPPL} repository, compile and finally install into it into a directory \texttt{\$prefix} as follows:
+\begin{lstlisting}[language=bash]
 git clone https://github.com/N3PDF/pineappl/
@@
 All \textsc{PineAPPL} functions have the prefix \texttt{pineappl\_}.
-The full example can be found at TODO.
+The full example can be found at \url{https://github.com/N3PDF/pineappl/tree/master/examples/capi-dy-aa}.
+
+\clearpage
 \begin{lstlisting}[language=C++,mathescape=true]
@@
 double ckm_factors[] = { 1.0 };
-pineappl_lumi_add(lumi, 2, pdg_ids, ckm_factors);
+pineappl_lumi_add(lumi, 1, pdg_ids, ckm_factors);
 
@@
 \end{lstlisting}
+\clearpage
 

### 2020-07-20 paper/sec-pineappl.tex
Revise PineAPPL section

@@
 This separates the task of producing predictions for observables into two steps: 1) the generation of the \emph{grids}, which is how the generated files are called, and 2) the convolution of those grids with a set of PDFs.
-The advantage of this method is that the time-consuming step 1) has to be done only once and, therefore, allows for very quick convolutions of a given grid with multiple PDF sets.
+The advantage of this method is that the time-consuming step 1) has to be done only once and, therefore, allows in step 2) for very quick convolutions of a given grid with multiple PDF sets.
 
@@
 w_{ab}^{(k,l,m,n,o)} \left( x_1, x_2, Q^2 \right)
+\label{eq:weight-map}
 \end{equation}
@@
 \begin{equation}
-\left\{ x_1^{(i)}, x_2^{(i)}, Q^2_i, \mathcal{O}_i \right\}_{i=1}^N \text{,}
+\left\{ x_1^{(i)}, x_2^{(i)}, Q^2_i, \mathcal{O}_i \right\}_{i=1}^N \text{,} \label{eq:phase-space-weights}
 \end{equation}
 given by the MC integrator.
+
 Using eq.~\eqref{eq:expansion} and
@@
 
-\subsection{Grid representation and accuracy}
+\subsection{Grid representations}
 \label{sec:grid-representation}
@@
 
-\subsubsection{Interpolation grids}
+\subsubsection{Lagrange-interpolation grid}
 
-A different choice partitions the $(x_1, x_2, Q^2)$ space,
+A different strategy is to partition the $(x_1, x_2, Q^2)$ space,
 \begin{equation}
@@
 along each axis into a small numbers of bins and to insert the phase-space weights $w$ into the corresponding discrete bin.
-This method is straightforward, but given a finite number of bins this usually yields a bad approximation for the cross section.
-Increasing the number of bins improves the accuracy, but it also increases the space requirements of the grid.
-Interpolation methods offer more precision, while keeping the number of bins constants.
+Using the bin centres and their values one already has a straightforward implementation of eq.~\eqref{eq:weight-map}, but given a finite number of bins it usually yields an insufficient approximation for the cross section.
+Increasing the number of bins improves the accuracy, but it also increases the space requirements.
+Interpolation methods offer more accuracy with the same number of bins.
 
-We use the same Lagrange-interpolation grid presented in Ref.~\cite{Carli:2010rw} with the parameters published in Ref.~\cite{Bertone:2014zva}, which give decent precision (see section~\ref{sec:results}).
-The method presented in the previous references first maps $(x_1, x_2, Q^2) \mapsto (y_1, y_2, \tau)$, with the maps defined as
+We use the same \enquote{Lagrange-interpolation grid} presented in ref.~\cite{Carli:2010rw} with the parameters published in ref.~\cite{Bertone:2014zva}, which give sufficient precision (see section~\ref{sec:results}).
+
+This method first maps $(x_1, x_2, Q^2) \mapsto (y_1, y_2, \tau)$, with
 \begin{equation}
-y(x) = 5 (1-x) - \log x \text{,} \qquad \tau (Q^2) = \log \log \frac{Q^2}{(\SI{0.25}{\giga\electronvolt})^2} \text{,}
+y(x) = 5 (1-x) - \log x \text{,} \qquad \tau (Q^2) = \log \log \frac{Q^2}{(\SI{0.25}{\giga\electronvolt})^2} \text{.}
+\label{eq:maps}
 \end{equation}
-and then feeds the variables $(y_1, y_2, \tau)$ into the 3-dimensional Lagrange-interpolation grid with 50 bins in each $y$ direction and 30 bins in $\tau$ direction.
-The interpolation order is 3 for each variable, and only the subspace $[\num{2e7},1] \times [\num{2e-7},1] \times [100,\num{e6}] \subset H$\footnote{In Ref.~\cite{Bertone:2014zva} the upper limit for $Q$ is given as \SI{3162}{\giga\electronvolt} (which corresponds to $Q_\mathrm{max}^2 \approx \SI{e7}{\giga\electronvolt}$), but in the code we found the value $Q_\mathrm{max}^2 = \SI{e6}{\giga\electronvolt\squared}$.} is mapped.
+The function $y(x)$ maps events with large $x$ effectively linearly and small $x$ effectively logarithmically onto $y$.
+This reflects our knowledge of PDFs, which behave differently in those regions, and thereby increases the accuracy of the interpolation.
 For the convolution of a grid with a PDF set also the inverse functions are needed, which are
 \begin{equation}
-x(y) = \frac{1}{5} \operatorname{W}_0 (5 \exp (5-x)) \text{,} \qquad Q^2 (\tau) = (\SI{0.25}{\giga\electronvolt})^2 \exp (\exp (\tau)) \text{,}
+x(y) = \frac{1}{5} \operatorname{W}_0 (5 \exp (5-y)) \text{,} \qquad Q^2 (\tau) = (\SI{0.25}{\giga\electronvolt})^2 \exp (\exp (\tau)) \text{,}
 \end{equation}
@@
 \end{tabular}
-\caption{Example for a 2-dimensional $10 \times 10$ grid, which is being filled at the location marked with the small black square, at $(5.8,4.8)$.
+\caption{Example for a 2-dimensional $10 \times 10$ grid, which is being filled at the location marked with the small black square at $(5.8,4.8)$.
 Each side of the grey square starting at $k_i = 4$ and $k_j = 3$ has a length of $N_y + 1 = 4$.
-This square marks the grid values that are being updated using eq.~\eqref{eq:interpolation}.
-The table on the right-hand side marks gives the parton-momentum fractions for each grid point.
-Note that around $u=3$ the values are linearly distributed, then logarithmically.}
+This square marks the grid values (grey dots) that are being updated using eq.~\eqref{eq:interpolation}.
+The table on the right-hand side gives the parton-momentum fractions for each grid point according to eq.~\eqref{eq:maps}.
+Note that for $u \in [0, 3]$ the values are roughly linearly distributed, then logarithmically.}
 \label{fig:grid}

### 2020-07-20 paper/sec-introduction.tex
Add small fixes

@@
 theoretical predictions, accurate to NLO in both (including mixed-coupling 
-QCD+EW terms), is automated~\cite{Biedermann:2017yoi,Frederix:2018nkq}.
+QCD--EW terms), is automated~\cite{Biedermann:2017yoi,Frederix:2018nkq}.
 
@@
 become similar, $\alphas^2\sim \alpha$. If NNLO QCD corrections are included
-by default in PDF determinations, NLO EW and NLO EW+QCD corrections should be 
+by default in PDF determinations, NLO EW and NLO QCD+EW corrections should be
 taken into account on the same footing. Second, the virtual exchange of soft or 

### 2020-07-21 paper/sec-doublecounting.tex
Add small fixes
small changes in double counting figure

@@
-\section{Double counting}
+\section{Double counting EW corrections}
 \label{sec:doublecounting}
@@
 subtracted, possibly evaluated with different parton densities and/or including (unphysical) higher-order 
-corrections. For example, in Refs.~\cite{Aaboud:2017ffb,Aad:2016zzw}, one reads:
+corrections. For example, in refs.~\cite{Aaboud:2017ffb,Aad:2016zzw}, one reads:
 \begin{quote}
@@
     \centering
-    \includegraphics[width=0.6\textwidth, trim=0.cm 11cm 0.cm 2cm, clip=True]{figures/dy-pi.pdf}\\
+    \begin{overpic}[width=0.6\textwidth, trim=0.cm 11cm 0.cm 10cm, clip=True]{figures/dy-pi.pdf}
+        \put (5, 33) {\large $q$}
+        \put (20, 37) {\large $q$}
+        \put (38, 5) {\large $\ell^+$}
+        \put (38, 31) {\large $\ell^-$}
+        \put (11, 6) {\large $\gamma$}
+        %
+        \put (65, 9) {\large $q$}
+        \put (73, 30) {\large $q$}
+        \put (96, 25) {\large $\ell^-$}
+        \put (96, 8) {\large $\ell^+$}
+        \put (55, 26) {\large $\gamma$}
+    \end{overpic}
     \caption{\label{fig:dy-pi}

### 2020-07-21 paper/sec-results.tex
Added plots
Some work on Sect. 3

@@
 
-In this section we present a comparison of NLO QCD and NLO QCD+EW predictions for three different processes: DY lepton-pair production, top-pair production, and finally Z-boson (lepton-pair) production with non-zero transverse momentum at the LHC.
+In this section we demonstrate the capabilities of \textsc{PineAPPL} by
+computing fast interpolation grids, accurate to NLO QCD and NLO QCD+EW,
+for a representative set of processes in which EW corrections are expected 
+to be sizeable. In order to consider some realistic kinematics for these
+processes, we resort to measurements commonly devised for inclusion in PDF
+fits. Our aim is twofold. On the one hand, we want to validate the results
+obtained with \textsc{PineAPPL}; on the other hand, we want to assess the
+impact of the EW corrections for usual experimental setups. We describe first
+the processes and measurements that we consider, then the computational
+settings that we adopt, and finally the results that we obtain.
 
-Our first aim is a technical one, namely to show the validity of the results reconstructed with the \textsc{PineAPPL} grids introduced in section~\ref{sec:pineappl} and to give a measure of accuracy that can be achieved with them.
-The second aim is to quantify the size of the EW corrections for the setups defined by the experimental collaborations for the processes given below.
+\subsection{Processes and measurements}
+\label{subsec:processes_and_measurements}
 
-The following processes are either already part of PDF determinations (7 and \SI{8}{\tera\electronvolt}) in refs.~\cite{} or will likely be part of next-generation PDF fits (\SI{13}{\tera\electronvolt}).
+We focus on the following three processes: DY lepton-pair production, top-quark
+pair production, and Z-boson (lepton-pair) production with non-zero transverse
+momentum at the LHC. For each of these processes, we consider the measurments
+described below.
+
+\paragraph{DY lepton pair production.}
+We select the distribution, single-differential in the invariant mass of the
+lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of
+mass energy of 7~TeV in the high-mass region
+($M_{\ell\bar\ell}>116$~GeV)~\cite{Aad:2013iua}.
+We also select the distribution, double-differential in the rapidity and in
+the invariant mass of the lepton pair, $y_{\ell\bar\ell}$ and $M_{\ell\bar\ell}$,
+measured by the CMS experiment at 7~TeV~\cite{Chatrchyan:2013tia}.
+These measurements are currently included as standard in the
+NNPDF3.1~\cite{Ball:2017nwa} and MMHT2014~\cite{Harland-Lang:2014zoa} PDF sets,
+although with appropriate kinematic cuts that remove the bins at the largest
+values of invariant mass, where EW corrections become sizeable.
+
+\paragraph{Top-quark pair production.}
+We select the distributions, single-differential in either the transverse
+momentum of the top quark, $p_T^t$, or the invariant mass of the top-quark
+pair, $m_{t\bar t}$, measured by the ATLAS and CMS experiments at a centre-of-mass
+energy of 8~TeV~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
+been extensively studied in the context of PDF fits in
+Refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml}.
+Because EW corrections are significantly smaller for distributions differential
+in the rapidity of either the top quark or the top-quark
+pair~\cite{Czakon:2017wor}, these were preferred for inclusion in the NNPDF3.1
+set~\cite{Ball:2017nwa}.
+
+\paragraph{$Z$-boson production with non-zero transverse momentum.}
+We select the distribution, single-differential in the transverse momentum of
+the $Z$ boson, $p_T^Z$, measured by the CMS experiment at a centre-of-mass
+energy of 13~TeV~\cite{Sirunyan:2019bzr}. This measurement has not been
+included in a PDF determination yet. Given that it has sub-percent
+uncertainties, it is expected that EW corrections will be essential to
+achieve a good description of it, and to constrain accurately the PDFs.
+A similar challenge was observed in similar measurements, from the
+ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa} experiment at a
+centre-of-mass energy of 8~TeV, in Ref.~\cite{Boughezal:2017nla}, which lead to
+their partial inclusion (upon the selection of an appropriate kinematic cut)
+in the NNDPF3.1 PDF set~\cite{Ball:2017nwa} and in variants of the CT18 PDF
+set~\cite{Hou:2019efy}.
+
+\subsection{Computational settings}
+\label{subsec:computational_settings}
+
 We discuss,
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TPT}%
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TTM}
+    \caption{PineAPPL comparison for ATLAS top pair.}
+    \label{fig:cmsdy2d11_bins56}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMS_Z_13_TEV}
+    \caption{PineAPPL comparison for CMS $Z$ $p_T$ distribution.}
+    \label{fig:cmsdy2d11_bins56}
+\end{figure}
+
 %ERN 7 Apr: there is consensus on the fact that we should present results for the

### 2020-07-23 paper/sec-doublecounting.tex
changes in section doublecounting

@@
-\section{Double counting EW corrections}
+\section{On the presentation of experimental data}
 \label{sec:doublecounting}
@@
 PDF fits is not enough to make a fully-fledged fit possible in a consistent manner. Indeed, experimental data should
-be provided in  a format that allows PDF collaborations to employ them in such fits in a theoretically sound manner. In this
-section, we will try to provide some guidelines, by highlighting some sources of inconsistency commonly occurring in experimental 
-analyses. These will either lead to accounting multiple times for EW effects (so-called double counting), or to not accounting at
-all for such effects.\footnote{By no means we intend to blame on our beloved experimental colleagues for what they write or do. However,
-    we think that by highlighting errors and making everybody more cautious about them is the only way to avoid repeating such
-    errors in the future.}
+be provided in  a format that allows PDF collaborations to employ them in such fits in a theoretically sound manner. Before concluding the paper,
+we will try to provide some guidelines, to facilitate a consistent presentation of experimental data. Common sources of inconsistency in the extraction of data
+typically lead to accounting multiple times for EW effects (so-called double counting), or to not accounting at
+all for such effects.
 
-A common source of inconsistency is the subtraction of (irreducible) background processes which must not be considered as such. The typical example
-is neutral-current Drell--Yan, where the signal process is an opposite-sign lepton pair, which starts
-at $\mathcal O(\alpha^2)$. Because this process is usually thought
-as a quark-initiated, $s$-channel mechanism ($q\bar q \to \gamma^*/Z \to \ell^+ \ell^-$), in many analyses the photon-induced component,
-$\gamma \gamma \to \ell^+ \ell^-$ in the $t$ channel, is considered as a different process, and it 
-subtracted, possibly evaluated with different parton densities and/or including (unphysical) higher-order 
-corrections. For example, in refs.~\cite{Aaboud:2017ffb,Aad:2016zzw}, one reads:
-\begin{quote}
-The photon-induced process, $\gamma\gamma \to \ell \ell$, is simulated at LO using Pythia 8 
-and the MRST2004qed PDF set~\cite{Martin:2004dh}. The expected yield for this process also accounts for 
-NLO QED/EW corrections from references~\cite{Bardin:2012jk,Bondarenko:2013nu}, which decrease the yield by approximately 30\%.
-\end{quote}
-A similar statement appears also in an older analysis~\cite{Aad:2013iua}. Such a distinction cannot be physically
-justified beyond LO\@. Indeed, at $\mathcal O(\alpha^3)$, the reaction $q \gamma \to \ell^+ \ell^- q$ becomes possible, which
-includes both kind of topologies, see Fig.~\ref{fig:dy-pi}. 
 \begin{figure}[ht!]
@@
 \end{figure}
-
-{\bf It looks like CMS does things in a pretty consistent manner~\cite{Sirunyan:2018owv, CMS:2014jea}. Shall we mention? We should
-not make ATLAS appear as the bad guys, and CMS as the good ones.} The problem here derives from the fact 
-that identifying a process based only on its
-initial-state partons is plain wrong in quantum mechanics. While this fact is well established in QCD---nobody would ever
+An example is the subtraction of (irreducible) background processes which must not be considered as such. A very blatant case
+is neutral-current Drell--Yan, where the signal process is an opposite-sign lepton pair, which starts
+at $\mathcal O(\alpha^2)$. Because this process is usually thought
+as a quark-initiated, $s$-channel mechanism ($q\bar q \to \gamma^*/Z \to \ell^+ \ell^-$), in many analyses the photon-induced component,
+$\gamma \gamma \to \ell^+ \ell^-$ in the $t$ channel, is considered as a different process, and it 
+subtracted, possibly evaluated with different parton densities and/or including (unphysical) higher-order 
+corrections. For example, in refs.~\cite{Aaboud:2017ffb,Aad:2016zzw} (a similar statement appears also in an older analysis~\cite{Aad:2013iua}), one reads:
+\begin{quote}
+The photon-induced process, $\gamma\gamma \to \ell \ell$, is simulated at LO using Pythia 8 
+and the MRST2004qed PDF set~\cite{Martin:2004dh}. The expected yield for this process also accounts for 
+NLO QED/EW corrections from references~\cite{Bardin:2012jk,Bondarenko:2013nu}, which decrease the yield by approximately 30\%.
+\end{quote}
+Such a distinction, which is unphysical and incorrect in quantum mechanics, may be somehow justified at LO. Beyond this order, it is simply wrong.
+Indeed, at $\mathcal O(\alpha^3)$, the reaction $q \gamma \to \ell^+ \ell^- q$ becomes possible, which
+includes both kind of topologies discussed above, see Fig.~\ref{fig:dy-pi}. While it is common sense that the QCD counterpart of this subtraction should never 
+be performed---nobody would ever
 consider to \enquote{subtract} the gluon-initiated contribution to top-pair production in top analyses---seemingly it is not so
@@
 
-A second example is related to removing EW effects from data. These can be either the full EW corrections (Refs??) 
+{\bf It looks like CMS does things in a pretty consistent manner~\cite{Sirunyan:2018owv, CMS:2014jea}. Shall we mention? We should
+not make ATLAS appear as the bad guys, and CMS as the good ones.}
+
+A second example is related to removing EW effects from data. These can be either the full EW corrections
 or just a part, for example deconvolving multiple-photon radiation from light particles in the final state. This applies mostly
@@
 for in hard matrix-elements. Thus, leptons that are measured in the detector are less energetic, and this fact is compensated for
-by undoing the photon shower before publishing data, which are referred to e.g.\ as \emph{Born-level electrons}~\cite{}. There are
-at least two 
+by undoing the photon shower before publishing data, which are referred to e.g.\ as \emph{Born-level electrons} (see e.g. Ref.~\cite{Aad:2015auj} for
+its definition). There are at least two 
 problems related with this. The first, a quite obvious one, is that when EW corrections
-are included at fixed order, the first photon emission is included exactly at the matrix-element level. The second, which
+are included at fixed order, the first photon emission is included exactly at the matrix-element level. The inclusion of 
+subsequent emission would require the matching with the QED shower, which is not yet available for general processes. It is interesting
+to note that one can tune the QED parton shower in order to mimick NLO EW effects, so that a prediction only accurate at NLO
+QCD displays a remarkable agreement with another at NLO QCD+EW when the photonic shower is included (see example the behaviour of predictions showered with
+\textsc{Photos}~\cite{Barberio:1990ms,Barberio:1993qi,Golonka:2005pn}in Ref.~\cite{CarloniCalame:2016ouw}). However, this kind of agreement
+always comes \emph{a posteriori}, and cannot be ensured in general. The second, which
 applies for electrons, is that they are never measured as bare particles, because of the finite resolution 
-of the electromagnetic calorimeter. Since collinear photonic emission cannot be resolved, at least data 
+of the electromagnetic calorimeter. Since collinear photonic emission cannot be resolved, data 
 involving electrons should also be published
@@
 compute EW corrections treat leptons as massless. This fact encourages to explore the possibility of employing dressed
-muons, on the same footing as their electron counterpart.
+muons, on the same footing as their electron counterpart. It is reassuring to acknowledge that this practice is already quite common in experimental analyses:
+indeed, to mention two examples of analyses discussed in this paper, in Ref.~\cite{Aad:2015auj} data for dressed leptons are published, together with the pre- and post-ISR ones, while Refs.~\cite{Sirunyan:2019bzr} employs a dressed-lepton definition.
 

### 2020-07-24 paper/paper.tex
small changes in double counting figure
changes in section doublecounting
other changes in doublecounting section

@@
 \usepackage{xcolor}
+\usepackage[percent]{overpic}
+\usepackage[section]{placeins}
 
@@
 \author[a]{C. Schwan}
-\author[a,b]{and M. Zaro}
+\author[a]{and M. Zaro}
 
@@
 \acknowledgments
-
+We are grateful to Rikkert Frederix for discussions and explanation about
+\textsc{aMCfast}. We acknowledge discussions with 
+Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
+treatment of EW effects in experimental data. \\
+Alessandro Vicini\\
 C.S.\ is supported by the European Research Council under the European Unions
 Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
+MZ thanks the Nikhef institute in Amsterdam,
+where he was employed during the early stages of this paper.
 

### 2020-07-24 paper/sec-doublecounting.tex
other changes in doublecounting section

@@
-\section{On the presentation of experimental data}
+\section{On the conistency of experimental data}
 \label{sec:doublecounting}
@@
 as a quark-initiated, $s$-channel mechanism ($q\bar q \to \gamma^*/Z \to \ell^+ \ell^-$), in many analyses the photon-induced component,
-$\gamma \gamma \to \ell^+ \ell^-$ in the $t$ channel, is considered as a different process, and it 
-subtracted, possibly evaluated with different parton densities and/or including (unphysical) higher-order 
+$\gamma \gamma \to \ell^+ \ell^-$ in the $t$ channel, is considered as a different process, often as a background, and it is possibly 
+evaluated with different parton densities and/or including (unphysical) higher-order 
 corrections. For example, in refs.~\cite{Aaboud:2017ffb,Aad:2016zzw} (a similar statement appears also in an older analysis~\cite{Aad:2013iua}), one reads:
@@
 
-{\bf It looks like CMS does things in a pretty consistent manner~\cite{Sirunyan:2018owv, CMS:2014jea}. Shall we mention? We should
-not make ATLAS appear as the bad guys, and CMS as the good ones.}
+%%{\bf It looks like CMS does things in a pretty consistent manner~\cite{Sirunyan:2018owv, CMS:2014jea}. Shall we mention? We should
+%%not make ATLAS appear as the bad guys, and CMS as the good ones.}
 
@@
 by undoing the photon shower before publishing data, which are referred to e.g.\ as \emph{Born-level electrons} (see e.g. Ref.~\cite{Aad:2015auj} for
-its definition). There are at least two 
-problems related with this. The first, a quite obvious one, is that when EW corrections
+its definition). The problem with this definition is that, when EW corrections
 are included at fixed order, the first photon emission is included exactly at the matrix-element level. The inclusion of 
@@
 \textsc{Photos}~\cite{Barberio:1990ms,Barberio:1993qi,Golonka:2005pn}in Ref.~\cite{CarloniCalame:2016ouw}). However, this kind of agreement
-always comes \emph{a posteriori}, and cannot be ensured in general. The second, which
-applies for electrons, is that they are never measured as bare particles, because of the finite resolution 
-of the electromagnetic calorimeter. Since collinear photonic emission cannot be resolved, data 
-involving electrons should also be published
-in terms of dressed particles, after applying some recombination scheme. This has the further advantage of being 
-inclusive on the effect of further collinear emissions. For what concerns muons, while in principle
-the concept of bare muons is a physical one, it should be kept in mind that modern, general-purpose codes employed to
-compute EW corrections treat leptons as massless. This fact encourages to explore the possibility of employing dressed
-muons, on the same footing as their electron counterpart. It is reassuring to acknowledge that this practice is already quite common in experimental analyses:
-indeed, to mention two examples of analyses discussed in this paper, in Ref.~\cite{Aad:2015auj} data for dressed leptons are published, together with the pre- and post-ISR ones, while Refs.~\cite{Sirunyan:2019bzr} employs a dressed-lepton definition.
+always comes \emph{a posteriori}, and cannot be ensured in general. A more physical definition would be either the one of bare leptons (post FSR)
+or of recombined ones. The problem with the former is that 
+electrons are never measured as bare particles, because of the finite resolution 
+of the electromagnetic calorimeter. For what concerns muons, while in principle the concept of a bare muon is physical, it should be kept in 
+mind that modern, general-purpose codes employed to
+compute EW corrections treat leptons as massless, to ensure numerical stability of the matrix elements. In this case, using bare leptons is not collinear safe. Recombined
+leptons avoid all these shortcomings, with the further advantage of being 
+inclusive on the effect of extra collinear emissions. This fact encourages to explore the possibility of employing a dressed-lepton
+definition, regardless of the leptonic flavour. It is reassuring to acknowledge that this practice is already being followed in experimental analyses:
+indeed, to mention two examples of analyses discussed in this paper, in Ref.~\cite{Aad:2015auj} data for dressed leptons are published, together with the Born-level
+and bare ones, while Refs.~\cite{Sirunyan:2019bzr} employs a dressed-lepton definition.
+
+{\bf this section may be troublesome with part of our community, e.g. paper of tackmann suggests to use born-level electrons https://arxiv.org/pdf/2006.11382.pdf}
 

### 2020-07-24 paper/sec-doublecounting.tex
small addition

@@
 Indeed, at $\mathcal O(\alpha^3)$, the reaction $q \gamma \to \ell^+ \ell^- q$ becomes possible, which
-includes both kind of topologies discussed above, see Fig.~\ref{fig:dy-pi}. While it is common sense that the QCD counterpart of this subtraction should never 
+includes both kind of topologies discussed above (and needs both in order to yield an IR-finite result), see Fig.~\ref{fig:dy-pi}.
+While it is common sense that the QCD counterpart of this subtraction should never
 be performed---nobody would ever

### 2020-07-26 paper/sec-doublecounting.tex
Add corrections and comments from CS to DC section

@@
-\section{On the conistency of experimental data}
+\section{On the consistency of experimental data}
 \label{sec:doublecounting}
 
-As it has been mentioned in the introduction, the ability to consistently include electro-weak correction in
-PDF fits is not enough to make a fully-fledged fit possible in a consistent manner. Indeed, experimental data should
-be provided in  a format that allows PDF collaborations to employ them in such fits in a theoretically sound manner. Before concluding the paper,
-we will try to provide some guidelines, to facilitate a consistent presentation of experimental data. Common sources of inconsistency in the extraction of data
-typically lead to accounting multiple times for EW effects (so-called double counting), or to not accounting at
-all for such effects.
+The ability to include theoretical calculations of EW corrections in
+PDF determinations, as has been mentioned in the introduction, is not enough to make a \emph{consistent} fit possible. Indeed, experimental data should
+be provided in a format that allows PDF collaborations to easily employ them in these fits in a theoretically sound manner. Before concluding the paper,
+we will provide some guidelines to facilitate a consistent presentation of experimental data to that end.
+We focus on the problem of subtracting (partial) EW effects in the data, which, in PDF fits with theory predictions including them, leads to multiple accounting of EW effects (so-called double counting).
 
@@
 An example is the subtraction of (irreducible) background processes which must not be considered as such. A very blatant case
-is neutral-current Drell--Yan, where the signal process is an opposite-sign lepton pair, which starts
-at $\mathcal O(\alpha^2)$. Because this process is usually thought
-as a quark-initiated, $s$-channel mechanism ($q\bar q \to \gamma^*/Z \to \ell^+ \ell^-$), in many analyses the photon-induced component,
-$\gamma \gamma \to \ell^+ \ell^-$ in the $t$ channel, is considered as a different process, often as a background, and it is possibly 
-evaluated with different parton densities and/or including (unphysical) higher-order 
+is neutral-current Drell--Yan, where the signal process is the production of an opposite-sign lepton pair, which starts
+at $\mathcal O(\alpha^2)$. Because this process is sometimes thought
+as a quark-initiated $s$-channel mechanism ($q\bar q \to \gamma^*/Z \to \ell^+ \ell^-$), in many analyses the photon-induced component,
+$\gamma \gamma \to \ell^+ \ell^-$ in the $t$ channel, is considered to be a different process, and therefore as a background and subtracted.
+The subtraction from the measured data is done by calculating the theoretical predictions of the double-photon initiated contribution, possibly including (unphysical) higher-order
 corrections. For example, in refs.~\cite{Aaboud:2017ffb,Aad:2016zzw} (a similar statement appears also in an older analysis~\cite{Aad:2013iua}), one reads:
@@
 While it is common sense that the QCD counterpart of this subtraction should never
-be performed---nobody would ever
+be performed---no one would 
 consider to \enquote{subtract} the gluon-initiated contribution to top-pair production in top analyses---seemingly it is not so
@@
 or just a part, for example deconvolving multiple-photon radiation from light particles in the final state. This applies mostly
-to processes such as neutral- or charge-current Drell--Yan, specially when electrons are considered. The problem lie in the fact that
+to processes such as neutral- or charge-current Drell--Yan, specially when electrons are considered. The problem lies in the fact that
  electrons, and to a lesser extent muons, tend to radiate photons, and such photons are typically not accounted
-for in hard matrix-elements. Thus, leptons that are measured in the detector are less energetic, and this fact is compensated for
-by undoing the photon shower before publishing data, which are referred to e.g.\ as \emph{Born-level electrons} (see e.g. Ref.~\cite{Aad:2015auj} for
-its definition). The problem with this definition is that, when EW corrections
-are included at fixed order, the first photon emission is included exactly at the matrix-element level. The inclusion of 
+for in QCD matrix-elements. Thus, leptons that are measured in the detector are less energetic, and this fact is compensated for
+by inverting the photon shower. The resulting dataset is e.g.\ referred to as \emph{pre-FSR} with observables of \emph{Born-level electrons} (see e.g.\ Ref.~\cite{Aad:2015auj} for
+its definition).
+These datasets are needed for and correctly used in QCD-only PDF determinations, since the EW corrections to some DY observables can be significant, and excluding them would therefore degrade the fit.
+In fits including fixed-order EW corrections the problem with this definition is that the first photon emission is included exactly at the matrix-element level. The inclusion of
 subsequent emission would require the matching with the QED shower, which is not yet available for general processes. It is interesting
-to note that one can tune the QED parton shower in order to mimick NLO EW effects, so that a prediction only accurate at NLO
+to note that one can tune the QED parton shower in order to mimic NLO EW effects, so that a prediction only accurate at NLO
 QCD displays a remarkable agreement with another at NLO QCD+EW when the photonic shower is included (see example the behaviour of predictions showered with
 \textsc{Photos}~\cite{Barberio:1990ms,Barberio:1993qi,Golonka:2005pn}in Ref.~\cite{CarloniCalame:2016ouw}). However, this kind of agreement
-always comes \emph{a posteriori}, and cannot be ensured in general. A more physical definition would be either the one of bare leptons (post FSR)
+always comes \emph{a posteriori}, and cannot be ensured in general.
+A more physical definition would be either the one of bare leptons (post FSR; \textbf{CS}: post FSR is for recombined leptons, I haven't seen a dataset for bare leptons, but they should exist)
 or of recombined ones. The problem with the former is that 
 electrons are never measured as bare particles, because of the finite resolution 
-of the electromagnetic calorimeter. For what concerns muons, while in principle the concept of a bare muon is physical, it should be kept in 
+of the electromagnetic calorimeter.
+For what concerns muons, while in principle the concept of a bare muon is physical (\textbf{CS}: cite papers for non-collinear safe observables/subtraction?), it should be kept in
 mind that modern, general-purpose codes employed to
@@
 indeed, to mention two examples of analyses discussed in this paper, in Ref.~\cite{Aad:2015auj} data for dressed leptons are published, together with the Born-level
-and bare ones, while Refs.~\cite{Sirunyan:2019bzr} employs a dressed-lepton definition.
+and bare ones (\textbf{CS}: wrong?), while Refs.~\cite{Sirunyan:2019bzr} employs a dressed-lepton definition.
 
-{\bf this section may be troublesome with part of our community, e.g. paper of tackmann suggests to use born-level electrons https://arxiv.org/pdf/2006.11382.pdf}
-
-\clearpage
-\noindent
-\textbf{Notes from CS}:
-\begin{itemize}
-\item overall we should also point out the positive (rewrite the last part of this section a bit): for leptonic observables there always seems to be a pre-/post-FSR dataset with born/dressed leptons
-\begin{itemize}
-\item is this really the case?
-\item is this also the case for non-leptonic observables? Specifically: Do ATLAS/CMS subtract photon radiation for observables of jet, top, or any other reconstructed objects (for instance: Z pT)?
-\end{itemize}
-\item double-photon initiated processes:
-\begin{itemize}
-\item how do they subtract it exactly (one analysis uses a concrete PDF set and subtracts the theory prediction; point out first how they do it, then that this is not a good idea, even if it would make sense: mixing theory predictions with measurements)
-\item explain why they do it and point that this is not good
-\end{itemize}
-\item stress subtraction of \emph{irreducible} backgrounds
-\end{itemize}
+{\bf this section may be troublesome with part of our community, e.g. paper of Tackmann suggests to use born-level electrons https://arxiv.org/pdf/2006.11382.pdf}

### 2020-07-27 paper/sec-doublecounting.tex
some additions in the DC part

@@
 A second example is related to removing EW effects from data. These can be either the full EW corrections
-or just a part, for example deconvolving multiple-photon radiation from light particles in the final state. This applies mostly
+or just a part. In either case, a comparison between these data and a NLO-EW accurate simulation aimed at the extraction of some parameter would be meaningless, as some effects included in the latter
+have been removed from the former. The typical example relevant for LHC is the deconvolution of effects due to multiple-photon radiation
+from light particles in the final state. This applies mostly
 to processes such as neutral- or charge-current Drell--Yan, specially when electrons are considered. The problem lies in the fact that

### 2020-07-27 paper/app-pineappl.tex
Complete section 2 and appendix A

@@
-\section{More technical details about \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
+\section{Installation and usage of \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
 
@@
 \begin{lstlisting}[language=bash]
-curl --proto '=https' --tlsv1.2 -sSf https://sh.rustup.rs | sh
+ $ curl --proto '=https' --tlsv1.2 -sSf https://sh.rustup.rs | sh
 \end{lstlisting}
@@
 \begin{lstlisting}[language=bash]
-cargo install pineappl_cli
+ $ cargo install pineappl_cli
 \end{lstlisting}
@@
 \begin{lstlisting}[language=bash]
-cargo install cargo-c
+ $ cargo install cargo-c
 \end{lstlisting}
@@
 \begin{lstlisting}[language=bash]
-git clone https://github.com/N3PDF/pineappl/
-cd pineappl_capi/
-cargo cinstall --release --prefix=${prefix}
+ $ git clone https://github.com/N3PDF/pineappl/
+ $ cd pineappl_capi/
+ $ cargo cinstall --release --prefix=DIRECTORY
 \end{lstlisting}
-The last line will install the C header \texttt{pineappl\_capi.h}, the library, and a pkg-config\footnote{A standard way on Linux to express how dependencies are compiled/linked against, see \url{https://www.freedesktop.org/wiki/Software/pkg-config/}} file (\texttt{pineappl\_capi.pc}).
+The last line will install the C header \texttt{pineappl\_capi.h}, the library, and a pkg-config\footnote{A standard way on Linux to express how dependencies are compiled/linked against, see \url{https://www.freedesktop.org/wiki/Software/pkg-config/}} file (\texttt{pineappl\_capi.pc}) into the directory specified as \texttt{DIRECTORY}.
 Make sure that the environment variables \texttt{PATH}, \texttt{LD\_LIBRARY\_PATH}, and \texttt{PKG\_CONFIG\_PATH} are properly set.
 The latter is needed for \texttt{pkg-config -{}-cflags -{}-libs pineappl\_capi} to work, which prints the necessary compiler/linker flags.
+
+After being installed, you can compile and link against the library.
 See App.~\ref{app:example-program} for an example.
@@
 Updated installation instructions are kept in the file \texttt{README.md} in \textsc{PineAPPL}'s repository at \url{https://github.com/N3PDF/pineappl/}.
-
-\subsection{Drell--Yan \texorpdfstring{$n$}{n}-tuple storage size}
-\label{app:drell-yan-storage}
-
-TODO
 
@@
 
-\clearpage
 \begin{lstlisting}[language=C++,mathescape=true]
@@
 \end{lstlisting}
-\clearpage
 
@@
 
-TODO
+The program \texttt{pineappl} can be used to perform quick convolutions and other calculations with existing grids on the command line.
+If started without any arguments, it prints its help and lists all supported subcommands:
+\begin{lstlisting}[language=bash]
+ $ pineappl
+pineappl 0.1.0
+Read, write, and query PineAPPL grids
+
+USAGE:
+    pineappl <SUBCOMMAND>
+
+FLAGS:
+    -h, --help       Prints help information
+    -V, --version    Prints version information
+
+SUBCOMMANDS:
+    channels           Shows the contribution for each partonic channel
+    convolute          Convolutes a PineAPPL grid with a PDF set
+    help               Prints this message or the help of the given
+                       subcommand(s)
+    luminosity         Shows the luminosity function
+    merge              Merges one or more PineAPPL grids together
+    orders             Shows the predictions for all bins for each order
+                       separately
+    pdf_uncertainty    Calculates PDF uncertainties
+\end{lstlisting}
+As an example we show the grid produced for the ATLAS DY high-mass lepton-pair production (from section~\ref{sec:atlas-high-mass-dy}).
+The output shows all 13 bins with lower (\texttt{xmin}) and upper limit (\texttt{xmax}) of the invariant mass $M_{\ell \bar{\ell}}$ of the lepton pair, with the differential cross section $\mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}}$ (\texttt{diff}), integrated cross section $(M_{\ell \bar{\ell}}^\mathrm{max} - M_{\ell \bar{\ell}}^\mathrm{min}) \mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}}$ (\texttt{integ}), together with the perturbative uncertainty estimated from a 7-point scale variation (\texttt{neg unc} and \texttt{pos unc}).
+\begin{lstlisting}[language=bash]
+ $ pineappl convolute ATLASZHIGHMASS49FB.pineappl \
+ > NNPDF31_nlo_as_0118_luxqed
+bin xmin xmax     diff        integ     neg unc pos unc
+---+----+----+------------+------------+-------+-------
+  0  116  130 2.0630698e-1  2.8882978e0  -2.08%   1.69%
+  1  130  150 9.1818985e-2  1.8363797e0  -1.79%   1.86%
+  2  150  170 4.5306370e-2 9.0612740e-1  -1.60%   1.98%
+  3  170  190 2.5894856e-2 5.1789712e-1  -1.66%   2.06%
+  4  190  210 1.6075267e-2 3.2150534e-1  -1.70%   2.10%
+  5  210  230 1.0526659e-2 2.1053317e-1  -1.71%   2.12%
+  6  230  250 7.1928162e-3 1.4385632e-1  -1.71%   2.13%
+  7  250  300 4.0776555e-3 2.0388277e-1  -1.70%   2.44%
+  8  300  400 1.4775481e-3 1.4775481e-1  -1.94%   2.87%
+  9  400  500 4.5473785e-4 4.5473785e-2  -2.30%   3.19%
+ 10  500  700 1.2164277e-4 2.4328555e-2  -2.41%   3.12%
+ 11  700 1000 1.9792340e-5 5.9377019e-3  -2.05%   2.12%
+ 12 1000 1500 2.0228761e-6 1.0114381e-3  -1.29%   0.47%
+\end{lstlisting}
 
@@
 
-TODO
+The following run card was used to produce the results shown in section~\ref{sec:atlas-high-mass-dy}.
+The only difference to a normal \textsc{mg5\_aMC@NLO} run is the switch \texttt{set iappl 1}, which enables filling a \textsc{PineAPPL} grid.
+For a complete set of runcards and patches see TODO.
+
+\lstset{
+  basicstyle=\ttfamily\small,
+  showstringspaces=false,
+  commentstyle=\ttfamily\small,
+  keywordstyle=\ttfamily\small,
+  identifierstyle=\color{black},
+  stringstyle=\color{black},
+}
+
+\begin{lstlisting}
+set complex_mass_scheme True
+import model loop_qcd_qed_sm_Gmu
+define p = p b b~
+define j = p
+generate p p > e+ e- [QCD QED]
+output @OUTPUT@
+launch @OUTPUT@
+fixed_order = ON
+set mz @MZ@
+set ymt @YMT@
+set ebeam1 3500
+set ebeam2 3500
+set pdlabel lhapdf
+set lhaid 324900
+set fixed_ren_scale True
+set fixed_fac_scale True
+set mur_ref_fixed @MZ@
+set muf_ref_fixed @MZ@
+set reweight_scale True
+set ptl = 25.0
+set etal = 2.5
+set mll = 116
+#user_defined_cut set mmllmax = 1500.0
+set req_acc_FO 0.0001
+set iappl 1
+done
+quit
+\end{lstlisting}

### 2020-07-27 paper/sec-doublecounting.tex
Complete section 2 and appendix A

@@
 we will provide some guidelines to facilitate a consistent presentation of experimental data to that end.
-We focus on the problem of subtracting (partial) EW effects in the data, which, in PDF fits with theory predictions including them, leads to multiple accounting of EW effects (so-called double counting).
+We focus on the problem of data with (partially) subtracted EW effects, which, in PDF fits with theory predictions including them, leads to double counting of these EW effects.
 

### 2020-07-27 paper/sec-pineappl.tex
Complete section 2 and appendix A

@@
 See appendix~\ref{app:example-program} for an example.
-%\textsc{PineAPPL} itself is written in Rust (see appendix~\ref{app:installation} for installation instructions).
 \item The shell command \texttt{pineappl}, which performs convolutions on the command line (see appendix~\ref{app:pineappl-demo}), without requiring the user to write a new program.
@@
 
-% TODO: add table with aMCfast notation
-
-%\begin{table}
-%\begin{tabular}{ll}
-%\toprule
-%Old notation & new notation \\
-%\midrule
-%\bottomrule
-%\end{tabular}
-%\caption{Translation table for the notation of ref.~\cite{Bertone:2014zva} to the one used in eq.~\eqref{eq:expansion}.}
-%\label{tab:amcfast-notation}
-%\end{table}
-
 If chosen dynamically the Ellis--Sexton scale $Q^2$ depends on the phase space, but we assume the fractions $\xi_\mathrm{R}$ and $\xi_\mathrm{F}$ to be constants of phase space in any case.
@@
 
-Note that in this section we have omitted the dependence of the weights, observable and scales on the specific kinematics for
-which they are computed. Indeed, beyond LO,
-different kinematic contributions have to be considered (in ref.~\cite{Bertone:2014zva} they are labelled with an index $\alpha$, see
-eq.\ 12 therein). Their consistent treatment must be ensured by the interface between
-\textsc{PineAPPL} and the specific cross-section computation at hand\footnote{
-    In the FKS subtraction scheme~\cite{Frixione:1995ms,Frixione:1997np} employed in \textsc{mg5\_aMC@NLO}
-    maximally one kind of kinematics for each counterterm (soft, collinear, and soft-collinear) is needed, but this
-    is not the general case, for example in the Catani--Seymour subtraction~\cite{Catani:1996jh} different dipoles may have different phase spaces and therefore different scales.}.
-However, \textsc{PineAPPL} remains completely blind to this fact, as all weights are filled into a given grid
-identified only by the indices $k, l, m, n$.
+Note that in this section we have omitted the dependence of the weights $w$, the observable $\mathcal{O}$, and the scales $\mu_\mathrm{F}, \mu_\mathrm{R}, Q^2$ on the specific kinematics for which they are computed.
+Indeed, beyond LO, different kinematic contributions have to be considered (in ref.~\cite{Bertone:2014zva}, for example, they are labelled with an index $\alpha$, see eq.~(12) therein).
+In the FKS subtraction scheme~\cite{Frixione:1995ms,Frixione:1997np} employed in \textsc{mg5\_aMC@NLO} maximally one type of kinematics for each counterterm (soft, collinear, and soft-collinear) is needed, but this is not the general case.
+In Catani--Seymour subtraction~\cite{Catani:1996jh}, for example, different dipoles have different phase spaces and therefore different scales.
+However, \textsc{PineAPPL} remains completely blind to this fact, and consistent treatment is ensured by correctly using the interface between \textsc{PineAPPL}, which fills each event into a grid using the \emph{numerical value} of $Q^2$.
 
@@
 The EW corrections also introduce quark--photon contributions, in analogy of QCD corrections introducing quark--gluon contributions.
-
-%At NLO this process has 63 different initial states, of which there is one photon--photon initial state and 31 initial states with at least one (anti-)quark.
-%The remaining 31 are given by the transposition of the partons from the first 31 initial states.
-
-% TODO: add graphical representation of the multi-coupling expansion
 
@@
 Furthermore, they reproduce the exact numerical value that is also calculated by the MC integrator.
-However, the price one has to pay is the size of the 4-tuples, which scales linearly with the number of phase-space weights $N$.
-Because the uncertainties of MC integrators shrink only as $1/\sqrt{N}$ this typically means \numrange{e6}{e9} phase-space points are necessary for a good convergence.
-In the case of the NLO Drell--Yan (section~\ref{sec:pineappl-example}) the 4-tuples need roughly TODO~\si{\giga\byte} of storage (see appendix~\ref{app:drell-yan-storage} for an explanation of this number).
+However, the price one has to pay is the size of the 4-tuples.
+To give a concrete example, NLO QCD+EW Drell--Yan lepton-pair production (see section~\ref{sec:pineappl-example} and section~\ref{sec:atlas-high-mass-dy}) needs \SI{159}{\giga\byte} of storage for a target precision of \SI{1}{\percent} of the integrated cross section with this precision.
+While this is an acceptable size, increasing the precision by an order of magnitude would require roughly 100 times the size, due to the Monte Carlo convergence that goes as $1/\sqrt{N}$ with $N$ being the number of 4-tuples.
 With increasing size also the speed of the convolution degrades, because it basically becomes bound by the speed with which the 4-tuples can be read from disk.
+However, due to the uncompressed nature of this representation it can serve as a intermediate format to develop and quickly cross check more space-efficient representations, which we will discuss next.
 
@@
 along each axis into a small numbers of bins and to insert the phase-space weights $w$ into the corresponding discrete bin.
-Using the bin centres and their values one already has a straightforward implementation of eq.~\eqref{eq:weight-map}, but given a finite number of bins it usually yields an insufficient approximation for the cross section.
-Increasing the number of bins improves the accuracy, but it also increases the space requirements.
-Interpolation methods offer more accuracy with the same number of bins.
+Using the bin centres and their values one already has a straightforward implementation of eq.~\eqref{eq:weight-map}, but given a finite number of bins usually yields an insufficient approximation for the cross section.
+Increasing the number of bins improves the precision, but it also increases the space requirements.
+Interpolation methods offer more precision using the same number of bins.
 
@@
 The function $y(x)$ maps events with large $x$ effectively linearly and small $x$ effectively logarithmically onto $y$.
-This reflects our knowledge of PDFs, which behave differently in those regions, and thereby increases the accuracy of the interpolation.
+This reflects our knowledge of PDFs, which behave differently in those regions, and thereby increases the precision of the interpolation.
 For the convolution of a grid with a PDF set also the inverse functions are needed, which are
@@
 
-Following ref.~\cite{Carli:2010rw} (see eq.~(17) therein), we divide the weights before filling them into the grid by the function
+Following ref.~\cite{Carli:2010rw} (see eq.~(17) therein), we furthermore divide the weights, before filling them into the grid, by the function
 \begin{equation}
@@
 This flattens the interpolated function in the region $x \to 1$, where the PDFs are small and tend towards zero, and enhances the function in the small-$x$ region.
-The effect of this step is an improvement of the accuracy that depends on the initial states and the process, but it can be as large as a factor of \numrange{10}{100} (one or two more correct digits), see section~TODO.
+The effect of this step is an improvement of the precision that depends on the initial states and the process, but it can be as large as a factor of \numrange{10}{100} (one or two more correct digits compared to the MC result).
 Before performing a convolution this step is inverted by simply multiplying the interpolated grid values with $\omega (x_1, x_2)$.
@@
 
-To illustrate the filling step we give an example in figure~\ref{fig:grid}, where, for simplicity, we assume we have chosen a static scale, so that we do not need to interpolate $\tau$ direction, and where we also limited the number of grid points to $N_y = 10$.
-To each grid point a numerical value $a_{i,j}$ is associated, and the set of all numerical values $\{ a_{i,j} \}$ for all grid indices $(i,j) \in [0,N_y) \times [0,N_y)$ constitute \enquote{the grid}.
+To illustrate the filling step we give an example in figure~\ref{fig:grid}, where, for simplicity, we assume we have chosen a static scale, so that we do not need to interpolate in $\tau$ direction, and where we also limited the number of grid points to $N_y = 10$.
+Each grid point has a numerical value $a_{i,j}$ associated, and the set of all numerical values $\{ a_{i,j} \}$ for all grid indices $(i,j) \in [0,N_y) \times [0,N_y)$ constitute \enquote{the grid}.
 Inserting a specific weight $W = w (x_1, x_2) / \omega(x_1, x_2)$ into the grid is shown in figure~\ref{fig:grid} as a small black square, inside the larger grey one.
@@
 where the product runs over all indices of the grid points covered by the grey square in figure~\ref{fig:grid}, starting the smallest index in the square, $k_i$ and $k_j$.
-We also remapped
+Finally, we remapped
 \begin{equation}
@@
 \end{equation}
-using $y_\text{min} = y(x_\text{max})$ and $y_\text{max} = y(x_\text{min})$ and the grid spacing $\Delta y = (y_\text{max} - y_\text{min})/(N_y-1)$, so that the integer part of $u(y)$ gives the grid index, e.g.\ $u(y_\text{min}) = 0$ and $u(y_\text{max}) = N_y - 1$.
-
-\begin{figure}
-\centering
-TODO
-\caption{TODO}
-\label{fig:example-grid}
-\end{figure}
-
-Finally, figure~\ref{fig:example-grid} shows an example of a convoluted grid, but differential in $x_1$ and $x_2$.
-
-\subsubsection{Combination of differently weighed phase-spaces points}
-
-To improve the convergence of phase-space integrations MC integrators usually use importance sampling, typically using one or both of VEGAS~\cite{} and multi-channel MC~\cite{}.
-Both algorithms are adaptive and perform a number of iterations, each iteration trying to improve the convergence by changing the distribution from which phase-space points are sampled.
-This raises the question if the differently sampled phase-space points are compatible with each other in the grid generation, and, if the answer is no, how this can be remedied.
+using $y_\text{min} = y(x_\text{max})$ and $y_\text{max} = y(x_\text{min})$ and the grid spacing $\Delta y = (y_\text{max} - y_\text{min})/(N_y-1)$, so that the integer part of $u(y)$ gives the grid index, e.g.\ $u(y_\text{min}) = 0$ and $u(y_\text{max}) = N_y - 1$, and the fractional part gives the location between the nearest grid points.

### 2020-07-28 run.sh
Print scale-varied results from the MC

@@ -162,11 +162,11 @@ EOF
     # compare the results from the grid and from mg5_aMC
     paste -d ' ' results.grid results.mg5_aMC | awk -v program=${program} \
         'function abs(x) { return x < 0.0 ? -x : x; }
-         BEGIN { print "---------------------------------------------------------------"
-                 print "   " program "       mg5_aMC   mg5_aMC unc.   sigmas   per mille"
-                 print "---------------------------------------------------------------" }
-         { printf "% e % e %e %8.3f %10.4f\n", $1, $4, $5, $5 != 0.0 ? abs($1-$4)/$5 : 0.0,
-                                               $4 != 0.0 ? abs($1-$4)/$4*1000 : 0.0 }' | \
+         BEGIN { print "----------------------------------------------------------------------------------------"
+                 print "   " program "       mg5_aMC   mg5_aMC unc.   sigmas   per mille   9-point scale var. (MC)"
+                 print "----------------------------------------------------------------------------------------" }
+         { printf "% e % e %e %8.3f %10.4f % e % e\n",
+                  $1, $4, $5, $5 != 0.0 ? abs($1-$4)/$5 : 0.0, $4 != 0.0 ? abs($1-$4)/$4*1000 : 0.0, $7, $8 }' | \
         tee results.log
 
     rm results.mg5_aMC results.grid

### 2020-07-28 paper/paper.tex
Sect.3, partial

@@
 Alessandro Vicini\\
-C.S.\ is supported by the European Research Council under the European Unions
+E.R.N. is supported by the European Commission through the Marie
+Sk\l odowska-Curie Action ParDHonS FFs.TMDs (grant number 752748).
+C.S.\ is supported by the European Research Council under the European Union's
 Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).

### 2020-07-28 paper/sec-results.tex
Sect.3, partial

@@
 pair production, and Z-boson (lepton-pair) production with non-zero transverse
-momentum at the LHC. For each of these processes, we consider the measurments
+momentum at the LHC. For each of these processes, we consider the measurements
 described below.
@@
 the invariant mass of the lepton pair, $y_{\ell\bar\ell}$ and $M_{\ell\bar\ell}$,
-measured by the CMS experiment at 7~TeV~\cite{Chatrchyan:2013tia}.
+measured by the CMS experiment at a centre-of-mass energy of
+7~TeV~\cite{Chatrchyan:2013tia}.
 These measurements are currently included as standard in the
@@
 been extensively studied in the context of PDF fits in
-Refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml}.
+Refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml}, and
+included by default in the CT18~\cite{Hou:2019efy} analysis.
 Because EW corrections are significantly smaller for distributions differential
 in the rapidity of either the top quark or the top-quark
-pair~\cite{Czakon:2017wor}, these were preferred for inclusion in the NNPDF3.1
-set~\cite{Ball:2017nwa}.
+pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
+in the NNPDF3.1 analysis~\cite{Ball:2017nwa}.
 
@@
 the $Z$ boson, $p_T^Z$, measured by the CMS experiment at a centre-of-mass
-energy of 13~TeV~\cite{Sirunyan:2019bzr}. This measurement has not been
-included in a PDF determination yet. Given that it has sub-percent
-uncertainties, it is expected that EW corrections will be essential to
-achieve a good description of it, and to constrain accurately the PDFs.
-A similar challenge was observed in similar measurements, from the
-ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa} experiment at a
-centre-of-mass energy of 8~TeV, in Ref.~\cite{Boughezal:2017nla}, which lead to
-their partial inclusion (upon the selection of an appropriate kinematic cut)
-in the NNDPF3.1 PDF set~\cite{Ball:2017nwa} and in variants of the CT18 PDF
-set~\cite{Hou:2019efy}.
+energy of 13~TeV~\cite{Sirunyan:2019bzr}. So far, this measurement has not been
+included in any PDF determination. Because it has sub-percent uncertainties,
+EW corrections are expected to be essential in order to achieve a good
+description of it, and to constrain accurately the PDFs. Analogous measurements,
+from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
+experiments at a centre-of-mass energy of 8~TeV were partly included (upon the
+selection of an appropriate kinematic cut that excluded bins with large EW
+corrections) in the NNDPF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
+the CT18 PDF set~\cite{Hou:2019efy}.
 
@@
 
-We discuss,
-\begin{itemize}
-\item in section~\ref{sec:atlas-high-mass-dy}, ATLAS high-mass DY lepton-pair production at \SI{7}{\tera\electronvolt} \cite{Aad:2013iua}, measuring $\mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}}$ for the lepton-pair invariant mass $M_{\ell \bar{\ell}} > \SI{116}{\giga\electronvolt}$,
-\item in section~\ref{sec:cms-dy}, CMS DY lepton-pair production at \SI{7}{\tera\electronvolt} \cite{Chatrchyan:2013tia}, measuring $\mathrm{d} \sigma / \mathrm{d} y_{\ell \bar{\ell}}$ for six slices in the range $\SI{20}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{1500}{\giga\electronvolt}$,
-\item in section~\ref{sec:atlas-top-pair-production}, ATLAS top-pair production at \SI{8}{\tera\electronvolt} \cite{Aad:2015mbv}, measuring
-\begin{itemize}
-\item the transverse momentum of the reconstructed top, $\mathrm{d} \sigma / \mathrm{d} p_\mathrm{T}^\mathrm{t}$,
-\item its rapidity, $\mathrm{d} \sigma / \mathrm{d} y_\mathrm{t}$,
-\item the invariant mass of the reconstructed top pair, $\mathrm{d} \sigma / \mathrm{d} M_{\mathrm{t} \bar{\mathrm{t}}}$, and
-\item its rapidity, $\mathrm{d} \sigma / \mathrm{d} M_{\mathrm{t} \bar{\mathrm{t}}}$,
-\end{itemize}
-\item in section~\ref{sec:cms-transverse-momentum}, CMS transverse momentum of the Z boson at \SI{13}{\tera\electronvolt} \cite{Sirunyan:2019bzr}, measuring $\mathrm{d} \sigma / \mathrm{d} p_\mathrm{Z}$ for $p_\mathrm{Z} > \SI{20}{\giga\electronvolt}$.
-\end{itemize}
-We used the MC \texttt{mg5\_aMC@NLO}~\cite{} and the PDF set \texttt{NNPDF31\_as\_0118\_luxqed}~\cite{} to generate the predictions.
-The chosen PDF set contains a photon PDF calculated from the LUXQED method~\cite{}.
-For each process---except top-pair production, which has stable tops in the final state---we use a complex-mass scheme~\cite{} as described in ref.~\cite{}.
-The values of the most important parameters are
+We generate each process by means of the Universal FeynRules Output
+(UFO)~\cite{Degrande:2011ua} model {\tt loop\_qcd\_qed\_sm\_Gmu},
+included as standard in {\sc MG5\_aMC}. It contains the UV and $R_2$
+counterterms relevant to NLO QCD and EW corrections, the latter in the
+$\overline{G}_\mu$ scheme. The model features five massless quark flavours,
+sets the CKM matrix equal to the identity, and is compatible with the usage of
+the complex mass (CM) scheme for all massive particles, see
+Ref.~\cite{Frederix:2018nkq} for details. We use this scheme
+for all processes that do not involve stable top quarks in the final state.
+The photon is always considered as part of the proton in the initial state and
+of any hadronic jet produced in the final state: PI effects and EW corrections
+are therefore treated on the same footing. We use a PDF set that contains a
+consistently defined photon PDF, namely
+{\tt NNPDF31\_as\_0118\_luxqed}~\cite{Bertone:2017bme}. We evaluate the PDF
+uncertainty associated to the theoretical predictions a posteriori, that is,
+we convolve the fast interpolation grid generated with {\sc PineAPPL} with
+each member in the PDF set, and we compute the associated standard deviation.
+
+The central values of the renormalisation and factorisation scales, $\mu_R$ and
+$\mu_F$, are chosen, for each process, as follows. In the case of DY lepton pair
+production, we use the fixed scale $\mu_R=\mu_F=M_Z$, where $M_Z$ is the mass
+of the $Z$-boson, for the ATLAS measurement, and the dynamic scale
+$\mu_R=\mu_F=$ for the CMS measurement.
+In the case of top-quark pair production, we use the dynamic scales
+$\mu_R=\mu_F=\sqrt{m_t^2+(p_T^t)^2}{\Big /}2$ for the distribution differential
+in the transverse momentum of the top quark, and $\mu_R=\mu_F=H_T/4$ for the
+distribution differential in the invariant mass of the top-quark pair, where
+$H_T=\sqrt{m_t^2+(p_T^t)^2}+\sqrt{m_t^2+(p_T^{\bar{t}})}$, with $m_t$,
+$p_T^t$ and $p_T^{\bar t}$ the mass of the top quark and the transverse momenta
+of the top and antitop quarks, respectively. These choices were demonstrated
+to maximise the convergence of the perturbative expansion~\cite{Czakon:2016dgf}.
+In the case of $Z$-boson production with non-zero transverse momentum, we use
+$\mu_R=\mu_F=M_Z$. In order to estimate the missing higher-order uncertainty,
+we allow the events to be reweighted in the Monte Carlo generation upon scale
+variations. As is customary, the factorisation and renormalisation scales
+are varied down to a factor $1/2$ and up to a factor $2$.
+
+The values of the relevant physical parameters are chosen as
 \begin{equation}
-\begin{aligned}
-M_\mathrm{W} &= \SI{80}{\giga\electronvolt} \text{,} \quad &
-M_\mathrm{Z} &= \SI{90}{\giga\electronvolt} \text{,} \quad &
-m_\mathrm{t} &= \SI{170}{\giga\electronvolt} \text{,} \\
-\Gamma_\mathrm{W} &= \SI{2}{\giga\electronvolt} \text{,} &
-\Gamma_\mathrm{Z} &= \SI{2}{\giga\electronvolt} \text{,} &
-G_\mu &= \text{.}
-\end{aligned}
+%\begin{aligned}
+M_\mathrm{W} = \SI{80}{\giga\electronvolt} \text{,} \quad 
+M_\mathrm{Z} = \SI{90}{\giga\electronvolt} \text{,} \quad 
+m_\mathrm{t} = \SI{170}{\giga\electronvolt} \text{,} \quad
+\Gamma_\mathrm{W} = \SI{2}{\giga\electronvolt} \text{,} \quad
+\Gamma_\mathrm{Z} = \SI{2}{\giga\electronvolt} \text{,} 
+\label{eq:parameters}
+%\end{aligned}
 \end{equation}
+where $M_W$, $M_Z$ and $m_t$ are the values of the $W$-boson, $Z$-boson and
+top quark masses, respectively, and $\Gamma_W$ and $\Gamma_Z$ are the width of
+the $W$-boson and of the $Z$-boson, respectively. The value of the strong
+coupling is chosen consistently with the PDF set, $\alpha_s(M_Z)=0.118$.
 
-\noindent
-TODO for each of the following subsections:
-\begin{itemize}
-\item size of the photon-initiated contributions,
-\item largest partonic channel,
-\item most important $x$ region,
-\item PDF uncertainty,
-\end{itemize}
+Finally, we implement the kinematic cuts specified in the corresponding
+experimental analyses. In the case of high-mass DY lepton pair
+production at 7~TeV measured by ATLAS, we require $p_T^\ell>25$~GeV,
+$|\eta_\ell|<2.5$ and 116~GeV$<M_{\ell\bar\ell}<$ 1500~GeV for the transverse
+momentum and the rapidity of each lepton and for the invariant mass of the
+lepton pair, respectively. In the case of the DY lepton-pair production at
+7~TeV measured by CMS, we require $p_T^{\ell_1}>14$~GeV, $p_T^{\ell_2}>9$~GeV,
+$|\eta_\ell|<2.4$, $|\eta_{\ell\bar\ell}|<2.4$ and 20~GeV$<M_{\ell\bar\ell}<$ 1500~GeV
+for the transverse momentum and the rapidity of each lepton, and for the
+rapidity and the invariant mass of the lepton pair. In the case of $Z$-boson
+production with non-zero transverse momentum at 13~TeV measured by CMS, we
+require $p_T^\ell>25$~GeV, $|\eta_\ell|<2.4$,
+$M_Z$-15~GeV$<M_{\ell\bar\ell}<M_Z$+20~GeV,
+$|\eta_{\ell\bar\ell}|<2.4$ and 20~GeV$<p_T^{\ell\bar\ell}<1500$~GeV for the
+transverse momentum and rapidity of each lepton, and for the invariant mass,
+rapidity and transverse momentum of the lepton pair.
 
-\subsection{ATLAS high-mass DY lepton-pair production at \SI{7}{\tera\electronvolt}}
-\label{sec:atlas-high-mass-dy}
-
-\begin{equation}
-\begin{gathered}
-p_\mathrm{T}^\ell > \SI{25}{\giga\electronvolt} \text{,} \quad |\eta_\ell| < 2.5 \text{,} \\
-\SI{116}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{1500}{\giga\electronvolt} \text{,}
-\end{gathered}
-\end{equation}
-
-\subsection{CMS DY lepton-pair production at \SI{7}{\tera\electronvolt}}
-\label{sec:cms-dy}
-
-\begin{equation}
-\begin{gathered}
-p_\mathrm{T}^{\ell_1} > \SI{14}{\giga\electronvolt} \text{,} \quad p_\mathrm{T}^{\ell_2} > \SI{9}{\giga\electronvolt} \text{,} \quad |\eta_\ell| < 2.4 \text{,} \\
-|\eta_{\ell \bar{\ell}}| < 2.4 \text{,} \quad \SI{20}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{1500}{\giga\electronvolt} \text{,}
-\end{gathered}
-\end{equation}
-
-\subsection{ATLAS top-pair production at \SI{8}{\tera\electronvolt}}
-\label{sec:atlas-top-pair-production}
-
-\subsection{CMS transverse momentum of the Z boson at \SI{13}{\tera\electronvolt}}
-\label{sec:cms-transverse-momentum}
-
-\begin{equation}
-\begin{gathered}
-p_\mathrm{T}^\ell > \SI{25}{\giga\electronvolt} \text{,} \quad |\eta_\ell| < 2.4 \text{,} \quad M_\mathrm{Z} - \SI{15}{\giga\electronvolt} < M_{\ell \bar{\ell}} < M_\mathrm{Z} + \SI{20}{\giga\electronvolt} \text{,} \\
-|\eta_{\ell \bar{\ell}}| < 2.4 \text{,} \quad \SI{20}{\giga\electronvolt} < p_\mathrm{T}^{\ell \bar{\ell}} < \SI{1500}{\giga\electronvolt} \text{,}
-\end{gathered}
-\end{equation}
+\subsection{Numerical results}
+\label{subsec:numerical_results}
 
@@
 
+\noindent
+TODO for each of the following subsections:
+\begin{itemize}
+\item size of the photon-initiated contributions,
+\item largest partonic channel,
+\item most important $x$ region,
+\item PDF uncertainty,
+\end{itemize}
+
 %ERN 7 Apr: there is consensus on the fact that we should present results for the

### 2020-07-28 paper/sec-results.tex
Small tweaks

@@
 processes, we resort to measurements commonly devised for inclusion in PDF
-fits. Our aim is twofold. On the one hand, we want to validate the results
-obtained with \textsc{PineAPPL}; on the other hand, we want to assess the
-impact of the EW corrections for usual experimental setups. We describe first
+fits. Our aim is twofold. First, we want to validate the results
+obtained with \textsc{PineAPPL}; second, we want to assess the
+impact of the EW corrections for usual experimental setups. We describe, first,
 the processes and measurements that we consider, then the computational
@@
 variations. As is customary, the factorisation and renormalisation scales
-are varied down to a factor $1/2$ and up to a factor $2$.
+are varied down to a factor $1/2$ and up to a factor $2$, and an envelope
+from the nine-point scale variations is constructed.
 

### 2020-07-28 paper/sec-doublecounting.tex
addressing CS's comments in sec 4

@@
 for in QCD matrix-elements. Thus, leptons that are measured in the detector are less energetic, and this fact is compensated for
-by inverting the photon shower. The resulting dataset is e.g.\ referred to as \emph{pre-FSR} with observables of \emph{Born-level electrons} (see e.g.\ Ref.~\cite{Aad:2015auj} for
+by inverting the photon shower. The resulting dataset is e.g.\ referred to as \emph{pre-FSR} or \emph{Born-level electrons} (see e.g.\ Ref.~\cite{Aad:2015auj} for
 its definition).
@@
 \textsc{Photos}~\cite{Barberio:1990ms,Barberio:1993qi,Golonka:2005pn}in Ref.~\cite{CarloniCalame:2016ouw}). However, this kind of agreement
-always comes \emph{a posteriori}, and cannot be ensured in general.
-A more physical definition would be either the one of bare leptons (post FSR; \textbf{CS}: post FSR is for recombined leptons, I haven't seen a dataset for bare leptons, but they should exist)
-or of recombined ones. The problem with the former is that 
+always comes \emph{a posteriori}, and cannot be ensured in general. A more physical definition would be either the one of bare leptons (the leptons as they emerge after FSR)
+or of recombined ones (leptons and photons are clustered together and their momenta are combined, in analogy with jets in QCD). The problem with the former is that 
 electrons are never measured as bare particles, because of the finite resolution 
@@
 indeed, to mention two examples of analyses discussed in this paper, in Ref.~\cite{Aad:2015auj} data for dressed leptons are published, together with the Born-level
-and bare ones (\textbf{CS}: wrong?), while Refs.~\cite{Sirunyan:2019bzr} employs a dressed-lepton definition.
+and bare ones, while Refs.~\cite{Sirunyan:2019bzr} employs a dressed-lepton definition.
 

### 2020-07-28 paper/paper.tex
addressing CS's comments in sec 4
v0 of the abstract

@@
 
-\abstract{}
+\abstract{We introduce {\sc PineAPPL}, a computer library that makes it possible to produce fast interpolation 
+grids for fitting parton distribution functions (PDFs)
+including corrections of strong and electroweak origin. After presenting
+the features and performances of such a code, we show how to interface {\sc PineAPPL} with general-purpose
+softwares that allow the user to compute such corrections, providing an explicit example with
+{\sc MadGraph5\_aMC@NLO}. We showcase some phenomenological result focusing on processes and observables
+relevant for PDF fits, and 
+we discuss what steps need to be undertaken in the presentation of experimental data in order to have them
+consistently included in a fit including electroweak corrections.}
 
@@
 treatment of EW effects in experimental data. \\
-Alessandro Vicini\\
+%Alessandro Vicini\\
 E.R.N. is supported by the European Commission through the Marie

### 2020-07-28 paper/sec-results.tex

@@
 production, we use the fixed scale $\mu_R=\mu_F=M_Z$, where $M_Z$ is the mass
-of the $Z$-boson, for the ATLAS measurement, and the dynamic scale
-$\mu_R=\mu_F=$ for the CMS measurement.
+of the $Z$-boson, for the ATLAS measurement, and the scale
+$\mu_R=\mu_F=M_{\ell\bar\ell}$, where $M_{\ell\bar\ell}$ is the central value of each
+invariant mass bin, for the CMS measurement.
 In the case of top-quark pair production, we use the dynamic scales
@@
 \label{subsec:numerical_results}
+
+Given one of the measurements discussed in
+Sect.~\ref{subsec:processes_and_measurements}, we compute the expectation
+value of the corresponding observable in for each bin in two different ways:
+directly, by means of {\sc MG5\_aMC}, and a posteriori, by convolving the
+fast interpolation grid produced by {\sc PineAPPL} with the PDF set specified
+in Sect.~\ref{subsec:computational_settings}. In order to validate the
+
+\paragraph{DY lepton pair production.}
+
+\paragraph{Top-quark pair production.}
+
+\paragraph{$Z$-boson production with non-zero transverse momentum.}
 

### 2020-07-28 paper/paper.tex
small correction

@@
 we discuss what steps need to be undertaken in the presentation of experimental data in order to have them
-consistently included in a fit including electroweak corrections.}
+consistently employed in a fit including electroweak corrections.}
 

### 2020-07-28 paper/paper.tex
typo
Change the title to something more meaningful

@@
 
-\title{Including EW and mixed QCD-EW corrections into PDF fits}
+\title{PineAPPL: EW and mixed QCD--EW corrections for PDF fits}
 
@@
 \acknowledgments
-We are grateful to Rikkert Frederix for discussions and explanation about
+We are grateful to Rikkert Frederix for discussions and explanations about
 \textsc{aMCfast}. We acknowledge discussions with 

### 2020-07-28 paper/sec-doublecounting.tex
Add smaller correction to the DC section

@@
 
-\begin{figure}[ht!]
+\begin{figure}
     \centering
-    \begin{overpic}[width=0.6\textwidth, trim=0.cm 11cm 0.cm 10cm, clip=True]{figures/dy-pi.pdf}
-        \put (5, 33) {\large $q$}
-        \put (20, 37) {\large $q$}
-        \put (38, 5) {\large $\ell^+$}
-        \put (38, 31) {\large $\ell^-$}
+    \begin{overpic}[width=0.6\textwidth, trim=0.cm 11cm 0.cm 10cm, clip=True]{figures/dy-pi}
+        \put (5, 33) {\large $\mathrm{q}$}
+        \put (20, 37) {\large $\mathrm{q}$}
+        \put (38, 5) {\large $\bar{\ell}$}
+        \put (38, 31) {\large $\ell$}
         \put (11, 6) {\large $\gamma$}
         %
-        \put (65, 9) {\large $q$}
-        \put (73, 30) {\large $q$}
-        \put (96, 25) {\large $\ell^-$}
-        \put (96, 8) {\large $\ell^+$}
+        \put (65, 9) {\large $\mathrm{q}$}
+        \put (73, 30) {\large $\mathrm{q}$}
+        \put (96, 25) {\large $\ell$}
+        \put (96, 8) {\large $\bar{\ell}$}
         \put (55, 26) {\large $\gamma$}
@@
     Photon-induced (left) and quark-induced (right) contributions to the Drell-Yan process. In black, the LO process is shown.
-    In red, the initial-state splitting leading to the real-emission $q \gamma \to \ell^+ \ell^- q$ is highlighted. Such a 
+    In red, the initial-state splitting leading to the real-emission $\mathrm{q} \gamma \to \ell \bar{\ell} \mathrm{q}$ is highlighted. Such a
     real emission enters in the NLO EW corrections.}
@@
 at $\mathcal O(\alpha^2)$. Because this process is sometimes thought
-as a quark-initiated $s$-channel mechanism ($q\bar q \to \gamma^*/Z \to \ell^+ \ell^-$), in many analyses the photon-induced component,
-$\gamma \gamma \to \ell^+ \ell^-$ in the $t$ channel, is considered to be a different process, and therefore as a background and subtracted.
+as a quark-initiated $s$-channel mechanism ($\mathrm{q} \bar{\mathrm{q}} \to \gamma^*/Z \to \ell \bar{\ell}$), in many analyses the photon-induced component,
+$\gamma \gamma \to \ell \bar{\ell}$ in the $t$ channel, is considered to be a different process, and therefore as a background and subtracted.
 The subtraction from the measured data is done by calculating the theoretical predictions of the double-photon initiated contribution, possibly including (unphysical) higher-order
@@
 \begin{quote}
-The photon-induced process, $\gamma\gamma \to \ell \ell$, is simulated at LO using Pythia 8 
+The photon-induced process, $\gamma\gamma \to \ell \bar{\ell}$, is simulated at LO using Pythia 8
 and the MRST2004qed PDF set~\cite{Martin:2004dh}. The expected yield for this process also accounts for 
-NLO QED/EW corrections from references~\cite{Bardin:2012jk,Bondarenko:2013nu}, which decrease the yield by approximately 30\%.
+NLO QED/EW corrections from references~\cite{Bardin:2012jk,Bondarenko:2013nu}, which decrease the yield by approximately \SI{30}{\percent}.
 \end{quote}
 Such a distinction, which is unphysical and incorrect in quantum mechanics, may be somehow justified at LO. Beyond this order, it is simply wrong.
-Indeed, at $\mathcal O(\alpha^3)$, the reaction $q \gamma \to \ell^+ \ell^- q$ becomes possible, which
+Indeed, at $\mathcal O(\alpha^3)$, the reaction $\mathrm{q} \gamma \to \ell \bar{\ell} \mathrm{q}$ becomes possible, which
 includes both kind of topologies discussed above (and needs both in order to yield an IR-finite result), see Fig.~\ref{fig:dy-pi}.
@@
 A second example is related to removing EW effects from data. These can be either the full EW corrections
-or just a part. In either case, a comparison between these data and a NLO-EW accurate simulation aimed at the extraction of some parameter would be meaningless, as some effects included in the latter
+or just a part of them.
+In either case, a comparison between these data and a NLO-EW accurate simulation aimed at the extraction of some parameter would be meaningless, as some effects included in the latter
 have been removed from the former. The typical example relevant for LHC is the deconvolution of effects due to multiple-photon radiation
@@
 to processes such as neutral- or charge-current Drell--Yan, specially when electrons are considered. The problem lies in the fact that
- electrons, and to a lesser extent muons, tend to radiate photons, and such photons are typically not accounted
-for in QCD matrix-elements. Thus, leptons that are measured in the detector are less energetic, and this fact is compensated for
-by inverting the photon shower. The resulting dataset is e.g.\ referred to as \emph{pre-FSR} or \emph{Born-level electrons} (see e.g.\ Ref.~\cite{Aad:2015auj} for
-its definition).
-These datasets are needed for and correctly used in QCD-only PDF determinations, since the EW corrections to some DY observables can be significant, and excluding them would therefore degrade the fit.
+ electrons, and to a lesser extent muons, tend to radiate photons, which are not accounted
+for in QCD-only matrix-elements. Thus, leptons that are measured in the detector are less energetic, and this fact is compensated for
+by inverting a photon shower.
+The resulting dataset is e.g.\ referred to as \emph{pre-FSR} with observables defined in terms of \emph{Born-level electrons} (see e.g.\ Ref.~\cite{Aad:2015auj} for its definition).
+These datasets are needed for and correctly used in QCD-only PDF determinations, since the EW corrections to some DY observables can be significant, and excluding them would therefore degrade the quality of the fit.
 In fits including fixed-order EW corrections the problem with this definition is that the first photon emission is included exactly at the matrix-element level. The inclusion of
@@
 QCD displays a remarkable agreement with another at NLO QCD+EW when the photonic shower is included (see example the behaviour of predictions showered with
-\textsc{Photos}~\cite{Barberio:1990ms,Barberio:1993qi,Golonka:2005pn}in Ref.~\cite{CarloniCalame:2016ouw}). However, this kind of agreement
+\textsc{Photos}~\cite{Barberio:1990ms,Barberio:1993qi,Golonka:2005pn} in Ref.~\cite{CarloniCalame:2016ouw}). However, this kind of agreement
 always comes \emph{a posteriori}, and cannot be ensured in general. A more physical definition would be either the one of bare leptons (the leptons as they emerge after FSR)
@@
 electrons are never measured as bare particles, because of the finite resolution 
-of the electromagnetic calorimeter.
-For what concerns muons, while in principle the concept of a bare muon is physical (\textbf{CS}: cite papers for non-collinear safe observables/subtraction?), it should be kept in
+of the electromagnetic calorimeter. For what concerns muons, while in principle the concept of a bare muon is physical, it should be kept in
 mind that modern, general-purpose codes employed to

### 2020-07-28 paper/sec-pineappl.tex
Add smaller corrections to the PineAPPL section

@@
 With respect to the capabilities of these computer codes, \textsc{PineAPPL} makes it possible for the first time to include also higher-order corrections due to electroweak (EW), and in general mixed QCD--EW, effects.
-Documenting this extension, and how to interface \textsc{PineAPPL} with a general-purpose matrix-element generator, is the main interest of this paper.
+Documenting this extension, and how to interface \textsc{PineAPPL} with a general-purpose matrix-element generator, is of the main interests of this paper.
 
@@
 In fact, \textsc{PineAPPL} allows arbitrary initial-state combinations, e.g.\ leptonic initial states~\cite{Bertone:2015lqa,Buonocore:2020nai}.
-\item The estimate of theory uncertainty via variations of the renormalisation and factorisation scale (the electroweak coupling is assumed to be scale-independent, consistently with the commonest renormalisation schemes).
-%\item Support for all-order predictions coming from a resummation calculation or a photon-/parton-shower, which are important for some observables (see section~\ref{sec:results}),
+\item The estimate of theory uncertainty via variations of the renormalisation and factorisation scale (the electroweak coupling is assumed to be scale-independent, consistently with the most common renormalisation schemes).
 \end{itemize}
@@
 
-If chosen dynamically the Ellis--Sexton scale $Q^2$ depends on the phase space, but we assume the fractions $\xi_\mathrm{R}$ and $\xi_\mathrm{F}$ to be constants of phase space in any case.
-This allows variations around the central scale choice $\xi_\mathrm{R} = \xi_\mathrm{F} = 1$, but not changing the scale arbitrarily.
+The Ellis--Sexton scale $Q^2$, if chosen dynamically, depends on the phase space, but we assume the fractions $\xi_\mathrm{R}$ and $\xi_\mathrm{F}$ to be constants of phase space in any case.
+This allows variations around the central scale choice $\xi_\mathrm{R} = \xi_\mathrm{F} = 1$, but it does not allow changing the scale arbitrarily.
 The terms with powers $m > 0$ and $n > 0$ vanish for the central scale choice and are only required for variations of the factorisation and renormalisation scales.
@@
 This, however, includes the most common choices of the coupling, which are (not necessarily in this order), $\alpha (0)$, $\alpha (M_\mathrm{Z})$, and $\alpha_{G_\mu}$.
-The task that \textsc{PineAPPL} solves can now be described: Approximately reconstruct the functions
+
+The problem that \textsc{PineAPPL} solves can now be described: Approximately reconstruct the functions
 \begin{equation}
@@
 \end{equation}
-given by the MC integrator.
-
-Using eq.~\eqref{eq:expansion} and
+given by the MC integrator. Using eq.~\eqref{eq:expansion} and
 \begin{multline}
@@
 For many processes there is only one LO, but when a process has multiple quark lines, colourless (photons, \dots) and coloured particles (gluons, \ldots) can be exchanged between them, making it possible to have more than one LO.
-An important example at the LHC is di-jet production, which has three different LOs: $\mathcal{O} (\alpha^2)$, $\mathcal{O} (\alphas \alpha)$, and $\mathcal{O} (\alpha^2)$.
+An important example at the LHC is dijet production, which has three different LOs: $\mathcal{O} (\alpha^2)$, $\mathcal{O} (\alphas \alpha)$, and $\mathcal{O} (\alpha^2)$.
 Each LO receives a higher-order correction with an additional power of $\alphas$ or $\alpha$, which in general leads to at least two next-to-leading order (NLO) corrections.
@@
 However, the price one has to pay is the size of the 4-tuples.
-To give a concrete example, NLO QCD+EW Drell--Yan lepton-pair production (see section~\ref{sec:pineappl-example} and section~\ref{sec:atlas-high-mass-dy}) needs \SI{159}{\giga\byte} of storage for a target precision of \SI{1}{\percent} of the integrated cross section with this precision.
+To give a concrete example, NLO QCD+EW Drell--Yan lepton-pair production (see section~\ref{sec:pineappl-example} and section~\ref{sec:atlas-high-mass-dy}) needs \SI{159}{\giga\byte} of storage for a target precision of \SI{1}{\percent} of the integrated cross section.
 While this is an acceptable size, increasing the precision by an order of magnitude would require roughly 100 times the size, due to the Monte Carlo convergence that goes as $1/\sqrt{N}$ with $N$ being the number of 4-tuples.

### 2020-07-29 paper/sec-results.tex
Something mor eon Sect.3

@@
-\section{Results}
+\section{PineAPPL at work: generation and validation of interpolation grids}
 \label{sec:results}
@@
 
-Given one of the measurements discussed in
+For each of the measurements discussed in
 Sect.~\ref{subsec:processes_and_measurements}, we compute the expectation
-value of the corresponding observable in for each bin in two different ways:
-directly, by means of {\sc MG5\_aMC}, and a posteriori, by convolving the
+value of the corresponding observable for each kinematic bin in two different
+ways: directly, by means of {\sc MG5\_aMC}, and a posteriori, by convolving the
 fast interpolation grid produced by {\sc PineAPPL} with the PDF set specified
-in Sect.~\ref{subsec:computational_settings}. In order to validate the
+in Sect.~\ref{subsec:computational_settings}. In the following, we will refer
+to the the first result as the {\sc MC} result, and to the second as the
+{\sc PineAPPL} result. We repeat the computation for theories accurate to NLO
+QCD and to NLO QCD+EW, respectively. In each case, we determine the PDF
+uncertainty (coming from the PDF ensemble), the scale uncertainty (coming from
+variations of the factorisation and renormalisation scales), and the Monte
+Carlo uncertainty (coming from the finite number of events generated). In this
+last respect, we consider by default high-statistics computations, whereby we
+require a relative Monte Carlo precision of a fraction of permille. This choice
+ensures that the statistical uncertainty of the computation is negligible
+in comparison to the PDF and scale uncertainties, as we will explicitly
+demonstrate.
+%Add here a sentence on a low-statistics run?
+
+Our goal is twofold. On the one hand, we aim to validate the fast interpolation
+grids generated with {\sc PineAPPL}: to this purpose we shall verify that the
+MC and the {\sc PineAPPL} results are identical up to numerical inaccuracies
+due to the grid interpolation. This equivalence must hold for any choice of
+renormalisation and factorisation scale. On the other hand, we aim to study
+the size of the EW corrections, in particular with respect to the kinematics of
+each process, and to an array of relative uncertainties coming from the PDFs,
+the scale variations, and the experimental data.
 

### 2020-07-29 paper/app-pineappl.tex
Fix missing reference

@@
 \end{lstlisting}
-As an example we show the grid produced for the ATLAS DY high-mass lepton-pair production (from section~\ref{sec:atlas-high-mass-dy}).
+As an example we show the grid produced for the ATLAS DY high-mass lepton-pair production (from section~\ref{subsec:numerical_results}).
 The output shows all 13 bins with lower (\texttt{xmin}) and upper limit (\texttt{xmax}) of the invariant mass $M_{\ell \bar{\ell}}$ of the lepton pair, with the differential cross section $\mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}}$ (\texttt{diff}), integrated cross section $(M_{\ell \bar{\ell}}^\mathrm{max} - M_{\ell \bar{\ell}}^\mathrm{min}) \mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}}$ (\texttt{integ}), together with the perturbative uncertainty estimated from a 7-point scale variation (\texttt{neg unc} and \texttt{pos unc}).
@@
 
-The following run card was used to produce the results shown in section~\ref{sec:atlas-high-mass-dy}.
+The following run card was used to produce the results shown in section~\ref{subsec:numerical_results}.
 The only difference to a normal \textsc{mg5\_aMC@NLO} run is the switch \texttt{set iappl 1}, which enables filling a \textsc{PineAPPL} grid.

### 2020-07-29 paper/sec-pineappl.tex
Fix missing reference

@@
 However, the price one has to pay is the size of the 4-tuples.
-To give a concrete example, NLO QCD+EW Drell--Yan lepton-pair production (see section~\ref{sec:pineappl-example} and section~\ref{sec:atlas-high-mass-dy}) needs \SI{159}{\giga\byte} of storage for a target precision of \SI{1}{\percent} of the integrated cross section.
+To give a concrete example, NLO QCD+EW Drell--Yan lepton-pair production (see section~\ref{sec:pineappl-example} and section~\ref{subsec:numerical_results}) needs \SI{159}{\giga\byte} of storage for a target precision of \SI{1}{\percent} of the integrated cross section.
 While this is an acceptable size, increasing the precision by an order of magnitude would require roughly 100 times the size, due to the Monte Carlo convergence that goes as $1/\sqrt{N}$ with $N$ being the number of 4-tuples.

### 2020-07-29 paper/sec-conclusion.tex
Intro - first draft
Add first draft of the conclusion

@@
-\section{Outlook}
+\section{Conclusions and Outlook}
+\label{sec:conclusion}
 
-ALL
+We presented a new tool called \textsc{PineAPPL}, which stores perturbative calculations calculated from an external Monte Carlo in a PDF-independent way using interpolation grids.
+This offers the advantage of fast a-posteriori convolutions with PDFs, for example to study the uncertainties coming from different PDF sets and/or the strong coupling constant $\alphas$.
+Another application that we focused on is in PDF fitting, where the interpolation grids constitute the theoretical input.
 
-\cite{Carli:2010rw}
-\cite{Bertone:2014zva}
+A distinguishing feature of \textsc{PineAPPL} is the support for arbitrary coupling orders not only in the strong, but also in the electroweak coupling.
+This enables us to generate, for the first time, NLO EW and NLO mixed QCD--EW interpolation grids.
+Using \textsc{mg5\_aMC@NLO} we calculated and showcased the impact of these corrections for important PDF processes for specific analyses from ATLAS and CMS: Drell--Yan lepton-pair production, top-pair production, and Z-boson production with non-zero transverse momentum.
+
+Finally, we discussed the issue of subtracting EW corrections in experimental data, which becomes an important consideration when combining the interpolations grids with the corresponding experimental data in a PDF fit including EW and mixed QCD--EW corrections.
+
+Having developed and thoroughly tested \textsc{PineAPPL} with the Monte Carlo generator \textsc{mg5\_aMC@NLO}, all technical requirements are fulfilled for producing the first global PDF fit including EW and mixed QCD--EW corrections.
+This has at least two advantages: in PDF fits phase-space regions are usually discarded if they exhibited large EW corrections; including them enables one to enlarge the number of data points of a fit and therefore enlarging the PDFs interpolation region.
+Secondly, this allows to use experimental data that, in some cases, is closer to the actual measurements and does not contain subtractions from theoretical calculation such as \textsc{Photos}.

### 2020-07-29 paper/sec-results.tex
Corrected values of the physical parameters

@@
 M_\mathrm{W} = \SI{80}{\giga\electronvolt} \text{,} \quad 
-M_\mathrm{Z} = \SI{90}{\giga\electronvolt} \text{,} \quad 
-m_\mathrm{t} = \SI{170}{\giga\electronvolt} \text{,} \quad
-\Gamma_\mathrm{W} = \SI{2}{\giga\electronvolt} \text{,} \quad
-\Gamma_\mathrm{Z} = \SI{2}{\giga\electronvolt} \text{,} 
+M_\mathrm{Z} = \SI{91.176}{\giga\electronvolt} \text{,} \quad 
+m_\mathrm{t} = \SI{172.5}{\giga\electronvolt} \text{,} \quad
+\Gamma_\mathrm{W} = \SI{2.50}{\giga\electronvolt} \text{,} \quad
+\Gamma_\mathrm{Z} = \SI{2.09}{\giga\electronvolt} \text{,} 
 \label{eq:parameters}
@@
 the size of the EW corrections, in particular with respect to the kinematics of
-each process, and to an array of relative uncertainties coming from the PDFs,
+each process, and to an array of relative uncertainties arising from the PDFs,
 the scale variations, and the experimental data.

### 2020-07-29 paper/sec-conclusion.tex
Add corrections to the conclusion section

@@
 
-We presented a new tool called \textsc{PineAPPL}, which stores perturbative calculations calculated from an external Monte Carlo in a PDF-independent way using interpolation grids.
+We presented a new tool called \textsc{PineAPPL}, which stores perturbative calculations from an external Monte Carlo in a PDF-independent way using interpolation grids.
 This offers the advantage of fast a-posteriori convolutions with PDFs, for example to study the uncertainties coming from different PDF sets and/or the strong coupling constant $\alphas$.
-Another application that we focused on is in PDF fitting, where the interpolation grids constitute the theoretical input.
+Another application that we focused on is PDF fitting, where the interpolation grids constitute the theoretical input.
+We tested \textsc{PineAPPL} together with \textsc{mg5\_aMC@NLO} and found a precision of \numrange{e-4}{e-5} relative to the MC result, which is more than enough for the applications described before.
+Although we used \textsc{mg5\_aMC@NLO}, we note that \textsc{PineAPPL} is not tied in any way to a specific MC and can be easily interfaced with any generator.
 
@@
 
-Having developed and thoroughly tested \textsc{PineAPPL} with the Monte Carlo generator \textsc{mg5\_aMC@NLO}, all technical requirements are fulfilled for producing the first global PDF fit including EW and mixed QCD--EW corrections.
-This has at least two advantages: in PDF fits phase-space regions are usually discarded if they exhibited large EW corrections; including them enables one to enlarge the number of data points of a fit and therefore enlarging the PDFs interpolation region.
-Secondly, this allows to use experimental data that, in some cases, is closer to the actual measurements and does not contain subtractions from theoretical calculation such as \textsc{Photos}.
+Having developed and thoroughly tested \textsc{PineAPPL}, all technical requirements are fulfilled for producing the first global PDF fit including EW and mixed QCD--EW corrections.
+This will have at least two advantages: in PDF fits phase-space regions are usually cut away if they exhibit large EW corrections; including them therefore increases the number of data points in a fit and therefore indirectly enlarges a PDF set's interpolation region.
+Secondly, this makes it possible to use experimental data that are closer to the actual measurement, without the need to compensate for missing EW corrections.

### 2020-07-30 paper/sec-results.tex
added references for ew processes

@@
 although with appropriate kinematic cuts that remove the bins at the largest
-values of invariant mass, where EW corrections become sizeable.
+values of invariant mass, where EW corrections become sizeable. EW corrections for this process
+have been computed in Refs.~\cite{Baur:2001ze,Dittmaier:2009cr}.
 
@@
 pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
-in the NNPDF3.1 analysis~\cite{Ball:2017nwa}.
+in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. EW corrections for this process
+have been computed in Refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}.
 
@@
 corrections) in the NNDPF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
-the CT18 PDF set~\cite{Hou:2019efy}.
+the CT18 PDF set~\cite{Hou:2019efy}. EW corrections for this process
+have been computed in Refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
 

### 2020-07-30 paper/sec-results.tex
Sect 3

--- 2020-07-29 paper/sec-results.tex
@@
 consistently defined photon PDF, namely
-{\tt NNPDF31\_as\_0118\_luxqed}~\cite{Bertone:2017bme}. We evaluate the PDF
+{\tt NNPDF31\_nlo\_as\_0118\_luxqed}~\cite{Bertone:2017bme}. We evaluate the PDF
 uncertainty associated to the theoretical predictions a posteriori, that is,
@@
 are varied down to a factor $1/2$ and up to a factor $2$, and an envelope
-from the nine-point scale variations is constructed.
+from the seven-point scale variations is constructed.
 
@@
 last respect, we consider by default high-statistics computations, whereby we
-require a relative Monte Carlo precision of a fraction of permille. This choice
-ensures that the statistical uncertainty of the computation is negligible
-in comparison to the PDF and scale uncertainties, as we will explicitly
-demonstrate.
-%Add here a sentence on a low-statistics run?
+require a relative Monte Carlo precision of a fraction of permille. While
+this choice does not affect the validation of the {\sc PineAPPL} result against
+the {\sc MC} result, it ensures that the statistical uncertainty of the
+computation remains negligible in comparison to the PDF and scale uncertainties,
+as we will explicitly demonstrate. This is a desirable feature to correctly
+interpret the size of the theoretical corrections.
 
-Our goal is twofold. On the one hand, we aim to validate the fast interpolation
-grids generated with {\sc PineAPPL}: to this purpose we shall verify that the
-MC and the {\sc PineAPPL} results are identical up to numerical inaccuracies
-due to the grid interpolation. This equivalence must hold for any choice of
-renormalisation and factorisation scale. On the other hand, we aim to study
-the size of the EW corrections, in particular with respect to the kinematics of
-each process, and to an array of relative uncertainties arising from the PDFs,
-the scale variations, and the experimental data.
+Our goal is indeed twofold. On the one hand, we aim to validate the
+interpolation grids generated with {\sc PineAPPL}: to this purpose we shall
+verify that the MC and the {\sc PineAPPL} results are identical up to numerical
+inaccuracies due to the grid interpolation. This equivalence must hold for any
+choice of renormalisation and factorisation scale. On the other hand, we aim to
+study the size of the EW corrections, in particular with respect to the
+kinematics of each process, and to three kinds of uncertainties: the PDF
+uncertainty, the scale variation uncertainty, and the uncertainty of the
+experimental data.
+
+We present these comparisons in
+Figs.~\ref{fig:atlaszhighmass49fb}-\ref{fig:cmsZ13TeV} for each of the processes
+and data sets outlined in Sect.~\ref{subsec:processes_and_measurements}.
+The format of the plots is the same across all figures. The first panel
+displays the relative difference (in permille) between the {\sc PineAPPL} and
+the {\sc MC} results for the central, upper and lower scale choices, for
+theories accurate to both NLO QCD and NLO QCD+EW. The following three panels
+present the theoretical predictions, accurate to either NLO QCD or NLO QCD+EW,
+always normalised to the former: the second displays the PDF uncertainty, the
+third the scale uncertainty and the fourth the Monte Carlo statistical
+uncertainty. The relative uncertainty of the experimental data points is also
+shown for comparison. We shall now discuss the results for each
+process and data set in turn.
 
@@
     \caption{PineAPPL comparison for ATLAS top pair.}
-    \label{fig:cmsdy2d11_bins56}
+    \label{fig:atlastop}
 \end{figure}
@@
     \caption{PineAPPL comparison for CMS $Z$ $p_T$ distribution.}
-    \label{fig:cmsdy2d11_bins56}
+    \label{fig:cmsZ13TeV}
 \end{figure}
@@
 \noindent
-TODO for each of the following subsections:
+
+TODO for each process:
 \begin{itemize}
@@
 \end{itemize}
-
-%ERN 7 Apr: there is consensus on the fact that we should present results for the
-%following data sets:
-%\begin{itemize}
-%\item ATLAS high mass DY distributions, 7 TeV~\cite{Aad:2013iua} (CS);
-%\item CMS 2D DY distributions, 7 TeV~\cite{Chatrchyan:2013tia} (CS);
-%\item ATLAS top pair differential distributions ($m_{t\bar{t}}$ and $p_T^t$),
-%8 TeV~\cite{Aad:2015mbv} (ERN);
-%\item CMS $Z$ $pT$ distributions, 13 TeV~\cite{Sirunyan:2019bzr} (ERN).
-%\end{itemize}
-%
-%We agree not to display any LHCb measurement, given that they won't add
-%further value to our discussion.
-%Note added: we might also want to have a look at the ATLAS 2D and 3D DY
-%distributions, 8 TeV~\cite{Aad:2016zzw,Aaboud:2017ffb}, if time allows
-%us to do so.
-%
-%CS 25 Jun: We've agreed to show basically two types of plots: 1) technical plots showing the good agreement between the MC compared to the results from the grids, and 2) phenomenological results showing larger EW corrections, for example.
-%In the aMCfast paper both is shown in single plot, but since we have more to show, I suggest the following: for the technical plots we show a 2x2 matrix of plots, each showing the difference of the grid result compared to the MC result, in the following fashion:
-%\begin{itemize}
-%\item NLO QCD with low statistics,
-%\item NLO QCD+EW with low statistics,
-%\item NLO QCD with high statistics, and finally
-%\item NLO QCD+EW with high statistics,
-%\end{itemize}
-%each showing a few scale variations.
-%These plots then clearly show that no matter what corrections you choose, no matter the statistics, and no matter the scale variation, the agreement is always excellent.
-%In any case I would like to avoid showing a plot with absolute numbers and low statistics, which looks a bit ridiculous in my opinion (look at figure 1, left side, top plot of the aMCfast paper).
-%
-%Finally we can show another series of plots, which in my opinion should be very similar to the usual pheno paper plots: absolute numbers with a scale variation band, maybe a few corrections shown in the same plot and then in the bottom relative corrections.

### 2020-07-30 paper/sec-results.tex
Nine point scale variation

@@
 are varied down to a factor $1/2$ and up to a factor $2$, and an envelope
-from the seven-point scale variations is constructed.
+from the nine-point scale variations is constructed.
 

### 2020-07-30 paper/sec-results.tex
Restructuring sec 3 a little

--- 2020-07-30 paper/sec-results.tex
@@
 pair production, and Z-boson (lepton-pair) production with non-zero transverse
-momentum at the LHC. For each of these processes, we consider the measurements
+momentum in proton-proton collisions. For each of these processes, we consider the measurements
 described below.
@@
 although with appropriate kinematic cuts that remove the bins at the largest
-values of invariant mass, where EW corrections become sizeable.
+values of invariant mass, where EW corrections become sizeable. As explained in
+Sect.~\ref{sec:pineappl-example}, should PI contributions be taken into account,
+the process has a single LO, $\mathcal{O}(\alpha_s^0\alpha^2)$; at NLO, the
+QCD contribution is $\mathcal{O}(\alpha_s\alpha^2)$, while the EW contribution
+is $\mathcal{O}(\alpha_s^0\alpha^3)$. The latter is not included in the NLO
+QCD computation, but it is in the NLO QCD+EW computation. Mixed QCD-EW
+corrections occur only at NNLO, and are therefore not considered here.
+The process receives contributions from 12 (34) parton luminosities at NLO QCD
+(NLO QCD+EW), mainly from $q\bar q$ scattering. EW corrections for this process
+were computed in Refs.~\cite{Baur:2001ze,Dittmaier:2009cr}.
 
@@
 pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
-in the NNPDF3.1 analysis~\cite{Ball:2017nwa}.
+in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. EW corrections for this process
+were computed in Refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}.
 
@@
 from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
-experiments at a centre-of-mass energy of 8~TeV were partly included (upon the
+experiments at a centre-of-mass energy of 8~TeV, were partly included (upon
 selection of an appropriate kinematic cut that excluded bins with large EW
 corrections) in the NNDPF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
-the CT18 PDF set~\cite{Hou:2019efy}.
+the CT18 PDF set~\cite{Hou:2019efy}. EW corrections for this process
+were computed in Refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
 
@@
 variations. As is customary, the factorisation and renormalisation scales
-are varied down to a factor $1/2$ and up to a factor $2$, and an envelope
-from the seven-point scale variations is constructed.
+are varied down to a factor $1/2$ and up to a factor $2$, and the envelope
+from the nine-point scale variations is constructed.
 
@@
 require $p_T^\ell>25$~GeV, $|\eta_\ell|<2.4$,
-$M_Z$-15~GeV$<M_{\ell\bar\ell}<M_Z$+20~GeV,
+$M_Z-15$~GeV$<M_{\ell\bar\ell}<M_Z+20$~GeV,
 $|\eta_{\ell\bar\ell}|<2.4$ and 20~GeV$<p_T^{\ell\bar\ell}<1500$~GeV for the
@@
 in Sect.~\ref{subsec:computational_settings}. In the following, we will refer
-to the the first result as the {\sc MC} result, and to the second as the
+to the first result as the {\sc MC} result, and to the second as the
 {\sc PineAPPL} result. We repeat the computation for theories accurate to NLO
@@
 present the theoretical predictions, accurate to either NLO QCD or NLO QCD+EW,
-always normalised to the former: the second displays the PDF uncertainty, the
-third the scale uncertainty and the fourth the Monte Carlo statistical
-uncertainty. The relative uncertainty of the experimental data points is also
-shown for comparison. We shall now discuss the results for each
-process and data set in turn.
+always normalised to the former; on top of the theoretical predictions, the
+PDF uncertainty, the scale uncertainty and the Monte Carlo uncertainty are
+displayed in turn. The relative uncertainty of the experimental data is
+also shown for comparison. We shall now discuss the results for each
+process and data set.
 
 \paragraph{DY lepton pair production.}
+
+We first consider the single-differential measurement at a high lepton pair
+invariant mass performed by the ATLAS experiment at 7 TeV. 
+From Fig.~\ref{fig:atlaszhighmass49fb} we immediately
+observe that the validation of the \textsc{PineAPPL} result against the MC
+result is successful. The relative difference between the two is of the order
+$0.1\tcperthousand$ at most, with negligible fluctuations across different
+invariant mass bins. The same remains true for theories accurate to both NLO
+QCD or NLO QCD+EW, and irrespective of the scale choice.
+
+%-------------------------------------------------------------------------------
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB}
+    \caption{Validation and test of the \textsc{PineAPPL} grid for the ATLAS
+      high-mass DY lepton pair measurement in the high-mass region at
+      a centre-of-mass energy of 7 TeV~\cite{Aad:2013iua}. The first panel
+      displays the relative difference (in permille) between the {\sc PineAPPL}
+      and the {\sc MC} results for the central, upper and lower scale choices,
+      for theories accurate to both NLO QCD and NLO QCD+EW. The second, third
+      and fourth panels present the theoretical predictions, accurate to either
+      NLO QCD or NLO QCD+EW, always normalised to the former; on top of the
+      theoretical predictions, the PDF uncertainty, the scale uncertainty and
+      the Monte Carlo uncertainty are displayed in turn. The relative
+      uncertainty of the experimental data is also shown for comparison.}
+    \label{fig:atlaszhighmass49fb}
+\end{figure}
+%-------------------------------------------------------------------------------
 
@@
 \paragraph{$Z$-boson production with non-zero transverse momentum.}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB}
-    \caption{PineAPPL comparison for ATLAS high-mass Drell--Yan at $\sqrt{s}=7$ TeV.}
-    \label{fig:atlaszhighmass49fb}
-\end{figure}
 

### 2020-07-30 paper/paper.tex
Restructuring sec 3 a little
Remove `placeins` package

@@
 \usepackage[percent]{overpic}
-\usepackage[section]{placeins}
+\usepackage{mathcomp}
 
@@
 
-\title{PineAPPL: EW and mixed QCD--EW corrections for PDF fits}
+\title{PineAPPL:\\ EW and mixed QCD--EW corrections for PDF fits}
 
 \author[a]{S. Carrazza,}
-\author[b]{E. Nocera,}
+\author[b]{E.R. Nocera,}
 \author[a]{C. Schwan}
@@
 
-\abstract{We introduce {\sc PineAPPL}, a computer library that makes it possible to produce fast interpolation 
+\abstract{We introduce \textsc{PineAPPL}, a computer library that makes it possible to produce fast-interpolation 
 grids for fitting parton distribution functions (PDFs)
 including corrections of strong and electroweak origin. After presenting
-the features and performances of such a code, we show how to interface {\sc PineAPPL} with general-purpose
+the features and performance of such a code, we show how to interface \textsc{PineAPPL} with general-purpose
 softwares that allow the user to compute such corrections, providing an explicit example with
-{\sc MadGraph5\_aMC@NLO}. We showcase some phenomenological result focusing on processes and observables
+\textsc{MadGraph5\_aMC@NLO}. We showcase some phenomenological result focusing on processes and observables
 relevant for PDF fits, and 
@@
 \input{app-pineappl}
+\input{app-lumis}
+\input{app-addmaterial}
 

### 2020-07-30 paper/sec-results.tex
Sec.3

@@
 Sect.~\ref{sec:pineappl-example}, should PI contributions be taken into account,
-the process has a single LO, $\mathcal{O}(\alpha_s^0\alpha^2)$; at NLO, the
+the process has a single LO, $\mathcal{O}(\alpha^2)$; at NLO, the
 QCD contribution is $\mathcal{O}(\alpha_s\alpha^2)$, while the EW contribution
-is $\mathcal{O}(\alpha_s^0\alpha^3)$. The latter is not included in the NLO
+is $\mathcal{O}(\alpha^3)$. The latter is not included in the NLO
 QCD computation, but it is in the NLO QCD+EW computation. Mixed QCD-EW
 corrections occur only at NNLO, and are therefore not considered here.
-The process receives contributions from 12 (34) parton luminosities at NLO QCD
-(NLO QCD+EW), mainly from $q\bar q$ scattering. EW corrections for this process
-were computed in Refs.~\cite{Baur:2001ze,Dittmaier:2009cr}.
+EW corrections for this process were computed in
+Refs.~\cite{Baur:2001ze,Dittmaier:2009cr}. The process receives contributions
+from 12 (34) parton luminosities at NLO QCD (NLO QCD+EW).
 
@@
 pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
-in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. EW corrections for this process
+in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. The process receives 
+pure QCD contributions at LO, $\mathcal{O}(\alpha_s^2)$, and
+at NLO, $\mathcal{O}(\alpha_s^2)$. They are included in the NLO QCD
+computation. The NLO QCD+EW computation includes the LO contribution
+$\mathcal{O}(\alpha_s^1\alpha^1)$ and the NLO contributions
+$\mathcal{O}(\alpha_s^2\alpha)$ and $\mathcal{O}(\alpha_s\alpha^2)$.
+We do not consider the LO PI contribution $\mathcal{O}(\alpha^2)$ and the
+corresponding higher-order EW correction. EW corrections for this process
 were computed in Refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}.
+The process receives contributions from
+6 (36) parton luminositites at NLO QCD (NLO QCD+EW), mainly from $gg$ fusion.
 

### 2020-07-30 paper/sec-results.tex
Typos

@@
 pure QCD contributions at LO, $\mathcal{O}(\alpha_s^2)$, and
-at NLO, $\mathcal{O}(\alpha_s^2)$. They are included in the NLO QCD
+at NLO, $\mathcal{O}(\alpha_s^3)$. They are included in the NLO QCD
 computation. The NLO QCD+EW computation includes the LO contribution
-$\mathcal{O}(\alpha_s^1\alpha^1)$ and the NLO contributions
+$\mathcal{O}(\alpha_s\alpha)$ and the NLO contributions
 $\mathcal{O}(\alpha_s^2\alpha)$ and $\mathcal{O}(\alpha_s\alpha^2)$.

### 2020-07-31 paper/app-addmaterial.tex
MOre on Sect. 3

--- 2020-07-30 paper/sec-results.tex
@@
-\section{PineAPPL at work: generation and validation of interpolation grids}
-\label{sec:results}
-
-In this section we demonstrate the capabilities of \textsc{PineAPPL} by
-computing fast interpolation grids, accurate to NLO QCD and NLO QCD+EW,
-for a representative set of processes in which EW corrections are expected 
-to be sizeable. In order to consider some realistic kinematics for these
-processes, we resort to measurements commonly devised for inclusion in PDF
-fits. Our aim is twofold. First, we want to validate the results
-obtained with \textsc{PineAPPL}; second, we want to assess the
-impact of the EW corrections for usual experimental setups. We describe, first,
-the processes and measurements that we consider, then the computational
-settings that we adopt, and finally the results that we obtain.
-
-\subsection{Processes and measurements}
-\label{subsec:processes_and_measurements}
-
-We focus on the following three processes: DY lepton-pair production, top-quark
-pair production, and Z-boson (lepton-pair) production with non-zero transverse
-momentum in proton-proton collisions. For each of these processes, we consider the measurements
-described below.
-
-\paragraph{DY lepton pair production.}
-We select the distribution, single-differential in the invariant mass of the
-lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of
-mass energy of 7~TeV in the high-mass region
-($M_{\ell\bar\ell}>116$~GeV)~\cite{Aad:2013iua}.
-We also select the distribution, double-differential in the rapidity and in
-the invariant mass of the lepton pair, $y_{\ell\bar\ell}$ and $M_{\ell\bar\ell}$,
-measured by the CMS experiment at a centre-of-mass energy of
-7~TeV~\cite{Chatrchyan:2013tia}.
-These measurements are currently included as standard in the
-NNPDF3.1~\cite{Ball:2017nwa} and MMHT2014~\cite{Harland-Lang:2014zoa} PDF sets,
-although with appropriate kinematic cuts that remove the bins at the largest
-values of invariant mass, where EW corrections become sizeable. As explained in
-Sect.~\ref{sec:pineappl-example}, should PI contributions be taken into account,
-the process has a single LO, $\mathcal{O}(\alpha_s^0\alpha^2)$; at NLO, the
-QCD contribution is $\mathcal{O}(\alpha_s\alpha^2)$, while the EW contribution
-is $\mathcal{O}(\alpha_s^0\alpha^3)$. The latter is not included in the NLO
-QCD computation, but it is in the NLO QCD+EW computation. Mixed QCD-EW
-corrections occur only at NNLO, and are therefore not considered here.
-The process receives contributions from 12 (34) parton luminosities at NLO QCD
-(NLO QCD+EW), mainly from $q\bar q$ scattering. EW corrections for this process
-were computed in Refs.~\cite{Baur:2001ze,Dittmaier:2009cr}.
-
-\paragraph{Top-quark pair production.}
-We select the distributions, single-differential in either the transverse
-momentum of the top quark, $p_T^t$, or the invariant mass of the top-quark
-pair, $m_{t\bar t}$, measured by the ATLAS and CMS experiments at a centre-of-mass
-energy of 8~TeV~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
-been extensively studied in the context of PDF fits in
-Refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml}, and
-included by default in the CT18~\cite{Hou:2019efy} analysis.
-Because EW corrections are significantly smaller for distributions differential
-in the rapidity of either the top quark or the top-quark
-pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
-in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. EW corrections for this process
-were computed in Refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}.
-
-\paragraph{$Z$-boson production with non-zero transverse momentum.}
-We select the distribution, single-differential in the transverse momentum of
-the $Z$ boson, $p_T^Z$, measured by the CMS experiment at a centre-of-mass
-energy of 13~TeV~\cite{Sirunyan:2019bzr}. So far, this measurement has not been
-included in any PDF determination. Because it has sub-percent uncertainties,
-EW corrections are expected to be essential in order to achieve a good
-description of it, and to constrain accurately the PDFs. Analogous measurements,
-from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
-experiments at a centre-of-mass energy of 8~TeV, were partly included (upon
-selection of an appropriate kinematic cut that excluded bins with large EW
-corrections) in the NNDPF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
-the CT18 PDF set~\cite{Hou:2019efy}. EW corrections for this process
-were computed in Refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
-
-\subsection{Computational settings}
-\label{subsec:computational_settings}
-
-We generate each process by means of the Universal FeynRules Output
-(UFO)~\cite{Degrande:2011ua} model {\tt loop\_qcd\_qed\_sm\_Gmu},
-included as standard in {\sc MG5\_aMC}. It contains the UV and $R_2$
-counterterms relevant to NLO QCD and EW corrections, the latter in the
-$\overline{G}_\mu$ scheme. The model features five massless quark flavours,
-sets the CKM matrix equal to the identity, and is compatible with the usage of
-the complex mass (CM) scheme for all massive particles, see
-Ref.~\cite{Frederix:2018nkq} for details. We use this scheme
-for all processes that do not involve stable top quarks in the final state.
-The photon is always considered as part of the proton in the initial state and
-of any hadronic jet produced in the final state: PI effects and EW corrections
-are therefore treated on the same footing. We use a PDF set that contains a
-consistently defined photon PDF, namely
-{\tt NNPDF31\_nlo\_as\_0118\_luxqed}~\cite{Bertone:2017bme}. We evaluate the PDF
-uncertainty associated to the theoretical predictions a posteriori, that is,
-we convolve the fast interpolation grid generated with {\sc PineAPPL} with
-each member in the PDF set, and we compute the associated standard deviation.
-
-The central values of the renormalisation and factorisation scales, $\mu_R$ and
-$\mu_F$, are chosen, for each process, as follows. In the case of DY lepton pair
-production, we use the fixed scale $\mu_R=\mu_F=M_Z$, where $M_Z$ is the mass
-of the $Z$-boson, for the ATLAS measurement, and the scale
-$\mu_R=\mu_F=M_{\ell\bar\ell}$, where $M_{\ell\bar\ell}$ is the central value of each
-invariant mass bin, for the CMS measurement.
-In the case of top-quark pair production, we use the dynamic scales
-$\mu_R=\mu_F=\sqrt{m_t^2+(p_T^t)^2}{\Big /}2$ for the distribution differential
-in the transverse momentum of the top quark, and $\mu_R=\mu_F=H_T/4$ for the
-distribution differential in the invariant mass of the top-quark pair, where
-$H_T=\sqrt{m_t^2+(p_T^t)^2}+\sqrt{m_t^2+(p_T^{\bar{t}})}$, with $m_t$,
-$p_T^t$ and $p_T^{\bar t}$ the mass of the top quark and the transverse momenta
-of the top and antitop quarks, respectively. These choices were demonstrated
-to maximise the convergence of the perturbative expansion~\cite{Czakon:2016dgf}.
-In the case of $Z$-boson production with non-zero transverse momentum, we use
-$\mu_R=\mu_F=M_Z$. In order to estimate the missing higher-order uncertainty,
-we allow the events to be reweighted in the Monte Carlo generation upon scale
-variations. As is customary, the factorisation and renormalisation scales
-are varied down to a factor $1/2$ and up to a factor $2$, and the envelope
-from the nine-point scale variations is constructed.
-
-The values of the relevant physical parameters are chosen as
-\begin{equation}
-%\begin{aligned}
-M_\mathrm{W} = \SI{80}{\giga\electronvolt} \text{,} \quad 
-M_\mathrm{Z} = \SI{91.176}{\giga\electronvolt} \text{,} \quad 
-m_\mathrm{t} = \SI{172.5}{\giga\electronvolt} \text{,} \quad
-\Gamma_\mathrm{W} = \SI{2.50}{\giga\electronvolt} \text{,} \quad
-\Gamma_\mathrm{Z} = \SI{2.09}{\giga\electronvolt} \text{,} 
-\label{eq:parameters}
-%\end{aligned}
-\end{equation}
-where $M_W$, $M_Z$ and $m_t$ are the values of the $W$-boson, $Z$-boson and
-top quark masses, respectively, and $\Gamma_W$ and $\Gamma_Z$ are the width of
-the $W$-boson and of the $Z$-boson, respectively. The value of the strong
-coupling is chosen consistently with the PDF set, $\alpha_s(M_Z)=0.118$.
-
-Finally, we implement the kinematic cuts specified in the corresponding
-experimental analyses. In the case of high-mass DY lepton pair
-production at 7~TeV measured by ATLAS, we require $p_T^\ell>25$~GeV,
-$|\eta_\ell|<2.5$ and 116~GeV$<M_{\ell\bar\ell}<$ 1500~GeV for the transverse
-momentum and the rapidity of each lepton and for the invariant mass of the
-lepton pair, respectively. In the case of the DY lepton-pair production at
-7~TeV measured by CMS, we require $p_T^{\ell_1}>14$~GeV, $p_T^{\ell_2}>9$~GeV,
-$|\eta_\ell|<2.4$, $|\eta_{\ell\bar\ell}|<2.4$ and 20~GeV$<M_{\ell\bar\ell}<$ 1500~GeV
-for the transverse momentum and the rapidity of each lepton, and for the
-rapidity and the invariant mass of the lepton pair. In the case of $Z$-boson
-production with non-zero transverse momentum at 13~TeV measured by CMS, we
-require $p_T^\ell>25$~GeV, $|\eta_\ell|<2.4$,
-$M_Z-15$~GeV$<M_{\ell\bar\ell}<M_Z+20$~GeV,
-$|\eta_{\ell\bar\ell}|<2.4$ and 20~GeV$<p_T^{\ell\bar\ell}<1500$~GeV for the
-transverse momentum and rapidity of each lepton, and for the invariant mass,
-rapidity and transverse momentum of the lepton pair.
-
-\subsection{Numerical results}
-\label{subsec:numerical_results}
-
-For each of the measurements discussed in
-Sect.~\ref{subsec:processes_and_measurements}, we compute the expectation
-value of the corresponding observable for each kinematic bin in two different
-ways: directly, by means of {\sc MG5\_aMC}, and a posteriori, by convolving the
-fast interpolation grid produced by {\sc PineAPPL} with the PDF set specified
-in Sect.~\ref{subsec:computational_settings}. In the following, we will refer
-to the first result as the {\sc MC} result, and to the second as the
-{\sc PineAPPL} result. We repeat the computation for theories accurate to NLO
-QCD and to NLO QCD+EW, respectively. In each case, we determine the PDF
-uncertainty (coming from the PDF ensemble), the scale uncertainty (coming from
-variations of the factorisation and renormalisation scales), and the Monte
-Carlo uncertainty (coming from the finite number of events generated). In this
-last respect, we consider by default high-statistics computations, whereby we
-require a relative Monte Carlo precision of a fraction of permille. While
-this choice does not affect the validation of the {\sc PineAPPL} result against
-the {\sc MC} result, it ensures that the statistical uncertainty of the
-computation remains negligible in comparison to the PDF and scale uncertainties,
-as we will explicitly demonstrate. This is a desirable feature to correctly
-interpret the size of the theoretical corrections.
-
-Our goal is indeed twofold. On the one hand, we aim to validate the
-interpolation grids generated with {\sc PineAPPL}: to this purpose we shall
-verify that the MC and the {\sc PineAPPL} results are identical up to numerical
-inaccuracies due to the grid interpolation. This equivalence must hold for any
-choice of renormalisation and factorisation scale. On the other hand, we aim to
-study the size of the EW corrections, in particular with respect to the
-kinematics of each process, and to three kinds of uncertainties: the PDF
-uncertainty, the scale variation uncertainty, and the uncertainty of the
-experimental data.
-
-We present these comparisons in
-Figs.~\ref{fig:atlaszhighmass49fb}-\ref{fig:cmsZ13TeV} for each of the processes
-and data sets outlined in Sect.~\ref{subsec:processes_and_measurements}.
-The format of the plots is the same across all figures. The first panel
-displays the relative difference (in permille) between the {\sc PineAPPL} and
-the {\sc MC} results for the central, upper and lower scale choices, for
-theories accurate to both NLO QCD and NLO QCD+EW. The following three panels
-present the theoretical predictions, accurate to either NLO QCD or NLO QCD+EW,
-always normalised to the former; on top of the theoretical predictions, the
-PDF uncertainty, the scale uncertainty and the Monte Carlo uncertainty are
-displayed in turn. The relative uncertainty of the experimental data is
-also shown for comparison. We shall now discuss the results for each
-process and data set.
-
-\paragraph{DY lepton pair production.}
-
-We first consider the single-differential measurement at a high lepton pair
-invariant mass performed by the ATLAS experiment at 7 TeV. 
-From Fig.~\ref{fig:atlaszhighmass49fb} we immediately
-observe that the validation of the \textsc{PineAPPL} result against the MC
-result is successful. The relative difference between the two is of the order
-$0.1\tcperthousand$ at most, with negligible fluctuations across different
-invariant mass bins. The same remains true for theories accurate to both NLO
-QCD or NLO QCD+EW, and irrespective of the scale choice.
-
-%-------------------------------------------------------------------------------
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB}
-    \caption{Validation and test of the \textsc{PineAPPL} grid for the ATLAS
-      high-mass DY lepton pair measurement in the high-mass region at
-      a centre-of-mass energy of 7 TeV~\cite{Aad:2013iua}. The first panel
-      displays the relative difference (in permille) between the {\sc PineAPPL}
-      and the {\sc MC} results for the central, upper and lower scale choices,
-      for theories accurate to both NLO QCD and NLO QCD+EW. The second, third
-      and fourth panels present the theoretical predictions, accurate to either
-      NLO QCD or NLO QCD+EW, always normalised to the former; on top of the
-      theoretical predictions, the PDF uncertainty, the scale uncertainty and
-      the Monte Carlo uncertainty are displayed in turn. The relative
-      uncertainty of the experimental data is also shown for comparison.}
-    \label{fig:atlaszhighmass49fb}
-\end{figure}
-%-------------------------------------------------------------------------------
-
-\paragraph{Top-quark pair production.}
-
-\paragraph{$Z$-boson production with non-zero transverse momentum.}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin1}%
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin2}
-    \caption{PineAPPL comparison for CMS 2D Drell--Yan.}
-    \label{fig:cmsdy2d11_bins12}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin3}%
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin4}
-    \caption{PineAPPL comparison for CMS 2D Drell--Yan.}
-    \label{fig:cmsdy2d11_bins34}
-\end{figure}
+\section{Additional material}
+\label{app:add_plots}
 
@@
 \end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TPT}%
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TTM}
-    \caption{PineAPPL comparison for ATLAS top pair.}
-    \label{fig:atlastop}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMS_Z_13_TEV}
-    \caption{PineAPPL comparison for CMS $Z$ $p_T$ distribution.}
-    \label{fig:cmsZ13TeV}
-\end{figure}
-
-\noindent
-
-TODO for each process:
-\begin{itemize}
-\item size of the photon-initiated contributions,
-\item largest partonic channel,
-\item most important $x$ region,
-\item PDF uncertainty,
-\end{itemize}

### 2020-07-31 paper/sec-results.tex
MOre on Sect. 3

@@
-\section{PineAPPL at work: generation and validation of interpolation grids}
+\section{Validation and interpretation of PineAPPL grids}
 \label{sec:results}
@@
 $\mathcal{O}(\alpha_s^2\alpha)$ and $\mathcal{O}(\alpha_s\alpha^2)$.
-We do not consider the LO PI contribution $\mathcal{O}(\alpha^2)$ and the
+We do not consider the LO contribution $\mathcal{O}(\alpha^2)$ and the
 corresponding higher-order EW correction. EW corrections for this process
@@
 corrections) in the NNDPF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
-the CT18 PDF set~\cite{Hou:2019efy}. EW corrections for this process
-were computed in Refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
+the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
+single LO contribution $\mathcal{O}(\alpha_s\alpha^2)$ and a single NLO
+contribution $\mathcal{O}(\alpha_s^2\alpha^2)$. In the NLO QCD+EW computation,
+they are supplemented with the LO and NLO EW corrections,
+$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alpha^4)$, and with the NLO
+QCD-EW mixed correction, $\mathcal{O}(\alpha_s\alpha^3)$. EW corrections for
+this process were computed in
+Refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
+The process receives contributions from 100 (165) parton luminosities, mainly
+from $qg$ and $\bar{q}g$ scattering.
 
@@
 
-We first consider the single-differential measurement at a high lepton pair
+We first consider the single-differential measurement at a high lepton-pair
 invariant mass performed by the ATLAS experiment at 7 TeV. 
@@
 $0.1\tcperthousand$ at most, with negligible fluctuations across different
-invariant mass bins. The same remains true for theories accurate to both NLO
-QCD or NLO QCD+EW, and irrespective of the scale choice.
+invariant mass bins. The agreement is similarly good irrespective of the
+perturbative accuracy of the theory (NLO QCD or NLO QCD+EW) or of the scale
+choice.
 
@@
 
+The measurement is mainly driven by $q\bar q$ scattering: specifically, the
+leading contribution comes from a $u\bar{u}$ ($d\bar{d}$) parton luminosity,
+which accounts for about 55\% (49\%) of the cross section for the lowest
+invariant mass bins, and 68\% (22\%) for the largest invariant mass bins.
+The PI contribution raises from about 1.3\% in the lowest bin to about 3.6\% in
+the highest bin. Overall, the EW corrections range between 5\% around
+$M_{\ell\bar\ell}\sim 150$~GeV, 2\%-3\% for intermediate invariant mass values,
+$150~\textrm{GeV}\lesssim M_{\ell\bar\ell}\lesssim 700~\textrm{GeV}$, and
+15\%-20\% for the largest invariant mass bins, $M_{\ell\bar\ell}\sim 1000$~GeV,
+see Fig.~\ref{fig:atlaszhighmass49fb}. For this reason, the data points with
+$M_{\ell\bar\ell}>210$~GeV were not included in the NNPDF3.1
+analysis~\cite{Ball:2017nwa}.
+
+The NLO QCD+EW corrections always lead to a reduction of the cross section in
+comparison to the NLO QCD prediction. The size of this shift is comparable to
+the data uncertainty at small values of $M_{\ell\bar\ell}$, and rapidly becomes
+negligible with respect to it as the value of the invariant mass increases
+and the data uncertainty blows up. This fact suggests a couple of observations
+in light of the inclusion of EW corrections in a fit of PDFs. First, the
+description of the more precise bins in the low invariant mass range is likely
+to change, and will possibly become more accurate should the inclusion of EW
+corrections improve the data/theory agreement. Second, the kinematic cut that
+excludes any data point at large $M_{\ell\bar\ell}$ can be safely removed: any
+shift in the predictions induced by the more accurate NLO QCD+EW theory is
+likely to be easily accommodated by the large data uncertainty.
+
+In comparison to the PDF uncertainty, the size of the EW correction is
+always larger, especially at the boundaries of the distribution. This fact
+suggests that, once included in a global fit, EW corrections could recast the
+relative weight of each data set included in the fit, and possibly lead to
+an improvement in their overall description. In comparison to the scale
+uncertainty, the size of the EW correction is similar, except for the four bins
+at the largest invariant mass, where the latter is significantly larger than
+the former. The size of the scale variation is the same for the QCD and the
+QCD+EW theories. These facts suggest that the NNLO QCD correction is comparable
+to the NLO QCD+EW correction, except at very large values of the invariant mass,
+where the EW correction still dominates. This result stresses the need to
+include the EW corrections in order to obtain an accurate description of the
+large invariant mass bins. Finally, the Monte Carlo statistical
+uncertainty remains negligible in comparison to the data, PDF and scale
+uncertainties, and to the size of the EW correction. Our conclusions are
+therefore not affected by a poor simultaion of the underlying events.
+
+We then turn our attention to the double-differential measurement performed by
+the CMS experiment at 7~TeV. For illustrative purposes, we report only four out
+of the six invariant mass bins, respectively below the $Z$-boson mass peak,
+45~GeV$<M_{\ell\bar\ell}<$60~GeV, on the $Z$-boson mass peak,
+60~GeV$<M_{\ell\bar\ell}<$120~GeV, above the mass peak,
+120~GeV$<M_{\ell\bar\ell}<$200~GeV, and at very high invarinat masses,
+200~GeV$<M_{\ell\bar\ell}<$1500~GeV, see Fig.~\ref{fig:cmsdy2d11_bins3456}.
+Analogous plots for the remaining invariant mass bins are collected in
+Appendix~\ref{app:add_plots}. From Fig.~\ref{fig:cmsdy2d11_bins3456},
+first of all we validate the \textsc{PineAPPL} result: its relative difference
+with respect to the \textsc{MC} result is always below a fraction of permille,
+again irrespective of the accuracy of the theory, of the choice of scale, and
+of the kinematic bin considered.
+
+%-------------------------------------------------------------------------------
+\begin{figure}[!p]
+    \centering
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin3}%
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin4}\\
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin5}%
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin6}\\
+    \caption{Same as Fig.~\ref{fig:atlaszhighmass49fb}, but for the CMS
+      double-differential DY lepton pair measurement at a centre-of-mass energy
+      of 7~TeV~\cite{Chatrchyan:2013tia}. Displayed are only two of the six
+      invariant mass bins available, respectively below the $Z$-boson mass peak,
+      45~GeV$<M_{\ell\bar\ell}<$60~GeV, on the $Z$-boson mass peak,
+      60~GeV$<M_{\ell\bar\ell}<$120~GeV, above the mass peak,
+      120~GeV$<M_{\ell\bar\ell}<$200~GeV, and at very high invarinat masses,
+      200~GeV$<M_{\ell\bar\ell}<$1500~GeV.}
+    \label{fig:cmsdy2d11_bins3456}
+\end{figure}
+%-------------------------------------------------------------------------------
+
+As in the case of the ATLAS high-mass DY measurement, the CMS measurement is
+also dominated by $q\bar{q}$ scattering. The leading (next-to-leading)
+contribution to the 45~GeV$<M_{\ell\bar\ell}<$60~GeV invariant mass bin comes from
+the $u\bar{u}$ ($d\bar{d}$) parton luminosity, which accounts for about 70\%
+(22\%) of the double differential cross section, with small fluctuations across
+the rapidity range. The PI contribution decreases from about 4\% at zero
+rapidity to 1.5\% in the largest rapidity bin. The situation is slightly
+different in the 60~GeV$<M_{\ell\bar\ell}<$120~GeV invariant mass bin, where the
+leading (next-to-leading) contribution comes instead from the $d\bar{d}$
+($u\bar{u}$) parton luminosity, which accounts for about 60\% (44\%) of the
+double differential cross section at small rapidities, and for about 56\% (50\%)
+at large rapidities. In the remaining two invariant mass bins, the leading
+(next-to-leading) contribution comes again from the $u\bar{u}$ ($d\bar{d}$)
+parton luminosity, which accounts for about 69\%-95\% (38\%-30\%) and
+57\%-70\% (48\%-34\%), respectively for 120~GeV$<M_{\ell\bar\ell}<$200~GeV and
+200~GeV$<M_{\ell\bar\ell}<$1500~GeV in the corresponding rapidity intervals; PI
+contributions range between 7.3\%-1.2\% and 3.7\%-0.6\% in the two invariant
+mass bins, respectively, for increasing rapidity.
+
+The way in which NLO QCD+EW corrections affect the theoretical prediction for
+the double differential cross section (with respect to its counterpart accurate
+to NLO QCD) depends on the invariant mass bin. In the
+45~GeV$<M_{\ell\bar\ell}<$60~GeV region, they enhance the value of the cross
+section by about 11\% across all the rapidity range; in the
+60~GeV$<M_{\ell\bar\ell}<$120~GeV region, they suppress the value of the cross
+section by about 2\%, again across all the rapidity range; in the 
+120~GeV$<M_{\ell\bar\ell}<$200~GeV bin, the suppression is around 4\%-5\%; and in
+the 200~GeV$<M_{\ell\bar\ell}<$1500~GeV bin, the suppression increases further to
+about 6\%-7\% for rapidities $y_{\ell\bar\ell}<2.0$ and up to 20\%-40\% at forward
+rapidities. For this reason, for instance, the data points with
+$M_{\ell\bar\ell}>200$~GeV and $y_{\ell\bar\ell}>2.2$ were not included in the
+NNPDF3.1 analysis~\cite{Ball:2017nwa}.
+
+In general, the size of the EW corrections is
+
 \paragraph{Top-quark pair production.}
@@
 \paragraph{$Z$-boson production with non-zero transverse momentum.}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin1}%
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin2}
-    \caption{PineAPPL comparison for CMS 2D Drell--Yan.}
-    \label{fig:cmsdy2d11_bins12}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin3}%
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin4}
-    \caption{PineAPPL comparison for CMS 2D Drell--Yan.}
-    \label{fig:cmsdy2d11_bins34}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin5}%
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin6}
-    \caption{PineAPPL comparison for CMS 2D Drell--Yan.}
-    \label{fig:cmsdy2d11_bins56}
-\end{figure}
 
@@
 
-TODO for each process:
-\begin{itemize}
-\item size of the photon-initiated contributions,
-\item largest partonic channel,
-\item most important $x$ region,
-\item PDF uncertainty,
-\end{itemize}
+%TODO for each process:
+%\begin{itemize}
+%\item size of the photon-initiated contributions,
+%\item largest partonic channel,
+%\item most important $x$ region,
+%\item PDF uncertainty,
+%\end{itemize}

### 2020-08-01 paper/sec-results.tex
more on Sect.3

@@
 uncertainties, and to the size of the EW correction. Our conclusions are
-therefore not affected by a poor simultaion of the underlying events.
+therefore not affected by a poor simulation of the underlying events.
 
@@
 
-In general, the size of the EW corrections is
+In general, the size of the EW corrections is comparable to or slightly larger
+than the data uncertainty, except for the invariant mass bin 
+45~GeV$<M_{\ell\bar\ell}<$60~GeV, where the shift due to the EW correction
+overshoots the data uncertainty by about a factor of ten, and at large
+rapidities, where the shift due to the EW correction, although it can become
+large, is always a fraction of the data uncertainty. As already observed in the
+case of the ATLAS measurement, should EW corrections be included in a fit of
+PDFs, the description of the precise bins in the low invariant mass range is
+likely to benefit from the more accurate theory and the kinematic cut that
+excludes any data point at large invariant mass and/or rapidity can be safely
+removed.
+
+In comparison to the PDF uncertainty, the size of the EW corrections is always
+larger. We therefore anticipate that, once included in a PDF fit, they would
+recast the relative weight of each data set included in the fit, and possibly
+lead to an improvement in their overall description. In comparison to the scale
+uncertainty, the size of the EW correction is similar, except on the $Z$-boson
+mass peak, 60~GeV$<M_{\ell\bar\ell}<$120~GeV, where the scale uncertainty exceeds
+the size of the EW correction by about a factor of five. These facts confirm,
+as expected, that EW corrections are almost immaterial at the $Z$-boson mass
+peak, but that NNLO QCD corrections are otherwise as relevant as NLO QCD+EW
+corrections. Finally, the Monte Carlo statistical uncertainty remains negligible
+in comparison to the data, PDF and scale uncertainties, and to the size of the
+EW correction, except for a couple of bins at forward rapidity in the highest
+invariant mass bins. Improving the Monte Carlo statistical precision will
+require to generate an unrealistically large number of events; therefore, it
+might be desirable to treat this uncertainty as an additional theoretical
+uncertainty in the PDF fit~\cite{Ball:2018lag}.
 
@@
 
-\paragraph{$Z$-boson production with non-zero transverse momentum.}
-
-\begin{figure}
+\begin{figure}[!t]
     \centering
@@
     \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TTM}
-    \caption{PineAPPL comparison for ATLAS top pair.}
+    \caption{Same as Fig.~\ref{fig:atlaszhighmass49fb}, but for the ATLAS
+      differential top-quark pair measuremen at a centre-of-mass energy of
+      8~TeV~\cite{Aad:2015mbv}. Displayed are the distributions in the
+      transverse momentum of the top quark $p_T^t$ (left), and in the invariant
+      mass of the top-quark pair $m_{t\bar{t}}$ (right).}
     \label{fig:atlastop}
@@
 
-\begin{figure}
+\paragraph{$Z$-boson production with non-zero transverse momentum.}
+
+\begin{figure}[!t]
     \centering

### 2020-08-01 paper/sec-results.tex
Typos

@@
 
-We focus on the following three processes: DY lepton-pair production, top-quark
+We focus on the following three processes: Drell--Yan lepton-pair production, top-quark
 pair production, and Z-boson (lepton-pair) production with non-zero transverse
@@
 
-\paragraph{DY lepton pair production.}
+\paragraph{Drell--Yan lepton pair production.}
 We select the distribution, single-differential in the invariant mass of the
@@
 The central values of the renormalisation and factorisation scales, $\mu_R$ and
-$\mu_F$, are chosen, for each process, as follows. In the case of DY lepton pair
+$\mu_F$, are chosen, for each process, as follows. In the case of Drell--Yan lepton pair
 production, we use the fixed scale $\mu_R=\mu_F=M_Z$, where $M_Z$ is the mass
@@
 Finally, we implement the kinematic cuts specified in the corresponding
-experimental analyses. In the case of high-mass DY lepton pair
+experimental analyses. In the case of high-mass Drell--Yan lepton pair
 production at 7~TeV measured by ATLAS, we require $p_T^\ell>25$~GeV,
@@
 momentum and the rapidity of each lepton and for the invariant mass of the
-lepton pair, respectively. In the case of the DY lepton-pair production at
+lepton pair, respectively. In the case of the Drell--Yan lepton-pair production at
 7~TeV measured by CMS, we require $p_T^{\ell_1}>14$~GeV, $p_T^{\ell_2}>9$~GeV,
@@
 
-\paragraph{DY lepton pair production.}
+\paragraph{Drell--Yan lepton pair production.}
 
@@
     \caption{Validation and test of the \textsc{PineAPPL} grid for the ATLAS
-      high-mass DY lepton pair measurement in the high-mass region at
+      high-mass Drell--Yan lepton pair measurement in the high-mass region at
       a centre-of-mass energy of 7 TeV~\cite{Aad:2013iua}. The first panel
@@
     \caption{Same as Fig.~\ref{fig:atlaszhighmass49fb}, but for the CMS
-      double-differential DY lepton pair measurement at a centre-of-mass energy
+      double-differential Drell--Yan lepton pair measurement at a centre-of-mass energy
       of 7~TeV~\cite{Chatrchyan:2013tia}. Displayed are only two of the six
@@
 
-As in the case of the ATLAS high-mass DY measurement, the CMS measurement is
+As in the case of the ATLAS high-mass Drell--Yan measurement, the CMS measurement is
 also dominated by $q\bar{q}$ scattering. The leading (next-to-leading)

### 2020-08-01 paper/sec-results.tex
Fix a few spelling mistakes

@@
 In this section we demonstrate the capabilities of \textsc{PineAPPL} by
-computing fast interpolation grids, accurate to NLO QCD and NLO QCD+EW,
-for a representative set of processes in which EW corrections are expected 
-to be sizeable. In order to consider some realistic kinematics for these
+computing fast-interpolation grids, accurate to NLO QCD and NLO QCD+EW,
+for a representative set of processes in which EW corrections may have a
+sizeable effect on the accuracy of the theoretical predictions.
+In order to consider some realistic kinematics for these
 processes, we resort to measurements commonly devised for inclusion in PDF
@@
 
-We focus on the following three processes: Drell--Yan lepton-pair production, top-quark
-pair production, and Z-boson (lepton-pair) production with non-zero transverse
-momentum in proton-proton collisions. For each of these processes, we consider the measurements
-described below.
+We focus on the following three processes: Drell--Yan lepton-pair production,
+top-quark pair production, and Z-boson (lepton-pair) production with non-zero
+transverse momentum in proton-proton collisions. For each of these processes,
+we consider the following measurements.
 
@@
 We select the distribution, single-differential in the invariant mass of the
-lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of
-mass energy of 7~TeV in the high-mass region
+lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of-mass
+energy of 7~TeV in the high-mass region
 ($M_{\ell\bar\ell}>116$~GeV)~\cite{Aad:2013iua}.
-We also select the distribution, double-differential in the rapidity and in
+We also select the distributions, double-differential in the rapidity and in
 the invariant mass of the lepton pair, $y_{\ell\bar\ell}$ and $M_{\ell\bar\ell}$,
@@
 values of invariant mass, where EW corrections become sizeable. As explained in
-Sect.~\ref{sec:pineappl-example}, should PI contributions be taken into account,
+section~\ref{sec:pineappl-example}, should PI contributions be taken into account,
 the process has a single LO, $\mathcal{O}(\alpha^2)$; at NLO, the
@@
 EW corrections for this process were computed in
-Refs.~\cite{Baur:2001ze,Dittmaier:2009cr}. The process receives contributions
-from 12 (34) parton luminosities at NLO QCD (NLO QCD+EW).
+refs.~\cite{Baur:2001ze,Dittmaier:2009cr}. The process receives contributions
+from 12 (34) parton luminosities at NLO QCD (NLO QCD+EW),
+see Appendix~\ref{app:lumis} for details.
 
@@
 been extensively studied in the context of PDF fits in
-Refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml}, and
+refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml}, and
 included by default in the CT18~\cite{Hou:2019efy} analysis.
@@
 pure QCD contributions at LO, $\mathcal{O}(\alpha_s^2)$, and
-at NLO, $\mathcal{O}(\alpha_s^3)$. They are included in the NLO QCD
+at NLO, $\mathcal{O}(\alpha_s^3)$. They make up the NLO QCD
 computation. The NLO QCD+EW computation includes the LO contribution
@@
 corresponding higher-order EW correction. EW corrections for this process
-were computed in Refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}.
+were computed in refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}.
 The process receives contributions from
-6 (36) parton luminositites at NLO QCD (NLO QCD+EW), mainly from $gg$ fusion.
+6 (36) parton luminosities at NLO QCD (NLO QCD+EW),
+see Appendix~\ref{app:lumis} for details.
 
@@
 selection of an appropriate kinematic cut that excluded bins with large EW
-corrections) in the NNDPF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
+corrections) in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
 the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
@@
 contribution $\mathcal{O}(\alpha_s^2\alpha^2)$. In the NLO QCD+EW computation,
-they are supplemented with the LO and NLO EW corrections,
+we supplement these with the LO and NLO EW corrections,
 $\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alpha^4)$, and with the NLO
@@
 this process were computed in
-Refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
-The process receives contributions from 100 (165) parton luminosities, mainly
-from $qg$ and $\bar{q}g$ scattering.
+refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
+The process receives contributions from 100 (165) parton luminosities,
+see Appendix~\ref{app:lumis} for details.
 
@@
 the complex mass (CM) scheme for all massive particles, see
-Ref.~\cite{Frederix:2018nkq} for details. We use this scheme
+ref.~\cite{Frederix:2018nkq} for details. We use this scheme
 for all processes that do not involve stable top quarks in the final state.
@@
 uncertainty associated to the theoretical predictions a posteriori, that is,
-we convolve the fast interpolation grid generated with {\sc PineAPPL} with
+we convolve the fast-interpolation grid generated with {\sc PineAPPL} with
 each member in the PDF set, and we compute the associated standard deviation.
@@
 The central values of the renormalisation and factorisation scales, $\mu_R$ and
-$\mu_F$, are chosen, for each process, as follows. In the case of Drell--Yan lepton pair
-production, we use the fixed scale $\mu_R=\mu_F=M_Z$, where $M_Z$ is the mass
-of the $Z$-boson, for the ATLAS measurement, and the scale
+$\mu_F$, are chosen, for each process, as follows. In the case of Drell--Yan
+lepton pair production, we use the fixed scale $\mu_R=\mu_F=M_Z$, where $M_Z$ is
+the mass of the $Z$-boson, for the ATLAS measurement, and the scale
 $\mu_R=\mu_F=M_{\ell\bar\ell}$, where $M_{\ell\bar\ell}$ is the central value of each
@@
 we allow the events to be reweighted in the Monte Carlo generation upon scale
-variations. As is customary, the factorisation and renormalisation scales
+variations. To this purpose, we use the default \textsc{MG5\_aMC}
+implementation, whereby the factorisation and renormalisation scales
 are varied down to a factor $1/2$ and up to a factor $2$, and the envelope
-from the nine-point scale variations is constructed.
+from the nine-point scale variations is constructed. However, we note that
+\textsc{PineAPPL} allows the user to determine the envelope with any point
+prescription, see Appendix~\ref{app:pineappl-demo} for an example.
 
@@
 \begin{equation}
-%\begin{aligned}
 M_\mathrm{W} = \SI{80}{\giga\electronvolt} \text{,} \quad 
@@
 \label{eq:parameters}
-%\end{aligned}
 \end{equation}
@@
 momentum and the rapidity of each lepton and for the invariant mass of the
-lepton pair, respectively. In the case of the Drell--Yan lepton-pair production at
-7~TeV measured by CMS, we require $p_T^{\ell_1}>14$~GeV, $p_T^{\ell_2}>9$~GeV,
+lepton pair, respectively. In the case of double-differential Drell--Yan
+lepton-pair production
+at 7~TeV measured by CMS, we require $p_T^{\ell_1}>14$~GeV, $p_T^{\ell_2}>9$~GeV,
 $|\eta_\ell|<2.4$, $|\eta_{\ell\bar\ell}|<2.4$ and 20~GeV$<M_{\ell\bar\ell}<$ 1500~GeV
@@
 For each of the measurements discussed in
-Sect.~\ref{subsec:processes_and_measurements}, we compute the expectation
+section~\ref{subsec:processes_and_measurements}, we compute the expectation
 value of the corresponding observable for each kinematic bin in two different
-ways: directly, by means of {\sc MG5\_aMC}, and a posteriori, by convolving the
-fast interpolation grid produced by {\sc PineAPPL} with the PDF set specified
-in Sect.~\ref{subsec:computational_settings}. In the following, we will refer
-to the first result as the {\sc MC} result, and to the second as the
-{\sc PineAPPL} result. We repeat the computation for theories accurate to NLO
-QCD and to NLO QCD+EW, respectively. In each case, we determine the PDF
-uncertainty (coming from the PDF ensemble), the scale uncertainty (coming from
-variations of the factorisation and renormalisation scales), and the Monte
+ways: directly, by means of \textsc{MG5\_aMC}, and a posteriori, by convolving
+the fast-interpolation grid produced by \textsc{PineAPPL} with the PDF set
+specified in section~\ref{subsec:computational_settings}. In the following, we
+will refer to the first result as the \textsc{MC} result, and to the second as
+the \textsc{PineAPPL} result. We repeat the computation for theories accurate
+to NLO QCD and to NLO QCD+EW, respectively. The corresponding orders of the
+strong and electroweak couplings that we consider have been specified in
+section~\ref{subsec:processes_and_measurements}. In each case, we determine the
+PDF uncertainty (coming from the PDF ensemble), the scale uncertainty (coming
+from variations of the factorisation and renormalisation scales), and the Monte
 Carlo uncertainty (coming from the finite number of events generated). In this
 last respect, we consider by default high-statistics computations, whereby we
-require a relative Monte Carlo precision of a fraction of permille. While
-this choice does not affect the validation of the {\sc PineAPPL} result against
-the {\sc MC} result, it ensures that the statistical uncertainty of the
-computation remains negligible in comparison to the PDF and scale uncertainties,
-as we will explicitly demonstrate. This is a desirable feature to correctly
-interpret the size of the theoretical corrections.
+require a relative Monte Carlo precision of a fraction of per mille. While
+this choice does not affect the validation of the \textsc{PineAPPL} result
+against the \textsc{MC} result, it ensures that the statistical uncertainty of
+the computation remains negligible in comparison to the PDF and scale
+uncertainties, as we will explicitly demonstrate. This is a desirable feature
+to correctly interpret the size of the EW corrections.
 
 Our goal is indeed twofold. On the one hand, we aim to validate the
-interpolation grids generated with {\sc PineAPPL}: to this purpose we shall
-verify that the MC and the {\sc PineAPPL} results are identical up to numerical
-inaccuracies due to the grid interpolation. This equivalence must hold for any
-choice of renormalisation and factorisation scale. On the other hand, we aim to
-study the size of the EW corrections, in particular with respect to the
-kinematics of each process, and to three kinds of uncertainties: the PDF
-uncertainty, the scale variation uncertainty, and the uncertainty of the
+interpolation grids generated with \textsc{PineAPPL}: to this purpose we shall
+verify that the MC and the \textsc{PineAPPL} results are identical up to
+numerical inaccuracies due to the grid interpolation. This equivalence must
+hold for any choice of renormalisation and factorisation scale. On the other
+hand, we aim to study the size of the EW corrections, in particular with
+respect to the kinematics of each process, and to three kinds of uncertainties:
+the PDF uncertainty, the scale uncertainty, and the uncertainty of the
 experimental data.
@@
 We present these comparisons in
-Figs.~\ref{fig:atlaszhighmass49fb}-\ref{fig:cmsZ13TeV} for each of the processes
-and data sets outlined in Sect.~\ref{subsec:processes_and_measurements}.
+figures~\ref{fig:atlaszhighmass49fb}-\ref{fig:cmsZ13TeV} for each of the processes
+and data sets outlined in section~\ref{subsec:processes_and_measurements}.
 The format of the plots is the same across all figures. The first panel
-displays the relative difference (in permille) between the {\sc PineAPPL} and
+displays the relative difference (in per mille) between the {\sc PineAPPL} and
 the {\sc MC} results for the central, upper and lower scale choices, for
@@
 invariant mass performed by the ATLAS experiment at 7 TeV. 
-From Fig.~\ref{fig:atlaszhighmass49fb} we immediately
+From figure~\ref{fig:atlaszhighmass49fb} we immediately
 observe that the validation of the \textsc{PineAPPL} result against the MC
@@
       a centre-of-mass energy of 7 TeV~\cite{Aad:2013iua}. The first panel
-      displays the relative difference (in permille) between the {\sc PineAPPL}
+      displays the relative difference (in per mille) between the {\sc PineAPPL}
       and the {\sc MC} results for the central, upper and lower scale choices,
@@
 The measurement is mainly driven by $q\bar q$ scattering: specifically, the
-leading contribution comes from a $u\bar{u}$ ($d\bar{d}$) parton luminosity,
-which accounts for about 55\% (49\%) of the cross section for the lowest
-invariant mass bins, and 68\% (22\%) for the largest invariant mass bins.
-The PI contribution raises from about 1.3\% in the lowest bin to about 3.6\% in
-the highest bin. Overall, the EW corrections range between 5\% around
-$M_{\ell\bar\ell}\sim 150$~GeV, 2\%-3\% for intermediate invariant mass values,
-$150~\textrm{GeV}\lesssim M_{\ell\bar\ell}\lesssim 700~\textrm{GeV}$, and
-15\%-20\% for the largest invariant mass bins, $M_{\ell\bar\ell}\sim 1000$~GeV,
-see Fig.~\ref{fig:atlaszhighmass49fb}. For this reason, the data points with
+leading (next-to-leading) contribution comes from a $u\bar{u}$ ($d\bar{d}$)
+parton luminosity, which accounts for about 55\% (49\%) of the cross section
+for the lowest invariant mass bins, and 68\% (22\%) for the largest invariant
+mass bins. The PI contribution raises from about 1.3\% in the lowest bin to
+about 3.6\% in the highest bin. Overall, the EW corrections range between 5\%
+around $M_{\ell\bar\ell}\sim 150$~GeV, 2\%-3\% for intermediate invariant mass
+values, $150~\textrm{GeV}\lesssim M_{\ell\bar\ell}\lesssim 700~\textrm{GeV}$, and
+15\%-20\% for the argest invariant mass bin, $M_{\ell\bar\ell}>1000$~GeV,
+see figure~\ref{fig:atlaszhighmass49fb}. For this reason, the data points with
 $M_{\ell\bar\ell}>210$~GeV were not included in the NNPDF3.1
@@
 
-In comparison to the PDF uncertainty, the size of the EW correction is
+In comparison to the PDF uncertainty, the size of the EW corrections is
 always larger, especially at the boundaries of the distribution. This fact
@@
 60~GeV$<M_{\ell\bar\ell}<$120~GeV, above the mass peak,
-120~GeV$<M_{\ell\bar\ell}<$200~GeV, and at very high invarinat masses,
-200~GeV$<M_{\ell\bar\ell}<$1500~GeV, see Fig.~\ref{fig:cmsdy2d11_bins3456}.
-Analogous plots for the remaining invariant mass bins are collected in
-Appendix~\ref{app:add_plots}. From Fig.~\ref{fig:cmsdy2d11_bins3456},
+120~GeV$<M_{\ell\bar\ell}<$200~GeV, and at very high invariant masses,
+200~GeV$<M_{\ell\bar\ell}<$1500~GeV, see figure~\ref{fig:cmsdy2d11_bins3456}.
+Analogous plots for the remaining low invariant mass bins are collected in
+Appendix~\ref{app:add_plots}. From figure~\ref{fig:cmsdy2d11_bins3456},
 first of all we validate the \textsc{PineAPPL} result: its relative difference
-with respect to the \textsc{MC} result is always below a fraction of permille,
+with respect to the \textsc{MC} result is always below a fraction of per mille,
 again irrespective of the accuracy of the theory, of the choice of scale, and
@@
     \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin6}\\
-    \caption{Same as Fig.~\ref{fig:atlaszhighmass49fb}, but for the CMS
-      double-differential Drell--Yan lepton pair measurement at a centre-of-mass energy
-      of 7~TeV~\cite{Chatrchyan:2013tia}. Displayed are only two of the six
-      invariant mass bins available, respectively below the $Z$-boson mass peak,
-      45~GeV$<M_{\ell\bar\ell}<$60~GeV, on the $Z$-boson mass peak,
-      60~GeV$<M_{\ell\bar\ell}<$120~GeV, above the mass peak,
-      120~GeV$<M_{\ell\bar\ell}<$200~GeV, and at very high invarinat masses,
+    \caption{Same as figure~\ref{fig:atlaszhighmass49fb}, but for the CMS
+      double-differential Drell--Yan lepton pair measurement at a
+      centre-of-mass energy of 7~TeV~\cite{Chatrchyan:2013tia}. Displayed are
+      only two of the six invariant mass bins available, respectively below the
+      $Z$-boson mass peak, 45~GeV$<M_{\ell\bar\ell}<$60~GeV, on the $Z$-boson mass
+      peak, 60~GeV$<M_{\ell\bar\ell}<$120~GeV, above the mass peak,
+      120~GeV$<M_{\ell\bar\ell}<$200~GeV, and at very high invariant masses,
       200~GeV$<M_{\ell\bar\ell}<$1500~GeV.}
@@
 
-As in the case of the ATLAS high-mass Drell--Yan measurement, the CMS measurement is
-also dominated by $q\bar{q}$ scattering. The leading (next-to-leading)
-contribution to the 45~GeV$<M_{\ell\bar\ell}<$60~GeV invariant mass bin comes from
+As in the case of the ATLAS high-mass Drell--Yan measurement, the CMS
+measurement is also dominated by $q\bar{q}$ scattering. The leading
+(next-to-leading) contribution to the 45~GeV$<M_{\ell\bar\ell}<$60~GeV invariant
+mass bin comes from
 the $u\bar{u}$ ($d\bar{d}$) parton luminosity, which accounts for about 70\%
@@
 parton luminosity, which accounts for about 69\%-95\% (38\%-30\%) and
-57\%-70\% (48\%-34\%), respectively for 120~GeV$<M_{\ell\bar\ell}<$200~GeV and
-200~GeV$<M_{\ell\bar\ell}<$1500~GeV in the corresponding rapidity intervals; PI
-contributions range between 7.3\%-1.2\% and 3.7\%-0.6\% in the two invariant
-mass bins, respectively, for increasing rapidity.
+57\%-70\% (48\%-34\%) of the cross section, respectively for
+120~GeV$<M_{\ell\bar\ell}<$200~GeV and 200~GeV$<M_{\ell\bar\ell}<$1500~GeV in the
+corresponding rapidity intervals; PI contributions range between 7.3\%-1.2\%
+and 3.7\%-0.6\% in the two invariant mass bins, respectively, for increasing
+rapidity.
 
@@
 PDFs, the description of the precise bins in the low invariant mass range is
-likely to benefit from the more accurate theory and the kinematic cut that
-excludes any data point at large invariant mass and/or rapidity can be safely
-removed.
+likely to benefit from the more accurate theory; furthermore, the kinematic cut
+that excludes any data point at large invariant mass and/or rapidity can be
+safely removed.
 
@@
 
-\paragraph{Top-quark pair production.}
+\paragraph{Top-quark pair production.} We now consider
 
@@
     \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TTM}
-    \caption{Same as Fig.~\ref{fig:atlaszhighmass49fb}, but for the ATLAS
-      differential top-quark pair measuremen at a centre-of-mass energy of
+    \caption{Same as figure~\ref{fig:atlaszhighmass49fb}, but for the ATLAS
+      differential top-quark pair measurement at a centre-of-mass energy of
       8~TeV~\cite{Aad:2015mbv}. Displayed are the distributions in the
@@
 \end{figure}
-
-\noindent
-
-%TODO for each process:
-%\begin{itemize}
-%\item size of the photon-initiated contributions,
-%\item largest partonic channel,
-%\item most important $x$ region,
-%\item PDF uncertainty,
-%\end{itemize}

### 2020-08-01 paper/sec-results.tex
Typos

@@
 In this section we demonstrate the capabilities of \textsc{PineAPPL} by
-computing fast-interpolation grids, accurate to NLO QCD and NLO QCD+EW,
-for a representative set of processes in which EW corrections may have a
-sizeable effect on the accuracy of the theoretical predictions.
-In order to consider some realistic kinematics for these
+computing fast interpolation grids, accurate to NLO QCD and NLO QCD+EW,
+for a representative set of processes in which EW corrections are expected 
+to be sizeable. In order to consider some realistic kinematics for these
 processes, we resort to measurements commonly devised for inclusion in PDF
@@
 transverse momentum in proton-proton collisions. For each of these processes,
-we consider the following measurements.
+we consider the measurements described below.
 
@@
 We select the distribution, single-differential in the invariant mass of the
-lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of-mass
-energy of 7~TeV in the high-mass region
+lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of
+mass energy of 7~TeV in the high-mass region
 ($M_{\ell\bar\ell}>116$~GeV)~\cite{Aad:2013iua}.
@@
 values of invariant mass, where EW corrections become sizeable. As explained in
-section~\ref{sec:pineappl-example}, should PI contributions be taken into account,
+Sect.~\ref{sec:pineappl-example}, should PI contributions be taken into account,
 the process has a single LO, $\mathcal{O}(\alpha^2)$; at NLO, the
@@
 EW corrections for this process were computed in
-refs.~\cite{Baur:2001ze,Dittmaier:2009cr}. The process receives contributions
-from 12 (34) parton luminosities at NLO QCD (NLO QCD+EW),
-see Appendix~\ref{app:lumis} for details.
+Refs.~\cite{Baur:2001ze,Dittmaier:2009cr}. The process receives contributions
+from 12 (34) parton luminosities at NLO QCD (NLO QCD+EW), mainly from $q\bar{q}$
+scattering, see Appendix~\ref{app:lumis} for details.
 
@@
 been extensively studied in the context of PDF fits in
-refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml}, and
+Refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml}, and
 included by default in the CT18~\cite{Hou:2019efy} analysis.
@@
 corresponding higher-order EW correction. EW corrections for this process
-were computed in refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}.
+were computed in Refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}.
 The process receives contributions from
-6 (36) parton luminosities at NLO QCD (NLO QCD+EW),
+6 (36) parton luminositites at NLO QCD (NLO QCD+EW), mainly from $gg$ fusion,
 see Appendix~\ref{app:lumis} for details.
@@
 this process were computed in
-refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
-The process receives contributions from 100 (165) parton luminosities,
-see Appendix~\ref{app:lumis} for details.
+Refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
+The process receives contributions from 100 (165) parton luminosities, mainly
+from $qg$ and $\bar{q}g$ scattering, see Appendix~\ref{app:lumis} for details.
 
@@
 the complex mass (CM) scheme for all massive particles, see
-ref.~\cite{Frederix:2018nkq} for details. We use this scheme
+Ref.~\cite{Frederix:2018nkq} for details. We use this scheme
 for all processes that do not involve stable top quarks in the final state.
@@
 uncertainty associated to the theoretical predictions a posteriori, that is,
-we convolve the fast-interpolation grid generated with {\sc PineAPPL} with
+we convolve the fast interpolation grid generated with {\sc PineAPPL} with
 each member in the PDF set, and we compute the associated standard deviation.
@@
 For each of the measurements discussed in
-section~\ref{subsec:processes_and_measurements}, we compute the expectation
+Sect.~\ref{subsec:processes_and_measurements}, we compute the expectation
 value of the corresponding observable for each kinematic bin in two different
 ways: directly, by means of \textsc{MG5\_aMC}, and a posteriori, by convolving
-the fast-interpolation grid produced by \textsc{PineAPPL} with the PDF set
-specified in section~\ref{subsec:computational_settings}. In the following, we
+the fast interpolation grid produced by \textsc{PineAPPL} with the PDF set
+specified in Sect.~\ref{subsec:computational_settings}. In the following, we
 will refer to the first result as the \textsc{MC} result, and to the second as
@@
 strong and electroweak couplings that we consider have been specified in
-section~\ref{subsec:processes_and_measurements}. In each case, we determine the
+Sect.~\ref{subsec:processes_and_measurements}. In each case, we determine the
 PDF uncertainty (coming from the PDF ensemble), the scale uncertainty (coming
@@
 last respect, we consider by default high-statistics computations, whereby we
-require a relative Monte Carlo precision of a fraction of per mille. While
+require a relative Monte Carlo precision of a fraction of permille. While
 this choice does not affect the validation of the \textsc{PineAPPL} result
@@
 We present these comparisons in
-figures~\ref{fig:atlaszhighmass49fb}-\ref{fig:cmsZ13TeV} for each of the processes
-and data sets outlined in section~\ref{subsec:processes_and_measurements}.
+Figs.~\ref{fig:atlaszhighmass49fb}-\ref{fig:cmsZ13TeV} for each of the processes
+and data sets outlined in Sect.~\ref{subsec:processes_and_measurements}.
 The format of the plots is the same across all figures. The first panel
-displays the relative difference (in per mille) between the {\sc PineAPPL} and
+displays the relative difference (in permille) between the {\sc PineAPPL} and
 the {\sc MC} results for the central, upper and lower scale choices, for
@@
 invariant mass performed by the ATLAS experiment at 7 TeV. 
-From figure~\ref{fig:atlaszhighmass49fb} we immediately
+From Fig.~\ref{fig:atlaszhighmass49fb} we immediately
 observe that the validation of the \textsc{PineAPPL} result against the MC
@@
       a centre-of-mass energy of 7 TeV~\cite{Aad:2013iua}. The first panel
-      displays the relative difference (in per mille) between the {\sc PineAPPL}
+      displays the relative difference (in permille) between the {\sc PineAPPL}
       and the {\sc MC} results for the central, upper and lower scale choices,
@@
 15\%-20\% for the argest invariant mass bin, $M_{\ell\bar\ell}>1000$~GeV,
-see figure~\ref{fig:atlaszhighmass49fb}. For this reason, the data points with
+see Fig.~\ref{fig:atlaszhighmass49fb}. For this reason, the data points with
 $M_{\ell\bar\ell}>210$~GeV were not included in the NNPDF3.1
@@
 120~GeV$<M_{\ell\bar\ell}<$200~GeV, and at very high invariant masses,
-200~GeV$<M_{\ell\bar\ell}<$1500~GeV, see figure~\ref{fig:cmsdy2d11_bins3456}.
+200~GeV$<M_{\ell\bar\ell}<$1500~GeV, see Fig.~\ref{fig:cmsdy2d11_bins3456}.
 Analogous plots for the remaining low invariant mass bins are collected in
-Appendix~\ref{app:add_plots}. From figure~\ref{fig:cmsdy2d11_bins3456},
+Appendix~\ref{app:add_plots}. From Fig.~\ref{fig:cmsdy2d11_bins3456},
 first of all we validate the \textsc{PineAPPL} result: its relative difference
-with respect to the \textsc{MC} result is always below a fraction of per mille,
+with respect to the \textsc{MC} result is always below a fraction of permille,
 again irrespective of the accuracy of the theory, of the choice of scale, and
@@
     \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin6}\\
-    \caption{Same as figure~\ref{fig:atlaszhighmass49fb}, but for the CMS
+    \caption{Same as Fig.~\ref{fig:atlaszhighmass49fb}, but for the CMS
       double-differential Drell--Yan lepton pair measurement at a
@@
       peak, 60~GeV$<M_{\ell\bar\ell}<$120~GeV, above the mass peak,
-      120~GeV$<M_{\ell\bar\ell}<$200~GeV, and at very high invariant masses,
+      120~GeV$<M_{\ell\bar\ell}<$200~GeV, and at very high invarinat masses,
       200~GeV$<M_{\ell\bar\ell}<$1500~GeV.}
@@
 
-\paragraph{Top-quark pair production.} We now consider
+\paragraph{Top-quark pair production.}
 
@@
     \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TTM}
-    \caption{Same as figure~\ref{fig:atlaszhighmass49fb}, but for the ATLAS
-      differential top-quark pair measurement at a centre-of-mass energy of
+    \caption{Same as Fig.~\ref{fig:atlaszhighmass49fb}, but for the ATLAS
+      differential top-quark pair measuremen at a centre-of-mass energy of
       8~TeV~\cite{Aad:2015mbv}. Displayed are the distributions in the

### 2020-08-03 paper/sec-results.tex
Typos
I think that I've included MArco's comments to Sect.3

@@
 computing fast interpolation grids, accurate to NLO QCD and NLO QCD+EW,
-for a representative set of processes in which EW corrections are expected 
-to be sizeable. In order to consider some realistic kinematics for these
+for a representative set of processes in which EW corrections may have a
+sizeable effect on the accuracy of the theoretical predictions.
+In order to consider some realistic kinematics for these
 processes, we resort to measurements commonly devised for inclusion in PDF
@@
 Refs.~\cite{Baur:2001ze,Dittmaier:2009cr}. The process receives contributions
-from 12 (34) parton luminosities at NLO QCD (NLO QCD+EW), mainly from $q\bar{q}$
-scattering, see Appendix~\ref{app:lumis} for details.
+from 12 (34) parton luminosities at NLO QCD (NLO QCD+EW),
+see Appendix~\ref{app:lumis} for details.
 
@@
 The process receives contributions from
-6 (36) parton luminositites at NLO QCD (NLO QCD+EW), mainly from $gg$ fusion,
+6 (36) parton luminositites at NLO QCD (NLO QCD+EW), 
 see Appendix~\ref{app:lumis} for details.
@@
 Refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
-The process receives contributions from 100 (165) parton luminosities, mainly
-from $qg$ and $\bar{q}g$ scattering, see Appendix~\ref{app:lumis} for details.
+The process receives contributions from 100 (165) parton luminosities,
+see Appendix~\ref{app:lumis} for details.
 

### 2020-08-03 paper/sec-introduction.tex
Intro revised

@@
 sophisticated determination of the Parton Distribution Functions (PDFs) of the 
-proton~\cite{Gao:2017yyd}, on the other hand.
+proton~\cite{Gao:2017yyd,Ethier:2020way}, on the other hand.
 
@@
 of higher-order corrections in the electroweak (EW) and mixed QCD+EW theory has
-witnessed a comparatively less comprehensive progress. Nevertheless frameworks 
+also witnessed a comprehensive progress. Frameworks 
 were developed in which the QCD and EW couplings are simultaneously treated as 
@@
 determined~\cite{Schmidt:2015zda,Bertone:2017bme,Harland-Lang:2019pla}.
-The resulting relative PDF uncertainty---which accounts only for the
-uncertainty of the data and of residual methodology inefficiencies inherent to 
-each PDF determination---can be as low as 1\% at the EW
+Data points in kinematic regions where EW corrections are expected to affect
+the accuracy of the theoretical predictions are usually removed from the fits.
+The resulting relative PDF uncertainty --- which accounts only for the
+uncertainty of the data and of residual methodological inefficiencies inherent to 
+each PDF determination --- can be as low as 1\% at the EW
 scale~\cite{Ball:2017nwa}. Theoretical uncertainties, possibly of comparable 
@@
 into PDF uncertainties only very 
-recently~\cite{AbdulKhalek:2019bux,AbdulKhalek:2019ihb}. This has led to a 
-noticeable improvement of PDF accuracy, in terms of an overall
+recently~\cite{AbdulKhalek:2019bux,AbdulKhalek:2019ihb}. This has led to an 
+improvement of PDF accuracy, in terms of an overall
 better statistical quality of the fit, at the price of a modest deterioration 
@@
 In this paper we address the first of these two problems. Specifically, 
-we develop \textsc{PineAPPL}, a new library that provides a direct interface
+we develop \textsc{PineAPPL}, a new computer library that provides a direct interface
 from parton-level Monte Carlo event generators accurate up to NLO QCD+EW to
@@
 parton-shower. The library is included by default in 
-\textsc{MadGraph5\_aMC@NLO} (\textsc{mg5\_aMC@NLO} henceforth) within which it has
+\textsc{MadGraph5\_aMC@NLO} (\textsc{MG5\_aMC} henceforth) within which it has
 been designed and tested. However, it is suitable for use as a plugin in any 
@@
 \textsc{SHERPA}~\cite{Biedermann:2017yoi}. In this respect, \textsc{PineAPPL}
-supersedes the \textsc{aMCfast} interface~\cite{Bertone:2014zva} and complements
-the \textsc{MCgrid} interface~\cite{DelDebbio:2013kxa,Bothmann:2015dba}.
+supersedes \textsc{aMCfast}~\cite{Bertone:2014zva} and complements
+\textsc{MCgrid}~\cite{DelDebbio:2013kxa,Bothmann:2015dba}.
 
@@
 \textsc{PineAPPL}, we describe its features, we illustrate its operation, and we
-assess its performance. In section~\ref{sec:results}, by means of
-\textsc{mg5\_AMC@NLO} and \textsc{PineAPPL}, we compute fast interpolation grids for
-a representative set of data that is typically included in a fit of PDFs.
+assess its performance. In section~\ref{sec:results} we validate
+\textsc{PineAPPL} and demonstrate its capabilities by computing fast
+interpolation grids, accurate to NLO QCD and NLO QCD+EW, for a representative
+set of processes, usually included in PDF fits, for which EW corrections may
+have a sizeable effect on the accuracy of the theoretical predictions.
 In section~\ref{sec:doublecounting} we use these results to formulate more
@@
 however, remains beyond the scope of the current work. We provide our
-conclusions and an outlook in section~\ref{sec:conclusion}.
-
-%Outline a possible strategy to deal with EW correction in LHC observables 
-%(FSR, PHOTOS, dressed/born, ...).
+conclusions and an outlook in section~\ref{sec:conclusion}. Examples of
+installation and usage of \textsc{PineAPPL} are provided in
+appendix~\ref{app:pineappl}; appendix~\ref{app:lumis} collects the parton
+luminosities for each process considered in section~\ref{sec:results}; and
+appendix~\ref{app:add_plots} complements some of the results presented
+in section~\ref{sec:results}.

### 2020-08-03 paper/sec-pineappl.tex
Very very small tweaks in section 2

@@
 
-In this paper we present a new library called \textsc{PineAPPL}, which stores phase-space weights of a Monte Carlo (MC) integration of a fixed-order calculation independently from the chosen PDFs.
+\textsc{PineAPPL} is a new library which stores phase-space weights of a Monte Carlo (MC) integration of a fixed-order calculation independently from the chosen PDFs.
 This separates the task of producing predictions for observables into two steps: 1) the generation of the \emph{grids}, which is how the generated files are called, and 2) the convolution of those grids with a set of PDFs.
@@
 This puts \textsc{PineAPPL} in the same category as \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}.
-With respect to the capabilities of these computer codes, \textsc{PineAPPL} makes it possible for the first time to include also higher-order corrections due to electroweak (EW), and in general mixed QCD--EW, effects.
-Documenting this extension, and how to interface \textsc{PineAPPL} with a general-purpose matrix-element generator, is of the main interests of this paper.
+With respect to the capabilities of these computer codes, \textsc{PineAPPL} makes it possible for the first time to include also higher-order corrections due to EW, and in general mixed QCD--EW, effects.
+Documenting this extension, and how to interface \textsc{PineAPPL} with a general-purpose matrix-element generator, is the main interest of this paper.
 
@@
 
-We have interfaced \textsc{PineAPPL} with the new version (v3+) of \textsc{mg5\_aMC@NLO}~\cite{Alwall:2014hca,Frederix:2018nkq}\footnote{It can be downloaded from \url{https://code.launchpad.net/~amcblast/+junk/3.0.2}, and will soon be merged in the official code release.}, where it will replace the \textsc{aMCfast}~\cite{Bertone:2014zva} interface.
+We have interfaced \textsc{PineAPPL} with the new version (v3+) of \textsc{mg5\_aMC}~\cite{Alwall:2014hca,Frederix:2018nkq}\footnote{It can be downloaded from \url{https://code.launchpad.net/~amcblast/+junk/3.0.2}, and will soon be merged in the official code release.}, where it will replace the \textsc{aMCfast}~\cite{Bertone:2014zva} interface.
 Its usage is very similar to that of \textsc{mg5\_aMC v2}+\textsc{aMCfast}+\textsc{APPLgrid}.
@@
 See appendix~\ref{app:sample-runcard} for an example of a runcard.
-
 Building an interface for other MC generators poses no difficulties, see appendix~\ref{app:example-program} for a small example program.
@@
 \end{multline}
-The cross section shown above is differential w.r.t.\ the observable $\mathcal{O}$, which, in general, is a function of phase space and subject to the usual conditions (soft- and collinear safety, etc.).
+The cross section shown above is differential w.r.t.\ the observable $\mathcal{O}$, which, in general, is a function of phase space and subject to the usual conditions (soft and collinear safety, etc.).
 
@@
 The Ellis--Sexton scale $Q^2$, if chosen dynamically, depends on the phase space, but we assume the fractions $\xi_\mathrm{R}$ and $\xi_\mathrm{F}$ to be constants of phase space in any case.
-This allows variations around the central scale choice $\xi_\mathrm{R} = \xi_\mathrm{F} = 1$, but it does not allow changing the scale arbitrarily.
+This allows for variations around the central scale choice $\xi_\mathrm{R} = \xi_\mathrm{F} = 1$, but it does not otherwise allow for arbitrary changes of the scale.
 The terms with powers $m > 0$ and $n > 0$ vanish for the central scale choice and are only required for variations of the factorisation and renormalisation scales.
-To estimate the perturbative QCD uncertainty---no EW uncertainty is covered by this method---one typically uses a 7-point scale variation, which evaluates the cross section using the following values,
+To estimate the perturbative QCD uncertainty --- no EW uncertainty is covered by this method --- one typically uses a 7-point scale variation, which evaluates the cross section using the following values,
 \begin{equation}
@@
 
-The problem that \textsc{PineAPPL} solves can now be described: Approximately reconstruct the functions
+The problem that \textsc{PineAPPL} solves can now be described: approximately reconstruct the functions
 \begin{equation}
@@
 \end{equation}
-from a set of $N$ function evaluations for specific momentum fractions, scales, and values of the observable:
+from a set of $N$ function evaluations for specific momentum fractions, scales, and values of the observable
 \begin{equation}
@@
 Indeed, beyond LO, different kinematic contributions have to be considered (in ref.~\cite{Bertone:2014zva}, for example, they are labelled with an index $\alpha$, see eq.~(12) therein).
-In the FKS subtraction scheme~\cite{Frixione:1995ms,Frixione:1997np} employed in \textsc{mg5\_aMC@NLO} maximally one type of kinematics for each counterterm (soft, collinear, and soft-collinear) is needed, but this is not the general case.
+In the FKS subtraction scheme~\cite{Frixione:1995ms,Frixione:1997np} employed in \textsc{mg5\_aMC} maximally one type of kinematics for each counterterm (soft, collinear, and soft-collinear) is needed, but this is not the general case.
 In Catani--Seymour subtraction~\cite{Catani:1996jh}, for example, different dipoles have different phase spaces and therefore different scales.
-However, \textsc{PineAPPL} remains completely blind to this fact, and consistent treatment is ensured by correctly using the interface between \textsc{PineAPPL}, which fills each event into a grid using the \emph{numerical value} of $Q^2$.
+However, \textsc{PineAPPL} remains completely blind to this fact, and a consistent treatment is ensured by correctly using the interface between \textsc{PineAPPL}, which fills each event into a grid using the \emph{numerical value} of $Q^2$.
 
@@
 With increasing size also the speed of the convolution degrades, because it basically becomes bound by the speed with which the 4-tuples can be read from disk.
-However, due to the uncompressed nature of this representation it can serve as a intermediate format to develop and quickly cross check more space-efficient representations, which we will discuss next.
+However, due to the uncompressed nature of this representation it can serve as an intermediate format to develop and quickly cross check more space-efficient representations, which we will discuss next.
 
@@
 \end{equation}
-along each axis into a small numbers of bins and to insert the phase-space weights $w$ into the corresponding discrete bin.
+along each axis into a small number of bins and to insert the phase-space weights $w$ into the corresponding discrete bin.
 Using the bin centres and their values one already has a straightforward implementation of eq.~\eqref{eq:weight-map}, but given a finite number of bins usually yields an insufficient approximation for the cross section.

### 2020-08-03 paper/paper.tex
MOre on Sect. 3
Typos
Abstract

@@
 \usepackage[percent]{overpic}
+\usepackage[section]{placeins}
 \usepackage{mathcomp}
@@
 
-\abstract{We introduce \textsc{PineAPPL}, a computer library that makes it possible to produce fast-interpolation 
+\abstract{We introduce \textsc{PineAPPL}, a computer library that makes it possible to produce interpolation 
 grids for fitting parton distribution functions (PDFs)

### 2020-08-03 paper/sec-introduction.tex
Fast-interpolation

@@
 the solution of two separate problems. First, a problem of efficiency:
-fast interpolation grids should be constructed, whereby partonic matrix 
+fast-interpolation grids should be constructed, whereby partonic matrix 
 elements, accurate to NLO QCD+EW, are precomputed in such a way that the 
@@
 from parton-level Monte Carlo event generators accurate up to NLO QCD+EW to
-fast interpolation grids. The library supports variations of the factorisation
+fast-interpolation grids. The library supports variations of the factorisation
 and renormalisation scales, resummation, and matching with a photon- and/or
@@
 assess its performance. In section~\ref{sec:results} we validate
-\textsc{PineAPPL} and demonstrate its capabilities by computing fast
-interpolation grids, accurate to NLO QCD and NLO QCD+EW, for a representative
+\textsc{PineAPPL} and demonstrate its capabilities by computing fast-interpolation grids, accurate to NLO QCD and NLO QCD+EW, for a representative
 set of processes, usually included in PDF fits, for which EW corrections may

### 2020-08-03 paper/sec-results.tex
Fast-interpolation

--- 2020-08-01 paper/sec-results.tex
@@
 The process receives contributions from
-6 (36) parton luminosities at NLO QCD (NLO QCD+EW),
+6 (36) parton luminositites at NLO QCD (NLO QCD+EW), 
 see Appendix~\ref{app:lumis} for details.
@@
 The format of the plots is the same across all figures. The first panel
-displays the relative difference (in per mille) between the {\sc PineAPPL} and
+displays the relative difference (in permille) between the {\sc PineAPPL} and
 the {\sc MC} results for the central, upper and lower scale choices, for
@@
 first of all we validate the \textsc{PineAPPL} result: its relative difference
-with respect to the \textsc{MC} result is always below a fraction of per mille,
+with respect to the \textsc{MC} result is always below a fraction of permille,
 again irrespective of the accuracy of the theory, of the choice of scale, and
@@
     \caption{Same as figure~\ref{fig:atlaszhighmass49fb}, but for the ATLAS
-      differential top-quark pair measurement at a centre-of-mass energy of
+      differential top-quark pair measuremen at a centre-of-mass energy of
       8~TeV~\cite{Aad:2015mbv}. Displayed are the distributions in the

### 2020-08-03 paper/sec-results.tex
added discussion on recombination

@@
 We select the distribution, single-differential in the invariant mass of the
-lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of
-mass energy of 7~TeV in the high-mass region
+lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of-mass
+energy of 7~TeV in the high-mass region
 ($M_{\ell\bar\ell}>116$~GeV)~\cite{Aad:2013iua}.
@@
 The process receives contributions from
-6 (36) parton luminositites at NLO QCD (NLO QCD+EW), 
+6 (36) parton luminosities at NLO QCD (NLO QCD+EW),
 see Appendix~\ref{app:lumis} for details.
@@
 coupling is chosen consistently with the PDF set, $\alpha_s(M_Z)=0.118$.
+When relevant, final-state photons and massless charged fermions (leptons and light quarks) are recombined together 
+if they statisfy the condition $\Delta R_{f \gamma} < 0.1$. In this case the
+sum of their momenta is assigned to the charged fermion, and the photon is removed
+from the event. Kinematics observables and cuts are defined starting from recombined momenta. In 
+case we would have been interested also to jet-related observables,
+photons surviving the recombination should have to be clustered together with colored 
+partons.\footnote{For issues related to the definition of jets in presence of EW corrections,
+    see refs.~\cite{Frederix:2016ost,Denner:2019zfp}}
 
@@
 last respect, we consider by default high-statistics computations, whereby we
-require a relative Monte Carlo precision of a fraction of permille. While
+require a relative Monte Carlo precision of a fraction of per mille. While
 this choice does not affect the validation of the \textsc{PineAPPL} result
@@
 The format of the plots is the same across all figures. The first panel
-displays the relative difference (in permille) between the {\sc PineAPPL} and
+displays the relative difference (in per mille) between the {\sc PineAPPL} and
 the {\sc MC} results for the central, upper and lower scale choices, for
@@
 first of all we validate the \textsc{PineAPPL} result: its relative difference
-with respect to the \textsc{MC} result is always below a fraction of permille,
+with respect to the \textsc{MC} result is always below a fraction of per mille,
 again irrespective of the accuracy of the theory, of the choice of scale, and
@@
       peak, 60~GeV$<M_{\ell\bar\ell}<$120~GeV, above the mass peak,
-      120~GeV$<M_{\ell\bar\ell}<$200~GeV, and at very high invarinat masses,
+      120~GeV$<M_{\ell\bar\ell}<$200~GeV, and at very high invariant masses,
       200~GeV$<M_{\ell\bar\ell}<$1500~GeV.}
@@
     \caption{Same as figure~\ref{fig:atlaszhighmass49fb}, but for the ATLAS
-      differential top-quark pair measuremen at a centre-of-mass energy of
+      differential top-quark pair measurement at a centre-of-mass energy of
       8~TeV~\cite{Aad:2015mbv}. Displayed are the distributions in the

### 2020-08-04 paper/sec-results.tex
Use siunitx macros for better spacing
- the SI macro can be used both in- and outside math mode and produces
  the correct spacing between figure and its unit
- the SI range macro does the same for a range of numbers

@@
 lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of-mass
-energy of 7~TeV in the high-mass region
-($M_{\ell\bar\ell}>116$~GeV)~\cite{Aad:2013iua}.
+energy of \SI{7}{\tera\electronvolt} in the high-mass region
+($M_{\ell\bar\ell}>\SI{116}{\giga\electronvolt}$)~\cite{Aad:2013iua}.
 We also select the distributions, double-differential in the rapidity and in
@@
 measured by the CMS experiment at a centre-of-mass energy of
-7~TeV~\cite{Chatrchyan:2013tia}.
+\SI{7}{\tera\electronvolt}~\cite{Chatrchyan:2013tia}.
 These measurements are currently included as standard in the
@@
 pair, $m_{t\bar t}$, measured by the ATLAS and CMS experiments at a centre-of-mass
-energy of 8~TeV~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
+energy of \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
 been extensively studied in the context of PDF fits in
@@
 the $Z$ boson, $p_T^Z$, measured by the CMS experiment at a centre-of-mass
-energy of 13~TeV~\cite{Sirunyan:2019bzr}. So far, this measurement has not been
+energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. So far, this measurement has not been
 included in any PDF determination. Because it has sub-percent uncertainties,
@@
 from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
-experiments at a centre-of-mass energy of 8~TeV, were partly included (upon
+experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt}, were partly included (upon
 selection of an appropriate kinematic cut that excluded bins with large EW
@@
 experimental analyses. In the case of high-mass Drell--Yan lepton pair
-production at 7~TeV measured by ATLAS, we require $p_T^\ell>25$~GeV,
-$|\eta_\ell|<2.5$ and 116~GeV$<M_{\ell\bar\ell}<$ 1500~GeV for the transverse
+production at \SI{7}{\tera\electronvolt} measured by ATLAS, we require $p_T^\ell>\SI{25}{\giga\electronvolt}$,
+$|\eta_\ell|<2.5$ and $\SI{116}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the transverse
 momentum and the rapidity of each lepton and for the invariant mass of the
@@
 lepton-pair production
-at 7~TeV measured by CMS, we require $p_T^{\ell_1}>14$~GeV, $p_T^{\ell_2}>9$~GeV,
-$|\eta_\ell|<2.4$, $|\eta_{\ell\bar\ell}|<2.4$ and 20~GeV$<M_{\ell\bar\ell}<$ 1500~GeV
+at \SI{7}{\tera\electronvolt} measured by CMS, we require $p_T^{\ell_1}>\SI{14}{\giga\electronvolt}$, $p_T^{\ell_2}>\SI{9}{\giga\electronvolt}$,
+$|\eta_\ell|<2.4$, $|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$
 for the transverse momentum and the rapidity of each lepton, and for the
 rapidity and the invariant mass of the lepton pair. In the case of $Z$-boson
-production with non-zero transverse momentum at 13~TeV measured by CMS, we
-require $p_T^\ell>25$~GeV, $|\eta_\ell|<2.4$,
-$M_Z-15$~GeV$<M_{\ell\bar\ell}<M_Z+20$~GeV,
-$|\eta_{\ell\bar\ell}|<2.4$ and 20~GeV$<p_T^{\ell\bar\ell}<1500$~GeV for the
+production with non-zero transverse momentum at \SI{13}{\tera\electronvolt} measured by CMS, we
+require $p_T^\ell>\SI{25}{\giga\electronvolt}$, $|\eta_\ell|<2.4$,
+$M_Z-\SI{15}{\giga\electronvolt}<M_{\ell\bar\ell}<M_Z+\SI{20}{\giga\electronvolt}$,
+$|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<p_T^{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the
 transverse momentum and rapidity of each lepton, and for the invariant mass,
@@
 We first consider the single-differential measurement at a high lepton-pair
-invariant mass performed by the ATLAS experiment at 7 TeV. 
+invariant mass performed by the ATLAS experiment at \SI{7}{\tera\electronvolt}.
 From figure~\ref{fig:atlaszhighmass49fb} we immediately
@@
       high-mass Drell--Yan lepton pair measurement in the high-mass region at
-      a centre-of-mass energy of 7 TeV~\cite{Aad:2013iua}. The first panel
+      a centre-of-mass energy of \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The first panel
       displays the relative difference (in per mille) between the {\sc PineAPPL}
@@
 leading (next-to-leading) contribution comes from a $u\bar{u}$ ($d\bar{d}$)
-parton luminosity, which accounts for about 55\% (49\%) of the cross section
-for the lowest invariant mass bins, and 68\% (22\%) for the largest invariant
-mass bins. The PI contribution raises from about 1.3\% in the lowest bin to
-about 3.6\% in the highest bin. Overall, the EW corrections range between 5\%
-around $M_{\ell\bar\ell}\sim 150$~GeV, 2\%-3\% for intermediate invariant mass
-values, $150~\textrm{GeV}\lesssim M_{\ell\bar\ell}\lesssim 700~\textrm{GeV}$, and
-15\%-20\% for the argest invariant mass bin, $M_{\ell\bar\ell}>1000$~GeV,
+parton luminosity, which accounts for about \SI{55}{\percent} (\SI{49}{\percent}) of the cross section
+for the lowest invariant mass bins, and \SI{68}{\percent} (\SI{22}{\percent}) for the largest invariant
+mass bins. The PI contribution raises from about \SI{1.3}{\percent} in the lowest bin to
+about \SI{3.6}{\percent} in the highest bin. Overall, the EW corrections range between \SI{5}{\percent}
+around $M_{\ell\bar\ell}\sim \SI{150}{\giga\electronvolt}$, \SIrange{2}{3}{\percent} for intermediate invariant mass
+values, $\SI{150}{\giga\electronvolt}\lesssim M_{\ell\bar\ell}\lesssim \SI{700}{\giga\electronvolt}$, and
+\SIrange{15}{20}{\percent} for the argest invariant mass bin, $M_{\ell\bar\ell}>\SI{1000}{\giga\electronvolt}$,
 see figure~\ref{fig:atlaszhighmass49fb}. For this reason, the data points with
-$M_{\ell\bar\ell}>210$~GeV were not included in the NNPDF3.1
+$M_{\ell\bar\ell}>\SI{210}{\giga\electronvolt}$ were not included in the NNPDF3.1
 analysis~\cite{Ball:2017nwa}.
@@
 We then turn our attention to the double-differential measurement performed by
-the CMS experiment at 7~TeV. For illustrative purposes, we report only four out
+the CMS experiment at \SI{7}{\tera\electronvolt}. For illustrative purposes, we report only four out
 of the six invariant mass bins, respectively below the $Z$-boson mass peak,
-45~GeV$<M_{\ell\bar\ell}<$60~GeV, on the $Z$-boson mass peak,
-60~GeV$<M_{\ell\bar\ell}<$120~GeV, above the mass peak,
-120~GeV$<M_{\ell\bar\ell}<$200~GeV, and at very high invariant masses,
-200~GeV$<M_{\ell\bar\ell}<$1500~GeV, see figure~\ref{fig:cmsdy2d11_bins3456}.
+$\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$, on the $Z$-boson mass peak,
+$\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$, above the mass peak,
+$\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$, and at very high invariant masses,
+$\SI{200}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$, see figure~\ref{fig:cmsdy2d11_bins3456}.
 Analogous plots for the remaining low invariant mass bins are collected in
@@
       double-differential Drell--Yan lepton pair measurement at a
-      centre-of-mass energy of 7~TeV~\cite{Chatrchyan:2013tia}. Displayed are
+      centre-of-mass energy of \SI{7}{\tera\electronvolt}~\cite{Chatrchyan:2013tia}. Displayed are
       only two of the six invariant mass bins available, respectively below the
-      $Z$-boson mass peak, 45~GeV$<M_{\ell\bar\ell}<$60~GeV, on the $Z$-boson mass
-      peak, 60~GeV$<M_{\ell\bar\ell}<$120~GeV, above the mass peak,
-      120~GeV$<M_{\ell\bar\ell}<$200~GeV, and at very high invariant masses,
-      200~GeV$<M_{\ell\bar\ell}<$1500~GeV.}
+      $Z$-boson mass peak, $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$, on the $Z$-boson mass
+      peak, $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$, above the mass peak,
+      $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$, and at very high invariant masses,
+      $\SI{200}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$.}
     \label{fig:cmsdy2d11_bins3456}
@@
 measurement is also dominated by $q\bar{q}$ scattering. The leading
-(next-to-leading) contribution to the 45~GeV$<M_{\ell\bar\ell}<$60~GeV invariant
+(next-to-leading) contribution to the $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$ invariant
 mass bin comes from
-the $u\bar{u}$ ($d\bar{d}$) parton luminosity, which accounts for about 70\%
-(22\%) of the double differential cross section, with small fluctuations across
-the rapidity range. The PI contribution decreases from about 4\% at zero
-rapidity to 1.5\% in the largest rapidity bin. The situation is slightly
-different in the 60~GeV$<M_{\ell\bar\ell}<$120~GeV invariant mass bin, where the
+the $u\bar{u}$ ($d\bar{d}$) parton luminosity, which accounts for about \SI{70}{\percent}
+(\SI{22}{\percent}) of the double differential cross section, with small fluctuations across
+the rapidity range. The PI contribution decreases from about \SI{4}{\percent} at zero
+rapidity to \SI{1.5}{\percent} in the largest rapidity bin. The situation is slightly
+different in the $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$ invariant mass bin, where the
 leading (next-to-leading) contribution comes instead from the $d\bar{d}$
-($u\bar{u}$) parton luminosity, which accounts for about 60\% (44\%) of the
-double differential cross section at small rapidities, and for about 56\% (50\%)
+($u\bar{u}$) parton luminosity, which accounts for about \SI{60}{\percent} (\SI{44}{\percent}) of the
+double differential cross section at small rapidities, and for about \SI{56}{\percent} (\SI{50}{\percent})
 at large rapidities. In the remaining two invariant mass bins, the leading
 (next-to-leading) contribution comes again from the $u\bar{u}$ ($d\bar{d}$)
-parton luminosity, which accounts for about 69\%-95\% (38\%-30\%) and
-57\%-70\% (48\%-34\%) of the cross section, respectively for
-120~GeV$<M_{\ell\bar\ell}<$200~GeV and 200~GeV$<M_{\ell\bar\ell}<$1500~GeV in the
-corresponding rapidity intervals; PI contributions range between 7.3\%-1.2\%
-and 3.7\%-0.6\% in the two invariant mass bins, respectively, for increasing
+parton luminosity, which accounts for about \SIrange{69}{95}{\percent} (\SIrange{38}{30}{\percent}) and
+\SIrange{57}{70}{\percent} (\SIrange{48}{34}{\percent}) of the cross section, respectively for
+$\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$ and $\SI{200}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ in the
+corresponding rapidity intervals; PI contributions range between \SIrange{7.3}{1.2}{\percent}
+and \SIrange{3.7}{0.6}{\percent} in the two invariant mass bins, respectively, for increasing
 rapidity.
@@
 to NLO QCD) depends on the invariant mass bin. In the
-45~GeV$<M_{\ell\bar\ell}<$60~GeV region, they enhance the value of the cross
-section by about 11\% across all the rapidity range; in the
-60~GeV$<M_{\ell\bar\ell}<$120~GeV region, they suppress the value of the cross
-section by about 2\%, again across all the rapidity range; in the 
-120~GeV$<M_{\ell\bar\ell}<$200~GeV bin, the suppression is around 4\%-5\%; and in
-the 200~GeV$<M_{\ell\bar\ell}<$1500~GeV bin, the suppression increases further to
-about 6\%-7\% for rapidities $y_{\ell\bar\ell}<2.0$ and up to 20\%-40\% at forward
+$\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$ region, they enhance the value of the cross
+section by about \SI{11}{\percent} across all the rapidity range; in the
+$\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$ region, they suppress the value of the cross
+section by about \SI{2}{\percent}, again across all the rapidity range; in the
+$\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$ bin, the suppression is around \SIrange{4}{5}{\percent}; and in
+the $\SI{200}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ bin, the suppression increases further to
+about \SIrange{6}{7}{\percent} for rapidities $y_{\ell\bar\ell}<2.0$ and up to \SIrange{20}{40}{\percent} at forward
 rapidities. For this reason, for instance, the data points with
-$M_{\ell\bar\ell}>200$~GeV and $y_{\ell\bar\ell}>2.2$ were not included in the
+$M_{\ell\bar\ell}>\SI{200}{\giga\electronvolt}$ and $y_{\ell\bar\ell}>2.2$ were not included in the
 NNPDF3.1 analysis~\cite{Ball:2017nwa}.
@@
 than the data uncertainty, except for the invariant mass bin 
-45~GeV$<M_{\ell\bar\ell}<$60~GeV, where the shift due to the EW correction
+$\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$, where the shift due to the EW correction
 overshoots the data uncertainty by about a factor of ten, and at large
@@
 uncertainty, the size of the EW correction is similar, except on the $Z$-boson
-mass peak, 60~GeV$<M_{\ell\bar\ell}<$120~GeV, where the scale uncertainty exceeds
+mass peak, $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$, where the scale uncertainty exceeds
 the size of the EW correction by about a factor of five. These facts confirm,
@@
       differential top-quark pair measurement at a centre-of-mass energy of
-      8~TeV~\cite{Aad:2015mbv}. Displayed are the distributions in the
+      \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv}. Displayed are the distributions in the
       transverse momentum of the top quark $p_T^t$ (left), and in the invariant

### 2020-08-04 paper/sec-results.tex
Use alphas macro for strong coupling

@@
 the process has a single LO, $\mathcal{O}(\alpha^2)$; at NLO, the
-QCD contribution is $\mathcal{O}(\alpha_s\alpha^2)$, while the EW contribution
+QCD contribution is $\mathcal{O}(\alphas\alpha^2)$, while the EW contribution
 is $\mathcal{O}(\alpha^3)$. The latter is not included in the NLO
@@
 in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. The process receives
-pure QCD contributions at LO, $\mathcal{O}(\alpha_s^2)$, and
-at NLO, $\mathcal{O}(\alpha_s^3)$. They make up the NLO QCD
+pure QCD contributions at LO, $\mathcal{O}(\alphas^2)$, and
+at NLO, $\mathcal{O}(\alphas^3)$. They make up the NLO QCD
 computation. The NLO QCD+EW computation includes the LO contribution
-$\mathcal{O}(\alpha_s\alpha)$ and the NLO contributions
-$\mathcal{O}(\alpha_s^2\alpha)$ and $\mathcal{O}(\alpha_s\alpha^2)$.
+$\mathcal{O}(\alphas\alpha)$ and the NLO contributions
+$\mathcal{O}(\alphas^2\alpha)$ and $\mathcal{O}(\alphas\alpha^2)$.
 We do not consider the LO contribution $\mathcal{O}(\alpha^2)$ and the
@@
 the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
-single LO contribution $\mathcal{O}(\alpha_s\alpha^2)$ and a single NLO
-contribution $\mathcal{O}(\alpha_s^2\alpha^2)$. In the NLO QCD+EW computation,
+single LO contribution $\mathcal{O}(\alphas\alpha^2)$ and a single NLO
+contribution $\mathcal{O}(\alphas^2\alpha^2)$. In the NLO QCD+EW computation,
 we supplement these with the LO and NLO EW corrections,
 $\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alpha^4)$, and with the NLO
-QCD-EW mixed correction, $\mathcal{O}(\alpha_s\alpha^3)$. EW corrections for
+QCD-EW mixed correction, $\mathcal{O}(\alphas\alpha^3)$. EW corrections for
 this process were computed in
@@
 the $W$-boson and of the $Z$-boson, respectively. The value of the strong
-coupling is chosen consistently with the PDF set, $\alpha_s(M_Z)=0.118$.
+coupling is chosen consistently with the PDF set, $\alphas(M_Z)=0.118$.
 When relevant, final-state photons and massless charged fermions (leptons and light quarks) are recombined together 

### 2020-08-04 paper/sec-results.tex
Fix particle and observable names

@@
 We select the distributions, single-differential in either the transverse
-momentum of the top quark, $p_T^t$, or the invariant mass of the top-quark
-pair, $m_{t\bar t}$, measured by the ATLAS and CMS experiments at a centre-of-mass
+momentum of the top quark, $p_\mathrm{T}^\mathrm{t}$, or the invariant mass of the top-quark
+pair, $m_{\mathrm{t}\bar{\mathrm{t}}}$, measured by the ATLAS and CMS experiments at a centre-of-mass
 energy of \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
@@
 
-\paragraph{$Z$-boson production with non-zero transverse momentum.}
+\paragraph{Z-boson production with non-zero transverse momentum.}
 We select the distribution, single-differential in the transverse momentum of
-the $Z$ boson, $p_T^Z$, measured by the CMS experiment at a centre-of-mass
+the Z boson, $p_\mathrm{T}^\mathrm{Z}$, measured by the CMS experiment at a centre-of-mass
 energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. So far, this measurement has not been
@@
 
-The central values of the renormalisation and factorisation scales, $\mu_R$ and
-$\mu_F$, are chosen, for each process, as follows. In the case of Drell--Yan
-lepton pair production, we use the fixed scale $\mu_R=\mu_F=M_Z$, where $M_Z$ is
-the mass of the $Z$-boson, for the ATLAS measurement, and the scale
-$\mu_R=\mu_F=M_{\ell\bar\ell}$, where $M_{\ell\bar\ell}$ is the central value of each
+The central values of the renormalisation and factorisation scales, $\mu_\mathrm{R}$ and
+$\mu_\mathrm{F}$, are chosen, for each process, as follows. In the case of Drell--Yan
+lepton pair production, we use the fixed scale $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$, where $M_\mathrm{Z}$ is
+the mass of the Z-boson, for the ATLAS measurement, and the scale
+$\mu_\mathrm{R}=\mu_\mathrm{F}=M_{\ell\bar\ell}$, where $M_{\ell\bar\ell}$ is the central value of each
 invariant mass bin, for the CMS measurement.
 In the case of top-quark pair production, we use the dynamic scales
-$\mu_R=\mu_F=\sqrt{m_t^2+(p_T^t)^2}{\Big /}2$ for the distribution differential
-in the transverse momentum of the top quark, and $\mu_R=\mu_F=H_T/4$ for the
+$\mu_\mathrm{R}=\mu_\mathrm{F}=\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^\mathrm{t})^2}{\Big /}2$ for the distribution differential
+in the transverse momentum of the top quark, and $\mu_\mathrm{R}=\mu_\mathrm{F}=H_\mathrm{T}/4$ for the
 distribution differential in the invariant mass of the top-quark pair, where
-$H_T=\sqrt{m_t^2+(p_T^t)^2}+\sqrt{m_t^2+(p_T^{\bar{t}})}$, with $m_t$,
-$p_T^t$ and $p_T^{\bar t}$ the mass of the top quark and the transverse momenta
+$H_\mathrm{T}=\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^\mathrm{t})^2}+\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^{\bar{\mathrm{t}}})}$, with $m_\mathrm{t}$,
+$p_\mathrm{T}^\mathrm{t}$ and $p_\mathrm{T}^{\bar{\mathrm{t}}}$ the mass of the top quark and the transverse momenta
 of the top and antitop quarks, respectively. These choices were demonstrated
 to maximise the convergence of the perturbative expansion~\cite{Czakon:2016dgf}.
-In the case of $Z$-boson production with non-zero transverse momentum, we use
-$\mu_R=\mu_F=M_Z$. In order to estimate the missing higher-order uncertainty,
+In the case of Z-boson production with non-zero transverse momentum, we use
+$\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$. In order to estimate the missing higher-order uncertainty,
 we allow the events to be reweighted in the Monte Carlo generation upon scale
@@
 \end{equation}
-where $M_W$, $M_Z$ and $m_t$ are the values of the $W$-boson, $Z$-boson and
-top quark masses, respectively, and $\Gamma_W$ and $\Gamma_Z$ are the width of
-the $W$-boson and of the $Z$-boson, respectively. The value of the strong
-coupling is chosen consistently with the PDF set, $\alphas(M_Z)=0.118$.
+where $M_\mathrm{W}$, $M_\mathrm{Z}$ and $m_\mathrm{t}$ are the values of the W-boson, Z-boson and
+top quark masses, respectively, and $\Gamma_\mathrm{W}$ and $\Gamma_\mathrm{Z}$ are the width of
+the W-boson and of the Z-boson, respectively. The value of the strong
+coupling is chosen consistently with the PDF set, $\alphas(M_\mathrm{Z})=0.118$.
 When relevant, final-state photons and massless charged fermions (leptons and light quarks) are recombined together 
@@
 experimental analyses. In the case of high-mass Drell--Yan lepton pair
-production at \SI{7}{\tera\electronvolt} measured by ATLAS, we require $p_T^\ell>\SI{25}{\giga\electronvolt}$,
+production at \SI{7}{\tera\electronvolt} measured by ATLAS, we require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$,
 $|\eta_\ell|<2.5$ and $\SI{116}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the transverse
@@
 lepton-pair production
-at \SI{7}{\tera\electronvolt} measured by CMS, we require $p_T^{\ell_1}>\SI{14}{\giga\electronvolt}$, $p_T^{\ell_2}>\SI{9}{\giga\electronvolt}$,
+at \SI{7}{\tera\electronvolt} measured by CMS, we require $p_\mathrm{T}^{\ell_1}>\SI{14}{\giga\electronvolt}$, $p_\mathrm{T}^{\ell_2}>\SI{9}{\giga\electronvolt}$,
 $|\eta_\ell|<2.4$, $|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$
 for the transverse momentum and the rapidity of each lepton, and for the
-rapidity and the invariant mass of the lepton pair. In the case of $Z$-boson
+rapidity and the invariant mass of the lepton pair. In the case of Z-boson
 production with non-zero transverse momentum at \SI{13}{\tera\electronvolt} measured by CMS, we
-require $p_T^\ell>\SI{25}{\giga\electronvolt}$, $|\eta_\ell|<2.4$,
-$M_Z-\SI{15}{\giga\electronvolt}<M_{\ell\bar\ell}<M_Z+\SI{20}{\giga\electronvolt}$,
-$|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<p_T^{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the
+require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$, $|\eta_\ell|<2.4$,
+$M_\mathrm{Z}-\SI{15}{\giga\electronvolt}<M_{\ell\bar\ell}<M_\mathrm{Z}+\SI{20}{\giga\electronvolt}$,
+$|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<p_\mathrm{T}^{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the
 transverse momentum and rapidity of each lepton, and for the invariant mass,
@@
 
-The measurement is mainly driven by $q\bar q$ scattering: specifically, the
-leading (next-to-leading) contribution comes from a $u\bar{u}$ ($d\bar{d}$)
+The measurement is mainly driven by $\mathrm{q}\bar{\mathrm{q}}$ scattering: specifically, the
+leading (next-to-leading) contribution comes from a $\mathrm{u}\bar{\mathrm{u}}$ ($\mathrm{d}\bar{\mathrm{d}}$)
 parton luminosity, which accounts for about \SI{55}{\percent} (\SI{49}{\percent}) of the cross section
@@
 the CMS experiment at \SI{7}{\tera\electronvolt}. For illustrative purposes, we report only four out
-of the six invariant mass bins, respectively below the $Z$-boson mass peak,
-$\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$, on the $Z$-boson mass peak,
+of the six invariant mass bins, respectively below the Z-boson mass peak,
+$\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$, on the Z-boson mass peak,
 $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$, above the mass peak,
@@
       only two of the six invariant mass bins available, respectively below the
-      $Z$-boson mass peak, $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$, on the $Z$-boson mass
+      Z-boson mass peak, $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$, on the Z-boson mass
       peak, $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$, above the mass peak,
@@
 As in the case of the ATLAS high-mass Drell--Yan measurement, the CMS
-measurement is also dominated by $q\bar{q}$ scattering. The leading
+measurement is also dominated by $\mathrm{q}\bar{\mathrm{q}}$ scattering. The leading
 (next-to-leading) contribution to the $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$ invariant
 mass bin comes from
-the $u\bar{u}$ ($d\bar{d}$) parton luminosity, which accounts for about \SI{70}{\percent}
+the $\mathrm{u}\bar{\mathrm{u}}$ ($\mathrm{d}\bar{\mathrm{d}}$) parton luminosity, which accounts for about \SI{70}{\percent}
 (\SI{22}{\percent}) of the double differential cross section, with small fluctuations across
@@
 different in the $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$ invariant mass bin, where the
-leading (next-to-leading) contribution comes instead from the $d\bar{d}$
-($u\bar{u}$) parton luminosity, which accounts for about \SI{60}{\percent} (\SI{44}{\percent}) of the
+leading (next-to-leading) contribution comes instead from the $\mathrm{d}\bar{\mathrm{d}}$
+($\mathrm{u}\bar{\mathrm{u}}$) parton luminosity, which accounts for about \SI{60}{\percent} (\SI{44}{\percent}) of the
 double differential cross section at small rapidities, and for about \SI{56}{\percent} (\SI{50}{\percent})
 at large rapidities. In the remaining two invariant mass bins, the leading
-(next-to-leading) contribution comes again from the $u\bar{u}$ ($d\bar{d}$)
+(next-to-leading) contribution comes again from the $\mathrm{u}\bar{\mathrm{u}}$ ($\mathrm{d}\bar{\mathrm{d}}$)
 parton luminosity, which accounts for about \SIrange{69}{95}{\percent} (\SIrange{38}{30}{\percent}) and
@@
 lead to an improvement in their overall description. In comparison to the scale
-uncertainty, the size of the EW correction is similar, except on the $Z$-boson
+uncertainty, the size of the EW correction is similar, except on the Z-boson
 mass peak, $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$, where the scale uncertainty exceeds
 the size of the EW correction by about a factor of five. These facts confirm,
-as expected, that EW corrections are almost immaterial at the $Z$-boson mass
+as expected, that EW corrections are almost immaterial at the Z-boson mass
 peak, but that NNLO QCD corrections are otherwise as relevant as NLO QCD+EW
@@
       \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv}. Displayed are the distributions in the
-      transverse momentum of the top quark $p_T^t$ (left), and in the invariant
-      mass of the top-quark pair $m_{t\bar{t}}$ (right).}
+      transverse momentum of the top quark $p_\mathrm{T}^\mathrm{t}$ (left), and in the invariant
+      mass of the top-quark pair $m_{\mathrm{t}\bar{\mathrm{t}}}$ (right).}
     \label{fig:atlastop}
@@
 
-\paragraph{$Z$-boson production with non-zero transverse momentum.}
+\paragraph{Z-boson production with non-zero transverse momentum.}
 
@@
     \includegraphics[width=0.5\textwidth]{figures/pineappl_CMS_Z_13_TEV}
-    \caption{PineAPPL comparison for CMS $Z$ $p_T$ distribution.}
+    \caption{PineAPPL comparison for CMS Z $p_\mathrm{T}$ distribution.}
     \label{fig:cmsZ13TeV}

### 2020-08-04 paper/sec-results.tex
Fix spelling and typsetting

@@
 from 12 (34) parton luminosities at NLO QCD (NLO QCD+EW),
-see Appendix~\ref{app:lumis} for details.
+see appendix~\ref{app:lumis} for details.
 
@@
 6 (36) parton luminosities at NLO QCD (NLO QCD+EW),
-see Appendix~\ref{app:lumis} for details.
+see appendix~\ref{app:lumis} for details.
 
@@
 The process receives contributions from 100 (165) parton luminosities,
-see Appendix~\ref{app:lumis} for details.
+see appendix~\ref{app:lumis} for details.
 
@@
 lepton pair production, we use the fixed scale $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$, where $M_\mathrm{Z}$ is
-the mass of the Z-boson, for the ATLAS measurement, and the scale
+the mass of the Z boson, for the ATLAS measurement, and the scale
 $\mu_\mathrm{R}=\mu_\mathrm{F}=M_{\ell\bar\ell}$, where $M_{\ell\bar\ell}$ is the central value of each
@@
 \textsc{PineAPPL} allows the user to determine the envelope with any point
-prescription, see Appendix~\ref{app:pineappl-demo} for an example.
+prescription, see appendix~\ref{app:pineappl-demo} for an example.
 
@@
 \end{equation}
-where $M_\mathrm{W}$, $M_\mathrm{Z}$ and $m_\mathrm{t}$ are the values of the W-boson, Z-boson and
+where $M_\mathrm{W}$, $M_\mathrm{Z}$ and $m_\mathrm{t}$ are the values of the W-boson, Z-boson, and
 top quark masses, respectively, and $\Gamma_\mathrm{W}$ and $\Gamma_\mathrm{Z}$ are the width of
-the W-boson and of the Z-boson, respectively. The value of the strong
+the W boson and of the Z boson, respectively. The value of the strong
 coupling is chosen consistently with the PDF set, $\alphas(M_\mathrm{Z})=0.118$.
 When relevant, final-state photons and massless charged fermions (leptons and light quarks) are recombined together 
-if they statisfy the condition $\Delta R_{f \gamma} < 0.1$. In this case the
+if they satisfy the condition $\Delta R_{f \gamma} < 0.1$. In this case the
 sum of their momenta is assigned to the charged fermion, and the photon is removed
@@
 case we would have been interested also to jet-related observables,
-photons surviving the recombination should have to be clustered together with colored 
+photons surviving the recombination should have to be clustered together with coloured
 partons.\footnote{For issues related to the definition of jets in presence of EW corrections,
@@
 specified in section~\ref{subsec:computational_settings}. In the following, we
-will refer to the first result as the \textsc{MC} result, and to the second as
+will refer to the first result as the MC result, and to the second as
 the \textsc{PineAPPL} result. We repeat the computation for theories accurate
@@
 this choice does not affect the validation of the \textsc{PineAPPL} result
-against the \textsc{MC} result, it ensures that the statistical uncertainty of
+against the MC result, it ensures that the statistical uncertainty of
 the computation remains negligible in comparison to the PDF and scale
@@
 We present these comparisons in
-figures~\ref{fig:atlaszhighmass49fb}-\ref{fig:cmsZ13TeV} for each of the processes
+figures~\ref{fig:atlaszhighmass49fb}--\ref{fig:cmsZ13TeV} for each of the processes
 and data sets outlined in section~\ref{subsec:processes_and_measurements}.
@@
 displays the relative difference (in per mille) between the {\sc PineAPPL} and
-the {\sc MC} results for the central, upper and lower scale choices, for
+the MC results for the central, upper and lower scale choices, for
 theories accurate to both NLO QCD and NLO QCD+EW. The following three panels
@@
       displays the relative difference (in per mille) between the {\sc PineAPPL}
-      and the {\sc MC} results for the central, upper and lower scale choices,
+      and the MC results for the central, upper and lower scale choices,
       for theories accurate to both NLO QCD and NLO QCD+EW. The second, third
@@
 values, $\SI{150}{\giga\electronvolt}\lesssim M_{\ell\bar\ell}\lesssim \SI{700}{\giga\electronvolt}$, and
-\SIrange{15}{20}{\percent} for the argest invariant mass bin, $M_{\ell\bar\ell}>\SI{1000}{\giga\electronvolt}$,
+\SIrange{15}{20}{\percent} for the largest invariant mass bin, $M_{\ell\bar\ell}>\SI{1000}{\giga\electronvolt}$,
 see figure~\ref{fig:atlaszhighmass49fb}. For this reason, the data points with
@@
 Analogous plots for the remaining low invariant mass bins are collected in
-Appendix~\ref{app:add_plots}. From figure~\ref{fig:cmsdy2d11_bins3456},
+appendix~\ref{app:add_plots}. From figure~\ref{fig:cmsdy2d11_bins3456},
 first of all we validate the \textsc{PineAPPL} result: its relative difference
-with respect to the \textsc{MC} result is always below a fraction of per mille,
+with respect to the MC result is always below a fraction of per mille,
 again irrespective of the accuracy of the theory, of the choice of scale, and

### 2020-08-04 paper/sec-doublecounting.tex
Add more typographical changes

@@
 at $\mathcal O(\alpha^2)$. Because this process is sometimes thought
-as a quark-initiated $s$-channel mechanism ($\mathrm{q} \bar{\mathrm{q}} \to \gamma^*/Z \to \ell \bar{\ell}$), in many analyses the photon-induced component,
+as a quark-initiated $s$-channel mechanism ($\mathrm{q} \bar{\mathrm{q}} \to \gamma^*/\mathrm{Z} \to \ell \bar{\ell}$), in many analyses the photon-induced component,
 $\gamma \gamma \to \ell \bar{\ell}$ in the $t$ channel, is considered to be a different process, and therefore as a background and subtracted.
@@
 While it is common sense that the QCD counterpart of this subtraction should never
-be performed---no one would 
-consider to \enquote{subtract} the gluon-initiated contribution to top-pair production in top analyses---seemingly it is not so
+be performed --- no one would
+consider to \enquote{subtract} the gluon-initiated contribution to top-pair production in top analyses --- seemingly it is not so
 when EW corrections are considered.

### 2020-08-04 paper/sec-introduction.tex
Add more typographical changes

@@
 uncertainty of the data and of residual methodological inefficiencies inherent to 
-each PDF determination --- can be as low as 1\% at the EW
+each PDF determination --- can be as low as \SI{1}{\percent} at the EW
 scale~\cite{Ball:2017nwa}. Theoretical uncertainties, possibly of comparable 
@@
 phase-space regions associated with large mass scales (roughly of the order
-of the \si{\tera\electronvolt}), where several LHC data sets (e.g.\ $Z$ boson transverse
-momentum distributions) enter both the determination of PDFs and the search
+of the \si{\tera\electronvolt}), where several LHC data sets (e.g.\ Z-boson
+transverse-momentum distributions) enter both the determination of PDFs and the search
 for New Physics.

### 2020-08-04 paper/app-pineappl.tex
Intro revised
Expand appendix A

--- 2020-07-20 paper/app-pineappl.tex
@@
-\section{More technical details about \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
-
-%\subsection{Efficiency of the grid representation}
-%\label{app:pineappl-representation-efficiency}
-%
-%Using a similar notation introduced in eq.~\eqref{eq:expansion}, we single out a specific NLO correction:
-%\begin{equation}
-%\begin{split}
-%\alphas^k \bigl( \mu_\mathrm{R}^2 \bigr) \alpha^l \Bigl[ \log \bigl( \mu_\mathrm{R}^2 \bigr) &W_{ab}^{(k,l,1,0)} (x_1, x_2) \\
-%+ \log \bigl( \mu_\mathrm{F}^2 \bigr) &W_{ab}^{(k,l,0,1)} (x_1, x_2) \\
-%&W_{ab}^{(k,l,0,0)} (x_1, x_2) \Bigr] \text{.}
-%\end{split}
-%\end{equation}
-%If we assume the case of a dynamic scale choice, i.e.\ $\mu_\mathrm{R}^2 \equiv \mu_\mathrm{R}^2 \bigl( x_1, x_2 \bigr)$ and $\mu_\mathrm{F}^2 \equiv \mu_\mathrm{F}^2 \bigl( x_1, x_2 \bigr)$,
+\section{Installation and usage of \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
+\label{app:pineappl}
 
@@
 On computers with a \texttt{bash} shell the installation is as simple as
-\begin{lstlisting}[language=bash]
-curl --proto '=https' --tlsv1.2 -sSf https://sh.rustup.rs | sh
-\end{lstlisting}
+\begin{verbatim}
+ $ curl --proto '=https' --tlsv1.2 -sSf https://sh.rustup.rs | sh
+\end{verbatim}
 which downloads the compiler \texttt{rustc}, the package manager \texttt{cargo}, and a few other helpful tools.
@@
 The command-line program \texttt{pineappl} is compiled and installed using
-\begin{lstlisting}[language=bash]
-cargo install pineappl_cli
-\end{lstlisting}
+\begin{verbatim}
+ $ cargo install pineappl_cli
+\end{verbatim}
 This program also needs \texttt{LHAPDF} \cite{Buckley:2014ana} installed.
@@
 For the C interface you need to first install \texttt{cargo-c},
-\begin{lstlisting}[language=bash]
-cargo install cargo-c
-\end{lstlisting}
+\begin{verbatim}
+ $ cargo install cargo-c
+\end{verbatim}
 and then download the \textsc{PineAPPL} repository, compile and finally install into it into a directory \texttt{\$prefix} as follows:
-\begin{lstlisting}[language=bash]
-git clone https://github.com/N3PDF/pineappl/
-cd pineappl_capi/
-cargo cinstall --release --prefix=${prefix}
-\end{lstlisting}
-The last line will install the C header \texttt{pineappl\_capi.h}, the library, and a pkg-config\footnote{A standard way on Linux to express how dependencies are compiled/linked against, see \url{https://www.freedesktop.org/wiki/Software/pkg-config/}} file (\texttt{pineappl\_capi.pc}).
+\begin{verbatim}
+ $ git clone https://github.com/N3PDF/pineappl/
+ $ cd pineappl_capi/
+ $ cargo cinstall --release --prefix=DIRECTORY
+\end{verbatim}
+The last line will install the C header \texttt{pineappl\_capi.h}, the library, and a pkg-config\footnote{A standard way on Linux to express how dependencies are compiled/linked against, see \url{https://www.freedesktop.org/wiki/Software/pkg-config/}} file (\texttt{pineappl\_capi.pc}) into the directory specified as \texttt{DIRECTORY}.
 Make sure that the environment variables \texttt{PATH}, \texttt{LD\_LIBRARY\_PATH}, and \texttt{PKG\_CONFIG\_PATH} are properly set.
 The latter is needed for \texttt{pkg-config -{}-cflags -{}-libs pineappl\_capi} to work, which prints the necessary compiler/linker flags.
-See App.~\ref{app:example-program} for an example.
+
+After being installed, you can compile and link against the library.
+See appendix~\ref{app:example-program} for an example.
 
@@
 
-\subsection{Drell--Yan \texorpdfstring{$n$}{n}-tuple storage size}
-\label{app:drell-yan-storage}
-
-TODO
-
 \subsection{Example Monte Carlo program}
 \label{app:example-program}
+
+% TODO: link to documentation
 
@@
 
-TODO
+The program \texttt{pineappl} can be used to perform quick convolutions and other calculations with existing grids on the command line.
+If started without any arguments, it prints its help and lists all supported subcommands:
+\begin{verbatim}
+ $ pineappl
+pineappl 0.2.0
+Read, write, and query PineAPPL grids
+
+USAGE:
+    pineappl <SUBCOMMAND>
+
+FLAGS:
+    -h, --help       Prints help information
+    -V, --version    Prints version information
+
+SUBCOMMANDS:
+    channels           Shows the contribution for each partonic channel
+    convolute          Convolutes a PineAPPL grid with a PDF set
+    diff               Compares the contents of two grids with each other
+    info               Shows information about the grid
+    luminosity         Shows the luminosity function
+    merge              Merges one or more PineAPPL grids together
+    orders             Shows the predictions for all bins for each order
+                       separately
+    pdf_uncertainty    Calculates PDF uncertainties
+\end{verbatim}
+
+\paragraph{Convolutions.}
+The most important subcommand is \texttt{convolute}, which performs a convolution of a single grid with a single or multiple PDF sets.
+As an example we show the grid produced for the ATLAS DY high-mass lepton-pair production from section~\ref{subsec:numerical_results}, convoluted with \texttt{NNPDF31\_nlo\_as\_0118\_luxqed} as the main PDF set and with \texttt{CT18NLO} as a second PDF set.
+\begin{verbatim}
+ $ pineappl convolute ATLASZHIGHMASS49FB.pineappl \
+ > NNPDF31_nlo_as_0118_luxqed CT18NLO
+bin xmin xmax     diff        integ    neg unc pos unc       CT18NLO
+---+----+----+------------+-----------+-------+-------+------------+------
+  0  116  130 2.0630698e-1  2.888297e0  -2.08%   1.69% 2.0246802e-1 -1.86%
+  1  130  150 9.1818985e-2  1.836379e0  -1.79%   1.86% 8.9766355e-2 -2.24%
+  2  150  170 4.5306370e-2 9.061274e-1  -1.60%   1.98% 4.4115960e-2 -2.63%
+  3  170  190 2.5894856e-2 5.178971e-1  -1.66%   2.06% 2.5138525e-2 -2.92%
+  4  190  210 1.6075267e-2 3.215053e-1  -1.70%   2.10% 1.5566535e-2 -3.16%
+  5  210  230 1.0526659e-2 2.105331e-1  -1.71%   2.12% 1.0173163e-2 -3.36%
+  6  230  250 7.1928162e-3 1.438563e-1  -1.71%   2.13% 6.9403972e-3 -3.51%
+  7  250  300 4.0776555e-3 2.038827e-1  -1.70%   2.44% 3.9255068e-3 -3.73%
+  8  300  400 1.4775481e-3 1.477548e-1  -1.94%   2.87% 1.4182754e-3 -4.01%
+  9  400  500 4.5473785e-4 4.547378e-2  -2.30%   3.19% 4.3525336e-4 -4.28%
+ 10  500  700 1.2164277e-4 2.432855e-2  -2.41%   3.12% 1.1612523e-4 -4.54%
+ 11  700 1000 1.9792340e-5 5.937701e-3  -2.05%   2.12% 1.8813113e-5 -4.95%
+ 12 1000 1500 2.0228761e-6 1.011438e-3  -1.29%   0.47% 1.9221978e-6 -4.98%
+\end{verbatim}
+The output shows all 13 bins with lower (\texttt{xmin}) and upper limit (\texttt{xmax}) of the invariant mass $M_{\ell \bar{\ell}}$ of the lepton pair, with the differential cross section $\mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}}$ (\texttt{diff}), integrated cross section $(M_{\ell \bar{\ell}}^\mathrm{max} - M_{\ell \bar{\ell}}^\mathrm{min}) \mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}}$ (\texttt{integ}), and the perturbative uncertainty estimated from a 7-point scale variation (envelope given by \texttt{neg unc} and \texttt{pos unc}).
+The uncertainty estimation can alternatively use a 3- or a 9-point scale variation using the optional program switch \texttt{-{}-scales 3} or \texttt{-{}-scales 9}, respectively.
+The (differential) results for the second PDF set (\texttt{CT18NLO}) is shown in absolute and relative (to first PDF set) numbers.
+
+\paragraph{Perturbative orders.}
+Often it is helpful to see the impact of the different perturbative orders to the cross section.
+The subcommand \texttt{orders} shows this:
+\begin{verbatim}
+ $ pineappl orders ATLASZHIGHMASS49FB.pineappl \
+ > NNPDF31_nlo_as_0118_luxqed
+bin xmin xmax     diff     O(as^0 a^2) O(as^1 a^2) O(as^0 a^3)
+---+----+----+------------+-----------+-----------+-----------
+  0  116  130 2.0630698e-1     100.00%      15.97%      -5.26%
+  1  130  150 9.1818985e-2     100.00%      18.07%      -4.29%
+  2  150  170 4.5306370e-2     100.00%      19.66%      -3.64%
+  3  170  190 2.5894856e-2     100.00%      20.69%      -3.21%
+  4  190  210 1.6075267e-2     100.00%      21.26%      -2.91%
+  5  210  230 1.0526659e-2     100.00%      21.48%      -2.85%
+  6  230  250 7.1928162e-3     100.00%      21.60%      -2.62%
+  7  250  300 4.0776555e-3     100.00%      21.36%      -2.75%
+  8  300  400 1.4775481e-3     100.00%      20.32%      -3.11%
+  9  400  500 4.5473785e-4     100.00%      17.83%      -3.65%
+ 10  500  700 1.2164277e-4     100.00%      14.04%      -4.68%
+ 11  700 1000 1.9792340e-5     100.00%       7.21%      -6.75%
+ 12 1000 1500 2.0228761e-6     100.00%      -3.05%      -9.99%
+\end{verbatim}
+The first four columns are the same as in \texttt{convolute}, and the remaining ones show all orders normalised to the sum of the leading orders, which in this case is only the $\mathcal{O} (\alpha^2)$.
+Absolute numbers are shown if the switch \texttt{-{}-absolute} or \texttt{-a} is passed to the program.
+
+\paragraph{Channels and Luminosity function.}
+Sometimes it is usuful to know which partons contribute the most and by how much.
+This is what the subcommand \texttt{channels} shows:
+\begin{verbatim}
+ $ pineappl channels ATLASZHIGHMASS49FB.pineappl \
+ > NNPDF31_nlo_as_0118_luxqed --limit 5
+bin xmin xmax lumi  size
+---+----+----+----+------+---+------+---+------+---+------+---+-----
+  0  116  130  #15 27.42%  #0 27.42%  #5 24.52% #20 24.51% #30 1.30%
+  1  130  150  #15 28.83%  #0 28.83%  #5 21.78% #20 21.78% #30 1.86%
+  2  150  170  #15 29.87%  #0 29.82%  #5 19.63% #20 19.62% #30 2.32%
+  3  170  190  #15 30.54%  #0 30.53% #20 18.17%  #5 18.13% #30 2.58%
+  4  190  210   #0 31.06% #15 31.04%  #5 17.07% #20 17.04% #30 2.75%
+  5  210  230   #0 31.46% #15 31.38% #20 16.27%  #5 16.24% #30 2.86%
+  6  230  250   #0 31.73% #15 31.64% #20 15.66%  #5 15.62% #30 2.91%
+  7  250  300   #0 32.07% #15 32.02%  #5 14.91% #20 14.86% #30 2.98%
+  8  300  400   #0 32.62% #15 32.56%  #5 13.83% #20 13.81% #30 2.98%
+  9  400  500  #15 33.14%  #0 33.12% #20 12.89%  #5 12.87% #30 2.93%
+ 10  500  700   #0 33.71% #15 33.31% #20 12.28%  #5 12.26% #30 2.93%
+ 11  700 1000  #15 34.08%  #0 33.71% #20 11.59%  #5 11.51% #30 3.06%
+ 12 1000 1500   #0 33.95% #15 33.88% #20 11.12%  #5 10.88% #30 3.56%
+\end{verbatim}
+The first three columns are known from \texttt{convolute}.
+The next columns (the switch \texttt{-{}-limit 5} limits the output to five columns) show first the channel index and then relative size of the corresponding contribution.
+Since the contribution of a partonic channel can be negative, the columns are sorted ignoring the sign of the contribution.
+The first line shows that for bin 0, i.e.\ for the range $\SI{116}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{130}{\giga\electronvolt}$, the cross section is dominated by partonic channel \texttt{\#15} (\SI{27.42}{\percent}), following by partonic channel \texttt{\#0}, then \texttt{\#5}, etc.
+The meaning of the channel numbers is given by using the subcommand \texttt{luminosity} (only an excerpt is shown):
+\begin{verbatim}
+id    entry
+--+------------+------------+------------
+0  1 × ( 2, -2) 1 × ( 4, -4)
+5  1 × ( 1, -1) 1 × ( 3, -3)
+15 1 × (-4,  4) 1 × (-2,  2)
+20 1 × (-3,  3) 1 × (-1,  1)
+30 1 × (22, 22)
+\end{verbatim}
+This shows that channel \texttt{\#0} represents the up-type quark--anti-quark contribution (shown with PDG id 2 and 4 for up and charm quarks, which have the same matrix elements), channel \texttt{\#15} is the same channel with initial states transposed, channels \texttt{\#5} and \texttt{\#20} are the down-type quark--anti-quark channels, and channel \texttt{\#30} is the photon--photon channel.
+The factors \texttt{1} are not important here, but in general they can contain CKM matrix elements that would otherwise not allow to share the matrix elements between different quark flavours.
 
@@
 
-TODO
+The following run card was used to produce the results shown in section~\ref{subsec:numerical_results}.
+The only difference to a normal \textsc{mg5\_aMC@NLO} run is the switch \texttt{set iappl 1}, which enables filling a \textsc{PineAPPL} grid.
+For a complete set of runcards and patches see TODO.
+
+\lstset{
+  basicstyle=\ttfamily\small,
+  showstringspaces=false,
+  commentstyle=\ttfamily\small,
+  keywordstyle=\ttfamily\small,
+  identifierstyle=\color{black},
+  stringstyle=\color{black},
+}
+
+\begin{verbatim}
+set complex_mass_scheme True
+import model loop_qcd_qed_sm_Gmu
+define p = p b b~
+define j = p
+generate p p > e+ e- [QCD QED]
+output @OUTPUT@
+launch @OUTPUT@
+fixed_order = ON
+set mz @MZ@
+set ymt @YMT@
+set ebeam1 3500
+set ebeam2 3500
+set pdlabel lhapdf
+set lhaid 324900
+set fixed_ren_scale True
+set fixed_fac_scale True
+set mur_ref_fixed @MZ@
+set muf_ref_fixed @MZ@
+set reweight_scale True
+set ptl = 25.0
+set etal = 2.5
+set mll = 116
+#user_defined_cut set mmllmax = 1500.0
+set req_acc_FO 0.0001
+set iappl 1
+done
+quit
+\end{verbatim}

### 2020-08-04 paper/sec-pineappl.tex
Add more typographical changes
Improve wording and fix a few mistakes
- takes care of Stefan's comments in points 3) and 4)

@@
 \end{equation}
-given by the MC integrator. Using eq.~\eqref{eq:expansion} and
+given by the MC integrator.
+Using eq.~\eqref{eq:expansion} and
 \begin{multline}
-\frac{\mathrm{d} \sigma}{\mathrm{d} \mathcal{O}} (\mathcal{O}, \xi_\mathrm{R}, \xi_\mathrm{R}) \\
-= \sum_{a,b} \int_0^1 \mathrm{d} x_1 \int_0^1 \mathrm{d} x_2 \int_{Q^2_\mathrm{min}}^{Q^2_\mathrm{max}} \mathrm{d} Q^2 \, f_a (x_1, \xi_\mathrm{F}^2 Q^2) f_b (x_2, \xi_\mathrm{F}^2 Q^2) \sigma_{ab} (x_1, x_2, Q^2, \xi_\mathrm{R}, \xi_\mathrm{R}) \text{,}
+\frac{\mathrm{d} \sigma}{\mathrm{d} \mathcal{O}} (\mathcal{O}, \xi_\mathrm{R}, \xi_\mathrm{F}) \\
+= \sum_{a,b} \int_0^1 \mathrm{d} x_1 \int_0^1 \mathrm{d} x_2 \int_{Q^2_\mathrm{min}}^{Q^2_\mathrm{max}} \mathrm{d} Q^2 \, f_a (x_1, \xi_\mathrm{F}^2 Q^2) f_b (x_2, \xi_\mathrm{F}^2 Q^2) \sigma_{ab} (x_1, x_2, Q^2, \xi_\mathrm{R}, \xi_\mathrm{F}) \text{,}
 \label{eq:pineappl-convolution}
@@
 
-In general, we define leading order (LO) as the set of all possible initial states $a b$ which lead to the same final state $X$, for which the sum of the coupling exponents in eq.~\eqref{eq:expansion} is smallest, i.e.\ $k + l = p$, where $p = \min (k+l)$.
+In general, we define leading order (LO) as the set of contributions for all possible initial states $a b$ that lead to the same final state $X$, for which the sum of the coupling exponents in eq.~\eqref{eq:expansion} is smallest, i.e.\ $k + l = p$, where $p = \min (k+l)$.
 This number is process dependent and usually determined by the number of external particles.
@@
 This includes the photon--photon initial state, which appears already at LO.
-In the corresponding Feynman diagrams all particles are colourless, so that this subprocess only receives EW and mixed QCD--EW corrections, but never (pure) QCD corrections.
+In the corresponding Feynman diagrams all particles are colourless, so that the photon--photon initiated contributions only receive EW and mixed QCD--EW corrections, but never (pure) QCD corrections.
 The EW corrections also introduce quark--photon contributions, in analogy of QCD corrections introducing quark--gluon contributions.

### 2020-08-04 paper/sec-doublecounting.tex
Improve wording and fix a few mistakes
- takes care of Stefan's comments in points 3) and 4)
Address most of Stefan's about the subtraction

@@
 by inverting a photon shower.
-The resulting dataset is e.g.\ referred to as \emph{pre-FSR} with observables defined in terms of \emph{Born-level electrons} (see e.g.\ Ref.~\cite{Aad:2015auj} for its definition).
+The resulting dataset is e.g.\ referred to as \emph{pre-FSR} with observables defined in terms of \emph{Born-level electrons} (see e.g.\ ref.~\cite{Aad:2015auj} for its definition).
 These datasets are needed for and correctly used in QCD-only PDF determinations, since the EW corrections to some DY observables can be significant, and excluding them would therefore degrade the quality of the fit.
 In fits including fixed-order EW corrections the problem with this definition is that the first photon emission is included exactly at the matrix-element level. The inclusion of
-subsequent emission would require the matching with the QED shower, which is not yet available for general processes. It is interesting
-to note that one can tune the QED parton shower in order to mimic NLO EW effects, so that a prediction only accurate at NLO
-QCD displays a remarkable agreement with another at NLO QCD+EW when the photonic shower is included (see example the behaviour of predictions showered with
-\textsc{Photos}~\cite{Barberio:1990ms,Barberio:1993qi,Golonka:2005pn} in Ref.~\cite{CarloniCalame:2016ouw}). However, this kind of agreement
-always comes \emph{a posteriori}, and cannot be ensured in general. A more physical definition would be either the one of bare leptons (the leptons as they emerge after FSR)
-or of recombined ones (leptons and photons are clustered together and their momenta are combined, in analogy with jets in QCD). The problem with the former is that 
+subsequent emission would require the matching with the QED shower, which is not yet available for general processes.
+
+It is interesting
+to note that one can tune the QED parton shower to specific decays to mimic NLO EW effects, so that a prediction only accurate at NLO
+QCD displays a remarkable agreement with another at NLO QCD+EW when the photonic shower is included (see for example the behaviour of predictions showered with
+\textsc{Photos}~\cite{Barberio:1990ms,Barberio:1993qi,Golonka:2005pn} in ref.~\cite{CarloniCalame:2016ouw}). However, this kind of agreement
+always comes \emph{a posteriori}, and cannot be ensured in general.
+Another problem with this approach is that it introduces a dependence on the program, or even on a specific version of the program if bugs have been found.
+This is especially problematic if these datasets are the only ones published, since undoing the exact subtraction can be very difficult or practically impossible as time passes (TODO insert comment about LEP ISR and DIS EW effects removal).
+
+A more physical definition of leptonic observables would be one making use of either bare leptons (the leptons as they emerge after FSR)
+or of dressed leptons (leptons and photons are clustered together and their momenta are combined, in analogy with jets in QCD). The problem with the former is that 
 electrons are never measured as bare particles, because of the finite resolution 
@@
 mind that modern, general-purpose codes employed to
-compute EW corrections treat leptons as massless, to ensure numerical stability of the matrix elements. In this case, using bare leptons is not collinear safe. Recombined
-leptons avoid all these shortcomings, with the further advantage of being 
+compute EW corrections treat leptons as massless, to ensure numerical stability of the matrix elements. In this case, using bare leptons is not collinear safe.
+Dressed leptons avoid all these shortcomings, with the further advantage of being
 inclusive on the effect of extra collinear emissions. This fact encourages to explore the possibility of employing a dressed-lepton
 definition, regardless of the leptonic flavour. It is reassuring to acknowledge that this practice is already being followed in experimental analyses:
-indeed, to mention two examples of analyses discussed in this paper, in Ref.~\cite{Aad:2015auj} data for dressed leptons are published, together with the Born-level
-and bare ones, while Refs.~\cite{Sirunyan:2019bzr} employs a dressed-lepton definition.
-
-{\bf this section may be troublesome with part of our community, e.g. paper of Tackmann suggests to use born-level electrons https://arxiv.org/pdf/2006.11382.pdf}
+indeed, to mention two examples of analyses discussed in this paper, in ref.~\cite{Aad:2015auj} data for dressed leptons are published, together with the Born-level
+and bare ones, while refs.~\cite{Sirunyan:2019bzr} employs a dressed-lepton definition.

### 2020-08-04 paper/sec-introduction.tex
Address most of Stefan's about the subtraction

@@
 Drell--Yan, especially with electrons). Be that as it may, if EW effects are
-systematically included in theoretical predictions, they should not be included 
-in the data, otherwise they will be double counted.
+systematically included in theoretical predictions, they should not be subtracted
+from experimental results, otherwise they will be double counted.
 

### 2020-08-04 paper/app-pineappl.tex
Add more smaller changes

@@
   commentstyle=\color{red},
-  keywordstyle=\color{blue}
+  keywordstyle=\color{blue},
 }
@@
 \paragraph{Channels and Luminosity function.}
-Sometimes it is usuful to know which partons contribute the most and by how much.
+Sometimes it is useful to know which partons contribute the most and by how much.
 This is what the subcommand \texttt{channels} shows:
@@
 
-\lstset{
-  basicstyle=\ttfamily\small,
-  showstringspaces=false,
-  commentstyle=\ttfamily\small,
-  keywordstyle=\ttfamily\small,
-  identifierstyle=\color{black},
-  stringstyle=\color{black},
-}
-
 \begin{verbatim}

### 2020-08-04 paper/sec-doublecounting.tex
Add more smaller changes

@@
-\section{On the consistency of experimental data}
+\section{Subtraction of EW effects from data}
 \label{sec:doublecounting}
@@
 from light particles in the final state. This applies mostly
-to processes such as neutral- or charge-current Drell--Yan, specially when electrons are considered. The problem lies in the fact that
+to processes such as neutral- or charge-current Drell--Yan, especially when electrons are considered. The problem lies in the fact that
  electrons, and to a lesser extent muons, tend to radiate photons, which are not accounted
@@
 These datasets are needed for and correctly used in QCD-only PDF determinations, since the EW corrections to some DY observables can be significant, and excluding them would therefore degrade the quality of the fit.
-In fits including fixed-order EW corrections the problem with this definition is that the first photon emission is included exactly at the matrix-element level. The inclusion of
+However, in fits including fixed-order EW corrections the problem with this definition is that the first photon emission is included exactly at the matrix-element level. The inclusion of
 subsequent emission would require the matching with the QED shower, which is not yet available for general processes.
@@
 always comes \emph{a posteriori}, and cannot be ensured in general.
-Another problem with this approach is that it introduces a dependence on the program, or even on a specific version of the program if bugs have been found.
+Another problem with this approach is that it introduces a dependence on the program that is used for the shower inversion, or even on a specific version of the program, for examples if bugs have been found.
 This is especially problematic if these datasets are the only ones published, since undoing the exact subtraction can be very difficult or practically impossible as time passes (TODO insert comment about LEP ISR and DIS EW effects removal).

### 2020-08-05 paper/sec-doublecounting.tex
small edits in sec-doublecounting

@@
 is neutral-current Drell--Yan, where the signal process is the production of an opposite-sign lepton pair, which starts
-at $\mathcal O(\alpha^2)$. Because this process is sometimes thought
+at $\mathcal O(\alpha^2)$. Because this process is usually thought
 as a quark-initiated $s$-channel mechanism ($\mathrm{q} \bar{\mathrm{q}} \to \gamma^*/\mathrm{Z} \to \ell \bar{\ell}$), in many analyses the photon-induced component,
 $\gamma \gamma \to \ell \bar{\ell}$ in the $t$ channel, is considered to be a different process, and therefore as a background and subtracted.
-The subtraction from the measured data is done by calculating the theoretical predictions of the double-photon initiated contribution, possibly including (unphysical) higher-order
+The subtraction from the measured data is done by calculating the theoretical predictions of the double-photon initiated contribution, possibly including (ill-defined) higher-order
 corrections. For example, in refs.~\cite{Aaboud:2017ffb,Aad:2016zzw} (a similar statement appears also in an older analysis~\cite{Aad:2013iua}), one reads:
@@
 Indeed, at $\mathcal O(\alpha^3)$, the reaction $\mathrm{q} \gamma \to \ell \bar{\ell} \mathrm{q}$ becomes possible, which
-includes both kind of topologies discussed above (and needs both in order to yield an IR-finite result), see Fig.~\ref{fig:dy-pi}.
+includes both kind of topologies discussed above, and needs both in order to yield an IR-finite result, see Fig.~\ref{fig:dy-pi} (as a consequence, one cannot speak of EW corrections to $\gamma \gamma \to \ell \bar{\ell}$).
 While it is common sense that the QCD counterpart of this subtraction should never
@@
 It is interesting
-to note that one can tune the QED parton shower to specific decays to mimic NLO EW effects, so that a prediction only accurate at NLO
+to note that one can tune the QED parton shower to mimic NLO EW effects for specific processes and observables, so that a prediction only accurate at NLO
 QCD displays a remarkable agreement with another at NLO QCD+EW when the photonic shower is included (see for example the behaviour of predictions showered with
@@
 always comes \emph{a posteriori}, and cannot be ensured in general.
-Another problem with this approach is that it introduces a dependence on the program that is used for the shower inversion, or even on a specific version of the program, for examples if bugs have been found.
-This is especially problematic if these datasets are the only ones published, since undoing the exact subtraction can be very difficult or practically impossible as time passes (TODO insert comment about LEP ISR and DIS EW effects removal).
+Furthermore, the deconvolution of QED effects in data introduces a dependence on the program (and possibly on 
+the specific version) employed for the shower inversion. 
+This fact is especially problematic if deconvolved datasets are the only ones which are published, since undoing the exact deconvolution can be very difficult, or practically impossible, as time passes.
+(TODO insert comment about LEP ISR and DIS EW effects removal).
 

### 2020-08-05 paper/sec-introduction.tex
added some refs in intro, and improved discussion of PI effects in sec3

@@
 theoretical predictions, accurate to NLO in both (including mixed-coupling 
-QCD--EW terms), is automated~\cite{Biedermann:2017yoi,Frederix:2018nkq}.
+QCD--EW terms), is automated~\cite{Kallweit:2014xda,Biedermann:2017yoi,Frederix:2018nkq}. For an extensive and recent review, see ref.~\cite{Denner:2019vbn}.
 
@@
 optimised, except for QED effects if a photon PDF is 
-determined~\cite{Schmidt:2015zda,Bertone:2017bme,Harland-Lang:2019pla}.
+determined~\cite{Schmidt:2015zda,Manohar:2016nzj,Manohar:2017eqh,Bertone:2017bme,Harland-Lang:2019pla}.
 Data points in kinematic regions where EW corrections are expected to affect

### 2020-08-05 paper/sec-results.tex
Improve wording and fix a few mistakes
- takes care of Stefan's comments in points 3) and 4)
added some refs in intro, and improved discussion of PI effects in sec3

@@
 values of invariant mass, where EW corrections become sizeable. As explained in
-section~\ref{sec:pineappl-example}, should PI contributions be taken into account,
+section~\ref{sec:pineappl-example}, 
 the process has a single LO, $\mathcal{O}(\alpha^2)$; at NLO, the
@@
 The photon is always considered as part of the proton in the initial state and
-of any hadronic jet produced in the final state: PI effects and EW corrections
-are therefore treated on the same footing. We use a PDF set that contains a
+of any hadronic jet produced in the final state: 
+ in particular, PI contribution are consistently included at LO and NLO.\footnote{We employ the $\overline{G}_\mu$ scheme also for the QED coupling entering vertices involving initial-state photons, see Sec.~4.3.3 of ref.\cite{Denner:2019vbn}.}
+We use a PDF set that contains a
 consistently defined photon PDF, namely
@@
 \begin{equation}
-M_\mathrm{W} = \SI{80}{\giga\electronvolt} \text{,} \quad 
-M_\mathrm{Z} = \SI{91.176}{\giga\electronvolt} \text{,} \quad 
-m_\mathrm{t} = \SI{172.5}{\giga\electronvolt} \text{,} \quad
-\Gamma_\mathrm{W} = \SI{2.50}{\giga\electronvolt} \text{,} \quad
-\Gamma_\mathrm{Z} = \SI{2.09}{\giga\electronvolt} \text{,} 
+\begin{aligned}
+M_\mathrm{W} &= \SI{80}{\giga\electronvolt} \text{,} \quad &
+M_\mathrm{Z} &= \SI{91.176}{\giga\electronvolt} \text{,} \quad &
+m_\mathrm{t} &= \SI{172.5}{\giga\electronvolt} \text{,} \quad \\
+\Gamma_\mathrm{W} &= \SI{2.09}{\giga\electronvolt} \text{,} &
+\Gamma_\mathrm{Z} &= \SI{2.50}{\giga\electronvolt} \text{,}
+\end{aligned}
 \label{eq:parameters}

### 2020-08-05 paper/sec-results.tex
Top pair sect 3

--- 2020-08-04 paper/sec-results.tex
@@
 
-\paragraph{Top-quark pair production.} We now consider
+\paragraph{Top-quark pair production.} We now consider the top-pair differential
+distributions measured by the ATLAS and CMS experiments at
+\SI{7}{\tera\electronvolt}. In figure~\ref{fig:atlastop} we report the
+distributions differential in the transverse momentum of the top quark,
+$p_\mathrm{T}^\mathrm{t}$, and in the invariant mass of the top-quark pair,
+$m_{\mathrm{t}\bar{\mathrm{t}}}$. Analogous plots for the distributions differential
+in the rapidity of either the top quark or the top-quark pair are collected in
+appendix~\ref{app:add_plots}. From figure~\ref{fig:atlastop}, we immediately
+validate the \textsc{PineAPPL} result: its relative difference with respect to
+the MC result is at most as large as $0.4\tcperthousand$, irrespective of the
+accuracy of the theory, of the choice of scale and of the distribution
+considered.
 
+%-------------------------------------------------------------------------------
 \begin{figure}[!t]
@@
 \end{figure}
+%-------------------------------------------------------------------------------
+
+The process is dominated by
 

### 2020-08-05 paper/sec-pineappl.tex

@@
 In the FKS subtraction scheme~\cite{Frixione:1995ms,Frixione:1997np} employed in \textsc{mg5\_aMC} maximally one type of kinematics for each counterterm (soft, collinear, and soft-collinear) is needed, but this is not the general case.
-In Catani--Seymour subtraction~\cite{Catani:1996jh}, for example, different dipoles have different phase spaces and therefore different scales.
+In Catani--Seymour subtraction~\cite{Catani:1996jh,Catani:2002hc}, for example, different dipoles have different phase spaces and therefore different scales.
 However, \textsc{PineAPPL} remains completely blind to this fact, and a consistent treatment is ensured by correctly using the interface between \textsc{PineAPPL}, which fills each event into a grid using the \emph{numerical value} of $Q^2$.

### 2020-08-05 paper/sec-results.tex
Top pair, sect 3

@@
 distributions measured by the ATLAS and CMS experiments at
-\SI{7}{\tera\electronvolt}. In figure~\ref{fig:atlastop} we report the
+\SI{8}{\tera\electronvolt}. In figure~\ref{fig:atlastop} we report the
 distributions differential in the transverse momentum of the top quark,
@@
 
-The process is dominated by
+The process receives its leading contribution from the $\mathrm{gg}$ channel,
+which varies between 81\% and 61\% (76\% and 83\%) of the $p_\mathrm{T}^\mathrm{t}$
+($m_{\mathrm{t}\bar{\mathrm{t}}}$) differential cross section as the value of the
+transverse momentum of the top quark (the invariant mass of the top-quark pair)
+increases in the bin range; $\mathrm{\gamma}\mathrm{g}$ scattering
+correspondingly accounts for about 0.5\% -- 1\% (0.5\% -- 0.7\%) of the cross
+section; the contribution from other PI parton luminosities is comparatively
+negligible. Overall, the EW corrections suppress the $p_\mathrm{T}^\mathrm{t}$
+($m_{\mathrm{t}\bar{\mathrm{t}}}$) distribution by about 0.2\% -- 3.5\%
+(0.5\% -- 0.2\%) for increasing values of $p_\mathrm{T}^\mathrm{t}$
+($m_{\mathrm{t}\bar{\mathrm{t}}}$), except in the first bin of the
+$p_\mathrm{T}^\mathrm{t}$ distribution, where they enhance the cross section by
+about 1\%. The size of these shifts, however, remains always significantly
+smaller than the data uncertainty.\footnote{In
+  figure~\ref{fig:atlastop} the data uncertainty corresponds to the ATLAS
+  measurement~\cite{Aad:2015auj}. Similar considerations apply also for the CMS
+  measurement~\cite{Khachatryan:2015oaa}.}
+As a consequence, we anticipate that the more accurate NLO QCD+EW theory is
+likely to be easily accommodated by the large data uncertainty, should the data
+be fitted with the inclusion of EW corrections; PDFs will possibly not become
+more precise.
+
+The size of the EW correction is comparable to the size of the PDF uncertainty,
+except at large values of transverse momentum or invariant mass, where the
+former becomes larger than the latter. This fact suggests that, once included in
+a global fit, EW corrections can improve the accuracy of the PDFs. In comparison
+to the scale uncertainty, the size of the EW corrections remains negligible:
+despite the fact that the choice of factorisation and renormalisation scales
+have been devised to optimise the convergence of the perturbative expansion,
+NNLO QCD corrections remain large, as expected in a process mostly initiated
+by gluons. Their inclusion is therefore mandatory in a fit of PDFs. Finally,
+the Monte Carlo statistical uncertainty remains negligible in comparison to the
+data, PDF and scale uncertainties, and to the size of the EW correction. Our
+conclusions are therefore not affected by Monte Carlo inefficiencies.
 
@@
 
+%-------------------------------------------------------------------------------
 \begin{figure}[!t]
@@
     \includegraphics[width=0.5\textwidth]{figures/pineappl_CMS_Z_13_TEV}
-    \caption{PineAPPL comparison for CMS Z $p_\mathrm{T}$ distribution.}
+    \caption{Same as figure~\ref{fig:atlaszhighmass49fb} but for the 
+      CMS differential Z $p_\mathrm{T}$ measurement at a centre-of-mass energy of
+      \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}.}
     \label{fig:cmsZ13TeV}
 \end{figure}
+%-------------------------------------------------------------------------------

### 2020-08-05 paper/app-pineappl.tex
Add small changes

@@
 \end{verbatim}
-This shows that channel \texttt{\#0} represents the up-type quark--anti-quark contribution (shown with PDG id 2 and 4 for up and charm quarks, which have the same matrix elements), channel \texttt{\#15} is the same channel with initial states transposed, channels \texttt{\#5} and \texttt{\#20} are the down-type quark--anti-quark channels, and channel \texttt{\#30} is the photon--photon channel.
-The factors \texttt{1} are not important here, but in general they can contain CKM matrix elements that would otherwise not allow to share the matrix elements between different quark flavours.
+This shows that channel \texttt{\#0} represents the up-type quark--anti-quark contributions (shown with PDG id 2 and 4 for up and charm quarks, which have the same matrix elements), channel \texttt{\#15} is the same channel with its initial states transposed, channels \texttt{\#5} and \texttt{\#20} are the down-type quark--anti-quark channels, and channel \texttt{\#30} is the photon--photon channel.
+The size of the remaining channels is smaller than the photon--photon channel.
+The factors \texttt{1} are not important here, but in general they can contain CKM values that, if kept in the squared matrix elements, would not allow to share a single matrix elements for different quark flavours and therefore slow down the calculation.
 

### 2020-08-05 paper/paper.tex
fast-interpolation in the abstract
Add small changes

--- 2020-07-30 paper/paper.tex
@@
 %Alessandro Vicini\\
+%Stefan Dittmaier
 E.R.N. is supported by the European Commission through the Marie
 Sk\l odowska-Curie Action ParDHonS FFs.TMDs (grant number 752748).
-C.S.\ is supported by the European Research Council under the European Union's
+C.S.\ and S.C.\ are supported by the European Research Council under the European Union's
 Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).

### 2020-08-05 paper/sec-results.tex
Add low statistics plot
Part of Christopher's and Marco's comments are now implemented

@@
 QCD contribution is $\mathcal{O}(\alphas\alpha^2)$, while the EW contribution
-is $\mathcal{O}(\alpha^3)$. The latter is not included in the NLO
-QCD computation, but it is in the NLO QCD+EW computation. Mixed QCD-EW
-corrections occur only at NNLO, and are therefore not considered here. 
-EW corrections for this process were computed in
+is $\mathcal{O}(\alpha^3)$. Our NLO QCD computation includes the
+$\mathcal{O}(\alpha^2)$ and $\mathcal{O}(\alphas\alpha^2)$ contributions, while
+our NLO QCD+EW computation includes the $\mathcal{O}(\alpha^2)$, 
+$\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$ contributions.
+Mixed-coupling QCD-EW corrections occur only at NNLO, and are therefore not
+considered here. EW corrections for this process were computed in
 refs.~\cite{Baur:2001ze,Dittmaier:2009cr}. The process receives contributions
@@
 pure QCD contributions at LO, $\mathcal{O}(\alphas^2)$, and
-at NLO, $\mathcal{O}(\alphas^3)$. They make up the NLO QCD
-computation. The NLO QCD+EW computation includes the LO contribution
-$\mathcal{O}(\alphas\alpha)$ and the NLO contributions
-$\mathcal{O}(\alphas^2\alpha)$ and $\mathcal{O}(\alphas\alpha^2)$.
-We do not consider the LO contribution $\mathcal{O}(\alpha^2)$ and the
-corresponding higher-order EW correction. EW corrections for this process
+at NLO, $\mathcal{O}(\alphas^3)$. They make up our NLO QCD
+computation. The NLO QCD+EW computation includes the $\mathcal{O}(\alphas^2)$
+and $\mathcal{O}(\alphas^3)$ QCD contributions, the LO contribution
+$\mathcal{O}(\alphas\alpha)$ and the NLO contribution
+$\mathcal{O}(\alphas^2\alpha)$.
+We do not consider the LO contribution $\mathcal{O}(\alpha^2)$ nor the
+NLO contribution $\mathcal{O}(\alphas\alpha^2)$.
+EW corrections for this process
 were computed in refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}.
@@
 energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. So far, this measurement has not been
-included in any PDF determination. Because it has sub-percent uncertainties,
+included in any PDF determination. Because it has sub-percent experimental uncertainties,
 EW corrections are expected to be essential in order to achieve a good
@@
 $\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alpha^4)$, and with the NLO
-QCD-EW mixed correction, $\mathcal{O}(\alphas\alpha^3)$. EW corrections for
+QCD-EW mixed-coupling correction, $\mathcal{O}(\alphas\alpha^3)$. EW corrections for
 this process were computed in
@@
 sets the CKM matrix equal to the identity, and is compatible with the usage of
-the complex mass (CM) scheme for all massive particles, see
+the complex mass (CM) scheme~\cite{Denner:1999gp,Denner:2005fg} for all massive particles, see
 ref.~\cite{Frederix:2018nkq} for details. We use this scheme
@@
 of any hadronic jet produced in the final state: 
- in particular, PI contribution are consistently included at LO and NLO.\footnote{We employ the $\overline{G}_\mu$ scheme also for the QED coupling entering vertices involving initial-state photons, see Sec.~4.3.3 of ref.\cite{Denner:2019vbn}.}
-We use a PDF set that contains a
-consistently defined photon PDF, namely
+ in particular, PI contributions are consistently included at LO and NLO.\footnote{We employ the $\overline{G}_\mu$ scheme also for the QED coupling entering vertices involving initial-state photons, see section~4.3.3 of ref.\cite{Denner:2019vbn}.}
+We use a PDF set that contains a photon PDF, namely
 {\tt NNPDF31\_nlo\_as\_0118\_luxqed}~\cite{Bertone:2017bme}. We evaluate the PDF
@@
 last respect, we consider by default high-statistics computations, whereby we
-require a relative Monte Carlo precision of a fraction of per mille. While
+require a relative Monte Carlo precision of a fraction of per mille on the total cross section. While
 this choice does not affect the validation of the \textsc{PineAPPL} result
@@
 numerical inaccuracies due to the grid interpolation. This equivalence must
-hold for any choice of renormalisation and factorisation scale. On the other
+hold for any choice of renormalisation and factorisation scale and should not
+depend on the MC uncertainty of the binned cross section. On the other
 hand, we aim to study the size of the EW corrections, in particular with
@@
 displays the relative difference (in per mille) between the {\sc PineAPPL} and
-the MC results for the central, upper and lower scale choices, for
+the MC results for the central scale choice and upper/lower edges of the
+scale-uncertainty envelope, for
 theories accurate to both NLO QCD and NLO QCD+EW. The following three panels
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB}
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB}%
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB_lowstat}
     \caption{Validation and test of the \textsc{PineAPPL} grid for the ATLAS
@@
 uncertainty remains negligible in comparison to the data, PDF and scale
-uncertainties, and to the size of the EW correction. Our conclusions are
-therefore not affected by a poor simulation of the underlying events.
+uncertainties, and to the size of the EW correction. Our conclusions should
+therefore not be affected by a too low number of Monte Carlo events generated.
 
@@
 EW correction, except for a couple of bins at forward rapidity in the highest
-invariant mass bins. Improving the Monte Carlo statistical precision will
-require to generate an unrealistically large number of events; therefore, it
-might be desirable to treat this uncertainty as an additional theoretical
-uncertainty in the PDF fit~\cite{Ball:2018lag}.
+invariant mass bins. Improving the Monte Carlo precision will require to
+generate a larger number of events, possibly with cuts that select
+only the kinematic bins affected by the largest MC uncertainties. If this
+turned out to be computationally too expensive, it would be desirable to treat
+this uncertainty as an additional theoretical uncertainty in the PDF
+fit~\cite{Ball:2018lag}.
 

### 2020-08-05 paper/sec-results.tex
More comments addressed

@@
 When relevant, final-state photons and massless charged fermions (leptons and light quarks) are recombined together 
-if they satisfy the condition $\Delta R_{f \gamma} < 0.1$. In this case the
+if they satisfy the condition $\Delta R_{f \gamma}<0.1$, where $\Delta R_{f \gamma}$
+is the fermion-photon cone radius. In this case the
 sum of their momenta is assigned to the charged fermion, and the photon is removed
-from the event. Kinematics observables and cuts are defined starting from recombined momenta. In 
-case we would have been interested also to jet-related observables,
-photons surviving the recombination should have to be clustered together with coloured
+from the event. Kinematics observables and cuts are defined starting from recombined momenta. If we were interested also in jet-related observables,
+photons surviving the recombination wouldl have to be clustered together with coloured
 partons.\footnote{For issues related to the definition of jets in presence of EW corrections,
@@
 $|\eta_\ell|<2.5$ and $\SI{116}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the transverse
-momentum and the rapidity of each lepton and for the invariant mass of the
+momentum and the pseudorapidity of each lepton and for the invariant mass of the
 lepton pair, respectively. In the case of double-differential Drell--Yan
@@
 $|\eta_\ell|<2.4$, $|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$
-for the transverse momentum and the rapidity of each lepton, and for the
-rapidity and the invariant mass of the lepton pair. In the case of Z-boson
+for the transverse momentum and the pseudorapidity of each lepton, and for the
+pseudorapidity and the invariant mass of the lepton pair. In the case of Z-boson
 production with non-zero transverse momentum at \SI{13}{\tera\electronvolt} measured by CMS, we
@@
 $|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<p_\mathrm{T}^{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the
-transverse momentum and rapidity of each lepton, and for the invariant mass,
-rapidity and transverse momentum of the lepton pair.
+transverse momentum and pseudorapidity of each lepton, and for the invariant mass,
+pseudorapidity and transverse momentum of the lepton pair.
 
@@
 for the lowest invariant mass bins, and \SI{68}{\percent} (\SI{22}{\percent}) for the largest invariant
-mass bins. The PI contribution raises from about \SI{1.3}{\percent} in the lowest bin to
+mass bins.\footnote{The size of these contributions may depend on the input PDF
+  set. Here and in the following, we always quote results obtained from the
+  \texttt{NNPDF31\_nlo\_as\_0118\_luxqed} PDF set.}
+The PI contribution raises from about \SI{1.3}{\percent} in the lowest bin to
 about \SI{3.6}{\percent} in the highest bin. Overall, the EW corrections range between \SI{5}{\percent}
@@
 than the data uncertainty, except for the invariant mass bin 
-$\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$, where the shift due to the EW correction
-overshoots the data uncertainty by about a factor of ten, and at large
-rapidities, where the shift due to the EW correction, although it can become
-large, is always a fraction of the data uncertainty. As already observed in the
-case of the ATLAS measurement, should EW corrections be included in a fit of
-PDFs, the description of the precise bins in the low invariant mass range is
-likely to benefit from the more accurate theory; furthermore, the kinematic cut
+$\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$,
+where the shift due to the EW correction overshoots the data uncertainty by
+about a factor of ten, and at large rapidities, where the shift due to the EW
+correction, although it can become large, is always a fraction of the data
+uncertainty. Because EW effects are subtracted from the data used
+in PDF fits (see section~\ref{sec:doublecounting}), a good agreement between
+data and theory is usually achieved without the inclusion of EW corrections.
+However, as already observed in the case of the ATLAS measurement, should EW
+corrections be included in a fit of PDFs, these are likely to become more
+accurate: even though the apparent description of the data will not
+improve, including of the precise bins in the low invariant mass range, PDFs
+will resemble more closely the underlying truth. Furthermore, the kinematic cut
 that excludes any data point at large invariant mass and/or rapidity can be

### 2020-08-06 paper/sec-results.tex
Updated ERN funding
added some comments in results. Removed commented tex in doublecounting

@@
 been extensively studied in the context of PDF fits in
-refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml}, and
+refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml} (see
+also refs.~\cite{Pagani:2016caq,Czakon:2017wor} for studies related to the photon density) and
 included by default in the CT18~\cite{Hou:2019efy} analysis.
@@
 We do not consider the LO contribution $\mathcal{O}(\alpha^2)$ nor the
-NLO contribution $\mathcal{O}(\alphas\alpha^2)$.
+NLO contributions $\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$, which have been shown to be negligible~\cite{Czakon:2017wor,Frederix:2018nkq}.
 EW corrections for this process
@@
 partons.\footnote{For issues related to the definition of jets in presence of EW corrections,
-    see refs.~\cite{Frederix:2016ost,Denner:2019zfp}}
+see refs.~\cite{Frederix:2016ost,Denner:2019zfp}.} Finally, although contributions corresponding to the radiation
+of a heavy boson are formally of the same perturbative order as the EW corrections, they are not included in our
+computations. In fact, while nothing prevents to include these contributions \emph{a posteriori}, as they are finite,
+their impact is either smaller than the one of ``standard'' EW corrections, or anyway negligible with respect to
+the total cross section (see refs.~\cite{Frixione:2014qaa,Frixione:2015zaa,Pagani:2016caq} for some process-specific cases {\bf MZ OTHERS???}).
 
@@
     \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB}%
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB_lowstat}
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB_lowstat}\\
     \caption{Validation and test of the \textsc{PineAPPL} grid for the ATLAS
@@
 correspondingly accounts for about 0.5\% -- 1\% (0.5\% -- 0.7\%) of the cross
-section; the contribution from other PI parton luminosities is comparatively
+section, and is almost entirely {\bf MZ CHECK!!!} due to the LO contribution at $\mathcal{O}(\alphas\alpha)$; the contribution from other PI parton luminosities is comparatively
 negligible. Overall, the EW corrections suppress the $p_\mathrm{T}^\mathrm{t}$

### 2020-08-06 paper/sec-results.tex
Sect 3

--- 2020-08-05 paper/sec-results.tex
@@
 In comparison to the PDF uncertainty, the size of the EW corrections is always
-larger. We therefore anticipate that, once included in a PDF fit, they would
-recast the relative weight of each data set included in the fit, and possibly
-lead to an improvement in their overall description. In comparison to the scale
+larger. We therefore anticipate that, even if the agreement between the more
+accurate theory (including EW corrections) and the data will remain the same,
+the PDFs will however become overall more accurate. In comparison to the scale
 uncertainty, the size of the EW correction is similar, except on the Z-boson

### 2020-08-06 paper/sec-results.tex
ismall fix

@@
 if they satisfy the condition $\Delta R_{f \gamma}<0.1$, where $\Delta R_{f \gamma}$
-is the fermion-photon cone radius. In this case the
+is the fermion-photon distance. In this case the
 sum of their momenta is assigned to the charged fermion, and the photon is removed

### 2020-08-06 paper/app-pineappl.tex
Minor tweaks in appendix A

@@
 
-\textsc{PineAPPL} currently consists of three parts: 1) the library itself, which is a dependency for the other parts, 2) the helper program \texttt{pineappl}, which allows to read \textsc{PineAPPL} grids from the command line and make predictions with it, and finally 3) the C interface, which is intended to be used in Monte Carlo integrators to generate the grids.
+\textsc{PineAPPL} currently consists of three parts: 1) the library itself, which is a dependency for the other parts, 2) the helper program \texttt{pineappl}, which allows one to read \textsc{PineAPPL} grids from the command line and make predictions with it, and finally 3) the C interface, which is intended to be used in Monte Carlo integrators to generate the grids.
 
@@
 
-All parts are written in Rust and therefore need a Rust compiler and other tools.
-On computers with a \texttt{bash} shell the installation is as simple as
+All parts are written in Rust: a Rust compiler and related tools are needed.
+On operating systems with a \texttt{bash} shell (such as Linux or MacOS) the installation is as simple as
 \begin{verbatim}
@@
 which downloads the compiler \texttt{rustc}, the package manager \texttt{cargo}, and a few other helpful tools.
-When the installation has completed make sure to read and follow the instructions printed before.
-See also \url{https://www.rust-lang.org/tools/install} for more details and for installation instructions for other systems.
+When the installation has completed make sure to read and follow the instructions printed on screen.
+See also \url{https://www.rust-lang.org/tools/install} for more details and for installation instructions for other operating systems.
 
@@
 
-After being installed, you can compile and link against the library.
+After being installed, one can compile and link against the library.
 See appendix~\ref{app:example-program} for an example.
-
 Updated installation instructions are kept in the file \texttt{README.md} in \textsc{PineAPPL}'s repository at \url{https://github.com/N3PDF/pineappl/}.
@@
 The most important subcommand is \texttt{convolute}, which performs a convolution of a single grid with a single or multiple PDF sets.
-As an example we show the grid produced for the ATLAS DY high-mass lepton-pair production from section~\ref{subsec:numerical_results}, convoluted with \texttt{NNPDF31\_nlo\_as\_0118\_luxqed} as the main PDF set and with \texttt{CT18NLO} as a second PDF set.
+As an example we show the grid produced for the ATLAS Drell--Yan high-mass lepton-pair production from section~\ref{subsec:numerical_results}, convoluted with \texttt{NNPDF31\_nlo\_as\_0118\_luxqed} as the main PDF set and with \texttt{CT18NLO} as a second PDF set.
 \begin{verbatim}
@@
 The first three columns are known from \texttt{convolute}.
-The next columns (the switch \texttt{-{}-limit 5} limits the output to five columns) show first the channel index and then relative size of the corresponding contribution.
+The next columns (the switch \texttt{-{}-limit 5} limits the output to five columns) show first the channel index and then the relative size of the corresponding contribution.
 Since the contribution of a partonic channel can be negative, the columns are sorted ignoring the sign of the contribution.
@@
 The size of the remaining channels is smaller than the photon--photon channel.
-The factors \texttt{1} are not important here, but in general they can contain CKM values that, if kept in the squared matrix elements, would not allow to share a single matrix elements for different quark flavours and therefore slow down the calculation.
+The factors \texttt{1} are not important here, but in general they can contain CKM values that, if kept in the squared matrix elements, would not allow for sharing a single matrix element for different quark flavours and therefore slow down the calculation.
+A complete list of the most important channels and of their
+contibution to the cross section for all of the processes discussed in
+section~\ref{sec:results} is collected in appendix~\ref{app:lumis}.
 
-\subsection{Sample runcard for \texorpdfstring{\textsc{mg5\_aMC@NLO}}{mg5\_aMC@NLO}}
+\subsection{Sample runcard for \texorpdfstring{\textsc{mg5\_aMC}}{mg5\_aMC}}
 \label{app:sample-runcard}
@@
 The following run card was used to produce the results shown in section~\ref{subsec:numerical_results}.
-The only difference to a normal \textsc{mg5\_aMC@NLO} run is the switch \texttt{set iappl 1}, which enables filling a \textsc{PineAPPL} grid.
+The only difference with respect to a standard \textsc{mg5\_aMC} run is the switch \texttt{set iappl 1}, which enables to fill a \textsc{PineAPPL} grid.
 For a complete set of runcards and patches see TODO.

### 2020-08-06 paper/sec-results.tex
z-pt part

@@
 the Z boson, $p_\mathrm{T}^\mathrm{Z}$, measured by the CMS experiment at a centre-of-mass
-energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. So far, this measurement has not been
-included in any PDF determination. Because it has sub-percent experimental uncertainties,
+energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. While this measurement is not
+included in any PDF determination, its expected impact on parton densities has been studied in 
+ref.~\cite{Boughezal:2017nla}. Since this process shows very low experimental uncertainties (at the percent level or below), and is
+known to an excellent degree as far as QCD corrections are concerned~\cite{Gehrmann-DeRidder:2017mvr,Bizon:2019zgf} {\bf MZ there are at least 5-6 other papers both
+by the zurich group and the argonne one, but on Z+jet rather than z-pt predictions. Should we cite them?}
 EW corrections are expected to be essential in order to achieve a good
@@
 pseudorapidity and the invariant mass of the lepton pair. In the case of Z-boson
-production with non-zero transverse momentum at \SI{13}{\tera\electronvolt} measured by CMS, we
+production with non-zero transverse momentum at \SI{13}{\tera\electronvolt} measured by CMS,
 require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$, $|\eta_\ell|<2.4$,
@@
 transverse momentum and pseudorapidity of each lepton, and for the invariant mass,
-pseudorapidity and transverse momentum of the lepton pair.
+pseudorapidity and transverse momentum of the lepton pair. Imposing a minimum cut for the transverse momentum of the lepton pair 
+is necessary as we stick to a fixed-order computation, without including resummation effects.
 

### 2020-08-06 paper/sec-results.tex
fixed typo

@@
 refs.~\cite{Baur:2001ze,Dittmaier:2009cr}. The process receives contributions
-from 12 (34) parton luminosities at NLO QCD (NLO QCD+EW),
+from 13 (35) parton luminosities at NLO QCD (NLO QCD+EW),
 see appendix~\ref{app:lumis} for details.
@@
 The process receives contributions from
-6 (36) parton luminosities at NLO QCD (NLO QCD+EW),
+7 (37) parton luminosities at NLO QCD (NLO QCD+EW),
 see appendix~\ref{app:lumis} for details.
@@
 refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
-The process receives contributions from 100 (165) parton luminosities,
+The process receives contributions from 101 (166) parton luminosities,
 see appendix~\ref{app:lumis} for details.

### 2020-08-06 paper/sec-results-marco.tex
restructured sec-results (keep the old one as well)

--- 2020-08-06 paper/sec-results.tex
@@
 obtained with \textsc{PineAPPL}; second, we want to assess the
-impact of the EW corrections for usual experimental setups. We describe, first,
-the processes and measurements that we consider, then the computational
-settings that we adopt, and finally the results that we obtain.
+impact of the EW corrections for usual experimental setups. We start by describing the
+setup employed for the computation, then we discuss the features of each process, along with
+the corresponding results.
 
-\subsection{Processes and measurements}
+\subsection{Computational settings}
+\label{subsec:computational_settings}
+
+We generate each process by means of the Universal FeynRules Output
+(UFO)~\cite{Degrande:2011ua} model {\tt loop\_qcd\_qed\_sm\_Gmu},
+included as standard in {\sc MG5\_aMC}. It contains the UV and $R_2$
+counterterms relevant to NLO QCD and EW corrections, the latter in the
+$\overline{G}_\mu$ scheme. The model features five massless quark flavours,
+sets the CKM matrix equal to the identity, and is compatible with the usage of
+the complex mass (CM) scheme~\cite{Denner:1999gp,Denner:2005fg} for all massive particles, see
+ref.~\cite{Frederix:2018nkq} for details. We use this scheme
+for all processes that involve only massless particles in the final state.
+The photon is always considered as part of the proton in the initial state and
+of any hadronic jet produced in the final state: 
+ in particular, PI contributions are consistently included at LO and NLO.\footnote{We employ the $\overline{G}_\mu$ scheme also for the QED coupling entering vertices involving initial-state photons, see section~4.3.3 of ref.\cite{Denner:2019vbn}.}
+We use a PDF set that contains a photon PDF, namely
+{\tt NNPDF31\_nlo\_as\_0118\_luxqed}~\cite{Bertone:2017bme}. We evaluate the PDF
+uncertainty associated to the theoretical predictions a posteriori, that is,
+we convolve the fast-interpolation grid generated with {\sc PineAPPL} with
+each member in the PDF set, and we compute the associated standard deviation.
+
+The central values of the renormalisation and factorisation scales, $\mu_\mathrm{R}$ and
+$\mu_\mathrm{F}$, are chosen in a process specific way, and are discussed in sec.~\ref{subsec:processes_and_measurements}. In order to estimate the missing higher-order uncertainty,
+we allow the events to be reweighted on-the-fly in the Monte Carlo generation upon scale
+variations, with the technique presented in Ref.~\cite{Frederix:2011ss}. To this purpose, we use the default \textsc{MG5\_aMC}
+implementation, whereby the factorisation and renormalisation scales
+are varied down to a factor $1/2$ and up to a factor $2$, and the envelope
+from the nine-point scale variations is constructed. However, we note that
+\textsc{PineAPPL} allows the user to determine the envelope with any point
+prescription, see appendix~\ref{app:pineappl-demo} for an example.
+
+The values of the relevant physical parameters are chosen as
+\begin{equation}
+\begin{aligned}
+M_\mathrm{W} &= \SI{80}{\giga\electronvolt} \text{,} \quad &
+M_\mathrm{Z} &= \SI{91.176}{\giga\electronvolt} \text{,} \quad &
+m_\mathrm{t} &= \SI{172.5}{\giga\electronvolt} \text{,} \quad \\
+\Gamma_\mathrm{W} &= \SI{2.09}{\giga\electronvolt} \text{,} &
+\Gamma_\mathrm{Z} &= \SI{2.50}{\giga\electronvolt} \text{,}
+\end{aligned}
+\label{eq:parameters}
+\end{equation}
+where $M_\mathrm{W}$, $M_\mathrm{Z}$ and $m_\mathrm{t}$ are the values of the W-boson, Z-boson, and
+top quark masses, respectively, and $\Gamma_\mathrm{W}$ and $\Gamma_\mathrm{Z}$ are the width of
+the W boson and of the Z boson, respectively. The value of the strong
+coupling is chosen consistently with the PDF set, $\alphas(M_\mathrm{Z})=0.118$.
+The definition of observables and cuts is process-specific, and it follows the corresponding experimental measurements.
+When relevant, final-state photons and massless charged fermions (leptons and light quarks) are recombined together 
+if they satisfy the condition $\Delta R_{f \gamma}<0.1$, where $\Delta R_{f \gamma}$
+is the fermion-photon distance. In this case the
+sum of their momenta is assigned to the charged fermion, and the photon is removed
+from the event. Kinematics observables and cuts are defined starting from recombined momenta. If we were interested also in jet-related observables,
+photons surviving the recombination would have to be clustered together with coloured
+partons.\footnote{For issues related to the definition of jets in presence of EW corrections,
+see refs.~\cite{Frederix:2016ost,Denner:2019zfp}.} Finally, although contributions corresponding to the radiation
+of a heavy boson are formally of the same perturbative order as the EW corrections, they are not included in our
+computations. In fact, while nothing prevents to include these contributions \emph{a posteriori}, as they are finite,
+their impact is either smaller than the one of ``standard'' EW corrections, or anyway negligible with respect to
+the total cross section (see refs.~\cite{Frixione:2014qaa,Frixione:2015zaa,Pagani:2016caq} for some process-specific cases {\bf MZ OTHERS???}).
+
+\subsection{Results for specific processes and measurements}
 \label{subsec:processes_and_measurements}
@@
 transverse momentum in proton-proton collisions. For each of these processes,
-we consider the following measurements.
+we present the experimental measurements, process-specific settings, and phenomenological results.
 
-\paragraph{Drell--Yan lepton pair production.}
+When presenting the results, for each of the processes and measurements considered, we compute the expectation
+value of the corresponding observable for each kinematic bin in two different
+ways: directly, by means of \textsc{MG5\_aMC}, and a posteriori, by convolving
+the fast-interpolation grid produced by \textsc{PineAPPL} with the PDF set
+specified in section~\ref{subsec:computational_settings}. We
+will refer to the first result as the MC result, and to the second as
+the \textsc{PineAPPL} result. We repeat the computation for theories accurate
+to NLO QCD and to NLO QCD+EW, respectively. The corresponding orders of the
+strong and electroweak couplings that we consider are specified for each process. In each case, we determine the
+PDF uncertainty (coming from the PDF ensemble), the scale uncertainty (coming
+from variations of the factorisation and renormalisation scales), and the Monte
+Carlo uncertainty (coming from the finite number of events generated). In this
+last respect, we consider by default high-statistics computations, whereby we
+require a relative Monte Carlo precision of a fraction of per mille on the total cross section. While
+this choice does not affect the validation of the \textsc{PineAPPL} result
+against the MC result, it ensures that the statistical uncertainty of
+the computation remains negligible in comparison to the PDF and scale
+uncertainties, as we will explicitly demonstrate. This is a desirable feature
+to correctly interpret the size of the EW corrections.
+
+Our goal is indeed twofold. On the one hand, we aim to validate the
+interpolation grids generated with \textsc{PineAPPL}: to this purpose we shall
+verify that the MC and the \textsc{PineAPPL} results are identical up to
+numerical inaccuracies due to the grid interpolation. This equivalence must
+hold for any choice of renormalisation and factorisation scale and should not
+depend on the MC uncertainty of the binned cross section. On the other
+hand, we aim to study the size of the EW corrections, in particular with
+respect to the kinematics of each process, and to three kinds of uncertainties:
+the PDF uncertainty, the scale uncertainty, and the uncertainty of the
+experimental data.
+
+We present these comparisons in
+figures~\ref{fig:atlaszhighmass49fb}--\ref{fig:cmsZ13TeV}.
+The format of the plots is the same across all figures. The first panel
+displays the relative difference (in per mille) between the {\sc PineAPPL} and
+the MC results for the central scale choice and upper/lower edges of the
+scale-uncertainty envelope, for
+theories accurate to both NLO QCD and NLO QCD+EW. The following three panels
+present the theoretical predictions, accurate to either NLO QCD or NLO QCD+EW,
+always normalised to the former; on top of the theoretical predictions, the
+PDF uncertainty, the scale uncertainty and the Monte Carlo uncertainty are
+displayed in turn. The relative uncertainty of the experimental data is
+also shown for comparison. We shall now discuss the results for each
+process and data set.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Drell--Yan lepton pair production.}
+
+\paragraph{Experimental measurements and process features.}
 We select the distribution, single-differential in the invariant mass of the
@@
 
-\paragraph{Top-quark pair production.}
-We select the distributions, single-differential in either the transverse
-momentum of the top quark, $p_\mathrm{T}^\mathrm{t}$, or the invariant mass of the top-quark
-pair, $m_{\mathrm{t}\bar{\mathrm{t}}}$, measured by the ATLAS and CMS experiments at a centre-of-mass
-energy of \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
-been extensively studied in the context of PDF fits in
-refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml} (see
-also refs.~\cite{Pagani:2016caq,Czakon:2017wor} for studies related to the photon density) and
-included by default in the CT18~\cite{Hou:2019efy} analysis.
-Because EW corrections are significantly smaller for distributions differential
-in the rapidity of either the top quark or the top-quark
-pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
-in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. The process receives
-pure QCD contributions at LO, $\mathcal{O}(\alphas^2)$, and
-at NLO, $\mathcal{O}(\alphas^3)$. They make up our NLO QCD
-computation. The NLO QCD+EW computation includes the $\mathcal{O}(\alphas^2)$
-and $\mathcal{O}(\alphas^3)$ QCD contributions, the LO contribution
-$\mathcal{O}(\alphas\alpha)$ and the NLO contribution
-$\mathcal{O}(\alphas^2\alpha)$.
-We do not consider the LO contribution $\mathcal{O}(\alpha^2)$ nor the
-NLO contributions $\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$, which have been shown to be negligible~\cite{Czakon:2017wor,Frederix:2018nkq}.
-EW corrections for this process
-were computed in refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}.
-The process receives contributions from
-7 (37) parton luminosities at NLO QCD (NLO QCD+EW),
-see appendix~\ref{app:lumis} for details.
-
-\paragraph{Z-boson production with non-zero transverse momentum.}
-We select the distribution, single-differential in the transverse momentum of
-the Z boson, $p_\mathrm{T}^\mathrm{Z}$, measured by the CMS experiment at a centre-of-mass
-energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. While this measurement is not
-included in any PDF determination, its expected impact on parton densities has been studied in 
-ref.~\cite{Boughezal:2017nla}. Since this process shows very low experimental uncertainties (at the percent level or below), and is
-known to an excellent degree as far as QCD corrections are concerned~\cite{Gehrmann-DeRidder:2017mvr,Bizon:2019zgf} {\bf MZ there are at least 5-6 other papers both
-by the zurich group and the argonne one, but on Z+jet rather than z-pt predictions. Should we cite them?}
-EW corrections are expected to be essential in order to achieve a good
-description of it, and to constrain accurately the PDFs. Analogous measurements,
-from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
-experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt}, were partly included (upon
-selection of an appropriate kinematic cut that excluded bins with large EW
-corrections) in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
-the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
-single LO contribution $\mathcal{O}(\alphas\alpha^2)$ and a single NLO
-contribution $\mathcal{O}(\alphas^2\alpha^2)$. In the NLO QCD+EW computation,
-we supplement these with the LO and NLO EW corrections,
-$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alpha^4)$, and with the NLO
-QCD-EW mixed-coupling correction, $\mathcal{O}(\alphas\alpha^3)$. EW corrections for
-this process were computed in
-refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
-The process receives contributions from 101 (166) parton luminosities,
-see appendix~\ref{app:lumis} for details.
-
-\subsection{Computational settings}
-\label{subsec:computational_settings}
-
-We generate each process by means of the Universal FeynRules Output
-(UFO)~\cite{Degrande:2011ua} model {\tt loop\_qcd\_qed\_sm\_Gmu},
-included as standard in {\sc MG5\_aMC}. It contains the UV and $R_2$
-counterterms relevant to NLO QCD and EW corrections, the latter in the
-$\overline{G}_\mu$ scheme. The model features five massless quark flavours,
-sets the CKM matrix equal to the identity, and is compatible with the usage of
-the complex mass (CM) scheme~\cite{Denner:1999gp,Denner:2005fg} for all massive particles, see
-ref.~\cite{Frederix:2018nkq} for details. We use this scheme
-for all processes that do not involve stable top quarks in the final state.
-The photon is always considered as part of the proton in the initial state and
-of any hadronic jet produced in the final state: 
- in particular, PI contributions are consistently included at LO and NLO.\footnote{We employ the $\overline{G}_\mu$ scheme also for the QED coupling entering vertices involving initial-state photons, see section~4.3.3 of ref.\cite{Denner:2019vbn}.}
-We use a PDF set that contains a photon PDF, namely
-{\tt NNPDF31\_nlo\_as\_0118\_luxqed}~\cite{Bertone:2017bme}. We evaluate the PDF
-uncertainty associated to the theoretical predictions a posteriori, that is,
-we convolve the fast-interpolation grid generated with {\sc PineAPPL} with
-each member in the PDF set, and we compute the associated standard deviation.
-
-The central values of the renormalisation and factorisation scales, $\mu_\mathrm{R}$ and
-$\mu_\mathrm{F}$, are chosen, for each process, as follows. In the case of Drell--Yan
-lepton pair production, we use the fixed scale $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$, where $M_\mathrm{Z}$ is
+\paragraph{Process-specific settings.}
+We use a fixed value for the renormalisation and factorisation scales $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$, where $M_\mathrm{Z}$ is
 the mass of the Z boson, for the ATLAS measurement, and the scale
 $\mu_\mathrm{R}=\mu_\mathrm{F}=M_{\ell\bar\ell}$, where $M_{\ell\bar\ell}$ is the central value of each
-invariant mass bin, for the CMS measurement.
-In the case of top-quark pair production, we use the dynamic scales
-$\mu_\mathrm{R}=\mu_\mathrm{F}=\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^\mathrm{t})^2}{\Big /}2$ for the distribution differential
-in the transverse momentum of the top quark, and $\mu_\mathrm{R}=\mu_\mathrm{F}=H_\mathrm{T}/4$ for the
-distribution differential in the invariant mass of the top-quark pair, where
-$H_\mathrm{T}=\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^\mathrm{t})^2}+\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^{\bar{\mathrm{t}}})}$, with $m_\mathrm{t}$,
-$p_\mathrm{T}^\mathrm{t}$ and $p_\mathrm{T}^{\bar{\mathrm{t}}}$ the mass of the top quark and the transverse momenta
-of the top and antitop quarks, respectively. These choices were demonstrated
-to maximise the convergence of the perturbative expansion~\cite{Czakon:2016dgf}.
-In the case of Z-boson production with non-zero transverse momentum, we use
-$\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$. In order to estimate the missing higher-order uncertainty,
-we allow the events to be reweighted in the Monte Carlo generation upon scale
-variations. To this purpose, we use the default \textsc{MG5\_aMC}
-implementation, whereby the factorisation and renormalisation scales
-are varied down to a factor $1/2$ and up to a factor $2$, and the envelope
-from the nine-point scale variations is constructed. However, we note that
-\textsc{PineAPPL} allows the user to determine the envelope with any point
-prescription, see appendix~\ref{app:pineappl-demo} for an example.
-
-The values of the relevant physical parameters are chosen as
-\begin{equation}
-\begin{aligned}
-M_\mathrm{W} &= \SI{80}{\giga\electronvolt} \text{,} \quad &
-M_\mathrm{Z} &= \SI{91.176}{\giga\electronvolt} \text{,} \quad &
-m_\mathrm{t} &= \SI{172.5}{\giga\electronvolt} \text{,} \quad \\
-\Gamma_\mathrm{W} &= \SI{2.09}{\giga\electronvolt} \text{,} &
-\Gamma_\mathrm{Z} &= \SI{2.50}{\giga\electronvolt} \text{,}
-\end{aligned}
-\label{eq:parameters}
-\end{equation}
-where $M_\mathrm{W}$, $M_\mathrm{Z}$ and $m_\mathrm{t}$ are the values of the W-boson, Z-boson, and
-top quark masses, respectively, and $\Gamma_\mathrm{W}$ and $\Gamma_\mathrm{Z}$ are the width of
-the W boson and of the Z boson, respectively. The value of the strong
-coupling is chosen consistently with the PDF set, $\alphas(M_\mathrm{Z})=0.118$.
-When relevant, final-state photons and massless charged fermions (leptons and light quarks) are recombined together 
-if they satisfy the condition $\Delta R_{f \gamma}<0.1$, where $\Delta R_{f \gamma}$
-is the fermion-photon distance. In this case the
-sum of their momenta is assigned to the charged fermion, and the photon is removed
-from the event. Kinematics observables and cuts are defined starting from recombined momenta. If we were interested also in jet-related observables,
-photons surviving the recombination wouldl have to be clustered together with coloured
-partons.\footnote{For issues related to the definition of jets in presence of EW corrections,
-see refs.~\cite{Frederix:2016ost,Denner:2019zfp}.} Finally, although contributions corresponding to the radiation
-of a heavy boson are formally of the same perturbative order as the EW corrections, they are not included in our
-computations. In fact, while nothing prevents to include these contributions \emph{a posteriori}, as they are finite,
-their impact is either smaller than the one of ``standard'' EW corrections, or anyway negligible with respect to
-the total cross section (see refs.~\cite{Frixione:2014qaa,Frixione:2015zaa,Pagani:2016caq} for some process-specific cases {\bf MZ OTHERS???}).
-
-Finally, we implement the kinematic cuts specified in the corresponding
-experimental analyses. In the case of high-mass Drell--Yan lepton pair
-production at \SI{7}{\tera\electronvolt} measured by ATLAS, we require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$,
+invariant mass bin, for the CMS one. In the case of ATLAS, we require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$,
 $|\eta_\ell|<2.5$ and $\SI{116}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the transverse
 momentum and the pseudorapidity of each lepton and for the invariant mass of the
-lepton pair, respectively. In the case of double-differential Drell--Yan
-lepton-pair production
-at \SI{7}{\tera\electronvolt} measured by CMS, we require $p_\mathrm{T}^{\ell_1}>\SI{14}{\giga\electronvolt}$, $p_\mathrm{T}^{\ell_2}>\SI{9}{\giga\electronvolt}$,
+lepton pair, respectively. Conversely, in the case of CMS, we require $p_\mathrm{T}^{\ell_1}>\SI{14}{\giga\electronvolt}$, $p_\mathrm{T}^{\ell_2}>\SI{9}{\giga\electronvolt}$,
 $|\eta_\ell|<2.4$, $|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$
 for the transverse momentum and the pseudorapidity of each lepton, and for the
-pseudorapidity and the invariant mass of the lepton pair. In the case of Z-boson
-production with non-zero transverse momentum at \SI{13}{\tera\electronvolt} measured by CMS,
-require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$, $|\eta_\ell|<2.4$,
-$M_\mathrm{Z}-\SI{15}{\giga\electronvolt}<M_{\ell\bar\ell}<M_\mathrm{Z}+\SI{20}{\giga\electronvolt}$,
-$|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<p_\mathrm{T}^{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the
-transverse momentum and pseudorapidity of each lepton, and for the invariant mass,
-pseudorapidity and transverse momentum of the lepton pair. Imposing a minimum cut for the transverse momentum of the lepton pair 
-is necessary as we stick to a fixed-order computation, without including resummation effects.
+pseudorapidity and the invariant mass of the lepton pair.
 
-\subsection{Numerical results}
-\label{subsec:numerical_results}
-
-For each of the measurements discussed in
-section~\ref{subsec:processes_and_measurements}, we compute the expectation
-value of the corresponding observable for each kinematic bin in two different
-ways: directly, by means of \textsc{MG5\_aMC}, and a posteriori, by convolving
-the fast-interpolation grid produced by \textsc{PineAPPL} with the PDF set
-specified in section~\ref{subsec:computational_settings}. In the following, we
-will refer to the first result as the MC result, and to the second as
-the \textsc{PineAPPL} result. We repeat the computation for theories accurate
-to NLO QCD and to NLO QCD+EW, respectively. The corresponding orders of the
-strong and electroweak couplings that we consider have been specified in
-section~\ref{subsec:processes_and_measurements}. In each case, we determine the
-PDF uncertainty (coming from the PDF ensemble), the scale uncertainty (coming
-from variations of the factorisation and renormalisation scales), and the Monte
-Carlo uncertainty (coming from the finite number of events generated). In this
-last respect, we consider by default high-statistics computations, whereby we
-require a relative Monte Carlo precision of a fraction of per mille on the total cross section. While
-this choice does not affect the validation of the \textsc{PineAPPL} result
-against the MC result, it ensures that the statistical uncertainty of
-the computation remains negligible in comparison to the PDF and scale
-uncertainties, as we will explicitly demonstrate. This is a desirable feature
-to correctly interpret the size of the EW corrections.
-
-Our goal is indeed twofold. On the one hand, we aim to validate the
-interpolation grids generated with \textsc{PineAPPL}: to this purpose we shall
-verify that the MC and the \textsc{PineAPPL} results are identical up to
-numerical inaccuracies due to the grid interpolation. This equivalence must
-hold for any choice of renormalisation and factorisation scale and should not
-depend on the MC uncertainty of the binned cross section. On the other
-hand, we aim to study the size of the EW corrections, in particular with
-respect to the kinematics of each process, and to three kinds of uncertainties:
-the PDF uncertainty, the scale uncertainty, and the uncertainty of the
-experimental data.
-
-We present these comparisons in
-figures~\ref{fig:atlaszhighmass49fb}--\ref{fig:cmsZ13TeV} for each of the processes
-and data sets outlined in section~\ref{subsec:processes_and_measurements}.
-The format of the plots is the same across all figures. The first panel
-displays the relative difference (in per mille) between the {\sc PineAPPL} and
-the MC results for the central scale choice and upper/lower edges of the
-scale-uncertainty envelope, for
-theories accurate to both NLO QCD and NLO QCD+EW. The following three panels
-present the theoretical predictions, accurate to either NLO QCD or NLO QCD+EW,
-always normalised to the former; on top of the theoretical predictions, the
-PDF uncertainty, the scale uncertainty and the Monte Carlo uncertainty are
-displayed in turn. The relative uncertainty of the experimental data is
-also shown for comparison. We shall now discuss the results for each
-process and data set.
-
-\paragraph{Drell--Yan lepton pair production.}
-
+\paragraph{Numerical results.}
 We first consider the single-differential measurement at a high lepton-pair
@@
 
-\paragraph{Top-quark pair production.} We now consider the top-pair differential
-distributions measured by the ATLAS and CMS experiments at
-\SI{8}{\tera\electronvolt}. In figure~\ref{fig:atlastop} we report the
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Top-quark pair production.}
+\paragraph{Experimental measurements and process features.}
+We select the distributions, single-differential in either the transverse
+momentum of the top quark, $p_\mathrm{T}^\mathrm{t}$, or the invariant mass of the top-quark
+pair, $m_{\mathrm{t}\bar{\mathrm{t}}}$, measured by the ATLAS and CMS experiments at a centre-of-mass
+energy of \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
+been extensively studied in the context of PDF fits in
+refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml} (see
+also refs.~\cite{Pagani:2016caq,Czakon:2017wor} for studies related to the photon density) and
+included by default in the CT18~\cite{Hou:2019efy} analysis.
+Because EW corrections are significantly smaller for distributions differential
+in the rapidity of either the top quark or the top-quark
+pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
+in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. The process receives
+pure QCD contributions at LO, $\mathcal{O}(\alphas^2)$, and
+at NLO, $\mathcal{O}(\alphas^3)$. They make up our NLO QCD
+computation. The NLO QCD+EW computation includes the $\mathcal{O}(\alphas^2)$
+and $\mathcal{O}(\alphas^3)$ QCD contributions, the LO contribution
+$\mathcal{O}(\alphas\alpha)$ and the NLO contribution
+$\mathcal{O}(\alphas^2\alpha)$.
+We do not consider the LO contribution $\mathcal{O}(\alpha^2)$ nor the
+NLO contributions $\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$, which have been shown to be negligible~\cite{Czakon:2017wor,Frederix:2018nkq}.
+EW corrections for this process
+were computed in refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}.
+The process receives contributions from
+7 (37) parton luminosities at NLO QCD (NLO QCD+EW),
+see appendix~\ref{app:lumis} for details.
+
+\paragraph{Process-specific settings.}
+We employ the following functional form for the renormalisation and factorisation scales
+$\mu_\mathrm{R}=\mu_\mathrm{F}=\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^\mathrm{t})^2}{\Big /}2$ for the distribution differential
+in the transverse momentum of the top quark, and $\mu_\mathrm{R}=\mu_\mathrm{F}=H_\mathrm{T}/4$ for the
+distribution differential in the invariant mass of the top-quark pair, where
+$H_\mathrm{T}=\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^\mathrm{t})^2}+\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^{\bar{\mathrm{t}}})}$, with $m_\mathrm{t}$,
+$p_\mathrm{T}^\mathrm{t}$ and $p_\mathrm{T}^{\bar{\mathrm{t}}}$ the mass of the top quark and the transverse momenta
+of the top and antitop quarks, respectively. These choices were demonstrated
+to maximise the convergence of the perturbative expansion~\cite{Czakon:2016dgf}. No cuts are imposed.
+
+\paragraph{Numerical results.}
+
+In figure~\ref{fig:atlastop} we report the
 distributions differential in the transverse momentum of the top quark,
@@
 
-\paragraph{Z-boson production with non-zero transverse momentum.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Z-boson production with non-zero transverse momentum.}
 
+\paragraph{Experimental measurements and process features.}
+We select the distribution, single-differential in the transverse momentum of
+the Z boson, $p_\mathrm{T}^\mathrm{Z}$, measured by the CMS experiment at a centre-of-mass
+energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. While this measurement is not
+included in any PDF determination, its expected impact on parton densities has been studied in 
+ref.~\cite{Boughezal:2017nla}. Since this process shows very low experimental uncertainties (at the percent level or below), and is
+known to an excellent degree as far as QCD corrections are concerned~\cite{Gehrmann-DeRidder:2017mvr,Bizon:2019zgf} {\bf MZ there are at least 5-6 other papers both
+by the zurich group and the argonne one, but on Z+jet rather than z-pt predictions. Should we cite them?}
+EW corrections are expected to be essential in order to achieve a good
+description of it, and to constrain accurately the PDFs. Analogous measurements,
+from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
+experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt}, were partly included (upon
+selection of an appropriate kinematic cut that excluded bins with large EW
+corrections) in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
+the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
+single LO contribution $\mathcal{O}(\alphas\alpha^2)$ and a single NLO
+contribution $\mathcal{O}(\alphas^2\alpha^2)$. In the NLO QCD+EW computation,
+we supplement these with the LO and NLO EW corrections,
+$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alpha^4)$, and with the NLO
+QCD-EW mixed-coupling correction, $\mathcal{O}(\alphas\alpha^3)$. EW corrections for
+this process were computed in
+refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
+The process receives contributions from 101 (166) parton luminosities,
+see appendix~\ref{app:lumis} for details.
+
+\paragraph{Process-specific settings.}
+
+As in the case of Drell-Yan, we use a fixed value for the renormalisation and factorisation 
+scales $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$.
+We require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$, $|\eta_\ell|<2.4$,
+$M_\mathrm{Z}-\SI{15}{\giga\electronvolt}<M_{\ell\bar\ell}<M_\mathrm{Z}+\SI{20}{\giga\electronvolt}$,
+$|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<p_\mathrm{T}^{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the
+transverse momentum and pseudorapidity of each lepton, and for the invariant mass,
+pseudorapidity and transverse momentum of the lepton pair. Imposing a minimum cut for the transverse momentum of the lepton pair 
+is necessary as we stick to a fixed-order computation, without including resummation effects.
+
+\paragraph{Numerical results.}
 %-------------------------------------------------------------------------------

### 2020-08-06 paper/sec-results.tex
Move low-statistics plot into an appendix

@@
 $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$. In order to estimate the missing higher-order uncertainty,
-we allow the events to be reweighted in the Monte Carlo generation upon scale
-variations. To this purpose, we use the default \textsc{MG5\_aMC}
+we allow the events to be reweighted on-the-fly in the Monte Carlo generation upon scale
+variations, with the technique presented in Ref.~\cite{Frederix:2011ss}. To this purpose, we use the default \textsc{MG5\_aMC}
 implementation, whereby the factorisation and renormalisation scales
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB}%
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB_lowstat}\\
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB}\\
     \caption{Validation and test of the \textsc{PineAPPL} grid for the ATLAS

### 2020-08-06 paper/sec-results.tex
Fix low-invariant mass slices of CMS DY

@@
       $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$, and at very high invariant masses,
-      $\SI{200}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$.}
+      $\SI{200}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$.
+      Results for the slices $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$ and $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$ can be found in figure~\ref{fig:cmsdy2d11_bins12}.}
     \label{fig:cmsdy2d11_bins3456}

### 2020-08-06 paper/app-lumis.tex
First try to appendix B

\section{Parton Luminosities}
\label{app:lumis}

\begin{table}[!t]
  \centering
  \tiny
  \input{tables/TableB1.tex}\\
  \caption{The 34 parton luminosities contributing to the predictions, accurate
    to NLO QCD+EW, of the Drell--Yan lepton-pair production measured by the
    ATLAS experiment at a centre-of-mass energy of
    \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The ten largest contributions
    to the cross section (irrespective of their sign) are reported, in
    percentage, for each bin. Empty spaces typically denote contributions
    smaller than a fraction of percent. The bin edges are in the invariant mass
    of the lepton pair, $M_{\ell\bar\ell}$, as follows: 116, 130, 150, 170, 190,
    210, 230, 250, 300, 400, 500, 700, 1000, 1500 [GeV].
  }
  \label{tab:B1}
\end{table}

### 2020-08-06 paper/app-pineappl.tex

@@
 The uncertainty estimation can alternatively use a 3- or a 9-point scale variation using the optional program switch \texttt{-{}-scales 3} or \texttt{-{}-scales 9}, respectively.
-The (differential) results for the second PDF set (\texttt{CT18NLO}) is shown in absolute and relative (to first PDF set) numbers.
+The (differential) results for the second PDF set (\texttt{CT18NLO}) is shown in absolute numbers and also as a percentage relative to the result of the first PDF set.
 
@@
 Since the contribution of a partonic channel can be negative, the columns are sorted ignoring the sign of the contribution.
-The first line shows that for bin 0, i.e.\ for the range $\SI{116}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{130}{\giga\electronvolt}$, the cross section is dominated by partonic channel \texttt{\#15} (\SI{27.42}{\percent}), following by partonic channel \texttt{\#0}, then \texttt{\#5}, etc.
+The first line shows that for bin 0, i.e.\ for the range $\SI{116}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{130}{\giga\electronvolt}$, the cross section is dominated by partonic channel \texttt{\#15} (\SI{27.42}{\percent}), following by partonic channel \texttt{\#0} with same size, then channel \texttt{\#5}, etc.
 The meaning of the channel numbers is given by using the subcommand \texttt{luminosity} (only an excerpt is shown):
@@
 A complete list of the most important channels and of their
-contibution to the cross section for all of the processes discussed in
+contribution to the cross section for all of the processes discussed in
 section~\ref{sec:results} is collected in appendix~\ref{app:lumis}.
@@
 For a complete set of runcards and patches see TODO.
-
 \begin{verbatim}

### 2020-08-06 paper/paper.tex
Updated ERN funding
restructured sec-results (keep the old one as well)
First try to appendix B
Tab 1 app B

@@
 \usepackage{lmodern}
-\usepackage[binary-units=true,detect-weight=true]{siunitx}
+\usepackage[binary-units=true,detect-weight=true,table-format=4.2]{siunitx}
 \usepackage{xcolor}
@@
 \input{sec-pineappl}
-\input{sec-results}
+\input{sec-results-marco}
 \input{sec-doublecounting}
@@
 Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
-treatment of EW effects in experimental data. \\
+treatment of EW effects in experimental data.
 %Alessandro Vicini\\
 %Stefan Dittmaier
-E.R.N. is supported by the European Commission through the Marie
-Sk\l odowska-Curie Action ParDHonS FFs.TMDs (grant number 752748).
+E.R.N.\ is supported by the European Commission through a Marie
+Sk\l odowska-Curie Action (grant agreement no.\ 752748).
 C.S.\ and S.C.\ are supported by the European Research Council under the European Union's

### 2020-08-06 paper/sec-results.tex
Clarify one comment

@@
 
-\paragraph{Top-quark pair production.}
-We select the distributions, single-differential in either the transverse
-momentum of the top quark, $p_\mathrm{T}^\mathrm{t}$, or the invariant mass of the top-quark
-pair, $m_{\mathrm{t}\bar{\mathrm{t}}}$, measured by the ATLAS and CMS experiments at a centre-of-mass
-energy of \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
-been extensively studied in the context of PDF fits in
-refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml} (see
-also refs.~\cite{Pagani:2016caq,Czakon:2017wor} for studies related to the photon density) and
-included by default in the CT18~\cite{Hou:2019efy} analysis.
-Because EW corrections are significantly smaller for distributions differential
-in the rapidity of either the top quark or the top-quark
-pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
-in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. The process receives
-pure QCD contributions at LO, $\mathcal{O}(\alphas^2)$, and
-at NLO, $\mathcal{O}(\alphas^3)$. They make up our NLO QCD
-computation. The NLO QCD+EW computation includes the $\mathcal{O}(\alphas^2)$
-and $\mathcal{O}(\alphas^3)$ QCD contributions, the LO contribution
-$\mathcal{O}(\alphas\alpha)$ and the NLO contribution
-$\mathcal{O}(\alphas^2\alpha)$.
-We do not consider the LO contribution $\mathcal{O}(\alpha^2)$ nor the
-NLO contributions $\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$, which have been shown to be negligible~\cite{Czakon:2017wor,Frederix:2018nkq}.
-EW corrections for this process
-were computed in refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}.
-The process receives contributions from
-7 (37) parton luminosities at NLO QCD (NLO QCD+EW),
-see appendix~\ref{app:lumis} for details.
-
-\paragraph{Z-boson production with non-zero transverse momentum.}
-We select the distribution, single-differential in the transverse momentum of
-the Z boson, $p_\mathrm{T}^\mathrm{Z}$, measured by the CMS experiment at a centre-of-mass
-energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. While this measurement is not
-included in any PDF determination, its expected impact on parton densities has been studied in 
-ref.~\cite{Boughezal:2017nla}. Since this process shows very low experimental uncertainties (at the percent level or below), and is
-known to an excellent degree as far as QCD corrections are concerned~\cite{Gehrmann-DeRidder:2017mvr,Bizon:2019zgf} {\bf MZ there are at least 5-6 other papers both
-by the zurich group and the argonne one, but on Z+jet rather than z-pt predictions. Should we cite them?}
-EW corrections are expected to be essential in order to achieve a good
-description of it, and to constrain accurately the PDFs. Analogous measurements,
-from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
-experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt}, were partly included (upon
-selection of an appropriate kinematic cut that excluded bins with large EW
-corrections) in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
-the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
-single LO contribution $\mathcal{O}(\alphas\alpha^2)$ and a single NLO
-contribution $\mathcal{O}(\alphas^2\alpha^2)$. In the NLO QCD+EW computation,
-we supplement these with the LO and NLO EW corrections,
-$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alpha^4)$, and with the NLO
-QCD-EW mixed-coupling correction, $\mathcal{O}(\alphas\alpha^3)$. EW corrections for
-this process were computed in
-refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
-The process receives contributions from 101 (166) parton luminosities,
-see appendix~\ref{app:lumis} for details.
-
-\subsection{Computational settings}
-\label{subsec:computational_settings}
-
-We generate each process by means of the Universal FeynRules Output
-(UFO)~\cite{Degrande:2011ua} model {\tt loop\_qcd\_qed\_sm\_Gmu},
-included as standard in {\sc MG5\_aMC}. It contains the UV and $R_2$
-counterterms relevant to NLO QCD and EW corrections, the latter in the
-$\overline{G}_\mu$ scheme. The model features five massless quark flavours,
-sets the CKM matrix equal to the identity, and is compatible with the usage of
-the complex mass (CM) scheme~\cite{Denner:1999gp,Denner:2005fg} for all massive particles, see
-ref.~\cite{Frederix:2018nkq} for details. We use this scheme
-for all processes that do not involve stable top quarks in the final state.
-The photon is always considered as part of the proton in the initial state and
-of any hadronic jet produced in the final state: 
- in particular, PI contributions are consistently included at LO and NLO.\footnote{We employ the $\overline{G}_\mu$ scheme also for the QED coupling entering vertices involving initial-state photons, see section~4.3.3 of ref.\cite{Denner:2019vbn}.}
-We use a PDF set that contains a photon PDF, namely
-{\tt NNPDF31\_nlo\_as\_0118\_luxqed}~\cite{Bertone:2017bme}. We evaluate the PDF
-uncertainty associated to the theoretical predictions a posteriori, that is,
-we convolve the fast-interpolation grid generated with {\sc PineAPPL} with
-each member in the PDF set, and we compute the associated standard deviation.
-
-The central values of the renormalisation and factorisation scales, $\mu_\mathrm{R}$ and
-$\mu_\mathrm{F}$, are chosen, for each process, as follows. In the case of Drell--Yan
-lepton pair production, we use the fixed scale $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$, where $M_\mathrm{Z}$ is
+\paragraph{Process-specific settings.}
+We use a fixed value for the renormalisation and factorisation scales $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$, where $M_\mathrm{Z}$ is
 the mass of the Z boson, for the ATLAS measurement, and the scale
 $\mu_\mathrm{R}=\mu_\mathrm{F}=M_{\ell\bar\ell}$, where $M_{\ell\bar\ell}$ is the central value of each
-invariant mass bin, for the CMS measurement.
-In the case of top-quark pair production, we use the dynamic scales
-$\mu_\mathrm{R}=\mu_\mathrm{F}=\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^\mathrm{t})^2}{\Big /}2$ for the distribution differential
-in the transverse momentum of the top quark, and $\mu_\mathrm{R}=\mu_\mathrm{F}=H_\mathrm{T}/4$ for the
-distribution differential in the invariant mass of the top-quark pair, where
-$H_\mathrm{T}=\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^\mathrm{t})^2}+\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^{\bar{\mathrm{t}}})}$, with $m_\mathrm{t}$,
-$p_\mathrm{T}^\mathrm{t}$ and $p_\mathrm{T}^{\bar{\mathrm{t}}}$ the mass of the top quark and the transverse momenta
-of the top and antitop quarks, respectively. These choices were demonstrated
-to maximise the convergence of the perturbative expansion~\cite{Czakon:2016dgf}.
-In the case of Z-boson production with non-zero transverse momentum, we use
-$\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$. In order to estimate the missing higher-order uncertainty,
-we allow the events to be reweighted on-the-fly in the Monte Carlo generation upon scale
-variations, with the technique presented in Ref.~\cite{Frederix:2011ss}. To this purpose, we use the default \textsc{MG5\_aMC}
-implementation, whereby the factorisation and renormalisation scales
-are varied down to a factor $1/2$ and up to a factor $2$, and the envelope
-from the nine-point scale variations is constructed. However, we note that
-\textsc{PineAPPL} allows the user to determine the envelope with any point
-prescription, see appendix~\ref{app:pineappl-demo} for an example.
-
-The values of the relevant physical parameters are chosen as
-\begin{equation}
-\begin{aligned}
-M_\mathrm{W} &= \SI{80}{\giga\electronvolt} \text{,} \quad &
-M_\mathrm{Z} &= \SI{91.176}{\giga\electronvolt} \text{,} \quad &
-m_\mathrm{t} &= \SI{172.5}{\giga\electronvolt} \text{,} \quad \\
-\Gamma_\mathrm{W} &= \SI{2.09}{\giga\electronvolt} \text{,} &
-\Gamma_\mathrm{Z} &= \SI{2.50}{\giga\electronvolt} \text{,}
-\end{aligned}
-\label{eq:parameters}
-\end{equation}
-where $M_\mathrm{W}$, $M_\mathrm{Z}$ and $m_\mathrm{t}$ are the values of the W-boson, Z-boson, and
-top quark masses, respectively, and $\Gamma_\mathrm{W}$ and $\Gamma_\mathrm{Z}$ are the width of
-the W boson and of the Z boson, respectively. The value of the strong
-coupling is chosen consistently with the PDF set, $\alphas(M_\mathrm{Z})=0.118$.
-When relevant, final-state photons and massless charged fermions (leptons and light quarks) are recombined together 
-if they satisfy the condition $\Delta R_{f \gamma}<0.1$, where $\Delta R_{f \gamma}$
-is the fermion-photon distance. In this case the
-sum of their momenta is assigned to the charged fermion, and the photon is removed
-from the event. Kinematics observables and cuts are defined starting from recombined momenta. If we were interested also in jet-related observables,
-photons surviving the recombination wouldl have to be clustered together with coloured
-partons.\footnote{For issues related to the definition of jets in presence of EW corrections,
-see refs.~\cite{Frederix:2016ost,Denner:2019zfp}.} Finally, although contributions corresponding to the radiation
-of a heavy boson are formally of the same perturbative order as the EW corrections, they are not included in our
-computations. In fact, while nothing prevents to include these contributions \emph{a posteriori}, as they are finite,
-their impact is either smaller than the one of ``standard'' EW corrections, or anyway negligible with respect to
-the total cross section (see refs.~\cite{Frixione:2014qaa,Frixione:2015zaa,Pagani:2016caq} for some process-specific cases {\bf MZ OTHERS???}).
-
-Finally, we implement the kinematic cuts specified in the corresponding
-experimental analyses. In the case of high-mass Drell--Yan lepton pair
-production at \SI{7}{\tera\electronvolt} measured by ATLAS, we require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$,
+invariant mass bin, for the CMS one. In the case of ATLAS, we require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$,
 $|\eta_\ell|<2.5$ and $\SI{116}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the transverse
 momentum and the pseudorapidity of each lepton and for the invariant mass of the
-lepton pair, respectively. In the case of double-differential Drell--Yan
-lepton-pair production
-at \SI{7}{\tera\electronvolt} measured by CMS, we require $p_\mathrm{T}^{\ell_1}>\SI{14}{\giga\electronvolt}$, $p_\mathrm{T}^{\ell_2}>\SI{9}{\giga\electronvolt}$,
+lepton pair, respectively. Conversely, in the case of CMS, we require $p_\mathrm{T}^{\ell_1}>\SI{14}{\giga\electronvolt}$, $p_\mathrm{T}^{\ell_2}>\SI{9}{\giga\electronvolt}$,
 $|\eta_\ell|<2.4$, $|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$
 for the transverse momentum and the pseudorapidity of each lepton, and for the
-pseudorapidity and the invariant mass of the lepton pair. In the case of Z-boson
-production with non-zero transverse momentum at \SI{13}{\tera\electronvolt} measured by CMS,
-require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$, $|\eta_\ell|<2.4$,
-$M_\mathrm{Z}-\SI{15}{\giga\electronvolt}<M_{\ell\bar\ell}<M_\mathrm{Z}+\SI{20}{\giga\electronvolt}$,
-$|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<p_\mathrm{T}^{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the
-transverse momentum and pseudorapidity of each lepton, and for the invariant mass,
-pseudorapidity and transverse momentum of the lepton pair. Imposing a minimum cut for the transverse momentum of the lepton pair 
-is necessary as we stick to a fixed-order computation, without including resummation effects.
+pseudorapidity and the invariant mass of the lepton pair.
 
-\subsection{Numerical results}
-\label{subsec:numerical_results}
-
-For each of the measurements discussed in
-section~\ref{subsec:processes_and_measurements}, we compute the expectation
-value of the corresponding observable for each kinematic bin in two different
-ways: directly, by means of \textsc{MG5\_aMC}, and a posteriori, by convolving
-the fast-interpolation grid produced by \textsc{PineAPPL} with the PDF set
-specified in section~\ref{subsec:computational_settings}. In the following, we
-will refer to the first result as the MC result, and to the second as
-the \textsc{PineAPPL} result. We repeat the computation for theories accurate
-to NLO QCD and to NLO QCD+EW, respectively. The corresponding orders of the
-strong and electroweak couplings that we consider have been specified in
-section~\ref{subsec:processes_and_measurements}. In each case, we determine the
-PDF uncertainty (coming from the PDF ensemble), the scale uncertainty (coming
-from variations of the factorisation and renormalisation scales), and the Monte
-Carlo uncertainty (coming from the finite number of events generated). In this
-last respect, we consider by default high-statistics computations, whereby we
-require a relative Monte Carlo precision of a fraction of per mille on the total cross section. While
-this choice does not affect the validation of the \textsc{PineAPPL} result
-against the MC result, it ensures that the statistical uncertainty of
-the computation remains negligible in comparison to the PDF and scale
-uncertainties, as we will explicitly demonstrate. This is a desirable feature
-to correctly interpret the size of the EW corrections.
-
-Our goal is indeed twofold. On the one hand, we aim to validate the
-interpolation grids generated with \textsc{PineAPPL}: to this purpose we shall
-verify that the MC and the \textsc{PineAPPL} results are identical up to
-numerical inaccuracies due to the grid interpolation. This equivalence must
-hold for any choice of renormalisation and factorisation scale and should not
-depend on the MC uncertainty of the binned cross section. On the other
-hand, we aim to study the size of the EW corrections, in particular with
-respect to the kinematics of each process, and to three kinds of uncertainties:
-the PDF uncertainty, the scale uncertainty, and the uncertainty of the
-experimental data.
-
-We present these comparisons in
-figures~\ref{fig:atlaszhighmass49fb}--\ref{fig:cmsZ13TeV} for each of the processes
-and data sets outlined in section~\ref{subsec:processes_and_measurements}.
-The format of the plots is the same across all figures. The first panel
-displays the relative difference (in per mille) between the {\sc PineAPPL} and
-the MC results for the central scale choice and upper/lower edges of the
-scale-uncertainty envelope, for
-theories accurate to both NLO QCD and NLO QCD+EW. The following three panels
-present the theoretical predictions, accurate to either NLO QCD or NLO QCD+EW,
-always normalised to the former; on top of the theoretical predictions, the
-PDF uncertainty, the scale uncertainty and the Monte Carlo uncertainty are
-displayed in turn. The relative uncertainty of the experimental data is
-also shown for comparison. We shall now discuss the results for each
-process and data set.
-
-\paragraph{Drell--Yan lepton pair production.}
-
+\paragraph{Numerical results.}
 We first consider the single-differential measurement at a high lepton-pair
@@
 transverse momentum of the top quark (the invariant mass of the top-quark pair)
-increases in the bin range; $\mathrm{\gamma}\mathrm{g}$ scattering
-correspondingly accounts for about 0.5\% -- 1\% (0.5\% -- 0.7\%) of the cross
-section, and is almost entirely {\bf MZ CHECK!!!} due to the LO contribution at $\mathcal{O}(\alphas\alpha)$; the contribution from other PI parton luminosities is comparatively
+increases; the largest PI contribution for this process is $\gamma\mathrm{g}$ scattering,
+which accounts for about 0.5\% -- 1\% (0.5\% -- 0.7\%) of the cross
+section, and is almost entirely (90\%) due to the LO contribution at $\mathcal{O}(\alphas\alpha)$; the contribution from other PI parton luminosities is comparatively
 negligible. Overall, the EW corrections suppress the $p_\mathrm{T}^\mathrm{t}$

### 2020-08-06 paper/app-pineappl.tex
Fix reference

@@
 The most important subcommand is \texttt{convolute}, which performs a convolution of a single grid with a single or multiple PDF sets.
-As an example we show the grid produced for the ATLAS Drell--Yan high-mass lepton-pair production from section~\ref{subsec:numerical_results}, convoluted with \texttt{NNPDF31\_nlo\_as\_0118\_luxqed} as the main PDF set and with \texttt{CT18NLO} as a second PDF set.
+As an example we show the grid produced for the ATLAS Drell--Yan high-mass lepton-pair production from section~\ref{sec:dy-lepton-pair-production}, convoluted with \texttt{NNPDF31\_nlo\_as\_0118\_luxqed} as the main PDF set and with \texttt{CT18NLO} as a second PDF set.
 \begin{verbatim}
@@
 
-The following run card was used to produce the results shown in section~\ref{subsec:numerical_results}.
+The following run card was used to produce the results shown in section~\ref{sec:dy-lepton-pair-production}.
 The only difference with respect to a standard \textsc{mg5\_aMC} run is the switch \texttt{set iappl 1}, which enables to fill a \textsc{PineAPPL} grid.

### 2020-08-06 paper/sec-pineappl.tex
Fix reference

@@
 However, the price one has to pay is the size of the 4-tuples.
-To give a concrete example, NLO QCD+EW Drell--Yan lepton-pair production (see section~\ref{sec:pineappl-example} and section~\ref{subsec:numerical_results}) needs \SI{159}{\giga\byte} of storage for a target precision of \SI{1}{\percent} of the integrated cross section.
+To give a concrete example, NLO QCD+EW Drell--Yan lepton-pair production (see section~\ref{sec:pineappl-example} and section~\ref{sec:dy-lepton-pair-production}) needs \SI{159}{\giga\byte} of storage for a target precision of \SI{1}{\percent} of the integrated cross section.
 While this is an acceptable size, increasing the precision by an order of magnitude would require roughly 100 times the size, due to the Monte Carlo convergence that goes as $1/\sqrt{N}$ with $N$ being the number of 4-tuples.

### 2020-08-07 paper/app-pineappl.tex
Add more smaller fixes

@@
 \end{verbatim}
-This program also needs \texttt{LHAPDF} \cite{Buckley:2014ana} installed.
+This program also needs \texttt{LHAPDF} \cite{Buckley:2014ana} installed; make sure that the environment variables \texttt{PATH}, \texttt{LD\_LIBRARY\_PATH}, and \texttt{PKG\_CONFIG\_PATH} are properly set.
 For usage instructions simply type \texttt{pineappl} in your shell and read the help message.

### 2020-08-07 paper/sec-conclusion.tex
Add more smaller fixes

@@
 
-Finally, we discussed the issue of subtracting EW corrections in experimental data, which becomes an important consideration when combining the interpolations grids with the corresponding experimental data in a PDF fit including EW and mixed QCD--EW corrections.
+Finally, we discussed the issue of subtracting EW corrections in experimental data, which becomes an important consideration when combining the interpolation grids with the corresponding experimental data in a PDF fit including EW and mixed QCD--EW corrections.
 

### 2020-08-07 paper/sec-introduction.tex
Add more smaller fixes

@@
 forthcoming twenty years of LHC operation. Nevertheless the statistical 
-uncertainty of the data has already shrunk to unprecedented small values,
+uncertainty of the data has already shrunk to unprecedentedly small values,
 typically \SI{1}{\percent} or less, a fact that will allow for precision tests of the
@@
 has been devoted to the computation of higher-order QCD corrections: 
-fully-differential next-to-leading order (NLO) results, possibly matched to the
+fully-differential next-to-leading order (NLO) results, possibly matched to a
 parton shower, are currently automated in various general-purpose
@@
 considered as such (e.g.\ the $t$-channel photon-induced component in
-neutral-current Drell--Yan, which is not a separate processes beyond the leading
+neutral-current Drell--Yan, which is not a separate processes beyond leading
 order) or of just a part of the EW effects (e.g.\ multiple-photon

### 2020-08-07 paper/sec-pineappl.tex
Add more smaller fixes

--- 2020-08-05 paper/sec-pineappl.tex
@@
 For many processes there is only one LO, but when a process has multiple quark lines, colourless (photons, \dots) and coloured particles (gluons, \ldots) can be exchanged between them, making it possible to have more than one LO.
-An important example at the LHC is dijet production, which has three different LOs: $\mathcal{O} (\alpha^2)$, $\mathcal{O} (\alphas \alpha)$, and $\mathcal{O} (\alpha^2)$.
+An important example at the LHC is (on-shell) top-pair production, which has three different LOs: $\mathcal{O} (\alpha^2)$, $\mathcal{O} (\alphas \alpha)$, and $\mathcal{O} (\alpha^2)$.
 Each LO receives a higher-order correction with an additional power of $\alphas$ or $\alpha$, which in general leads to at least two next-to-leading order (NLO) corrections.
@@
 
-Due to the typical sizes of the couplings $\alphas^2 \sim \alpha$, it is naively expected that within the same order, i.e.\ for fixed $k + l$, terms with larger powers $\alphas^k$ dominate over those with smaller powers.
+Due to the typical sizes of the couplings $\alphas^2 \sim \alpha$, it is naively expected that within the same order, i.e.\ for fixed $k + l$, terms with larger powers $\alphas^k$ dominate over those with smaller powers (and larger powers of $\alpha^l$).
 In practice, however, this naive expectation is not always true due to dynamic effects.
@@
 However, the price one has to pay is the size of the 4-tuples.
-To give a concrete example, NLO QCD+EW Drell--Yan lepton-pair production (see section~\ref{sec:pineappl-example} and section~\ref{subsec:numerical_results}) needs \SI{159}{\giga\byte} of storage for a target precision of \SI{1}{\percent} of the integrated cross section.
+To give a concrete example, NLO QCD+EW Drell--Yan lepton-pair production (see section~\ref{sec:pineappl-example} and section~\ref{sec:dy-lepton-pair-production}) needs \SI{159}{\mega\byte} of storage for a target precision of \SI{1}{\percent} of the integrated cross section.
 While this is an acceptable size, increasing the precision by an order of magnitude would require roughly 100 times the size, due to the Monte Carlo convergence that goes as $1/\sqrt{N}$ with $N$ being the number of 4-tuples.
@@
 The function $y(x)$ maps events with large $x$ effectively linearly and small $x$ effectively logarithmically onto $y$.
-This reflects our knowledge of PDFs, which behave differently in those regions, and thereby increases the precision of the interpolation.
+This reflects our knowledge of PDFs, which behave differently in those two regions, and thereby increases the precision of the interpolation.
 For the convolution of a grid with a PDF set also the inverse functions are needed, which are
@@
 
-To illustrate the filling step we give an example in figure~\ref{fig:grid}, where, for simplicity, we assume we have chosen a static scale, so that we do not need to interpolate in $\tau$ direction, and where we also limited the number of grid points to $N_y = 10$.
+To illustrate the filling step we give an example in figure~\ref{fig:grid}, where, for simplicity, we have chosen a static scale, so that we do not need to interpolate in $\tau$ direction, and where we also limited the number of grid points to $N_y = 10$.
 Each grid point has a numerical value $a_{i,j}$ associated, and the set of all numerical values $\{ a_{i,j} \}$ for all grid indices $(i,j) \in [0,N_y) \times [0,N_y)$ constitute \enquote{the grid}.
@@
 using $y_\text{min} = y(x_\text{max})$ and $y_\text{max} = y(x_\text{min})$ and the grid spacing $\Delta y = (y_\text{max} - y_\text{min})/(N_y-1)$, so that the integer part of $u(y)$ gives the grid index, e.g.\ $u(y_\text{min}) = 0$ and $u(y_\text{max}) = N_y - 1$, and the fractional part gives the location between the nearest grid points.
+
+% TODO: explain how convolutions are performed

### 2020-08-07 paper/sec-results.tex
Fix reference
Add more smaller fixes

@@
 sizeable effect on the accuracy of the theoretical predictions.
-In order to consider some realistic kinematics for these
-processes, we resort to measurements commonly devised for inclusion in PDF
+In order to consider realistic kinematics for these
+processes, we rely on the measurements that are commonly included in PDF
 fits. Our aim is twofold. First, we want to validate the results
 obtained with \textsc{PineAPPL}; second, we want to assess the
-impact of the EW corrections for usual experimental setups. We start by describing the
+impact of the EW corrections for the specific experimental setups. We start by describing the
 setup employed for the computation, then we discuss the features of each process, along with
@@
 \subsubsection{Drell--Yan lepton pair production.}
+\label{sec:dy-lepton-pair-production}
 

### 2020-08-07 paper/sec-introduction.tex
small tweaks+comments

@@
 become similar, $\alphas^2\sim \alpha$. If NNLO QCD corrections are included
-by default in PDF determinations, NLO EW and NLO QCD+EW corrections should be
+by default in PDF determinations, NLO EW corrections should be
 taken into account on the same footing. Second, the virtual exchange of soft or 
@@
 transverse-momentum distributions) enter both the determination of PDFs and the search
-for New Physics.
+for new physics.
 
@@
 fast-interpolation grids. The library supports variations of the factorisation
-and renormalisation scales, resummation, and matching with a photon- and/or
-parton-shower. The library is included by default in 
+and renormalisation scales. Planned extensions will include support for resummation and matching with a photon- and/or
+parton-shower {\bf MZ remove sentence if not true}. The library is included by default in 
 \textsc{MadGraph5\_aMC@NLO} (\textsc{MG5\_aMC} henceforth) within which it has
@@
 \textsc{SHERPA}~\cite{Biedermann:2017yoi}. In this respect, \textsc{PineAPPL}
-supersedes \textsc{aMCfast}~\cite{Bertone:2014zva} and complements
+supersedes \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{aMCfast}~\cite{Bertone:2014zva}, and complements
 \textsc{MCgrid}~\cite{DelDebbio:2013kxa,Bothmann:2015dba}.
@@
 have a sizeable effect on the accuracy of the theoretical predictions.
-In section~\ref{sec:doublecounting} we use these results to formulate more
-comprehensively the second problem sketched above, the solution of which, 
+In section~\ref{sec:doublecounting} we try to detail in a more
+comprehensive maneer the second problem sketched above, the solution of which, 
 however, remains beyond the scope of the current work. We provide our

### 2020-08-07 paper/sec-pineappl.tex
small tweaks+comments

@@
 In fact, \textsc{PineAPPL} allows arbitrary initial-state combinations, e.g.\ leptonic initial states~\cite{Bertone:2015lqa,Buonocore:2020nai}.
-\item The estimate of theory uncertainty via variations of the renormalisation and factorisation scale (the electroweak coupling is assumed to be scale-independent, consistently with the most common renormalisation schemes).
+\item The estimate of theory uncertainties via variations of the renormalisation and factorisation scale (the electroweak coupling is assumed to be scale-independent, consistently with the most common renormalisation schemes).
 \end{itemize}
@@
 
-We have interfaced \textsc{PineAPPL} with the new version (v3+) of \textsc{mg5\_aMC}~\cite{Alwall:2014hca,Frederix:2018nkq}\footnote{It can be downloaded from \url{https://code.launchpad.net/~amcblast/+junk/3.0.2}, and will soon be merged in the official code release.}, where it will replace the \textsc{aMCfast}~\cite{Bertone:2014zva} interface.
+We have interfaced \textsc{PineAPPL} with the new version (v3+) of \textsc{mg5\_aMC}~\cite{Alwall:2014hca,Frederix:2018nkq}\footnote{It can be downloaded from \url{https://launchpad.net/mg5amc-pineappl/trunk}, and will soon be merged in the official code release.}, where it will replace the \textsc{aMCfast}~\cite{Bertone:2014zva} interface.
 Its usage is very similar to that of \textsc{mg5\_aMC v2}+\textsc{aMCfast}+\textsc{APPLgrid}.
@@
 
-Fixed-order partonic cross sections $a + b \to X$ supported by \textsc{PineAPPL} are expansions in powers of the strong coupling $\alphas$, the electromagnetic coupling $\alpha$, and the logarithms of $\xi_\mathrm{R} = \mu_\mathrm{R} / Q$ and $\xi_\mathrm{F} = \mu_\mathrm{F} / Q$,
+Fixed-order partonic cross sections $a + b \to X$ supported by \textsc{PineAPPL} are written as an expansion in powers of the strong coupling $\alphas$, the electromagnetic coupling $\alpha$, and the logarithms of $\xi_\mathrm{R} = \mu_\mathrm{R} / Q$ and $\xi_\mathrm{F} = \mu_\mathrm{F} / Q$,
 \begin{multline}
@@
 The terms with powers $m > 0$ and $n > 0$ vanish for the central scale choice and are only required for variations of the factorisation and renormalisation scales.
-To estimate the perturbative QCD uncertainty --- no EW uncertainty is covered by this method --- one typically uses a 7-point scale variation, which evaluates the cross section using the following values,
+To estimate the perturbative QCD uncertainty --- no EW uncertainty is covered by this method --- one typically uses a 7-point scale variation, {\bf MZ warning, this is not what we do later} which evaluates the cross section using the following values,
 \begin{equation}
@@
 All remaining corrections are of mixed type, meaning that they, in general, cannot be attributed to either one of strong or electroweak origin.
+However, for the sake of simplicity and with a slight abuse of notation, it is customary to refer
+as NLO QCD (EW) corrections as
+corrections of order $\alphas$ ($\alpha$) times the couplings of the LO contribution 
+with the largest power of $\alphas$. In the example above, NLO QCD and EW corrections to top pair production will denote
+respectively those at $\mathcal{O} (\alphas^3 )$ and $\mathcal{O} (\alphas^2 \alpha)$. In this paper, in particular
+when discussing results in sec.~\ref{sec:results}, we will explicitly list the orders that are considered in the cross
+section at LO, NLO QCD and NLO QCD+EW accuracy.
 %Sometimes there are higher orders that cannot directly be understood as a correction to a LO, e.g.\ $\mathrm{p} \mathrm{p} \to \ell \bar{\ell} + \mathrm{jet} + X$, which has one LO, $\mathcal{O} (\alphas \alpha^2)$, but three NLOs, one of which is $\mathcal{O} (\alpha^4)$~TODO.

### 2020-08-07 applgriddiff/src/diffs.cpp
Remove `applgriddiff`

@@ -1,282 +1,0 @@
-#include "applgriddiff.hpp"
-
-#include <algorithm>
-#include <cstddef>
-#include <iostream>
-#include <string>
-#include <vector>
-
-#include <TH3.h>
-#include <TKey.h>
-
-bool diff_directory(TDirectory& dir1, TDirectory& dir2)
-{
-    auto dir1_keys = dir1.GetListOfKeys();
-    auto dir2_keys = dir2.GetListOfKeys();
-
-    std::vector<std::string> dir1_names;
-    std::vector<std::string> dir2_names;
-
-    for (auto const& key : *dir1_keys)
-    {
-        dir1_names.emplace_back(key->GetName());
-    }
-
-    for (auto const& key : *dir2_keys)
-    {
-        dir2_names.emplace_back(key->GetName());
-    }
-
-    if (dir1_names.size() != dir2_names.size())
-    {
-        std::cout << ">>> files have different structures\n";
-        return true;
-    }
-
-    std::sort(dir1_names.begin(), dir1_names.end());
-    std::sort(dir2_names.begin(), dir2_names.end());
-
-    if (!std::equal(dir1_names.begin(), dir1_names.end(), dir2_names.begin()))
-    {
-        std::cout << ">>> files have different structures\n";
-        return true;
-    }
-
-    bool diff = false;
-
-    for (auto const& name : dir1_names)
-    {
-        auto* cls1 = dir1.FindKey(name.c_str())->GetClassName();
-        auto* cls2 = dir1.FindKey(name.c_str())->GetClassName();
-
-        if ((cls1 != std::string("TFileString")) && (cls2 != std::string("TFileString")))
-        {
-            auto* obj1 = dir1.Get(name.c_str());
-            auto* obj2 = dir2.Get(name.c_str());
-
-            if ((obj1 == nullptr) && (obj2 == nullptr))
-            {
-                std::cout << "???\n";
-                continue;
-            }
-
-            diff &= dispatch_and_diff(*obj1, *obj2);
-        }
-        else
-        {
-            std::cout << ">>> ignoring unknown TFileString objects\n";
-        }
-    }
-
-    return diff;
-}
-
-bool diff_histogram(TH1 const& obj1, TH1 const& obj2)
-{
-    if (obj1.GetNbinsX() != obj2.GetNbinsX())
-    {
-        std::cout << ">>> files have different structures\n";
-
-        return true;
-    }
-    else if (obj1.GetNbinsY() != obj2.GetNbinsY())
-    {
[…]

### 2020-08-07 applgriddiff/src/main.cpp

@@ -1,40 +1,0 @@
-#include "applgriddiff.hpp"
-
-#include <iostream>
-#include <memory>
-#include <string>
-#include <vector>
-
-#include <TFile.h>
-
-std::unique_ptr<TFile> load_root_file(std::string const& file)
-{
-    return std::unique_ptr<TFile>{new TFile{file.c_str()}};
-}
-
-void print_help()
-{
-    std::cout << "Usage: applgriddiff file1 file2\n";
-}
-
-int main(int argc, char* argv[])
-{
-    // store arguments in a vector
-    std::vector<std::string> args(argv, argv + argc);
-
-    if (args.size() != 3)
-    {
-        print_help();
-
-        return -1;
-    }
-
-    // TODO: make sure both files actually exist
-
-    auto file1 = load_root_file(args[1]);
-    auto file2 = load_root_file(args[2]);
-
-    bool const diff = dispatch_and_diff(*file1, *file2);
-
-    return diff ? 1 : 0;
-}

### 2020-08-07 run.sh
Use `pineappl` instead of the old programs

@@ -32,17 +32,10 @@ check_args_and_cd_output() {
         exit 1
     fi
 
-    applcheck=$(which applcheck 2> /dev/null || true)
+    pineappl=$(which pineappl 2> /dev/null || true)
 
-    if [[ ! -x ${applcheck} ]]; then
-        echo "The binary \`applcheck\` wasn't found. Please adjust your PATH variable" >&2
-        exit 1
-    fi
-
-    merge_bins=$(which merge_bins 2> /dev/null || true)
-
-    if [[ ! -x ${merge_bins} ]]; then
-        echo "The binary \`merge_bins\` wasn't found. Please adjust your PATH variable" >&2
+    if [[ ! -x ${pineappl} ]]; then
+        echo "The binary \`pineappl\` wasn't found. Please adjust your PATH variable" >&2
         exit 1
     fi
 
@@ -133,37 +126,39 @@ EOF
 
     # TODO: the following assumes that all observables belong to the same distribution
 
+    grid="${dataset}".pineappl
+
     # merge the final bins
-    "${merge_bins}" "${dataset}".root $(ls -v "${dataset}"/Events/run_01*/amcblast_obs_*.root)
+    "${pineappl}" merge "${grid}" $(ls -v "${dataset}"/Events/run_01*/amcblast_obs_*.root)
+
+    lz4=$(which lz4 2> /dev/null || true)
+
+    # compress the grid with `lz4` if it's available
+    if [[ -x ${lz4} ]]; then
+        lz4 -9 "${grid}"
+        rm "${grid}"
+        grid="${grid}.lz4"
+    fi
 
     # find out which PDF set was used to generate the predictions
     pdfstring=$(grep "set lhaid" "${launch_file}" | sed 's/set lhaid \([0-9]\+\)/\1/')
 
     # (re-)produce predictions
-    "${applcheck}" "${pdfstring}" "${dataset}".root > applcheck.log
+    "${pineappl}" convolute "${grid}" "${pdfstring}" --scales 9 > pineappl.convolute
+    "${pineappl}" orders "${grid}" "${pdfstring}" --absolute > pineappl.orders
+    "${pineappl}" pdf_uncertainty "${grid}" "${pdfstring}" > pineappl.pdf_uncertainty
 
     # extract the numerical results from mg5_aMC
     sed '/^  [+-]/!d' "${dataset}"/Events/run_01*/MADatNLO.HwU > results.mg5_aMC
 
-    # extract the numerical results from the APPLgrid
-    sed -e '1,/all bins:/d' \
[…]

### 2020-08-07 applgridphoton/appl_grid/SparseMatrix3d.h
Remove applgridphoton

@@ -1,75 +1,0 @@
-// emacs: this is -*- c++ -*-
-//
-//   SparseMatrix3d.h        
-//
-//                   
-// 
-//   Copyright (C) 2007 M.Sutton (sutt@hep.ucl.ac.uk)    
-//
-//   $Id: SparseMatrix3d.h, v1.0   Wed Nov 14 14:23:49 GMT 2007 sutt
-
-
-#ifndef __SPARSEMATRIX3D_H
-#define __SPARSEMATRIX3D_H
-
-#include "axis.h"
-#include "tsparse3d.h"
-
-class SparseMatrix3d : public tsparse3d<double> {
-
-public:
-
-  // constructors and destructor
-
-  SparseMatrix3d( int Nx, double lx, double ux, 
-		  int Ny, double ly, double uy, 
-		  int Nz, double lz, double uz);
-
-  SparseMatrix3d(const SparseMatrix3d& s); 
-
-  // axis accessors
-  const axis<double>& xaxis() const { return m_xaxis; } 
-  const axis<double>& yaxis() const { return m_yaxis; } 
-  const axis<double>& zaxis() const { return m_zaxis; } 
-
-
-  // trim to sparse structure 
-  void trim() { tsparse3d<double>::trim(); }
-
-  void fill(double x, double y, double z, double w);
-  
-  /// check if the axes are all the same
-  bool compare_axes(const SparseMatrix3d& s) const { 
-
-    return ( m_xaxis == s.m_xaxis &&  
-	     m_yaxis == s.m_yaxis &&
-	     m_zaxis == s.m_zaxis );
-   
-  }
-
-
-  /// checks if the actual contents are the same
-  bool operator==(const SparseMatrix3d& s) const;
-
-  bool operator!=(const SparseMatrix3d& s) const { 
-    return !( *this == s );
-  }
-
-
-private:
-  axis<double> m_xaxis;
-  axis<double> m_yaxis;
-  axis<double> m_zaxis;
-};
-
-#endif  // __SPARSEMATRIX3D_H 
-
-
-
-
-
-
-
-
-
-

### 2020-08-07 applgridphoton/appl_grid/appl_grid.h

@@ -1,276 +1,0 @@
-// emacs: this is -*- c++ -*-
-
-//  appl_grid.h       
-
-//  grid class header - all the functions needed to create and 
-//  fill the grid from an NLO calculation program
-//  
-//  Copyright (C) 2007 Mark Sutton (sutt@hep.ucl.ac.uk)    
-
-// $Id: appl_grid.h, v1.00 2007/10/16 17:01:39 sutt
-
-// Fixme: this needs to be tidied up. eg there are too many different, 
-//        and too many version of, accessors for x/y, Q2/tau etc there 
-//        should be only  one set, for x and Q2 *or* y and tau, but 
-//        not both. In fact they should be for x and Q2, since y and tau 
-//        should be purely an internal grid issue of no concern for the 
-//        user.
-
-#ifndef __APPL_PHOTON
-#define __APPL_PHOTON
-#endif
-
-#ifndef __APPL_GRID_H
-#define __APPL_GRID_H
-
-#include "histo1d.hpp"
-
-#include <exception>
-#include <iosfwd>
-#include <string>
-#include <vector>
-
-namespace appl { 
-
-
-/// forward declarations - full definitions included 
-/// from appl_grid.cxx 
-class igrid;
-class appl_pdf;
-
-class order_id
-{
-public:
-    order_id(int alphs, int alpha, int lmuf2, int lmur2)
-        : alphs_{alphs}
-        , alpha_{alpha}
-        , lmuf2_{lmuf2}
-        , lmur2_{lmur2}
-    {
-    }
-
-    int alphs() const
-    {
-        return alphs_;
-    }
-
-    int alpha() const
-    {
-        return alpha_;
-    }
-
-    int lmuf2() const
-    {
-        return lmuf2_;
-    }
-
-    int lmur2() const
-    {
-        return lmur2_;
-    }
-
-private:
-    int alphs_;
-    int alpha_;
-    int lmuf2_;
-    int lmur2_;
-};
-
-inline bool operator==(order_id const& a, order_id const& b)
-{
-    return (a.alphs() == b.alphs()) && (a.alpha() == b.alpha()) && (a.lmuf2() == b.lmuf2())
-        && (a.lmur2() == b.lmur2());
-}
-
-/// externally visible grid class
-class grid {
-
-public:
-
-  // grid error exception
-  class exception : public std::exception { 
-  public:
-    exception(const std::string& s);
-    exception(std::ostream&);
[…]

### 2020-08-07 applgridphoton/appl_grid/appl_pdf.h

@@ -1,189 +1,0 @@
-// emacs: this is -*- c++ -*-
-//
-//   appl_pdf.h        
-//
-//   pdf transform functions header                  
-// 
-//   Copyright (C) 2007 M.Sutton (sutt@hep.ucl.ac.uk)    
-//
-//   $Id: appl_pdf.h, v   Fri Dec 21 22:19:50 GMT 2007 sutt $
-
-
-#ifndef __APPL_PDF_H
-#define __APPL_PDF_H
-
-#include <iostream>
-#include <fstream>
-#include <sstream>
-
-#include <exception>
-#include <vector> 
-#include <map> 
-#include <string> 
-
-#include <exception> 
-
-
-namespace appl { 
-
-
-class appl_pdf;
-
-typedef std::map<const std::string, appl_pdf*> pdfmap;
-
-
-// this is a *maybe* nice class, a base class for pdf 
-// functions
-//
-// it has a virtual evaluate() method to be definied in 
-// the derived class, and a static std::map of all the names
-// of instances of the derived classes
-//
-// when a new instance of the class is created, it 
-// automatically adds it's name to the std::map, so the user 
-// doesn't need to worry about consistency, and removes 
-// itself when the derived instance is deleted
-
-class appl_pdf { 
-
-public:
-
-  // pdf error exception
-  class exception : public std::exception { 
-  public: 
-    exception(const std::string& s="");
-    exception(std::ostream&);
-    const char* what() const noexcept;
-  };
-  
-public:
-
-  /// constructor and destructor
-  appl_pdf(const std::string& name);
-
-  virtual ~appl_pdf();
-
-  /// retrieve an instance from the std::map 
-  static appl_pdf* getpdf(const std::string& s, bool printout=true);
-  
-  /// initialise the factory  
-  static bool create_map(); 
-
-  virtual void evaluate(const double* fA, const double* fB, double* H) = 0; 
-
-  virtual int decideSubProcess( const int , const int  ) const;
-
-  std::string   name() const { return m_name;  }
-
-  int     Nproc() const { return m_Nproc; } 
-  int     size()  const { return m_Nproc; } 
-
-
-
-  std::string  rename(const std::string& name) { 
-    /// remove my entry from the std::map, and add me again with my new name
-    if ( __pdfmap.find(m_name)!=__pdfmap.end() ) { 
-      __pdfmap.erase(__pdfmap.find(m_name));
-    }
-    else { 
[…]

### 2020-08-07 applgridphoton/appl_grid/histo1d.hpp

@@ -1,29 +1,0 @@
-#ifndef APPL_GRID_HISTO1D_HPP
-#define APPL_GRID_HISTO1D_HPP
-
-//#include <cstddef>
-
-namespace appl
-{
-
-class histo1d
-{
-public:
-    histo1d(void* pointer);
-
-    int Fill(double x, double w);
-    void Scale(double c);
-    double GetBinContent(int bin) const;
-    void SetBinContent(int bin, double content);
-    int GetNbinsX() const;
-    double GetBinWidth(int bin) const;
-
-    void* pointer() const;
-
-private:
-    void* pointer_;
-};
-
-}
-
-#endif

### 2020-08-07 applgridphoton/appl_grid/lumi_pdf.h

@@ -1,108 +1,0 @@
-// emacs: this is -*- c++ -*-
-//
-//   @file    lumi_pdf.h        
-//
-//            a lumi pdf type - to read in the combinations
-//            for the subprocesses from a file
-//
-//            the file format is as from madgraph nproc rows ...
-//
-//              index  npairs   p1 p2   p3 p4   p5 p6 ...  
-//              index  npairs   ...
-//              ...
-//
-//            where  npairs is the number of parton-parton pairs
-//            in this subprocess
-//
-//  
-//   Copyright (C) 2013 M.Sutton (sutt@cern.ch)    
-//
-//   $Id: lumi_pdf.h, v0.0   Mon 28 Jan 2013 15:41:10 GMT sutt $
-
-
-#ifndef  LUMI_PDF_H
-#define  LUMI_PDF_H
-
-#include <iostream>
-
-#include "appl_grid/appl_pdf.h" 
-#include "appl_grid/combination.h"
-
-
-class lumi_pdf : public appl::appl_pdf {
-
-public:
-
-  lumi_pdf(const std::string& s="", const std::vector<int>& combinations=std::vector<int>() );   // , int Wcharge=0 );
-
-  lumi_pdf(const std::string& s, const std::vector<combination>& combinations, int ckmcharge=0 );             // , int Wcharge=0 );
-
-  virtual ~lumi_pdf() {   } 
-
-  void evaluate(const double* _fA, const double* _fB, double* H);
-
-  /// additional user defined functions to actually initialise 
-  /// based on the input file
-
-  /// how many combinations of subprocesses are there ?
-  unsigned size() const { return m_combinations.size(); }
- 
-  //  void initialise(const std::string& filename);
-
-  //  bool initialised() const { return m_initialised; }
-
-  const combination& operator[](int i) const { return m_combinations.at(i); }  
-
-  int  decideSubProcess(const int iflav1, const int iflav2) const ;
-
-  std::vector<int> serialise() const;
-
-  void write(const std::string& filename) const;
- 
-  void write(std::ostream& s=std::cout) const; 
-
-  //  std::string summary(std::ostream& s=std::cout) const; 
-  std::string summary() const; 
-  
-private:
-
-  /// add a combination
-  void add(const combination& c) {  m_combinations.push_back(c); }
-
-  void create_lookup();
-
-private:
-
[…]

### 2020-08-07 applgridphoton/appl_grid/tsparse2d.h

@@ -1,348 +1,0 @@
-// emacs: this is -*- c++ -*-
-//
-//   tsparse2d.h        
-//
-//   very basic 2d sparse matrix class, needs to be improved, 
-//   and extended to 3d.
-//
-//   NB: be VERY CAREFUL about the use of the (i,j) index operator, 
-//       since it checks to see whether the given element exists,
-//       and if not, it creates it, so even viewing it such as...
-//
-//          tsparse2d<...> d(10,10); std::cout << a(2,3) << std::endl;                    
-//
-//       will create the element if it doesn't exist *unless* you 
-//       are looking at a const tsparse2d<...>
-// 
-//   Copyright (C) 2007 M.Sutton (sutt@hep.ucl.ac.uk)    
-//
-//   $Id: tsparse2d.h, v1.0   Fri Nov  9 00:17:31 CET 2007 sutt
-
-
-#ifndef __TSPARSE2D_H
-#define __TSPARSE2D_H
-
-#include <iostream>
-
-#include <iomanip>
-
-#include <cmath>
-
-
-
-#include "tsparse1d.h"
-
-
-template<class T> 
-class tsparse2d : public tsparse_base {
-
-#if 0
-public:
-
-  class exception { 
-  public:
-    exception(const std::string& s) { cerr << s << std::endl; }; 
-    exception(ostream&) { cerr << s << std::endl; };
-  };
-#endif
-
-public:
-
-  tsparse2d(int nx, int ny) : tsparse_base(nx), m_Ny(ny), m_v(NULL) {  
-    m_v = new tsparse1d<T>*[m_Nx];
-    for ( int i=0 ; i<Nx() ; i++ ) m_v[i] = new tsparse1d<T>(m_Ny);
-  }
-
-  tsparse2d(int nx, int ny, int lx, int ly, int _size=1, int _sizey=1) : tsparse_base(nx, lx, _size), m_Ny(ny), m_v(NULL) {  
-    if ( _size ) m_v = new tsparse1d<T>*[_size];
-    for ( int i=0 ; i<_size ; i++ ) m_v[i] = new tsparse1d<T>(m_Ny,ly, _sizey);
-  }
-
-
-  
-  ~tsparse2d() { 
-    if ( m_v ) { 
[…]

### 2020-08-07 applgridphoton/appl_grid/tsparse3d.h

@@ -1,109 +1,0 @@
-// emacs: this is -*- c++ -*-
-//
-//   tsparse3d.h        
-//
-//   very basic 3d sparse matrix class, needs to be improved, 
-//   and extended to 3d                   
-// 
-//   Copyright (C) 2007 M.Sutton (sutt@hep.ucl.ac.uk)    
-//
-//   $Id: tsparse3d.h, v   Fri Nov  9 00:17:31 CET 2007 sutt
-
-
-#ifndef __TSPARSE3D_H
-#define __TSPARSE3D_H
-
-#include <iostream>
-
-#include "tsparse2d.h"
-
-
-template<class T> 
-class tsparse3d : public tsparse_base {
-
-public:
-
-  tsparse3d(int nx, int ny, int nz);
-
-  tsparse3d(const tsparse3d& t);
-
-  ~tsparse3d();
-
-  // accessors
-  int Ny() const { return m_Ny; } 
-  int Nz() const { return m_Nz; } 
-
-
-
-  void trim();
-
-  void untrim();
-
-  bool trimmed() const { return m_trimmed; }
-
-  bool trimmed(int i, int j, int k) const;
-
-  T operator()(int i, int j, int k) const;
-
-  const tsparse2d<T>* operator[](int i) const;
-
-  T& operator()(int i, int j, int k);
-
-  int size() const;
-
-  void print() const;
-
-  int ymin();
-
-  int ymax();
-
-  int zmin();
-
-  int zmax();
-
-
-  // algebraic operators
-
-  tsparse3d& operator=(const tsparse3d& t);
-
-  tsparse3d& operator*=(const double& d);
-
-  tsparse3d& operator+=(const tsparse3d& t) {
-    m_trimmed = false;
-    if ( Nx()!=t.Nx() || Ny()!=t.Ny() || Nz()!=t.Nz() ) throw out_of_range("bin mismatch");
-    for ( int i=0 ; i<Nx() ; i++ ) {
-      for ( int j=0 ; j<Ny() ; j++ ) {
-	for ( int k=0 ; k<Nz() ; k++ ) (*this)(i,j,k) += t(i,j,k);
-      }
-    }
-    return *this;
-  }
-
-private:
-
-  void grow(int i);
-
-protected:
-  
-  int m_Ny;
-  int m_Nz;
-  
-  tsparse2d<T>**  m_v;
-  
-  //  T** m_fastindex;
-  
[…]

### 2020-08-07 applgridphoton/appl_grid/tsparse_base.h

@@ -1,91 +1,0 @@
-// emacs: this is -*- c++ -*-
-//
-//   tsparse_base.h        
-//
-//   base class for common range checking and utilities for generic 
-//   sparse matrix classes
-//                   
-// 
-//   Copyright (C) 2007 M.Sutton (sutt@hep.ucl.ac.uk)    
-//
-//   $Id: tsparse_base.h, v0.0   Thu Nov 22 01:28:27 GMT 2007 sutt
-
-
-#ifndef __TSPARSE_BASE_H
-#define __TSPARSE_BASE_H
-
-#include <iostream>
-
-
-#include <cmath>
-
-
-class tsparse_base {
-
-public: 
-
-  // range exception
-  class out_of_range { 
-  public: 
-    out_of_range(const std::string& s="out of range");
-  };
-
-public:
-  
-  // constructors etc
-
-  tsparse_base()       : m_Nx(0),  m_lx(1),  m_ux(0)    { }
-  tsparse_base(const int& nx) : m_Nx(nx), m_lx(0),  m_ux(nx-1) { } 
-  tsparse_base(const int& nx, const int& lx, const int& _size=1)  
-    : m_Nx(nx), m_lx(lx), m_ux(lx+_size-1) { } 
-
-  virtual ~tsparse_base() { } 
-
-
-  // access functions
-
-  int Nx() const { return m_Nx; } 
-  int lo() const { return m_lx; }
-  int hi() const { return m_ux; }
-
-  virtual int size() const { return m_ux-m_lx+1; } //  + 3*sizeof(int); } 
-
-  bool trimmed(int i) const { return ( i<m_lx || i>m_ux ? false : true );  } 
-
-  // make sure index is not out of range
-  void range_check(int i) const { if ( i<0 || i>m_Nx-1 ) { 
-      std::cerr << "index i=" << i << std::endl;
-      throw out_of_range(); 
-    }    
-  } 
-
-  bool operator==(int i) const { return size()==i; } 
-
-  int xmin() { return m_lx; } 
-  int xmax() { return m_ux; } 
-
-  // shouldn't really be in here, it's just for printing 
-  static double mant(double x) { 
-    return  x/std::pow(10.,int(std::log10(std::fabs(x))+128)-128);
-  }
-
-protected:
-
-  int m_Nx; // number of elements
-  int m_lx; // indices of lowest and highest occupied 
[…]

### 2020-08-07 applgridphoton/include/pineappl_capi.h

@@ -1,259 +1,0 @@
-/*
- * PineAPPL - PineAPPL is not an extension of APPLgrid
- * Copyright (C) 2019-2020  Christopher Schwan
- *
- * This program is free software: you can redistribute it and/or modify
- * it under the terms of the GNU General Public License as published by
- * the Free Software Foundation, either version 3 of the License, or
- * (at your option) any later version.
- *
- * This program is distributed in the hope that it will be useful,
- * but WITHOUT ANY WARRANTY; without even the implied warranty of
- * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- * GNU General Public License for more details.
- *
- * You should have received a copy of the GNU General Public License
- * along with this program.  If not, see <https://www.gnu.org/licenses/>.
- */
-
-#ifndef PINEAPPL_H
-#define PINEAPPL_H
-
-/* Generated with cbindgen:0.14.1 */
-
-#include <stdbool.h>
-#include <stdint.h>
-
-/**
- * Main data structure of `PineAPPL`. This structure contains a `Subgrid` for each `LumiEntry`,
- * bin, and coupling order it was created with.
- */
-typedef struct pineappl_grid pineappl_grid;
-
-/**
- * Key-value storage for passing optional information during grid creation with
- * `pineappl_grid_new`.
- */
-typedef struct pineappl_keyval pineappl_keyval;
-
-/**
- * Type for defining a luminosity function.
- */
-typedef struct pineappl_lumi pineappl_lumi;
-
-#ifdef __cplusplus
-extern "C" {
-#endif // __cplusplus
-
-/**
- * Returns the number of bins in `grid`.
- */
-uintptr_t pineappl_grid_bin_count(const pineappl_grid *grid);
-
-/**
- * Stores the bin sizes of `grid` in `bin_sizes`.
- */
-void pineappl_grid_bin_sizes(const pineappl_grid *grid, double *bin_sizes);
-
-/**
- * Convolutes the specified grid with the PDFs `xfx1` and `xfx2` and strong coupling `alphas`.
- * These functions must evaluate the PDFs for the given `x` and `q2` and write the results for all
- * partons into `pdfs`. Note that the value must be the PDF for the given `pdg_id` multiplied with
- * `x`. The value of the pointer `state` provided to these functions is the same one given to this
- * function. The parameter `order_mask` must be as long as there are perturbative orders contained
[…]

### 2020-08-07 applgridphoton/src/Directory.h

@@ -1,70 +1,0 @@
-// emacs: this is -*- c++ -*-
-/**************************************************************************
- **
- **   File:         appl_grid/Directory.h  
- **
- **   Description:  class to keep a directory for each object 
- **                 in a root sort of way, but needed to keep 
- **                 the root objects out of the actual code.   
- ** 
- **   Author:       M.Sutton  
- **
- **   Created:      Wed May  4 17:54:25 BST 2005
- **   Modified:     
- **                   
- **                   
- **
- **************************************************************************/ 
-
-
-#ifndef __DIRECTORY_H
-#define __DIRECTORY_H
-
-#include "TDirectory.h"
-
-// #include "utils.h"
-
-class Directory {
-
- public:
-
-  Directory() : mDir(NULL), mPop(NULL) { } 
-  Directory(std::string n) : mDir(NULL) { 
-    mPop = gDirectory;
-    //    depunctuate(n);
-    mDir = gDirectory->mkdir(n.c_str());
-  } 
-
-  void push() { 
-    mPop = gDirectory;
-    if (mDir) mDir->cd();
-  } 
-
-  void pop() { if (mPop) mPop->cd(); }
-
-  void Write() { 
-    push();
-    mDir->Write();
-    pop();
-  } 
-
- private:
-  
-  TDirectory* mDir;
-  TDirectory* mPop;
-
-};
-
-
-
-#endif  /* __DIRECTORY_H */
-
-
-
-
-
-
-
-
-
-

### 2020-08-07 applgridphoton/src/applcheck.cpp

@@ -1,120 +1,0 @@
-#include <algorithm>
-#include <array>
-#include <cstddef>
-#include <iostream>
-#include <memory>
-#include <vector>
-
-#include <LHAPDF/LHAPDF.h>
-#include <pineappl_capi.h>
-
-double xfx(int32_t pdg_id, double x, double q2, void* state)
-{
-    auto* pdf = static_cast <LHAPDF::PDF*> (state);
-    return pdf->xfxQ2(pdg_id, x, q2);
-}
-
-double alphas(double q2, void* state)
-{
-    auto* pdf = static_cast <LHAPDF::PDF*> (state);
-    return pdf->alphasQ2(q2);
-}
-
-int main(int argc, char* argv[])
-{
-    // set LHAPDF low verbosity
-    LHAPDF::setVerbosity(0);
-
-    if (argc != 3)
-    {
-        std::cerr << "Usage: applcheck PDF-set-name/LHAID applgrid-file\n";
-        return 1;
-    }
-
-    std::unique_ptr<LHAPDF::PDF> pdf;
-
-    auto* g = pineappl_grid_read(argv[2]);
-
-    int lhaid = -1;
-
-    try
-    {
-        lhaid = std::stoi(argv[1]);
-    }
-    catch (...)
-    {
-    }
-
-    // initialise the PDF set via LHAPDF6
-    if (lhaid == -1)
-    {
-        pdf.reset(LHAPDF::mkPDF(argv[1], 0));
-    }
-    else
-    {
-        pdf.reset(LHAPDF::mkPDF(lhaid));
-    }
-
-    std::vector<uint32_t> orders(4 * pineappl_grid_order_count(g));
-    pineappl_grid_order_params(g, orders.data());
-
-    std::vector<double> bins(pineappl_grid_bin_count(g));
-    std::vector<double> bin_sizes(bins.size());
-    pineappl_grid_bin_sizes(g, bin_sizes.data());
-
-    std::cout << "\n>>> all bins, all orders:\n\n";
-
-    for (std::size_t i = 0; i != orders.size() / 4; ++i)
-    {
-        if ((orders.at(4 * i + 2) != 0) || (orders.at(4 * i + 3) != 0))
-        {
-            continue;
-        }
-
-        auto const alphas = orders.at(4 * i + 0);
-        auto const alpha = orders.at(4 * i + 1);
-
-        bool* order_mask = new bool[orders.size() / 4]();
-
-        order_mask[i] = true;
-
[…]

### 2020-08-07 applgridphoton/src/merge_bins.cpp

@@ -1,27 +1,0 @@
-#include <pineappl_capi.h>
-
-#include <iostream>
-#include <string>
-#include <vector>
-
-int main(int argc, char* argv[])
-{
-    if (argc < 3)
-    {
-        std::cerr << "Usage: merge_bins outgrid grid1 [grid2 ...]\n";
-
-        return 1;
-    }
-
-    std::vector<std::string> args(&argv[3], &argv[argc]);
-
-    auto* grid = pineappl_grid_read(argv[2]);
-
-    for (auto const& arg : args)
-    {
-        auto* other = pineappl_grid_read(arg.c_str());
-        pineappl_grid_merge_and_delete(grid, other);
-    }
-
-    pineappl_grid_write(grid, argv[1]);
-}

### 2020-08-07 applgridphoton/src/pineappl_capi.cpp

@@ -1,500 +1,0 @@
-#include "pineappl_capi.h"
-
-#include "appl_grid/appl_igrid.h"
-#include "appl_grid/appl_grid.h"
-#include "appl_grid/appl_pdf.h"
-#include "appl_grid/lumi_pdf.h"
-
-#include <algorithm>
-#include <array>
-#include <cassert>
-#include <cstddef>
-#include <chrono>
-#include <cmath>
-#include <string>
-#include <unordered_map>
-#include <utility>
-#include <vector>
-
-namespace
-{
-
-double (*pdf1_ptr)(int32_t pdg_id, double x, double q2, void *state) = nullptr;
-double (*pdf2_ptr)(int32_t pdg_id, double x, double q2, void *state) = nullptr;
-double (*alphas_ptr)(double q2, void *state) = nullptr;
-void* state = nullptr;
-
-double alphas(double const& q)
-{
-    return alphas_ptr(q * q, state);
-}
-
-void xfx1(double const& x, double const& q, double* pdfs)
-{
-    pdfs[ 0] = pdf1_ptr(-6, x, q * q, state);
-    pdfs[ 1] = pdf1_ptr(-5, x, q * q, state);
-    pdfs[ 2] = pdf1_ptr(-4, x, q * q, state);
-    pdfs[ 3] = pdf1_ptr(-3, x, q * q, state);
-    pdfs[ 4] = pdf1_ptr(-2, x, q * q, state);
-    pdfs[ 5] = pdf1_ptr(-1, x, q * q, state);
-    pdfs[ 6] = pdf1_ptr(21, x, q * q, state);
-    pdfs[ 7] = pdf1_ptr( 1, x, q * q, state);
-    pdfs[ 8] = pdf1_ptr( 2, x, q * q, state);
-    pdfs[ 9] = pdf1_ptr( 3, x, q * q, state);
-    pdfs[10] = pdf1_ptr( 4, x, q * q, state);
-    pdfs[11] = pdf1_ptr( 5, x, q * q, state);
-    pdfs[12] = pdf1_ptr( 6, x, q * q, state);
-    pdfs[13] = pdf1_ptr(22, x, q * q, state);
-}
-
-void xfx2(double const& x, double const& q, double* pdfs)
-{
-    pdfs[ 0] = pdf2_ptr(-6, x, q * q, state);
[…]

### 2020-08-07 applgridphoton/src/sparse_matrix3d_root_interface.cpp

@@ -1,90 +1,0 @@
-#include "sparse_matrix3d_root_interface.hpp"
-
-#include "appl_grid/tsparse2d.h"
-#include "appl_grid/tsparse1d.h"
-
-#include <TH1D.h>
-
-SparseMatrix3d* sparse_matrix3d_from_th3d(TH3D const& histogram)
-{
-    // TODO: are the following casts neccessary?
-    TH1D* hx = (TH1D*)(&histogram)->Project3D("x");
-    TH1D* hy = (TH1D*)(&histogram)->Project3D("y");
-    TH1D* hz = (TH1D*)(&histogram)->Project3D("z");
-
-    auto* matrix = new SparseMatrix3d(
-        hx->GetNbinsX(), hx->GetBinCenter(1), hx->GetBinCenter(hx->GetNbinsX()),
-        hy->GetNbinsX(), hy->GetBinCenter(1), hy->GetBinCenter(hy->GetNbinsX()),
-        hz->GetNbinsX(), hz->GetBinCenter(1), hz->GetBinCenter(hz->GetNbinsX())
-    );
-
-    delete hx;
-    delete hy;
-    delete hz;
-
-    for (int i = 0; i < matrix->xaxis().N(); ++i)
-    {
-        for (int j = 0; j < matrix->yaxis().N(); ++j)
-        {
-            for (int k = 0; k < matrix->zaxis().N(); ++k)
-            {
-                auto const value = histogram.GetBinContent(i + 1, j + 1, k + 1);
-
-                if (value != 0.0)
-                {
-                    (*matrix)(i,j,k) = value;
-                }
-            }
-        }
-    }
-
-    return matrix;
-}
-
-TH3D* sparse_matrix3d_to_th3d(SparseMatrix3d const& matrix, std::string const& s)
-{
-    double const delx = matrix.xaxis().delta();
-    double const dely = matrix.yaxis().delta();
-    double const delz = matrix.zaxis().delta();
-
-    TH3D* h = new TH3D(
-        s.c_str(),
-        s.c_str(),
-        matrix.xaxis().N(),
-        matrix.xaxis().min()-0.5*delx,
-        matrix.xaxis().max()+0.5*delx,
-        matrix.yaxis().N(),
-        matrix.yaxis().min()-0.5*dely,
-        matrix.yaxis().max()+0.5*dely,
-        matrix.zaxis().N(),
-        matrix.zaxis().min()-0.5*delz,
-        matrix.zaxis().max()+0.5*delz
-    );
-
[…]

### 2020-08-07 applgridphoton/tests/basic.cpp

@@ -1,117 +1,0 @@
-#include <pineappl_capi.h>
-
-#include <algorithm>
-#include <array>
-
-#include <catch2/catch.hpp>
-
-TEST_CASE("", "")
-{
-    // create a new and empty luminosity function
-    auto* lumi = pineappl_lumi_new();
-
-    // add a new entry to the luminosity function; the combination `1.0 * (up up)`
-    std::array<int32_t, 2> pdg_id_pairs = { 2, 2 };
-    std::array<double, 1> factors = { 1.0 };
-    pineappl_lumi_add(lumi, pdg_id_pairs.size() / 2, pdg_id_pairs.data(), factors.data());
-
-    // we'd like to have a single grid of order alpha^2 - for example LO Drell-Yan
-    std::array<uint32_t, 4> order_parameters = { 0, 2, 0, 0 };
-
-    // global grid parameters, not really that important here
-    auto* key_vals = pineappl_keyval_new();
-
-    pineappl_keyval_set_int(key_vals, "q2_order", 1);
-    pineappl_keyval_set_int(key_vals, "x_order", 1);
-
-    // a distribution with only one bin
-    std::array<double, 2> bin_limits = { 0.0, 1.0 };
-
-    // create a new file
-    auto* grid = pineappl_grid_new(
-        lumi,
-        order_parameters.size() / 4,
-        order_parameters.data(),
-        bin_limits.size() - 1,
-        bin_limits.data(),
-        key_vals
-    );
-
-    pineappl_keyval_delete(key_vals);
-
-    // delete luminosity function
-    pineappl_lumi_delete(lumi);
-
-    std::array<double, 1> const weights = { 1.0 };
-
-    pineappl_grid_fill_all(grid, 0.25, 0.25, 10000.0, 0, 0.25, weights.data());
-
-    double result;
-
-    pineappl_grid_convolute(
-        grid,
-        [](int32_t /*id*/, double x, double /*q2*/, void* /*state*/) { return x; },
-        [](int32_t /*id*/, double x, double /*q2*/, void* /*state*/) { return x; },
-        [](double /*q2*/, void* /*state*/) { return 1.0; },
-        nullptr,
-        nullptr,
-        nullptr,
-        1.0,
-        1.0,
-        &result
-    );
-
-    CHECK( result == 1.0 );
-
[…]

### 2020-08-07 applgridphoton/tests/files.cpp

@@ -1,72 +1,0 @@
-#include <pineappl_capi.h>
-
-#include <algorithm>
-#include <array>
-
-#include <catch2/catch.hpp>
-
-TEST_CASE("check read and write functions", "[files]")
-{
-    // create a new and empty luminosity function
-    auto* lumi = pineappl_lumi_new();
-
-    // add a new entry to the luminosity function; the combination `1.0 * (up up)`
-    std::array<int32_t, 2> pdg_id_pairs = { 2, 2 };
-    std::array<double, 1> factors = { 1.0 };
-    pineappl_lumi_add(lumi, pdg_id_pairs.size() / 2, pdg_id_pairs.data(), factors.data());
-
-    // we'd like to have a single grid of order alpha^2 - for example LO Drell-Yan
-    std::array<uint32_t, 4> grid_parameters = { 0, 2, 0, 0 };
-
-    // global grid parameters, not really that important here
-    auto* key_vals = pineappl_keyval_new();
-
-    pineappl_keyval_set_int(key_vals, "q2_order", 1);
-    pineappl_keyval_set_int(key_vals, "x_order", 1);
-
-    // a distribution with only one bin
-    std::array<double, 2> bin_limits = { 0.0, 1.0 };
-
-    // create a new file
-    auto* grid = pineappl_grid_new(
-        lumi,
-        grid_parameters.size() / 4,
-        grid_parameters.data(),
-        bin_limits.size() - 1,
-        bin_limits.data(),
-        key_vals
-    );
-
-    pineappl_keyval_delete(key_vals);
-
-    // delete luminosity function
-    pineappl_lumi_delete(lumi);
-
-    std::array<double, 1> const weights = { 1.0 };
-
-    pineappl_grid_fill_all(grid, 0.25, 0.25, 10000.0, 0, 0.25, weights.data());
-
-    pineappl_grid_write(grid, "test");
-    pineappl_grid_delete(grid);
-
-    grid = pineappl_grid_read("test");
-
-    double result;
-
-    pineappl_grid_convolute(
-        grid,
-        [](int32_t /*id*/, double x, double /*q2*/, void* /*state*/) { return x; },
-        [](int32_t /*id*/, double x, double /*q2*/, void* /*state*/) { return x; },
-        [](double /*q2*/, void* /*state*/) { return 1.0; },
-        nullptr,
-        nullptr,
-        nullptr,
-        1.0,
-        1.0,
-        &result
[…]

### 2020-08-07 applgridphoton/tests/storage.cpp

@@ -1,55 +1,0 @@
-#include <pineappl_capi.h>
-
-#include <string>
-
-#include <catch2/catch.hpp>
-
-TEST_CASE("check storage creation", "[storage]")
-{
-    auto* f2 = pineappl_keyval_new();
-
-    CHECK( f2 != nullptr );
-
-    pineappl_keyval_delete(f2);
-}
-
-TEST_CASE("check f2 storage default values", "[storage]")
-{
-    auto* f2 = pineappl_keyval_new();
-
-    CHECK( pineappl_keyval_int(f2, "nx") == 50);
-    CHECK( pineappl_keyval_double(f2, "x_min") == 2e-7);
-    CHECK( pineappl_keyval_double(f2, "x_max") == 1.0);
-    CHECK( pineappl_keyval_int(f2, "x_order") == 3);
-    CHECK( pineappl_keyval_int(f2, "nq2") == 30);
-    CHECK( pineappl_keyval_double(f2, "q2_min") == 100);
-    CHECK( pineappl_keyval_double(f2, "q2_max") == 1000000);
-    CHECK( pineappl_keyval_int(f2, "q2_order") == 3);
-
-    pineappl_keyval_delete(f2);
-}
-
-TEST_CASE("check storage getter and setter", "[storage]")
-{
-    auto* f2 = pineappl_keyval_new();
-
-    pineappl_keyval_set_int(f2, "nx", 10);
-    pineappl_keyval_set_int(f2, "x_order", 11);
-    pineappl_keyval_set_int(f2, "nq2", 12);
-    pineappl_keyval_set_int(f2, "q2_order", 13);
-
-    CHECK( pineappl_keyval_int(f2, "nx") == 10 );
-    CHECK( pineappl_keyval_int(f2, "x_order") == 11 );
-    CHECK( pineappl_keyval_int(f2, "nq2") == 12 );
-    CHECK( pineappl_keyval_int(f2, "q2_order") == 13 );
-
-    pineappl_keyval_set_bool(f2, "reweight", true);
-
-    CHECK( pineappl_keyval_bool(f2, "reweight") );
-
-    pineappl_keyval_set_string(f2, "documentation", "foobar");
-
-    CHECK( pineappl_keyval_string(f2, "documentation") == std::string("foobar") );
-
-    pineappl_keyval_delete(f2);
-}

### 2020-08-08 paper/paper.tex
Sect 3 replaced
Title
adding preprint number
Added Nikhef preprint number
small tweaks+comments
Added tabularx package
Fix more Latex warnings

@@
 \pdfoutput=1
+\pdfsuppresswarningpagegroup=1
 
@@
 \usepackage{mathcomp}
+\usepackage{tabularx}
 
 \newcommand{\alphas}{\alpha_\mathrm{s}}
+\preprint{Nikhef-2020-026 TIF-UNIMI-2020-22}
 
-\title{PineAPPL:\\ EW and mixed QCD--EW corrections for PDF fits}
+\title{PineAPPL:\\ combining EW and QCD corrections for PDF fits}
 
@@
 
-\abstract{We introduce \textsc{PineAPPL}, a computer library that makes it possible to produce fast-interpolation 
+\abstract{We introduce \textsc{PineAPPL}, a computer library allowing to produce fast-in\-ter\-po\-la\-tion
 grids for fitting parton distribution functions (PDFs)
@@
 \input{sec-pineappl}
-\input{sec-results-marco}
+\input{sec-results}
 \input{sec-doublecounting}

### 2020-08-08 paper/sec-results.tex
small tweaks+comments
Fix more Latex warnings

@@
 In this section we demonstrate the capabilities of \textsc{PineAPPL} by
-computing fast-interpolation grids, accurate to NLO QCD and NLO QCD+EW,
+computing fast-in\-ter\-po\-la\-tion grids, accurate to NLO QCD and NLO QCD+EW,
 for a representative set of processes in which EW corrections may have a
@@
 we convolve the fast-interpolation grid generated with {\sc PineAPPL} with
-each member in the PDF set, and we compute the associated standard deviation.
+each member in the PDF set, and we compute the associated standard deviation. Monte Carlo
+weights are stored as Lagrange-interpolation grids.
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin3}%
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin4}\\
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin5}%
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin6}\\
+    \includegraphics[width=0.46\textwidth]{figures/pineappl_CMSDY2D11_bin3}%
+    \includegraphics[width=0.46\textwidth]{figures/pineappl_CMSDY2D11_bin4}\\
+    \includegraphics[width=0.46\textwidth]{figures/pineappl_CMSDY2D11_bin5}%
+    \includegraphics[width=0.46\textwidth]{figures/pineappl_CMSDY2D11_bin6}\\
     \caption{Same as figure~\ref{fig:atlaszhighmass49fb}, but for the CMS

### 2020-08-08 paper/sec-results.tex
Use SI macros for percentages

@@
 result is successful. The relative difference between the two is of the order
-$0.1\tcperthousand$ at most, with negligible fluctuations across different
+\SI{0.1}{\permille} at most, with negligible fluctuations across different
 invariant mass bins. The agreement is similarly good irrespective of the
@@
 validate the \textsc{PineAPPL} result: its relative difference with respect to
-the MC result is at most as large as $0.4\tcperthousand$, irrespective of the
+the MC result is at most as large as \SI{0.4}{\permille}, irrespective of the
 accuracy of the theory, of the choice of scale and of the distribution
@@
 The process receives its leading contribution from the $\mathrm{gg}$ channel,
-which varies between 81\% and 61\% (76\% and 83\%) of the $p_\mathrm{T}^\mathrm{t}$
+which varies between \SI{81}{\percent} and \SI{61}{\percent} (\SI{76}{\percent} and \SI{83}{\percent}) of the $p_\mathrm{T}^\mathrm{t}$
 ($m_{\mathrm{t}\bar{\mathrm{t}}}$) differential cross section as the value of the
@@
 increases; the largest PI contribution for this process is $\gamma\mathrm{g}$ scattering,
-which accounts for about 0.5\% -- 1\% (0.5\% -- 0.7\%) of the cross
-section, and is almost entirely (90\%) due to the LO contribution at $\mathcal{O}(\alphas\alpha)$; the contribution from other PI parton luminosities is comparatively
+which accounts for about \SIrange{0.5}{1}{\percent} (\SIrange{0.5}{0.7}{\percent}) of the cross
+section, and is almost entirely (\SI{90}{\percent}) due to the LO contribution at $\mathcal{O}(\alphas\alpha)$; the contribution from other PI parton luminosities is comparatively
 negligible. Overall, the EW corrections suppress the $p_\mathrm{T}^\mathrm{t}$
-($m_{\mathrm{t}\bar{\mathrm{t}}}$) distribution by about 0.2\% -- 3.5\%
-(0.5\% -- 0.2\%) for increasing values of $p_\mathrm{T}^\mathrm{t}$
+($m_{\mathrm{t}\bar{\mathrm{t}}}$) distribution by about \SIrange{0.2}{3.5}{\percent}
+(\SIrange{0.5}{0.2}{\percent}) for increasing values of $p_\mathrm{T}^\mathrm{t}$
 ($m_{\mathrm{t}\bar{\mathrm{t}}}$), except in the first bin of the
 $p_\mathrm{T}^\mathrm{t}$ distribution, where they enhance the cross section by
-about 1\%. The size of these shifts, however, remains always significantly
+about \SI{1}{\percent}. The size of these shifts, however, remains always significantly
 smaller than the data uncertainty.\footnote{In

### 2020-08-08 paper/app-lumis.tex
App B - still not complete

@@
 
+In this appendix, we present the complete breakdown of parton luminosities
+entering the NLO QCD+EW predictions of the various measurements
+considered in section~\ref{sec:results}. For each parton luminosity,
+we indicate its percentage contribution to the cross section in a given bin.
+In particular:
+\begin{itemize}
+\item Table~\ref{tab:B1} collects the thirty-five parton luminosities
+  contributing to the Drell--Yan lepton-pair production measured by the
+  ATLAS experiment at a centre-of-mass energy of
+  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}.
+  The thirteen bins are for the invariant mass of the lepton pair,
+  $M_{\ell\bar\ell}$, with edges at 116, 130, 150, 170, 190,
+  210, 230, 250, 300, 400, 500, 700, 1000 and 1500 GeV.
+\item Tables~\ref{tab:B2}-\ref{tab:B7} collect the thirty-five parton
+  luminositites contributing to the double differential Drell--Yan lepton-pair
+  production measured by the CMS experiment at a centre-of-mass energy of
+  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The one hundred and thirty-two
+  bins are split across tables~\ref{tab:B2}-\ref{tab:B7}, where each table
+  corresponds to a bin in the invariant mass of the lepton pair:
+  table~\ref{tab:B2} to  $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$; table~\ref{tab:B3} to  $\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$; table~\ref{tab:B4} to  $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$; table~\ref{tab:B5} to  $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$; table~\ref{tab:B6} to $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$; and table~\ref{tab:B7} to $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$.
+In each table, the bins are in the rapidity of the lepton pair, $0.0<y_{\ell\bar\ell}<2.4$, and each of them has a width of 0.1 (0.2 in the largest invariant mass range).
+\item Table~\ref{tab:B8} collects the thirty-seven parton luminosities
+  contributing to the top-quark pair distributions measured by the ATLAS and
+  CMS experiments at a centre-of-mass energy of
+  \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}.
+  The four distributions, differential in the transverse momentum of the top
+  quark,  $p_\mathrm{T}^\mathrm{t}$, in the rapidity of the top quark,
+  $y_\mathrm{t}$, in the invariant mass of the top-quark pair,
+  $m_{\mathrm{t}\bar{\mathrm{t}}}$, and in the rapidity of the top-quark pair,
+  $y_{\mathrm{t}\bar{\mathrm{t}}}$ are shown. The bin edges are, respectively:
+  0, 60, 100, 150, 200, 260, 320, 400, 500~GeV; 0.0, 0.4, 0.8, 1.2, 1.6, 2.5;
+  345, 400, 470, 550, 650, 800, 1100, 1600~GeV;
+  and 0.0, 0.3, 0.6, 0.9, 1.3, 2.5.
+\item Table~\ref{tab:B9} collects 
+\end{itemize}
+
+%-------------------------------------------------------------------------------
 \begin{table}[!t]
@@
   \input{tables/TableB1.tex}\\
-  \caption{The 34 parton luminosities contributing to the predictions, accurate
+  \caption{The 35 parton luminosities contributing to the predictions, accurate
     to NLO QCD+EW, of the Drell--Yan lepton-pair production measured by the
     ATLAS experiment at a centre-of-mass energy of
-    \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The ten largest contributions
-    to the cross section (irrespective of their sign) are reported, in
-    percentage, for each bin. Empty spaces typically denote contributions
-    smaller than a fraction of percent. The bin edges are in the invariant mass
-    of the lepton pair, $M_{\ell\bar\ell}$, as follows: 116, 130, 150, 170, 190,
-    210, 230, 250, 300, 400, 500, 700, 1000, 1500 [GeV].
-  }
+    \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The contributions
+    are reported, in percentage, for each of the thirteen bins. The bin edges
+    are in the invariant mass of the lepton pair, $M_{\ell\bar\ell}$, as follows:
+    116, 130, 150, 170, 190,
+    210, 230, 250, 300, 400, 500, 700, 1000, 1500 GeV.}
   \label{tab:B1}
 \end{table}
+%-------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------
+\begin{table}[!p]
+  \centering
+  \tiny
+  \input{tables/TableB2.tex}\\
+  \caption{The 35 parton luminositites contributing to the predictions, accurate
+    to NLO QCD+EW, of the double differential Drell--Yan lepton pair production
+    measured by the CMS experiment at a centre-of-mass energy of
+    \SI{7}{\tera\electronvolt}~\cite{Chatrchyan:2013tia}. The invariant mass
+    bin is $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$; bins 1-24 are in the rapidity of the lepton pair,
+  $0.0<y_{\ell\bar\ell}<2.4$, and each bin has a width of 0.1.}
+  \label{tab:B2}
+\end{table}
+%-------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------
+\begin{table}[!p]
+  \centering
+  \tiny
+  \input{tables/TableB3.tex}\\
+  \caption{Same as table~\ref{tab:B2}, but for the invariant mass bin
+    $\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$.}
+  \label{tab:B3}
+\end{table}
+%-------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------
+\begin{table}[!p]
+  \centering
+  \tiny
+  \input{tables/TableB4.tex}\\
+    \caption{Same as table~\ref{tab:B2}, but for the invariant mass bin
+    $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$.}
+  \label{tab:B4}
+\end{table}
+%-------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------
+\begin{table}[!p]
+  \centering
+  \tiny
+  \input{tables/TableB5.tex}\\
+    \caption{Same as table~\ref{tab:B2}, but for the invariant mass bin
+    $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$.}
+  \label{tab:B5}
+\end{table}
+%-------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------
+\begin{table}[!p]
+  \centering
+  \tiny
+  \input{tables/TableB6.tex}\\
+    \caption{Same as table~\ref{tab:B2}, but for the invariant mass bin
+    $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$.}
+  \label{tab:B6}
+\end{table}
+%-------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------
+\begin{table}[!t]
+  \centering
+  \tiny
+  \input{tables/TableB7.tex}\\
+    \caption{Same as table~\ref{tab:B2}, but for the invariant mass bin
+      $\SI{200}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$. Each bin in the rapidity of the lepton pair has a width of 0.2.}
+  \label{tab:B7}
+\end{table}
+%-------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------
+\begin{table}[!p]
+  \centering
+  \tiny
+  \input{tables/TableB8.tex}\\
+  \input{tables/TableB9.tex}\\
+  \caption{}
+  \label{tab:B1}
+\end{table}
+%-------------------------------------------------------------------------------

### 2020-08-09 paper/app-pineappl.tex
Move appendix A.2 to the end of appendix A
Fix more Latex warnings
Fix bug in PineAPPL example

@@
-\section{Installation and usage of \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
+\section{Installation and usage of PineAPPL}
 \label{app:pineappl}
@@
 Updated installation instructions are kept in the file \texttt{README.md} in \textsc{PineAPPL}'s repository at \url{https://github.com/N3PDF/pineappl/}.
-
-\subsection{Example Monte Carlo program}
-\label{app:example-program}
-
-% TODO: link to documentation
-
-\definecolor{mygreen}{rgb}{0,0.6,0}
-\definecolor{mygray}{rgb}{0.5,0.5,0.5}
-\definecolor{mymauve}{rgb}{0.58,0,0.82}
-
-\lstset{
-  belowcaptionskip=1\baselineskip,
-  breaklines=true,
-  frame=L,
-  numbers=left,
-  xleftmargin=\parindent,
-  showstringspaces=false,
-  basicstyle=\footnotesize\ttfamily,
-  keywordstyle=\bfseries\color{green!40!black},
-  commentstyle=\itshape\color{purple!40!black},
-  identifierstyle=\color{blue},
-  stringstyle=\color{orange},
-}
-
-The following listing shows how to setup \textsc{PineAPPL} using its C interface in a simple Monte Carlo integrator for calculating the double-photon contribution to Drell--Yan lepton-pair production at the LHC.
-All \textsc{PineAPPL} functions have the prefix \texttt{pineappl\_}.
-The full example can be found at \url{https://github.com/N3PDF/pineappl/tree/master/examples/capi-dy-aa}.
-
-\begin{lstlisting}[language=C++,mathescape=true]
-// create a new luminosity function for the $\gamma\gamma$ initial state
-auto* lumi = pineappl_lumi_new();
-int32_t pdg_ids[] = { 22, 22 };
-double ckm_factors[] = { 1.0 };
-pineappl_lumi_add(lumi, 1, pdg_ids, ckm_factors);
-
-// only LO $\alpha_\mathrm{s}^0 \alpha^2 \log^0(\xi_\mathrm{R}) \log^0(\xi_\mathrm{F})$
-uint32_t orders[] = { 0, 2, 0, 0 };
-
-// we bin in rapidity from 0 to 2.4 in steps of 0.1
-double bins[] = {
-    0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0, 1.1, 1.2,
-    1.3, 1.4, 1.5, 1.6, 1.7, 1.8, 1.9, 2.0, 2.1, 2.2, 2.3, 2.4
-};
-
-// create the PineAPPL grid with default interpolation and binning parameters
-auto* keyval = pineappl_keyval_new();
-auto* grid = pineappl_grid_new(lumi, 1, orders, 24, bins, keyval);
-
-// now we no longer need `keyval` and `lumi`
-pineappl_keyval_delete(keyval);
-pineappl_lumi_delete(lumi);
-
-// fill the grid with phase-space points
-fill_grid(grid, 10000000);
-
-// perform a convolution of the grid with PDFs
-auto* pdf = LHAPDF::mkPDF("NNPDF31_nlo_as_0118_luxqed", 0);
-auto xfx = [](int32_t id, double x, double q2, void* pdf) {
-    return static_cast <LHAPDF::PDF*> (pdf)->xfxQ2(id, x, q2);
-};
-auto alphas = [](double q2, void* pdf) {
-    return static_cast <LHAPDF::PDF*> (pdf)->alphasQ2(q2);
-};
-
-std::vector<double> dxsec(24);
-pineappl_grid_convolute(grid, xfx, xfx, alphas, pdf, nullptr,
-    nullptr, 1.0, 1.0, dxsec.data());
-
-// print the results
-for (std::size_t i = 0; i != 24; ++i) {
-    std::printf("%.1f %.1f %.3e\n", bins[i], bins[i + 1], dxsec[i]);
-}
-
-// write the grid to disk
-pineappl_grid_write(grid, "DY-LO-AA.pineappl");
-
-// destroy the object
-pineappl_grid_delete(grid);
-\end{lstlisting}
 
@@
 
-\subsection{Sample runcard for \texorpdfstring{\textsc{mg5\_aMC}}{mg5\_aMC}}
+\subsection{Sample runcard for mg5\_aMC@NLO}
 \label{app:sample-runcard}
@@
 \end{verbatim}
+
+\subsection{Example Monte Carlo program}
+\label{app:example-program}
+
+% TODO: link to documentation
+
+\definecolor{mygreen}{rgb}{0,0.6,0}
+\definecolor{mygray}{rgb}{0.5,0.5,0.5}
+\definecolor{mymauve}{rgb}{0.58,0,0.82}
+
+\lstset{
+  belowcaptionskip=1\baselineskip,
+  breaklines=true,
+  frame=L,
+  numbers=left,
+  xleftmargin=\parindent,
+  showstringspaces=false,
+  basicstyle=\footnotesize\ttfamily,
+  keywordstyle=\bfseries\color{green!40!black},
+  commentstyle=\itshape\color{purple!40!black},
+  identifierstyle=\color{blue},
+  stringstyle=\color{orange},
+}
+
+The following listing shows how to setup \textsc{PineAPPL} using its C interface in a simple Monte Carlo integrator for calculating the double-photon contribution to Drell--Yan lepton-pair production at the LHC.
+All \textsc{PineAPPL} functions have the prefix \texttt{pineappl\_}.
+The full example can be found at \url{https://github.com/N3PDF/pineappl/tree/master/examples/capi-dy-aa}.
+
+\begin{lstlisting}[language=C++,mathescape=true]
+// create a new luminosity function for the $\gamma\gamma$ initial state
+auto* lumi = pineappl_lumi_new();
+int32_t pdg_ids[] = { 22, 22 };
+double ckm_factors[] = { 1.0 };
+pineappl_lumi_add(lumi, 1, pdg_ids, ckm_factors);
+
+// only LO $\alpha_\mathrm{s}^0 \alpha^2 \log^0(\xi_\mathrm{R}) \log^0(\xi_\mathrm{F})$
+uint32_t orders[] = { 0, 2, 0, 0 };
+
+// we bin in rapidity from 0 to 2.4 in steps of 0.1
+double bins[] = {
+    0.0,
+    0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0, 1.1, 1.2,
+    1.3, 1.4, 1.5, 1.6, 1.7, 1.8, 1.9, 2.0, 2.1, 2.2, 2.3, 2.4
+};
+
+// create the PineAPPL grid with default interpolation and binning parameters
+auto* keyval = pineappl_keyval_new();
+auto* grid = pineappl_grid_new(lumi, 1, orders, 24, bins, keyval);
+
+// now we no longer need `keyval` and `lumi`
+pineappl_keyval_delete(keyval);
+pineappl_lumi_delete(lumi);
+
+// fill the grid with phase-space points
+fill_grid(grid, 10000000);
+
+// perform a convolution of the grid with PDFs
+auto* pdf = LHAPDF::mkPDF("NNPDF31_nlo_as_0118_luxqed", 0);
+auto xfx = [](int32_t id, double x, double q2, void* pdf) {
+    return static_cast <LHAPDF::PDF*> (pdf)->xfxQ2(id, x, q2);
+};
+auto alphas = [](double q2, void* pdf) {
+    return static_cast <LHAPDF::PDF*> (pdf)->alphasQ2(q2);
+};
+
+std::vector<double> dxsec(24);
+pineappl_grid_convolute(grid, xfx, xfx, alphas, pdf, nullptr,
+    nullptr, 1.0, 1.0, dxsec.data());
+
+// print the results
+for (std::size_t i = 0; i != 24; ++i) {
+    std::printf("%.1f %.1f %.3e\n", bins[i], bins[i + 1], dxsec[i]);
+}
+
+// write the grid to disk
+pineappl_grid_write(grid, "DY-LO-AA.pineappl");
+
+// destroy the object
+pineappl_grid_delete(grid);
+\end{lstlisting}

### 2020-08-09 paper/app-pineappl.tex
Polish a few sentences

@@
 The size of the remaining channels is smaller than the photon--photon channel.
-The factors \texttt{1} are not important here, but in general they can contain CKM values that, if kept in the squared matrix elements, would not allow for sharing a single matrix element for different quark flavours and therefore slow down the calculation.
+The factors \texttt{1} are not important here, but in general they can contain CKM values and charge factors that, if kept in the squared matrix elements, would not allow for sharing a single matrix element for different quark flavours and therefore slow down the calculation.
 A complete list of the most important channels and of their

### 2020-08-09 paper/sec-introduction.tex
Polish a few sentences

@@
 we develop \textsc{PineAPPL}, a new computer library that provides a direct interface
-from parton-level Monte Carlo event generators accurate up to NLO QCD+EW to
+from parton-level Monte Carlo event generators accurate up to any fixed order to
 fast-interpolation grids. The library supports variations of the factorisation
 and renormalisation scales. Planned extensions will include support for resummation and matching with a photon- and/or
-parton-shower {\bf MZ remove sentence if not true}. The library is included by default in 
-\textsc{MadGraph5\_aMC@NLO} (\textsc{MG5\_aMC} henceforth) within which it has
-been designed and tested. However, it is suitable for use as a plugin in any 
-Monte Carlo generator that supports NLO QCD+EW computations, such as 
-\textsc{SHERPA}~\cite{Biedermann:2017yoi}. In this respect, \textsc{PineAPPL}
-supersedes \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{aMCfast}~\cite{Bertone:2014zva}, and complements
-\textsc{MCgrid}~\cite{DelDebbio:2013kxa,Bothmann:2015dba}.
+parton-shower. An interface to the library is included in
+\textsc{MadGraph5\_aMC@NLO} (\textsc{MG5\_aMC} henceforth), with which it has
+been developed and tested, and which supersedes \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{aMCfast}~\cite{Bertone:2014zva}.
+However, \textsc{PineAPPL} can be easily interfaced with every
+Monte Carlo generator, e.g.\ \textsc{SHERPA}~\cite{Biedermann:2017yoi}, where it could complement \textsc{MCgrid}~\cite{DelDebbio:2013kxa,Bothmann:2015dba}.
 
@@
 In section~\ref{sec:doublecounting} we try to detail in a more
-comprehensive maneer the second problem sketched above, the solution of which, 
+comprehensive manner the second problem sketched above, the solution of which,
 however, remains beyond the scope of the current work. We provide our

### 2020-08-09 paper/figures/grid-insertion.tex

\pdfminorversion=4

\documentclass[varwidth=true,11pt]{standalone}

\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{tikz}

\begin{document}
\thispagestyle{empty}

\begin{tikzpicture}[baseline=(current bounding box.center),scale=0.5]
% draw coordinate axes
\draw[thick] [->](9.5,9.5) -- (-0.5,9.5) node[left]{$u(y(x_1))$};
\draw[thick] [->](9.5,9.5) -- (9.5,-0.5) node[anchor=north]{$u(y(x_2))$};
% draw labels
\foreach \x in {0,...,9} {\draw[thick] (9-\x,9.5cm+4pt) -- (9-\x,9.5cm-4pt) node[anchor=south,outer sep=3pt] {$\x$};}
\foreach \y in {0,...,9} {\draw[thick] (9.5cm-4pt,9-\y) -- (9.5cm+4pt,9-\y) node[anchor=west,outer sep=0pt] {$\y$};}
% draw the grid
\foreach \x in {0,...,9}
\foreach \y in {0,...,9}
{
\fill[lightgray] (\x,\y) circle (3pt);
}
\node[opacity=0.4,fill,black,minimum height=2cm,minimum width=2cm] at (3.2,4.2) {};
\node[fill,inner sep=0,minimum height=3pt,minimum width=3pt] at (3.2,4.2) {};
\draw[thick] [->] (5.5,6.5) -- (1.5,6.5) node[right] {};
\draw[thick] [->] (5.5,6.5) -- (5.5,2.5) node[anchor=south] {};
\foreach \x in {4,...,7} {\draw[thick] (9-\x,6.5cm+4pt) -- (9-\x,6.5cm-4pt) node[anchor=south,outer sep=7pt,inner sep=0] {$\x$};}
\foreach \y in {3,...,6} {\draw[thick] (9cm-3.5cm-4pt,9-\y) -- (9cm-3.5cm+4pt,9-\y) node[anchor=west,outer sep=2pt,inner sep=0] {$\y$};}
\end{tikzpicture}
\end{document}

### 2020-08-09 paper/sec-doublecounting.tex

@@
 as a quark-initiated $s$-channel mechanism ($\mathrm{q} \bar{\mathrm{q}} \to \gamma^*/\mathrm{Z} \to \ell \bar{\ell}$), in many analyses the photon-induced component,
-$\gamma \gamma \to \ell \bar{\ell}$ in the $t$ channel, is considered to be a different process, and therefore as a background and subtracted.
+$\gamma \gamma \to \ell \bar{\ell}$ in the $t$ channel, is considered a different process, and therefore as a background and subtracted.
 The subtraction from the measured data is done by calculating the theoretical predictions of the double-photon initiated contribution, possibly including (ill-defined) higher-order
@@
 
-%%{\bf It looks like CMS does things in a pretty consistent manner~\cite{Sirunyan:2018owv, CMS:2014jea}. Shall we mention? We should
-%%not make ATLAS appear as the bad guys, and CMS as the good ones.}
-
 A second example is related to removing EW effects from data. These can be either the full EW corrections
@@
  electrons, and to a lesser extent muons, tend to radiate photons, which are not accounted
-for in QCD-only matrix-elements. Thus, leptons that are measured in the detector are less energetic, and this fact is compensated for
+for in QCD-only matrix elements. Thus, leptons that are measured in the detector are less energetic, and this fact is compensated for
 by inverting a photon shower.
@@
 These datasets are needed for and correctly used in QCD-only PDF determinations, since the EW corrections to some DY observables can be significant, and excluding them would therefore degrade the quality of the fit.
-However, in fits including fixed-order EW corrections the problem with this definition is that the first photon emission is included exactly at the matrix-element level. The inclusion of
+In fits including fixed-order EW corrections the problem with this definition, besides double counting, is that the first photon emission is included exactly at the matrix-element level.
+The inclusion of
 subsequent emission would require the matching with the QED shower, which is not yet available for general processes.

### 2020-08-09 paper/sec-pineappl.tex

@@
-\section{PDF-independent storage of phase-space weights with \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
+\section{PDF-independent storage of phase-space weights with PineAPPL}
 \label{sec:pineappl}
@@
 \end{multline}
-The cross section shown above is differential w.r.t.\ the observable $\mathcal{O}$, which, in general, is a function of phase space and subject to the usual conditions (soft and collinear safety, etc.).
+The cross section shown above is differential with respect to the observable $\mathcal{O}$, which, in general, is a function of phase space and subject to the usual conditions (soft and collinear safety, etc.).
 

### 2020-08-09 paper/app-addmaterial.tex
Part of Christopher's and Marco's comments are now implemented
Move low-statistics plot into an appendix
Fix low-invariant mass slices of CMS DY
Fix duplicated reference
appendices B and C

@@
-\section{Additional material}
+\section{Low statistics and complementary results}
 \label{app:add_plots}
 
-\begin{figure}
+In this appendix, we collect some additional plots, in the same format of those
+presented in figures~\ref{fig:atlaszhighmass49fb}-\ref{fig:cmsZ13TeV},
+specifically: figure~\ref{fig:atlaszhighmass49fb-lowstat} is the same as
+figure~\ref{fig:atlaszhighmass49fb}, but for a low-statistic MC run;
+figure~\ref{fig:cmsdy2d11_bins12} is the same as
+figure~\ref{fig:cmsdy2d11_bins3456}, but for the two missing lepton-pair
+invariant mass bins,
+$\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$ and
+$\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$;
+and figure~\ref{fig:atlastop-rap} is the same as figure~\ref{fig:atlastop},
+but for the distributions in the rapidity of the top quark, $y_{\mathrm{t}}$,
+and in the rapidity of the top-quark pair, $y_{\mathrm{t}\bar{\mathrm{t}}}$.
+
+%-------------------------------------------------------------------------------
+\begin{figure}[!t]
     \centering
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin5}%
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin6}
-    \caption{PineAPPL comparison for CMS 2D Drell--Yan.}
-    \label{fig:cmsdy2d11_bins56}
+    \includegraphics[width=0.46\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB_lowstat}\\
+    \caption{Same as figure~\ref{fig:atlaszhighmass49fb}, but for a
+    low-statistics MC run.}
+    \label{fig:atlaszhighmass49fb-lowstat}
 \end{figure}
+%-------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------
+\begin{figure}[!p]
+    \centering
+    \includegraphics[width=0.46\textwidth]{figures/pineappl_CMSDY2D11_bin1}%
+    \includegraphics[width=0.46\textwidth]{figures/pineappl_CMSDY2D11_bin2}\\
+    \caption{Same as figure~\ref{fig:cmsdy2d11_bins3456}, but for the two missing
+      lepton-pair invariant mass bins,
+      $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$ and
+      $\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$.}
+    \label{fig:cmsdy2d11_bins12}
+\end{figure}
+%-------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------
+\begin{figure}[!p]
+    \centering
+    \includegraphics[width=0.46\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TRAP}%
+    \caption{Same as figure~\ref{fig:atlastop}, but for the distributions
+      in the rapidity of the top quark, $y_{\mathrm{t}}$, and in the rapidity of
+      the top-quark pair, $y_{\mathrm{t}\bar{\mathrm{t}}}$.}
+    \label{fig:atlastop-rap}
+\end{figure}
+%-------------------------------------------------------------------------------
+
+From figure~\ref{fig:atlaszhighmass49fb-lowstat}, we observe that the validation
+of the \textsc{PineAPPL} result remains successful: its difference with respect
+to the MC result is at most \SI{3}{\permille}, as usual irrespective of the
+accuracy of the theory and of the choice of scale. As expected, however, the
+result is largely unreliable to make any conclusion about the size of the EW
+corrections: large fluctuations are seen in the predictions, and the MC
+uncertainty dominates over the PDF and scale uncertainties.
+
+Figure~\ref{fig:cmsdy2d11_bins12} demonstrates that the two bins at the
+lowest invariant mass of the Drell--Yan lepton-pair measured by the CMS
+experiment display very similar features as the bin at immediately larger
+values of invariant mass, see figure~\ref{fig:cmsdy2d11_bins3456}: the EW
+enhances the cross section (although of the order of 2\% -- 3\% across all the
+rapidity range); the amount of this shift is slightly larger than the PDF
+ucnertainty, but is largely overshot by the scale uncertainty; the MC\
+uncertainty remains comparatively negligible.
+
+Finally, figure~\ref{fig:atlastop-rap} allows us to further validate the
+\textsc{PineAPPL} result against the MC result for the top-quark
+rapidity distributions, and to explicitly check that the size of the EW
+corrections in this case is negligible with respect to the companion
+top-quark transverse momentum and top-quark pair invariant mass distributions,
+see figure~\ref{fig:atlastop}, consistently with what was already observed in
+ref.~\cite{Czakon:2017wor}.

### 2020-08-09 paper/app-lumis.tex
appendices B and C

@@
   and 0.0, 0.3, 0.6, 0.9, 1.3, 2.5.
-\item Table~\ref{tab:B9} collects 
+\item Table~\ref{tab:B9} collects the parton luminosities contributing
+  to the Z $p_{\mathrm{T}}$ distribution measured by the CMS experiment at
+  a centre-of-mass energy of
+  \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. The bin edges are:
+  20, 22, 26, 28, 32, 37, 43, 52, 65, 85, 120, 160, 190, 220, 250, 300,
+  400, 500, 800, 1500~GeV.
 \end{itemize}
@@
   \input{tables/TableB9.tex}\\
-  \caption{}
-  \label{tab:B1}
+  \caption{The 37 parton luminosities contributing to the predictions,
+    accurate to NLO QCD+EW, to the top-quark pair distributions measured by the
+    ATLAS and CMS experiments at a centre-of-mass-energy of
+    $\SI{8}{\tera\electronvolt}$~\cite{Aad:2015mbv,Khachatryan:2015oqa}.
+    From left to right, top to bottom,
+    predictions are reported for the 8 bins of transverse momentum of the
+    top quark, for the 5 bins of top-quark rapidity, for the 7 bins of
+    top-quark pair invariant mass, and for the 5 bins of top-quark pair
+  rapidity, see text for details.}
+  \label{tab:B8}
 \end{table}

### 2020-08-09 paper/sec-results.tex
Removed conflict
Add another review, mostly of section 3

@@
 where $M_\mathrm{W}$, $M_\mathrm{Z}$ and $m_\mathrm{t}$ are the values of the W-boson, Z-boson, and
-top quark masses, respectively, and $\Gamma_\mathrm{W}$ and $\Gamma_\mathrm{Z}$ are the width of
+top-quark masses, respectively, and $\Gamma_\mathrm{W}$ and $\Gamma_\mathrm{Z}$ are the width of
 the W boson and of the Z boson, respectively. The value of the strong
@@
 computations. In fact, while nothing prevents to include these contributions \emph{a posteriori}, as they are finite,
-their impact is either smaller than the one of ``standard'' EW corrections, or anyway negligible with respect to
+their impact is either smaller than the one of \enquote{standard} EW corrections, or anyway negligible with respect to
 the total cross section (see refs.~\cite{Frixione:2014qaa,Frixione:2015zaa,Pagani:2016caq} for some process-specific cases {\bf MZ OTHERS???}).
@@
 
-When presenting the results, for each of the processes and measurements considered, we compute the expectation
-value of the corresponding observable for each kinematic bin in two different
+When presenting the results, for each of the processes and measurements considered, we compute differential
+cross sections for the observables defined in the experimental analyses in two different
 ways: directly, by means of \textsc{MG5\_aMC}, and a posteriori, by convolving
@@
 last respect, we consider by default high-statistics computations, whereby we
-require a relative Monte Carlo precision of a fraction of per mille on the total cross section. While
+require a relative Monte Carlo precision of \SI{0.1}{\permille} on the integrated cross section. While
 this choice does not affect the validation of the \textsc{PineAPPL} result
@@
 We present these comparisons in
-figures~\ref{fig:atlaszhighmass49fb}--\ref{fig:cmsZ13TeV}.
+figures~\ref{fig:atlaszhighmass49fb}, \ref{fig:cmsdy2d11_bins3456}, \ref{fig:atlastop}, and \ref{fig:cmsZ13TeV}.
 The format of the plots is the same across all figures. The first panel
@@
 \paragraph{Experimental measurements and process features.}
-We select the distribution, single-differential in the invariant mass of the
+We select the single-differential invariant mass distribution of the
 lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of-mass
@@
 ($M_{\ell\bar\ell}>\SI{116}{\giga\electronvolt}$)~\cite{Aad:2013iua}.
-We also select the distributions, double-differential in the rapidity and in
-the invariant mass of the lepton pair, $y_{\ell\bar\ell}$ and $M_{\ell\bar\ell}$,
+We also select the single-differential rapidity distribution, $y_{\ell\bar\ell}$, in slices of
+the invariant mass of the lepton pair, $M_{\ell\bar\ell}$,
 measured by the CMS experiment at a centre-of-mass energy of
@@
 $\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$ contributions.
-Mixed-coupling QCD-EW corrections occur only at NNLO, and are therefore not
+Mixed-coupling QCD--EW corrections occur only at NNLO, and are therefore not
 considered here. EW corrections for this process were computed in
@@
 $\mu_\mathrm{R}=\mu_\mathrm{F}=M_{\ell\bar\ell}$, where $M_{\ell\bar\ell}$ is the central value of each
-invariant mass bin, for the CMS one. In the case of ATLAS, we require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$,
+invariant mass slice, for the CMS one. In the case of ATLAS, we require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$,
 $|\eta_\ell|<2.5$ and $\SI{116}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the transverse
@@
 lepton pair, respectively. Conversely, in the case of CMS, we require $p_\mathrm{T}^{\ell_1}>\SI{14}{\giga\electronvolt}$, $p_\mathrm{T}^{\ell_2}>\SI{9}{\giga\electronvolt}$,
-$|\eta_\ell|<2.4$, $|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$
+$|\eta_\ell|<2.4$, $|y_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$
 for the transverse momentum and the pseudorapidity of each lepton, and for the
-pseudorapidity and the invariant mass of the lepton pair.
+rapidity and the invariant mass of the lepton pair.
 
 \paragraph{Numerical results.}
-We first consider the single-differential measurement at a high lepton-pair
-invariant mass performed by the ATLAS experiment at \SI{7}{\tera\electronvolt}.
+We first consider the single-differential measurement of a lepton-pair
+for large invariant masses performed by the ATLAS experiment at \SI{7}{\tera\electronvolt}.
 From figure~\ref{fig:atlaszhighmass49fb} we immediately
@@
 The measurement is mainly driven by $\mathrm{q}\bar{\mathrm{q}}$ scattering: specifically, the
-leading (next-to-leading) contribution comes from a $\mathrm{u}\bar{\mathrm{u}}$ ($\mathrm{d}\bar{\mathrm{d}}$)
+leading (next-to-leading) contribution comes from a $\mathrm{u}\bar{\mathrm{u}}$/$\mathrm{c}\bar{\mathrm{c}}$ ($\mathrm{d}\bar{\mathrm{d}}$/$\mathrm{s}\bar{\mathrm{s}}$)
 parton luminosity, which accounts for about \SI{55}{\percent} (\SI{49}{\percent}) of the cross section
@@
 uncertainties, and to the size of the EW correction. Our conclusions should
-therefore not be affected by a too low number of Monte Carlo events generated.
+therefore not be affected by a generation of too few Monte Carlo events.
 
@@
 mass bin comes from
-the $\mathrm{u}\bar{\mathrm{u}}$ ($\mathrm{d}\bar{\mathrm{d}}$) parton luminosity, which accounts for about \SI{70}{\percent}
+the $\mathrm{u}\bar{\mathrm{u}}$/$\mathrm{c}\bar{\mathrm{c}}$ ($\mathrm{d}\bar{\mathrm{d}}$/$\mathrm{s}\bar{\mathrm{s}}$) parton luminosity, which accounts for about \SI{70}{\percent}
 (\SI{22}{\percent}) of the double differential cross section, with small fluctuations across
@@
 different in the $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$ invariant mass bin, where the
-leading (next-to-leading) contribution comes instead from the $\mathrm{d}\bar{\mathrm{d}}$
-($\mathrm{u}\bar{\mathrm{u}}$) parton luminosity, which accounts for about \SI{60}{\percent} (\SI{44}{\percent}) of the
+leading (next-to-leading) contribution comes instead from the $\mathrm{d}\bar{\mathrm{d}}$/$\mathrm{s}\bar{\mathrm{s}}$
+($\mathrm{u}\bar{\mathrm{u}}$/$\mathrm{c}\bar{\mathrm{c}}$) parton luminosity, which accounts for about \SI{60}{\percent} (\SI{44}{\percent}) of the
 double differential cross section at small rapidities, and for about \SI{56}{\percent} (\SI{50}{\percent})
 at large rapidities. In the remaining two invariant mass bins, the leading
-(next-to-leading) contribution comes again from the $\mathrm{u}\bar{\mathrm{u}}$ ($\mathrm{d}\bar{\mathrm{d}}$)
+(next-to-leading) contribution comes again from the $\mathrm{u}\bar{\mathrm{u}}$/$\mathrm{c}\bar{\mathrm{c}}$ ($\mathrm{d}\bar{\mathrm{d}}$/$\mathrm{s}\bar{\mathrm{s}}$)
 parton luminosity, which accounts for about \SIrange{69}{95}{\percent} (\SIrange{38}{30}{\percent}) and
@@
 $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$ and $\SI{200}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ in the
-corresponding rapidity intervals; PI contributions range between \SIrange{7.3}{1.2}{\percent}
-and \SIrange{3.7}{0.6}{\percent} in the two invariant mass bins, respectively, for increasing
+corresponding rapidity intervals; PI contributions range between \SIrange{3.7}{0.6}{\percent}
+and \SIrange{7.3}{1.6}{\percent} in the two invariant mass bins, respectively, for increasing
 rapidity.
@@
 accurate: even though the apparent description of the data will not
-improve, including of the precise bins in the low invariant mass range, PDFs
+improve, by including the more precisely predicted bins in the low invariant mass range, PDFs
 will resemble more closely the underlying truth. Furthermore, the kinematic cut
@@
 mass peak, $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$, where the scale uncertainty exceeds
-the size of the EW correction by about a factor of five. These facts confirm,
-as expected, that EW corrections are almost immaterial at the Z-boson mass
-peak, but that NNLO QCD corrections are otherwise as relevant as NLO QCD+EW
-corrections. Finally, the Monte Carlo statistical uncertainty remains negligible
+the size of the EW correction by about a factor of five. This is due to the choice
+of invariant mass window around the Z peak, in which positive and negative EW corrections almost cancel.
+Finally, the Monte Carlo statistical uncertainty remains negligible
 in comparison to the data, PDF and scale uncertainties, and to the size of the
-EW correction, except for a couple of bins at forward rapidity in the highest
+EW correction, except for a couple of bins at forward/backward rapidity in the highest
 invariant mass bins. Improving the Monte Carlo precision will require to
@@
 \paragraph{Experimental measurements and process features.}
-We select the distributions, single-differential in either the transverse
+We select the single-differential distribution in either the transverse
 momentum of the top quark, $p_\mathrm{T}^\mathrm{t}$, or the invariant mass of the top-quark
@@
 \paragraph{Process-specific settings.}
-We employ the following functional form for the renormalisation and factorisation scales
+We employ the following functional form for the renormalisation and factorisation scales;
 $\mu_\mathrm{R}=\mu_\mathrm{F}=\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^\mathrm{t})^2}{\Big /}2$ for the distribution differential
@@
 \paragraph{Experimental measurements and process features.}
-We select the distribution, single-differential in the transverse momentum of
+We select the single-differential transverse momentum distribution of the
 the Z boson, $p_\mathrm{T}^\mathrm{Z}$, measured by the CMS experiment at a centre-of-mass
@@
 contribution $\mathcal{O}(\alphas^2\alpha^2)$. In the NLO QCD+EW computation,
-we supplement these with the LO and NLO EW corrections,
-$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alpha^4)$, and with the NLO
-QCD-EW mixed-coupling correction, $\mathcal{O}(\alphas\alpha^3)$. EW corrections for
-this process were computed in
+we supplement these with another LO and NLO, which are
+$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alphas\alpha^3)$;
+contributions of the order $\mathcal{O}(\alpha^4)$ are not considered (see ref.~\cite{Denner:2019zfp}).
+EW corrections for this process were computed in
 refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
@@
 We require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$, $|\eta_\ell|<2.4$,
-$M_\mathrm{Z}-\SI{15}{\giga\electronvolt}<M_{\ell\bar\ell}<M_\mathrm{Z}+\SI{20}{\giga\electronvolt}$,
-$|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<p_\mathrm{T}^{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the
+$|M_{\ell\bar\ell} - M_\mathrm{Z}| < \SI{15}{\giga\electronvolt}$,
+$|y_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<p_\mathrm{T}^{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the
 transverse momentum and pseudorapidity of each lepton, and for the invariant mass,
 pseudorapidity and transverse momentum of the lepton pair. Imposing a minimum cut for the transverse momentum of the lepton pair 
-is necessary as we stick to a fixed-order computation, without including resummation effects.
+is necessary as we rely on a fixed-order computation, without including resummation effects.
 
-\paragraph{Numerical results.}
+\paragraph{Numerical results.} We finally
+
 %-------------------------------------------------------------------------------

### 2020-08-10 run_merge.sh
Add `run_merge.sh` script

@@ -1,0 +1,100 @@
+#!/bin/bash
+
+check_args_and_cd_output() {
+    # exit script at the first sign of an error
+    set -o errexit
+
+    # the following exits if undeclared variables are used
+    set -o nounset
+
+    # exit if some program in a pipeline fails
+    set -o pipefail
+
+    # check arguments of the script
+    if (( $# != 1 )); then
+        exit 1
+    fi
+
+    # name of the dataset
+    dataset="${1%-[0-9]*}"
+
+    mg5amc=$(which mg5_aMC 2> /dev/null || true)
+
+    if [[ ! -x ${mg5amc} ]]; then
+        echo "The binary \`mg5_aMC\` wasn't found. Please adjust your PATH variable" >&2
+        exit 1
+    fi
+
+    pineappl=$(which pineappl 2> /dev/null || true)
+
+    if [[ ! -x ${pineappl} ]]; then
+        echo "The binary \`pineappl\` wasn't found. Please adjust your PATH variable" >&2
+        exit 1
+    fi
+
+    # name of the directory where the output is written to
+    output="$1"
+
+    if [[ ! -d $output ]]; then
+        # since we add a date postfix to the name this shouldn't happen
+        echo "Error: output directory doesn't exists" >&2
+        exit 1
+    fi
+
+    cd "${output}"
+}
+
+main() {
+    launch_file=launch.txt
+
+    # TODO: the following assumes that all observables belong to the same distribution
+
+    grid="${dataset}".pineappl
+    rm -f "${grid}"
+
+    # merge the final bins
+    "${pineappl}" merge "${grid}" $(ls -v "${dataset}"/Events/run_01*/amcblast_obs_*.root)
+
+    lz4=$(which lz4 2> /dev/null || true)
+
+    # compress the grid with `lz4` if it's available
+    if [[ -x ${lz4} ]]; then
+        lz4 -9 "${grid}"
+        rm "${grid}"
+        grid="${grid}.lz4"
+    fi
+
+    # find out which PDF set was used to generate the predictions
+    pdfstring=$(grep "set lhaid" "${launch_file}" | sed 's/set lhaid \([0-9]\+\)/\1/')
+
+    # (re-)produce predictions
+    "${pineappl}" convolute "${grid}" "${pdfstring}" --scales 9 > pineappl.convolute
+    "${pineappl}" orders "${grid}" "${pdfstring}" --absolute > pineappl.orders
[…]

### 2020-08-10 paper/sec-conclusion.tex
Replace 'mixed' with 'combined'

@@
 \label{sec:conclusion}
+{\bf MZ I would like to have some sort of introduction here (a short bla bla on precision), before turning to Pineappl}
 
@@
 A distinguishing feature of \textsc{PineAPPL} is the support for arbitrary coupling orders not only in the strong, but also in the electroweak coupling.
-This enables us to generate, for the first time, NLO EW and NLO mixed QCD--EW interpolation grids.
+This enables us to generate, for the first time, NLO EW and NLO combined QCD--EW interpolation grids.
 Using \textsc{mg5\_aMC@NLO} we calculated and showcased the impact of these corrections for important PDF processes for specific analyses from ATLAS and CMS: Drell--Yan lepton-pair production, top-pair production, and Z-boson production with non-zero transverse momentum.
 
-Finally, we discussed the issue of subtracting EW corrections in experimental data, which becomes an important consideration when combining the interpolation grids with the corresponding experimental data in a PDF fit including EW and mixed QCD--EW corrections.
+Finally, we discussed the issue of subtracting EW corrections in experimental data, which becomes an important consideration when combining the interpolation grids with the corresponding experimental data in a PDF fit including EW and combined QCD--EW corrections.
 
-Having developed and thoroughly tested \textsc{PineAPPL}, all technical requirements are fulfilled for producing the first global PDF fit including EW and mixed QCD--EW corrections.
+Having developed and thoroughly tested \textsc{PineAPPL}, all technical requirements are fulfilled for producing the first global PDF fit including EW and combined QCD--EW corrections.
 This will have at least two advantages: in PDF fits phase-space regions are usually cut away if they exhibit large EW corrections; including them therefore increases the number of data points in a fit and therefore indirectly enlarges a PDF set's interpolation region.

### 2020-08-10 paper/sec-introduction.tex
Replace 'mixed' with 'combined'

@@
 (see e.g.\ ref.~\cite{Amoroso:2020lgh} and references therein). The computation
-of higher-order corrections in the electroweak (EW) and mixed QCD+EW theory has
+of higher-order corrections in the electroweak (EW) and combined QCD+EW theory has
 also witnessed a comprehensive progress. Frameworks 
@@
 small parameters in the perturbative expansion, and the computation of 
-theoretical predictions, accurate to NLO in both (including mixed-coupling 
+theoretical predictions, accurate to NLO in both (including multi-coupling
 QCD--EW terms), is automated~\cite{Kallweit:2014xda,Biedermann:2017yoi,Frederix:2018nkq}. For an extensive and recent review, see ref.~\cite{Denner:2019vbn}.
@@
 the accuracy of the perturbative computation used in the PDF determination
-(matched to the precision of the data). Electroweak (including mixed QCD+EW) 
+(matched to the precision of the data). Electroweak (including combined QCD--EW) 
 effects should therefore naturally be included in a PDF determination. The 

### 2020-08-10 paper/sec-pineappl.tex
Replace 'mixed' with 'combined'

@@
 This puts \textsc{PineAPPL} in the same category as \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}.
-With respect to the capabilities of these computer codes, \textsc{PineAPPL} makes it possible for the first time to include also higher-order corrections due to EW, and in general mixed QCD--EW, effects.
+With respect to the capabilities of these computer codes, \textsc{PineAPPL} makes it possible for the first time to include also higher-order corrections due to EW, and in general combined QCD--EW, effects.
 Documenting this extension, and how to interface \textsc{PineAPPL} with a general-purpose matrix-element generator, is the main interest of this paper.
@@
 \begin{itemize}
-\item The inclusion of perturbative corrections (fixed-order, i.e.\ without parton-shower matching) with any given set of powers of $\alpha$, $\alphas$, in particular including mixed QCD--EW corrections.
+\item The inclusion of perturbative corrections (fixed-order, i.e.\ without parton-shower matching) with any given set of powers of $\alpha$, $\alphas$, in particular including combined QCD--EW corrections.
 \item The support for non-coloured initial-state partons, such as photon-initiated contributions.
@@
 The correction with the largest power in $\alphas$ can be unambiguously called \enquote{the} QCD correction, and the one with the largest power in $\alpha$ \enquote{the} EW correction.
-All remaining corrections are of mixed type, meaning that they, in general, cannot be attributed to either one of strong or electroweak origin.
+All remaining corrections are of combined type, meaning that they, in general, cannot be attributed to either one of strong or electroweak origin.
 However, for the sake of simplicity and with a slight abuse of notation, it is customary to refer
@@
 
-Since this process has a single LO, mixed QCD--EW corrections first appear at next-to-next-to-leading order (NNLO), which include the QCD correction at $\mathcal{O} (\alphas^2 \alpha^2)$, the EW correction $\mathcal{O} (\alpha^4)$, and a single mixed correction at $\mathcal{O} (\alphas \alpha^3)$.
+Since this process has a single LO, combined QCD--EW corrections first appear at next-to-next-to-leading order (NNLO), which include the QCD correction at $\mathcal{O} (\alphas^2 \alpha^2)$, the EW correction $\mathcal{O} (\alpha^4)$, and a single combined correction at $\mathcal{O} (\alphas \alpha^3)$.
 
@@
 This includes the photon--photon initial state, which appears already at LO.
-In the corresponding Feynman diagrams all particles are colourless, so that the photon--photon initiated contributions only receive EW and mixed QCD--EW corrections, but never (pure) QCD corrections.
+In the corresponding Feynman diagrams all particles are colourless, so that the photon--photon initiated contributions only receive EW and combined QCD--EW corrections, but never (pure) QCD corrections.
 The EW corrections also introduce quark--photon contributions, in analogy of QCD corrections introducing quark--gluon contributions.

### 2020-08-10 paper/sec-results.tex
Add sentence about PI size of MRST2004qed
Replace 'mixed' with 'combined'

@@
 $\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$ contributions.
-Mixed-coupling QCD--EW corrections occur only at NNLO, and are therefore not
+Combined QCD--EW corrections occur only at NNLO, and are therefore not
 considered here. EW corrections for this process were computed in
@@
 The PI contribution raises from about \SI{1.3}{\percent} in the lowest bin to
-about \SI{3.6}{\percent} in the highest bin. Overall, the EW corrections range between \SI{5}{\percent}
+about \SI{3.6}{\percent} in the highest bin.
+For the MRST2004qed PDF set, which is used to subtract PI contributions (see section~\ref{sec:doublecounting}), the value in the largest highest bin is roughly twice as large, \SI{6.9}{\percent} (also in absolute numbers).
+Overall, the EW corrections range between \SI{5}{\percent}
 around $M_{\ell\bar\ell}\sim \SI{150}{\giga\electronvolt}$, \SIrange{2}{3}{\percent} for intermediate invariant mass

### 2020-08-12 paper/app-lumis.tex
Appendix B done, modulo final Z pT results

@@
   and 0.0, 0.3, 0.6, 0.9, 1.3, 2.5.
-\item Table~\ref{tab:B9} collects the parton luminosities contributing
-  to the Z $p_{\mathrm{T}}$ distribution measured by the CMS experiment at
-  a centre-of-mass energy of
+\item Table~\ref{tab:B10} collects the one hundred and sixty-six
+  parton luminosities contributing to the Z $p_{\mathrm{T}}$ distribution
+  measured by the CMS experiment at a centre-of-mass energy of
   \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. The bin edges are:
@@
 %-------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------
+\begin{table}[!p]
+  \centering
+  \tiny
+  \input{tables/TableB10a.tex}
+\end{table}
+\begin{table}[!p]
+  \centering
+  \tiny  
+  \input{tables/TableB10b.tex}
+\end{table}
+\begin{table}[!p]
+  \centering
+  \tiny 
+  \input{tables/TableB10c.tex}
+\end{table}
+\begin{table}[!p]
+  \centering
+  \tiny
+  \renewcommand{\arraystretch}{0.9}
+  \input{tables/TableB10d.tex}
+  \caption{The 166 parton luminosities contributing to the predictions,
+    accurate to NLO QCD+EW, to the Z $p_{\mathrm{T}}$ distribution
+    measured by the CMS experiment at a centre-of-mass energy of
+    \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. The bin edges are:
+    20, 22, 26, 28, 32, 37, 43, 52, 65, 85, 120, 160, 190, 220, 250, 300,
+    400, 500, 800, 1500~GeV.}
+  \label{tab:B10}
+\end{table}
+%-------------------------------------------------------------------------------

### 2020-08-12 paper/sec-results.tex
Provisional results for Z pT

@@
 The process receives contributions from 101 (166) parton luminosities,
-see appendix~\ref{app:lumis} for details.
+see appendix~\ref{app:lumis}.
 
@@
 
-As in the case of Drell-Yan, we use a fixed value for the renormalisation and factorisation 
-scales $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$.
-We require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$, $|\eta_\ell|<2.4$,
-$|M_{\ell\bar\ell} - M_\mathrm{Z}| < \SI{15}{\giga\electronvolt}$,
+As in the case of Drell-Yan, we use a fixed value for the renormalisation and
+factorisation scales $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$, where
+$M_\mathrm{Z}$ is the $\mathrm{Z}$-boson mass. Consistently with the
+experimental analysis, we require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$,
+$|\eta_\ell|<2.4$, $|M_{\ell\bar\ell} - M_\mathrm{Z}| < \SI{15}{\giga\electronvolt}$,
 $|y_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<p_\mathrm{T}^{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the
-transverse momentum and pseudorapidity of each lepton, and for the invariant mass,
-pseudorapidity and transverse momentum of the lepton pair. Imposing a minimum cut for the transverse momentum of the lepton pair 
-is necessary as we rely on a fixed-order computation, without including resummation effects.
+transverse momentum and pseudorapidity of each lepton, and for the invariant
+mass, pseudorapidity and transverse momentum of the lepton pair.
+We finally discard all bins with
+$p_\mathrm{T}^\mathrm{Z}<\SI{20}{\giga\electronvolt}$ to avoid a kinematic
+ergion where resummation effects are sizeable.
 
-\paragraph{Numerical results.} We finally
+\paragraph{Numerical results.} In figure~\ref{fig:cmsZ13TeV} we report the
+distribution differential in the transverse momentum of the $\mathrm{Z}$
+boson. Also in this case, the \textsc{PineAPPL} result is well validated, as it
+differs from the MC result by $\SI{0.5}{\permille}$ at most. The accuracy of the
+theory or the choice of scale do not alter this conclusion.
 
@@
 %-------------------------------------------------------------------------------
+
+The process receives its leading contribution from $\mathrm{qg}$ and
+$\bar{\mathrm{q}}g$ initiated channels, which account for about 65\%
+of the cross section, with some variations in the relative contributions from
+individual quark and atiquark flavours as the transverse momentum of the
+$\mathrm{Z}$ boson varies; the PI contribution always remain negligible.
+Overall, the EW corrections suppress the theoretical predictions by about
+2\% -- 7\% as the transverse momentum of the $\mathrm{Z}$ boson increases.
+The size of this shift is usually as large as the data uncertainty, and
+exceeds it at large values of $p_\mathrm{T}^\mathrm{Z}$. As a consequence,
+we anticipate the inclusion of EW corrections to be relevant for an accurate
+fit to this data set.
+
+The size of the EW correction is between four and six times larger than the
+size of the PDF uncertainty: as previously noted in th eother cases, this fact
+suggests that, once included in a PDF fit, EW corrections can improve the
+accuracy of the PDFs. In comparison to the scale ucnertainty, the size of the
+EW corrections remains negligible, as NNLO QCD corrections are comparatively
+large, as expected in a process mostly initiated by gluons. They should
+therefore be included along with EW corrections in a fit of PDFs. Finally, the
+Monte Carlo uncertainty is well under control, as it remains mostly negligible
+in comparison to the PDF, scale and data uncertainty.

### 2020-08-13 paper/sec-results.tex
section 3

@@
 
-In this section we demonstrate the capabilities of \textsc{PineAPPL} by
-computing fast-in\-ter\-po\-la\-tion grids, accurate to NLO QCD and NLO QCD+EW,
+In this section we demonstrate the capabilities of \textsc{MG5\_aMC}+\textsc{PineAPPL} by
+computing fast-interpolation grids, accurate to NLO QCD and NLO QCD+EW,
 for a representative set of processes in which EW corrections may have a
 sizeable effect on the accuracy of the theoretical predictions.
-In order to consider realistic kinematics for these
-processes, we rely on the measurements that are commonly included in PDF
+In order to consider some realistic kinematics for these
+processes, we rely on a set of measurements that are commonly included in PDF
 fits. Our aim is twofold. First, we want to validate the results
 obtained with \textsc{PineAPPL}; second, we want to assess the
-impact of the EW corrections for the specific experimental setups. We start by describing the
-setup employed for the computation, then we discuss the features of each process, along with
-the corresponding results.
+impact of the EW corrections for the specific experimental setups. We describe
+the settings employed for the computations, and the corresponding results for
+each process considered.
 
@@
 of any hadronic jet produced in the final state: 
- in particular, PI contributions are consistently included at LO and NLO.\footnote{We employ the $\overline{G}_\mu$ scheme also for the QED coupling entering vertices involving initial-state photons, see section~4.3.3 of ref.\cite{Denner:2019vbn}.}
+ in particular, photon-induced (PI) contributions are consistently included at LO and NLO.\footnote{We employ the $\overline{G}_\mu$ scheme also for the QED coupling entering vertices involving initial-state photons, see section~4.3.3 of ref.\cite{Denner:2019vbn}.}
 We use a PDF set that contains a photon PDF, namely
@@
 The central values of the renormalisation and factorisation scales, $\mu_\mathrm{R}$ and
-$\mu_\mathrm{F}$, are chosen in a process specific way, and are discussed in sec.~\ref{subsec:processes_and_measurements}. In order to estimate the missing higher-order uncertainty,
+$\mu_\mathrm{F}$, are chosen in a process-specific way, as discussed in sec.~\ref{subsec:processes_and_measurements}. In order to estimate the missing higher-order uncertainty,
 we allow the events to be reweighted on-the-fly in the Monte Carlo generation upon scale
@@
 are varied down to a factor $1/2$ and up to a factor $2$, and the envelope
-from the nine-point scale variations is constructed. However, we note that
+from the nine-point scale variations is constructed,
+see equation~\eqref{eq:}. However, we note that
 \textsc{PineAPPL} allows the user to determine the envelope with any point
@@
 \begin{equation}
-\begin{aligned}
-M_\mathrm{W} &= \SI{80}{\giga\electronvolt} \text{,} \quad &
-M_\mathrm{Z} &= \SI{91.176}{\giga\electronvolt} \text{,} \quad &
-m_\mathrm{t} &= \SI{172.5}{\giga\electronvolt} \text{,} \quad \\
-\Gamma_\mathrm{W} &= \SI{2.09}{\giga\electronvolt} \text{,} &
-\Gamma_\mathrm{Z} &= \SI{2.50}{\giga\electronvolt} \text{,}
-\end{aligned}
+%\begin{aligned}
+%M_\mathrm{W} &= \SI{80}{\giga\electronvolt} \text{,} \quad &
+M_\mathrm{Z} = \SI{91.176}{\giga\electronvolt} \text{,} \quad 
+m_\mathrm{t} = \SI{172.5}{\giga\electronvolt} \text{,} \quad 
+%\Gamma_\mathrm{W} &= \SI{2.09}{\giga\electronvolt} \text{,} &
+\Gamma_\mathrm{Z} = \SI{2.50}{\giga\electronvolt} \text{,}
+%\end{aligned}
 \label{eq:parameters}
 \end{equation}
-where $M_\mathrm{W}$, $M_\mathrm{Z}$ and $m_\mathrm{t}$ are the values of the W-boson, Z-boson, and
-top-quark masses, respectively, and $\Gamma_\mathrm{W}$ and $\Gamma_\mathrm{Z}$ are the width of
-the W boson and of the Z boson, respectively. The value of the strong
+where $M_\mathrm{Z}$ and $m_\mathrm{t}$ are the values of the Z-boson, and
+top-quark masses, respectively, and $\Gamma_\mathrm{Z}$ is the width of
+the Z boson. The value of the strong
 coupling is chosen consistently with the PDF set, $\alphas(M_\mathrm{Z})=0.118$.
-The definition of observables and cuts is process-specific, and it follows the corresponding experimental measurements.
+
+The definition of observables and cuts is process-specific, and it follows the corresponding experimental measurements,
+see secion~\ref{sec:subsec:processes_and_measurements}.
 When relevant, final-state photons and massless charged fermions (leptons and light quarks) are recombined together 
@@
 see refs.~\cite{Frederix:2016ost,Denner:2019zfp}.} Finally, although contributions corresponding to the radiation
-of a heavy boson are formally of the same perturbative order as the EW corrections, they are not included in our
+of a heavy boson are formally of the same perturbative order of the EW corrections, they are not included in our
 computations. In fact, while nothing prevents to include these contributions \emph{a posteriori}, as they are finite,
@@
 top-quark pair production, and Z-boson (lepton-pair) production with non-zero
-transverse momentum in proton-proton collisions. For each of these processes,
-we present the experimental measurements, process-specific settings, and phenomenological results.
+transverse momentum in proton-proton collisions. In the following, we shall
+present the experimental measurements, the process-specific settings, and
+the phenomenological results for each of these processes.
 
@@
 specified in section~\ref{subsec:computational_settings}. We
-will refer to the first result as the MC result, and to the second as
+refer to the first result as the MC result, and to the second as
 the \textsc{PineAPPL} result. We repeat the computation for theories accurate
 to NLO QCD and to NLO QCD+EW, respectively. The corresponding orders of the
-strong and electroweak couplings that we consider are specified for each process. In each case, we determine the
+strong and EW couplings that we consider are specified for each process. In each case, we determine the
 PDF uncertainty (coming from the PDF ensemble), the scale uncertainty (coming
@@
 observe that the validation of the \textsc{PineAPPL} result against the MC
-result is successful. The relative difference between the two is of the order
+result is successful. The relative difference between the two is of the order of
 \SI{0.1}{\permille} at most, with negligible fluctuations across different
@@
 The PI contribution raises from about \SI{1.3}{\percent} in the lowest bin to
-about \SI{3.6}{\percent} in the highest bin.
-For the MRST2004qed PDF set, which is used to subtract PI contributions (see section~\ref{sec:doublecounting}), the value in the largest highest bin is roughly twice as large, \SI{6.9}{\percent} (also in absolute numbers).
+about \SI{3.6}{\percent} in the highest bin.\footnote{For the \texttt{MRST2004qed} PDF set~\cite{Martin:2004dh}, which is used to subtract PI contributions (see section~\ref{sec:doublecounting}), the value in the highest bin is roughly twice as large, \SI{6.9}{\percent} (also in absolute numbers).}
 Overall, the EW corrections range between \SI{5}{\percent}
@@
 always larger, especially at the boundaries of the distribution. This fact
-suggests that, once included in a global fit, EW corrections could recast the
-relative weight of each data set included in the fit, and possibly lead to
-an improvement in their overall description. In comparison to the scale
+suggests that, once included in a global fit, EW corrections will make PDFs
+more accurate. In comparison to the scale
 uncertainty, the size of the EW correction is similar, except for the four bins
 at the largest invariant mass, where the latter is significantly larger than
-the former. The size of the scale variation is the same for the QCD and the
-QCD+EW theories. These facts suggest that the NNLO QCD correction is comparable
+the former. This fact suggests that the NNLO QCD correction is comparable
 to the NLO QCD+EW correction, except at very large values of the invariant mass,
@@
 include the EW corrections in order to obtain an accurate description of the
-large invariant mass bins. Finally, the Monte Carlo statistical
+large invariant mass bins. Finally, the Monte Carlo 
 uncertainty remains negligible in comparison to the data, PDF and scale
@@
       centre-of-mass energy of \SI{7}{\tera\electronvolt}~\cite{Chatrchyan:2013tia}. Displayed are
-      only two of the six invariant mass bins available, respectively below the
+      only four of the six invariant mass bins available, respectively below the
       Z-boson mass peak, $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$, on the Z-boson mass
@@
 However, as already observed in the case of the ATLAS measurement, should EW
-corrections be included in a fit of PDFs, these are likely to become more
+corrections be included in a fit of PDFs, the latter are likely to become more
 accurate: even though the apparent description of the data will not
@@
 of invariant mass window around the Z peak, in which positive and negative EW corrections almost cancel.
-Finally, the Monte Carlo statistical uncertainty remains negligible
+Finally, the Monte Carlo uncertainty remains negligible
 in comparison to the data, PDF and scale uncertainties, and to the size of the
@@
 pure QCD contributions at LO, $\mathcal{O}(\alphas^2)$, and
-at NLO, $\mathcal{O}(\alphas^3)$. They make up our NLO QCD
+at NLO, $\mathcal{O}(\alphas^3)$. These orders make up our NLO QCD
 computation. The NLO QCD+EW computation includes the $\mathcal{O}(\alphas^2)$
@@
 transverse momentum of the top quark (the invariant mass of the top-quark pair)
-increases; the largest PI contribution for this process is $\gamma\mathrm{g}$ scattering,
+increases; the largest PI contribution for this process comes from $\gamma\mathrm{g}$ scattering,
 which accounts for about \SIrange{0.5}{1}{\percent} (\SIrange{0.5}{0.7}{\percent}) of the cross
@@
 likely to be easily accommodated by the large data uncertainty, should the data
-be fitted with the inclusion of EW corrections; PDFs will possibly not become
-more precise.
+be fitted with the inclusion of EW corrections.
 
@@
 We select the single-differential transverse momentum distribution of the
-the Z boson, $p_\mathrm{T}^\mathrm{Z}$, measured by the CMS experiment at a centre-of-mass
-energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. While this measurement is not
-included in any PDF determination, its expected impact on parton densities has been studied in 
-ref.~\cite{Boughezal:2017nla}. Since this process shows very low experimental uncertainties (at the percent level or below), and is
-known to an excellent degree as far as QCD corrections are concerned~\cite{Gehrmann-DeRidder:2017mvr,Bizon:2019zgf} {\bf MZ there are at least 5-6 other papers both
-by the zurich group and the argonne one, but on Z+jet rather than z-pt predictions. Should we cite them?}
-EW corrections are expected to be essential in order to achieve a good
-description of it, and to constrain accurately the PDFs. Analogous measurements,
+the Z boson, $p_\mathrm{T}^\mathrm{Z}$, measured by the CMS experiment at a
+centre-of-mass energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}.
+This measurement, which has not been included in any PDF determination so far,
+shows very low experimental uncertainties (at the percent level or below).
+EW corrections are therefore expected to be essential to achieve a good
+description of it, and to constrain accurately the PDFs, together with
+NNLO QCD corrections, which are already well
+known~\cite{Gehrmann-DeRidder:2017mvr,Bizon:2019zgf}
+{\bf MZ there are at least 5-6 other papers both
+  by the Zurich group and the Argonne one, but on Z+jet rather than
+  Z-pt predictions. Should we cite them?}
+Analogous measurements,
 from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
-experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt}, were partly included (upon
+experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt},
+were partly included (upon
 selection of an appropriate kinematic cut that excluded bins with large EW
-corrections) in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
+corrections) in a dedicated study~\cite{Boughezal:2017nla},
+in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
 the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
@@
 
-The process receives its leading contribution from $\mathrm{qg}$ and
-$\bar{\mathrm{q}}g$ initiated channels, which account for about 65\%
+The process receives its leading contribution from $\mathrm{qg}$- and
+$\bar{\mathrm{q}}\mathrm{g}$-initiated channels, which account for about 65\%
 of the cross section, with some variations in the relative contributions from
@@
 The size of the EW correction is between four and six times larger than the
-size of the PDF uncertainty: as previously noted in th eother cases, this fact
+size of the PDF uncertainty: as previously noted in the other cases, this fact
 suggests that, once included in a PDF fit, EW corrections can improve the
-accuracy of the PDFs. In comparison to the scale ucnertainty, the size of the
+accuracy of the PDFs. In comparison to the scale uncertainty, the size of the
 EW corrections remains negligible, as NNLO QCD corrections are comparatively
@@
 Monte Carlo uncertainty is well under control, as it remains mostly negligible
-in comparison to the PDF, scale and data uncertainty.
+in comparison to the PDF, scale and data uncertainty, and to the size of the
+EW correction.

### 2020-08-13 paper/sec-doublecounting.tex
section 4

@@
 The ability to include theoretical calculations of EW corrections in
-PDF determinations, as has been mentioned in the introduction, is not enough to make a \emph{consistent} fit possible. Indeed, experimental data should
-be provided in a format that allows PDF collaborations to easily employ them in these fits in a theoretically sound manner. Before concluding the paper,
-we will provide some guidelines to facilitate a consistent presentation of experimental data to that end.
-We focus on the problem of data with (partially) subtracted EW effects, which, in PDF fits with theory predictions including them, leads to double counting of these EW effects.
+PDF determinations is not sufficient to make a \emph{consistent} fit possible. Indeed, experimental data should
+be provided in a format that allows PDF collaborations to easily employ them in these fits in a theoretically sound manner. To this purpose, in this section
+we formulate some
+guidelines to facilitate a consistent presentation of the experimental data.
+We focus on the problem of data with (partially) subtracted EW effects, which, in PDF fits with theory predictions including them, leads to a double counting issue.
 
-\begin{figure}
+\begin{figure}[!t]
     \centering
@@
 \end{figure}
-An example is the subtraction of (irreducible) background processes which must not be considered as such. A very blatant case
+
+A first example is the subtraction of (irreducible) background processes which must not be considered as such. A very blatant case
 is neutral-current Drell--Yan, where the signal process is the production of an opposite-sign lepton pair, which starts
 at $\mathcal O(\alpha^2)$. Because this process is usually thought
-as a quark-initiated $s$-channel mechanism ($\mathrm{q} \bar{\mathrm{q}} \to \gamma^*/\mathrm{Z} \to \ell \bar{\ell}$), in many analyses the photon-induced component,
+as a quark-initiated $s$-channel mechanism ($\mathrm{q} \bar{\mathrm{q}} \to \gamma^*/\mathrm{Z} \to \ell \bar{\ell}$), in many analyses the PI component,
 $\gamma \gamma \to \ell \bar{\ell}$ in the $t$ channel, is considered a different process, and therefore as a background and subtracted.
@@
 In either case, a comparison between these data and a NLO-EW accurate simulation aimed at the extraction of some parameter would be meaningless, as some effects included in the latter
-have been removed from the former. The typical example relevant for LHC is the deconvolution of effects due to multiple-photon radiation
+have been removed from the former. The typical example relevant for the LHC is the deconvolution of effects due to multiple-photon radiation
 from light particles in the final state. This applies mostly
-to processes such as neutral- or charge-current Drell--Yan, especially when electrons are considered. The problem lies in the fact that
+to processes such as neutral- or charged-current Drell--Yan, especially when electrons are considered. The problem lies in the fact that
  electrons, and to a lesser extent muons, tend to radiate photons, which are not accounted
@@
 the specific version) employed for the shower inversion. 
-This fact is especially problematic if deconvolved datasets are the only ones which are published, since undoing the exact deconvolution can be very difficult, or practically impossible, as time passes.
-(TODO insert comment about LEP ISR and DIS EW effects removal).
+This fact is especially problematic if deconvolved datasets are the only ones which are published, since undoing the exact deconvolution can be very difficult, or practically impossible.
+(\textbf{TODO insert comment about LEP ISR and DIS EW effects removal}).
 
@@
 inclusive on the effect of extra collinear emissions. This fact encourages to explore the possibility of employing a dressed-lepton
-definition, regardless of the leptonic flavour. It is reassuring to acknowledge that this practice is already being followed in experimental analyses:
-indeed, to mention two examples of analyses discussed in this paper, in ref.~\cite{Aad:2015auj} data for dressed leptons are published, together with the Born-level
-and bare ones, while refs.~\cite{Sirunyan:2019bzr} employs a dressed-lepton definition.
+definition, regardless of the leptonic flavour. We acknowledge that this practice is already being followed in (some) experimental analyses:
+indeed, to mention two examples discussed in this paper, in ref.~\cite{Aad:2015auj} data for dressed leptons are published, together with the Born-level
+and bare ones, while refs.~\cite{Sirunyan:2019bzr} employs a dressed-lepton definition. We therefore recommend that these ways of presenting the experimental
+data becomes standard in the future.

### 2020-08-13 paper/paper.tex
Appendix B done, modulo final Z pT results
Acknowledgements

@@
 \usepackage{tabularx}
+\usepackage{textcomp}
+\usepackage{xltabular}
 
 \newcommand{\alphas}{\alpha_\mathrm{s}}
+\DeclareSIUnit\permille{\text{\textperthousand}}
+
 \preprint{Nikhef-2020-026 TIF-UNIMI-2020-22}
@@
 \acknowledgments
-We are grateful to Rikkert Frederix for discussions and explanations about
-\textsc{aMCfast}. We acknowledge discussions with 
+We are grateful to Rikkert Frederix for discussions about
+\textsc{aMCfast}, and to Stefan Dittmaier for a critical reading of the
+manuscript. We acknowledge discussions with 
 Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
@@
 %Alessandro Vicini\\
-%Stefan Dittmaier
+S.C.\ and C.S.\ are supported by the European Research Council under the European Union's
+Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
 E.R.N.\ is supported by the European Commission through a Marie
 Sk\l odowska-Curie Action (grant agreement no.\ 752748).
-C.S.\ and S.C.\ are supported by the European Research Council under the European Union's
-Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
-MZ thanks the Nikhef institute in Amsterdam,
-where he was employed during the early stages of this paper.
+M.Z.\ thanks the Nikhef institute in Amsterdam,
+where he was employed when this paper was started.
 

### 2020-08-13 paper/sec-introduction.tex
section 1

@@
 by default in PDF determinations, NLO EW corrections should be
-taken into account on the same footing. Second, the virtual exchange of soft or 
+taken into account as well. Second, the virtual exchange of soft or 
 collinear weak bosons leads to Sudakov 
@@
 these grids, \textsc{APPLgrid}~\cite{Carli:2010rw} and
-\textsc{fastNLO}~\cite{Kluge:2006xs}, none of them supports the inclusion of EW
+\textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}, none of them supports the inclusion of EW
 corrections nor the interface to a Monte Carlo generator accurate to 
@@
 In this paper we address the first of these two problems. Specifically, 
-we develop \textsc{PineAPPL}, a new computer library that provides a direct interface
-from parton-level Monte Carlo event generators accurate up to any fixed order to
-fast-interpolation grids. The library supports variations of the factorisation
-and renormalisation scales. Planned extensions will include support for resummation and matching with a photon- and/or
-parton-shower. An interface to the library is included in
-\textsc{MadGraph5\_aMC@NLO} (\textsc{MG5\_aMC} henceforth), with which it has
-been developed and tested, and which supersedes \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{aMCfast}~\cite{Bertone:2014zva}.
-However, \textsc{PineAPPL} can be easily interfaced with every
-Monte Carlo generator, e.g.\ \textsc{SHERPA}~\cite{Biedermann:2017yoi}, where it could complement \textsc{MCgrid}~\cite{DelDebbio:2013kxa,Bothmann:2015dba}.
+we develop \textsc{PineAPPL}, a library that allows the user to generate
+fast-interpolation grids, accurate to up to any fixed order in the strong and
+EW couplings. The library supports variations of the factorisation
+and renormalisation scales, and can be extended to include
+resummation and matching with a photon- and/or parton-shower.
+The grids in the new \textsc{PineAPPL} format complement those
+(accurate to fixed-orders in the strong coupling only) that can be generated 
+in the \textsc{APPLgrid} and \textsc{FastNLO} formats. The \textsc{PineAPPL}
+library is interfaced to \textsc{MadGraph5\_aMC@NLO} (\textsc{MG5\_aMC}
+henceforth), with which it has been developed and tested. In this respect,
+\textsc{PineAPPL} supersedes
+\textsc{APPLgrid}+\textsc{aMCfast}~\cite{Bertone:2014zva}.
+\textsc{PineAPPL} can also be easily interfaced with any Monte Carlo generator,
+e.g.\ \textsc{SHERPA}~\cite{Biedermann:2017yoi}, where it complements
+\textsc{MCgrid}~\cite{DelDebbio:2013kxa,Bothmann:2015dba}.
 

### 2020-08-13 paper/sec-introduction.tex
General revision

@@
 which can make the coefficients of the EW series grow faster than 
-their QCD counterparts. Such a behaviour becomes relevant in
+their QCD counterparts. This behaviour is relevant in
 phase-space regions associated with large mass scales (roughly of the order
@@
 In this paper we address the first of these two problems. Specifically, 
-we develop \textsc{PineAPPL}, a library that allows the user to generate
+we develop \textsc{PineAPPL}, a library that allows any user to generate
 fast-interpolation grids, accurate to up to any fixed order in the strong and
@@
 and renormalisation scales, and can be extended to include
-resummation and matching with a photon- and/or parton-shower.
+resummation, and matching with a photon- and/or parton-shower.
 The grids in the new \textsc{PineAPPL} format complement those
@@
 in the \textsc{APPLgrid} and \textsc{FastNLO} formats. The \textsc{PineAPPL}
-library is interfaced to \textsc{MadGraph5\_aMC@NLO} (\textsc{MG5\_aMC}
+library is interfaced to \textsc{MadGraph5\_aMC@NLO} (\textsc{mg5\_aMC}
 henceforth), with which it has been developed and tested. In this respect,
@@
 \textsc{APPLgrid}+\textsc{aMCfast}~\cite{Bertone:2014zva}.
-\textsc{PineAPPL} can also be easily interfaced with any Monte Carlo generator,
+\textsc{PineAPPL} can also be easily interfaced to any Monte Carlo generator,
 e.g.\ \textsc{SHERPA}~\cite{Biedermann:2017yoi}, where it complements

### 2020-08-13 paper/sec-pineappl.tex
General revision

@@
 
+In this section we introduce \textsc{PineAPPL}. We first describe the
+general scope and features of the library, we then formulate the problem of
+computing Monte Carlo weights for cross sections in a multi-coupling expansion,
+and we finally address how this problem is solved with a suitable grid
+representation.
+
+\subsection{The \textsc{PineAPPL} library}
+\label{sec:library}
+
 \textsc{PineAPPL} is a new library which stores phase-space weights of a Monte Carlo (MC) integration of a fixed-order calculation independently from the chosen PDFs.
-This separates the task of producing predictions for observables into two steps: 1) the generation of the \emph{grids}, which is how the generated files are called, and 2) the convolution of those grids with a set of PDFs.
-The advantage of this method is that the time-consuming step 1) has to be done only once and, therefore, allows in step 2) for very quick convolutions of a given grid with multiple PDF sets.
+The task of computing predictions for physical observables is therefore split
+into two steps: 1) the generation of the \emph{grids}, that is the files in
+which the MC weights are stored, and 2) the convolution of these grids with a set of PDFs.
+The advantage of this method is that the time-consuming step 1) has to be performed only once, and that step 2) is reduced to a fast convolution of a given grid with one (or more) PDF set(s).
 
-The convolution is typically done in a few seconds or less, which offers at least two applications:
+The convolution is typically done in few seconds or less, a fact that offers at least two applications:
 \begin{enumerate}
-\item the study of PDF-dependence of observables; e.g.\ PDF set comparisons, PDF uncertainties for different PDF set, $\alphas$ variations, etc., and
-\item the determination of PDF sets themselves; the grids together with the corresponding experimental data constitute two important ingredients for a PDF fit.
+\item the study of the PDF-dependence of the observables; e.g.\ PDF set comparisons, PDF uncertainty computations, $\alphas$ variations, etc., and
+\item the determination of PDF sets themselves; together with the corresponding experimental data, the grids constitute two important ingredients for a PDF fit.
 \end{enumerate}
-This puts \textsc{PineAPPL} in the same category as \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}.
-With respect to the capabilities of these computer codes, \textsc{PineAPPL} makes it possible for the first time to include also higher-order corrections due to EW, and in general combined QCD--EW, effects.
-Documenting this extension, and how to interface \textsc{PineAPPL} with a general-purpose matrix-element generator, is the main interest of this paper.
+These features are common to both \textsc{PineAPPL} and \textsc{APPLgrid}~\cite{Carli:2010rw} or \textsc{FastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}.
+However, in comparison to the last two pieces of code,
+\textsc{PineAPPL} allows one to include also higher-order corrections due to EW, and in general combined QCD--EW, effects for the first time.
+Documenting this extension, and how to interface \textsc{PineAPPL} with a general-purpose matrix-element generator, is the main goal of this paper.
 
-In particular, the following features are supported:
+In particular, \textsc{PineAPPL} supports the following features.
 \begin{itemize}
 \item The inclusion of perturbative corrections (fixed-order, i.e.\ without parton-shower matching) with any given set of powers of $\alpha$, $\alphas$, in particular including combined QCD--EW corrections.
-\item The support for non-coloured initial-state partons, such as photon-initiated contributions.
-In fact, \textsc{PineAPPL} allows arbitrary initial-state combinations, e.g.\ leptonic initial states~\cite{Bertone:2015lqa,Buonocore:2020nai}.
+\item The support for non-coloured initial-state partons, such as photon-initiated contributions, and, more generally, arbitrary initial-state combinations, e.g.\ leptonic initial states~\cite{Bertone:2015lqa,Buonocore:2020nai}.
 \item The estimate of theory uncertainties via variations of the renormalisation and factorisation scale (the electroweak coupling is assumed to be scale-independent, consistently with the most common renormalisation schemes).
 \end{itemize}
-On a more technical level, we further point out the following differences and improvements in \textsc{PineAPPL}:
+
+On a more technical level, we point out the following additional features of \textsc{PineAPPL}.
+
 \begin{itemize}
-\item \textsc{APPLgrid} typically required a substantial amount of memory (close to \SI{120}{\giga\byte} for Drell--Yan), if a grid for a differential distributions with more than 10 bins was generated.
+
+\item \textsc{PineAPPL} comes with the shell command \texttt{pineappl}, which performs convolutions on the command line, without requiring the user to write a new program.
+In addition to convolutions, the shell command can also print how the luminosity function is constructed, which perturbative orders are stored in the grids, their size, the size of each partonic channel, etc., separately for each bin.
+See appendix~\ref{app:pineappl-demo} for details.
+
+\item \textsc{PineAPPL} offers an easy-to-use interface written in the C programming language, that allows MC integrators to read and write \textsc{PineAPPL} grids.
+C was chosen because it can be easily interfaced with both Fortran and C++, the two main programming languages in which most MC integrators are written.
+The interface consists of roughly thirty functions, among which only a handful are needed in practice.
+See appendix~\ref{app:example-program} for an example.
+
+\item \textsc{PineAPPL} has been explicitly interfaced to \textsc{mg5\_aMC} (v3+)~\cite{Alwall:2014hca,Frederix:2018nkq},\footnote{A version of \textsc{mg5\_aMC} interfaced to \textsc{PineAPPL} can be downloaded from \url{https://launchpad.net/mg5amc-pineappl/trunk}, and it will be included as standard in the next \textsc{mg5\_aMC} release.} for which it supersedes \textsc{aMCfast}~\cite{Bertone:2014zva}.
+See appendix~\ref{app:sample-runcard} for an example of a runcard.
+While the usage of
+\textsc{mg5\_aMC}(v3+) + \textsc{PineAPPL} is similar to that of 
+\textsc{mg5\_aMC}(v2) + \textsc{PineAPPL} + \textsc{APPLgrid}, it is however more
+efficient.
+For instance, the usage of the latter typically required a substantial amount of memory (close to \SI{120}{\giga\byte} for Drell--Yan), if a grid for a differential distribution with more than 10 bins was generated.
 The memory usage is substantially reduced (roughly \SI{1}{\giga\byte}) after \enquote{optimisation} of the grids, i.e.\ an optimisation of the grid representation in memory.
@@
 \textsc{PineAPPL} avoids this by using a more space-efficient representation from the start.
-\item \textsc{PineAPPL} offers an easy-to-use interface written in the C programming language, to allow MC integrators to read and write \textsc{PineAPPL} grids.
-C was chosen because it can be easily interfaced with both Fortran and C++, in which most MC integrators are written.
-The interface consists of roughly 30 functions, among which only a handful are needed in practice.
-See appendix~\ref{app:example-program} for an example.
-\item The shell command \texttt{pineappl}, which performs convolutions on the command line (see appendix~\ref{app:pineappl-demo}), without requiring the user to write a new program.
-In addition to convolutions, it can also print how the luminosity function is constructed, which perturbative orders are stored, their size, the size of each partonic channel, etc., separately for each bin.
+This leads to substantially faster run times, in particular for simple processes, because the grids do not need to be optimised
+and their combination is faster.
+
 %\item Possibility to import \textsc{APPLgrids} and \textsc{fastNLO} tables.
 \end{itemize}
-
-We have interfaced \textsc{PineAPPL} with the new version (v3+) of \textsc{mg5\_aMC}~\cite{Alwall:2014hca,Frederix:2018nkq}\footnote{It can be downloaded from \url{https://launchpad.net/mg5amc-pineappl/trunk}, and will soon be merged in the official code release.}, where it will replace the \textsc{aMCfast}~\cite{Bertone:2014zva} interface.
-Its usage is very similar to that of \textsc{mg5\_aMC v2}+\textsc{aMCfast}+\textsc{APPLgrid}.
-In practice, using \textsc{PineAPPL} leads to substantially faster run times, in particular for simple processes, because the grids do not need to be optimised 
-and their combination is faster.
-See appendix~\ref{app:sample-runcard} for an example of a runcard.
-Building an interface for other MC generators poses no difficulties, see appendix~\ref{app:example-program} for a small example program.
 
@@
 \end{multline}
-The cross section shown above is differential with respect to the observable $\mathcal{O}$, which, in general, is a function of phase space and subject to the usual conditions (soft and collinear safety, etc.).
+This cross section is differential with respect to the observable $\mathcal{O}$, which, in general, is a function of phase space and subject to the usual conditions (soft and collinear safety, etc.).
 
@@
 \end{equation}
-
-The Ellis--Sexton scale $Q^2$, if chosen dynamically, depends on the phase space, but we assume the fractions $\xi_\mathrm{R}$ and $\xi_\mathrm{F}$ to be constants of phase space in any case.
+The Ellis--Sexton scale $Q^2$, if chosen dynamically, depends on the phase space, however we assume the fractions $\xi_\mathrm{R}$ and $\xi_\mathrm{F}$ to be  phase-space constants in any case.
 This allows for variations around the central scale choice $\xi_\mathrm{R} = \xi_\mathrm{F} = 1$, but it does not otherwise allow for arbitrary changes of the scale.
 The terms with powers $m > 0$ and $n > 0$ vanish for the central scale choice and are only required for variations of the factorisation and renormalisation scales.
-To estimate the perturbative QCD uncertainty --- no EW uncertainty is covered by this method --- one typically uses a 7-point scale variation, {\bf MZ warning, this is not what we do later} which evaluates the cross section using the following values,
-\begin{equation}
-(\xi_\mathrm{R}, \xi_\mathrm{F}) \in \left\{ \bigl( 1, 1 \bigr), \bigl( \tfrac{1}{2}, \tfrac{1}{2} \bigr), \bigl( 2, 2 \bigr), \bigl( \tfrac{1}{2}, 1 \bigr), \bigl( 1, \tfrac{1}{2} \bigr), \bigl( 2, 1 \bigr), \bigl( 1, 2 \bigr) \right\} \text{.}
-\end{equation}
+To estimate the perturbative QCD uncertainty --- no EW uncertainty is covered by this method --- one typically uses scale variations. Common prescriptions are
+7-point and 9-points scale variations, which evaluate the cross section using
+respectively the following values
+  \begin{align}
+    (\xi_\mathrm{R}, \xi_\mathrm{F})_{\mathrm{7-pt}}
+    & \in
+    \left\{ \bigl( 1, 1 \bigr), \bigl( \tfrac{1}{2}, \tfrac{1}{2} \bigr), \bigl( 2, 2 \bigr), \bigl( \tfrac{1}{2}, 1 \bigr), \bigl( 1, \tfrac{1}{2} \bigr), \bigl( 2, 1 \bigr), \bigl( 1, 2 \bigr) \right\} \text{;}
+    \label{eq:7pt}\\
+    (\xi_\mathrm{R}, \xi_\mathrm{F})_{\mathrm{9-pt}}
+    & \in
+    \left\{ \bigl( 1, 1 \bigr), \bigl( \tfrac{1}{2}, \tfrac{1}{2} \bigr), \bigl( 2, 2 \bigr), \bigl( \tfrac{1}{2}, 1 \bigr), \bigl( 1, \tfrac{1}{2} \bigr), \bigl( 2, 1 \bigr), \bigl( 1, 2 \bigr), \bigl( \tfrac{1}{2}, 2 \bigr), \bigl(2, \tfrac{1}{2} \bigr) \right\}  \text{.}
+    \label{eq:9pt}
+   \end{align}
 The (asymmetric) uncertainties are then given as the minimum and maximum value (the envelope), measured from the central value $(1, 1)$.
@@
 \end{multline}
-\textsc{PineAPPL} can then quickly calculate hadronic cross sections for arbitrarily many PDF sets and perform scale variations.
+\textsc{PineAPPL} can then quickly calculate hadronic cross sections for
+an arbitrary number of PDF sets and perform scale variations.
 
-Note that in this section we have omitted the dependence of the weights $w$, the observable $\mathcal{O}$, and the scales $\mu_\mathrm{F}, \mu_\mathrm{R}, Q^2$ on the specific kinematics for which they are computed.
+Note that we have omitted the dependence of the weights $w$, the observable $\mathcal{O}$, and the scales $\mu_\mathrm{F}, \mu_\mathrm{R}, Q^2$ on the specific kinematics for which they are computed.
 Indeed, beyond LO, different kinematic contributions have to be considered (in ref.~\cite{Bertone:2014zva}, for example, they are labelled with an index $\alpha$, see eq.~(12) therein).
-In the FKS subtraction scheme~\cite{Frixione:1995ms,Frixione:1997np} employed in \textsc{mg5\_aMC} maximally one type of kinematics for each counterterm (soft, collinear, and soft-collinear) is needed, but this is not the general case.
+In the FKS subtraction scheme~\cite{Frixione:1995ms,Frixione:1997np} employed in \textsc{mg5\_aMC} one type of kinematics for each counterterm (soft, collinear, and soft-collinear) is needed, however this is not the general case.
 In Catani--Seymour subtraction~\cite{Catani:1996jh,Catani:2002hc}, for example, different dipoles have different phase spaces and therefore different scales.
-However, \textsc{PineAPPL} remains completely blind to this fact, and a consistent treatment is ensured by correctly using the interface between \textsc{PineAPPL}, which fills each event into a grid using the \emph{numerical value} of $Q^2$.
+\textsc{PineAPPL} remains completely blind to this fact, and a consistent treatment is ensured by filling each event into a grid using the \emph{numerical value} of $Q^2$.
 
-\subsubsection{General characteristics}
+\subsubsection{Perturbative orders}
 
-In general, we define leading order (LO) as the set of contributions for all possible initial states $a b$ that lead to the same final state $X$, for which the sum of the coupling exponents in eq.~\eqref{eq:expansion} is smallest, i.e.\ $k + l = p$, where $p = \min (k+l)$.
-This number is process dependent and usually determined by the number of external particles.
+In general, we define as leading order (LO) the set of contributions for all possible initial states $a b$ that lead to the same final state $X$, for which the sum of the coupling exponents in eq.~\eqref{eq:expansion} is smallest, i.e.\ $k + l = p$, where $p = \min (k+l)$.
+This number is process dependent and is usually determined by the number of external particles.
 For many processes there is only one LO, but when a process has multiple quark lines, colourless (photons, \dots) and coloured particles (gluons, \ldots) can be exchanged between them, making it possible to have more than one LO.
@@
 The correction with the largest power in $\alphas$ can be unambiguously called \enquote{the} QCD correction, and the one with the largest power in $\alpha$ \enquote{the} EW correction.
-All remaining corrections are of combined type, meaning that they, in general, cannot be attributed to either one of strong or electroweak origin.
-However, for the sake of simplicity and with a slight abuse of notation, it is customary to refer
-as NLO QCD (EW) corrections as
+All remaining corrections are of combined type, meaning that, in general, they cannot be attributed to either one of strong or electroweak origin.
+However, for the sake of simplicity and with a slight abuse of notation, it is customary to call
+NLO QCD (EW) corrections those
 corrections of order $\alphas$ ($\alpha$) times the couplings of the LO contribution 
@@
 \end{equation}
-The first term with index $(0,2,0,0)$ is the LO term, the following line shows the NLO QCD correction, and the final line the NLO EW correction.
+The term in the first line is the LO term, the second line shows the NLO QCD correction, and the third line the NLO EW correction.
 Note that all terms depend on the renormalisation scale only indirectly through $\alphas$, because 1) higher-order terms in $\alpha$ never generate a renormalisation scale dependence (in the $\alpha$ schemes that are valid according to section~\ref{sec:multi-coupling-expansion}) and 2) higher-order QCD corrections only introduce an explicit renormalisation scale dependence in counterterms with vertices with more than two gluons.
@@
 Both NLOs, however, have contributions from a collinear counterterm that depends on the factorisation scale.
-
 Since this process has a single LO, combined QCD--EW corrections first appear at next-to-next-to-leading order (NNLO), which include the QCD correction at $\mathcal{O} (\alphas^2 \alpha^2)$, the EW correction $\mathcal{O} (\alpha^4)$, and a single combined correction at $\mathcal{O} (\alphas \alpha^3)$.
@@
 
-In this subsection we explain the details of how the phase-space weights $w_{ab}$ in eq.~\eqref{eq:bins-of-diff-xsection} are represented.
+We now explain the details of how the phase-space weights $w_{ab}$ in eq.~\eqref{eq:bins-of-diff-xsection} are represented.
 
@@
 
-A straightforward representation are 4-tuples, which for each phase-space point saves a list of the momentum fractions $x_1$ and $x_2$, the scale $Q^2$, and the phase-space weight $w$; this is sufficient to reconstruct a total cross section.
-
+A straightforward representation is provided by  4-tuples, a list of the momentum fractions $x_1$ and $x_2$, the scale $Q^2$, and the phase-space weight $w$ for each phase-space point; 4-tuples are sufficient to reconstruct a total cross section.
 For each combination $(a,b,k,l,m,n,o)$ we save the following 4-tuples,
@@
 
-Using 4-tuples has the clear advantage of being very easy to implement and test.
-Furthermore, they reproduce the exact numerical value that is also calculated by the MC integrator.
+The 4-tuple representation is very easy to implement and test.
+Furthermore, it reproduces the exact numerical value that is also calculated by the MC integrator.
 However, the price one has to pay is the size of the 4-tuples.
-To give a concrete example, NLO QCD+EW Drell--Yan lepton-pair production (see section~\ref{sec:pineappl-example} and section~\ref{sec:dy-lepton-pair-production}) needs \SI{159}{\mega\byte} of storage for a target precision of \SI{1}{\percent} of the integrated cross section.
+For example, NLO QCD+EW Drell--Yan lepton-pair production (see section~\ref{sec:pineappl-example} and section~\ref{sec:dy-lepton-pair-production}) needs \SI{159}{\mega\byte} of storage for a target precision of \SI{1}{\percent} of the integrated cross section.
 While this is an acceptable size, increasing the precision by an order of magnitude would require roughly 100 times the size, due to the Monte Carlo convergence that goes as $1/\sqrt{N}$ with $N$ being the number of 4-tuples.
@@
 Increasing the number of bins improves the precision, but it also increases the space requirements.
-Interpolation methods offer more precision using the same number of bins.
+Interpolation methods increase the precision using the same number of bins.
 
@@
 
-The final step is filling the weights into the grid, which maps the variables $(y_1, y_2, \tau)$ onto the 3-dimensional Lagrange-interpolation grid with $N_y = 50$ points in each $y$ direction and $N_\tau = 30$ points in $\tau$ direction.
+The final step is filling the weights into the grid, which maps the variables $(y_1, y_2, \tau)$ onto the 3-dimensional Lagrange-interpolation grid with $N_y = 50$ points in each $y$ direction and $N_\tau = 30$ points in the $\tau$ direction.
 The interpolation orders $s_y$ and $s_\tau$ are 3 for each dimension, and only the subspace $[\num{2e-7},1] \times [\num{2e-7},1] \times [\num{e2},\num{e6}] \subset H$\footnote{In ref.~\cite{Bertone:2014zva} the upper limit for $Q$ is given as \SI{3162}{\giga\electronvolt} (which corresponds to $Q_\mathrm{max}^2 \approx \SI{e7}{\giga\electronvolt}$), but in the code we found the value $Q_\mathrm{max}^2 = \SI{e6}{\giga\electronvolt\squared}$.} is mapped.
 
-\begin{figure}
+\begin{figure}[!t]
 \centering
@@
 \end{tabular}
-\caption{Example for a 2-dimensional $10 \times 10$ grid, which is being filled at the location marked with the small black square at $(5.8,4.8)$.
+\caption{Example of a 2-dimensional $10 \times 10$ grid, which is being filled at the location marked with the small black square at $(5.8,4.8)$.
 Each side of the grey square starting at $k_i = 4$ and $k_j = 3$ has a length of $N_y + 1 = 4$.
@@
 
-To illustrate the filling step we give an example in figure~\ref{fig:grid}, where, for simplicity, we have chosen a static scale, so that we do not need to interpolate in $\tau$ direction, and where we also limited the number of grid points to $N_y = 10$.
+To illustrate the filling step we give an example in figure~\ref{fig:grid}, where, for simplicity, we have chosen a static scale, so that we do not need to interpolate in the $\tau$ direction, and where we also limited the number of grid points to $N_y = 10$.
 Each grid point has a numerical value $a_{i,j}$ associated, and the set of all numerical values $\{ a_{i,j} \}$ for all grid indices $(i,j) \in [0,N_y) \times [0,N_y)$ constitute \enquote{the grid}.
@@
 \end{equation}
-where the product runs over all indices of the grid points covered by the grey square in figure~\ref{fig:grid}, starting the smallest index in the square, $k_i$ and $k_j$.
+where the product runs over all indices of the grid points covered by the grey square in figure~\ref{fig:grid}, starting from the smallest index in the square, $k_i$ and $k_j$.
 Finally, we remapped

### 2020-08-13 paper/sec-results.tex
General revision

@@
 
-In this section we demonstrate the capabilities of \textsc{MG5\_aMC}+\textsc{PineAPPL} by
+In this section we demonstrate the capabilities of \textsc{mg5\_aMC}+\textsc{PineAPPL} by
 computing fast-interpolation grids, accurate to NLO QCD and NLO QCD+EW,
@@
 the settings employed for the computations, and the corresponding results for
-each process considered.
+each process.
 
@@
 (UFO)~\cite{Degrande:2011ua} model {\tt loop\_qcd\_qed\_sm\_Gmu},
-included as standard in {\sc MG5\_aMC}. It contains the UV and $R_2$
+included as standard in {\sc mg5\_aMC}. It contains the UV and $R_2$
 counterterms relevant to NLO QCD and EW corrections, the latter in the
@@
 we allow the events to be reweighted on-the-fly in the Monte Carlo generation upon scale
-variations, with the technique presented in Ref.~\cite{Frederix:2011ss}. To this purpose, we use the default \textsc{MG5\_aMC}
+variations, with the technique presented in Ref.~\cite{Frederix:2011ss}. To this purpose, we use the default \textsc{mg5\_aMC}
 implementation, whereby the factorisation and renormalisation scales
@@
 from the nine-point scale variations is constructed,
-see equation~\eqref{eq:}. However, we note that
+see equation~\eqref{eq:9pt}. However, we note that
 \textsc{PineAPPL} allows the user to determine the envelope with any point
@@
 The definition of observables and cuts is process-specific, and it follows the corresponding experimental measurements,
-see secion~\ref{sec:subsec:processes_and_measurements}.
+see section~\ref{subsec:processes_and_measurements}.
 When relevant, final-state photons and massless charged fermions (leptons and light quarks) are recombined together 
@@
 sum of their momenta is assigned to the charged fermion, and the photon is removed
-from the event. Kinematics observables and cuts are defined starting from recombined momenta. If we were interested also in jet-related observables,
+from the event. Kinematic observables and cuts are defined starting from recombined momenta. If we were interested also in jet-related observables,
 photons surviving the recombination would have to be clustered together with coloured
@@
 cross sections for the observables defined in the experimental analyses in two different
-ways: directly, by means of \textsc{MG5\_aMC}, and a posteriori, by convolving
+ways: directly, by means of \textsc{mg5\_aMC}, and a posteriori, by convolving
 the fast-interpolation grid produced by \textsc{PineAPPL} with the PDF set

### 2020-08-13 paper/app-addmaterial.tex
Updated appendices
Appendix C
General revision

@@
 but for the distributions in the rapidity of the top quark, $y_{\mathrm{t}}$,
-and in the rapidity of the top-quark pair, $y_{\mathrm{t}\bar{\mathrm{t}}}$.
+and in the rapidity of the top-quark pair, $y_{\mathrm{t}\bar{\mathrm{t}}}$. In this
+case the factorisation and renormalisation scales are kept equal to
+$H_T/s$, see section~\ref{sec:toppair}.
 
@@
     \centering
-    \includegraphics[width=0.46\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TRAP}%
+    \includegraphics[width=0.46\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TRAP}
+    \includegraphics[width=0.46\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TTRAP}\\
     \caption{Same as figure~\ref{fig:atlastop}, but for the distributions
@@
 values of invariant mass, see figure~\ref{fig:cmsdy2d11_bins3456}: the EW
-enhances the cross section (although of the order of 2\% -- 3\% across all the
-rapidity range); the amount of this shift is slightly larger than the PDF
+correction enhances the cross section by 2\% to 3\% across all the
+rapidity range; the amount of this shift is slightly larger than the PDF
 ucnertainty, but is largely overshot by the scale uncertainty; the MC\

### 2020-08-13 paper/sec-pineappl.tex
Add small fixes
- hyphenation of 'Dittmaier'
- don't use small caps PineAPPL in titles, latex doesn't do that
- use pt of the sum of the two leptons instead of the Z boson
- use SIrange for percentage ranges

@@
 
-\subsection{The \textsc{PineAPPL} library}
+\subsection{The PineAPPL library}
 \label{sec:library}
@@
 The task of computing predictions for physical observables is therefore split
-into two steps: 1) the generation of the \emph{grids}, that is the files in
+into two steps: 1) the generation of the \emph{grids}, i.e.\ the files in
 which the MC weights are stored, and 2) the convolution of these grids with a set of PDFs.

### 2020-08-13 paper/sec-results.tex
General revision
Add small fixes
- hyphenation of 'Dittmaier'
- don't use small caps PineAPPL in titles, latex doesn't do that
- use pt of the sum of the two leptons instead of the Z boson
- use SIrange for percentage ranges

@@
 \subsubsection{Top-quark pair production.}
+\label{sec:toppair}
+
 \paragraph{Experimental measurements and process features.}
@@
 \subsubsection{Z-boson production with non-zero transverse momentum.}
+\label{sec:Zpt}
 
@@
 We select the single-differential transverse momentum distribution of the
-the Z boson, $p_\mathrm{T}^\mathrm{Z}$, measured by the CMS experiment at a
+sum of the two leptons (the \enquote{Z boson}), $p_\mathrm{T}^{\ell \bar{\ell}}$, measured by the CMS experiment at a
 centre-of-mass energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}.
@@
 factorisation scales $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$, where
-$M_\mathrm{Z}$ is the $\mathrm{Z}$-boson mass. Consistently with the
+$M_\mathrm{Z}$ is the Z-boson mass. Consistently with the
 experimental analysis, we require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$,
@@
 We finally discard all bins with
-$p_\mathrm{T}^\mathrm{Z}<\SI{20}{\giga\electronvolt}$ to avoid a kinematic
-ergion where resummation effects are sizeable.
+$p_\mathrm{T}^{\ell \bar{\ell}}<\SI{20}{\giga\electronvolt}$ to avoid a kinematic
+region where resummation effects are sizeable.
 
 \paragraph{Numerical results.} In figure~\ref{fig:cmsZ13TeV} we report the
-distribution differential in the transverse momentum of the $\mathrm{Z}$
+distribution differential in the transverse momentum of the Z
 boson. Also in this case, the \textsc{PineAPPL} result is well validated, as it
@@
 The process receives its leading contribution from $\mathrm{qg}$- and
-$\bar{\mathrm{q}}\mathrm{g}$-initiated channels, which account for about 65\%
+$\bar{\mathrm{q}}\mathrm{g}$-initiated channels, which account for about \SI{65}{\percent}
 of the cross section, with some variations in the relative contributions from
-individual quark and atiquark flavours as the transverse momentum of the
-$\mathrm{Z}$ boson varies; the PI contribution always remain negligible.
+individual quark and antiquark flavours as the transverse momentum of the
+Z boson varies; the PI contribution always remain negligible.
 Overall, the EW corrections suppress the theoretical predictions by about
-2\% -- 7\% as the transverse momentum of the $\mathrm{Z}$ boson increases.
+\SIrange{2}{7}{\percent} as the transverse momentum of the Z boson increases.
 The size of this shift is usually as large as the data uncertainty, and
-exceeds it at large values of $p_\mathrm{T}^\mathrm{Z}$. As a consequence,
+exceeds it at large values of $p_\mathrm{T}^{\ell \bar{\ell}}$. As a consequence,
 we anticipate the inclusion of EW corrections to be relevant for an accurate

### 2020-08-13 paper/paper.tex
Add small fixes
- hyphenation of 'Dittmaier'
- don't use small caps PineAPPL in titles, latex doesn't do that
- use pt of the sum of the two leptons instead of the Z boson
- use SIrange for percentage ranges
Specify W-boson parameters and Gmu
These parameters enter in the definition of the EW coupling and
explicitly in some virtuals

@@
 \usepackage{lmodern}
-\usepackage[binary-units=true,detect-weight=true,table-format=4.2]{siunitx}
+\usepackage[binary-units=true,detect-weight=true,digitsep=none,table-format=4.2]{siunitx}
 \usepackage{xcolor}
@@
 We are grateful to Rikkert Frederix for discussions about
-\textsc{aMCfast}, and to Stefan Dittmaier for a critical reading of the
+\textsc{aMCfast}, and to Stefan Ditt\-mai\-er for a critical reading of the
 manuscript. We acknowledge discussions with 

### 2020-08-13 paper/sec-results.tex
Specify W-boson parameters and Gmu
These parameters enter in the definition of the EW coupling and
explicitly in some virtuals

@@
 \begin{equation}
-%\begin{aligned}
-%M_\mathrm{W} &= \SI{80}{\giga\electronvolt} \text{,} \quad &
-M_\mathrm{Z} = \SI{91.176}{\giga\electronvolt} \text{,} \quad 
-m_\mathrm{t} = \SI{172.5}{\giga\electronvolt} \text{,} \quad 
-%\Gamma_\mathrm{W} &= \SI{2.09}{\giga\electronvolt} \text{,} &
-\Gamma_\mathrm{Z} = \SI{2.50}{\giga\electronvolt} \text{,}
-%\end{aligned}
+\begin{aligned}
+M_\mathrm{W} &= \SI{80.419}{\giga\electronvolt} \text{,} \quad &
+M_\mathrm{Z} &= \SI{91.176}{\giga\electronvolt} \text{,} \quad &
+m_\mathrm{t} &= \SI{172.5}{\giga\electronvolt} \text{,} \quad \\
+\Gamma_\mathrm{W} &= \SI{2.09291}{\giga\electronvolt} \text{,} &
+\Gamma_\mathrm{Z} &= \SI{2.49877}{\giga\electronvolt} \text{,} &
+G_\mu &= \SI{1.16639e-5}{\per\giga\electronvolt\squared} \text{,}
+\end{aligned}
 \label{eq:parameters}
 \end{equation}
-where $M_\mathrm{Z}$ and $m_\mathrm{t}$ are the values of the Z-boson, and
-top-quark masses, respectively, and $\Gamma_\mathrm{Z}$ is the width of
-the Z boson. The value of the strong
+where $M_\mathrm{Z}$, $M_\mathrm{W}$, $m_\mathrm{t}$ are the values of the Z-boson, W-boson, and
+top-quark masses, respectively, $\Gamma_\mathrm{Z}$ and $\Gamma_\mathrm{W}$ are the widths of
+the Z and W bosons, and $G_\mu$ is value of the Fermi coupling. The value of the strong
 coupling is chosen consistently with the PDF set, $\alphas(M_\mathrm{Z})=0.118$.

### 2020-08-13 paper/paper.tex
Abstract

--- 2020-08-13 paper/paper.tex
@@
 
-\abstract{We introduce \textsc{PineAPPL}, a computer library allowing to produce fast-in\-ter\-po\-la\-tion
-grids for fitting parton distribution functions (PDFs)
-including corrections of strong and electroweak origin. After presenting
-the features and performance of such a code, we show how to interface \textsc{PineAPPL} with general-purpose
-softwares that allow the user to compute such corrections, providing an explicit example with
-\textsc{MadGraph5\_aMC@NLO}. We showcase some phenomenological result focusing on processes and observables
-relevant for PDF fits, and 
-we discuss what steps need to be undertaken in the presentation of experimental data in order to have them
-consistently employed in a fit including electroweak corrections.}
+\abstract{We introduce \textsc{PineAPPL}, a library that produces
+  fast-interpolation grids of physical cross sections, computed with a 
+  general-purpose Monte Carlo generator, accurate to fixed order in the
+  strong, electroweak, and combined strong-electroweak couplings. We
+  discuss its features in comparison to similar software
+  available in the literature, and we explicitly interface it to
+  \textsc{MadGraph5\_aMC@NLO}. We validate the performance of \textsc{PineAPPL}
+  by computing fast-interpolation grids, accurate to next-to-leading order in
+  the strong and electroweak couplings, for a representative set of processes
+  commonly used in the determination of the parton distribution functions (PDFs)
+  of the proton. We formulate a recommendation on the format of the experimental
+  deliverables in order to consistently incorporate them in forthcoming
+  fits of PDFs including electroweak corrections.}
 

### 2020-08-13 paper/app-addmaterial.tex

@@
 In this appendix, we collect some additional plots, in the same format of those
-presented in figures~\ref{fig:atlaszhighmass49fb}-\ref{fig:cmsZ13TeV},
+presented in figures~\ref{fig:atlaszhighmass49fb}--\ref{fig:cmsZ13TeV},
 specifically: figure~\ref{fig:atlaszhighmass49fb-lowstat} is the same as
@@
 values of invariant mass, see figure~\ref{fig:cmsdy2d11_bins3456}: the EW
-correction enhances the cross section by 2\% to 3\% across all the
+correction enhances the cross section by \SIrange{2}{3}{\percent} across all the
 rapidity range; the amount of this shift is slightly larger than the PDF
-ucnertainty, but is largely overshot by the scale uncertainty; the MC\
+uncertainty, but is largely overshot by the scale uncertainty; the MC
 uncertainty remains comparatively negligible.

### 2020-08-13 paper/app-lumis.tex
Fix pagination

@@
 \label{app:lumis}
-
-In this appendix, we present the complete breakdown of parton luminosities
-entering the NLO QCD+EW predictions of the various measurements
-considered in section~\ref{sec:results}. For each parton luminosity,
-we indicate its percentage contribution to the cross section in a given bin.
-In particular:
-\begin{itemize}
-\item Table~\ref{tab:B1} collects the thirty-five parton luminosities
-  contributing to the Drell--Yan lepton-pair production measured by the
-  ATLAS experiment at a centre-of-mass energy of
-  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}.
-  The thirteen bins are for the invariant mass of the lepton pair,
-  $M_{\ell\bar\ell}$, with edges at 116, 130, 150, 170, 190,
-  210, 230, 250, 300, 400, 500, 700, 1000 and 1500 GeV.
-\item Tables~\ref{tab:B2}-\ref{tab:B7} collect the thirty-five parton
-  luminositites contributing to the double differential Drell--Yan lepton-pair
-  production measured by the CMS experiment at a centre-of-mass energy of
-  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The one hundred and thirty-two
-  bins are split across tables~\ref{tab:B2}-\ref{tab:B7}, where each table
-  corresponds to a bin in the invariant mass of the lepton pair:
-  table~\ref{tab:B2} to  $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$; table~\ref{tab:B3} to  $\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$; table~\ref{tab:B4} to  $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$; table~\ref{tab:B5} to  $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$; table~\ref{tab:B6} to $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$; and table~\ref{tab:B7} to $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$.
-In each table, the bins are in the rapidity of the lepton pair, $0.0<y_{\ell\bar\ell}<2.4$, and each of them has a width of 0.1 (0.2 in the largest invariant mass range).
-\item Table~\ref{tab:B8} collects the thirty-seven parton luminosities
-  contributing to the top-quark pair distributions measured by the ATLAS and
-  CMS experiments at a centre-of-mass energy of
-  \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}.
-  The four distributions, differential in the transverse momentum of the top
-  quark, $p_\mathrm{T}^\mathrm{t}$, in the rapidity of the top quark,
-  $y_\mathrm{t}$, in the invariant mass of the top-quark pair,
-  $m_{\mathrm{t}\bar{\mathrm{t}}}$, and in the rapidity of the top-quark pair,
-  $y_{\mathrm{t}\bar{\mathrm{t}}}$ are shown. The bin edges are, respectively:
-  0, 60, 100, 150, 200, 260, 320, 400, 500~GeV; 0.0, 0.4, 0.8, 1.2, 1.6, 2.5;
-  345, 400, 470, 550, 650, 800, 1100, 1600~GeV;
-  and 0.0, 0.3, 0.6, 0.9, 1.3, 2.5.
-\item Table~\ref{tab:B10} collects the one hundred and sixty-six
-  parton luminosities contributing to the Z $p_{\mathrm{T}}$ distribution
-  measured by the CMS experiment at a centre-of-mass energy of
-  \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. The bin edges are:
-  20, 22, 26, 28, 32, 37, 43, 52, 65, 85, 120, 160, 190, 220, 250, 300,
-  400, 500, 800, 1500~GeV.
-\end{itemize}
 
@@
   \input{tables/TableB2.tex}\\
-  \caption{The 35 parton luminositites contributing to the predictions, accurate
+  \caption{The 35 parton luminosities contributing to the predictions, accurate
     to NLO QCD+EW, of the double differential Drell--Yan lepton pair production
@@
 %-------------------------------------------------------------------------------
+
+In this appendix, we present the complete breakdown of parton luminosities
+entering the NLO QCD+EW predictions of the various measurements
+considered in section~\ref{sec:results}. For each parton luminosity,
+we indicate its percentage contribution to the cross section in a given bin.
+In particular:
+\begin{itemize}
+\item Table~\ref{tab:B1} collects the thirty-five parton luminosities
+  contributing to the Drell--Yan lepton-pair production measured by the
+  ATLAS experiment at a centre-of-mass energy of
+  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}.
+  The thirteen bins are for the invariant mass of the lepton pair,
+  $M_{\ell\bar\ell}$, with edges at 116, 130, 150, 170, 190,
+  210, 230, 250, 300, 400, 500, 700, 1000 and 1500 GeV.
+\item Tables~\ref{tab:B2}--\ref{tab:B7} collect the thirty-five parton
+  luminosities contributing to the double differential Drell--Yan lepton-pair
+  production measured by the CMS experiment at a centre-of-mass energy of
+  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The one hundred and thirty-two
+  bins are split across tables~\ref{tab:B2}--\ref{tab:B7}, where each table
+  corresponds to a bin in the invariant mass of the lepton pair:
+  table~\ref{tab:B2} to  $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$; table~\ref{tab:B3} to  $\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$; table~\ref{tab:B4} to  $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$; table~\ref{tab:B5} to  $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$; table~\ref{tab:B6} to $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$; and table~\ref{tab:B7} to $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$.
+In each table, the bins are in the rapidity of the lepton pair, $0.0<y_{\ell\bar\ell}<2.4$, and each of them has a width of 0.1 (0.2 in the largest invariant mass range).
+\item Table~\ref{tab:B8} collects the thirty-seven parton luminosities
+  contributing to the top-quark pair distributions measured by the ATLAS and
+  CMS experiments at a centre-of-mass energy of
+  \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}.
+  The four distributions, differential in the transverse momentum of the top
+  quark, $p_\mathrm{T}^\mathrm{t}$, in the rapidity of the top quark,
+  $y_\mathrm{t}$, in the invariant mass of the top-quark pair,
+  $m_{\mathrm{t}\bar{\mathrm{t}}}$, and in the rapidity of the top-quark pair,
+  $y_{\mathrm{t}\bar{\mathrm{t}}}$ are shown. The bin edges are, respectively:
+  0, 60, 100, 150, 200, 260, 320, 400, 500~GeV; 0.0, 0.4, 0.8, 1.2, 1.6, 2.5;
+  345, 400, 470, 550, 650, 800, 1100, 1600~GeV;
+  and 0.0, 0.3, 0.6, 0.9, 1.3, 2.5.
+\item Table~\ref{tab:B10} collects the one hundred and sixty-six
+  parton luminosities contributing to the Z $p_{\mathrm{T}}$ distribution
+  measured by the CMS experiment at a centre-of-mass energy of
+  \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. The bin edges are:
+  20, 22, 26, 28, 32, 37, 43, 52, 65, 85, 120, 160, 190, 220, 250, 300,
+  400, 500, 800, 1500~GeV.
+\end{itemize}

### 2020-08-14 paper/sec-results.tex
section 3

@@
 uncertainties, as we will explicitly demonstrate. This is a desirable feature
-to correctly interpret the size of the EW corrections.
+to correctly interpret the size of the EW corrections. An example that
+validates the \textsc{PineAPPL} result in the case of a low-statistic run is
+nevertheless provided in appendix~\ref{app:add_plots}.
 
@@
 perturbative accuracy of the theory (NLO QCD or NLO QCD+EW) or of the scale
-choice.
+choice. As explicitly demonstrated in appendix~\ref{app:add_plots}, the good
+agreement is also independent from the numerical precision of the Monte Carlo
+run.
 
@@
 Overall, the EW corrections suppress the theoretical predictions by about
-\SIrange{2}{7}{\percent} as the transverse momentum of the Z boson increases.
-The size of this shift is usually as large as the data uncertainty, and
-exceeds it at large values of $p_\mathrm{T}^{\ell \bar{\ell}}$. As a consequence,
+\SIrange{2}{10}{\percent} as the transverse momentum of the Z boson increases.
+The size of this shift is as large as the data uncertainty up to
+$p_{\mathrm{T}}^{\ell\bar\ell}\sim \SI{200}{\giga\electronvolt}$, and 
+exceeds it by about \SI{60}{\percent} at larger values of
+$p_\mathrm{T}^{\ell \bar{\ell}}$. As a consequence,
 we anticipate the inclusion of EW corrections to be relevant for an accurate
-fit to this data set.
+fit of this data.
 
-The size of the EW correction is between four and six times larger than the
+The size of the EW correction is between four and tenty times larger than the
 size of the PDF uncertainty: as previously noted in the other cases, this fact
@@
 accuracy of the PDFs. In comparison to the scale uncertainty, the size of the
-EW corrections remains negligible, as NNLO QCD corrections are comparatively
-large, as expected in a process mostly initiated by gluons. They should
-therefore be included along with EW corrections in a fit of PDFs. Finally, the
-Monte Carlo uncertainty is well under control, as it remains mostly negligible
-in comparison to the PDF, scale and data uncertainty, and to the size of the
-EW correction.
+EW corrections remains negligible at small values of $p_{\mathrm{T}}^{\ell\bar\ell}$,
+roughly $p_{\mathrm{T}}^{\ell\bar\ell}\lesssim\SI{400}{\giga\electronvolt}$, while it
+becomes up to four times larger than it in the two bins at the largest value of
+$p_{\mathrm{T}}^{\ell\bar\ell}$. In this kinematic region, NLO EW corrections might
+therefore become even more relevant than NNLO QCD corrections, and should
+therefore be mandatorily included in a fit of PDFs to this data set.
+Finally, the Monte Carlo uncertainty is well under control, as it remains
+mostly negligible in comparison to the PDF, scale and data uncertainty, and to
+the size of the EW correction.

### 2020-08-17 paper/app-addmaterial.tex
section 3
Fix a few grammatical/typographical mistakes

@@
 
-In this appendix, we collect some additional plots, in the same format of those
+In this appendix we collect some additional plots, in the same format of those
 presented in figures~\ref{fig:atlaszhighmass49fb}--\ref{fig:cmsZ13TeV},
@@
 case the factorisation and renormalisation scales are kept equal to
-$H_T/s$, see section~\ref{sec:toppair}.
+$H_\mathrm{T}/4$, see section~\ref{sec:toppair}.
 

### 2020-08-17 paper/app-lumis.tex
Fix a few grammatical/typographical mistakes

@@
     \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The contributions
-    are reported, in percentage, for each of the thirteen bins. The bin edges
+    are reported, in percentage, for each of the 13 bins. The bin edges
     are in the invariant mass of the lepton pair, $M_{\ell\bar\ell}$, as follows:
@@
     \SI{7}{\tera\electronvolt}~\cite{Chatrchyan:2013tia}. The invariant mass
-    bin is $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$; bins 1-24 are in the rapidity of the lepton pair,
+    bin is $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$; bins 1--24 are in the rapidity of the lepton pair,
   $0.0<y_{\ell\bar\ell}<2.4$, and each bin has a width of 0.1.}
@@
     From left to right, top to bottom,
-    predictions are reported for the 8 bins of transverse momentum of the
-    top quark, for the 5 bins of top-quark rapidity, for the 7 bins of
-    top-quark pair invariant mass, and for the 5 bins of top-quark pair
+    predictions are reported for the eight bins of transverse momentum of the
+    top quark, for the five bins of top-quark rapidity, for the seven bins of
+    top-quark pair invariant mass, and for the five bins of top-quark pair
   rapidity, see text for details.}
@@
 \begin{itemize}
-\item Table~\ref{tab:B1} collects the thirty-five parton luminosities
+\item Table~\ref{tab:B1} collects the 35 parton luminosities
   contributing to the Drell--Yan lepton-pair production measured by the
@@
   \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}.
-  The thirteen bins are for the invariant mass of the lepton pair,
+  The 13 bins are for the invariant mass of the lepton pair,
   $M_{\ell\bar\ell}$, with edges at 116, 130, 150, 170, 190,
   210, 230, 250, 300, 400, 500, 700, 1000 and 1500 GeV.
-\item Tables~\ref{tab:B2}--\ref{tab:B7} collect the thirty-five parton
+\item Tables~\ref{tab:B2}--\ref{tab:B7} collect the 35 parton
   luminosities contributing to the double differential Drell--Yan lepton-pair
   production measured by the CMS experiment at a centre-of-mass energy of
-  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The one hundred and thirty-two
+  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The 132
   bins are split across tables~\ref{tab:B2}--\ref{tab:B7}, where each table
@@
 In each table, the bins are in the rapidity of the lepton pair, $0.0<y_{\ell\bar\ell}<2.4$, and each of them has a width of 0.1 (0.2 in the largest invariant mass range).
-\item Table~\ref{tab:B8} collects the thirty-seven parton luminosities
+\item Table~\ref{tab:B8} collects the 37 parton luminosities
   contributing to the top-quark pair distributions measured by the ATLAS and
@@
   and 0.0, 0.3, 0.6, 0.9, 1.3, 2.5.
-\item Table~\ref{tab:B10} collects the one hundred and sixty-six
+\item Table~\ref{tab:B10} collects the 166
   parton luminosities contributing to the Z $p_{\mathrm{T}}$ distribution

### 2020-08-17 paper/app-pineappl.tex
Add missing links to documentation

@@
 The only difference with respect to a standard \textsc{mg5\_aMC} run is the switch \texttt{set iappl 1}, which enables to fill a \textsc{PineAPPL} grid.
-For a complete set of runcards and patches see TODO.
+For a complete set of runcards and patches see \url{https://n3pdf.github.io/pineappl}.
 \begin{verbatim}
@@
 
-% TODO: link to documentation
-
 \definecolor{mygreen}{rgb}{0,0.6,0}
@@
 All \textsc{PineAPPL} functions have the prefix \texttt{pineappl\_}.
-The full example can be found at \url{https://github.com/N3PDF/pineappl/tree/master/examples/capi-dy-aa}.
+The full example can be found at \url{https://github.com/N3PDF/pineappl/tree/master/examples/capi-dy-aa} and the full documentation of the C API can be found at \url{https://docs.rs/pineappl_capi}.
 

### 2020-08-17 paper/sec-conclusion.tex
added references for z+jet and first sentence of conclusions

--- 2020-08-07 paper/sec-conclusion.tex
@@
 \label{sec:conclusion}
-
+The systematic inclusion of EW corrections in collider-physics simulations is crucial when high accuracy is required. Until
+now, it was possible to include these effects only in one of the two ingredients of the physical cross section, namely
+the short-distance (partonic) matrix element. For what concerns the second ingredient, PDFs, they were still extracted including
+only QCD effects. In this paper, we amended to this situation, making it possible to include EW effects also in PDF fits.
 We presented a new tool called \textsc{PineAPPL}, which stores perturbative calculations from an external Monte Carlo in a PDF-independent way using interpolation grids.

### 2020-08-17 paper/sec-results.tex
added references for z+jet and first sentence of conclusions

--- 2020-08-13 paper/sec-results.tex
@@
 
-In this section we demonstrate the capabilities of \textsc{mg5\_aMC}+\textsc{PineAPPL} by
-computing fast-interpolation grids, accurate to NLO QCD and NLO QCD+EW,
+In this section we demonstrate the capabilities of \textsc{PineAPPL} by
+computing fast-in\-ter\-po\-la\-tion grids, accurate to NLO QCD and NLO QCD+EW,
 for a representative set of processes in which EW corrections may have a
 sizeable effect on the accuracy of the theoretical predictions.
-In order to consider some realistic kinematics for these
-processes, we rely on a set of measurements that are commonly included in PDF
+In order to consider realistic kinematics for these
+processes, we rely on the measurements that are commonly included in PDF
 fits. Our aim is twofold. First, we want to validate the results
 obtained with \textsc{PineAPPL}; second, we want to assess the
-impact of the EW corrections for the specific experimental setups. We describe
-the settings employed for the computations, and the corresponding results for
-each process.
+impact of the EW corrections for the specific experimental setups. We start by describing the
+setup employed for the computation, then we discuss the features of each process, along with
+the corresponding results.
 
@@
 (UFO)~\cite{Degrande:2011ua} model {\tt loop\_qcd\_qed\_sm\_Gmu},
-included as standard in {\sc mg5\_aMC}. It contains the UV and $R_2$
+included as standard in {\sc MG5\_aMC}. It contains the UV and $R_2$
 counterterms relevant to NLO QCD and EW corrections, the latter in the
@@
 of any hadronic jet produced in the final state: 
- in particular, photon-induced (PI) contributions are consistently included at LO and NLO.\footnote{We employ the $\overline{G}_\mu$ scheme also for the QED coupling entering vertices involving initial-state photons, see section~4.3.3 of ref.\cite{Denner:2019vbn}.}
+ in particular, PI contributions are consistently included at LO and NLO.\footnote{We employ the $\overline{G}_\mu$ scheme also for the QED coupling entering vertices involving initial-state photons, see section~4.3.3 of ref.\cite{Denner:2019vbn}.}
 We use a PDF set that contains a photon PDF, namely
@@
 The central values of the renormalisation and factorisation scales, $\mu_\mathrm{R}$ and
-$\mu_\mathrm{F}$, are chosen in a process-specific way, as discussed in sec.~\ref{subsec:processes_and_measurements}. In order to estimate the missing higher-order uncertainty,
+$\mu_\mathrm{F}$, are chosen in a process specific way, and are discussed in sec.~\ref{subsec:processes_and_measurements}. In order to estimate the missing higher-order uncertainty,
 we allow the events to be reweighted on-the-fly in the Monte Carlo generation upon scale
-variations, with the technique presented in Ref.~\cite{Frederix:2011ss}. To this purpose, we use the default \textsc{mg5\_aMC}
+variations, with the technique presented in Ref.~\cite{Frederix:2011ss}. To this purpose, we use the default \textsc{MG5\_aMC}
 implementation, whereby the factorisation and renormalisation scales
 are varied down to a factor $1/2$ and up to a factor $2$, and the envelope
-from the nine-point scale variations is constructed,
-see equation~\eqref{eq:9pt}. However, we note that
+from the nine-point scale variations is constructed. However, we note that
 \textsc{PineAPPL} allows the user to determine the envelope with any point
@@
 \begin{equation}
-%\begin{aligned}
-%M_\mathrm{W} &= \SI{80}{\giga\electronvolt} \text{,} \quad &
-M_\mathrm{Z} = \SI{91.176}{\giga\electronvolt} \text{,} \quad 
-m_\mathrm{t} = \SI{172.5}{\giga\electronvolt} \text{,} \quad 
-%\Gamma_\mathrm{W} &= \SI{2.09}{\giga\electronvolt} \text{,} &
-\Gamma_\mathrm{Z} = \SI{2.50}{\giga\electronvolt} \text{,}
-%\end{aligned}
+\begin{aligned}
+M_\mathrm{W} &= \SI{80}{\giga\electronvolt} \text{,} \quad &
+M_\mathrm{Z} &= \SI{91.176}{\giga\electronvolt} \text{,} \quad &
+m_\mathrm{t} &= \SI{172.5}{\giga\electronvolt} \text{,} \quad \\
+\Gamma_\mathrm{W} &= \SI{2.09}{\giga\electronvolt} \text{,} &
+\Gamma_\mathrm{Z} &= \SI{2.50}{\giga\electronvolt} \text{,}
+\end{aligned}
 \label{eq:parameters}
 \end{equation}
-where $M_\mathrm{Z}$ and $m_\mathrm{t}$ are the values of the Z-boson, and
-top-quark masses, respectively, and $\Gamma_\mathrm{Z}$ is the width of
-the Z boson. The value of the strong
+where $M_\mathrm{W}$, $M_\mathrm{Z}$ and $m_\mathrm{t}$ are the values of the W-boson, Z-boson, and
+top quark masses, respectively, and $\Gamma_\mathrm{W}$ and $\Gamma_\mathrm{Z}$ are the width of
+the W boson and of the Z boson, respectively. The value of the strong
 coupling is chosen consistently with the PDF set, $\alphas(M_\mathrm{Z})=0.118$.
-
-The definition of observables and cuts is process-specific, and it follows the corresponding experimental measurements,
-see section~\ref{subsec:processes_and_measurements}.
+The definition of observables and cuts is process-specific, and it follows the corresponding experimental measurements.
 When relevant, final-state photons and massless charged fermions (leptons and light quarks) are recombined together 
@@
 sum of their momenta is assigned to the charged fermion, and the photon is removed
-from the event. Kinematic observables and cuts are defined starting from recombined momenta. If we were interested also in jet-related observables,
+from the event. Kinematics observables and cuts are defined starting from recombined momenta. If we were interested also in jet-related observables,
 photons surviving the recombination would have to be clustered together with coloured
@@
 see refs.~\cite{Frederix:2016ost,Denner:2019zfp}.} Finally, although contributions corresponding to the radiation
-of a heavy boson are formally of the same perturbative order of the EW corrections, they are not included in our
+of a heavy boson are formally of the same perturbative order as the EW corrections, they are not included in our
 computations. In fact, while nothing prevents to include these contributions \emph{a posteriori}, as they are finite,
-their impact is either smaller than the one of \enquote{standard} EW corrections, or anyway negligible with respect to
+their impact is either smaller than the one of ``standard'' EW corrections, or anyway negligible with respect to
 the total cross section (see refs.~\cite{Frixione:2014qaa,Frixione:2015zaa,Pagani:2016caq} for some process-specific cases {\bf MZ OTHERS???}).
@@
 top-quark pair production, and Z-boson (lepton-pair) production with non-zero
-transverse momentum in proton-proton collisions. In the following, we shall
-present the experimental measurements, the process-specific settings, and
-the phenomenological results for each of these processes.
+transverse momentum in proton-proton collisions. For each of these processes,
+we present the experimental measurements, process-specific settings, and phenomenological results.
 
-When presenting the results, for each of the processes and measurements considered, we compute differential
-cross sections for the observables defined in the experimental analyses in two different
-ways: directly, by means of \textsc{mg5\_aMC}, and a posteriori, by convolving
+When presenting the results, for each of the processes and measurements considered, we compute the expectation
+value of the corresponding observable for each kinematic bin in two different
+ways: directly, by means of \textsc{MG5\_aMC}, and a posteriori, by convolving
 the fast-interpolation grid produced by \textsc{PineAPPL} with the PDF set
 specified in section~\ref{subsec:computational_settings}. We
-refer to the first result as the MC result, and to the second as
+will refer to the first result as the MC result, and to the second as
 the \textsc{PineAPPL} result. We repeat the computation for theories accurate
 to NLO QCD and to NLO QCD+EW, respectively. The corresponding orders of the
-strong and EW couplings that we consider are specified for each process. In each case, we determine the
+strong and electroweak couplings that we consider are specified for each process. In each case, we determine the
 PDF uncertainty (coming from the PDF ensemble), the scale uncertainty (coming
@@
 last respect, we consider by default high-statistics computations, whereby we
-require a relative Monte Carlo precision of \SI{0.1}{\permille} on the integrated cross section. While
+require a relative Monte Carlo precision of a fraction of per mille on the total cross section. While
 this choice does not affect the validation of the \textsc{PineAPPL} result
@@
 We present these comparisons in
-figures~\ref{fig:atlaszhighmass49fb}, \ref{fig:cmsdy2d11_bins3456}, \ref{fig:atlastop}, and \ref{fig:cmsZ13TeV}.
+figures~\ref{fig:atlaszhighmass49fb}--\ref{fig:cmsZ13TeV}.
 The format of the plots is the same across all figures. The first panel
@@
 \paragraph{Experimental measurements and process features.}
-We select the single-differential invariant mass distribution of the
+We select the distribution, single-differential in the invariant mass of the
 lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of-mass
@@
 ($M_{\ell\bar\ell}>\SI{116}{\giga\electronvolt}$)~\cite{Aad:2013iua}.
-We also select the single-differential rapidity distribution, $y_{\ell\bar\ell}$, in slices of
-the invariant mass of the lepton pair, $M_{\ell\bar\ell}$,
+We also select the distributions, double-differential in the rapidity and in
+the invariant mass of the lepton pair, $y_{\ell\bar\ell}$ and $M_{\ell\bar\ell}$,
 measured by the CMS experiment at a centre-of-mass energy of
@@
 $\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$ contributions.
-Combined QCD--EW corrections occur only at NNLO, and are therefore not
+Mixed-coupling QCD-EW corrections occur only at NNLO, and are therefore not
 considered here. EW corrections for this process were computed in
@@
 $\mu_\mathrm{R}=\mu_\mathrm{F}=M_{\ell\bar\ell}$, where $M_{\ell\bar\ell}$ is the central value of each
-invariant mass slice, for the CMS one. In the case of ATLAS, we require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$,
+invariant mass bin, for the CMS one. In the case of ATLAS, we require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$,
 $|\eta_\ell|<2.5$ and $\SI{116}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the transverse
@@
 lepton pair, respectively. Conversely, in the case of CMS, we require $p_\mathrm{T}^{\ell_1}>\SI{14}{\giga\electronvolt}$, $p_\mathrm{T}^{\ell_2}>\SI{9}{\giga\electronvolt}$,
-$|\eta_\ell|<2.4$, $|y_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$
+$|\eta_\ell|<2.4$, $|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$
 for the transverse momentum and the pseudorapidity of each lepton, and for the
-rapidity and the invariant mass of the lepton pair.
+pseudorapidity and the invariant mass of the lepton pair.
 
 \paragraph{Numerical results.}
-We first consider the single-differential measurement of a lepton-pair
-for large invariant masses performed by the ATLAS experiment at \SI{7}{\tera\electronvolt}.
+We first consider the single-differential measurement at a high lepton-pair
+invariant mass performed by the ATLAS experiment at \SI{7}{\tera\electronvolt}.
 From figure~\ref{fig:atlaszhighmass49fb} we immediately
 observe that the validation of the \textsc{PineAPPL} result against the MC
-result is successful. The relative difference between the two is of the order of
+result is successful. The relative difference between the two is of the order
 \SI{0.1}{\permille} at most, with negligible fluctuations across different
@@
 The measurement is mainly driven by $\mathrm{q}\bar{\mathrm{q}}$ scattering: specifically, the
-leading (next-to-leading) contribution comes from a $\mathrm{u}\bar{\mathrm{u}}$/$\mathrm{c}\bar{\mathrm{c}}$ ($\mathrm{d}\bar{\mathrm{d}}$/$\mathrm{s}\bar{\mathrm{s}}$)
+leading (next-to-leading) contribution comes from a $\mathrm{u}\bar{\mathrm{u}}$ ($\mathrm{d}\bar{\mathrm{d}}$)
 parton luminosity, which accounts for about \SI{55}{\percent} (\SI{49}{\percent}) of the cross section
@@
 The PI contribution raises from about \SI{1.3}{\percent} in the lowest bin to
-about \SI{3.6}{\percent} in the highest bin.\footnote{For the \texttt{MRST2004qed} PDF set~\cite{Martin:2004dh}, which is used to subtract PI contributions (see section~\ref{sec:doublecounting}), the value in the highest bin is roughly twice as large, \SI{6.9}{\percent} (also in absolute numbers).}
-Overall, the EW corrections range between \SI{5}{\percent}
+about \SI{3.6}{\percent} in the highest bin. Overall, the EW corrections range between \SI{5}{\percent}
 around $M_{\ell\bar\ell}\sim \SI{150}{\giga\electronvolt}$, \SIrange{2}{3}{\percent} for intermediate invariant mass
@@
 always larger, especially at the boundaries of the distribution. This fact
-suggests that, once included in a global fit, EW corrections will make PDFs
-more accurate. In comparison to the scale
+suggests that, once included in a global fit, EW corrections could recast the
+relative weight of each data set included in the fit, and possibly lead to
+an improvement in their overall description. In comparison to the scale
 uncertainty, the size of the EW correction is similar, except for the four bins
 at the largest invariant mass, where the latter is significantly larger than
-the former. This fact suggests that the NNLO QCD correction is comparable
+the former. The size of the scale variation is the same for the QCD and the
+QCD+EW theories. These facts suggest that the NNLO QCD correction is comparable
 to the NLO QCD+EW correction, except at very large values of the invariant mass,
@@
 include the EW corrections in order to obtain an accurate description of the
-large invariant mass bins. Finally, the Monte Carlo 
+large invariant mass bins. Finally, the Monte Carlo statistical
 uncertainty remains negligible in comparison to the data, PDF and scale
 uncertainties, and to the size of the EW correction. Our conclusions should
-therefore not be affected by a generation of too few Monte Carlo events.
+therefore not be affected by a too low number of Monte Carlo events generated.
 
@@
       centre-of-mass energy of \SI{7}{\tera\electronvolt}~\cite{Chatrchyan:2013tia}. Displayed are
-      only four of the six invariant mass bins available, respectively below the
+      only two of the six invariant mass bins available, respectively below the
       Z-boson mass peak, $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$, on the Z-boson mass
@@
 mass bin comes from
-the $\mathrm{u}\bar{\mathrm{u}}$/$\mathrm{c}\bar{\mathrm{c}}$ ($\mathrm{d}\bar{\mathrm{d}}$/$\mathrm{s}\bar{\mathrm{s}}$) parton luminosity, which accounts for about \SI{70}{\percent}
+the $\mathrm{u}\bar{\mathrm{u}}$ ($\mathrm{d}\bar{\mathrm{d}}$) parton luminosity, which accounts for about \SI{70}{\percent}
 (\SI{22}{\percent}) of the double differential cross section, with small fluctuations across
@@
 different in the $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$ invariant mass bin, where the
-leading (next-to-leading) contribution comes instead from the $\mathrm{d}\bar{\mathrm{d}}$/$\mathrm{s}\bar{\mathrm{s}}$
-($\mathrm{u}\bar{\mathrm{u}}$/$\mathrm{c}\bar{\mathrm{c}}$) parton luminosity, which accounts for about \SI{60}{\percent} (\SI{44}{\percent}) of the
+leading (next-to-leading) contribution comes instead from the $\mathrm{d}\bar{\mathrm{d}}$
+($\mathrm{u}\bar{\mathrm{u}}$) parton luminosity, which accounts for about \SI{60}{\percent} (\SI{44}{\percent}) of the
 double differential cross section at small rapidities, and for about \SI{56}{\percent} (\SI{50}{\percent})
 at large rapidities. In the remaining two invariant mass bins, the leading
-(next-to-leading) contribution comes again from the $\mathrm{u}\bar{\mathrm{u}}$/$\mathrm{c}\bar{\mathrm{c}}$ ($\mathrm{d}\bar{\mathrm{d}}$/$\mathrm{s}\bar{\mathrm{s}}$)
+(next-to-leading) contribution comes again from the $\mathrm{u}\bar{\mathrm{u}}$ ($\mathrm{d}\bar{\mathrm{d}}$)
 parton luminosity, which accounts for about \SIrange{69}{95}{\percent} (\SIrange{38}{30}{\percent}) and
@@
 $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$ and $\SI{200}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ in the
-corresponding rapidity intervals; PI contributions range between \SIrange{3.7}{0.6}{\percent}
-and \SIrange{7.3}{1.6}{\percent} in the two invariant mass bins, respectively, for increasing
+corresponding rapidity intervals; PI contributions range between \SIrange{7.3}{1.2}{\percent}
+and \SIrange{3.7}{0.6}{\percent} in the two invariant mass bins, respectively, for increasing
 rapidity.
@@
 However, as already observed in the case of the ATLAS measurement, should EW
-corrections be included in a fit of PDFs, the latter are likely to become more
+corrections be included in a fit of PDFs, these are likely to become more
 accurate: even though the apparent description of the data will not
-improve, by including the more precisely predicted bins in the low invariant mass range, PDFs
+improve, including of the precise bins in the low invariant mass range, PDFs
 will resemble more closely the underlying truth. Furthermore, the kinematic cut
@@
 mass peak, $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$, where the scale uncertainty exceeds
-the size of the EW correction by about a factor of five. This is due to the choice
-of invariant mass window around the Z peak, in which positive and negative EW corrections almost cancel.
-Finally, the Monte Carlo uncertainty remains negligible
+the size of the EW correction by about a factor of five. These facts confirm,
+as expected, that EW corrections are almost immaterial at the Z-boson mass
+peak, but that NNLO QCD corrections are otherwise as relevant as NLO QCD+EW
+corrections. Finally, the Monte Carlo statistical uncertainty remains negligible
 in comparison to the data, PDF and scale uncertainties, and to the size of the
-EW correction, except for a couple of bins at forward/backward rapidity in the highest
+EW correction, except for a couple of bins at forward rapidity in the highest
 invariant mass bins. Improving the Monte Carlo precision will require to
@@
 \subsubsection{Top-quark pair production.}
-\label{sec:toppair}
-
 \paragraph{Experimental measurements and process features.}
-We select the single-differential distribution in either the transverse
+We select the distributions, single-differential in either the transverse
 momentum of the top quark, $p_\mathrm{T}^\mathrm{t}$, or the invariant mass of the top-quark
@@
 pure QCD contributions at LO, $\mathcal{O}(\alphas^2)$, and
-at NLO, $\mathcal{O}(\alphas^3)$. These orders make up our NLO QCD
+at NLO, $\mathcal{O}(\alphas^3)$. They make up our NLO QCD
 computation. The NLO QCD+EW computation includes the $\mathcal{O}(\alphas^2)$
@@
 \paragraph{Process-specific settings.}
-We employ the following functional form for the renormalisation and factorisation scales;
+We employ the following functional form for the renormalisation and factorisation scales
 $\mu_\mathrm{R}=\mu_\mathrm{F}=\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^\mathrm{t})^2}{\Big /}2$ for the distribution differential
@@
 transverse momentum of the top quark (the invariant mass of the top-quark pair)
-increases; the largest PI contribution for this process comes from $\gamma\mathrm{g}$ scattering,
+increases; the largest PI contribution for this process is $\gamma\mathrm{g}$ scattering,
 which accounts for about \SIrange{0.5}{1}{\percent} (\SIrange{0.5}{0.7}{\percent}) of the cross
@@
 likely to be easily accommodated by the large data uncertainty, should the data
-be fitted with the inclusion of EW corrections.
+be fitted with the inclusion of EW corrections; PDFs will possibly not become
+more precise.
 
@@
 \subsubsection{Z-boson production with non-zero transverse momentum.}
-\label{sec:Zpt}
 
 \paragraph{Experimental measurements and process features.}
-We select the single-differential transverse momentum distribution of the
-sum of the two leptons (the \enquote{Z boson}), $p_\mathrm{T}^{\ell \bar{\ell}}$, measured by the CMS experiment at a
-centre-of-mass energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}.
-This measurement, which has not been included in any PDF determination so far,
-shows very low experimental uncertainties (at the percent level or below).
-EW corrections are therefore expected to be essential to achieve a good
-description of it, and to constrain accurately the PDFs, together with
-NNLO QCD corrections, which are already well
-known~\cite{Gehrmann-DeRidder:2017mvr,Bizon:2019zgf}
-{\bf MZ there are at least 5-6 other papers both
-  by the Zurich group and the Argonne one, but on Z+jet rather than
-  Z-pt predictions. Should we cite them?}
-Analogous measurements,
+We select the distribution, single-differential in the transverse momentum of
+the Z boson, $p_\mathrm{T}^\mathrm{Z}$, measured by the CMS experiment at a centre-of-mass
+energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. While this measurement is not
+included in any PDF determination, its expected impact on parton densities has been studied in 
+ref.~\cite{Boughezal:2017nla}. Since this process shows very low experimental uncertainties (at the percent level or below), and is
+known to an excellent degree as far as QCD corrections are concerned~\cite{Boughezal:2015ded,Boughezal:2016isb,Boughezal:2016yfp,Ridder:2015dxa,Ridder:2016nkl,Gehrmann-DeRidder:2017mvr,Bizon:2019zgf}
+EW corrections are expected to be essential in order to achieve a good
+description of it, and to constrain accurately the PDFs. Analogous measurements,
 from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
-experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt},
-were partly included (upon
+experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt}, were partly included (upon
 selection of an appropriate kinematic cut that excluded bins with large EW
-corrections) in a dedicated study~\cite{Boughezal:2017nla},
-in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
+corrections) in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
 the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
@@
 contribution $\mathcal{O}(\alphas^2\alpha^2)$. In the NLO QCD+EW computation,
-we supplement these with another LO and NLO, which are
-$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alphas\alpha^3)$;
-contributions of the order $\mathcal{O}(\alpha^4)$ are not considered (see ref.~\cite{Denner:2019zfp}).
-EW corrections for this process were computed in
+we supplement these with the LO and NLO EW corrections,
+$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alpha^4)$, and with the NLO
+QCD-EW mixed-coupling correction, $\mathcal{O}(\alphas\alpha^3)$. EW corrections for
+this process were computed in
 refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
 The process receives contributions from 101 (166) parton luminosities,
-see appendix~\ref{app:lumis}.
+see appendix~\ref{app:lumis} for details.
 
@@
 
-As in the case of Drell-Yan, we use a fixed value for the renormalisation and
-factorisation scales $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$, where
-$M_\mathrm{Z}$ is the Z-boson mass. Consistently with the
-experimental analysis, we require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$,
-$|\eta_\ell|<2.4$, $|M_{\ell\bar\ell} - M_\mathrm{Z}| < \SI{15}{\giga\electronvolt}$,
-$|y_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<p_\mathrm{T}^{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the
-transverse momentum and pseudorapidity of each lepton, and for the invariant
-mass, pseudorapidity and transverse momentum of the lepton pair.
-We finally discard all bins with
-$p_\mathrm{T}^{\ell \bar{\ell}}<\SI{20}{\giga\electronvolt}$ to avoid a kinematic
-region where resummation effects are sizeable.
+As in the case of Drell-Yan, we use a fixed value for the renormalisation and factorisation 
+scales $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$.
+We require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$, $|\eta_\ell|<2.4$,
+$M_\mathrm{Z}-\SI{15}{\giga\electronvolt}<M_{\ell\bar\ell}<M_\mathrm{Z}+\SI{20}{\giga\electronvolt}$,
+$|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<p_\mathrm{T}^{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the
+transverse momentum and pseudorapidity of each lepton, and for the invariant mass,
+pseudorapidity and transverse momentum of the lepton pair. Imposing a minimum cut for the transverse momentum of the lepton pair 
+is necessary as we stick to a fixed-order computation, without including resummation effects.
 
-\paragraph{Numerical results.} In figure~\ref{fig:cmsZ13TeV} we report the
-distribution differential in the transverse momentum of the Z
-boson. Also in this case, the \textsc{PineAPPL} result is well validated, as it
-differs from the MC result by $\SI{0.5}{\permille}$ at most. The accuracy of the
-theory or the choice of scale do not alter this conclusion.
+\paragraph{Numerical results.} We finally
 
@@
 %-------------------------------------------------------------------------------
-
-The process receives its leading contribution from $\mathrm{qg}$- and
-$\bar{\mathrm{q}}\mathrm{g}$-initiated channels, which account for about \SI{65}{\percent}
-of the cross section, with some variations in the relative contributions from
-individual quark and antiquark flavours as the transverse momentum of the
-Z boson varies; the PI contribution always remain negligible.
-Overall, the EW corrections suppress the theoretical predictions by about
-\SIrange{2}{7}{\percent} as the transverse momentum of the Z boson increases.
-The size of this shift is usually as large as the data uncertainty, and
-exceeds it at large values of $p_\mathrm{T}^{\ell \bar{\ell}}$. As a consequence,
-we anticipate the inclusion of EW corrections to be relevant for an accurate
-fit to this data set.
-
-The size of the EW correction is between four and six times larger than the
-size of the PDF uncertainty: as previously noted in the other cases, this fact
-suggests that, once included in a PDF fit, EW corrections can improve the
-accuracy of the PDFs. In comparison to the scale uncertainty, the size of the
-EW corrections remains negligible, as NNLO QCD corrections are comparatively
-large, as expected in a process mostly initiated by gluons. They should
-therefore be included along with EW corrections in a fit of PDFs. Finally, the
-Monte Carlo uncertainty is well under control, as it remains mostly negligible
-in comparison to the PDF, scale and data uncertainty, and to the size of the
-EW correction.

### 2020-08-17 paper/sec-conclusion.tex

--- 2020-08-10 paper/sec-conclusion.tex
@@
 \label{sec:conclusion}
-{\bf MZ I would like to have some sort of introduction here (a short bla bla on precision), before turning to Pineappl}
-
+The systematic inclusion of EW corrections in collider-physics simulations is crucial when high accuracy is required. Until
+now, it was possible to include these effects only in one of the two ingredients of the physical cross section, namely
+the short-distance (partonic) matrix element. For what concerns the second ingredient, PDFs, they were still extracted including
+only QCD effects. In this paper, we amended to this situation, making it possible to include EW effects also in PDF fits.
 We presented a new tool called \textsc{PineAPPL}, which stores perturbative calculations from an external Monte Carlo in a PDF-independent way using interpolation grids.

### 2020-08-17 paper/sec-results.tex

--- 2020-08-14 paper/sec-results.tex
@@
 NNLO QCD corrections, which are already well
-known~\cite{Gehrmann-DeRidder:2017mvr,Bizon:2019zgf}
-{\bf MZ there are at least 5-6 other papers both
-  by the Zurich group and the Argonne one, but on Z+jet rather than
-  Z-pt predictions. Should we cite them?}
+known~\cite{Boughezal:2015ded,Boughezal:2016isb,Boughezal:2016yfp,Ridder:2015dxa,Ridder:2016nkl,Gehrmann-DeRidder:2017mvr,Bizon:2019zgf}
 Analogous measurements,

### 2020-08-17 paper/sec-results.tex
tenty->twenty

--- 2020-08-14 paper/sec-results.tex
@@
 
-The size of the EW correction is between four and tenty times larger than the
+The size of the EW correction is between four and twenty times larger than the
 size of the PDF uncertainty: as previously noted in the other cases, this fact

### 2020-08-17 paper/sec-doublecounting.tex
General revision
Discuss the size of subtractions

@@
 to note that one can tune the QED parton shower to mimic NLO EW effects for specific processes and observables, so that a prediction only accurate at NLO
-QCD displays a remarkable agreement with another at NLO QCD+EW when the photonic shower is included (see for example the behaviour of predictions showered with
-\textsc{Photos}~\cite{Barberio:1990ms,Barberio:1993qi,Golonka:2005pn} in ref.~\cite{CarloniCalame:2016ouw}). However, this kind of agreement
+QCD displays a remarkable agreement with another at NLO QCD+EW when the photonic shower is included.
+Indeed, for the ATLAS DY measurement discussed in section~\ref{sec:dy-lepton-pair-production} the difference of the two datasets with and without shower subtractions closely resemble the size of full NLO EW effects over the entire mass range.
+%(see also the behaviour of predictions showered with
+%\textsc{Photos}~\cite{Barberio:1990ms,Barberio:1993qi,Golonka:2005pn} in ref.~\cite{CarloniCalame:2016ouw}).
+However, this kind of agreement
 always comes \emph{a posteriori}, and cannot be ensured in general.
+The transverse momentum of the Z boson as shown in section~\ref{sec:Zpt} is such an example: the difference between the two datasets is rather small (less than \SI{6}{\percent}), but the NLO EW corrections are as large as \SI{25}{\percent}.
 Furthermore, the deconvolution of QED effects in data introduces a dependence on the program (and possibly on 
@@
 and bare ones, while refs.~\cite{Sirunyan:2019bzr} employs a dressed-lepton definition. We therefore recommend that these ways of presenting the experimental
-data becomes standard in the future.
+data become standard in the future.

### 2020-08-17 paper/sec-doublecounting.tex
Remove wrong statement

--- 2020-08-13 paper/sec-doublecounting.tex
@@
 to note that one can tune the QED parton shower to mimic NLO EW effects for specific processes and observables, so that a prediction only accurate at NLO
-QCD displays a remarkable agreement with another at NLO QCD+EW when the photonic shower is included (see for example the behaviour of predictions showered with
-\textsc{Photos}~\cite{Barberio:1990ms,Barberio:1993qi,Golonka:2005pn} in ref.~\cite{CarloniCalame:2016ouw}). However, this kind of agreement
+QCD displays a remarkable agreement with another at NLO QCD+EW when the photonic shower is included (see also the behaviour of predictions showered with
+\textsc{Photos}~\cite{Barberio:1990ms,Barberio:1993qi,Golonka:2005pn} in ref.~\cite{CarloniCalame:2016ouw}).
+However, this kind of agreement
 always comes \emph{a posteriori}, and cannot be ensured in general.
+The transverse momentum of the Z boson as shown in section~\ref{sec:Zpt} is such an example: the difference between the two datasets is rather small (less than \SI{6}{\percent}), but the NLO EW corrections are as large as \SI{25}{\percent}.
 Furthermore, the deconvolution of QED effects in data introduces a dependence on the program (and possibly on 

### 2020-08-17 paper/sec-pineappl.tex
Remove two TODOs
few changes

@@
 This number is process dependent and is usually determined by the number of external particles.
-For many processes there is only one LO, but when a process has multiple quark lines, colourless (photons, \dots) and coloured particles (gluons, \ldots) can be exchanged between them, making it possible to have more than one LO.
-An important example at the LHC is (on-shell) top-pair production, which has three different LOs: $\mathcal{O} (\alpha^2)$, $\mathcal{O} (\alphas \alpha)$, and $\mathcal{O} (\alpha^2)$.
-Each LO receives a higher-order correction with an additional power of $\alphas$ or $\alpha$, which in general leads to at least two next-to-leading order (NLO) corrections.
+For many processes there is only one contribution at LO (in terms of $k$ and $l$), but this is not true in general.
+Indeed, when a process has multiple quark lines, colourless (photons, \dots) and coloured particles (gluons, \ldots) can be exchanged between them, making it possible to have more than one combinations of $\alphas$ and $\alpha$.
+A typical example at the LHC is (on-shell) top-pair production, which has three different contributions at LO: $\mathcal{O} (\alpha^2)$, $\mathcal{O} (\alphas \alpha)$, and $\mathcal{O} (\alpha^2)$.
+Each contribution receives a higher-order correction with an additional power of $\alphas$ or $\alpha$, which in general leads to at least two next-to-leading order (NLO) corrections.
 The correction with the largest power in $\alphas$ can be unambiguously called \enquote{the} QCD correction, and the one with the largest power in $\alpha$ \enquote{the} EW correction.
@@
 section at LO, NLO QCD and NLO QCD+EW accuracy.
-%Sometimes there are higher orders that cannot directly be understood as a correction to a LO, e.g.\ $\mathrm{p} \mathrm{p} \to \ell \bar{\ell} + \mathrm{jet} + X$, which has one LO, $\mathcal{O} (\alphas \alpha^2)$, but three NLOs, one of which is $\mathcal{O} (\alpha^4)$~TODO.
 
@@
 This includes the photon--photon initial state, which appears already at LO.
-In the corresponding Feynman diagrams all particles are colourless, so that the photon--photon initiated contributions only receive EW and combined QCD--EW corrections, but never (pure) QCD corrections.
+In the corresponding Feynman diagrams all particles are colourless, so that the photon--photon initiated contributions only receive EW corrections.
 The EW corrections also introduce quark--photon contributions, in analogy of QCD corrections introducing quark--gluon contributions.
@@
 using $y_\text{min} = y(x_\text{max})$ and $y_\text{max} = y(x_\text{min})$ and the grid spacing $\Delta y = (y_\text{max} - y_\text{min})/(N_y-1)$, so that the integer part of $u(y)$ gives the grid index, e.g.\ $u(y_\text{min}) = 0$ and $u(y_\text{max}) = N_y - 1$, and the fractional part gives the location between the nearest grid points.
-
-% TODO: explain how convolutions are performed

### 2020-08-17 paper/sec-results.tex
few changes

@@
 their impact is either smaller than the one of \enquote{standard} EW corrections, or anyway negligible with respect to
-the total cross section (see refs.~\cite{Frixione:2014qaa,Frixione:2015zaa,Pagani:2016caq} for some process-specific cases {\bf MZ OTHERS???}).
+the total cross section (see refs.~\cite{Frixione:2014qaa,Frixione:2015zaa,Pagani:2016caq} for some process-specific cases).
 
@@
 considered here. EW corrections for this process were computed in
-refs.~\cite{Baur:2001ze,Dittmaier:2009cr}. The process receives contributions
+refs.~\cite{Baur:2001ze,Dittmaier:2009cr,Frederix:2018nkq}. The process receives contributions
 from 13 (35) parton luminosities at NLO QCD (NLO QCD+EW),
@@
 shift in the predictions induced by the more accurate NLO QCD+EW theory is
-likely to be easily accommodated by the large data uncertainty.
+likely to be easily accommodated by the large data uncertainty {\bf MZ: may not be so with the RunII data, perhaps
+a comment is worth here..}.
 
@@
 EW corrections for this process
-were computed in refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}.
+were computed in refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Frederix:2018nkq,Czakon:2019bcq,Czakon:2019txp}.
 The process receives contributions from
@@
 EW corrections for this process were computed in
-refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
+refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum,Frederix:2018nkq}.
 The process receives contributions from 101 (166) parton luminosities,

### 2020-08-17 paper/sec-results.tex
Addressed MZ comment on DY data

@@
 shift in the predictions induced by the more accurate NLO QCD+EW theory is
-likely to be easily accommodated by the large data uncertainty {\bf MZ: may not be so with the RunII data, perhaps
-a comment is worth here..}.
+likely to be easily accommodated by the large data uncertainty. As the data
+will become more precise, in particular thanks to the increased Run-II LHC
+luminosity, this conclusion might not continue to hold.
 

### 2020-08-17 paper/sec-results.tex
added description of mg5amc

@@
 the settings employed for the computations, and the corresponding results for
-each process.
+each process. We remind the reader that \textsc{mg5\_aMC} makes it possible
+to compute predictions including NLO QCD and EW corrections for arbitrary processes
+in an automated manner. It employs the FKS subtraction scheme~\cite{Frixione:1995ms,Frixione:1997np}
+as automated in \textsc{MadFKS}~\cite{Frederix:2009yq,Frederix:2016rdc} to deal with IR singularities. One-loop
+amplitudes are computed by \textsc{MadLoop}~\cite{Hirschi:2011pa}, which employs different
+numerical techniques~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn,Ossola:2006us,Cascioli:2011va,Mastrolia:2012bu} implemented in the corresponding computer libraries~\cite{Ossola:2007ax,Peraro:2014cba,Hirschi:2016mdz,Denner:2016kdg}.
+Matching
+with parton showers is available only for pure-QCD corrections via the MC@NLO method~\cite{Frixione:2002ik}, and 
+will not be employed in the following.
 

### 2020-08-20 paper/sec-results.tex
two comments of stefan's addressed

@@
 shift in the predictions induced by the more accurate NLO QCD+EW theory is
-likely to be easily accommodated by the large data uncertainty. As the data
+likely to be easily accommodated by the large data uncertainty. However, 
+this conclusion might not continue to hold: first, data
 will become more precise, in particular thanks to the increased Run-II LHC
-luminosity, this conclusion might not continue to hold.
+luminosity. Second, both EW corrections and PI contributions are expected to
+grow larger at \SI{13}{\tera\electronvolt}, making their impact more relevant.
 
@@
 $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$ region, they enhance the value of the cross
-section by about \SI{11}{\percent} across all the rapidity range; in the
-$\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$ region, they suppress the value of the cross
+section by about \SI{11}{\percent} across all the rapidity range. This is mostly due to photon-radiation effects
+on events with $M_{\ell\bar\ell}\simeq M_\mathrm{Z}$ at the Born, for which the invariant mass is shifted to lower 
+values. In the 
+$\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$ region, EW corrections suppress the value of the cross
 section by about \SI{2}{\percent}, again across all the rapidity range; in the

### 2020-08-20 paper/sec-results.tex
some cites added

@@
 photons surviving the recombination would have to be clustered together with coloured
-partons.\footnote{For issues related to the definition of jets in presence of EW corrections,
-see refs.~\cite{Frederix:2016ost,Denner:2019zfp}.} Finally, although contributions corresponding to the radiation
+partons.\footnote{For issues related to the definition of jets in presence of EW corrections, in particular
+    about the fragmentation of partons into photons and vice-versa,
+see refs.~\cite{Glover:1993xc,Frederix:2016ost,Denner:2019zfp}.} Finally, although contributions corresponding to the radiation
 of a heavy boson are formally of the same perturbative order of the EW corrections, they are not included in our
@@
 considered here. EW corrections for this process were computed in
-refs.~\cite{Baur:2001ze,Dittmaier:2009cr,Frederix:2018nkq}. The process receives contributions
+refs.~\cite{Baur:2001ze,Arbuzov:2007db,Dittmaier:2009cr,Frederix:2018nkq}. The process receives contributions
 from 13 (35) parton luminosities at NLO QCD (NLO QCD+EW),
@@
 at the largest invariant mass, where the latter is significantly larger than
-the former. This fact suggests that the NNLO QCD correction is comparable
-to the NLO QCD+EW correction, except at very large values of the invariant mass,
+the former. This fact suggests that the impact of NNLO QCD corrections~\cite{Anastasiou:2003yy,Catani:2009sm,Gavin:2010az,Li:2012wna,Boughezal:2016wmq} is comparable
+to the one of NLO QCD+EW, except at very large values of the invariant mass,
 where the EW correction still dominates. This result stresses the need to

### 2020-08-21 paper/app-pineappl.tex
Improve PineAPPL appendix
- move installation appendix towards the end
- include complete code example

@@
 
-\subsection{Installation}
-\label{app:installation}
-
-\textsc{PineAPPL} currently consists of three parts: 1) the library itself, which is a dependency for the other parts, 2) the helper program \texttt{pineappl}, which allows one to read \textsc{PineAPPL} grids from the command line and make predictions with it, and finally 3) the C interface, which is intended to be used in Monte Carlo integrators to generate the grids.
-
-\subsubsection*{Installation of Rust}
-
-\lstset{
-  basicstyle=\ttfamily\small,
-  showstringspaces=false,
-  commentstyle=\color{red},
-  keywordstyle=\color{blue},
-}
-
-All parts are written in Rust: a Rust compiler and related tools are needed.
-On operating systems with a \texttt{bash} shell (such as Linux or MacOS) the installation is as simple as
-\begin{verbatim}
- $ curl --proto '=https' --tlsv1.2 -sSf https://sh.rustup.rs | sh
-\end{verbatim}
-which downloads the compiler \texttt{rustc}, the package manager \texttt{cargo}, and a few other helpful tools.
-When the installation has completed make sure to read and follow the instructions printed on screen.
-See also \url{https://www.rust-lang.org/tools/install} for more details and for installation instructions for other operating systems.
-
-\subsubsection*{Installation of the command-line program \texorpdfstring{\texttt{pineappl}}{pineappl}}
-
-The command-line program \texttt{pineappl} is compiled and installed using
-\begin{verbatim}
- $ cargo install pineappl_cli
-\end{verbatim}
-This program also needs \texttt{LHAPDF} \cite{Buckley:2014ana} installed; make sure that the environment variables \texttt{PATH}, \texttt{LD\_LIBRARY\_PATH}, and \texttt{PKG\_CONFIG\_PATH} are properly set.
-For usage instructions simply type \texttt{pineappl} in your shell and read the help message.
-
-\subsubsection*{Installation of the C-language interface (optional)}
-
-For the C interface you need to first install \texttt{cargo-c},
-\begin{verbatim}
- $ cargo install cargo-c
-\end{verbatim}
-and then download the \textsc{PineAPPL} repository, compile and finally install into it into a directory \texttt{\$prefix} as follows:
-\begin{verbatim}
- $ git clone https://github.com/N3PDF/pineappl/
- $ cd pineappl_capi/
- $ cargo cinstall --release --prefix=DIRECTORY
-\end{verbatim}
-The last line will install the C header \texttt{pineappl\_capi.h}, the library, and a pkg-config\footnote{A standard way on Linux to express how dependencies are compiled/linked against, see \url{https://www.freedesktop.org/wiki/Software/pkg-config/}} file (\texttt{pineappl\_capi.pc}) into the directory specified as \texttt{DIRECTORY}.
-Make sure that the environment variables \texttt{PATH}, \texttt{LD\_LIBRARY\_PATH}, and \texttt{PKG\_CONFIG\_PATH} are properly set.
-The latter is needed for \texttt{pkg-config -{}-cflags -{}-libs pineappl\_capi} to work, which prints the necessary compiler/linker flags.
-
-After being installed, one can compile and link against the library.
-See appendix~\ref{app:example-program} for an example.
-Updated installation instructions are kept in the file \texttt{README.md} in \textsc{PineAPPL}'s repository at \url{https://github.com/N3PDF/pineappl/}.
+\textsc{PineAPPL} currently consists of three parts: 1) the library itself, which is a dependency for the other parts, 2) the helper program \texttt{pineappl}, which allows one to read \textsc{PineAPPL} grids from the command line and make predictions with it (explained in section~\ref{app:pineappl-demo}), and finally 3) the C interface, which is intended to be used in Monte Carlo integrators to generate the grids.
 
@@
  $ pineappl
-pineappl 0.2.0
+pineappl 0.3.0
 Read, write, and query PineAPPL grids
@@
 id    entry
---+------------+------------+------------
+--+------------+------------
 0  1 × ( 2, -2) 1 × ( 4, -4)
@@
 The factors \texttt{1} are not important here, but in general they can contain CKM values and charge factors that, if kept in the squared matrix elements, would not allow for sharing a single matrix element for different quark flavours and therefore slow down the calculation.
-A complete list of the most important channels and of their
-contribution to the cross section for all of the processes discussed in
-section~\ref{sec:results} is collected in appendix~\ref{app:lumis}.
+A complete list of all channels and of their contribution to the cross section for all of the processes discussed in section~\ref{sec:results} is collected in appendix~\ref{app:lumis}.
 
@@
 
-\subsection{Example Monte Carlo program}
+\subsection{Example Monte Carlo program in C++}
 \label{app:example-program}
@@
 All \textsc{PineAPPL} functions have the prefix \texttt{pineappl\_}.
-The full example can be found at \url{https://github.com/N3PDF/pineappl/tree/master/examples/capi-dy-aa} and the full documentation of the C API can be found at \url{https://docs.rs/pineappl_capi}.
+The full example together with a makefile can be found at \url{https://github.com/N3PDF/pineappl/tree/master/examples/capi-dy-aa}.
+The documentation of the C API can be found at \url{https://docs.rs/pineappl_capi}.
 
 \begin{lstlisting}[language=C++,mathescape=true]
+#include <pineappl_capi.h>
+#include <LHAPDF/LHAPDF.h>
+
+#include <cmath>
+#include <cstddef>
+#include <cstdio>
+#include <random>
+#include <vector>
+
+double int_photo(double s, double t, double u) {
+    double alpha0 = 1.0 / 137.03599911;
+    return alpha0 * alpha0 / 2.0 / s * (t / u + u / t);
+}
+
+struct Psp2to2 {
+    double s;
+    double t;
+    double u;
+    double x1;
+    double x2;
+    double jacobian;
+};
+
+Psp2to2 hadronic_pspgen(std::mt19937& rng, double mmin, double mmax) {
+    using std::acos;
+    using std::log;
+    using std::pow;
+
+    double smin = mmin * mmin;
+    double smax = mmax * mmax;
+
+    double r1 = std::generate_canonical<double, 53>(rng);
+    double r2 = std::generate_canonical<double, 53>(rng);
+    double r3 = std::generate_canonical<double, 53>(rng);
+
+    double tau0 = smin / smax;
+    double tau = pow(tau0, r1);
+    double y = pow(tau, 1.0 - r2);
+    double x1 = y;
+    double x2 = tau / y;
+    double s = tau * smax;
+
+    double jacobian = tau * log(tau0) * log(tau0) * r1;
+
+    // theta integration (in the CMS)
+    double  cos_theta = 2.0 * r3 - 1.0;
+    jacobian *= 2.0;
+
+    double  t = -0.5 * s * (1.0 - cos_theta);
+    double  u = -0.5 * s * (1.0 + cos_theta);
+
+    // phi integration
+    jacobian *= 2.0 * acos(-1.0);
+
+    return { s, t, u, x1, x2, jacobian };
+}
+
+void fill_grid(pineappl_grid* grid, std::size_t calls) {
+    using std::acosh;
+    using std::fabs;
+    using std::log;
+    using std::sqrt;
+
+    auto rng = std::mt19937();
+
+    // in GeV^2 pbarn
+    double  hbarc2 = 389379372.1;
+
+    for (std::size_t i = 0; i != calls; ++i) {
+        // generate a phase-space point
+        auto tmp = hadronic_pspgen(rng, 10.0, 7000.0);
+        auto s = tmp.s;
+        auto t = tmp.t;
+        auto u = tmp.u;
+        auto x1 = tmp.x1;
+        auto x2 = tmp.x2;
+        auto jacobian = tmp.jacobian;
+
+        double ptl = sqrt((t * u / s));
+        double mll = sqrt(s);
+        double yll = 0.5 * log(x1 / x2);
+        double ylp = fabs(yll + acosh(0.5 * mll / ptl));
+        double ylm = fabs(yll - acosh(0.5 * mll / ptl));
+
+        jacobian *= hbarc2 / calls;
+
+        // cuts for LO for the invariant-mass slice containing the
+        // Z-peak from CMSDY2D11
+        if ((ptl < 14.0) || (fabs(yll) > 2.4) || (ylp > 2.4)
+            || (ylm > 2.4) || (mll < 60.0) || (mll > 120.0))
+        {
+            continue;
+        }
+
+        auto weight = jacobian * int_photo(s, u, t);
+        double  q2 = 90.0 * 90.0;
+
+        pineappl_grid_fill(grid, x1, x2, q2, 0, fabs(yll), 0, weight);
+    }
+}
+
+int main() {
     // create a new luminosity function for the $\gamma\gamma$ initial state
@@
     pineappl_grid_delete(grid);
+}
 \end{lstlisting}
+
+\subsection{Installation}
+\label{app:installation}
+
+Updated installation instructions are kept in the file \texttt{README.md} in \textsc{PineAPPL}'s repository at \url{https://github.com/N3PDF/pineappl/} and on its homepage \url{https://n3pdf.github.io/pineappl/}.
+
+\subsubsection*{Installation of Rust}
+
+\lstset{
+  basicstyle=\ttfamily\small,
+  showstringspaces=false,
+  commentstyle=\color{red},
+  keywordstyle=\color{blue},
+}
+
+All parts are written in Rust: a Rust compiler and related tools are needed.
+On operating systems with a \texttt{bash} shell (such as Linux or MacOS) the installation is as simple as
+\begin{verbatim}
+ $ curl --proto '=https' --tlsv1.2 -sSf https://sh.rustup.rs | sh
+\end{verbatim}
+which downloads the compiler \texttt{rustc}, the package manager \texttt{cargo}, and a few other helpful tools.
+When the installation has completed make sure to read and follow the instructions printed on screen.
+See also \url{https://www.rust-lang.org/tools/install} for more details and for installation instructions for other operating systems.
+
+\subsubsection*{Installation of the command-line program \texorpdfstring{\texttt{pineappl}}{pineappl}}
+
+The command-line program \texttt{pineappl} is compiled and installed using
+\begin{verbatim}
+ $ cargo install pineappl_cli
+\end{verbatim}
+This program also needs \texttt{LHAPDF} \cite{Buckley:2014ana} installed; make sure that the environment variables \texttt{PATH}, \texttt{LD\_LIBRARY\_PATH}, and \texttt{PKG\_CONFIG\_PATH} are properly set.
+For usage instructions simply type \texttt{pineappl} in your shell and read the help message.
+
+\subsubsection*{Installation of the C-language interface (optional)}
+
+For the C interface you need to first install \texttt{cargo-c},
+\begin{verbatim}
+ $ cargo install cargo-c
+\end{verbatim}
+and then download the \textsc{PineAPPL} repository, compile and finally install into it into a directory \texttt{\$prefix} as follows:
+\begin{verbatim}
+ $ git clone https://github.com/N3PDF/pineappl/
+ $ cd pineappl_capi/
+ $ cargo cinstall --release --prefix=DIRECTORY
+\end{verbatim}
+The last line will install the C header \texttt{pineappl\_capi.h}, the library, and a pkg-config\footnote{A standard way on Linux to express how dependencies are compiled/linked against, see \url{https://www.freedesktop.org/wiki/Software/pkg-config/}} file (\texttt{pineappl\_capi.pc}) into the directory specified as \texttt{DIRECTORY}.
+Make sure that the environment variables \texttt{PATH}, \texttt{LD\_LIBRARY\_PATH}, and \texttt{PKG\_CONFIG\_PATH} are properly set.
+The latter is needed for \texttt{pkg-config -{}-cflags -{}-libs pineappl\_capi} to work, which prints the necessary compiler/linker flags.
+
+After being installed, one can compile and link against the library.
+See appendix~\ref{app:example-program} for an example.

### 2020-08-21 paper/sec-pineappl.tex
adding sentence about the python module
Improve PineAPPL appendix
- move installation appendix towards the end
- include complete code example

@@
 The interface consists of roughly thirty functions, among which only a handful are needed in practice.
+We also provide and support a Python package based on this C interface.
 See appendix~\ref{app:example-program} for an example.
@@
 We have defined the grid points at specific positions, but the points given by the MC will land somewhere between them\footnote{The technical term for this interpolation problem is sometimes called \emph{subtabulation}.}.
-The interpolation order $s_y$ then defines a square with length $s_y + 1$ around its centre $(u_1(y_1(x_1)),u_2(y_2(x_2)))$, given by the MC.
+The interpolation order $s_y$ then defines a square with length $s_y + 1$ around its centre $(u(y(x_1)),u(y(x_2)))$, given by the MC.
 All grid points with indices $(i,j)$ covered by the grey square are then updated according to the following formula:

### 2020-08-24 paper/paper.tex
added ttbar references and citation to DY report

@@
 \input{app-pineappl}
-\input{app-lumis}
-\input{app-addmaterial}
+%\input{app-lumis}
+%\input{app-addmaterial}
 

### 2020-08-24 paper/sec-results.tex
added references

@@
 considered here. EW corrections for this process were computed in
-refs.~\cite{Baur:2001ze,Arbuzov:2007db,Dittmaier:2009cr,Frederix:2018nkq}. The process receives contributions
+refs.~\cite{Baur:2001ze,Arbuzov:2007db,Dittmaier:2009cr,Frederix:2018nkq} (see also~\cite{Alioli:2016fum} and references therein). The process receives contributions
 from 13 (35) parton luminosities at NLO QCD (NLO QCD+EW),
@@
 have been devised to optimise the convergence of the perturbative expansion,
-NNLO QCD corrections remain large, as expected in a process mostly initiated
+NNLO QCD corrections remain large~\cite{Czakon:2013goa,Czakon:2014xsa,Czakon:2015owf,Czakon:2016ckf,Catani:2019iny,Catani:2019hip,Catani:2020tko}, as expected in a process mostly initiated
 by gluons. Their inclusion is therefore mandatory in a fit of PDFs. Finally,

### 2020-08-24 paper/paper.tex
Order acknowledgements differently

@@
 \acknowledgments
-We are grateful to Rikkert Frederix for discussions about
-\textsc{aMCfast}, and to Stefan Ditt\-mai\-er for a critical reading of the
-manuscript. We acknowledge discussions with 
+We would like to thank Stefan Ditt\-mai\-er, Stefano Forte, Zahari Kassabov, and Juan Rojo for a critical reading of the manuscript, and we are grateful to Rikkert Frederix for discussions about \textsc{aMCfast}.
+We acknowledge discussions with
 Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
 treatment of EW effects in experimental data.
-%Alessandro Vicini\\
 S.C.\ and C.S.\ are supported by the European Research Council under the European Union's
@@
 \input{app-pineappl}
-%\input{app-lumis}
-%\input{app-addmaterial}
+\input{app-lumis}
+\input{app-addmaterial}
 

### 2020-08-24 paper/sec-pineappl.tex
Remind the reader where the indices are defined
Clarify that we use the same algorithm
Rewrite introduction of section 2

@@
 
-In this section we introduce \textsc{PineAPPL}. We first describe the
-general scope and features of the library, we then formulate the problem of
-computing Monte Carlo weights for cross sections in a multi-coupling expansion,
-and we finally address how this problem is solved with a suitable grid
-representation.
+In this section we introduce \textsc{PineAPPL}.
+We first describe the general scope and features of the library in comparison to \textsc{APPLgrid} and \textsc{fastNLO}.
+Section~\ref{sec:multi-coupling-expansion} gives the details and, in particular, describes the problem of computing Monte Carlo weights for cross sections in a multi-coupling expansion; this section may be read first by readers unfamiliar with the programs mentioned previously.
 
@@
 A straightforward representation is provided by  4-tuples, a list of the momentum fractions $x_1$ and $x_2$, the scale $Q^2$, and the phase-space weight $w$ for each phase-space point; 4-tuples are sufficient to reconstruct a total cross section.
-For each combination $(a,b,k,l,m,n,o)$ we save the following 4-tuples,
+For each combination $(a,b,k,l,m,n,o)$ (see section~\ref{sec:multi-coupling-expansion} for their definition) we save the following 4-tuples,
 \begin{equation}
@@
 We use the same \enquote{Lagrange-interpolation grid} presented in ref.~\cite{Carli:2010rw} with the parameters published in ref.~\cite{Bertone:2014zva}, which give sufficient precision (see section~\ref{sec:results}).
+For the sake of completeness, the following summarises the interpolation algorithm.
 

### 2020-08-24 paper/sec-introduction.tex
Introduction revised a little

@@
 
-The two respects are intertwined: PDFs provide a way of obtaining a prediction
-for a given process in terms of other processes, therefore the accuracy and 
-precision with which PDFs are able to make predictions crucially depend on 
-the accuracy of the perturbative computation used in the PDF determination
-(matched to the precision of the data). Electroweak (including combined QCD--EW) 
-effects should therefore naturally be included in a PDF determination. The 
-reason is twofold. First, one expects NNLO QCD and NLO EW corrections to be of 
+The two respects are intertwined, as they both concur to determine the accuracy
+of the theoretical predictions that are matched to the precision of the data.
+Electroweak (including combined QCD--EW) effects should therefore naturally be
+incorporated in calculations for LHC processes. The reason is twofold. First,
+one expects NNLO QCD and NLO EW corrections to be of
 comparable size because, at the EW scale, the QCD and EW running couplings 
 become similar, $\alphas^2\sim \alpha$. If NNLO QCD corrections are included
-by default in PDF determinations, NLO EW corrections should be
+by default in the computation, NLO EW corrections should be
 taken into account as well. Second, the virtual exchange of soft or 
@@
 
-The systematic inclusion of EW corrections in a PDF determination entails
+The systematic inclusion of EW corrections in precision computations for
+LHC processes entails
 the solution of two separate problems. First, a problem of efficiency:
@@
 numerical convolution with generic input PDFs can be efficiently approximated
-by means of interpolation techniques. Such grids are a fundamental ingredient
-in any PDF fit, where the evaluation of the hadronic cross section needs to 
-be performed a large number of times. While two default formats exist for
+by means of interpolation techniques. Such grids are essential
+whenever the evaluation of the hadronic cross section needs to 
+be performed a large number of times, as is the case in the evaluation of
+scale variations or of PDF fits. While two default formats exist for
 these grids, \textsc{APPLgrid}~\cite{Carli:2010rw} and
@@
 \textsc{PineAPPL} and demonstrate its capabilities by computing fast-interpolation grids, accurate to NLO QCD and NLO QCD+EW, for a representative
-set of processes, usually included in PDF fits, for which EW corrections may
+set of LHC processes for which EW corrections may
 have a sizeable effect on the accuracy of the theoretical predictions.

### 2020-08-24 paper/sec-pineappl.tex

@@
 Inserting a specific weight $W = w (x_1, x_2) / \omega(x_1, x_2)$ into the grid is shown in figure~\ref{fig:grid} as a small black square, inside the larger grey one.
-We have defined the grid points at specific positions, but the points given by the MC will land somewhere between them\footnote{The technical term for this interpolation problem is sometimes called \emph{subtabulation}.}.
+We have defined the grid points at specific positions, but the points given by the MC will land somewhere between them.
 The interpolation order $s_y$ then defines a square with length $s_y + 1$ around its centre $(u(y(x_1)),u(y(x_2)))$, given by the MC.
@@
 \begin{equation}
-a_{i,j} = a_{i,j} + I_i(u(y(x_1))) I_j(u(y(x_2))) W(x_1,x_2) / \omega(x_1,x_2)
+a_{i,j} \leftarrow a_{i,j} + I_i(u(y(x_1))) I_j(u(y(x_2))) W(x_1,x_2) / \omega(x_1,x_2)
 \label{eq:interpolation}

### 2020-08-24 paper/sec-pineappl.tex
Clarify with PineAPPL does a bit

@@
 W_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2, \mathcal{O} \right) \approx \sum_{o=1}^M \frac{\Theta (\mathcal{O}_o^\mathrm{min} \le \mathcal{O} < \mathcal{O}_o^\mathrm{max})}{\mathcal{O}_o^\mathrm{max} - \mathcal{O}_o^\mathrm{min}} w_{ab}^{(k,l,m,n,o)} \left( x_1, x_2, Q^2 \right) \text{,}
+\label{eq:differential-cross-section}
 \end{equation}
@@
 \end{equation}
-from a set of $N$ function evaluations for specific momentum fractions, scales, and values of the observable
+of eq.~\eqref{eq:differential-cross-section} from a set of $N$ function evaluations for specific momentum fractions, scales, and values of the observable
 \begin{equation}
@@
 \end{equation}
-given by the MC integrator.
+given by the MC integrator together with the corresponding value of the weights, eq.~\eqref{eq:weight-map}.
+This problem is solved by finding an appropriate representation of eq.~\eqref{eq:phase-space-weights} and is described in section~\ref{sec:grid-representation}.
 Using eq.~\eqref{eq:expansion} and
@@
 \end{multline}
-\textsc{PineAPPL} can then quickly calculate hadronic cross sections for
-an arbitrary number of PDF sets and perform scale variations.
+\textsc{PineAPPL} can then quickly calculate hadronic cross sections for an arbitrary number of PDF sets and perform scale variations.
 

### 2020-08-24 paper/sec-pineappl.tex
Shift the section 'Perturbative orders' to the end

@@
 
-\subsubsection{Perturbative orders}
-
-In general, we define as leading order (LO) the set of contributions for all possible initial states $a b$ that lead to the same final state $X$, for which the sum of the coupling exponents in eq.~\eqref{eq:expansion} is smallest, i.e.\ $k + l = p$, where $p = \min (k+l)$.
-This number is process dependent and is usually determined by the number of external particles.
-For many processes there is only one contribution at LO (in terms of $k$ and $l$), but this is not true in general.
-Indeed, when a process has multiple quark lines, colourless (photons, \dots) and coloured particles (gluons, \ldots) can be exchanged between them, making it possible to have more than one combinations of $\alphas$ and $\alpha$.
-A typical example at the LHC is (on-shell) top-pair production, which has three different contributions at LO: $\mathcal{O} (\alpha^2)$, $\mathcal{O} (\alphas \alpha)$, and $\mathcal{O} (\alpha^2)$.
-Each contribution receives a higher-order correction with an additional power of $\alphas$ or $\alpha$, which in general leads to at least two next-to-leading order (NLO) corrections.
-The correction with the largest power in $\alphas$ can be unambiguously called \enquote{the} QCD correction, and the one with the largest power in $\alpha$ \enquote{the} EW correction.
-All remaining corrections are of combined type, meaning that, in general, they cannot be attributed to either one of strong or electroweak origin.
-However, for the sake of simplicity and with a slight abuse of notation, it is customary to call
-NLO QCD (EW) corrections those
-corrections of order $\alphas$ ($\alpha$) times the couplings of the LO contribution 
-with the largest power of $\alphas$. In the example above, NLO QCD and EW corrections to top pair production will denote
-respectively those at $\mathcal{O} (\alphas^3 )$ and $\mathcal{O} (\alphas^2 \alpha)$. In this paper, in particular
-when discussing results in sec.~\ref{sec:results}, we will explicitly list the orders that are considered in the cross
-section at LO, NLO QCD and NLO QCD+EW accuracy.
-
-Due to the typical sizes of the couplings $\alphas^2 \sim \alpha$, it is naively expected that within the same order, i.e.\ for fixed $k + l$, terms with larger powers $\alphas^k$ dominate over those with smaller powers (and larger powers of $\alpha^l$).
-In practice, however, this naive expectation is not always true due to dynamic effects.
-Some examples are vector-boson scattering processes~\cite{Biedermann:2017bss,Denner:2019tmn}, top-pair production with a W boson and four-top production~\cite{Frederix:2017wme}, and Higgs production with a bottom-pair~\cite{Pagani:2020rsg}.
-
-\subsubsection{Example: Drell--Yan lepton-pair production at the LHC}
-\label{sec:pineappl-example}
-
-To give an example of eq.~\eqref{eq:expansion}, the following shows Drell--Yan lepton-pair production up to terms at NLO (with some arguments suppressed for the phase-space weights):
-\begin{equation}
-\begin{split}
-\sigma_{ab}
-    &= \alpha^2 W_{ab}^{(0,2,0,0)} \\
-    &+ \alphas \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^2 W_{ab}^{(1,2,0,0)} (Q^2) + \alphas \left( \xi_\mathrm{R}^2 Q^2 \right) \log (\xi_\mathrm{F}^2) \alpha^2 W_{ab}^{(1,2,0,1)} \\
-    &+ \alpha^3 W_{ab}^{(0,3,0,0)} (Q^2) + \log (\xi_\mathrm{F}^2) \alpha^3 W_{ab}^{(0,3,0,1)} \text{.}
-\end{split}
-\end{equation}
-The term in the first line is the LO term, the second line shows the NLO QCD correction, and the third line the NLO EW correction.
-Note that all terms depend on the renormalisation scale only indirectly through $\alphas$, because 1) higher-order terms in $\alpha$ never generate a renormalisation scale dependence (in the $\alpha$ schemes that are valid according to section~\ref{sec:multi-coupling-expansion}) and 2) higher-order QCD corrections only introduce an explicit renormalisation scale dependence in counterterms with vertices with more than two gluons.
-At NLO these terms are not present for this process so that terms proportional to $\log (\xi_\mathrm{R}^2)$ vanish.
-Both NLOs, however, have contributions from a collinear counterterm that depends on the factorisation scale.
-Since this process has a single LO, combined QCD--EW corrections first appear at next-to-next-to-leading order (NNLO), which include the QCD correction at $\mathcal{O} (\alphas^2 \alpha^2)$, the EW correction $\mathcal{O} (\alpha^4)$, and a single combined correction at $\mathcal{O} (\alphas \alpha^3)$.
-
-Note that all initial states have to be taken into account that lead to the same final state.
-This includes the photon--photon initial state, which appears already at LO.
-In the corresponding Feynman diagrams all particles are colourless, so that the photon--photon initiated contributions only receive EW corrections.
-The EW corrections also introduce quark--photon contributions, in analogy of QCD corrections introducing quark--gluon contributions.
-
-%\subsubsection{Example: top-pair production}
-%
-%\begin{equation}
-%\begin{split}
-%\sigma_{ab}
-%&= \alpha^2                                                                       W_{ab}^{(0,2,0,0)}
-% + \alphas   \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha                           W_{ab}^{(1,1,0,0)}
-% + \alphas^2 \left( \xi_\mathrm{R}^2 Q^2 \right)                                  W_{ab}^{(2,0,0,0)} \\
-%&+ \alphas^3 \left( \xi_\mathrm{R}^2 Q^2 \right)                                  W_{ab}^{(3,0,0,0)} \\
-%&+ \alphas^3 \left( \xi_\mathrm{R}^2 Q^2 \right)          \log (\xi_\mathrm{F}^2) W_{ab}^{(3,0,0,1)} (Q^2)
-% + \alphas^3 \left( \xi_\mathrm{R}^2 Q^2 \right)          \log (\xi_\mathrm{R}^2) W_{ab}^{(3,0,1,0)} (Q^2) \\
-%&+ \alphas^2 \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha                           W_{ab}^{(2,1,0,0)} \\
-%&+ \alphas^2 \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha   \log (\xi_\mathrm{F}^2) W_{ab}^{(2,1,0,1)} (Q^2)
-% + \alphas^2 \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha   \log (\xi_\mathrm{R}^2) W_{ab}^{(2,1,1,0)} (Q^2) \\
-%&+ \alphas   \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^2                         W_{ab}^{(1,2,0,0)} \\
-%&+ \alphas   \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^2 \log (\xi_\mathrm{F}^2) W_{ab}^{(1,2,0,1)} (Q^2)
-% + \alphas   \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^2 \log (\xi_\mathrm{R}^2) W_{ab}^{(1,2,1,0)} (Q^2) \\
-%&+           \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^3                         W_{ab}^{(0,3,0,0)} \\
-%&+           \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^3 \log (\xi_\mathrm{F}^2) W_{ab}^{(0,3,0,1)} (Q^2)
-% +           \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^3 \log (\xi_\mathrm{R}^2) W_{ab}^{(0,3,1,0)} (Q^2)
-%\end{split}
-%\end{equation}
-
-\subsection{Grid representations}
+\subsubsection{Grid representations}
 \label{sec:grid-representation}
@@
 
-\subsubsection{4-tuples}
-
-A straightforward representation is provided by  4-tuples, a list of the momentum fractions $x_1$ and $x_2$, the scale $Q^2$, and the phase-space weight $w$ for each phase-space point; 4-tuples are sufficient to reconstruct a total cross section.
+\paragraph{4-tuples}
+A straightforward representation is given by 4-tuples, i.e.\ a list of the momentum fractions $x_1$ and $x_2$, the scale $Q^2$, and the phase-space weight $w$ for each phase-space point; 4-tuples are sufficient to reconstruct a total cross section.
 For each combination $(a,b,k,l,m,n,o)$ (see section~\ref{sec:multi-coupling-expansion} for their definition) we save the following 4-tuples,
@@
 
-\subsubsection{Lagrange-interpolation grid}
-
-A different strategy is to partition the $(x_1, x_2, Q^2)$ space,
+\paragraph{Lagrange-interpolation grid}
+A different strategy is to partition a subset $H$ of the $(x_1, x_2, Q^2)$ space,
 \begin{equation}
@@
 using $y_\text{min} = y(x_\text{max})$ and $y_\text{max} = y(x_\text{min})$ and the grid spacing $\Delta y = (y_\text{max} - y_\text{min})/(N_y-1)$, so that the integer part of $u(y)$ gives the grid index, e.g.\ $u(y_\text{min}) = 0$ and $u(y_\text{max}) = N_y - 1$, and the fractional part gives the location between the nearest grid points.
+
+\subsection{Perturbative orders}
+
+In general, we define as leading order (LO) the set of contributions for all possible initial states $a b$ that lead to the same final state $X$, for which the sum of the coupling exponents in eq.~\eqref{eq:expansion} is smallest, i.e.\ $k + l = p$, where $p = \min (k+l)$.
+This number is process dependent and is usually determined by the number of external particles.
+For many processes there is only one contribution at LO (in terms of $k$ and $l$), but this is not true in general.
+Indeed, when a process has multiple quark lines, colourless (photons, \dots) and coloured particles (gluons, \ldots) can be exchanged between them, making it possible to have more than one combinations of $\alphas$ and $\alpha$.
+A typical example at the LHC is (on-shell) top-pair production, which has three different contributions at LO: $\mathcal{O} (\alpha^2)$, $\mathcal{O} (\alphas \alpha)$, and $\mathcal{O} (\alpha^2)$.
+Each contribution receives a higher-order correction with an additional power of $\alphas$ or $\alpha$, which in general leads to at least two next-to-leading order (NLO) corrections.
+The correction with the largest power in $\alphas$ can be unambiguously called \enquote{the} QCD correction, and the one with the largest power in $\alpha$ \enquote{the} EW correction.
+All remaining corrections are of combined type, meaning that, in general, they cannot be attributed to either one of strong or electroweak origin.
+However, for the sake of simplicity and with a slight abuse of notation, it is customary to call
+NLO QCD (EW) corrections those
+corrections of order $\alphas$ ($\alpha$) times the couplings of the LO contribution 
+with the largest power of $\alphas$. In the example above, NLO QCD and EW corrections to top pair production will denote
+respectively those at $\mathcal{O} (\alphas^3 )$ and $\mathcal{O} (\alphas^2 \alpha)$. In this paper, in particular
+when discussing results in sec.~\ref{sec:results}, we will explicitly list the orders that are considered in the cross
+section at LO, NLO QCD and NLO QCD+EW accuracy.
+
+Due to the typical sizes of the couplings $\alphas^2 \sim \alpha$, it is naively expected that within the same order, i.e.\ for fixed $k + l$, terms with larger powers $\alphas^k$ dominate over those with smaller powers (and larger powers of $\alpha^l$).
+In practice, however, this naive expectation is not always true due to dynamic effects.
+Some examples are vector-boson scattering processes~\cite{Biedermann:2017bss,Denner:2019tmn}, top-pair production with a W boson and four-top production~\cite{Frederix:2017wme}, and Higgs production with a bottom-pair~\cite{Pagani:2020rsg}.
+
+\subsubsection{Example: Drell--Yan lepton-pair production at the LHC}
+\label{sec:pineappl-example}
+
+To give an example of eq.~\eqref{eq:expansion}, the following shows Drell--Yan lepton-pair production up to terms at NLO (with some arguments suppressed for the phase-space weights):
+\begin{equation}
+\begin{split}
+\sigma_{ab}
+    &= \alpha^2 W_{ab}^{(0,2,0,0)} \\
+    &+ \alphas \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^2 W_{ab}^{(1,2,0,0)} (Q^2) + \alphas \left( \xi_\mathrm{R}^2 Q^2 \right) \log (\xi_\mathrm{F}^2) \alpha^2 W_{ab}^{(1,2,0,1)} \\
+    &+ \alpha^3 W_{ab}^{(0,3,0,0)} (Q^2) + \log (\xi_\mathrm{F}^2) \alpha^3 W_{ab}^{(0,3,0,1)} \text{.}
+\end{split}
+\end{equation}
+The term in the first line is the LO term, the second line shows the NLO QCD correction, and the third line the NLO EW correction.
+Note that all terms depend on the renormalisation scale only indirectly through $\alphas$, because 1) higher-order terms in $\alpha$ never generate a renormalisation scale dependence (in the $\alpha$ schemes that are valid according to section~\ref{sec:multi-coupling-expansion}) and 2) higher-order QCD corrections only introduce an explicit renormalisation scale dependence in counterterms with vertices with more than two gluons.
+At NLO these terms are not present for this process so that terms proportional to $\log (\xi_\mathrm{R}^2)$ vanish.
+Both NLOs, however, have contributions from a collinear counterterm that depends on the factorisation scale.
+Since this process has a single LO, combined QCD--EW corrections first appear at next-to-next-to-leading order (NNLO), which include the QCD correction at $\mathcal{O} (\alphas^2 \alpha^2)$, the EW correction $\mathcal{O} (\alpha^4)$, and a single combined correction at $\mathcal{O} (\alphas \alpha^3)$.
+
+Note that all initial states have to be taken into account that lead to the same final state.
+This includes the photon--photon initial state, which appears already at LO.
+In the corresponding Feynman diagrams all particles are colourless, so that the photon--photon initiated contributions only receive EW corrections.
+The EW corrections also introduce quark--photon contributions, in analogy of QCD corrections introducing quark--gluon contributions.

### 2020-08-24 paper/sec-introduction.tex
Refocus the introduction on a wider readership

@@
 determined~\cite{Schmidt:2015zda,Manohar:2016nzj,Manohar:2017eqh,Bertone:2017bme,Harland-Lang:2019pla}.
-Data points in kinematic regions where EW corrections are expected to affect
-the accuracy of the theoretical predictions are usually removed from the fits.
 The resulting relative PDF uncertainty --- which accounts only for the
@@
 size (e.g.\ from missing higher-order terms in the QCD perturbative
-expansion), have started to be included in a PDF determination and represented 
+expansion), have started to be represented 
 into PDF uncertainties only very 
-recently~\cite{AbdulKhalek:2019bux,AbdulKhalek:2019ihb}. This has led to an 
-improvement of PDF accuracy, in terms of an overall
-better statistical quality of the fit, at the price of a modest deterioration 
-of PDF precision, in terms of a slight inflation of PDF uncertainties.
+recently~\cite{AbdulKhalek:2019bux,AbdulKhalek:2019ihb}.
 
@@
 of the theoretical predictions that are matched to the precision of the data.
-Electroweak (including combined QCD--EW) effects should therefore naturally be
-incorporated in calculations for LHC processes. The reason is twofold. First,
-one expects NNLO QCD and NLO EW corrections to be of
+In particular EW (including combined QCD--EW) effects should start to be
+incorporated in calculations for LHC processes as standard. The reason is
+twofold. First, one expects NNLO QCD and NLO EW corrections to be of
 comparable size because, at the EW scale, the QCD and EW running couplings 
 become similar, $\alphas^2\sim \alpha$. If NNLO QCD corrections are included
-by default in the computation, NLO EW corrections should be
+by default in the computations, NLO EW corrections should be
 taken into account as well. Second, the virtual exchange of soft or 
 collinear weak bosons leads to Sudakov 
-logarithms~\cite{Denner:2000jv,Denner:2001gw},
+logarithms~\cite{Denner:2000jv,Denner:2001gw}
+(see also~\cite{Denner:2019vbn} and references therein),
 which can make the coefficients of the EW series grow faster than 
@@
 of the \si{\tera\electronvolt}), where several LHC data sets (e.g.\ Z-boson
-transverse-momentum distributions) enter both the determination of PDFs and the search
+transverse-momentum distributions) enter both the validation of the SM and the search
 for new physics.

### 2020-08-24 paper/sec-pineappl.tex

@@
 Section~\ref{sec:multi-coupling-expansion} gives the details and, in particular, describes the problem of computing Monte Carlo weights for cross sections in a multi-coupling expansion; this section may be read first by readers unfamiliar with the programs mentioned previously.
+In section~\ref{sec:perturbative-orders} we discuss a few properties of multi-coupling-expanded predictions.
 
@@
 
-In experiments, but also for many calculations where the phase-space integration is performed using MC techniques, finite statistics does not allow us to reconstruct the exact dependence of the cross section on the observable $\mathcal{O}$.
+In experiments, but also for many calculations where the phase-space integration is performed using MC techniques, finite statistics does not allow for the exact reconstruction of the dependence of the cross section on the observable $\mathcal{O}$.
 Instead, it it sufficient to approximate the derivative using a piecewise-constant function,
@@
 \subsection{Perturbative orders}
+\label{sec:perturbative-orders}
 
-In general, we define as leading order (LO) the set of contributions for all possible initial states $a b$ that lead to the same final state $X$, for which the sum of the coupling exponents in eq.~\eqref{eq:expansion} is smallest, i.e.\ $k + l = p$, where $p = \min (k+l)$.
-This number is process dependent and is usually determined by the number of external particles.
+In section~\ref{sec:multi-coupling-expansion} we labelled the different perturbative orders using the indices $k,l,m,n$.
+Their values are process specific.
+However, in general we define as leading order (LO) the set of contributions for all possible initial states $a b$ that lead to the same final state $X$, for which the sum of the coupling exponents in eq.~\eqref{eq:expansion} is smallest, i.e.\ $k + l = p$, where $p = \min (k+l)$.
+This number is also process dependent and is usually determined by the number of external particles.
 For many processes there is only one contribution at LO (in terms of $k$ and $l$), but this is not true in general.

### 2020-08-24 paper/paper.tex
reverted paper.tex
Abstract and introduction

@@
 
-\title{PineAPPL:\\ combining EW and QCD corrections for PDF fits}
+\title{PineAPPL: combining EW and QCD corrections\\
+  for fast evaluation of LHC processes}
 
@@
   by computing fast-interpolation grids, accurate to next-to-leading order in
-  the strong and electroweak couplings, for a representative set of processes
-  commonly used in the determination of the parton distribution functions (PDFs)
-  of the proton. We formulate a recommendation on the format of the experimental
-  deliverables in order to consistently incorporate them in forthcoming
-  fits of PDFs including electroweak corrections.}
+  the strong and electroweak couplings, for a representative set of LHC
+  processes for which EW corrections may have a sizeable effect on the accuracy
+  of the corresponding theoretical predictions.
+  We formulate a recommendation on the format of the experimental
+  deliverables in order to consistently compare them with computations
+  that incorporate EW corrections.}
 

### 2020-08-25 paper/sec-results.tex
Remove incorrect statement

@@
 likely to be easily accommodated by the large data uncertainty. However, 
-this conclusion might not continue to hold: first, data
-will become more precise, in particular thanks to the increased Run-II LHC
-luminosity. Second, both EW corrections and PI contributions are expected to
-grow larger at \SI{13}{\tera\electronvolt}, making their impact more relevant.
+due to the increased Run-II LHC luminosity data will become more precise.
 

### 2020-08-25 paper/paper.tex
Mention PDFs in the abstract; emphasise multi-coupling expansion in abstract and sec.1; discuss choice of processes in sec.3

@@
   strong, electroweak, and combined strong-electroweak couplings. We
-  discuss its features in comparison to similar software
-  available in the literature, and we explicitly interface it to
-  \textsc{MadGraph5\_aMC@NLO}. We validate the performance of \textsc{PineAPPL}
-  by computing fast-interpolation grids, accurate to next-to-leading order in
-  the strong and electroweak couplings, for a representative set of LHC
-  processes for which EW corrections may have a sizeable effect on the accuracy
-  of the corresponding theoretical predictions.
-  We formulate a recommendation on the format of the experimental
+  demonstrate this unique ability, that distinguishes \textsc{PineAPPL} from
+  similar software available in the literature, by interfacing it to
+  \textsc{MadGraph5\_aMC@NLO}. We compute fast-interpolation grids,
+  accurate to next-to-leading order in the strong and electroweak couplings,
+  for a representative set of LHC processes for which EW corrections may have
+  a sizeable effect on the accuracy of the corresponding theoretical
+  predictions. We formulate a recommendation on the format of the experimental
   deliverables in order to consistently compare them with computations
-  that incorporate EW corrections.}
+  that incorporate EW corrections, and specifically to determine
+  parton distribution functions to the same accuracy.}
 

### 2020-08-25 paper/sec-doublecounting.tex
Remove TODO
Mention PDFs in the abstract; emphasise multi-coupling expansion in abstract and sec.1; discuss choice of processes in sec.3

@@
 
-The ability to include theoretical calculations of EW corrections in
-PDF determinations is not sufficient to make a \emph{consistent} fit possible. Indeed, experimental data should
-be provided in a format that allows PDF collaborations to easily employ them in these fits in a theoretically sound manner. To this purpose, in this section
+The ability to perform theoretical calculations simultaneously accurate in both
+the QCD and EW couplings is not sufficient to make a \emph{consistent}
+comparison with experimental measurements. In this section
 we formulate some
-guidelines to facilitate a consistent presentation of the experimental data.
-We focus on the problem of data with (partially) subtracted EW effects, which, in PDF fits with theory predictions including them, leads to a double counting issue.
+guidelines to facilitate this task. We focus on the problem of data with (partially) subtracted EW effects, which, if compared to theory predictions including them, leads to a double counting issue.
 
@@
 This fact is especially problematic if deconvolved datasets are the only ones which are published, since undoing the exact deconvolution can be very difficult, or practically impossible.
-(\textbf{TODO insert comment about LEP ISR and DIS EW effects removal}).
 

### 2020-08-25 paper/sec-introduction.tex
Mention PDFs in the abstract; emphasise multi-coupling expansion in abstract and sec.1; discuss choice of processes in sec.3

@@
 of the theoretical predictions that are matched to the precision of the data.
-In particular EW (including combined QCD--EW) effects should start to be
+In particular, taking advantage of the automation pioneered
+in~\cite{Kallweit:2014xda,Biedermann:2017yoi,Frederix:2018nkq},
+perturbative corrections that arise from the simultaneous expansion in both the
+QCD and EW couplings should start to be
 incorporated in calculations for LHC processes as standard. The reason is
@@
 
-The systematic inclusion of EW corrections in precision computations for
+The consistent inclusion of QCD and EW corrections in precision computations for
 LHC processes entails
@@
 we develop \textsc{PineAPPL}, a library that allows any user to generate
-fast-interpolation grids, accurate to up to any fixed order in the strong and
+fast-interpolation grids, accurate to up to any fixed order in the QCD and
 EW couplings. The library supports variations of the factorisation

### 2020-08-25 paper/sec-results.tex
Mention PDFs in the abstract; emphasise multi-coupling expansion in abstract and sec.1; discuss choice of processes in sec.3

@@
 
-In this section we demonstrate the capabilities of \textsc{mg5\_aMC}+\textsc{PineAPPL} by
+In this section we demonstrate the capabilities of the \textsc{PineAPPL}
+library by interfacing it to \textsc{mg5\_aMC}, and by
 computing fast-interpolation grids, accurate to NLO QCD and NLO QCD+EW,
-for a representative set of processes in which EW corrections may have a
-sizeable effect on the accuracy of the theoretical predictions.
+for a common set of LHC processes in which EW corrections may sizeably
+affect the accuracy of the theoretical predictions.
 In order to consider some realistic kinematics for these
-processes, we rely on a set of measurements that are commonly included in PDF
-fits. Our aim is twofold. First, we want to validate the results
+processes, we rely on a representative set of LHC measurements. Our aim is twofold. First, we want to validate the results
 obtained with \textsc{PineAPPL}; second, we want to assess the
 impact of the EW corrections for the specific experimental setups. We describe
-the settings employed for the computations, and the corresponding results for
-each process. We remind the reader that \textsc{mg5\_aMC} makes it possible
+the settings employed for the computations, the corresponding results for
+each process, and possible implications for the determination of PDFs.
+
+\subsection{Computational settings}
+\label{subsec:computational_settings}
+
+\textsc{mg5\_aMC} makes it possible
 to compute predictions including NLO QCD and EW corrections for arbitrary processes
@@
 will not be employed in the following.
-
-\subsection{Computational settings}
-\label{subsec:computational_settings}
 
@@
 top-quark pair production, and Z-boson (lepton-pair) production with non-zero
-transverse momentum in proton-proton collisions. In the following, we shall
+transverse momentum in proton-proton collisions. These are some of the most
+commonly and most precisely measured processes at the LHC, which are widely
+studied to test the SM and/or search for new physics. We therefore expect them
+to allow us to clearly show the benefit of being able to make fast and
+reliable theoretical predictions accurate to NLO QCD+EW with \textsc{PineAPPL}.
+In the following, we shall
 present the experimental measurements, the process-specific settings, and

### 2020-08-25 paper/sec-conclusion.tex
adding landing page url in the conclusion section
Don't write outlook if there isn't any
the discussion on PDFs is a little dilapidated in the conclusions

--- 2020-08-10 paper/sec-conclusion.tex
@@
-\section{Conclusions and Outlook}
+\section{Conclusions}
 \label{sec:conclusion}
-{\bf MZ I would like to have some sort of introduction here (a short bla bla on precision), before turning to Pineappl}
 
-We presented a new tool called \textsc{PineAPPL}, which stores perturbative calculations from an external Monte Carlo in a PDF-independent way using interpolation grids.
-This offers the advantage of fast a-posteriori convolutions with PDFs, for example to study the uncertainties coming from different PDF sets and/or the strong coupling constant $\alphas$.
-Another application that we focused on is PDF fitting, where the interpolation grids constitute the theoretical input.
-We tested \textsc{PineAPPL} together with \textsc{mg5\_aMC@NLO} and found a precision of \numrange{e-4}{e-5} relative to the MC result, which is more than enough for the applications described before.
-Although we used \textsc{mg5\_aMC@NLO}, we note that \textsc{PineAPPL} is not tied in any way to a specific MC and can be easily interfaced with any generator.
+The systematic inclusion of EW corrections in accurate theoretical computations
+for several LHC processes is becoming more and more important in order to
+match the increasing precision of the data. In this paper we simplified the
+computational aspect of this task, building upon the automation of QCD and EW
+computations pioneered in recent years~\cite{Kallweit:2014xda,Biedermann:2017yoi,Frederix:2018nkq}.
+Specifically we developed \textsc{PineAPPL}, a new library that stores perturbative calculations from an external Monte Carlo generator in a PDF-independent way using interpolation grids.
+This offers the advantage of fast a posteriori convolutions with PDFs, for example to study the uncertainties coming from different PDF sets and/or the strong coupling constant $\alphas$, and to determine the PDFs themselves, a task for
+which fast-interpolation grids are fundamental.
+We tested \textsc{PineAPPL} together with \textsc{mg5\_aMC} and found a precision of \numrange{e-4}{e-5} relative to the MC result, which is excellent for all
+foreseeable practical purposes.
+Although we used \textsc{mg5\_aMC}, we note that \textsc{PineAPPL} is not tied in any way to a specific Monte Carlo generator, and can be easily interfaced with any of them.
 
-A distinguishing feature of \textsc{PineAPPL} is the support for arbitrary coupling orders not only in the strong, but also in the electroweak coupling.
+We emphasise that a distinguishing feature of \textsc{PineAPPL} is the support for arbitrary coupling orders not only in the strong, but also in the electroweak coupling.
 This enables us to generate, for the first time, NLO EW and NLO combined QCD--EW interpolation grids.
-Using \textsc{mg5\_aMC@NLO} we calculated and showcased the impact of these corrections for important PDF processes for specific analyses from ATLAS and CMS: Drell--Yan lepton-pair production, top-pair production, and Z-boson production with non-zero transverse momentum.
+Using \textsc{mg5\_aMC} we calculated and showcased the impact of these corrections for specific measurements of some representative LHC processes: Drell--Yan lepton-pair production, top-pair production, and Z-boson production with non-zero transverse momentum.
 
-Finally, we discussed the issue of subtracting EW corrections in experimental data, which becomes an important consideration when combining the interpolation grids with the corresponding experimental data in a PDF fit including EW and combined QCD--EW corrections.
-
-Having developed and thoroughly tested \textsc{PineAPPL}, all technical requirements are fulfilled for producing the first global PDF fit including EW and combined QCD--EW corrections.
+Finally, we discussed the issue of subtracting EW corrections in experimental data, which becomes important when theoretical predictions including EW corrections are compared to experimental data.
+In particular, with the
+development of \textsc{PineAPPL}, all technical requirements are fulfilled for producing the first PDF fit of LHC data including EW and combined QCD--EW corrections.
 This will have at least two advantages: in PDF fits phase-space regions are usually cut away if they exhibit large EW corrections; including them therefore increases the number of data points in a fit and therefore indirectly enlarges a PDF set's interpolation region.
 Secondly, this makes it possible to use experimental data that are closer to the actual measurement, without the need to compensate for missing EW corrections.
+We plan to address this task in a future work.
+
+The \textsc{PineAPPL} library is available at \url{https://n3pdf.github.io/pineappl}.

### 2020-08-25 paper/paper.tex
Acknowledgements

@@
 \acknowledgments
-We would like to thank Stefan Ditt\-mai\-er, Stefano Forte, Zahari Kassabov, and Juan Rojo for a critical reading of the manuscript, and we are grateful to Rikkert Frederix for discussions about \textsc{aMCfast}.
-We acknowledge discussions with
+We would like to thank Stefan Dittmaier, Stefano Forte, Zahari Kassabov, and Juan Rojo for a critical reading of the manuscript, and Rikkert Frederix for discussions about \textsc{aMCfast}.
+We also acknowledge discussions with
 Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 

### 2020-08-26 paper/paper.tex
added Davide in the acknowledgements

@@
 \acknowledgments
-We would like to thank Stefan Dittmaier, Stefano Forte, Zahari Kassabov, and Juan Rojo for a critical reading of the manuscript, and Rikkert Frederix for discussions about \textsc{aMCfast}.
+We would like to thank Stefan Dittmaier, Stefano Forte, Zahari Kassabov, Davide Pagani, and Juan Rojo for a critical reading of the manuscript, and Rikkert Frederix for discussions about \textsc{aMCfast}.
 We also acknowledge discussions with

### 2020-08-26 paper/sec-results.tex
added 3 references

@@
 EW corrections for this process
-were computed in refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Frederix:2018nkq,Czakon:2019bcq,Czakon:2019txp}.
+were computed in refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Denner:2016jyo,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Frederix:2018nkq,Czakon:2019bcq,Czakon:2019txp}.
 The process receives contributions from
@@
 have been devised to optimise the convergence of the perturbative expansion,
-NNLO QCD corrections remain large~\cite{Czakon:2013goa,Czakon:2014xsa,Czakon:2015owf,Czakon:2016ckf,Catani:2019iny,Catani:2019hip,Catani:2020tko}, as expected in a process mostly initiated
+NNLO QCD corrections remain large~\cite{Czakon:2013goa,Czakon:2014xsa,Czakon:2015owf,Czakon:2016ckf,Catani:2019iny,Behring:2019iiv,Catani:2019hip,Catani:2020tko,Czakon:2020qbd}, as expected in a process mostly initiated
 by gluons. Their inclusion is therefore mandatory in a fit of PDFs. Finally,

### 2020-08-27 paper/sec-conclusion.tex
Cosmetic changes on the final line of the conclusions
Polish introduction and conclusions

@@
-\section{Conclusions}
+\section{Conclusions and Outlook}
 \label{sec:conclusion}
@@
 Specifically we developed \textsc{PineAPPL}, a new library that stores perturbative calculations from an external Monte Carlo generator in a PDF-independent way using interpolation grids.
-This offers the advantage of fast a posteriori convolutions with PDFs, for example to study the uncertainties coming from different PDF sets and/or the strong coupling constant $\alphas$, and to determine the PDFs themselves, a task for
+This offers the advantage of fast a posteriori convolutions with PDFs, for example to study the uncertainties coming from different PDF sets and/or the strong coupling $\alphas$, and to determine the PDFs themselves, a task for
 which fast-interpolation grids are fundamental.
@@
 
+\vspace{0.5cm}
+\hrule
+\begin{center}
 The \textsc{PineAPPL} library is available at \url{https://n3pdf.github.io/pineappl}.
+\end{center}

### 2020-08-27 paper/sec-introduction.tex
Polish introduction and conclusions

@@
 computation of additional higher-order contributions to the fixed-order 
-coupling-constant perturbative expansion, on the one hand, and an increasingly 
+perturbative expansion, on the one hand, and an increasingly
 sophisticated determination of the Parton Distribution Functions (PDFs) of the 
@@
 considered as such (e.g.\ the $t$-channel photon-induced component in
-neutral-current Drell--Yan, which is not a separate processes beyond leading
+neutral-current Drell--Yan, which is not a separate process beyond leading
 order) or of just a part of the EW effects (e.g.\ multiple-photon
@@
 \textsc{APPLgrid}+\textsc{aMCfast}~\cite{Bertone:2014zva}.
-\textsc{PineAPPL} can also be easily interfaced to any Monte Carlo generator,
-e.g.\ \textsc{SHERPA}~\cite{Biedermann:2017yoi}, where it complements
+However, \textsc{PineAPPL} can also be easily interfaced to any Monte Carlo generator,
+e.g.\ \textsc{SHERPA}~\cite{Biedermann:2017yoi}, where it would complement
 \textsc{MCgrid}~\cite{DelDebbio:2013kxa,Bothmann:2015dba}.

### 2020-08-28 paper/sec-results.tex
ERN's final, very few, very minor typos

@@
 top-quark masses, respectively, $\Gamma_\mathrm{Z}$ and $\Gamma_\mathrm{W}$ are the widths of
-the Z and W bosons, and $G_\mu$ is value of the Fermi coupling. The value of the strong
+the Z and W bosons, and $G_\mu$ is the value of the Fermi coupling. The value of the strong
 coupling is chosen consistently with the PDF set, $\alphas(M_\mathrm{Z})=0.118$.
@@
 of a heavy boson are formally of the same perturbative order of the EW corrections, they are not included in our
-computations. In fact, while nothing prevents to include these contributions \emph{a posteriori}, as they are finite,
+computations. In fact, while nothing prevents one to include these contributions \emph{a posteriori}, as they are finite,
 their impact is either smaller than the one of \enquote{standard} EW corrections, or anyway negligible with respect to
@@
     \caption{Validation and test of the \textsc{PineAPPL} grid for the ATLAS
-      high-mass Drell--Yan lepton pair measurement in the high-mass region at
+      Drell--Yan lepton pair measurement in the high-mass region at
       a centre-of-mass energy of \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The first panel
@@
 likely to be easily accommodated by the large data uncertainty. However, 
-due to the increased Run-II LHC luminosity data will become more precise.
+due to the increased Run-II LHC luminosity, data will become more precise.
 

### 2020-08-28 paper/paper.tex
Add last-minute changes to abstract and intro

@@
   general-purpose Monte Carlo generator, accurate to fixed order in the
-  strong, electroweak, and combined strong-electroweak couplings. We
+  strong, electroweak, and combined strong--electroweak couplings. We
   demonstrate this unique ability, that distinguishes \textsc{PineAPPL} from

### 2020-08-28 paper/sec-introduction.tex
Add last-minute changes to abstract and intro

@@
 In particular, taking advantage of the automation pioneered
-in~\cite{Kallweit:2014xda,Biedermann:2017yoi,Frederix:2018nkq},
+in refs.~\cite{Kallweit:2014xda,Biedermann:2017yoi,Frederix:2018nkq},
 perturbative corrections that arise from the simultaneous expansion in both the
@@
 logarithms~\cite{Denner:2000jv,Denner:2001gw}
-(see also~\cite{Denner:2019vbn} and references therein),
+(see also ref.~\cite{Denner:2019vbn} and references therein),
 which can make the coefficients of the EW series grow faster than 
@@
 phase-space regions associated with large mass scales (roughly of the order
-of the \si{\tera\electronvolt}), where several LHC data sets (e.g.\ Z-boson
+of a \si{\tera\electronvolt}), where several LHC data sets (e.g.\ Z-boson
 transverse-momentum distributions) enter both the validation of the SM and the search
@@
 be performed a large number of times, as is the case in the evaluation of
-scale variations or of PDF fits. While two default formats exist for
+scale variations or of PDF fits. While two formats already exist for
 these grids, \textsc{APPLgrid}~\cite{Carli:2010rw} and
@@
 we develop \textsc{PineAPPL}, a library that allows any user to generate
-fast-interpolation grids, accurate to up to any fixed order in the QCD and
+fast-interpolation grids, accurate to any fixed order in the QCD and
 EW couplings. The library supports variations of the factorisation
@@
 The grids in the new \textsc{PineAPPL} format complement those
-(accurate to fixed-orders in the strong coupling only) that can be generated 
+(accurate to fixed order in the strong coupling only) that can be generated
 in the \textsc{APPLgrid} and \textsc{FastNLO} formats. The \textsc{PineAPPL}
@@
 In section~\ref{sec:doublecounting} we try to detail in a more
-comprehensive manner the second problem sketched above, the solution of which,
+comprehensive manner the double-counting problem sketched above, the solution of which,
 however, remains beyond the scope of the current work. We provide our
 conclusions and an outlook in section~\ref{sec:conclusion}. Examples of
-installation and usage of \textsc{PineAPPL} are provided in
+usage and the installation of \textsc{PineAPPL} are provided in
 appendix~\ref{app:pineappl}; appendix~\ref{app:lumis} collects the parton

### 2020-08-28 paper/sec-pineappl.tex
Add section reference
Fix missing reference
Add last-minute changes to section 2

@@
 In this section we introduce \textsc{PineAPPL}.
-We first describe the general scope and features of the library in comparison to \textsc{APPLgrid} and \textsc{fastNLO}.
+We first describe the general scope and features of the library in comparison to \textsc{APPLgrid} and \textsc{fastNLO} in section~\ref{sec:library}.
 Section~\ref{sec:multi-coupling-expansion} gives the details and, in particular, describes the problem of computing Monte Carlo weights for cross sections in a multi-coupling expansion; this section may be read first by readers unfamiliar with the programs mentioned previously.
@@
 
-\item \textsc{PineAPPL} has been explicitly interfaced to \textsc{mg5\_aMC} (v3+)~\cite{Alwall:2014hca,Frederix:2018nkq},\footnote{A version of \textsc{mg5\_aMC} interfaced to \textsc{PineAPPL} can be downloaded from \url{https://launchpad.net/mg5amc-pineappl/trunk}, and it will be included as standard in the next \textsc{mg5\_aMC} release.} for which it supersedes \textsc{aMCfast}~\cite{Bertone:2014zva}.
-See appendix~\ref{app:sample-runcard} for an example of a runcard.
+\item \textsc{PineAPPL} has been explicitly interfaced to \textsc{mg5\_aMC} (v3+)~\cite{Alwall:2014hca,Frederix:2018nkq},\footnote{A version of \textsc{mg5\_aMC} interfaced to \textsc{PineAPPL} can be downloaded from \url{https://launchpad.net/mg5amc-pineappl/trunk}, and it will be included as standard in the next \textsc{mg5\_aMC} release.} for which it supersedes \textsc{aMCfast}~\cite{Bertone:2014zva}; see appendix~\ref{app:sample-runcard} for an example of a runcard.
 While the usage of
 \textsc{mg5\_aMC}(v3+) + \textsc{PineAPPL} is similar to that of 
-\textsc{mg5\_aMC}(v2) + \textsc{PineAPPL} + \textsc{APPLgrid}, it is however more
+\textsc{mg5\_aMC}(v2) + \textsc{aMCfast} + \textsc{APPLgrid}, it is however more
 efficient.
@@
 
-\paragraph{4-tuples}
-A straightforward representation is given by 4-tuples, i.e.\ a list of the momentum fractions $x_1$ and $x_2$, the scale $Q^2$, and the phase-space weight $w$ for each phase-space point; 4-tuples are sufficient to reconstruct a total cross section.
+\paragraph{4-tuples.}
+A straightforward representation is given by 4-tuples, i.e.\ a list of the momentum fractions $x_1$ and $x_2$, the scale $Q^2$, and the phase-space weight $w$ for each phase-space point; 4-tuples are sufficient to reconstruct the differential cross sections.
 For each combination $(a,b,k,l,m,n,o)$ (see section~\ref{sec:multi-coupling-expansion} for their definition) we save the following 4-tuples,
@@
 \end{equation}
-The reconstruction of the differential cross section is then done by simply multiplying the phase-space weights $w$ with PDFs evaluated with the correct arguments given in the 4-tuple and summing over all indices $a$, $b$, $k$, $l$, $m$, $n$, $o$, and $i$.
+The reconstruction of the differential cross sections are then done by simply multiplying the phase-space weights $w$ with PDFs evaluated with the correct arguments given in the 4-tuple and summing over all indices $a$, $b$, $k$, $l$, $m$, $n$, $o$, and $i$.
 
@@
 With increasing size also the speed of the convolution degrades, because it basically becomes bound by the speed with which the 4-tuples can be read from disk.
-However, due to the uncompressed nature of this representation it can serve as an intermediate format to develop and quickly cross check more space-efficient representations, which we will discuss next.
+However, due to the uncompressed nature of this representation it can serve as an intermediate format to develop and quickly cross check more space-efficient representations, one of which we will discuss next.
 
-\paragraph{Lagrange-interpolation grid}
+\paragraph{Lagrange-interpolation grid.}
 A different strategy is to partition a subset $H$ of the $(x_1, x_2, Q^2)$ space,
@@
 along each axis into a small number of bins and to insert the phase-space weights $w$ into the corresponding discrete bin.
-Using the bin centres and their values one already has a straightforward implementation of eq.~\eqref{eq:weight-map}, but given a finite number of bins usually yields an insufficient approximation for the cross section.
+Using the bin centres and their values one already has a straightforward representation of eq.~\eqref{eq:weight-map}, but given a finite number of bins this approach usually yields an insufficient approximation for the cross section.
 Increasing the number of bins improves the precision, but it also increases the space requirements.
-Interpolation methods increase the precision using the same number of bins.
+This problem in turn in solved using interpolation methods, which increase the precision using the same number of bins.
 
-We use the same \enquote{Lagrange-interpolation grid} presented in ref.~\cite{Carli:2010rw} with the parameters published in ref.~\cite{Bertone:2014zva}, which give sufficient precision (see section~\ref{sec:results}).
+We use the \enquote{Lagrange-interpolation grid} method presented in ref.~\cite{Carli:2010rw} with the parameters published in ref.~\cite{Bertone:2014zva}, which give sufficient precision (see section~\ref{sec:results}).
 For the sake of completeness, the following summarises the interpolation algorithm.
@@
 The interpolation order $s_y$ then defines a square with length $s_y + 1$ around its centre $(u(y(x_1)),u(y(x_2)))$, given by the MC.
-All grid points with indices $(i,j)$ covered by the grey square are then updated according to the following formula:
+All grid points with indices $(i,j)$ covered by the grey square are then updated according to the following formula,
 \begin{equation}
-a_{i,j} \leftarrow a_{i,j} + I_i(u(y(x_1))) I_j(u(y(x_2))) W(x_1,x_2) / \omega(x_1,x_2)
+a_{i,j} \leftarrow a_{i,j} + I_i(u(y(x_1))) I_j(u(y(x_2))) W(x_1,x_2) / \omega(x_1,x_2) \text{,}
 \label{eq:interpolation}
 \end{equation}
-with the Lagrange basis functions
+with the Lagrange basis functions,
 \begin{equation}
-I_i (u) = \prod_{\substack{k=k_i \\ k \neq i}}^{k_i + s_y} \frac{u-k}{i-k}
+I_i (u) = \prod_{\substack{k=k_i \\ k \neq i}}^{k_i + s_y} \frac{u-k}{i-k} \text{,}
 \end{equation}
 where the product runs over all indices of the grid points covered by the grey square in figure~\ref{fig:grid}, starting from the smallest index in the square, $k_i$ and $k_j$.
-Finally, we remapped
+Finally, we remap
 \begin{equation}
@@
 \end{equation}
-using $y_\text{min} = y(x_\text{max})$ and $y_\text{max} = y(x_\text{min})$ and the grid spacing $\Delta y = (y_\text{max} - y_\text{min})/(N_y-1)$, so that the integer part of $u(y)$ gives the grid index, e.g.\ $u(y_\text{min}) = 0$ and $u(y_\text{max}) = N_y - 1$, and the fractional part gives the location between the nearest grid points.
+using $y_\text{min} = y(x_\text{max})$ and $y_\text{max} = y(x_\text{min})$ and the grid spacing $\Delta y = (y_\text{max} - y_\text{min})/(N_y-1)$, so that the integer part of $u(y)$ gives the grid point index, e.g.\ $u(y_\text{min}) = 0$ and $u(y_\text{max}) = N_y - 1$, and the fractional part of $u(y)$ gives the relative location between the nearest grid points.
 
@@
 
-In section~\ref{sec:multi-coupling-expansion} we labelled the different perturbative orders using the indices $k,l,m,n$.
-Their values are process specific.
+In section~\ref{sec:multi-coupling-expansion} we labelled the different perturbative orders using the indices $k,l,m,n$; their values are process specific.
 However, in general we define as leading order (LO) the set of contributions for all possible initial states $a b$ that lead to the same final state $X$, for which the sum of the coupling exponents in eq.~\eqref{eq:expansion} is smallest, i.e.\ $k + l = p$, where $p = \min (k+l)$.
-This number is also process dependent and is usually determined by the number of external particles.
+This number is usually determined by the number of external particles.
 For many processes there is only one contribution at LO (in terms of $k$ and $l$), but this is not true in general.
-Indeed, when a process has multiple quark lines, colourless (photons, \dots) and coloured particles (gluons, \ldots) can be exchanged between them, making it possible to have more than one combinations of $\alphas$ and $\alpha$.
+Indeed, when a process has multiple quark lines, colourless (photons, \dots) and coloured particles (gluons, \ldots) can be exchanged between them, making it possible to have more than one combination of $\alphas$ and $\alpha$.
 A typical example at the LHC is (on-shell) top-pair production, which has three different contributions at LO: $\mathcal{O} (\alpha^2)$, $\mathcal{O} (\alphas \alpha)$, and $\mathcal{O} (\alpha^2)$.

### 2020-08-28 paper/sec-results.tex
Add last-minute changes to section 3

@@
 affect the accuracy of the theoretical predictions.
-In order to consider some realistic kinematics for these
+In order to consider realistic kinematics for these
 processes, we rely on a representative set of LHC measurements. Our aim is twofold. First, we want to validate the results
@@
 of any hadronic jet produced in the final state: 
- in particular, photon-induced (PI) contributions are consistently included at LO and NLO.\footnote{We employ the $\overline{G}_\mu$ scheme also for the QED coupling entering vertices involving initial-state photons, see section~4.3.3 of ref.\cite{Denner:2019vbn}.}
+ in particular, photon-induced (PI) contributions are consistently included at LO and NLO.\footnote{We employ the $\overline{G}_\mu$ scheme also for the QED coupling entering vertices involving initial-state photons, see section~4.3.3 of ref.~\cite{Denner:2019vbn}.}
 We use a PDF set that contains a photon PDF, namely
@@
 we allow the events to be reweighted on-the-fly in the Monte Carlo generation upon scale
-variations, with the technique presented in Ref.~\cite{Frederix:2011ss}. To this purpose, we use the default \textsc{mg5\_aMC}
+variations, with the technique presented in ref.~\cite{Frederix:2011ss}. To this purpose, we use the default \textsc{mg5\_aMC}
 implementation, whereby the factorisation and renormalisation scales
@@
 about \SI{3.6}{\percent} in the highest bin.\footnote{For the \texttt{MRST2004qed} PDF set~\cite{Martin:2004dh}, which is used to subtract PI contributions (see section~\ref{sec:doublecounting}), the value in the highest bin is roughly twice as large, \SI{6.9}{\percent} (also in absolute numbers).}
-Overall, the EW corrections range between \SI{5}{\percent}
-around $M_{\ell\bar\ell}\sim \SI{150}{\giga\electronvolt}$, \SIrange{2}{3}{\percent} for intermediate invariant mass
+Overall, the EW corrections range between \SI{-5}{\percent}
+around $M_{\ell\bar\ell}\lesssim \SI{150}{\giga\electronvolt}$, \SIrange{-2}{-3}{\percent} for intermediate invariant mass
 values, $\SI{150}{\giga\electronvolt}\lesssim M_{\ell\bar\ell}\lesssim \SI{700}{\giga\electronvolt}$, and
-\SIrange{15}{20}{\percent} for the largest invariant mass bin, $M_{\ell\bar\ell}>\SI{1000}{\giga\electronvolt}$,
+\SIrange{-6}{-10}{\percent} for the largest invariant mass bin, $M_{\ell\bar\ell}>\SI{1000}{\giga\electronvolt}$,
 see figure~\ref{fig:atlaszhighmass49fb}. For this reason, the data points with
@@
 the $\SI{200}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ bin, the suppression increases further to
-about \SIrange{6}{7}{\percent} for rapidities $y_{\ell\bar\ell}<2.0$ and up to \SIrange{20}{40}{\percent} at forward
-rapidities. For this reason, for instance, the data points with
+about \SIrange{6}{7}{\percent} for rapidities $y_{\ell\bar\ell}<2.0$. For this reason, for instance, the data points with
 $M_{\ell\bar\ell}>\SI{200}{\giga\electronvolt}$ and $y_{\ell\bar\ell}>2.2$ were not included in the

### 2020-09-03 nnpdf31_proc/CMSDY2D11/analysis.f
Add small fixes
- removed single-precision pollution
- use `mll_sf` instead of `mll` (no difference here)

@@ -25,7 +25,7 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
       implicit none
       double precision dummy
       call HwU_write_file
-      return                
+      return
       end
 
 cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
@@ -96,10 +96,10 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
         maxmll=1500d0
       endif
 
-      call HwU_fill(bin,minmll*2.4+xyll*(maxmll-minmll),wgts)
+      call HwU_fill(bin,minmll*2.4d0+xyll*(maxmll-minmll),wgts)
 
 
- 999  return      
+ 999  return
       end
 
 cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
@@ -136,4 +136,3 @@ c
       getabsy=tmp
       return
       end
-

### 2020-09-03 paper/sec-introduction.tex
Addressed Valerio's complaint

@@
 library is interfaced to \textsc{MadGraph5\_aMC@NLO} (\textsc{mg5\_aMC}
-henceforth), with which it has been developed and tested. In this respect,
-\textsc{PineAPPL} supersedes
-\textsc{APPLgrid}+\textsc{aMCfast}~\cite{Bertone:2014zva}.
-However, \textsc{PineAPPL} can also be easily interfaced to any Monte Carlo generator,
-e.g.\ \textsc{SHERPA}~\cite{Biedermann:2017yoi}, where it would complement
+henceforth), with which it has been developed and tested,
+however it can be easily used with any Monte Carlo generator, 
+e.g.\ \textsc{SHERPA}~\cite{Biedermann:2017yoi}. In this respect,
+\textsc{PineAPPL} extends to EW corrections the scope of 
+\textsc{aMCfast}~\cite{Bertone:2014zva} and
 \textsc{MCgrid}~\cite{DelDebbio:2013kxa,Bothmann:2015dba}.

### 2020-09-03 paper/sec-pineappl.tex
Fix last-minute changes
Addressed Valerio's complaint

@@
 
-\item \textsc{PineAPPL} has been explicitly interfaced to \textsc{mg5\_aMC} (v3+)~\cite{Alwall:2014hca,Frederix:2018nkq},\footnote{A version of \textsc{mg5\_aMC} interfaced to \textsc{PineAPPL} can be downloaded from \url{https://launchpad.net/mg5amc-pineappl/trunk}, and it will be included as standard in the next \textsc{mg5\_aMC} release.} for which it supersedes \textsc{aMCfast}~\cite{Bertone:2014zva}; see appendix~\ref{app:sample-runcard} for an example of a runcard.
+\item \textsc{PineAPPL} has been explicitly interfaced to \textsc{mg5\_aMC} (v3+)~\cite{Alwall:2014hca,Frederix:2018nkq},\footnote{A version of \textsc{mg5\_aMC} interfaced to \textsc{PineAPPL} can be downloaded from \url{https://launchpad.net/mg5amc-pineappl/trunk}, and it will be included as standard in the next \textsc{mg5\_aMC} release.} see appendix~\ref{app:sample-runcard} for an example of a runcard.
 While the usage of
@@
 Increasing the number of bins improves the precision, but it also increases the space requirements.
-This problem in turn in solved using interpolation methods, which increase the precision using the same number of bins.
+This problem in turn is solved using interpolation methods, which increase the precision using the same number of bins.
 

### 2020-09-03 nnpdf31_proc/ATLAS_DY3D_8TEV/analysis.f
Implement proper bin limits and CS angle

@@ -8,13 +8,15 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
 
       call set_error_estimation(1)
       call HwU_inithist(nwgt,weights_info)
-      call HwU_book(1,'lmlp m yrap cos theta', 12,  46d0*2.4d0,   66d0*2.4d0)
-      call HwU_book(2,'lmlp m yrap cos theta', 12,  66d0*2.4d0,   80d0*2.4d0)
-      call HwU_book(3,'lmlp m yrap cos theta', 12,  80d0*2.4d0,   91d0*2.4d0)
-      call HwU_book(4,'lmlp m yrap cos theta', 12,  91d0*2.4d0,  102d0*2.4d0)
-      call HwU_book(5,'lmlp m yrap cos theta', 12, 102d0*2.4d0,  116d0*2.4d0)
-      call HwU_book(6,'lmlp m yrap cos theta', 12, 116d0*2.4d0,  150d0*2.4d0)
-      call HwU_book(7,'lmlp m yrap cos theta', 12, 150d0*2.4d0,  200d0*2.4d0)
+c     each HwU contains a complete invariant mass slice, with 12 rapidities bins, and 6 bins of the
+c     CS angle for each rapidity bin
+      call HwU_book(1,'dist', 12*6,  46d0*2.4d0*2d0,  66d0*2.4d0*2d0)
+      call HwU_book(2,'dist', 12*6,  66d0*2.4d0*2d0,  80d0*2.4d0*2d0)
+      call HwU_book(3,'dist', 12*6,  80d0*2.4d0*2d0,  91d0*2.4d0*2d0)
+      call HwU_book(4,'dist', 12*6,  91d0*2.4d0*2d0, 102d0*2.4d0*2d0)
+      call HwU_book(5,'dist', 12*6, 102d0*2.4d0*2d0, 116d0*2.4d0*2d0)
+      call HwU_book(6,'dist', 12*6, 116d0*2.4d0*2d0, 150d0*2.4d0*2d0)
+      call HwU_book(7,'dist', 12*6, 150d0*2.4d0*2d0, 200d0*2.4d0*2d0)
 
       return
       end
@@ -49,7 +51,7 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
       external getinvm
       external getabsy
       external getcostheta
-      integer bin
+      integer bin,xcosbin
       double precision minmll, maxmll
 
[…]

### 2020-09-05 paper/sec-pineappl.tex
Clarify the comparison with APPLgrid

@@
 \item \textsc{PineAPPL} has been explicitly interfaced to \textsc{mg5\_aMC} (v3+)~\cite{Alwall:2014hca,Frederix:2018nkq},\footnote{A version of \textsc{mg5\_aMC} interfaced to \textsc{PineAPPL} can be downloaded from \url{https://launchpad.net/mg5amc-pineappl/trunk}, and it will be included as standard in the next \textsc{mg5\_aMC} release.} see appendix~\ref{app:sample-runcard} for an example of a runcard.
-While the usage of
-\textsc{mg5\_aMC}(v3+) + \textsc{PineAPPL} is similar to that of 
-\textsc{mg5\_aMC}(v2) + \textsc{aMCfast} + \textsc{APPLgrid}, it is however more
-efficient.
-For instance, the usage of the latter typically required a substantial amount of memory (close to \SI{120}{\giga\byte} for Drell--Yan), if a grid for a differential distribution with more than 10 bins was generated.
-The memory usage is substantially reduced (roughly \SI{1}{\giga\byte}) after \enquote{optimisation} of the grids, i.e.\ an optimisation of the grid representation in memory.
-However, this required a two-step procedure: first, to produce an unoptimised grid in order to identify those parts where the cross section is either zero or extremely suppressed; second, after those parts are removed, to fill an optimised grid with a small number of bins.
+The usage of \textsc{mg5\_aMC}(v3+) + \textsc{PineAPPL} is similar to that of \textsc{mg5\_aMC}(v2) + \textsc{aMCfast} + \textsc{APPLgrid}.
+While the latter toolchain proved to be sufficiently efficient for NLO QCD calculations of typical kinematic distributions (with a few bins), this is longer so when taking into account NLO EW calculations and, with more precise data, distributions that are typically more complex and have more bins.
+Taking into account these two reasons, we find that the memory usage of \textsc{APPLgrid} is no longer satisfiable.
+In particular, using \textsc{APPLgrid} for NLO QCD+EW\footnote{For this a modified version of \textsc{APPLgrid} was developed which added support for photon-initiated processes and EW corrections.} typically requires close to \SI{120}{\giga\byte} for high-mass Drell--Yan with 13 bins (see section~\ref{sec:dy-lepton-pair-production}).
+The memory usage is substantially reduced to roughly \SI{1}{\giga\byte} after \enquote{optimisation} of the grids, i.e.\ an optimisation of the grid representation in memory.
+However, this requires a two-step procedure: first, to produce an unoptimised grid in order to identify those parts where the cross section is either zero or extremely suppressed; second, after those parts are removed, to fill an optimised grid with a small number of bins.
 \textsc{PineAPPL} avoids this by using a more space-efficient representation from the start.

### 2020-09-05 paper/paper.tex
Remove xltabular package
Fix a warning
Added V. Bertone in the acknowledgements

@@
 \usepackage{lmodern}
-\usepackage[binary-units=true,detect-weight=true,digitsep=none,table-format=4.2]{siunitx}
+\usepackage[binary-units=true,detect-weight=true,group-digits=false,table-format=4.2]{siunitx}
 \usepackage{xcolor}
@@
 \usepackage{textcomp}
-\usepackage{xltabular}
 
@@
 \acknowledgments
-We would like to thank Stefan Dittmaier, Stefano Forte, Zahari Kassabov, Davide Pagani, and Juan Rojo for a critical reading of the manuscript, and Rikkert Frederix for discussions about \textsc{aMCfast}.
+We would like to thank Valerio Bertone, Stefan Dittmaier, Stefano Forte, Zahari Kassabov, Davide Pagani, and Juan Rojo for a critical reading of the manuscript, and Rikkert Frederix for discussions about \textsc{aMCfast}.
 We also acknowledge discussions with

### 2020-10-13 paper/app-pineappl.tex
Address issues 3, 4, 6, 9, and 11 of the referee

@@
 --+------------+------------
-0  1 × ( 2, -2) 1 × ( 4, -4)
-5  1 × ( 1, -1) 1 × ( 3, -3)
-15 1 × (-4,  4) 1 × (-2,  2)
-20 1 × (-3,  3) 1 × (-1,  1)
-30 1 × (22, 22)
+0  1 x ( 2, -2) 1 x ( 4, -4)
+5  1 x ( 1, -1) 1 x ( 3, -3)
+15 1 x (-4,  4) 1 x (-2,  2)
+20 1 x (-3,  3) 1 x (-1,  1)
+30 1 x (22, 22)
 \end{verbatim}
@@
 The following run card was used to produce the results shown in section~\ref{sec:dy-lepton-pair-production}.
-The only difference with respect to a standard \textsc{mg5\_aMC} run is the switch \texttt{set iappl 1}, which enables to fill a \textsc{PineAPPL} grid.
+The only difference with respect to a standard \textsc{mg5\_aMC} run is the switch \texttt{set pineappl True}, which enables to fill a \textsc{PineAPPL} grid.
 For a complete set of runcards and patches see \url{https://n3pdf.github.io/pineappl}.
@@
 set req_acc_FO 0.0001
-set iappl 1
+set pineappl True
 done

### 2020-10-13 paper/sec-doublecounting.tex
Clarified that our recommendation is not the ultimate one
Address issues 3, 4, 6, 9, and 11 of the referee

@@
 guidelines to facilitate this task. We focus on the problem of data with (partially) subtracted EW effects, which, if compared to theory predictions including them, leads to a double counting issue.
+Our guidelines are intended to make the reader aware of an
+emerging new issue, whose definitive solution remains however beyond the scope
+of this work.
 
@@
 to processes such as neutral- or charged-current Drell--Yan, especially when electrons are considered. The problem lies in the fact that
- electrons, and to a lesser extent muons, tend to radiate photons, which are not accounted
+ electrons, and to a lesser extent muons, tend to radiate collinear photons, which are not accounted
 for in QCD-only matrix elements. Thus, leptons that are measured in the detector are less energetic, and this fact is compensated for

### 2020-10-13 paper/sec-pineappl.tex
Remove indentation
Address issues 3, 4, 6, 9, and 11 of the referee

@@
 \end{itemize}
-
 On a more technical level, we point out the following additional features of \textsc{PineAPPL}.
@@
 The usage of \textsc{mg5\_aMC}(v3+) + \textsc{PineAPPL} is similar to that of \textsc{mg5\_aMC}(v2) + \textsc{aMCfast} + \textsc{APPLgrid}.
-While the latter toolchain proved to be sufficiently efficient for NLO QCD calculations of typical kinematic distributions (with a few bins), this is longer so when taking into account NLO EW calculations and, with more precise data, distributions that are typically more complex and have more bins.
+While the latter toolchain proved to be sufficiently efficient for NLO QCD calculations of typical kinematic distributions (with a few bins), this is no longer so when taking into account NLO EW calculations and, with more precise data, distributions that are typically more complex and have more bins.
 Taking into account these two reasons, we find that the memory usage of \textsc{APPLgrid} is no longer satisfiable.

### 2020-10-13 paper/sec-results.tex
Address issues 3, 4, 6, 9, and 11 of the referee

@@
 M_\mathrm{W} &= \SI{80.419}{\giga\electronvolt} \text{,} \quad &
+\Gamma_\mathrm{W} &= \SI{2.09291}{\giga\electronvolt} \text{,} &
+m_\mathrm{t} &= \SI{172.5}{\giga\electronvolt} \text{,} \quad \\
 M_\mathrm{Z} &= \SI{91.176}{\giga\electronvolt} \text{,} \quad &
-m_\mathrm{t} &= \SI{172.5}{\giga\electronvolt} \text{,} \quad \\
-\Gamma_\mathrm{W} &= \SI{2.09291}{\giga\electronvolt} \text{,} &
 \Gamma_\mathrm{Z} &= \SI{2.49877}{\giga\electronvolt} \text{,} &
-G_\mu &= \SI{1.16639e-5}{\per\giga\electronvolt\squared} \text{,}
+G_\mu &= \SI{1.16639e-5}{\per\giga\electronvolt\squared} \text{,} \\
+M_\mathrm{H} &= \SI{125}{\giga\electronvolt} \text{,} &
+\Gamma_\mathrm{H} &= \SI{4.074680e-03}{\giga\electronvolt} \text{,}
 \end{aligned}
@@
 \end{equation}
-where $M_\mathrm{Z}$, $M_\mathrm{W}$, $m_\mathrm{t}$ are the values of the Z-boson, W-boson, and
-top-quark masses, respectively, $\Gamma_\mathrm{Z}$ and $\Gamma_\mathrm{W}$ are the widths of
-the Z and W bosons, and $G_\mu$ is the value of the Fermi coupling. The value of the strong
+where $M_\mathrm{Z}$, $M_\mathrm{W}$, $M_\mathrm{H}$, $m_\mathrm{t}$ are the values of the Z-, W-, Higgs-boson
+and top-quark masses, respectively, $\Gamma_\mathrm{Z}$, $\Gamma_\mathrm{W}$, $\Gamma_\mathrm{H}$ are the widths of
+the Z, W and Higgs bosons, and $G_\mu$ is the value of the Fermi coupling. The value of the strong
 coupling is chosen consistently with the PDF set, $\alphas(M_\mathrm{Z})=0.118$.
@@
 NNLO QCD corrections, which are already well
-known~\cite{Boughezal:2015ded,Boughezal:2016isb,Boughezal:2016yfp,Ridder:2015dxa,Ridder:2016nkl,Gehrmann-DeRidder:2017mvr,Bizon:2019zgf}
+known~\cite{Boughezal:2015ded,Boughezal:2016isb,Boughezal:2016yfp,Ridder:2015dxa,Ridder:2016nkl,Gehrmann-DeRidder:2017mvr,Bizon:2019zgf}.
 Analogous measurements,

### 2020-10-13 paper/sec-doublecounting.tex
points 8, 10 of the report

@@
 includes both kind of topologies discussed above, and needs both in order to yield an IR-finite result, see Fig.~\ref{fig:dy-pi} (as a consequence, one cannot speak of EW corrections to $\gamma \gamma \to \ell \bar{\ell}$).
-While it is common sense that the QCD counterpart of this subtraction should never
-be performed --- no one would
-consider to \enquote{subtract} the gluon-initiated contribution to top-pair production in top analyses --- seemingly it is not so
-when EW corrections are considered.
+It may be useful for the reader to consider a QCD counterpart of this issue,
+e.g. the subtraction of gluon-initiated contribution to top-pair production, in order to get convinced of the incorrectness of this procedure.
 

### 2020-10-13 paper/sec-results.tex
points 8, 10 of the report

@@
 the settings employed for the computations, the corresponding results for
-each process, and possible implications for the determination of PDFs.
+each process, and possible implications for the determination of PDFs. It is worth to mention
+that, in those phase-space regions where both NLO QCD and EW corrections are sizeable, the NNLO
+correction at $\mathcal O (\alphas \alpha)$ is also expected to be important, and has either to
+be included, when it is known exactly or at least in some approximate way, or to be accounted for 
+as an extra uncertainty. We leave this aspect to future studies
 
@@
 $\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$ contributions.
-Combined QCD--EW corrections occur only at NNLO, and are therefore not
+Combined QCD--EW corrections occur only at NNLO~\cite{Buccioni:2020cfi}, and are therefore not
 considered here. EW corrections for this process were computed in

### 2020-10-14 paper/sec-introduction.tex
Addressed point 1 in the referee reprot

@@
 optimised, except for QED effects if a photon PDF is 
-determined~\cite{Schmidt:2015zda,Manohar:2016nzj,Manohar:2017eqh,Bertone:2017bme,Harland-Lang:2019pla}.
+determined~\cite{Martin:2004dh,Ball:2013hta,Schmidt:2015zda,Manohar:2016nzj,Manohar:2017eqh,Bertone:2017bme,Harland-Lang:2019pla}. The QED contribution is
+included in the matrix element (at the lowest order for the LHC
+processes considered) and in the DGLAP splitting
+functions at leading order~\cite{Bertone:2013vaa}. Inclusion of NLO QCD--QED
+combined corrections in the evolution is in principle also
+possible~\cite{deFlorian:2015ujt}, and should be required to analyse the data
+within consistent pertubatibe accuracy if higher-order EW and QCD corrections
+are also included in partonic cross sections.
 The resulting relative PDF uncertainty --- which accounts only for the

### 2020-10-14 paper/sec-results.tex
referee's point 5 (references for ttbar NLO EW)

@@
 EW corrections for this process
-were computed in refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Denner:2016jyo,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Frederix:2018nkq,Czakon:2019bcq,Czakon:2019txp}.
+were computed in refs.~\cite{Kuhn:2006vh,Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Denner:2016jyo,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Gutschow:2018tuk,Frederix:2018nkq,Czakon:2019bcq,Czakon:2019txp}.
 The process receives contributions from

### 2020-10-14 paper/sec-doublecounting.tex
Fix fixes

@@
 It may be useful for the reader to consider a QCD counterpart of this issue,
-e.g. the subtraction of gluon-initiated contribution to top-pair production, in order to get convinced of the incorrectness of this procedure.
+e.g.\ the subtraction of the gluon-initiated contribution to top-pair production, in order to convince themselves of the incorrectness of this procedure.
 

### 2020-10-14 applcheck.cpp

@@ -106,7 +106,7 @@ int main(int argc, char* argv[])
     // check if PDF set has a photon; disable it this isn't the case
     flavour_map[photon] = pdf->hasFlavor(index_to_pdg_id(photon));
 
-    std::vector<double> const& xsecs = g.vconvolute(evolvepdf, alphaspdf);
+    std::vector<double> const& xsecs = g.vconvolute(evolvepdf, alphaspdf, 1);
 
     std::cout << "\n>>> all bins:\n\n";
 

### 2020-10-14 paper/answer_to_the_editor.txt
Add preliminary answer to the editor/referee

Dear Editor,

We would like to thank the referee for carefully reading the manuscript and
making useful comments and suggestions.

In the following our answers to the issues raised by the referee:

- Issues 1, 3, 4, 5, 6, 8, 9, and 11 have all been addressed as suggested or
  corrected otherwise.
- Issue 2: The decomposition of the fixed-order expansion written down in eq.
  (2.1) holds to all orders in both the strong and electroweak coupling, and
  therefore the mentioned sentence is correct—it only concerns PineAPPL. The
  Monte Carlo that we used is tied to NLO, of course.
- Issue 7:
- Issue 10:
- Issue 12: Although we agree with the referee that the mentioned tables are
  interesting only to a few readers, the main text refers to it in a few
  places and therefore removing it from the main document would require bigger
  changes. We see no harm in leaving the tables in the document and therefore
  decided to keep them.

Note that all changes have been highlighted in red in the text.

With these changes, we hope that the current version will meet the criteria of
publication of JHEP.

Best regards,
The authors

### 2020-10-14 paper/answer_to_the_editor.txt
added comment on point 10

@@
 - Issue 7:
-- Issue 10:
+- Issue 10: A brief discussion on this matter has been added at the beginning
+  of section 3. The reference suggested (Buccioni:2020cfi), is cited in section 
+  3.2.1, in the discussion relevant for Drell-Yan.
 - Issue 12: Although we agree with the referee that the mentioned tables are

### 2020-10-16 paper/app-pineappl.tex
Reintroduces multiplication signs
- with correct encoding this should work now
Fix errors found by `lacheck`

@@
 --+------------+------------
-0  1 x ( 2, -2) 1 x ( 4, -4)
-5  1 x ( 1, -1) 1 x ( 3, -3)
-15 1 x (-4,  4) 1 x (-2,  2)
-20 1 x (-3,  3) 1 x (-1,  1)
-30 1 x (22, 22)
+0  1 × ( 2, -2) 1 × ( 4, -4)
+5  1 × ( 1, -1) 1 × ( 3, -3)
+15 1 × (-4,  4) 1 × (-2,  2)
+20 1 × (-3,  3) 1 × (-1,  1)
+30 1 × (22, 22)
 \end{verbatim}
@@
 
-The following listing shows how to setup \textsc{PineAPPL} using its C interface in a simple Monte Carlo integrator for calculating the double-photon contribution to Drell--Yan lepton-pair production at the LHC.
+The following listing shows how to setup \textsc{PineAPPL} using its C interface in a simple Monte Carlo integrator for calculating the double-photon contribution to Drell--Yan lepton-pair production at the LHC\@.
 All \textsc{PineAPPL} functions have the prefix \texttt{pineappl\_}.

### 2020-10-16 paper/sec-pineappl.tex
Fix errors found by `lacheck`

@@
 We have defined the grid points at specific positions, but the points given by the MC will land somewhere between them.
-The interpolation order $s_y$ then defines a square with length $s_y + 1$ around its centre $(u(y(x_1)),u(y(x_2)))$, given by the MC.
+The interpolation order $s_y$ then defines a square with length $s_y + 1$ around its centre $(u(y(x_1)),u(y(x_2)))$, given by the MC\@.
 All grid points with indices $(i,j)$ covered by the grey square are then updated according to the following formula,
@@
 Note that all initial states have to be taken into account that lead to the same final state.
-This includes the photon--photon initial state, which appears already at LO.
+This includes the photon--photon initial state, which appears already at LO\@.
 In the corresponding Feynman diagrams all particles are colourless, so that the photon--photon initiated contributions only receive EW corrections.

### 2020-10-16 paper/sec-results.tex
Fix fixes
Fix errors found by `lacheck`

@@
 be included, when it is known exactly or at least in some approximate way, or to be accounted for 
-as an extra uncertainty. We leave this aspect to future studies
+as an extra uncertainty. We leave this aspect to future studies.
 
@@
 scale-uncertainty envelope, for
-theories accurate to both NLO QCD and NLO QCD+EW. The following three panels
+theories accurate to both NLO QCD and NLO QCD+EW\@. The following three panels
 present the theoretical predictions, accurate to either NLO QCD or NLO QCD+EW,
@@
       and the MC results for the central, upper and lower scale choices,
-      for theories accurate to both NLO QCD and NLO QCD+EW. The second, third
+      for theories accurate to both NLO QCD and NLO QCD+EW\@. The second, third
       and fourth panels present the theoretical predictions, accurate to either

### 2020-10-22 paper/sec-results.tex
Implement first changes for issue 7

@@
 
-As in the case of Drell-Yan, we use a fixed value for the renormalisation and
-factorisation scales $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$, where
-$M_\mathrm{Z}$ is the Z-boson mass. Consistently with the
+We choose a dynamic value for the renormalisation and factorisation scales $\mu_\mathrm{R}=\mu_\mathrm{F}=\sqrt{M_{\ell \bar{\ell}}^2 + \left( p_\mathrm{T}^{\ell \bar{\ell}} \right)^2}$, used for example in ref.~\cite{Ridder:2016nkl}, where $M_{\ell \bar{\ell}}$ is the invariant mass of the lepton pair and $p_\mathrm{T}^{\ell \bar{\ell}}$ the transverse momentum of it.\footnote{In the last bin the dynamic scale is $\mu_\mathrm{R} = \mu_\mathrm{F} \approx p_\mathrm{T}^{\ell \bar{\ell}}$, and therefore the bin limits drive the scale beyond the limit $Q_\text{max}^2 = (\SI{1}{\tera\electronvolt})^2$ defined in sec.~\ref{sec:grid-representation}, which we increase for this process to $Q_\text{max}^2 = (\SI{10}{\tera\electronvolt})^2$, along with $N_\tau = 40$.}
+Consistently with the
 experimental analysis, we require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$,
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMS_Z_13_TEV}
+    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMS_Z_13_TEV_dyn}
     \caption{Same as figure~\ref{fig:atlaszhighmass49fb} but for the 

### 2020-10-26 paper/sec-results.tex
Add more adjustments for issue 7

@@
 The process receives its leading contribution from $\mathrm{qg}$- and
-$\bar{\mathrm{q}}\mathrm{g}$-initiated channels, which account for about \SI{65}{\percent}
+$\bar{\mathrm{q}}\mathrm{g}$-initiated channels, which account for about \SI{79}{\percent}
 of the cross section, with some variations in the relative contributions from
@@
 Overall, the EW corrections suppress the theoretical predictions by about
-\SIrange{2}{10}{\percent} as the transverse momentum of the Z boson increases.
-The size of this shift is as large as the data uncertainty up to
-$p_{\mathrm{T}}^{\ell\bar\ell}\sim \SI{200}{\giga\electronvolt}$, and 
-exceeds it by about \SI{60}{\percent} at larger values of
-$p_\mathrm{T}^{\ell \bar{\ell}}$. As a consequence,
+\SIrange{2}{15}{\percent} as the transverse momentum of the Z boson increases.
+The size of this shift is as large (or slightly larger) as the data uncertainty over
+the entire range of $p_{\mathrm{T}}^{\ell\bar\ell}$. As a consequence,
 we anticipate the inclusion of EW corrections to be relevant for an accurate
@@
 
-The size of the EW correction is between four and twenty times larger than the
+The size of the EW correction is between four and fifteen times larger than the
 size of the PDF uncertainty: as previously noted in the other cases, this fact
@@
 roughly $p_{\mathrm{T}}^{\ell\bar\ell}\lesssim\SI{400}{\giga\electronvolt}$, while it
-becomes up to four times larger than it in the two bins at the largest value of
+becomes larger than it in the two bins at the largest value of
 $p_{\mathrm{T}}^{\ell\bar\ell}$. In this kinematic region, NLO EW corrections might

### 2020-10-26 paper/answer_to_the_editor.txt
Update answer to the editor

@@
 
+For convenience all changes are marked in the pre-compiled document as
+red/strikethrough (removed text) and blue/underlined (added text).
+
 In the following our answers to the issues raised by the referee:
 
-- Issues 1, 3, 4, 5, 6, 8, 9, and 11 have all been addressed as suggested or
+- Issues 1, 3, 4, 5, 6, 8, 9, and 11 have all been addressed as suggested, or
   corrected otherwise.
@@
   (2.1) holds to all orders in both the strong and electroweak coupling, and
-  therefore the mentioned sentence is correct—it only concerns PineAPPL. The
-  Monte Carlo that we used is tied to NLO, of course.
-- Issue 7:
+  therefore the mentioned sentence is correct, as it only concerns PineAPPL.
+  The Monte Carlo that we used is limited to NLO, of course.
+- Issue 7: For Drell-Yan we checked that a dynamical scale set to Mll does
+  change the NLO QCD in the largest invariant mass bins and therefore also the
+  scale uncertainty. In comparison to the shown data uncertainty the changes
+  are very minor, and therefore we did not update plots and text.
+  For the Z transverse momentum process we did update the both plots and text,
+  where we indeed see a significant increase of the scale variation band in
+  the large transverse momentum bins. The electroweak corrections are also
+  smaller, since we normalise to NLO QCD.
 - Issue 10: A brief discussion on this matter has been added at the beginning
@@
 
-Note that all changes have been highlighted in red in the text.
-
 With these changes, we hope that the current version will meet the criteria of

### 2020-10-26 paper/sec-introduction.tex
Add final changes to the text

@@
 possible~\cite{deFlorian:2015ujt}, and should be required to analyse the data
-within consistent pertubatibe accuracy if higher-order EW and QCD corrections
+within consistent perturbative accuracy if higher-order EW and QCD corrections
 are also included in partonic cross sections.

### 2021-03-09 paper2/paper.tex
Add skeleton for our 2nd paper

--- 2020-08-26 paper/paper.tex
@@
 
+% load before csquotes
+\usepackage[utf8]{inputenc}
+
 \usepackage[UKenglish]{babel}
-\usepackage{booktabs}
-\usepackage{csquotes}
+%\usepackage{booktabs}
+%\usepackage{csquotes}
 \usepackage{jheppub}
 \usepackage[T1]{fontenc}
-\usepackage{listings}
+%\usepackage{listings}
 \usepackage{lmodern}
-\usepackage[binary-units=true,detect-weight=true,digitsep=none,table-format=4.2]{siunitx}
-\usepackage{xcolor}
-\usepackage[percent]{overpic}
-\usepackage{mathcomp}
-\usepackage{tabularx}
-\usepackage{textcomp}
-\usepackage{xltabular}
+%\usepackage[binary-units=true,detect-weight=true,group-digits=false,table-format=4.2]{siunitx}
+%\usepackage{xcolor}
+%\usepackage[percent]{overpic}
+%\usepackage{mathcomp}
+%\usepackage{tabularx}
+%\usepackage{textcomp}
 
-\newcommand{\alphas}{\alpha_\mathrm{s}}
-\DeclareSIUnit\permille{\text{\textperthousand}}
+%\newcommand{\alphas}{\alpha_\mathrm{s}}
+%\DeclareSIUnit\permille{\text{\textperthousand}}
 
-\preprint{Nikhef-2020-026 TIF-UNIMI-2020-22}
+\preprint{TODO}
 
@@
 
-\abstract{We introduce \textsc{PineAPPL}, a library that produces
-  fast-interpolation grids of physical cross sections, computed with a 
-  general-purpose Monte Carlo generator, accurate to fixed order in the
-  strong, electroweak, and combined strong-electroweak couplings. We
-  demonstrate this unique ability, that distinguishes \textsc{PineAPPL} from
-  similar software available in the literature, by interfacing it to
-  \textsc{MadGraph5\_aMC@NLO}. We compute fast-interpolation grids,
-  accurate to next-to-leading order in the strong and electroweak couplings,
-  for a representative set of LHC processes for which EW corrections may have
-  a sizeable effect on the accuracy of the corresponding theoretical
-  predictions. We formulate a recommendation on the format of the experimental
-  deliverables in order to consistently compare them with computations
-  that incorporate EW corrections, and specifically to determine
-  parton distribution functions to the same accuracy.}
+\abstract{TODO}
+
+%\arxivnumber{}
 
@@
 \input{sec-introduction}
-\input{sec-pineappl}
 \input{sec-results}
-\input{sec-doublecounting}
 \input{sec-conclusion}
@@
 \acknowledgments
-We would like to thank Stefan Dittmaier, Stefano Forte, Zahari Kassabov, Davide Pagani, and Juan Rojo for a critical reading of the manuscript, and Rikkert Frederix for discussions about \textsc{aMCfast}.
-We also acknowledge discussions with
-Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
-treatment of EW effects in experimental data.
-S.C.\ and C.S.\ are supported by the European Research Council under the European Union's
-Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
-E.R.N.\ is supported by the European Commission through a Marie
-Sk\l odowska-Curie Action (grant agreement no.\ 752748).
-M.Z.\ thanks the Nikhef institute in Amsterdam,
-where he was employed when this paper was started.
-
-\input{app-pineappl}
-\input{app-lumis}
-\input{app-addmaterial}
+TODO
 

### 2021-03-26 paper/answer_to_the_editor.txt
Update answer to the editor

@@
 
-For convenience all changes are marked in the pre-compiled document as
+All changes are marked in the pre-compiled document (diff.pdf) as
 red/strikethrough (removed text) and blue/underlined (added text).
@@
   The Monte Carlo that we used is limited to NLO, of course.
-- Issue 7: For Drell-Yan we checked that a dynamical scale set to Mll does
-  change the NLO QCD in the largest invariant mass bins and therefore also the
-  scale uncertainty. In comparison to the shown data uncertainty the changes
-  are very minor, and therefore we did not update plots and text.
-  For the Z transverse momentum process we did update the both plots and text,
-  where we indeed see a significant increase of the scale variation band in
-  the large transverse momentum bins. The electroweak corrections are also
-  smaller, since we normalise to NLO QCD.
+- Issue 7: For Drell-Yan we checked (compare
+  figures/pineappl_ATLASZHIGHMASS49FB.pdf against
+  figures/pineappl_ATLASZHIGHMASS49FB_dyn.pdf) that a dynamical scale set to
+  Mll does change the NLO QCD in the largest invariant mass bins and therefore
+  also the scale uncertainty. However, in comparison to the shown data
+  uncertainty the changes are very minor, and therefore we did not update
+  plots and text. For the Z transverse momentum process we did update both
+  the plot and text, where we indeed see a significant increase of the scale
+  variation band in the large transverse momentum bins. The electroweak
+  corrections are also smaller, since we normalise to NLO QCD.
 - Issue 10: A brief discussion on this matter has been added at the beginning

### 2021-03-26 paper/sec-doublecounting.tex
Fix errors found by `lacheck`

--- 2020-10-13 paper/sec-doublecounting.tex
@@
 \end{quote}
-Such a distinction, which is unphysical and incorrect in quantum mechanics, may be somehow justified at LO. Beyond this order, it is simply wrong.
+Such a distinction, which is unphysical and incorrect in quantum mechanics, may be somehow justified at LO\@. Beyond this order, it is simply wrong.
 Indeed, at $\mathcal O(\alpha^3)$, the reaction $\mathrm{q} \gamma \to \ell \bar{\ell} \mathrm{q}$ becomes possible, which
@@
 It may be useful for the reader to consider a QCD counterpart of this issue,
-e.g. the subtraction of gluon-initiated contribution to top-pair production, in order to get convinced of the incorrectness of this procedure.
+e.g.\ the subtraction of the gluon-initiated contribution to top-pair production, in order to understand the incorrectness of this procedure.
 

### 2021-03-26 paper/sec-results.tex

@@
 
-We choose a dynamic value for the renormalisation and factorisation scales $\mu_\mathrm{R}=\mu_\mathrm{F}=\sqrt{M_{\ell \bar{\ell}}^2 + \left( p_\mathrm{T}^{\ell \bar{\ell}} \right)^2}$, used for example in ref.~\cite{Ridder:2016nkl}, where $M_{\ell \bar{\ell}}$ is the invariant mass of the lepton pair and $p_\mathrm{T}^{\ell \bar{\ell}}$ the transverse momentum of it.\footnote{In the last bin the dynamic scale is $\mu_\mathrm{R} = \mu_\mathrm{F} \approx p_\mathrm{T}^{\ell \bar{\ell}}$, and therefore the bin limits drive the scale beyond the limit $Q_\text{max}^2 = (\SI{1}{\tera\electronvolt})^2$ defined in sec.~\ref{sec:grid-representation}, which we increase for this process to $Q_\text{max}^2 = (\SI{10}{\tera\electronvolt})^2$, along with $N_\tau = 40$.}
+We choose a dynamic value for the renormalisation and factorisation scales $\mu_\mathrm{R}=\mu_\mathrm{F}=\sqrt{M_{\ell \bar{\ell}}^2 + \left( p_\mathrm{T}^{\ell \bar{\ell}} \right)^2}$, used for example in ref.~\cite{Ridder:2016nkl}, where $M_{\ell \bar{\ell}}$ is the invariant mass of the lepton pair and $p_\mathrm{T}^{\ell \bar{\ell}}$ its transverse momentum.\footnote{In the last bin the dynamic scale is $\mu_\mathrm{R} = \mu_\mathrm{F} \approx p_\mathrm{T}^{\ell \bar{\ell}}$, and therefore the bin limits drive the scale beyond the limit $Q_\text{max}^2 = (\SI{1}{\tera\electronvolt})^2$ defined in sec.~\ref{sec:grid-representation}, which we increase for this process to $Q_\text{max}^2 = (\SI{10}{\tera\electronvolt})^2$, along with $N_\tau = 40$.}
 Consistently with the

### 2021-03-26 nnpdf31_proc/CDFZRAP/precheck.sh
Remove obsolete file

@@ -1,8 +1,0 @@
-#!/bin/bash
-
-set -e
-
-pineappl info --set initial_state_2 -2212 "${GRID}".tmp "${GRID}"
-lz4 -9 "${GRID}".tmp
-rm "${GRID}".tmp
-mv "${GRID}".tmp.lz4 "${GRID%.lz4}".lz4

### 2021-03-30 paper2/paper.tex
Add acknowledgements for SC and CS
Add preliminary discussion of DY
Change title

@@
 \usepackage{lmodern}
-%\usepackage[binary-units=true,detect-weight=true,group-digits=false,table-format=4.2]{siunitx}
+\usepackage[binary-units=true,detect-weight=true,group-digits=false,table-format=4.2]{siunitx}
 %\usepackage{xcolor}
@@
 
-\title{PineAPPL: combining EW and QCD corrections\\
-  for fast evaluation of LHC processes}
+\title{TODO}
 
@@
 
-%\arxivnumber{}
+\arxivnumber{TODO}
 
@@
 \input{sec-results}
+\input{sec-datasets}
 \input{sec-conclusion}
@@
 \acknowledgments
-TODO
+S.C.\ and C.S.\ are supported by the European Research Council under the European Union's Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
+
+\input{app-misc}
 

### 2021-04-09 nnpdf31_proc/ATLAS_WPJET_8TEV_PTW/analysis.f
Add preliminary ATLAS_WPJET_8TEV_PTW dataset

@@ -1,0 +1,88 @@
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_begin(nwgt,weights_info)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      integer nwgt
+      character*(*) weights_info(*)
+
+      call set_error_estimation(1)
+      call HwU_inithist(nwgt,weights_info)
+      call HwU_book(1, 'W pT', 8,   0.0d0, 200.0d0)
+      call HwU_book(2, 'W pT', 6, 200.0d0, 500.0d0)
+      call HwU_book(3, 'W pT', 1, 500.0d0, 600.0d0)
+      call HwU_book(4, 'W pT', 1, 600.0d0, 800.0d0)
+
+      return
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_end(dummy)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      double precision dummy
+      call HwU_write_file
+      return
+      end
+
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      subroutine analysis_fill(p,istatus,ipdg,wgts,ibody)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+
+      implicit none
+      include 'nexternal.inc'
+      include 'cuts.inc'
+      integer istatus(nexternal)
+      integer iPDG(nexternal)
+      integer ibody
+      integer i
+      integer j
+      double precision p(0:4,nexternal)
+      double precision wgts(*)
+      double precision ppl(0:3), pplb(0:3), ppv(0:3), ptv, getinvm
+      external getinvm
+
+      double precision p_reco(0:4,nexternal)
+      integer iPDG_reco(nexternal)
+
+      call recombine_momenta(rphreco, etaphreco, lepphreco, quarkphreco,
+     $                       p, iPDG, p_reco, iPDG_reco)
+
+      do j = nincoming+1, nexternal
+        if (iPDG_reco(j).eq.14) ppl(0:3)=p_reco(0:3,j)
[…]

### 2021-04-09 paper/sec-pineappl.tex
Correct mistake in sentence

@@
 
-\item \textsc{PineAPPL} has been explicitly interfaced to \textsc{mg5\_aMC} (v3+)~\cite{Alwall:2014hca,Frederix:2018nkq},\footnote{A version of \textsc{mg5\_aMC} interfaced to \textsc{PineAPPL} can be downloaded from \url{https://launchpad.net/mg5amc-pineappl/trunk}, and it will be included as standard in the next \textsc{mg5\_aMC} release.} see appendix~\ref{app:sample-runcard} for an example of a runcard.
+\item \textsc{PineAPPL} has been explicitly interfaced to \textsc{mg5\_aMC} (v3+)~\cite{Alwall:2014hca,Frederix:2018nkq},\footnote{A version of \textsc{mg5\_aMC} interfaced to \textsc{PineAPPL} can be downloaded from \url{https://launchpad.net/mg5amc-pineappl/trunk}, and it will be included as standard starting from the 3.0.4 release of \textsc{mg5\_aMC}.} see appendix~\ref{app:sample-runcard} for an example of a runcard.
 The usage of \textsc{mg5\_aMC}(v3+) + \textsc{PineAPPL} is similar to that of \textsc{mg5\_aMC}(v2) + \textsc{aMCfast} + \textsc{APPLgrid}.
@@
 In experiments, but also for many calculations where the phase-space integration is performed using MC techniques, finite statistics does not allow for the exact reconstruction of the dependence of the cross section on the observable $\mathcal{O}$.
-Instead, it it sufficient to approximate the derivative using a piecewise-constant function,
+Instead, it is sufficient to approximate the derivative using a piecewise-constant function,
 \begin{equation}

### 2021-04-28 paper2/sec-datasets.tex

\section{Datasets}
\label{sec:datasets}

We will now discuss potential datasets for an NLO EW PDF fit.

\subsection{Drell--Yan lepton-pair production}
\label{sec:dy-at-the-lhc}

The inclusive production of a single same-flavour opposite-sign (SFOS) lepton pair, $\mathrm{p}\mathrm{p} \to \ell \bar{\ell} + \mathrm{X}$, is an important ingredient in PDF fitting.
On the experimental side this process features large cross sections, which translate to small experimental uncertainties.
On the other hand, the comparative simplicity of the $2 \to 2$ process allows for the calculation of NNLO QCD corrections, which are needed to match the experimental precision.
Finally, we do not expect any new physics in a very large phase space covered by Drell--Yan (DY) measurements.
This makes DY an ideal candidate for the inclusion in PDF determinations.

Observables often used in DY datasets are the invariant mass, $M_{\ell\bar{\ell}}$, and the rapidity, $y_{\ell\bar{\ell}}$, both for the lepton pair.
At LO they are directly related to the parton fractions $x_1$ and $x_2$:
\begin{equation}
M_{\ell\bar{\ell}} = \sqrt{s x_1 x_2} \text{,} \quad y_{\ell\bar{\ell}} = \frac{1}{2} \log \left( \frac{x_1}{x_2} \right) \text{.}
\end{equation}
Less-used observables include the Collins--Soper angle, $\cos \theta^*$, see e.g.\ ref.~\cite{Aaboud:2017ffb}, and see the discussion in app.~\ref{app:the-collins-soper-angle}.

In the context of EW PDF fits, the following features of are new with respect to a purely QCD fit:
\begin{enumerate}
\item Non-zero photon PDFs.
DY lepton-pair production features a contribution with two photon initial states.
These contributions are typically neglected in NNLO QCD PDF fits, and, also subtracted in data from the experimental collaborations.
The size of this contribution depends---obviously---on the PDF set used in the calculation, and can be as high as TODO in the region of $\SI{1}{\tera\electronvolt} < M_{\ell\bar{\ell}} < \SI{1.5}{\tera\electronvolt}$ for $\sqrt{s} = \SI{7}{\tera\electronvolt}$.
\item Final-state radiation (FSR).
The radiation of photons off the final-state leptons induce very large corrections, typically in the invariant mass distributions $M_{\ell\bar{\ell}}$ in the vicinity of the Z-boson mass.
For example, for the CMS \SI{13}{\tera\electronvolt} measurement~\cite{Sirunyan:2018owv}, the NLO EW corrections (which include a perturbative approximation of the FSR corrections) are as large as \SI{60}{\percent}.
However, the size depends very strongly on the chosen bin limits; often bin limits are chosen symmetrically around the Z-boson mass, in which positive and negative corrections almost cancel each other.
The remainder of large FSR corrections are then only seen in the bins below the Z peak.

Since FSR corrections are potentially large, but not covered by NNLO QCD corrections, they are often subtracted in data.
The problems of this practice are discussed e.g.\ in ref.~\cite{Carrazza:2020gss}.
\item Weak corrections.
Above a certain invariant mass of the lepton pair, say at \SI{200}{\giga\electronvolt}, the electroweak corrections show the typical negative corrections, which can be as large as TODO around \SI{1}{\tera\electronvolt}.
In NNLO QCD PDF fits this regions is therefore usually excluded.
\end{enumerate}

### 2021-05-06 paper2/sec-schemechange.tex

\section{Scheme-change operator}
\label{sec:scheme-change-operator}

At LO in $\alpha$, the coupling $\alpha$ in the PDF (as used in the evolution equations) and in the fixed-order calculations can be chosen independently.
This is important, because in the PDFs the coupling is typically assumed to be renormalised in the $\overline{\mathrm{MS}}$ scheme, while in fixed-order calculations $\alpha$ is usually chosen according to the $G_\mu$ scheme.

At NLO in $\alpha$, this is---at least conceptually---no longer trivially possible: in the fixed-order calculation a collinear counter term is present, which implements the PDF redefinition and, in particular, subtracts initial-state QED singularities.
From the PDF redefinition the evolution equations can be derived, which makes clear that there is a non-trivial connection in the choice of $\alpha$ in 1) the evolution equations and 2) the collinear counter term.
Note this only concerns the additional power in $\alpha$ in the counter term, as this corresponds to the $\alpha$ in the evolution equations.
The remaining powers in $\alpha$ coming from the LO are disconnected from the DGLAP equations, as argued above, and can therefore still be chosen independently.

For the additional power in $\alpha$ we therefore have a mismatch between the evolution equations and the collinear counter term in the fixed-order calculation.
We can correct for this mismatch by introducing a new term in the fixed-order calculation, which is the difference between the collinear counter term with a running $\overline{\mathrm{MS}}$ $\alpha (\mu)$, and the counter term actually used.
If we assume for the following that we use a $G_\mu$ input scheme for $\alpha$, this term is the collinear counter term, with the additional power in $\alpha$ replaced by
\begin{equation}
\alpha (Q^2) - \alpha_{G_\mu} \text{,} \label{eq:consistency-condition}
\end{equation}
and the remaining powers of $\alpha$ in the LO matrix element as chosen in the fixed-order calculation.
Consistency requires this term not to introduce additional singularities at NLO EW, so we have to expand $\alpha (Q^2)$, at the order given by the evolution equations used for fitting the PDFs.
For example, in leading-logarithmic approximation,
\begin{equation}
\alpha (Q^2) = \frac{\alpha (\mu^2)}{1 - \alpha (\mu^2)/(3\pi) \ln (Q^2/\mu^2)} \text{,}
\end{equation}
we can find a scale $\mu^2$ so that $\alpha (\mu^2) = \alpha_{G_\mu}$, and therefore eq.~\eqref{eq:consistency-condition} becomes
\begin{equation}
\alpha (Q^2) - \alpha_{G_\mu} = \frac{\alpha_{G_\mu}^2}{3 \pi} \ln \frac{Q^2}{\mu^2} + \mathcal{O} (\alpha_{G_\mu}^3) \text{,}
\end{equation}
which shows that although there is a non-trivial consistency condition at NLO EW, the difference is formally higher order.

### 2021-05-06 paper2/sec-schemechange.tex
Add placeholder for initial-state photons

@@
 
-At LO in $\alpha$, the coupling $\alpha$ in the PDF (as used in the evolution equations) and in the fixed-order calculations can be chosen independently.
+At LO in $\alpha$, the coupling $\alpha$ in the PDF (as used in the evolution equations) and in the fixed-order calculations can be chosen independently, if no initial-state photons are present.
+\textbf{TODO}: Marco insert discussion here, and change the next sentence accordingly.
+
 This is important, because in the PDFs the coupling is typically assumed to be renormalised in the $\overline{\mathrm{MS}}$ scheme, while in fixed-order calculations $\alpha$ is usually chosen according to the $G_\mu$ scheme.

### 2021-05-24 paper2/sec-schemechange.tex

@@
 For the additional power in $\alpha$ we therefore have a mismatch between the evolution equations and the collinear counter term in the fixed-order calculation.
-We can correct for this mismatch by introducing a new term in the fixed-order calculation, which is the difference between the collinear counter term with a running $\overline{\mathrm{MS}}$ $\alpha (\mu)$, and the counter term actually used.
-If we assume for the following that we use a $G_\mu$ input scheme for $\alpha$, this term is the collinear counter term, with the additional power in $\alpha$ replaced by
+We can correct for this mismatch by introducing a new term in the fixed-order calculation, which is the difference between the collinear counter term with a running $\overline{\mathrm{MS}}$ $\hat{\alpha} (\mu_\mathrm{R})$, and the counter term actually used.
+If we assume for the following that we use a $G_\mu$ input scheme for $\alpha$, this term is the collinear counter term, with the additional power in $\alpha$ replaced by the difference of $\alpha_{G_\mu}$ and the $\overline{\text{MS}}$ coupling $\hat{\alpha} (\mu_\mathrm{R}^2)$:
 \begin{equation}
-\alpha (Q^2) - \alpha_{G_\mu} \text{,} \label{eq:consistency-condition}
+\hat{\alpha} (\mu_\mathrm{R}^2) - \alpha_{G_\mu} = \alpha_{G_\mu} \left( \Delta \hat{\alpha} (\mu_\mathrm{R}^2) - \Delta r^{(1)} + \ldots \right) \text{,} \label{eq:consistency-condition}
 \end{equation}
-and the remaining powers of $\alpha$ in the LO matrix element as chosen in the fixed-order calculation.
-Consistency requires this term not to introduce additional singularities at NLO EW, so we have to expand $\alpha (Q^2)$, at the order given by the evolution equations used for fitting the PDFs.
-For example, in leading-logarithmic approximation,
+which uses the following definitions,
 \begin{equation}
-\alpha (Q^2) = \frac{\alpha (\mu^2)}{1 - \alpha (\mu^2)/(3\pi) \ln (Q^2/\mu^2)} \text{,}
+\hat{\alpha} (\mu_\mathrm{R}^2) = \frac{\alpha(0)}{1 - \Delta \hat{\alpha} (\mu_\mathrm{R}^2)} \text{,} \qquad \alpha_{G_\mu} = \alpha(0) \left( 1 + \Delta r^{(1)} \right) + \mathcal{O} (\alpha(0)^3) \text{,}
 \end{equation}
-we can find a scale $\mu^2$ so that $\alpha (\mu^2) = \alpha_{G_\mu}$, and therefore eq.~\eqref{eq:consistency-condition} becomes
-\begin{equation}
-\alpha (Q^2) - \alpha_{G_\mu} = \frac{\alpha_{G_\mu}^2}{3 \pi} \ln \frac{Q^2}{\mu^2} + \mathcal{O} (\alpha_{G_\mu}^3) \text{,}
-\end{equation}
-which shows that although there is a non-trivial consistency condition at NLO EW, the difference is formally higher order.
+which in make use of the fine-structure constant $\alpha(0)$; all quantities are given e.g.\ in ref.~\cite{Denner:2019vbn} and references therein.
+Since all $\Delta$ terms are $\mathcal{O} (\alpha)$, the difference in eq.~\eqref{eq:consistency-condition} is $\mathcal{O} (\alpha^2)$ and therefore zero at NLO EW in the full perturbative calculation.
+This must be the case, otherwise the scheme-change operator we defined above would introduce additional singularities.

### 2021-05-24 paper2/sec-schemechange.tex
some text in sec-schemechange

@@
 
-At LO in $\alpha$, the coupling $\alpha$ in the PDF (as used in the evolution equations) and in the fixed-order calculations can be chosen independently, if no initial-state photons are present.
-\textbf{TODO}: Marco insert discussion here, and change the next sentence accordingly.
+In this section, we elaborate on the consistency between the coupling renormalisation in the PDFs (entering the evolution equation) and in 
+the partonic matrix-element. {\bf MZ add citations}
+At LO accuracy in $\alpha$, the two couplings can be chosen independently, as any ambiguity in the definition of $\alpha$  is higher-order.
+While, in general, $\alpha$ is defined in the $\overline{\textrm{MS}}$ scheme in the PDF, the choice for the value (and renormalisation conditions)
+in the partonic matrix-element depends on the process at hand. For example, for most LHC processes, 
+one may want to use a scheme such as the $G_\mu$ scheme, which includes all-order weak effects. An exception is the case where tagged final-state
+photons are present, where one should use the Thomson value $\alpha(0)$ for the vertices where the photons are present. In the counterpart
+of this last example where the photons are in the initial state, i.e. they are part of the partonic content of the proton, a sensible choice 
+seems the one of employing $\overline{\textrm{MS}}$ scheme, at least for the vertices where the photons eneter, since they come 
+directly from the parton evolution.\\
 
-This is important, because in the PDFs the coupling is typically assumed to be renormalised in the $\overline{\mathrm{MS}}$ scheme, while in fixed-order calculations $\alpha$ is usually chosen according to the $G_\mu$ scheme.
-
-At NLO in $\alpha$, this is---at least conceptually---no longer trivially possible: in the fixed-order calculation a collinear counter term is present, which implements the PDF redefinition and, in particular, subtracts initial-state QED singularities.
-From the PDF redefinition the evolution equations can be derived, which makes clear that there is a non-trivial connection in the choice of $\alpha$ in 1) the evolution equations and 2) the collinear counter term.
-Note this only concerns the additional power in $\alpha$ in the counter term, as this corresponds to the $\alpha$ in the evolution equations.
-The remaining powers in $\alpha$ coming from the LO are disconnected from the DGLAP equations, as argued above, and can therefore still be chosen independently.
-
-For the additional power in $\alpha$ we therefore have a mismatch between the evolution equations and the collinear counter term in the fixed-order calculation.
-We can correct for this mismatch by introducing a new term in the fixed-order calculation, which is the difference between the collinear counter term with a running $\overline{\mathrm{MS}}$ $\hat{\alpha} (\mu_\mathrm{R})$, and the counter term actually used.
-If we assume for the following that we use a $G_\mu$ input scheme for $\alpha$, this term is the collinear counter term, with the additional power in $\alpha$ replaced by the difference of $\alpha_{G_\mu}$ and the $\overline{\text{MS}}$ coupling $\hat{\alpha} (\mu_\mathrm{R}^2)$:
+At NLO in $\alpha$, this freedom seems not to be there any longer, at least conceptually: in fixed-order calculations a collinear counter term is present,
+which subtracts initial-state collinear singularities and implements the so-called PDF redefinition. This counter-term is
+essentially the $\mathcal O(\alpha)$ expansion, or at least it should be, since the two definitions of $\alpha$ may differ. However, any
+dfference in the two definitions is $\mathcal O(\alpha^2)$, thus beyond NLO accuracy. This is why the usage of e.g. the $G_\mu$ scheme
+is still possible (and in general recommended) when NLO EW corrections are computed. One notable exception
+is the case when initial-state photons are present. As argued above, the corresponding coupling should be renormalised in the $\overline{\textrm{MS}}$ scheme.
+If one fails to do so, as it is the case for all (to our knowledge) general-purpose programs which compute NLO EW corrections for a generic process, in
+principle a mismatch is introduced at NLO. In practice, given that \emph{numerically} photon-initiated processes are of the same order of EW corrections,
+one can argue that such a mismatch turns to be subleading for all practical purposes. Still, it is worth to provide some formulas, which can help to gauge the impact of the missing terms.
+Let $n_I$ be the number of initial-state photons, and $b$ the power of $\alpha$ entering (a given contribution to) the Born squared matrix-element $\mathcal B$. If
+one employs the $G_\mu$ scheme everywhere, then
 \begin{equation}
-\hat{\alpha} (\mu_\mathrm{R}^2) - \alpha_{G_\mu} = \alpha_{G_\mu} \left( \Delta \hat{\alpha} (\mu_\mathrm{R}^2) - \Delta r^{(1)} + \ldots \right) \text{,} \label{eq:consistency-condition}
+    \mathcal B_{G_\mu}= \alpha_{G_\mu}^b B,
+\end{equation}
+where $B$ does not contain any power of $\alpha$. If instead the $\overline{\textrm{MS}}$ scheme is employed for initial-state photons, then one has
+\begin{equation}
+    \mathcal B_{\overline{\textrm{MS}}}= \alpha_{G_\mu}^{b-n_I} \hat \alpha^{n_I} B,
+\end{equation}
+where we have denoted $\alpha$ in the $\overline{\textrm{MS}}$ scheme as $\hat\alpha$, and we have omitted its dependence on the scale.
+Thus, the mismatch between the two cases is
+\begin{equation}
+    \mathcal B_{G_\mu} - \mathcal B_{\overline{\textrm{MS}}}  = \left[ \alpha_{G_\mu}^b B - \alpha_{G_\mu}^{b-n_I} \alpha_{\overline{\textrm{MS}}}^{n_I} \right] B =
+    n_I \frac{\Delta \alpha_{G_\mu-\overline{\textrm{MS}}}}{\alpha_{G_\mu}} \alpha_{G_\mu}^b B  + \mathcal O (\alpha^2),
+\end{equation}
+where
+\begin{equation}
+\frac{\Delta \alpha_{G_\mu-\overline{\textrm{MS}}}}{\alpha_{G_\mu}}(\mu_\mathrm{R}^2) = 
+\left(\Delta r^{(1)} - \Delta \hat{\alpha} (\mu_\mathrm{R}^2) + \ldots \right) \text{,} \label{eq:consistency-condition}
 \end{equation}
@@
 which in make use of the fine-structure constant $\alpha(0)$; all quantities are given e.g.\ in ref.~\cite{Denner:2019vbn} and references therein.
-Since all $\Delta$ terms are $\mathcal{O} (\alpha)$, the difference in eq.~\eqref{eq:consistency-condition} is $\mathcal{O} (\alpha^2)$ and therefore zero at NLO EW in the full perturbative calculation.
-This must be the case, otherwise the scheme-change operator we defined above would introduce additional singularities.
+
+{\bf MZ add plot of DeltaAlpha and discuss it a bit}
